### 2021-03-18 paper/tex/paper.tex
add latex source

\documentclass[twocolumn]{aastex63}
\received{\today}
\shorttitle{Detecting DCOs with LISA}
\graphicspath{{../figures/}}

\usepackage{lipsum}
\usepackage{physics}
\usepackage{multirow}
\usepackage{xspace} %this package handles when to use a whitespace in math symbols
\usepackage{natbib} %this package can be used for creating an automated bibliography.

% remove indents in footnotes
\usepackage[hang,flushmargin]{footmisc}

%Latex allows you to define abbreviations. \newcommand{.. here comes the short notation ...}{ ... here comes the full latex command... small change}

\newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}

\newcommand{\floor}[1]{\textcolor{magenta}{[Floor: #1]}}
\newcommand{\selma}[1]{\textcolor{pink}{[Selma: #1]}}
\newcommand{\tom}[1]{\textcolor{ForestGreen}{[Tom: #1]}}

% custom function for adding units
\makeatletter
\newcommand{\unit}[1]{%
    \,\mathrm{#1}\checknextarg}
\newcommand{\checknextarg}{\@ifnextchar\bgroup{\gobblenextarg}{}}
\newcommand{\gobblenextarg}[1]{\,\mathrm{#1}\@ifnextchar\bgroup{\gobblenextarg}{}}
\makeatother

% Define symbols for Rsun and Msun, Lsun and Teff ensuring proper formatting
\newcommand{\Rsun}{\ensuremath{\,\mathrm{R_\odot}}\xspace} % Solar radius symbol
\newcommand{\Msun}{\ensuremath{\,\mathrm{M_\odot}}\xspace} % Solar mass symbol
\newcommand{\Lsun}{\ensuremath{\,\mathrm{M_\odot}}\xspace} % Solar luminosity symbol
\newcommand{\Teff}{\ensuremath{\,\mathrm{T_{\rm eff}}}\xspace} % Effective temperature symbol
\newcommand{\Myr}{\ensuremath{\,\mathrm{Myr}}\xspace} % symbol for Mega year
\newcommand{\Gyr}{\ensuremath{\,\mathrm{Gyr}}\xspace} % symbol for Gyr

\newcommand{\avg}[1]{\left\langle#1\right\rangle}

%% Physics variations shortcuts
\newcommand{\modFid}{A}
\newcommand{\modBetaLow}{B}
\newcommand{\modBetaMed}{C}
\newcommand{\modBetaHigh}{D}
\newcommand{\modCaseBB}{E}
\newcommand{\modAlphaLow}{F}
\newcommand{\modAlphaHigh}{G}
\newcommand{\modOpt}{H}
\newcommand{\modRapid}{I}
\newcommand{\modNSLow}{J}
\newcommand{\modNSHigh}{K}
\newcommand{\modNoPISN}{L}
\newcommand{\modSigLow}{M}
\newcommand{\modSigLower}{N}
\newcommand{\modNoBH}{O}

\newcommand{\modRangeMT}{B-E}
\newcommand{\modRangeCE}{F-H}
\newcommand{\modRangeSN}{I-O}

\newcommand{\confinv}[3]{$#1${\raisebox{0.5ex}{\tiny$_{-#2}^{+#3}$}}}

\definecolor{Blush}{rgb}{0.87, 0.36, 0.51}
\newcommand{\SdM}[1]{{\color{Blush}{#1}}}

\begin{document}

\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}

\author[0000-0001-6147-5761]{T. Wagg}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0002-4421-4962]{F. Broekgaarden}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}

\begin{abstract}
{The Laser Inteferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves. Detections of double compact objects with LISA may help to constrain uncertainties in binary evolution and understand the prevalence of electromagnetic counterparts to gravitational wave events. We estimate the number of Galactic DCOs that will be detected by LISA using a sample generated with the rapid population synthesis code COMPAS and a model of the Milky Way that includes not only the radial birth profiles but also the star formation and enrichment histories. We explore the effects of varying 15 physical assumptions that focus on key uncertainties in our understanding of mass transfer, common envelope and supernova physics. For our fiducial model, we find that over a 4 year mission, LISA will detect 26 BHBHs, 27 BHNSs and 12 NSNSs. These detection rates increase to 41, 45 and 19 respectively for a 10 year mission length. We present the distributions of the characteristics of the detectable binaries and explore how our different models affect them. We also discuss how well we can distinguish between different DCO types and methods for doing so.}
\end{abstract}

\keywords{LISA, black hole, neutron star, binary}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction} \label{sec:intro}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{LIGO_2016_BBHinfirstRun}, there have been 50 gravitational wave events detected by LIGO \citep{LIGO_GWTC1, LIGO_GWTC2}. The investigation of double compact object (DCO) population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different DCO types.

The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) provides an exciting new lens through which to view the realm of gravitational waves. LISA will observe binaries at lower orbital frequencies than LIGO ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger. This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which allows for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}. In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Vigna-Gomez+2018}, differentiate between formation channels and distinguish between DCO types.

One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS). Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{LIGO_GW190425, LIGO_GW190814}.

Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. Collating a sample of BHNS binaries will allow us to better understand whether there are electromagnetic counterparts to their gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}. Moreover, if the neutron star is observable (such as a pulsar), a BHNS would be ideal for measuring the Hubble constant \citep[e.g.][]{Feeney+2020} and the neutron star equation of state. A detection with LISA would allow these various signals to be measured for years before the merger and give observers ample time to prepare for the merger itself.

The detection of double compact objects with LISA has been investigated in many recent studies. \citet{Korol+2017, Korol+2020} use the binary population synthesis code SeBa to focus on predictions for double white dwarf binaries (WDWD). \citet{Lamberts+2018, Lamberts+2019} instead use a hydrodynamic simulation from the FIRE project \citep{Hopkins+2014} to produce predictions for double black hole binaries (BHBH) and WDWD. Closer to this study, \citet{Breivik+2019} uses the COSMIC population synthesis code to predict detection rates for all double compact objects and \citet{Lau+2020} uses the same population synthesis code as this study, COMPAS, and focusses on double neutron star binaries (NSNS).

In this paper, we present predictions for the detection rate and distribution of binary characteristics (masses, frequency, eccentricity, distance, merger time) of BHNS, BHBH and NSNS binaries formed through isolated binary evolution in the Milky Way using binaries synthesised with the \href{https://compas.science}{COMPAS} rapid population synthesis code \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019} in tandem with the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019}. Additionally, we use a model of the Milky Way that not only includes the radial birth profiles but also the star formation and enrichment history. We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results. In this study we consider three main questions: (1) how many of each type of DCO will LISA detect? (2) can we distinguish between different DCOs with LISA? (3) can we use detections in LISA to constrain uncertainties in binary evolution?

In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA. In Section~\ref{sec:resultsI}, we explore the detection of double compact objects with LISA analytically. In Section~\ref{sec:resultsII}, we present our main results for each type of DCO and variation of physical assumptions. In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method} \label{sec:method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Binary population synthesis}\label{sec:COMPAS_explained}

We use a population of binaries synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}. COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}. Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using the single star evolution fitting formulae from \citet{Hurley+2000} to the models of \citet{Pols+1998}. In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample. This algorithm increases the prevalence of target DCOs (BHBH, BHNS and NSNS binaries in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.

\subsubsection{Population Overview}

The population of double compact objects used in this study was synthesised by \citet{Broekgaarden+2021}. One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.

\subsubsection{Initial Conditions}

Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation. The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$. The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g. with][]{Sana+2012}. We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star. We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik1924, Abt1983}. We assume that all binaries are circular at birth to reduce the dimensions of initial parameters. Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, de-Mink+2015}.

For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation and gravitational-wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL. We sample from these sets of parameters when creating synthetic galaxies.

\subsubsection{Physical assumptions in fiducial model}\label{sec:fiducial_physics}
In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see Section 2.1.2 and Table 1 of \citet{Broekgaarden+2021}.

\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}. The mass transfer efficiency, $\beta = \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor. We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}. The maximum accretion rate for double compact objects is limited to the Eddington accretion rate. If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star, thus varying $\beta$ \citep[e.g.][]{Massevitch+1975, Soberman+1997}. We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.

\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink1984} and \citet{de-Kool1990}. We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope. For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}. We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam&Sandquist2000, Ivanova+2004}. This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007a}. We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections.

\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs. For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}. The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}. We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.

We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto1984, Nomoto1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ as in \citet{Pfahl+2002} and \citet{Podsiadlowski+2004}.

We assume that stars that undergo case BB mass transfer experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).

Stars with helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.

We assume that kicks are isotropic in the frame of the collapsing star. The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996_maxNS, Fryer+2015, Margalit&Metzger2017}. % removed Lawrence+2015 Alsing+2018
We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

\subsubsection{Physical assumptions in other models} \label{sec:variation_assumptions}
In addition to our fiducial model, we explore 14 other models which change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions. Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.

Models \modRangeMT{} focus on changes to the mass transfer physics. We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively. In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.

Models \modRangeCE{} focus on altering the common envelope physics. We change the common envelope efficiency parameter in models \modAlphaLow{} and \modAlphaHigh{} to $\alpha = 0.5$ and $2.0$ respectively. In model \modOpt, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.

Finally, models \modRangeSN{} make changes related to our assumptions about supernova physics. Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription. We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses. Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae. In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks. Finally, model \modNoBH{} removes the natal kick for all black holes.

\begin{table}[htb]
    \centering
    \begin{tabular}{cl}
        \hline \hline
        Model & Physics Variation \\
        \hline \hline
        \modFid & -- \\
        \hline
        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
        \modCaseBB & Case BB mass transfer is always unstable \\
        \hline
        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
        \modOpt & HG donor stars initiating a CE survive CE \\
        \hline
        \modRapid & Fryer rapid SN remnant mass prescription \\
        \modNSLow & Maximum NS mass is fixed to $2\Msun$ \\
        \modNSHigh & Maximum NS mass is fixed to $3\Msun$ \\
        \modNoPISN & PISN and pulsational-PISN not implemented \\
        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
        \modNoBH & Black holes receive no natal kick \\
        \hline \hline
    \end{tabular}%
    \caption{Adapted from \citet[][Table 2]{Broekgaarden+2021}, a description of the 15 binary population synthesis models used in this study. \modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics.}
    \label{tab:physics_variations}
\end{table}

\subsection{Galaxy Synthesis}

In order to produce a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries. For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc. We do not find that adding other components would significantly alter our results.

Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution. We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.

\subsubsection{Milky Way disc model}

For the Milky Way thin disc, we use the model from \citet{Frankel+2018}. The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way. They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{APOGEE} and Gaia \citep{Gaia-Collaboration+2016}. The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy. We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.

The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
\begin{equation}\label{eq:galaxy_tau}
    p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
\end{equation}
where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}. The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq. 5]{Frankel+2018}
\begin{equation}\label{eq:galaxy_R}
    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \cdot \frac{R_0}{[R_{\rm exp}(\tau)]^2},
\end{equation}
where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
\begin{equation}
    R_{\rm exp}(\tau) = 4 \unit{kpc} \qty(1 - \alpha_{R_{\rm exp}} \qty(\frac{\tau}{8 \unit{Gyr}})),
\end{equation}
where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
\begin{equation}\label{eq:galaxy_FeH}
    \begin{split}
        [{\rm Fe} / {\rm H}] (R, \tau) = &F_m + \nabla [{\rm Fe} / {\rm H}] R \\
        &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
    \end{split}
\end{equation}
where
\begin{equation}
    f(\tau) = \qty(1 - \frac{\tau}{\tau_m})^{\gamma_{[{\rm Fe} / {\rm H}]}},
\end{equation}
$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}. We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
\begin{equation}\label{eq:galaxy_FeH_to_Z}
    \log Z = 0.977 [{\rm Fe} / {\rm H}] + \log(Z_\odot).
\end{equation}
Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan2011},
\begin{equation}\label{eq:galaxy_z}
    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
\end{equation}
where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$. Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{MAKEME}.

\subsubsection{Combining population and galaxy synthesis}

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_metallicity} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{galaxy_diagram.png}
    \caption{A schematic showing how we create a mock Mily Way disc. On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan2011}. On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points. The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$). The top panel shows a side-on view and the bottom panel shows a view from above.}
    \label{fig:galaxy_schematic}
\end{figure*}

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=\columnwidth]{galaxy_metallicity.png}
%     \caption{A random instance of the Milky Way of $10^5$ binaries, created using distributions from \citet{Frankel+2018}. The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$). The top panel shows a side-on view and the bottom panels shows a view from above.}
%     \label{fig:galaxy_metallicity}
% \end{figure}

We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by randomly drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.

Each binary is likely to move from its birth orbit. Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood&Binney2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.

The magnitude of the systemic kicks are typically small compared to the intital circular velocity of a binary at each Galactocentric radius. Therefore, kicks will not significantly alter the overall distribution of their positions. Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.

\subsection{Gravitational Wave Inspiral}

Each binary loses orbital energy to gravitational waves throughout its lifetime. This causes the binary to shrink and circularise over time. In order to assess the detectability of a binary, we need to know its eccentricity and frequency at the time of the LISA mission. For each binary in our simulated Milky Way, we know that the time from DCO formation to today is $\tau - t_{\rm evolve}$ and that the initial eccentricity and semi-major axis are $e_{\rm DCO}$ and $a_{\rm DCO}$. We find the eccentricity of the binary at the start of the LISA mission, $e_{\rm LISA}$, by numerically integrating its time derivative \citep[][Eq. 5.13]{Peters1964} given the initial conditions. This additionally can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq. 5.11]{Peters1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.

\subsection{Detectability}

We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2019, Korol+2020}. The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn&Thorne2000}
\begin{equation}\label{eq:snr}
    \rho^2 = \sum_{n=1}^{\infty} \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^{2}}{f_{n}^{2} S_{\rm n}\left(f_{n}\right)} \dd{f_n},
\end{equation}
where $n$ is a harmonic of the gravitational wave signal, $f_n = n \cdot f_{\rm orb}$ is the frequency of the $n^{\rm th}$ harmonic of the gravitational wave signal, $f_{\rm orb}$ is the orbital frequency, $S_{\rm n}(f_n)$ is the LISA sensitivity curve at frequency $f_n$ \citep[e.g.][]{Robson+2019} and $h_{c,n}$ is the characteristic strain of the $n^{\rm th}$ harmonic, given by
\begin{equation}\label{eq:charstrain}
    h^2_{c,n} = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n,e)}{F(e)}
\end{equation}
\citep[e.g.][]{Barack&Cutler2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters1963} and $\mathcal{M}_c$ is the chirp mass, defined as
\begin{equation}\label{eq:chirp_mass}
    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}}.
\end{equation}

For the sake of computational efficiency, it is convenient to make the approximation that many of the binaries are stationary in frequency space on the timescale of the observing mission. This simplifies the signal-to-ratio equation to
\begin{equation}\label{eq:snr_stat}
    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 \, T_{\rm obs} h_n^2}{S_n(f_n)},
\end{equation}
where $T_{\rm obs}$ is the observing time and $h_n$ is the strain amplitude of gravitational waves emitted in the $n^{\rm th}$ harmonic, given by
\begin{equation}
    h_n^2 = \frac{2^{25/3}}{5} \frac{\left(G \mathcal{M}_{c}\right)^{10/3}}{c^{8}} \frac{\left(\pi f_{\mathrm{orb}}\right)^{4 / 3}}{D_L^2} \frac{g(n, e)}{n^2}.
\end{equation}

We consider a binary as stationary if its change in gravitational wave frequency is less than 1\% of the initial frequency. None binaries in our sample are in the non-stationary regime and therefore we believe that this is an acceptable approximation.

\subsection{Detection rate}
We calculate the detection rate for any one Milky Way instance by determining the fraction of binaries that are detectable and normalising to the true mass and IMF of the Milky Way in order to account for our relatively smaller galaxy size and restricted mass ranges. For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results (I)  - Survey of the Problem} \label{sec:resultsI}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we explore the problem of detecting double compact objects with LISA analytically, focussing specifically on BHNS binaries, before presenting our full simulation results in Section~\ref{sec:resultsII}.

\subsection{The Role of Eccentricity}\label{sec:eccentricity_role}

Unlike BHBH binaries, a significant fraction of the BHNS binary population is highly eccentric. A high eccentricity has two major effects on detecting a binary with gravitational waves.

Firstly, eccentricity enhances the rate of energy emission via gravitational waves by a factor
\begin{equation}
    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}},
\end{equation}
compared to a circular binary with the same semi-major axis \citep[][Eq.\,17]{Peters1963}. This means that eccentric binaries will not only inspiral faster, but also produce gravitational waves with stronger strain amplitudes (when summed over all harmonics).

Secondly, eccentric binaries will emit gravitational waves at many harmonic frequencies (unlike circular binaries, which only emit at twice the orbital frequency). This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters1963}.

Therefore, though the first effect always increases the strength of the signal, the two effects in tandem do not necessarily always increase the detectability of a binary and we illustrate this point in Fig.\,\ref{fig:ecc_effects}. We show effect of eccentricity on the gravitational wave signal from a typical BHNS binary of chirp mass $\mathcal{M}_c = 3 \unit{M_{\odot}}$ and distance $8 \unit{kpc}$ at an orbital frequency of $f_{\rm orb} = 3 \times 10^{-4} \unit{Hz}$. Increasing the eccentricity from $e = 0.0$ to $0.5$ results in an increase in the signal-to-noise ratio (annotated on each set of points). This is because the eccentricity not only increases the gravitational wave emission, but also shifts the peak of the signal towards the minimum of the LISA sensitivity curve. However, further increasing the eccentricity from $e = 0.5$ to $0.9$ instead \textit{decreases} the signal-to-noise ratio. Although the greater eccentricity produces a stronger strain, it also shifts the peak of the gravitational wave signal to such high frequencies that the noise level is much higher and therefore has a lower signal-to-noise ratio.

Overall, we can therefore conclude that for BHNS binaries, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve. Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{e_sc_combined.png}
    \caption{An illustration of the effect of eccentricity on the detectability of a typical BHNS binary. Each point shows the strength of the gravitational wave signal at a harmonic frequency. We annotate each set of points with the binary's total signal-to-noise ratio summed over all harmonics and overplot the LISA sensitivity curve \citep{Robson+2019}.}
    \label{fig:ecc_effects}
\end{figure}

\subsection{Horizon Distance}

We define the horizon distance as the maximum distance at which a binary will have an signal-to-noise ratio above 7. In Figure~\ref{fig:bhns_horizon_distance} we show the horizon distance for a typical BHNS binary for different orbital frequencies and eccentricities. The horizon distance increases with frequency since the signal-to-noise ratio scales as
\begin{equation}
    \rho \propto \frac{N_{\rm cycle} \cdot h}{S_{\rm n}(f)} \propto \frac{f^{2/3} \cdot f^{1/2}}{S_{\rm n}(f)} \propto \frac{f^{7/6}}{S_{\rm n}(f)}.
\end{equation}
Since the minimum in the sensitivity curve occurs at $f \sim 10^{-2} \unit{Hz}$, the horizon distance increases monotonically with frequency. The dependence of the horizon distance on eccentricity follows the trends that we outlined in Section~\ref{sec:eccentricity_role}. The horizon distance increases with eccentricity up to a maximum, before decreasing once the eccentricity moves the peak of the gravitational wave luminosity past the minimum of the sensitivity curve. The eccentricity at which this maximum occurs is lower for higher orbital frequencies as less eccentricity is needed to move the peak past the minimum in the sensitivity curve. One may also note the sharp decrease in the horizon distance for binaries to the right of the $T_{\rm obs}$ contour, since these binaries will merge before the LISA mission is over.

This plot shows that, in principle, we could detect a BHNS binary up to several Mpc from Earth and thus plausibly in any galaxy in the Local Group. In reality, the number extragalactic detections will likely be very low since the binary needs to be very close to merging to be visible at that distance (as can be noted from the inspiral contours in Fig.~\ref{fig:bhns_horizon_distance}) and it is unlikely that a binary happen to be that close to merging during the LISA mission. However, more specific to this study, one can note that the combination of frequency and eccentricity required to be visible within the Milky Way (to the right of the white line in Fig.~\ref{fig:bhns_horizon_distance}) is much more probable.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{horizon_distance.pdf}
    \caption{The horizon distance for a typical BHNS binary at different initial orbital frequencies and eccentricities is shown in the filled contours. The dashed white line indicates the edge of the Milky Way when using the \cite{Frankel+2018} model, which we define as the distance within which 99\% of binaries are contained. The dotted black lines show the inspiral time for the binary.}
    \label{fig:bhns_horizon_distance}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results (II) - Synthetic Galaxy} \label{sec:resultsII}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results for fiducial model}\label{sec:fiducial_distributions}
We find that, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 12 NSNS binaries. Increasing the LISA mission length to ten years changes the number of detections to 41, 45 and 19 respectively. We can note that each shows an increase of approximately $\sqrt{10 / 4} \approx 1.6$ as expected since $\rho \propto \sqrt{T_{\rm obs}}$.

We illustrate the distribution of detectable DCOs lie on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}. The shape of the distributions are bounded by the edge of the Milky Way and the infrequency of nearby DCOs. We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO. The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{dcos_on_sc.png}
    \caption{\tom{This plot needs to be updated after SNR fixes}. Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}. We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries). If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights. In order to explain the edges of the distribution, we additionally plot lines of constant distance. The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
    \label{fig:dcos_on_sc}
\end{figure*}

In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$. This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation. The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.

The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios. The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.

The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable. This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs. Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer. Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.

\subsubsection{Neutron Star Mass}
The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively. The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.

\subsubsection{Eccentricity}
The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs. This may seem counterintuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric. However, these stronger kicks often instead result in disrupted or too-wide binaries. In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric. This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.

\subsubsection{Orbital Frequency and Frequency Evolution}
The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies. This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected. The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies. Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.

\subsubsection{Luminosity Distance}
Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. Each DCO also has a shoulder at lower distances since closer binaries are easier to detect. This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.

\subsubsection{Inspiral Time}
Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{explain the bumps}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{fiducial_pdf_distributions.pdf}
    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model. Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type. The dotted curves in the black hole mass distribution show the primary and secondary mass distributions. In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

\subsection{Distinguishing DCOs}
\todo{}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{fiducial_cdf_distributions.pdf}
    \caption{Cumulative distributions of observable parameters for binaries that are detectable in a 4 year LISA mission. Shaded areas indicate regimes in which no measurement can be made. Dotted lines on the angular resolution distribution show the field of view for various telescopes that could perform EM counterpart observations.}
    \label{fig:fiducial_cdf_distributions}
\end{figure*}

\subsection{Model variations}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections_variations.pdf}
    \caption{The number of expected detections in a four year LISA mission for different DCO types and model variations. Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties. Each model is described in further detail in Table\,\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section\,\ref{sec:fiducial_physics}}
    \label{fig:model_variation_detections}
\end{figure*}

\newcolumntype{S}{>{\centering}p{0.75cm}}
\newcolumntype{Z}{>{\centering\arraybackslash}p{0.75cm}}
\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
    \begin{tabular}{c|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

\subsection{Comparison with other studies}
\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate. This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version. They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:model_variation_detections}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).

We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way. \citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions. The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity. Both of these changes could decrease the rate since most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.

\citet{Breivik+2019} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission. Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2019} assumes the optimistic CE scenario. Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively. The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2019} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:model_variation_detections}, model \modCaseBB{}) . The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion} \label{sec:discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Caveats}
\begin{itemize}
    \item Standard pop synth limitations
    \item Systemic kicks
    \item No models for high $Z$ values in Frankel
    \item Only a single disc for the Milky Way
    \item Stationary approximation? But I'm pretty sure that is fine
\end{itemize}

\subsection{Can we distinguish them?}

\section{Conclusion \& Summary} \label{sec:conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\software{COMPAS (version 02.12.00) \url{http://github.com/TeamCOMPAS/COMPAS}. \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}, \texttt{Python} available from \url{python.org}, matplotlib \citep{matplotlib},  \texttt{NumPy} \citep{numpy}, 
Astropy \citep[\url{http://www.astropy.org}][]{Astropy-Collaboration+2013,Astropy-Collaboration+2018}.}

\acknowledgments{This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No. 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728. We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}

\clearpage

\bibliographystyle{aasjournal}
\bibliography{references, selma_huge_bibs}

\allowdisplaybreaks

\appendix

\section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.

\subsection{Conversions and definitions}
Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
\begin{equation}\label{eq:chirpmass}
    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
\end{equation}
where $m_1$ and $m_2$ are the primary and secondary mass of the binary. Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary. For convenience we show it here
\begin{equation}\label{eq:kepler3rd}
    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
\end{equation}
As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important. We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters1963}
\begin{equation}\label{eq:g(n,e)}
    \begin{aligned}
        g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
        &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
    \end{aligned}
\end{equation}
where $J_{n}(v)$ is the Bessel function of the first kind. Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary. This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters1963}
\begin{equation}\label{eq:eccentricity_enhancement_factor}
    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
\end{equation}
Note that $F(0) = 1$ as one would expect. A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.

\subsection{Characteristic Strain}
The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack&Cutler2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
\begin{equation}\label{eq:char_strain_dedf}
    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
\end{equation}
where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency. The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq. 19]{Peters1963}
\begin{equation}\label{eq:edot_peters}
    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
\end{equation}
where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity. Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
\begin{align}
    \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
    \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
\end{align}
The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
\begin{equation}\label{eq:fdot_chainrule}
    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
\end{equation}
The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
\begin{align}
    f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
    \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
\end{align}
The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters1964}
\begin{equation}\label{eq:dadt}
    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
\end{equation}
Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
\begin{align}
    \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
\end{align}
which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
\begin{align}
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
    &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
    \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
\end{align}
With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
\begin{align}
    h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
    &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
    h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
\end{align}

\subsection{Strain}
The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles. This is explained in \citet{Finn&Thorne2000} and in further detail in \citet{Moore+2015}. The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain. This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio. Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.

Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn&Thorne2000}
\begin{equation}\label{eq:strain-to-charstrain}
    h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
\end{equation}
Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
\begin{align}
    h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
    h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
    h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
\end{align}

\subsection{General Signal-to-Noise Ratio}
We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
\begin{equation}
    \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
\end{equation}
where $z$ is the redshift. We need to adjust this equation in a couple of key ways for LISA Galactic binaries. First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation. Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
\begin{equation}\label{eq:snr_abs}
    \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
\end{equation}
It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
\begin{equation}\label{eq:dedf}
    \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
\end{equation}
where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
\begin{align}
    \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
    &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
    \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
\end{align}
If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
\begin{equation}
    \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
\end{equation}
We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
\begin{equation}\label{eq:snr_general}
    \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
\end{equation}

\subsection{Stationary Signal-to-Noise Ratio}
For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission. In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
\begin{align}
    \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
    &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
\end{align}
Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
\begin{equation}
    \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
\end{equation}
where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}. This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
\begin{equation}
    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
\end{equation}

\section{Detection Rate Normalisation}\label{app:rate_normalisation}
From each instance of the Milky Way that we simulate we can extract the number of targets\footnote{By targets, we are referring to either BHBH, BHNS or NSNS that merge in a Hubble time} that are detectable. However, this number must be normalised in order to show the true detection rate for the Milky Way. Therefore, we write that the number of detectable targets in the Milky Way is
\begin{equation}\label{eq:norm_frame}
    N_{\rm detect} = f_{\rm detect} \cdot N_{\rm target, MW},
\end{equation}
where $f_{\rm detect}$ is the fraction of targets in the instance that were detectable and $N_{\rm target, MW}$ is the total number of targets that have been formed in the Milky Way's history. We can find this total in two steps: (1) find the average number of targets formed per star forming mass (2) find the total star forming mass that has existed in the Milky Way's history.

\subsection{Average target formation rate}
Since double compact object formation is strongly metallicity dependent, we can find the average rate as the integral over metallicity
\begin{equation}\label{eq:norm_avg_target_formation}
    \avg{ \mathcal{R}_{\rm target} } = \int_{Z_{\rm min}}^{Z_{\rm max}} p_{Z} \mathcal{R}_{\rm target, Z} \dd{Z},
\end{equation}
where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ \citep{Frankel+2018} and $\mathcal{R}_{\rm target, Z}$ is defined as the number of targets formed per star forming mass. 
\begin{equation}
    \mathcal{R}_{\rm target, Z} =  N_{\rm target, Z} / M_{\rm SF, Z}.
\end{equation}
The number of targets in our sample at a metallicity $Z$ can be written simply as the sum of the targets' weights:
\begin{equation}
    N_{\rm target, Z} = \sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i},
\end{equation}
where $w_i$ is the STROOPWAFEL weight assigned to a binary, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise 0. The total star forming mass at a metallicity $Z$ can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass that COMPAS samples from given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}). The cuts applied to the distributions mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass is sampled from.

\subsection{Total star forming mass in the Milky Way}
It is important to distinguish between the \textit{total} star forming mass in the Milky Way and the \textit{current} star forming mass in the Milky Way. Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass. \citet{Licquia&Newman2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \Msun$. This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs. We can write that the total star forming mass that has \textit{ever} existed in the Milky Way is
\begin{equation}\label{eq:m_SF_MW}
    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \Msun \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
\end{equation}
where $\avg{m}_{\rm SF, total}$ is the average star forming mass over the history of the Milky Way and $\avg{m}_{\rm SF, today}$ is the average star forming mass of the mass remaining today. The former is defined as
\begin{equation}
    \avg{m}_{\rm SF, total} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(t) \int_{0.01}^{200} \zeta(m)\ m \dd{m} \dd{t},
\end{equation}
where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}. The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
\begin{equation}
    \avg{m}_{\rm SF, today} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.08}^{200} \zeta(m)\ m_{\rm today}(m, \avg{Z}_\tau, \tau) \dd{m} \dd{\tau},
\end{equation}
where $m_{\rm today}(m, Z, \tau)$ is the mass of a star that was formed $\tau$ years ago at a metallicity $Z$. We calculate this by interpolating a grid of single stars in COMPAS over different masses and metallicities and seeing what final mass they get using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings. We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ main sequence lifetime of the star has passed, otherwise we just use the initial mass. Since we don't know the exact metallicity of each star we use the average metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}. If we now evaluate Equation \ref{eq:m_SF_MW}, we find the that total star forming mass that ever existed in the Milky Way is
\begin{equation}
    M_{\rm SF, MW} = 6.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = 9.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}},
\end{equation}
an increase of approximately 50\% from the value still in stars today.

\subsection{Normalisation summary}
We can plug Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
\begin{equation}
    N_{\rm detect} = 9.1 \times 10^{10} \unit{M_{\odot}} \cdot f_{\rm detect} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
\end{equation}

\end{document}

### 2021-03-20 simulation/output/formation_channels.py
add formation channels code

@@ -1,0 +1,148 @@
+import numpy as np
+from collections import defaultdict
+
+import sys
+sys.path.append("../src/")
+from compas_processing import get_COMPAS_vars
+
+
+def find_mass_transfer_moments(seeds):
+    """Create an array with each moment of mass transfer labelled. This is done
+    such that the first moment is labelled '1' at its index and second as '2'
+    etc.
+
+    Parameters
+    ----------
+    seeds : `int/array`
+        List of seeds that correspond to a binary and each instance
+        corresponds to a moment of mass transfer.
+
+    Returns
+    -------
+    moments : `int/array`
+        List same shape as ``seeds`` with each index labelled with which moment
+        of mass transfer that the binary is going through.
+    """
+    # start a counter that defaults to 0
+    counter = defaultdict(int)
+    moments = np.zeros_like(seeds).astype(int)
+
+    # loop over every seed
+    for i in range(len(seeds)):
+        # increment seed's count
+        counter[seeds[i]] += 1
+
+        # label index with mass transfer moment (1 is first)
+        moments[i] = counter[seeds[i]]
+    return moments
+
+
+def identify_formation_channels(seeds, file):
+    """Identify the formation channel that produced each seed. We consider 5
+    main channels: classic, only stable, single core CEE, double core CEE and
+    other. We define the channels as follows (the numbers are what is put in
+    the ``channels`` output):
+
+    Classic (1) -- In the first mass transfer, the primary overflows its
+    Roche lobe stably and has a clear core-envelope structure (HG - TPAGB)
+    whilst the secondary star is still on the main sequence. In the second mass
+    transfer, the secondary overflows its Roche Lobe before stripping occurs
+    and leads to a common envelope event.
+
+    Only stable (2) -- As Classic, but the second mass transfer is stable.
+
+    Single core CEE (3) -- In the first mass transfer, the primary overflows
+    its Roche lobe unstably (leading to a CEE) and has a clear core-envelope
+    structure (FGB - TPAGB) whilst the secondary star is still on the main
+    sequence.
+
+    Double core CEE (4) -- In the first mass transfer, the primary overflows
+    its Roche lobe unstably (leading to a CEE) and both the primary and
+    secondary have a clear core-envelope structure (FGB - TPAGB).
+
+    Other (5) -- Anything else
+
+    Parameters
+    ----------
+    seeds : `int/array`
+        List of seeds that each correspond to a binary (this should be a subset
+        of the seeds in the COMPAS output file)
+    file : `hdf5 File`
[…]

### 2021-03-20 simulation/output/combine_output.py
make combine output also find formation channels

@@ -5,15 +5,18 @@ from os.path import isfile
 import sys
 sys.path.append("../src/")
 
+from formation_channels import identify_formation_channels
 from variations import variations
 
 dt = np.dtype(float)
 dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
          ("tau", dt), ("dist", dt), ("Z", dt), ("snr", dt), ("weight", dt),
-         ("seed", dt)]
+         ("seed", dt), ("channel", dt)]
 
 runs = 50
+
+floor_path = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
 
 # loop over all binary types and physics variations
 for bt in ["BHBH", "BHNS", "NSNS"]:
@@ -48,13 +51,21 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
         if len(missing) != runs:
             # let the user know which ones are currently missing
             print(v, len(missing), missing)
+            
+            # work out the formation channels
+            floor_file = floor_path \
+                + "{}/COMPASOutputReduced.h5".format(variations[v]["file"])
+            with h5.File(floor_file, "r") as floor:
+                channels = identify_formation_channels(full_data["seed"],
+                                                       floor)
 
-            # write the rest of them to a single file
+            # write the rest of the files to a single file
             fname = "../data/{}_{}_all.h5".format(bt, variations[v]["file"])
             with h5.File(fname, "w") as file:
                 file.create_dataset("simulation", (np.sum(n_ten_year),),
                                     dtype=dtype)
                 file["simulation"][...] = full_data
+                file["simulation"]["channel"][...] = channels
                 file["simulation"].attrs["n_ten_year"] = n_ten_year
         # otherwise make sure that the user knows no data is present
         else:

### 2021-03-20 simulation/output/combine_output.py
fixes to writing of channels

@@ -12,7 +12,7 @@ dt = np.dtype(float)
 dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
          ("tau", dt), ("dist", dt), ("Z", dt), ("snr", dt), ("weight", dt),
-         ("seed", dt), ("channel", dt)]
+         ("seed", dt), ("channel", np.dtype(int))]
 
 runs = 50
 
@@ -51,10 +51,13 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
         if len(missing) != runs:
             # let the user know which ones are currently missing
             print(v, len(missing), missing)
-            
+
             # work out the formation channels
+            model = variations[v]["file"]
+            if model == "optimistic":
+                model = "fiducial"
             floor_file = floor_path \
-                + "{}/COMPASOutputReduced.h5".format(variations[v]["file"])
+                + "{}/COMPASOutputReduced.h5".format(model)
             with h5.File(floor_file, "r") as floor:
                 channels = identify_formation_channels(full_data["seed"],
                                                        floor)
@@ -64,9 +67,11 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
             with h5.File(fname, "w") as file:
                 file.create_dataset("simulation", (np.sum(n_ten_year),),
                                     dtype=dtype)
-                file["simulation"][...] = full_data
-                file["simulation"]["channel"][...] = channels
+                for col, _ in dtype:
+                    file["simulation"][col] = full_data[col] \
+                        if col != "channel" else channels
                 file["simulation"].attrs["n_ten_year"] = n_ten_year
+
         # otherwise make sure that the user knows no data is present
         else:
             print("No data found for {}".format(variations[v]["long"]))

### 2021-03-20 paper/tex/paper.tex
update plots
test overleaf sync

@@
     \centering
-    \includegraphics[width=\textwidth]{dco_detections_variations.pdf}
-    \caption{The number of expected detections in a four year LISA mission for different DCO types and model variations.
+    \includegraphics[width=\textwidth]{dco_detections.pdf}
+    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
 Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
-Each model is described in further detail in Table\,\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section\,\ref{sec:fiducial_physics}}
+The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
     \label{fig:model_variation_detections}

### 2021-03-20 paper/tex/paper.tex
overhaul references, add previous studies table

@@
 \usepackage{multirow}
-\usepackage{xspace} %this package handles when to use a whitespace in math symbols
-\usepackage{natbib} %this package can be used for creating an automated bibliography.
+\usepackage{xspace}
+\usepackage{natbib}
 
@@
 \usepackage[hang,flushmargin]{footmisc}
-
-%Latex allows you to define abbreviations. \newcommand{.. here comes the short notation ...}{ ... here comes the full latex command... small change}
 
@@
 \makeatother
-
-% Define symbols for Rsun and Msun, Lsun and Teff ensuring proper formatting
-\newcommand{\Rsun}{\ensuremath{\,\mathrm{R_\odot}}\xspace} % Solar radius symbol
-\newcommand{\Msun}{\ensuremath{\,\mathrm{M_\odot}}\xspace} % Solar mass symbol
-\newcommand{\Lsun}{\ensuremath{\,\mathrm{M_\odot}}\xspace} % Solar luminosity symbol
-\newcommand{\Teff}{\ensuremath{\,\mathrm{T_{\rm eff}}}\xspace} % Effective temperature symbol
-\newcommand{\Myr}{\ensuremath{\,\mathrm{Myr}}\xspace} % symbol for Mega year
-\newcommand{\Gyr}{\ensuremath{\,\mathrm{Gyr}}\xspace} % symbol for Gyr
 
@@
 \begin{abstract}
-{The Laser Inteferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves.
+{The Laser Interferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves.
 Detections of double compact objects with LISA may help to constrain uncertainties in binary evolution and understand the prevalence of electromagnetic counterparts to gravitational wave events.
@@
 
-Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{LIGO_2016_BBHinfirstRun}, there have been 50 gravitational wave events detected by LIGO \citep{LIGO_GWTC1, LIGO_GWTC2}.
+Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, there have been 50 gravitational wave events detected by LIGO \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
 The investigation of double compact object (DCO) population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different DCO types.
@@
 One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS).
-Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{LIGO_GW190425, LIGO_GW190814}.
+Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
 
@@
 
+The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
+Several focus only on the detection of the more numerous population of double white dwarf population
+
 The detection of double compact objects with LISA has been investigated in many recent studies.
@@
 \citet{Lamberts+2018, Lamberts+2019} instead use a hydrodynamic simulation from the FIRE project \citep{Hopkins+2014} to produce predictions for double black hole binaries (BHBH) and WDWD.
-Closer to this study, \citet{Breivik+2019} uses the COSMIC population synthesis code to predict detection rates for all double compact objects and \citet{Lau+2020} uses the same population synthesis code as this study, COMPAS, and focusses on double neutron star binaries (NSNS).
+Closer to this study, \citet{Breivik+2020} uses the COSMIC population synthesis code to predict detection rates for all double compact objects and \citet{Lau+2020} uses the same population synthesis code as this study, COMPAS, and focusses on double neutron star binaries (NSNS).
 
@@
 Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$.
+The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$.
 The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
@@
 We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star.
-We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik1924, Abt1983}.
+We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
 We assume that all binaries are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, de-Mink+2015}.
+Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
 
@@
 
-\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink1984} and \citet{de-Kool1990}.
+\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
 We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
 For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam&Sandquist2000, Ivanova+2004}.
-This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007a}.
+We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004}.
+This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
 We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections.
@@
 
-We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto1984, Nomoto1987, Ivanova+2008}.
+We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
 We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
@@
 We assume that kicks are isotropic in the frame of the collapsing star.
-The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996_maxNS, Fryer+2015, Margalit&Metzger2017}.
-% removed Lawrence+2015 Alsing+2018
+The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017}.
 We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
@@
         \modRapid & Fryer rapid SN remnant mass prescription \\
-        \modNSLow & Maximum NS mass is fixed to $2\Msun$ \\
-        \modNSHigh & Maximum NS mass is fixed to $3\Msun$ \\
+        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
+        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
         \modNoPISN & PISN and pulsational-PISN not implemented \\
@@
 The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way.
-They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{APOGEE} and Gaia \citep{Gaia-Collaboration+2016}.
+They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}.
 The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy.
@@
 \end{equation}
-Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan2011},
+Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
 \begin{equation}\label{eq:galaxy_z}
@@
 where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$.
-Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{MAKEME}.
+Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.
 
@@
 for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
-Figure~\ref{fig:galaxy_metallicity} shows an example of a random Milky Way instance created with these distributions.
+Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
 This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.
@@
     \includegraphics[width=\textwidth]{galaxy_diagram.png}
-    \caption{A schematic showing how we create a mock Mily Way disc.
-On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan2011}.
+    \caption{A schematic showing how we create a mock Milky Way disc.
+On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan+2011}.
 On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points.
@@
 Each binary is likely to move from its birth orbit.
-Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood&Binney2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.
+Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw+1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.
 
@@
 We find the eccentricity of the binary at the start of the LISA mission, $e_{\rm LISA}$, by numerically integrating its time derivative \citep[][Eq.
-5.13]{Peters1964} given the initial conditions.
+5.13]{Peters+1964} given the initial conditions.
 This additionally can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq.
-5.11]{Peters1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.
+5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.
 
@@
 
-We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2019, Korol+2020}.
-The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn&Thorne2000}
+We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
+The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn+2000}
 \begin{equation}\label{eq:snr}
@@
 \end{equation}
-\citep[e.g.][]{Barack&Cutler2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters1963} and $\mathcal{M}_c$ is the chirp mass, defined as
+\citep[e.g.][]{Barack+2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters+1963} and $\mathcal{M}_c$ is the chirp mass, defined as
 \begin{equation}\label{eq:chirp_mass}
@@
 \end{equation}
-compared to a circular binary with the same semi-major axis \citep[][Eq.\,17]{Peters1963}.
+compared to a circular binary with the same semi-major axis \citep[][Eq.\,17]{Peters+1963}.
 This means that eccentric binaries will not only inspiral faster, but also produce gravitational waves with stronger strain amplitudes (when summed over all harmonics).
@@
 Secondly, eccentric binaries will emit gravitational waves at many harmonic frequencies (unlike circular binaries, which only emit at twice the orbital frequency).
-This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters1963}.
+This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo{Add text about detection rates}
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{dco_detections.pdf}
+    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
+Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
+The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
+    \label{fig:detection_rates}
+\end{figure*}
+
 \subsection{Results for fiducial model}\label{sec:fiducial_distributions}
@@
 
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
-The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
-    \label{fig:model_variation_detections}
-\end{figure*}
-
 \newcolumntype{S}{>{\centering}p{0.75cm}}
@@
 They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:model_variation_detections}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
+However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
 
@@
 
-\citet{Breivik+2019} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2019} assumes the optimistic CE scenario.
+\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
+Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
 Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively.
-The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2019} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:model_variation_detections}, model \modCaseBB{}) .
+The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2020} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, model \modCaseBB{}) .
 The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
@@
 \software{COMPAS (version 02.12.00) \url{http://github.com/TeamCOMPAS/COMPAS}.
-\citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}, \texttt{Python} available from \url{python.org}, matplotlib \citep{matplotlib},  \texttt{NumPy} \citep{numpy},
-Astropy \citep[\url{http://www.astropy.org}][]{Astropy-Collaboration+2013,Astropy-Collaboration+2018}.}
+\citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}, \texttt{Python} available from \url{python.org}, matplotlib \citep{Hunter+2007},  \texttt{NumPy} \citep{vanderWalt+2011},
+Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.}
 
@@
 \bibliographystyle{aasjournal}
-\bibliography{references, selma_huge_bibs}
+\bibliography{references}
 
@@
 As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important.
-We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters1963}
+We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
 \begin{equation}\label{eq:g(n,e)}
@@
 Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary.
-This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters1963}
+This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
 \begin{equation}\label{eq:eccentricity_enhancement_factor}
@@
 \subsection{Characteristic Strain}
-The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack&Cutler2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
+The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
 \begin{equation}\label{eq:char_strain_dedf}
@@
 The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq.
-19]{Peters1963}
+19]{Peters+1963}
 \begin{equation}\label{eq:edot_peters}
@@
 \end{align}
-The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters1964}
+The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
 \begin{equation}\label{eq:dadt}
@@
 The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles.
-This is explained in \citet{Finn&Thorne2000} and in further detail in \citet{Moore+2015}.
+This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}.
 The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain.
@@
 
-Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn&Thorne2000}
+Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
 \begin{equation}\label{eq:strain-to-charstrain}
@@
 Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass.
-\citet{Licquia&Newman2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \Msun$.
+\citet{Licquia+2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$.
 This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs.
@@
 \begin{equation}\label{eq:m_SF_MW}
-    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \Msun \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
+    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
 \end{equation}
@@
 \end{equation}
-where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}.
+where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}.
 The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
@@
 
+\section{Extra figures}
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[height=\textheight]{previous_studies.png}
+    \caption{A table of previous studies of a similar nature to this work}
+    \label{fig:previous_studies}
+\end{figure*}
+
 \end{document}

### 2021-03-21 paper/tex/paper.tex
create new figures with updated sims

@@
 The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
-Several focus only on the detection of the more numerous population of double white dwarf population
-
-The detection of double compact objects with LISA has been investigated in many recent studies.
-\citet{Korol+2017, Korol+2020} use the binary population synthesis code SeBa to focus on predictions for double white dwarf binaries (WDWD).
-\citet{Lamberts+2018, Lamberts+2019} instead use a hydrodynamic simulation from the FIRE project \citep{Hopkins+2014} to produce predictions for double black hole binaries (BHBH) and WDWD.
-Closer to this study, \citet{Breivik+2020} uses the COSMIC population synthesis code to predict detection rates for all double compact objects and \citet{Lau+2020} uses the same population synthesis code as this study, COMPAS, and focusses on double neutron star binaries (NSNS).
+Several works focus only the more numerous population of double white dwarf population \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}, whilst others investigate the more massive BHBH, BHNS and NSNS binaries \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
+Our work improves upon previous studies by: exploring the effect of varying binary physics assumptions with 15 models, using a model for the Milky Way that is dependent on the chemical enrichment history and providing a full treatment of the eccentricity of detectable sources.
+We compare these studies with each other and our work in more detail in Section.~\ref{sec:compare_studies} and provide a summary in Fig.~\ref{fig:previous_studies}.
 
@@
 
-\subsection{Results for fiducial model}\label{sec:fiducial_distributions}
-We find that, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 12 NSNS binaries.
-Increasing the LISA mission length to ten years changes the number of detections to 41, 45 and 19 respectively.
-We can note that each shows an increase of approximately $\sqrt{10 / 4} \approx 1.6$ as expected since $\rho \propto \sqrt{T_{\rm obs}}$.
+Now talk about where they are on the sensitivity curve
 
@@
 \end{figure*}
+
+\subsection{Results for fiducial model}\label{sec:fiducial_distributions}
+We find that, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 12 NSNS binaries.
+Increasing the LISA mission length to ten years changes the number of detections to 41, 45 and 19 respectively.
+We can note that each shows an increase of approximately $\sqrt{10 / 4} \approx 1.6$ as expected since $\rho \propto \sqrt{T_{\rm obs}}$.
 
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[htbp]
     \centering
-    \includegraphics[width=\textwidth]{fiducial_pdf_distributions.pdf}
+    \includegraphics[width=\textwidth]{distribution_grid.pdf}
     \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model.
@@
 
-\subsection{Comparison with other studies}
+\subsection{Comparison with other studies}\label{sec:compare_studies}
 \citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
@@
     \centering
-    \includegraphics[height=\textheight]{previous_studies.png}
+    \includegraphics[height=0.95\textheight]{previous_studies.png}
     \caption{A table of previous studies of a similar nature to this work}

### 2021-03-21 paper/tex/paper.tex
started work on detection rate trends

@@
 
-\todo{Add text about detection rates}
+In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation.
+We find that on average, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 11 NSNS binaries.
+Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.
+The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
+Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
+In contrast, the NSNS and BHNS rates are very sensitive to changes in binary physics assumptions.
+Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
+
+Here is some attempted reasoning about the trends:
+
+\textbf{BHBH:} The major standout for the BHBHs is the optimistic.
+In this case Hertzsprung gap donors are allowed to survive CE and this is because many BHs are formed in this way rather than any effect on detectability.
+Can also comment on lower(higher) max NS mass being good(bad).
+Kicks same as BHNSs but less pronounced.
+
+\textbf{BHNS:} Whole bunch of trends here.
+The decrease with increasing $\beta$ seems to be due to fewer BHNSs surviving CE events (since envelope is harder to eject).
+Floor explains this in her paper and also references Kruckow.
+optimistic higher same as BHBH.
+Rapid higher because BHBHs become BHNSs instead.
+Maximum neutron star masses affect things because: lower means more things become BH instead of NS hence fewer BHNS and vice versa.
+PISN doesn't affect this mass range.
+Lower kicks means fewer disruptions.
+No BH kick lower again because NS kick is main factor at that point.
+\todo{this leaves E, F, G todo}
+
+\textbf{NSNS:} \todo{Why are B, C, D opposite?}.
+E is low because that's the main NSNS formation channel.
+CE follows nice trend (see Floor's about CE channels).
+Optimistic slightly up because duh.
+\todo{weirdly basically no change in rapid and max NS masses}.
+Lower kicks great as usual.
+No BH kicks no effect duh.
 
@@
 
+\begin{table*}[htb]
+    \centering
+    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
+    \begin{tabular}{c|lll|lll}
+        \hline
+        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
+         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+        \hline
+        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
+        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
+        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
+        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
+        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
+        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
+        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
+        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
+        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
+        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
+        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
+        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
+        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
+        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
+        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
+        \hline
+    \end{tabular}
+    \label{tab:detection_rates}
+\end{table*}
+
 Now talk about where they are on the sensitivity curve
 
-We illustrate the distribution of detectable DCOs lie on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-The shape of the distributions are bounded by the edge of the Milky Way and the infrequency of nearby DCOs.
+We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
+The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
 We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
@@
     \includegraphics[width=\textwidth]{dcos_on_sc.png}
-    \caption{\tom{This plot needs to be updated after SNR fixes}.
-Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
+    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
 We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
@@
 
-\subsection{Results for fiducial model}\label{sec:fiducial_distributions}
-We find that, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 12 NSNS binaries.
-Increasing the LISA mission length to ten years changes the number of detections to 41, 45 and 19 respectively.
-We can note that each shows an increase of approximately $\sqrt{10 / 4} \approx 1.6$ as expected since $\rho \propto \sqrt{T_{\rm obs}}$.
+\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}
 
@@
 \subsection{Model variations}
-
-\newcolumntype{S}{>{\centering}p{0.75cm}}
-\newcolumntype{Z}{>{\centering\arraybackslash}p{0.75cm}}
-\begin{table*}[htb]
-    \centering
-    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
-    \begin{tabular}{c|lll|lll}
-        \hline
-        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
-         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-        \hline
-        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
-        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
-        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
-        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
-        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
-        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
-        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
-        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
-        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
-        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
-        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
-        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
-        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
-        \hline
-    \end{tabular}
-    \label{tab:detection_rates}
-\end{table*}
 

### 2021-03-22 paper/tex/paper.tex
add text about detection rate trends

@@
 
-The magnitude of the systemic kicks are typically small compared to the intital circular velocity of a binary at each Galactocentric radius.
+The magnitude of the systemic kicks are typically small compared to the initial circular velocity of a binary at each Galactocentric radius.
 Therefore, kicks will not significantly alter the overall distribution of their positions.
@@
 
+\subsection{Detection Rates}
 In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation.
@@
 Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-In contrast, the NSNS and BHNS rates are very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-
-Here is some attempted reasoning about the trends:
-
-\textbf{BHBH:} The major standout for the BHBHs is the optimistic.
-In this case Hertzsprung gap donors are allowed to survive CE and this is because many BHs are formed in this way rather than any effect on detectability.
-Can also comment on lower(higher) max NS mass being good(bad).
-Kicks same as BHNSs but less pronounced.
-
-\textbf{BHNS:} Whole bunch of trends here.
-The decrease with increasing $\beta$ seems to be due to fewer BHNSs surviving CE events (since envelope is harder to eject).
-Floor explains this in her paper and also references Kruckow.
-optimistic higher same as BHBH.
-Rapid higher because BHBHs become BHNSs instead.
-Maximum neutron star masses affect things because: lower means more things become BH instead of NS hence fewer BHNS and vice versa.
-PISN doesn't affect this mass range.
-Lower kicks means fewer disruptions.
-No BH kick lower again because NS kick is main factor at that point.
-\todo{this leaves E, F, G todo}
-
-\textbf{NSNS:} \todo{Why are B, C, D opposite?}.
-E is low because that's the main NSNS formation channel.
-CE follows nice trend (see Floor's about CE channels).
-Optimistic slightly up because duh.
-\todo{weirdly basically no change in rapid and max NS masses}.
-Lower kicks great as usual.
-No BH kicks no effect duh.
 
@@
 \end{figure*}
+
+\subsubsection{BHBH detection rate trends}
+The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
+Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
+
+The exception to this statement is \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
+A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
+Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
+\tom{Can also mention slight trends in max NS mass and kicks that are explain in next paragraph}
+
+\subsubsection{BHNS detection rate trends}
+In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
+Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
+There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
+
+As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
+This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
+However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
+For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
+\todo{Why isn't the opposite true for model \modAlphaHigh{}?
+It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
+
+Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
+This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
+For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
+This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
+
+The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed.
+For the same reason, increasing the maximum neutron star mass increases the detection rate and the inverse is true when it is decreased (in models \modNSLow{} and \modNSHigh{}).
+
+Finally, models \modSigLow{}-\modNoBH{} show increased detection rates as lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
+Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
+The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
+
+\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
+\textbf{NSNS:} \todo{Why are B, C, D opposite?}.
+E is low because that's the main NSNS formation channel.
+CE follows nice trend (see Floor's about CE channels).
+Optimistic slightly up because duh.
+\todo{weirdly basically no change in rapid and max NS masses}.
+Lower kicks great as usual.
+No BH kicks no effect duh.
 
@@
 The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
-This may seem counterintuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
+This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
 However, these stronger kicks often instead result in disrupted or too-wide binaries.
@@
 
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{fiducial_cdf_distributions.pdf}
-    \caption{Cumulative distributions of observable parameters for binaries that are detectable in a 4 year LISA mission.
-Shaded areas indicate regimes in which no measurement can be made.
-Dotted lines on the angular resolution distribution show the field of view for various telescopes that could perform EM counterpart observations.}
-    \label{fig:fiducial_cdf_distributions}
-\end{figure*}
-
 \subsection{Model variations}
@@
     \item Only a single disc for the Milky Way
-    \item Stationary approximation? But I'm pretty sure that is fine
 \end{itemize}

### 2021-03-24 paper/tex/paper.tex
add some supplementary figures
add NSNS trends and variation figures

@@
 \subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
-\textbf{NSNS:} \todo{Why are B, C, D opposite?}.
-E is low because that's the main NSNS formation channel.
-CE follows nice trend (see Floor's about CE channels).
-Optimistic slightly up because duh.
+
+\todo{understand the $\beta$ trends}.
+There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
+This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
+As a result the total number of detections decreases, however interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).
+
+\todo{come back to CE ones once we understand the BHNS ones}.
 \todo{weirdly basically no change in rapid and max NS masses}.
-Lower kicks great as usual.
-No BH kicks no effect duh.
+As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the BH kick (model \modNoBH{}) of course has no effect on the NSNS population.
 
@@
 
-Now talk about where they are on the sensitivity curve
+\subsection{Distribution on the sensitivity curve}
 
@@
 
-\section{Extra figures}
+\section{Supplementary figures}
+
+\subsection{Physics variation cumulative distributions}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
+    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation.
+In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$.
+We additionally show the other physics variations in the background in light grey.}
+    \label{fig:variations_cdf_1_3}
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
+    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
+    \label{fig:variations_cdf_4_6}
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
+    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
+    \label{fig:variations_cdf_7_10}
+\end{figure*}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
+    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
+    \label{fig:variations_cdf_11_14}
+\end{figure*}
+
+\subsection{Detection rates}
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{dco_detections_fractions.pdf}
+    \caption{As Figure~\ref{fig:detection_rates} except only showing the detectable \textit{fraction}.}
+    \label{fig:detection_fractions}
+\end{figure*}
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{dco_merging.pdf}
+    \caption{The total number of merging DCOs in the Milky Way. When multiplied by Figure~\ref{fig:detection_fractions} this gives Figure~\ref{fig:detection_rates}.}
+    \label{fig:total_merging_dcos}
+\end{figure*}
+
+\subsection{Miscellaneous}
 

### 2021-03-26 simulation/output/combine_output.py
make combine output do formation channels

@@ -7,12 +7,16 @@ sys.path.append("../src/")
 
 from formation_channels import identify_formation_channels
 from variations import variations
+import time
 
 dt = np.dtype(float)
 dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
          ("tau", dt), ("dist", dt), ("Z", dt), ("snr", dt), ("weight", dt),
-         ("seed", dt), ("channel", np.dtype(int))]
+         ("seed", dt), ("channel", np.dtype(int)), ("m_1_ZAMS", dt),
+         ("m_2_ZAMS", dt), ("MT1_case", np.dtype(int)),
+         ("MT2_case", np.dtype(int)), ("a_ZAMS", dt), ("a_pre_SN2", dt),
+         ("kick_1", dt), ("kick_2", dt)]
 
 runs = 50
 
@@ -46,7 +50,7 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                         full_data[prev_len:] = add_data
             else:
                 missing.append(i)
-
+                
         # as long as there is at least one file
         if len(missing) != runs:
             # let the user know which ones are currently missing
@@ -61,17 +65,37 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
             with h5.File(floor_file, "r") as floor:
                 channels = identify_formation_channels(full_data["seed"],
                                                        floor)
+                
+                dco_seeds = floor["doubleCompactObjects"]["seed"][...].squeeze()
+    
+                index = np.argsort(dco_seeds)
+                sorted_dco_seeds = dco_seeds[index]
+                sorted_index = np.searchsorted(sorted_dco_seeds, full_data["seed"])
+
+                seeds_index = np.take(index, sorted_index, mode="clip")
+                supp_data = {
+                    "m_1_ZAMS": floor["doubleCompactObjects"]["M1ZAMS"][...].squeeze()[seeds_index],
+                    "m_2_ZAMS": floor["doubleCompactObjects"]["M2ZAMS"][...].squeeze()[seeds_index],
+                    "MT1_case": floor["doubleCompactObjects"]["PrimaryMTCase"][...].squeeze()[seeds_index],
+                    "MT2_case": floor["doubleCompactObjects"]["SecondaryMTCase"][...].squeeze()[seeds_index],
[…]

### 2021-03-26 simulation/src/simulate_DCO_detections.py
store total weight in simulation

@@ -105,6 +105,7 @@ def main():
     to_file = np.zeros(shape=(loops * MAX_HIGH,), dtype=dtype)
 
     n_ten_year_list = np.zeros(loops)
+    total_MW_weight = np.zeros(loops)
     tot_ten = 0
     for milky_way in range(loops):
         # draw position parameters from Frankel Model
@@ -157,6 +158,9 @@ def main():
             compas_a_DCO[binaries], compas_e_DCO[binaries],\
             compas_t_evol[binaries], compas_weights[binaries],\
             compas_Z[binaries], compas_seeds[binaries]
+
+        # store the total weight of full population (for normalisation)
+        total_MW_weight[milky_way] = np.sum(w)
 
         # work out which binaries are still inspiralling
         t_merge = lw.evol.get_t_merge_ecc(ecc_i=e_DCO, a_i=a_DCO,
@@ -215,6 +219,7 @@ def main():
         file.create_dataset("simulation", (tot_ten,), dtype=dtype)
         file["simulation"][...] = to_file
         file["simulation"].attrs["n_ten_year"] = n_ten_year_list
+        file["simulation"].attrs["total_MW_weight"] = total_MW_weight
 
 
 if __name__ == "__main__":

### 2021-04-08 paper/tex/paper.tex
refactor latex to use separate files for sections

--- 2021-03-21 paper/tex/paper.tex
@@
 
-\begin{abstract}
-{The Laser Interferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves.
-Detections of double compact objects with LISA may help to constrain uncertainties in binary evolution and understand the prevalence of electromagnetic counterparts to gravitational wave events.
-We estimate the number of Galactic DCOs that will be detected by LISA using a sample generated with the rapid population synthesis code COMPAS and a model of the Milky Way that includes not only the radial birth profiles but also the star formation and enrichment histories.
-We explore the effects of varying 15 physical assumptions that focus on key uncertainties in our understanding of mass transfer, common envelope and supernova physics.
-For our fiducial model, we find that over a 4 year mission, LISA will detect 26 BHBHs, 27 BHNSs and 12 NSNSs.
-These detection rates increase to 41, 45 and 19 respectively for a 10 year mission length.
-We present the distributions of the characteristics of the detectable binaries and explore how our different models affect them.
-We also discuss how well we can distinguish between different DCO types and methods for doing so.}
+\begin{abstract}{
+    \input{sections/abstract.tex}
+}
 \end{abstract}
@@
 
-Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, there have been 50 gravitational wave events detected by LIGO \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
-The investigation of double compact object (DCO) population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different DCO types.
-
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) provides an exciting new lens through which to view the realm of gravitational waves.
-LISA will observe binaries at lower orbital frequencies than LIGO ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger.
-This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which allows for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}.
-In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Vigna-Gomez+2018}, differentiate between formation channels and distinguish between DCO types.
-
-One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS).
-Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
-
-Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
-Collating a sample of BHNS binaries will allow us to better understand whether there are electromagnetic counterparts to their gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
-Moreover, if the neutron star is observable (such as a pulsar), a BHNS would be ideal for measuring the Hubble constant \citep[e.g.][]{Feeney+2020} and the neutron star equation of state.
-A detection with LISA would allow these various signals to be measured for years before the merger and give observers ample time to prepare for the merger itself.
-
-The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
-Several works focus only the more numerous population of double white dwarf population \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}, whilst others investigate the more massive BHBH, BHNS and NSNS binaries \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
-Our work improves upon previous studies by: exploring the effect of varying binary physics assumptions with 15 models, using a model for the Milky Way that is dependent on the chemical enrichment history and providing a full treatment of the eccentricity of detectable sources.
-We compare these studies with each other and our work in more detail in Section.~\ref{sec:compare_studies} and provide a summary in Fig.~\ref{fig:previous_studies}.
-
-In this paper, we present predictions for the detection rate and distribution of binary characteristics (masses, frequency, eccentricity, distance, merger time) of BHNS, BHBH and NSNS binaries formed through isolated binary evolution in the Milky Way using binaries synthesised with the \href{https://compas.science}{COMPAS} rapid population synthesis code \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019} in tandem with the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019}.
-Additionally, we use a model of the Milky Way that not only includes the radial birth profiles but also the star formation and enrichment history.
-We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results.
-In this study we consider three main questions: (1) how many of each type of DCO will LISA detect?
-(2) can we distinguish between different DCOs with LISA?
-(3) can we use detections in LISA to constrain uncertainties in binary evolution?
-
-In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
-In Section~\ref{sec:resultsI}, we explore the detection of double compact objects with LISA analytically.
-In Section~\ref{sec:resultsII}, we present our main results for each type of DCO and variation of physical assumptions.
-In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.
+\input{sections/introduction.tex}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Binary population synthesis}\label{sec:COMPAS_explained}
 
-We use a population of binaries synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
-COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}.
-Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using the single star evolution fitting formulae from \citet{Hurley+2000} to the models of \citet{Pols+1998}.
-In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
-This algorithm increases the prevalence of target DCOs (BHBH, BHNS and NSNS binaries in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
-
-\subsubsection{Population Overview}
-
-The population of double compact objects used in this study was synthesised by \citet{Broekgaarden+2021}.
-One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
-This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.
-
-\subsubsection{Initial Conditions}
-
-Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
-with][]{Sana+2012}.
-We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star.
-We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
-We assume that all binaries are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
-
-For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
-\begin{equation}
-    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
-\end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation and gravitational-wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL.
-We sample from these sets of parameters when creating synthetic galaxies.
-
-\subsubsection{Physical assumptions in fiducial model}\label{sec:fiducial_physics}
-In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see Section 2.1.2 and Table 1 of \citet{Broekgaarden+2021}.
-
-\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
-The mass transfer efficiency, $\beta = \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
-We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
-The maximum accretion rate for double compact objects is limited to the Eddington accretion rate.
-If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star, thus varying $\beta$ \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
-We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.
-
-\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
-We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
-For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004}.
-This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
-We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections.
-
-\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
-For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
-The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
-We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
-
-We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
-We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
-For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ as in \citet{Pfahl+2002} and \citet{Podsiadlowski+2004}.
-
-We assume that stars that undergo case BB mass transfer experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
-For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).
-
-Stars with helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
-We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
-
-We assume that kicks are isotropic in the frame of the collapsing star.
-The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017}.
-We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
-
-\subsubsection{Physical assumptions in other models} \label{sec:variation_assumptions}
-In addition to our fiducial model, we explore 14 other models which change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions.
-Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.
-
-Models \modRangeMT{} focus on changes to the mass transfer physics.
-We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
-In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.
-
-Models \modRangeCE{} focus on altering the common envelope physics.
-We change the common envelope efficiency parameter in models \modAlphaLow{} and \modAlphaHigh{} to $\alpha = 0.5$ and $2.0$ respectively.
-In model \modOpt, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
-
-Finally, models \modRangeSN{} make changes related to our assumptions about supernova physics.
-Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
-We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses.
-Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae.
-In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
-Finally, model \modNoBH{} removes the natal kick for all black holes.
-
-\begin{table}[htb]
-    \centering
-    \begin{tabular}{cl}
-        \hline \hline
-        Model & Physics Variation \\
-        \hline \hline
-        \modFid & -- \\
-        \hline
-        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
-        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
-        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
-        \modCaseBB & Case BB mass transfer is always unstable \\
-        \hline
-        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
-        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
-        \modOpt & HG donor stars initiating a CE survive CE \\
-        \hline
-        \modRapid & Fryer rapid SN remnant mass prescription \\
-        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
-        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
-        \modNoPISN & PISN and pulsational-PISN not implemented \\
-        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
-        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
-        \modNoBH & Black holes receive no natal kick \\
-        \hline \hline
-    \end{tabular}%
-    \caption{Adapted from \citet[][Table 2]{Broekgaarden+2021}, a description of the 15 binary population synthesis models used in this study.
-\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics.}
-    \label{tab:physics_variations}
-\end{table}
-
-\subsection{Galaxy Synthesis}
-
-In order to produce a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries.
-For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc.
-We do not find that adding other components would significantly alter our results.
-
-Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
-We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.
-
-\subsubsection{Milky Way disc model}
-
-For the Milky Way thin disc, we use the model from \citet{Frankel+2018}.
-The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way.
-They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}.
-The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy.
-We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.
-
-The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
-\begin{equation}\label{eq:galaxy_tau}
-    p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
-\end{equation}
-where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}.
-The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq.
-5]{Frankel+2018}
-\begin{equation}\label{eq:galaxy_R}
-    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \cdot \frac{R_0}{[R_{\rm exp}(\tau)]^2},
-\end{equation}
-where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
-\begin{equation}
-    R_{\rm exp}(\tau) = 4 \unit{kpc} \qty(1 - \alpha_{R_{\rm exp}} \qty(\frac{\tau}{8 \unit{Gyr}})),
-\end{equation}
-where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
-\begin{equation}\label{eq:galaxy_FeH}
-    \begin{split}
-        [{\rm Fe} / {\rm H}] (R, \tau) = &F_m + \nabla [{\rm Fe} / {\rm H}] R \\
-        &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
-    \end{split}
-\end{equation}
-where
-\begin{equation}
-    f(\tau) = \qty(1 - \frac{\tau}{\tau_m})^{\gamma_{[{\rm Fe} / {\rm H}]}},
-\end{equation}
-$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}.
-We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
-\begin{equation}\label{eq:galaxy_FeH_to_Z}
-    \log Z = 0.977 [{\rm Fe} / {\rm H}] + \log(Z_\odot).
-\end{equation}
-Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
-\begin{equation}\label{eq:galaxy_z}
-    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
-\end{equation}
-where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$.
-Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.
-
-\subsubsection{Combining population and galaxy synthesis}
-
-For each Milky Way instance, we randomly sample the following set of parameters
-\begin{equation}
-    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
-\end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
-Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
-This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{galaxy_diagram.png}
-    \caption{A schematic showing how we create a mock Milky Way disc.
-On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan+2011}.
-On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points.
-The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$).
-The top panel shows a side-on view and the bottom panel shows a view from above.}
-    \label{fig:galaxy_schematic}
-\end{figure*}
-
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=\columnwidth]{galaxy_metallicity.png}
-%     \caption{A random instance of the Milky Way of $10^5$ binaries, created using distributions from \citet{Frankel+2018}.
-The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$).
-The top panel shows a side-on view and the bottom panels shows a view from above.}
-%     \label{fig:galaxy_metallicity}
-% \end{figure}
-
-We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by randomly drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.
-
-Each binary is likely to move from its birth orbit.
-Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw+1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.
-
-The magnitude of the systemic kicks are typically small compared to the intital circular velocity of a binary at each Galactocentric radius.
-Therefore, kicks will not significantly alter the overall distribution of their positions.
-Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.
-
-\subsection{Gravitational Wave Inspiral}
-
-Each binary loses orbital energy to gravitational waves throughout its lifetime.
-This causes the binary to shrink and circularise over time.
-In order to assess the detectability of a binary, we need to know its eccentricity and frequency at the time of the LISA mission.
-For each binary in our simulated Milky Way, we know that the time from DCO formation to today is $\tau - t_{\rm evolve}$ and that the initial eccentricity and semi-major axis are $e_{\rm DCO}$ and $a_{\rm DCO}$.
-We find the eccentricity of the binary at the start of the LISA mission, $e_{\rm LISA}$, by numerically integrating its time derivative \citep[][Eq.
-5.13]{Peters+1964} given the initial conditions.
-This additionally can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq.
-5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.
-
-\subsection{Detectability}
-
-We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
-The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn+2000}
-\begin{equation}\label{eq:snr}
-    \rho^2 = \sum_{n=1}^{\infty} \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^{2}}{f_{n}^{2} S_{\rm n}\left(f_{n}\right)} \dd{f_n},
-\end{equation}
-where $n$ is a harmonic of the gravitational wave signal, $f_n = n \cdot f_{\rm orb}$ is the frequency of the $n^{\rm th}$ harmonic of the gravitational wave signal, $f_{\rm orb}$ is the orbital frequency, $S_{\rm n}(f_n)$ is the LISA sensitivity curve at frequency $f_n$ \citep[e.g.][]{Robson+2019} and $h_{c,n}$ is the characteristic strain of the $n^{\rm th}$ harmonic, given by
-\begin{equation}\label{eq:charstrain}
-    h^2_{c,n} = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n,e)}{F(e)}
-\end{equation}
-\citep[e.g.][]{Barack+2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters+1963} and $\mathcal{M}_c$ is the chirp mass, defined as
-\begin{equation}\label{eq:chirp_mass}
-    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}}.
-\end{equation}
-
-For the sake of computational efficiency, it is convenient to make the approximation that many of the binaries are stationary in frequency space on the timescale of the observing mission.
-This simplifies the signal-to-ratio equation to
-\begin{equation}\label{eq:snr_stat}
-    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 \, T_{\rm obs} h_n^2}{S_n(f_n)},
-\end{equation}
-where $T_{\rm obs}$ is the observing time and $h_n$ is the strain amplitude of gravitational waves emitted in the $n^{\rm th}$ harmonic, given by
-\begin{equation}
-    h_n^2 = \frac{2^{25/3}}{5} \frac{\left(G \mathcal{M}_{c}\right)^{10/3}}{c^{8}} \frac{\left(\pi f_{\mathrm{orb}}\right)^{4 / 3}}{D_L^2} \frac{g(n, e)}{n^2}.
-\end{equation}
-
-We consider a binary as stationary if its change in gravitational wave frequency is less than 1\% of the initial frequency.
-None binaries in our sample are in the non-stationary regime and therefore we believe that this is an acceptable approximation.
-
-\subsection{Detection rate}
-We calculate the detection rate for any one Milky Way instance by determining the fraction of binaries that are detectable and normalising to the true mass and IMF of the Milky Way in order to account for our relatively smaller galaxy size and restricted mass ranges.
-For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.
+\input{sections/methods.tex}
 
@@
 
-In this section, we explore the problem of detecting double compact objects with LISA analytically, focussing specifically on BHNS binaries, before presenting our full simulation results in Section~\ref{sec:resultsII}.
-
-\subsection{The Role of Eccentricity}\label{sec:eccentricity_role}
-
-Unlike BHBH binaries, a significant fraction of the BHNS binary population is highly eccentric. A high eccentricity has two major effects on detecting a binary with gravitational waves.
-
-Firstly, eccentricity enhances the rate of energy emission via gravitational waves by a factor
-\begin{equation}
-    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}},
-\end{equation}
-compared to a circular binary with the same semi-major axis \citep[][Eq.\,17]{Peters+1963}.
-This means that eccentric binaries will not only inspiral faster, but also produce gravitational waves with stronger strain amplitudes (when summed over all harmonics).
-
-Secondly, eccentric binaries will emit gravitational waves at many harmonic frequencies (unlike circular binaries, which only emit at twice the orbital frequency).
-This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.
-
-Therefore, though the first effect always increases the strength of the signal, the two effects in tandem do not necessarily always increase the detectability of a binary and we illustrate this point in Fig.\,\ref{fig:ecc_effects}.
-We show effect of eccentricity on the gravitational wave signal from a typical BHNS binary of chirp mass $\mathcal{M}_c = 3 \unit{M_{\odot}}$ and distance $8 \unit{kpc}$ at an orbital frequency of $f_{\rm orb} = 3 \times 10^{-4} \unit{Hz}$.
-Increasing the eccentricity from $e = 0.0$ to $0.5$ results in an increase in the signal-to-noise ratio (annotated on each set of points).
-This is because the eccentricity not only increases the gravitational wave emission, but also shifts the peak of the signal towards the minimum of the LISA sensitivity curve.
-However, further increasing the eccentricity from $e = 0.5$ to $0.9$ instead \textit{decreases} the signal-to-noise ratio.
-Although the greater eccentricity produces a stronger strain, it also shifts the peak of the gravitational wave signal to such high frequencies that the noise level is much higher and therefore has a lower signal-to-noise ratio.
-
-Overall, we can therefore conclude that for BHNS binaries, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve.
-Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{e_sc_combined.png}
-    \caption{An illustration of the effect of eccentricity on the detectability of a typical BHNS binary.
-Each point shows the strength of the gravitational wave signal at a harmonic frequency.
-We annotate each set of points with the binary's total signal-to-noise ratio summed over all harmonics and overplot the LISA sensitivity curve \citep{Robson+2019}.}
-    \label{fig:ecc_effects}
-\end{figure}
-
-\subsection{Horizon Distance}
-
-We define the horizon distance as the maximum distance at which a binary will have an signal-to-noise ratio above 7.
-In Figure~\ref{fig:bhns_horizon_distance} we show the horizon distance for a typical BHNS binary for different orbital frequencies and eccentricities.
-The horizon distance increases with frequency since the signal-to-noise ratio scales as
-\begin{equation}
-    \rho \propto \frac{N_{\rm cycle} \cdot h}{S_{\rm n}(f)} \propto \frac{f^{2/3} \cdot f^{1/2}}{S_{\rm n}(f)} \propto \frac{f^{7/6}}{S_{\rm n}(f)}.
-\end{equation}
-Since the minimum in the sensitivity curve occurs at $f \sim 10^{-2} \unit{Hz}$, the horizon distance increases monotonically with frequency.
-The dependence of the horizon distance on eccentricity follows the trends that we outlined in Section~\ref{sec:eccentricity_role}.
-The horizon distance increases with eccentricity up to a maximum, before decreasing once the eccentricity moves the peak of the gravitational wave luminosity past the minimum of the sensitivity curve.
-The eccentricity at which this maximum occurs is lower for higher orbital frequencies as less eccentricity is needed to move the peak past the minimum in the sensitivity curve.
-One may also note the sharp decrease in the horizon distance for binaries to the right of the $T_{\rm obs}$ contour, since these binaries will merge before the LISA mission is over.
-
-This plot shows that, in principle, we could detect a BHNS binary up to several Mpc from Earth and thus plausibly in any galaxy in the Local Group.
-In reality, the number extragalactic detections will likely be very low since the binary needs to be very close to merging to be visible at that distance (as can be noted from the inspiral contours in Fig.~\ref{fig:bhns_horizon_distance}) and it is unlikely that a binary happen to be that close to merging during the LISA mission.
-However, more specific to this study, one can note that the combination of frequency and eccentricity required to be visible within the Milky Way (to the right of the white line in Fig.~\ref{fig:bhns_horizon_distance}) is much more probable.
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{horizon_distance.pdf}
-    \caption{The horizon distance for a typical BHNS binary at different initial orbital frequencies and eccentricities is shown in the filled contours.
-The dashed white line indicates the edge of the Milky Way when using the \cite{Frankel+2018} model, which we define as the distance within which 99\% of binaries are contained.
-The dotted black lines show the inspiral time for the binary.}
-    \label{fig:bhns_horizon_distance}
-\end{figure}
+\input{sections/resultsI.tex}
 
@@
 
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation.
-We find that on average, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 11 NSNS binaries.
-Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-In contrast, the NSNS and BHNS rates are very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-
-Here is some attempted reasoning about the trends:
-
-\textbf{BHBH:} The major standout for the BHBHs is the optimistic.
-In this case Hertzsprung gap donors are allowed to survive CE and this is because many BHs are formed in this way rather than any effect on detectability.
-Can also comment on lower(higher) max NS mass being good(bad).
-Kicks same as BHNSs but less pronounced.
-
-\textbf{BHNS:} Whole bunch of trends here.
-The decrease with increasing $\beta$ seems to be due to fewer BHNSs surviving CE events (since envelope is harder to eject).
-Floor explains this in her paper and also references Kruckow.
-optimistic higher same as BHBH.
-Rapid higher because BHBHs become BHNSs instead.
-Maximum neutron star masses affect things because: lower means more things become BH instead of NS hence fewer BHNS and vice versa.
-PISN doesn't affect this mass range.
-Lower kicks means fewer disruptions.
-No BH kick lower again because NS kick is main factor at that point.
-\todo{this leaves E, F, G todo}
-
-\textbf{NSNS:} \todo{Why are B, C, D opposite?}.
-E is low because that's the main NSNS formation channel.
-CE follows nice trend (see Floor's about CE channels).
-Optimistic slightly up because duh.
-\todo{weirdly basically no change in rapid and max NS masses}.
-Lower kicks great as usual.
-No BH kicks no effect duh.
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
-The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
-    \label{fig:detection_rates}
-\end{figure*}
-
-\begin{table*}[htb]
-    \centering
-    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
-    \begin{tabular}{c|lll|lll}
-        \hline
-        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
-         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-        \hline
-        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
-        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
-        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
-        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
-        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
-        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
-        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
-        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
-        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
-        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
-        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
-        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
-        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
-        \hline
-    \end{tabular}
-    \label{tab:detection_rates}
-\end{table*}
-
-Now talk about where they are on the sensitivity curve
-
-We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
-We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
-The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
-We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
-If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-In order to explain the edges of the distribution, we additionally plot lines of constant distance.
-The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
-    \label{fig:dcos_on_sc}
-\end{figure*}
-
-\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}
-
-In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.
-
-\subsubsection{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$.
-This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation.
-The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.
-Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.
-
-The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios.
-The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.
-
-The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
-This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs.
-Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer.
-Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.
-
-\subsubsection{Neutron Star Mass}
-The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
-The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.
-
-\subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
-This may seem counterintuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often instead result in disrupted or too-wide binaries.
-In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
-This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
-
-\subsubsection{Orbital Frequency and Frequency Evolution}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
-
-\subsubsection{Luminosity Distance}
-Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-Each DCO also has a shoulder at lower distances since closer binaries are easier to detect.
-This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.
-
-\subsubsection{Inspiral Time}
-Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{explain the bumps}
-
-\begin{figure*}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{distribution_grid.pdf}
-    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model.
-Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type.
-The dotted curves in the black hole mass distribution show the primary and secondary mass distributions.
-In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
-    \label{fig:fiducial_pdf_distributions}
-\end{figure*}
-
-\subsection{Distinguishing DCOs}
-\todo{}
-
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{fiducial_cdf_distributions.pdf}
-    \caption{Cumulative distributions of observable parameters for binaries that are detectable in a 4 year LISA mission.
-Shaded areas indicate regimes in which no measurement can be made.
-Dotted lines on the angular resolution distribution show the field of view for various telescopes that could perform EM counterpart observations.}
-    \label{fig:fiducial_cdf_distributions}
-\end{figure*}
-
-\subsection{Model variations}
-
-\subsection{Comparison with other studies}\label{sec:compare_studies}
-\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
-This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version.
-They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
-
-We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
-The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity.
-Both of these changes could decrease the rate since most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
-
-\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
-Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively.
-The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2020} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, model \modCaseBB{}) .
-The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
+\input{sections/resultsII.tex}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Caveats}
-\begin{itemize}
-    \item Standard pop synth limitations
-    \item Systemic kicks
-    \item No models for high $Z$ values in Frankel
-    \item Only a single disc for the Milky Way
-    \item Stationary approximation? But I'm pretty sure that is fine
-\end{itemize}
 
-\subsection{Can we distinguish them?}
+\input{sections/discussion.tex}
 
 \section{Conclusion \& Summary} \label{sec:conclusion}
+
+\input{sections/conclusion.tex}
 
@@
 
-\section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
-In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.
-
-\subsection{Conversions and definitions}
-Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
-\begin{equation}\label{eq:chirpmass}
-    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
-\end{equation}
-where $m_1$ and $m_2$ are the primary and secondary mass of the binary.
-Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary.
-For convenience we show it here
-\begin{equation}\label{eq:kepler3rd}
-    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
-\end{equation}
-As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important.
-We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
-\begin{equation}\label{eq:g(n,e)}
-    \begin{aligned}
-        g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
-        &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
-    \end{aligned}
-\end{equation}
-where $J_{n}(v)$ is the Bessel function of the first kind.
-Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary.
-This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
-\begin{equation}\label{eq:eccentricity_enhancement_factor}
-    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
-\end{equation}
-Note that $F(0) = 1$ as one would expect.
-A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.
-
-\subsection{Characteristic Strain}
-The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
-\begin{equation}\label{eq:char_strain_dedf}
-    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
-\end{equation}
-where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
-The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq.
-19]{Peters+1963}
-\begin{equation}\label{eq:edot_peters}
-    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
-\end{equation}
-where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity.
-Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
-\begin{align}
-    \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
-    \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
-    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
-\end{align}
-The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
-\begin{equation}\label{eq:fdot_chainrule}
-    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
-\end{equation}
-The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
-\begin{align}
-    f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
-    \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
-\end{align}
-The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
-\begin{equation}\label{eq:dadt}
-    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
-\end{equation}
-Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
-\begin{align}
-    \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
-    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
-\end{align}
-which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
-\begin{align}
-    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
-    &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
-    \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
-\end{align}
-With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
-\begin{align}
-    h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
-    &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
-    h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
-\end{align}
-
-\subsection{Strain}
-The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles.
-This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}.
-The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain.
-This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio.
-Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.
-
-Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
-\begin{equation}\label{eq:strain-to-charstrain}
-    h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
-\end{equation}
-Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
-\begin{align}
-    h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
-    h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
-    h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
-\end{align}
-
-\subsection{General Signal-to-Noise Ratio}
-We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
-\begin{equation}
-    \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
-\end{equation}
-where $z$ is the redshift.
-We need to adjust this equation in a couple of key ways for LISA Galactic binaries.
-First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation.
-Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
-\begin{equation}\label{eq:snr_abs}
-    \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
-\end{equation}
-It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
-\begin{equation}\label{eq:dedf}
-    \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
-\end{equation}
-where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
-We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
-\begin{align}
-    \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
-    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
-    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
-    &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
-    \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
-\end{align}
-If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
-\begin{equation}
-    \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
-\end{equation}
-We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
-\begin{equation}\label{eq:snr_general}
-    \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
-\end{equation}
-
-\subsection{Stationary Signal-to-Noise Ratio}
-For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission.
-In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
-\begin{align}
-    \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
-    &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
-\end{align}
-Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
-\begin{equation}
-    \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
-\end{equation}
-where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}.
-This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
-\begin{equation}
-    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
-\end{equation}
-
-\section{Detection Rate Normalisation}\label{app:rate_normalisation}
-From each instance of the Milky Way that we simulate we can extract the number of targets\footnote{By targets, we are referring to either BHBH, BHNS or NSNS that merge in a Hubble time} that are detectable.
-However, this number must be normalised in order to show the true detection rate for the Milky Way.
-Therefore, we write that the number of detectable targets in the Milky Way is
-\begin{equation}\label{eq:norm_frame}
-    N_{\rm detect} = f_{\rm detect} \cdot N_{\rm target, MW},
-\end{equation}
-where $f_{\rm detect}$ is the fraction of targets in the instance that were detectable and $N_{\rm target, MW}$ is the total number of targets that have been formed in the Milky Way's history.
-We can find this total in two steps: (1) find the average number of targets formed per star forming mass (2) find the total star forming mass that has existed in the Milky Way's history.
-
-\subsection{Average target formation rate}
-Since double compact object formation is strongly metallicity dependent, we can find the average rate as the integral over metallicity
-\begin{equation}\label{eq:norm_avg_target_formation}
-    \avg{ \mathcal{R}_{\rm target} } = \int_{Z_{\rm min}}^{Z_{\rm max}} p_{Z} \mathcal{R}_{\rm target, Z} \dd{Z},
-\end{equation}
-where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ \citep{Frankel+2018} and $\mathcal{R}_{\rm target, Z}$ is defined as the number of targets formed per star forming mass.
-\begin{equation}
-    \mathcal{R}_{\rm target, Z} =  N_{\rm target, Z} / M_{\rm SF, Z}.
-\end{equation}
-The number of targets in our sample at a metallicity $Z$ can be written simply as the sum of the targets' weights:
-\begin{equation}
-    N_{\rm target, Z} = \sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i},
-\end{equation}
-where $w_i$ is the STROOPWAFEL weight assigned to a binary, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise 0.
-The total star forming mass at a metallicity $Z$ can be written as
-\begin{equation}
-    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
-\end{equation}
-where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass that COMPAS samples from given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
-The cuts applied to the distributions mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass is sampled from.
-
-\subsection{Total star forming mass in the Milky Way}
-It is important to distinguish between the \textit{total} star forming mass in the Milky Way and the \textit{current} star forming mass in the Milky Way.
-Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass.
-\citet{Licquia+2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$.
-This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs.
-We can write that the total star forming mass that has \textit{ever} existed in the Milky Way is
-\begin{equation}\label{eq:m_SF_MW}
-    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
-\end{equation}
-where $\avg{m}_{\rm SF, total}$ is the average star forming mass over the history of the Milky Way and $\avg{m}_{\rm SF, today}$ is the average star forming mass of the mass remaining today.
-The former is defined as
-\begin{equation}
-    \avg{m}_{\rm SF, total} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(t) \int_{0.01}^{200} \zeta(m)\ m \dd{m} \dd{t},
-\end{equation}
-where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}.
-The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
-\begin{equation}
-    \avg{m}_{\rm SF, today} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.08}^{200} \zeta(m)\ m_{\rm today}(m, \avg{Z}_\tau, \tau) \dd{m} \dd{\tau},
-\end{equation}
-where $m_{\rm today}(m, Z, \tau)$ is the mass of a star that was formed $\tau$ years ago at a metallicity $Z$.
-We calculate this by interpolating a grid of single stars in COMPAS over different masses and metallicities and seeing what final mass they get using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings.
-We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ main sequence lifetime of the star has passed, otherwise we just use the initial mass.
-Since we don't know the exact metallicity of each star we use the average metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}.
-If we now evaluate Equation \ref{eq:m_SF_MW}, we find the that total star forming mass that ever existed in the Milky Way is
-\begin{equation}
-    M_{\rm SF, MW} = 6.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = 9.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}},
-\end{equation}
-an increase of approximately 50\% from the value still in stars today.
-
-\subsection{Normalisation summary}
-We can plug Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
-\begin{equation}
-    N_{\rm detect} = 9.1 \times 10^{10} \unit{M_{\odot}} \cdot f_{\rm detect} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
-\end{equation}
-
-\section{Extra figures}
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[height=0.95\textheight]{previous_studies.png}
-    \caption{A table of previous studies of a similar nature to this work}
-    \label{fig:previous_studies}
-\end{figure*}
+\input{sections/appendix.tex}
 

### 2021-04-08 paper/tex/sections/abstract.tex
refactor latex to use separate files for sections

The Laser Interferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves. Detections of double compact objects with LISA may help to constrain uncertainties in binary evolution and understand the prevalence of electromagnetic counterparts to gravitational wave events. We estimate the number of Galactic DCOs that will be detected by LISA using a sample generated with the rapid population synthesis code COMPAS and a model of the Milky Way that includes not only the radial birth profiles but also the star formation and enrichment histories. We explore the effects of varying 15 physical assumptions that focus on key uncertainties in our understanding of mass transfer, common envelope and supernova physics. For our fiducial model, we find that over a 4 year mission, LISA will detect 26 BHBHs, 27 BHNSs and 12 NSNSs. These detection rates increase to 41, 45 and 19 respectively for a 10 year mission length. We present the distributions of the characteristics of the detectable binaries and explore how our different models affect them. We also discuss how well we can distinguish between different DCO types and methods for doing so.

### 2021-04-08 paper/tex/sections/appendix.tex
refactor latex to use separate files for sections

\section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.

\subsection{Conversions and definitions}
Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
\begin{equation}\label{eq:chirpmass}
    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
\end{equation}
where $m_1$ and $m_2$ are the primary and secondary mass of the binary. Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary. For convenience we show it here
\begin{equation}\label{eq:kepler3rd}
    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
\end{equation}
As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important. We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
\begin{equation}\label{eq:g(n,e)}
    \begin{aligned}
        g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
        &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
    \end{aligned}
\end{equation}
where $J_{n}(v)$ is the Bessel function of the first kind. Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary. This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
\begin{equation}\label{eq:eccentricity_enhancement_factor}
    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
\end{equation}
Note that $F(0) = 1$ as one would expect. A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.

\subsection{Characteristic Strain}
The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
\begin{equation}\label{eq:char_strain_dedf}
    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
\end{equation}
where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency. The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq. 19]{Peters+1963}
\begin{equation}\label{eq:edot_peters}
    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
\end{equation}
where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity. Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
\begin{align}
    \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
    \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
\end{align}
The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
\begin{equation}\label{eq:fdot_chainrule}
    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
\end{equation}
The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
\begin{align}
    f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
    \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
\end{align}
The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
\begin{equation}\label{eq:dadt}
    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
\end{equation}
Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
\begin{align}
    \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
\end{align}
which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
\begin{align}
    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
    &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
    \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
\end{align}
With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
\begin{align}
    h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
    &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
    h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
\end{align}

\subsection{Strain}
The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles. This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}. The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain. This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio. Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.

Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
\begin{equation}\label{eq:strain-to-charstrain}
    h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
\end{equation}
Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
\begin{align}
    h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
    h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
    h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
\end{align}

\subsection{General Signal-to-Noise Ratio}
We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
\begin{equation}
    \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
\end{equation}
where $z$ is the redshift. We need to adjust this equation in a couple of key ways for LISA Galactic binaries. First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation. Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
\begin{equation}\label{eq:snr_abs}
    \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
\end{equation}
It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
\begin{equation}\label{eq:dedf}
    \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
\end{equation}
where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
\begin{align}
    \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
    &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
    \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
\end{align}
If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
\begin{equation}
    \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
\end{equation}
We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
\begin{equation}\label{eq:snr_general}
    \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
\end{equation}

\subsection{Stationary Signal-to-Noise Ratio}
For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission. In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
\begin{align}
    \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
    &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
\end{align}
Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
\begin{equation}
    \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
\end{equation}
where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}. This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
\begin{equation}
    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
\end{equation}

\section{Detection Rate Normalisation}\label{app:rate_normalisation}
From each instance of the Milky Way that we simulate we can extract the number of targets\footnote{By targets, we are referring to either BHBH, BHNS or NSNS that merge in a Hubble time} that are detectable. However, this number must be normalised in order to show the true detection rate for the Milky Way. Therefore, we write that the number of detectable targets in the Milky Way is
\begin{equation}\label{eq:norm_frame}
    N_{\rm detect} = f_{\rm detect} \cdot N_{\rm target, MW},
\end{equation}
where $f_{\rm detect}$ is the fraction of targets in the instance that were detectable and $N_{\rm target, MW}$ is the total number of targets that have been formed in the Milky Way's history. We can find this total in two steps: (1) find the average number of targets formed per star forming mass (2) find the total star forming mass that has existed in the Milky Way's history.

\subsection{Average target formation rate}
Since double compact object formation is strongly metallicity dependent, we can find the average rate as the integral over metallicity
\begin{equation}\label{eq:norm_avg_target_formation}
    \avg{ \mathcal{R}_{\rm target} } = \int_{Z_{\rm min}}^{Z_{\rm max}} p_{Z} \mathcal{R}_{\rm target, Z} \dd{Z},
\end{equation}
where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ \citep{Frankel+2018} and $\mathcal{R}_{\rm target, Z}$ is defined as the number of targets formed per star forming mass. 
\begin{equation}
    \mathcal{R}_{\rm target, Z} =  N_{\rm target, Z} / M_{\rm SF, Z}.
\end{equation}
The number of targets in our sample at a metallicity $Z$ can be written simply as the sum of the targets' weights:
\begin{equation}
    N_{\rm target, Z} = \sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i},
\end{equation}
where $w_i$ is the STROOPWAFEL weight assigned to a binary, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise 0. The total star forming mass at a metallicity $Z$ can be written as
\begin{equation}
    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
\end{equation}
where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass that COMPAS samples from given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}). The cuts applied to the distributions mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass is sampled from.

\subsection{Total star forming mass in the Milky Way}
It is important to distinguish between the \textit{total} star forming mass in the Milky Way and the \textit{current} star forming mass in the Milky Way. Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass. \citet{Licquia+2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$. This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs. We can write that the total star forming mass that has \textit{ever} existed in the Milky Way is
\begin{equation}\label{eq:m_SF_MW}
    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
\end{equation}
where $\avg{m}_{\rm SF, total}$ is the average star forming mass over the history of the Milky Way and $\avg{m}_{\rm SF, today}$ is the average star forming mass of the mass remaining today. The former is defined as
\begin{equation}
    \avg{m}_{\rm SF, total} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(t) \int_{0.01}^{200} \zeta(m)\ m \dd{m} \dd{t},
\end{equation}
where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}. The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
\begin{equation}
    \avg{m}_{\rm SF, today} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.08}^{200} \zeta(m)\ m_{\rm today}(m, \avg{Z}_\tau, \tau) \dd{m} \dd{\tau},
\end{equation}
where $m_{\rm today}(m, Z, \tau)$ is the mass of a star that was formed $\tau$ years ago at a metallicity $Z$. We calculate this by interpolating a grid of single stars in COMPAS over different masses and metallicities and seeing what final mass they get using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings. We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ main sequence lifetime of the star has passed, otherwise we just use the initial mass. Since we don't know the exact metallicity of each star we use the average metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}. If we now evaluate Equation \ref{eq:m_SF_MW}, we find the that total star forming mass that ever existed in the Milky Way is
\begin{equation}
    M_{\rm SF, MW} = 6.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = 9.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}},
\end{equation}
an increase of approximately 50\% from the value still in stars today.

\subsection{Normalisation summary}
We can plug Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
\begin{equation}
    N_{\rm detect} = 9.1 \times 10^{10} \unit{M_{\odot}} \cdot f_{\rm detect} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
\end{equation}

\section{Supplementary figures}

\subsection{Physics variation cumulative distributions}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation. In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$. We additionally show the other physics variations in the background in light grey.}
    \label{fig:variations_cdf_1_3}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
    \label{fig:variations_cdf_4_6}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
    \label{fig:variations_cdf_7_10}
\end{figure*}

\begin{figure*}[h]
    \centering
    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
    \label{fig:variations_cdf_11_14}
\end{figure*}

\subsection{Detection rates}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections_fractions.pdf}
    \caption{As Figure~\ref{fig:detection_rates} except only showing the detectable \textit{fraction}.}
    \label{fig:detection_fractions}
\end{figure*}

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_merging.pdf}
    \caption{The total number of merging DCOs in the Milky Way. When multiplied by Figure~\ref{fig:detection_fractions} this gives Figure~\ref{fig:detection_rates}.}
    \label{fig:total_merging_dcos}
\end{figure*}

\subsection{Miscellaneous}

\begin{figure*}[p]
    \centering
    \includegraphics[height=0.95\textheight]{previous_studies.png}
    \caption{A table of previous studies of a similar nature to this work}
    \label{fig:previous_studies}
\end{figure*}

### 2021-04-08 paper/tex/sections/discussion.tex
refactor latex to use separate files for sections

\subsection{Caveats}
\begin{itemize}
    \item Standard pop synth limitations
    \item Systemic kicks
    \item No models for high $Z$ values in Frankel
    \item Only a single disc for the Milky Way
\end{itemize}

\subsection{Can we distinguish them?}

### 2021-04-08 paper/tex/sections/introduction.tex
refactor latex to use separate files for sections

Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, there have been 50 gravitational wave events detected by LIGO \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}. The investigation of double compact object (DCO) population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different DCO types.

The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) provides an exciting new lens through which to view the realm of gravitational waves. LISA will observe binaries at lower orbital frequencies than LIGO ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger. This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which allows for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}. In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Vigna-Gomez+2018}, differentiate between formation channels and distinguish between DCO types.

One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS). Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.

Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. Collating a sample of BHNS binaries will allow us to better understand whether there are electromagnetic counterparts to their gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}. Moreover, if the neutron star is observable (such as a pulsar), a BHNS would be ideal for measuring the Hubble constant \citep[e.g.][]{Feeney+2020} and the neutron star equation of state. A detection with LISA would allow these various signals to be measured for years before the merger and give observers ample time to prepare for the merger itself.

The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling. Several works focus only the more numerous population of double white dwarf population \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}, whilst others investigate the more massive BHBH, BHNS and NSNS binaries \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}. Our work improves upon previous studies by: exploring the effect of varying binary physics assumptions with 15 models, using a model for the Milky Way that is dependent on the chemical enrichment history and providing a full treatment of the eccentricity of detectable sources. We compare these studies with each other and our work in more detail in Section.~\ref{sec:compare_studies} and provide a summary in Fig.~\ref{fig:previous_studies}.

In this paper, we present predictions for the detection rate and distribution of binary characteristics (masses, frequency, eccentricity, distance, merger time) of BHNS, BHBH and NSNS binaries formed through isolated binary evolution in the Milky Way using binaries synthesised with the \href{https://compas.science}{COMPAS} rapid population synthesis code \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019} in tandem with the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019}. Additionally, we use a model of the Milky Way that not only includes the radial birth profiles but also the star formation and enrichment history. We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results. In this study we consider three main questions: (1) how many of each type of DCO will LISA detect? (2) can we distinguish between different DCOs with LISA? (3) can we use detections in LISA to constrain uncertainties in binary evolution?

In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA. In Section~\ref{sec:resultsI}, we explore the detection of double compact objects with LISA analytically. In Section~\ref{sec:resultsII}, we present our main results for each type of DCO and variation of physical assumptions. In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2021-04-08 paper/tex/sections/methods.tex
refactor latex to use separate files for sections

\subsection{Binary population synthesis}\label{sec:COMPAS_explained}

We use a population of binaries synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}. COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}. Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using the single star evolution fitting formulae from \citet{Hurley+2000} to the models of \citet{Pols+1998}. In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample. This algorithm increases the prevalence of target DCOs (BHBH, BHNS and NSNS binaries in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.

\subsubsection{Population Overview}

The population of double compact objects used in this study was synthesised by \citet{Broekgaarden+2021}. One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements. These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}. This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.

\subsubsection{Initial Conditions}

Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation. The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$. The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g. with][]{Sana+2012}. We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star. We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}. We assume that all binaries are circular at birth to reduce the dimensions of initial parameters. Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.

For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
\begin{equation}
    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
\end{equation}
for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation and gravitational-wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL. We sample from these sets of parameters when creating synthetic galaxies.

\subsubsection{Physical assumptions in fiducial model}\label{sec:fiducial_physics}
In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see Section 2.1.2 and Table 1 of \citet{Broekgaarden+2021}.

\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}. The mass transfer efficiency, $\beta = \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor. We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}. The maximum accretion rate for double compact objects is limited to the Eddington accretion rate. If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star, thus varying $\beta$ \citep[e.g.][]{Massevitch+1975, Soberman+1997}. We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.

\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}. We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope. For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}. We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004}. This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}. We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections.

\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs. For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}. The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}. We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.

We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}. We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}. For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ as in \citet{Pfahl+2002} and \citet{Podsiadlowski+2004}.

We assume that stars that undergo case BB mass transfer experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}. For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).

Stars with helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}. We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.

We assume that kicks are isotropic in the frame of the collapsing star. The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017}.
We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.

\subsubsection{Physical assumptions in other models} \label{sec:variation_assumptions}
In addition to our fiducial model, we explore 14 other models which change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions. Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.

Models \modRangeMT{} focus on changes to the mass transfer physics. We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively. In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.

Models \modRangeCE{} focus on altering the common envelope physics. We change the common envelope efficiency parameter in models \modAlphaLow{} and \modAlphaHigh{} to $\alpha = 0.5$ and $2.0$ respectively. In model \modOpt, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.

Finally, models \modRangeSN{} make changes related to our assumptions about supernova physics. Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription. We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses. Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae. In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks. Finally, model \modNoBH{} removes the natal kick for all black holes.

\begin{table}[htb]
    \centering
    \begin{tabular}{cl}
        \hline \hline
        Model & Physics Variation \\
        \hline \hline
        \modFid & -- \\
        \hline
        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
        \modCaseBB & Case BB mass transfer is always unstable \\
        \hline
        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
        \modOpt & HG donor stars initiating a CE survive CE \\
        \hline
        \modRapid & Fryer rapid SN remnant mass prescription \\
        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
        \modNoPISN & PISN and pulsational-PISN not implemented \\
        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
        \modNoBH & Black holes receive no natal kick \\
        \hline \hline
    \end{tabular}%
    \caption{Adapted from \citet[][Table 2]{Broekgaarden+2021}, a description of the 15 binary population synthesis models used in this study. \modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics.}
    \label{tab:physics_variations}
\end{table}

\subsection{Galaxy Synthesis}

In order to produce a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries. For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc. We do not find that adding other components would significantly alter our results.

Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution. We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.

\subsubsection{Milky Way disc model}

For the Milky Way thin disc, we use the model from \citet{Frankel+2018}. The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way. They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}. The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy. We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.

The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
\begin{equation}\label{eq:galaxy_tau}
    p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
\end{equation}
where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}. The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq. 5]{Frankel+2018}
\begin{equation}\label{eq:galaxy_R}
    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \cdot \frac{R_0}{[R_{\rm exp}(\tau)]^2},
\end{equation}
where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
\begin{equation}
    R_{\rm exp}(\tau) = 4 \unit{kpc} \qty(1 - \alpha_{R_{\rm exp}} \qty(\frac{\tau}{8 \unit{Gyr}})),
\end{equation}
where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
\begin{equation}\label{eq:galaxy_FeH}
    \begin{split}
        [{\rm Fe} / {\rm H}] (R, \tau) = &F_m + \nabla [{\rm Fe} / {\rm H}] R \\
        &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
    \end{split}
\end{equation}
where
\begin{equation}
    f(\tau) = \qty(1 - \frac{\tau}{\tau_m})^{\gamma_{[{\rm Fe} / {\rm H}]}},
\end{equation}
$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}. We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
\begin{equation}\label{eq:galaxy_FeH_to_Z}
    \log Z = 0.977 [{\rm Fe} / {\rm H}] + \log(Z_\odot).
\end{equation}
Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
\begin{equation}\label{eq:galaxy_z}
    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
\end{equation}
where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$. Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.

\subsubsection{Combining population and galaxy synthesis}

For each Milky Way instance, we randomly sample the following set of parameters
\begin{equation}
    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
\end{equation}
for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity. Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions. This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{galaxy_diagram.png}
    \caption{A schematic showing how we create a mock Milky Way disc. On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan+2011}. On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points. The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$). The top panel shows a side-on view and the bottom panel shows a view from above.}
    \label{fig:galaxy_schematic}
\end{figure*}

% \begin{figure}[t]
%     \centering
%     \includegraphics[width=\columnwidth]{galaxy_metallicity.png}
%     \caption{A random instance of the Milky Way of $10^5$ binaries, created using distributions from \citet{Frankel+2018}. The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$). The top panel shows a side-on view and the bottom panels shows a view from above.}
%     \label{fig:galaxy_metallicity}
% \end{figure}

We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by randomly drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.

Each binary is likely to move from its birth orbit. Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw+1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.

The magnitude of the systemic kicks are typically small compared to the initial circular velocity of a binary at each Galactocentric radius. Therefore, kicks will not significantly alter the overall distribution of their positions. Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.

\subsection{Gravitational Wave Inspiral}

Each binary loses orbital energy to gravitational waves throughout its lifetime. This causes the binary to shrink and circularise over time. In order to assess the detectability of a binary, we need to know its eccentricity and frequency at the time of the LISA mission. For each binary in our simulated Milky Way, we know that the time from DCO formation to today is $\tau - t_{\rm evolve}$ and that the initial eccentricity and semi-major axis are $e_{\rm DCO}$ and $a_{\rm DCO}$. We find the eccentricity of the binary at the start of the LISA mission, $e_{\rm LISA}$, by numerically integrating its time derivative \citep[][Eq. 5.13]{Peters+1964} given the initial conditions. This additionally can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq. 5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.

\subsection{Detectability}

We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}. The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn+2000}
\begin{equation}\label{eq:snr}
    \rho^2 = \sum_{n=1}^{\infty} \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^{2}}{f_{n}^{2} S_{\rm n}\left(f_{n}\right)} \dd{f_n},
\end{equation}
where $n$ is a harmonic of the gravitational wave signal, $f_n = n \cdot f_{\rm orb}$ is the frequency of the $n^{\rm th}$ harmonic of the gravitational wave signal, $f_{\rm orb}$ is the orbital frequency, $S_{\rm n}(f_n)$ is the LISA sensitivity curve at frequency $f_n$ \citep[e.g.][]{Robson+2019} and $h_{c,n}$ is the characteristic strain of the $n^{\rm th}$ harmonic, given by
\begin{equation}\label{eq:charstrain}
    h^2_{c,n} = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n,e)}{F(e)}
\end{equation}
\citep[e.g.][]{Barack+2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters+1963} and $\mathcal{M}_c$ is the chirp mass, defined as
\begin{equation}\label{eq:chirp_mass}
    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}}.
\end{equation}

For the sake of computational efficiency, it is convenient to make the approximation that many of the binaries are stationary in frequency space on the timescale of the observing mission. This simplifies the signal-to-ratio equation to
\begin{equation}\label{eq:snr_stat}
    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 \, T_{\rm obs} h_n^2}{S_n(f_n)},
\end{equation}
where $T_{\rm obs}$ is the observing time and $h_n$ is the strain amplitude of gravitational waves emitted in the $n^{\rm th}$ harmonic, given by
\begin{equation}
    h_n^2 = \frac{2^{25/3}}{5} \frac{\left(G \mathcal{M}_{c}\right)^{10/3}}{c^{8}} \frac{\left(\pi f_{\mathrm{orb}}\right)^{4 / 3}}{D_L^2} \frac{g(n, e)}{n^2}.
\end{equation}

We consider a binary as stationary if its change in gravitational wave frequency is less than 1\% of the initial frequency. None binaries in our sample are in the non-stationary regime and therefore we believe that this is an acceptable approximation.

\subsection{Detection rate}
We calculate the detection rate for any one Milky Way instance by determining the fraction of binaries that are detectable and normalising to the true mass and IMF of the Milky Way in order to account for our relatively smaller galaxy size and restricted mass ranges. For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.

### 2021-04-08 paper/tex/sections/resultsI.tex
refactor latex to use separate files for sections

In this section, we explore the problem of detecting double compact objects with LISA analytically, focussing specifically on BHNS binaries, before presenting our full simulation results in Section~\ref{sec:resultsII}.

\subsection{The Role of Eccentricity}\label{sec:eccentricity_role}

Unlike BHBH binaries, a significant fraction of the BHNS binary population is highly eccentric. A high eccentricity has two major effects on detecting a binary with gravitational waves.

Firstly, eccentricity enhances the rate of energy emission via gravitational waves by a factor
\begin{equation}
    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}},
\end{equation}
compared to a circular binary with the same semi-major axis \citep[][Eq.\,17]{Peters+1963}. This means that eccentric binaries will not only inspiral faster, but also produce gravitational waves with stronger strain amplitudes (when summed over all harmonics).

Secondly, eccentric binaries will emit gravitational waves at many harmonic frequencies (unlike circular binaries, which only emit at twice the orbital frequency). This leads to the gravitational wave signal being diluted over many frequencies higher than the orbital frequency, where the higher the eccentricity, the more harmonics are required to capture all of the gravitational luminosity \citep[see][Fig.\,3]{Peters+1963}.

Therefore, though the first effect always increases the strength of the signal, the two effects in tandem do not necessarily always increase the detectability of a binary and we illustrate this point in Fig.\,\ref{fig:ecc_effects}. We show effect of eccentricity on the gravitational wave signal from a typical BHNS binary of chirp mass $\mathcal{M}_c = 3 \unit{M_{\odot}}$ and distance $8 \unit{kpc}$ at an orbital frequency of $f_{\rm orb} = 3 \times 10^{-4} \unit{Hz}$. Increasing the eccentricity from $e = 0.0$ to $0.5$ results in an increase in the signal-to-noise ratio (annotated on each set of points). This is because the eccentricity not only increases the gravitational wave emission, but also shifts the peak of the signal towards the minimum of the LISA sensitivity curve. However, further increasing the eccentricity from $e = 0.5$ to $0.9$ instead \textit{decreases} the signal-to-noise ratio. Although the greater eccentricity produces a stronger strain, it also shifts the peak of the gravitational wave signal to such high frequencies that the noise level is much higher and therefore has a lower signal-to-noise ratio.

Overall, we can therefore conclude that for BHNS binaries, higher eccentricity will produce more detectable binaries only if the orbital frequency is not already at or above the minimum of the LISA sensitivity curve. Another consideration for more massive binaries is whether the increased eccentricity will cause the binary to merge before the mission ends, which would cause a significant decrease in signal-to-noise ratio.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{e_sc_combined.png}
    \caption{An illustration of the effect of eccentricity on the detectability of a typical BHNS binary. Each point shows the strength of the gravitational wave signal at a harmonic frequency. We annotate each set of points with the binary's total signal-to-noise ratio summed over all harmonics and overplot the LISA sensitivity curve \citep{Robson+2019}.}
    \label{fig:ecc_effects}
\end{figure}

\subsection{Horizon Distance}

We define the horizon distance as the maximum distance at which a binary will have an signal-to-noise ratio above 7. In Figure~\ref{fig:bhns_horizon_distance} we show the horizon distance for a typical BHNS binary for different orbital frequencies and eccentricities. The horizon distance increases with frequency since the signal-to-noise ratio scales as
\begin{equation}
    \rho \propto \frac{N_{\rm cycle} \cdot h}{S_{\rm n}(f)} \propto \frac{f^{2/3} \cdot f^{1/2}}{S_{\rm n}(f)} \propto \frac{f^{7/6}}{S_{\rm n}(f)}.
\end{equation}
Since the minimum in the sensitivity curve occurs at $f \sim 10^{-2} \unit{Hz}$, the horizon distance increases monotonically with frequency. The dependence of the horizon distance on eccentricity follows the trends that we outlined in Section~\ref{sec:eccentricity_role}. The horizon distance increases with eccentricity up to a maximum, before decreasing once the eccentricity moves the peak of the gravitational wave luminosity past the minimum of the sensitivity curve. The eccentricity at which this maximum occurs is lower for higher orbital frequencies as less eccentricity is needed to move the peak past the minimum in the sensitivity curve. One may also note the sharp decrease in the horizon distance for binaries to the right of the $T_{\rm obs}$ contour, since these binaries will merge before the LISA mission is over.

This plot shows that, in principle, we could detect a BHNS binary up to several Mpc from Earth and thus plausibly in any galaxy in the Local Group. In reality, the number extragalactic detections will likely be very low since the binary needs to be very close to merging to be visible at that distance (as can be noted from the inspiral contours in Fig.~\ref{fig:bhns_horizon_distance}) and it is unlikely that a binary happen to be that close to merging during the LISA mission. However, more specific to this study, one can note that the combination of frequency and eccentricity required to be visible within the Milky Way (to the right of the white line in Fig.~\ref{fig:bhns_horizon_distance}) is much more probable.

\begin{figure}[htb]
    \centering
    \includegraphics[width=\columnwidth]{horizon_distance.pdf}
    \caption{The horizon distance for a typical BHNS binary at different initial orbital frequencies and eccentricities is shown in the filled contours. The dashed white line indicates the edge of the Milky Way when using the \cite{Frankel+2018} model, which we define as the distance within which 99\% of binaries are contained. The dotted black lines show the inspiral time for the binary.}
    \label{fig:bhns_horizon_distance}
\end{figure}

### 2021-04-08 simulation/notebooks/seaborn_utility.py
improve sc plot

@@ -1,0 +1,327 @@
+import operator
+import math
+
+from matplotlib.colors import to_rgba
+import matplotlib
+import numpy as np
+
+
+def cmap_from_colour(colour):
+    r, g, b, _ = to_rgba(colour)
+    h, s, _ = rgb_to_husl(r, g, b)
+    xx = np.linspace(-1, 1, int(1.15 * 256))[:256]
+    ramp = np.zeros((256, 3))
+    ramp[:, 0] = h
+    ramp[:, 1] = s * np.cos(xx)
+    ramp[:, 2] = np.linspace(35, 80, 256)
+    colors = np.clip([husl_to_rgb(*hsl) for hsl in ramp], 0, 1)
+    return matplotlib.colors.ListedColormap(colors[::-1])
+
+
+m = [
+    [3.2406, -1.5372, -0.4986],
+    [-0.9689, 1.8758, 0.0415],
+    [0.0557, -0.2040, 1.0570]
+]
+
+m_inv = [
+    [0.4124, 0.3576, 0.1805],
+    [0.2126, 0.7152, 0.0722],
+    [0.0193, 0.1192, 0.9505]
+]
+
+# Hard-coded D65 illuminant
+refX = 0.95047
+refY = 1.00000
+refZ = 1.08883
+refU = 0.19784
+refV = 0.46834
+lab_e = 0.008856
+lab_k = 903.3
+
+
+# Public API
+
+def husl_to_rgb(h, s, l):
+    return lch_to_rgb(*husl_to_lch([h, s, l]))
+
+
+def husl_to_hex(h, s, l):
+    return rgb_to_hex(husl_to_rgb(h, s, l))
+
+
+def rgb_to_husl(r, g, b):
+    return lch_to_husl(rgb_to_lch(r, g, b))
+
+
+def hex_to_husl(hex):
+    return rgb_to_husl(*hex_to_rgb(hex))
+
+
+def huslp_to_rgb(h, s, l):
+    return lch_to_rgb(*huslp_to_lch([h, s, l]))
+
+
+def huslp_to_hex(h, s, l):
+    return rgb_to_hex(huslp_to_rgb(h, s, l))
+
+
+def rgb_to_huslp(r, g, b):
+    return lch_to_huslp(rgb_to_lch(r, g, b))
+
+
+def hex_to_huslp(hex):
+    return rgb_to_huslp(*hex_to_rgb(hex))
+
+
[…]

### 2021-04-09 paper/tex/sections/introduction.tex
remove results I and relabel

@@
 In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
-In Section~\ref{sec:resultsI}, we explore the detection of double compact objects with LISA analytically.
-In Section~\ref{sec:resultsII}, we present our main results for each type of DCO and variation of physical assumptions.
+In Section~\ref{sec:results}, we present our main results for each type of DCO and variation of physical assumptions.
 In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2021-04-09 paper/tex/sections/results.tex
remove results I and relabel

\subsection{Detection Rates}
In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation. We find that on average, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 11 NSNS binaries. Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties. The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
    \label{fig:detection_rates}
\end{figure*}

\subsubsection{BHBH detection rate trends}
The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}). Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.

The exception to this statement is \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events. A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events. Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections. \tom{Can also mention slight trends in max NS mass and kicks that are explain in next paragraph}

\subsubsection{BHNS detection rate trends}
In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions. Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics. There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.

As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases. This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population. However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}. For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers. \todo{Why isn't the opposite true for model \modAlphaHigh{}? It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}

Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form. This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}. For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections. This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.

The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed. For the same reason, increasing the maximum neutron star mass increases the detection rate and the inverse is true when it is decreased (in models \modNSLow{} and \modNSHigh{}).

Finally, models \modSigLow{}-\modNoBH{} show increased detection rates as lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}. The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.

\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}

\todo{understand the $\beta$ trends}. There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude. This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs. As a result the total number of detections decreases, however interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).

\todo{come back to CE ones once we understand the BHNS ones}. \todo{weirdly basically no change in rapid and max NS masses}. As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the BH kick (model \modNoBH{}) of course has no effect on the NSNS population.

\begin{table*}[htb]
    \centering
    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
    \begin{tabular}{c|lll|lll}
        \hline
        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
        \hline
    \end{tabular}
    \label{tab:detection_rates}
\end{table*}

\subsection{Distribution on the sensitivity curve}

We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}. The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs. We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO. The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{dcos_on_sc.png}
    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}. We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries). If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights. In order to explain the edges of the distribution, we additionally plot lines of constant distance. The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
    \label{fig:dcos_on_sc}
\end{figure*}

\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}

In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.

\subsubsection{Black Hole Mass}
For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$. This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation. The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes. Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.

The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios. The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.

The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable. This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs. Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer. Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.

\subsubsection{Neutron Star Mass}
The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively. The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.

\subsubsection{Eccentricity}
The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs. This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric. However, these stronger kicks often instead result in disrupted or too-wide binaries. In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric. This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.

\subsubsection{Orbital Frequency and Frequency Evolution}
The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies. This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected. The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies. Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.

\subsubsection{Luminosity Distance}
Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs. Each DCO also has a shoulder at lower distances since closer binaries are easier to detect. This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.

\subsubsection{Inspiral Time}
Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{explain the bumps}

\begin{figure*}[htbp]
    \centering
    \includegraphics[width=\textwidth]{distribution_grid.pdf}
    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model. Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type. The dotted curves in the black hole mass distribution show the primary and secondary mass distributions. In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
    \label{fig:fiducial_pdf_distributions}
\end{figure*}

\subsection{Distinguishing DCOs}
\todo{}

\subsection{Model variations}

\subsection{Comparison with other studies}\label{sec:compare_studies}
\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate. This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version. They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN. However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).

We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way. \citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions. The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity. Both of these changes could decrease the rate since most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.

\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission. Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario. Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively. The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2020} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, model \modCaseBB{}) . The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.

### 2021-04-10 paper/tex/sections/comparisons.tex
updates introduction and create comparison section

--- 2021-04-09 paper/tex/sections/results.tex
@@
-\subsection{Detection Rates}
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation.
-We find that on average, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 11 NSNS binaries.
-Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
-The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
-    \label{fig:detection_rates}
-\end{figure*}
-
-\subsubsection{BHBH detection rate trends}
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-
-The exception to this statement is \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
-A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
-Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
-\tom{Can also mention slight trends in max NS mass and kicks that are explain in next paragraph}
-
-\subsubsection{BHNS detection rate trends}
-In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
-
-As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
-This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
-However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
-For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
-\todo{Why isn't the opposite true for model \modAlphaHigh{}?
-It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
-
-Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
-This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
-For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
-This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
-
-The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed.
-For the same reason, increasing the maximum neutron star mass increases the detection rate and the inverse is true when it is decreased (in models \modNSLow{} and \modNSHigh{}).
-
-Finally, models \modSigLow{}-\modNoBH{} show increased detection rates as lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
-The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-
-\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
-
-\todo{understand the $\beta$ trends}.
-There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
-This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
-As a result the total number of detections decreases, however interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).
-
-\todo{come back to CE ones once we understand the BHNS ones}.
-\todo{weirdly basically no change in rapid and max NS masses}.
-As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the BH kick (model \modNoBH{}) of course has no effect on the NSNS population.
-
-\begin{table*}[htb]
-    \centering
-    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
-    \begin{tabular}{c|lll|lll}
-        \hline
-        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
-         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-        \hline
-        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
-        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
-        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
-        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
-        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
-        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
-        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
-        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
-        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
-        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
-        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
-        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
-        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
-        \hline
-    \end{tabular}
-    \label{tab:detection_rates}
-\end{table*}
-
-\subsection{Distribution on the sensitivity curve}
-
-We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
-We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
-The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
-We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
-If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-In order to explain the edges of the distribution, we additionally plot lines of constant distance.
-The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
-    \label{fig:dcos_on_sc}
-\end{figure*}
-
-\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}
-
-In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.
-
-\subsubsection{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$.
-This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation.
-The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.
-Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.
-
-The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios.
-The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.
-
-The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
-This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs.
-Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer.
-Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.
-
-\subsubsection{Neutron Star Mass}
-The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
-The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.
-
-\subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
-This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often instead result in disrupted or too-wide binaries.
-In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
-This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
-
-\subsubsection{Orbital Frequency and Frequency Evolution}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
-
-\subsubsection{Luminosity Distance}
-Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-Each DCO also has a shoulder at lower distances since closer binaries are easier to detect.
-This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.
-
-\subsubsection{Inspiral Time}
-Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{explain the bumps}
-
-\begin{figure*}[htbp]
-    \centering
-    \includegraphics[width=\textwidth]{distribution_grid.pdf}
-    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model.
-Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type.
-The dotted curves in the black hole mass distribution show the primary and secondary mass distributions.
-In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
-    \label{fig:fiducial_pdf_distributions}
-\end{figure*}
-
-\subsection{Distinguishing DCOs}
-\todo{}
-
-\subsection{Model variations}
-
-\subsection{Comparison with other studies}\label{sec:compare_studies}
 \citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.

### 2021-04-10 paper/tex/sections/introduction.tex
updates introduction and create comparison section

@@
-Since the first direct detection of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, there have been 50 gravitational wave events detected by LIGO \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
-The investigation of double compact object (DCO) population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different DCO types.
+Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
+These detections offer exciting insights into the endpoints of massive stars and the investigation of population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different double compact object (DCO) types.
 
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) provides an exciting new lens through which to view the realm of gravitational waves.
-LISA will observe binaries at lower orbital frequencies than LIGO ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger.
-This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which allows for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}.
-In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Vigna-Gomez+2018}, differentiate between formation channels and distinguish between DCO types.
+The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) presents an exciting new lens through which to view the realm of gravitational waves.
+In the same way that radio telescopes produce a different, but complementary, view of the sky than optical telescopes, LISA will detect a different and complementary population of gravitational wave sources.
+LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger.
+This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}.
+In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Breivik+2016}, differentiate between formation channels and distinguish between DCO types.
+The maxmimum detectable distance for stellar mass sources in LISA is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral than at the merger.
+This means that LISA stellar mass sources are an excellent probe for our galaxy's history and evolution.
+
+Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
+However, whilst NS and BH binaries are rare, they provide an excellent probe for the endpoints of massive stars.
+
+Double black hole (BHBH) binaries are the dominant source in ground-based gravitational wave detections and several studies have tried to model the black hole mass function as well as identify the pair instability mass gap \citep[e.g.][]{Baxter+2021}.
+In contrast, BHBHs in LISA are not biased towards higher masses and instead will probe lower mass black holes, potentially offering insight about the presence of a lower mass gap between neutron stars and black holes.
+
+Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been observed \citep[e.g.][]{Abbott+2017_NSNS}.
+The detection of a NSNS in LISA in which at least one NS is a pulsar could connect these two populations as the binary could be observed from inspiral to merger.
+NSNS binaries are excellent sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
 One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS).
-Of all the events detected by LIGO, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
+Of all the events detected by ground-based detectors, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
+Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
+These binaries are expected to have similar electromagnetic counterparts to NSNSs and so can studied in the same way.
+A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system as these could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to constrain uncertain binary evolution processes \citep{Chattopadhyay+2020}.
 
-Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
-Collating a sample of BHNS binaries will allow us to better understand whether there are electromagnetic counterparts to their gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
-Moreover, if the neutron star is observable (such as a pulsar), a BHNS would be ideal for measuring the Hubble constant \citep[e.g.][]{Feeney+2020} and the neutron star equation of state.
-A detection with LISA would allow these various signals to be measured for years before the merger and give observers ample time to prepare for the merger itself.
+The detection of DCOs with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
+Previous studies that investigate BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still rare.
+Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
 
-The detection of double compact objects with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
-Several works focus only the more numerous population of double white dwarf population \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}, whilst others investigate the more massive BHBH, BHNS and NSNS binaries \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
-Our work improves upon previous studies by: exploring the effect of varying binary physics assumptions with 15 models, using a model for the Milky Way that is dependent on the chemical enrichment history and providing a full treatment of the eccentricity of detectable sources.
-We compare these studies with each other and our work in more detail in Section.~\ref{sec:compare_studies} and provide a summary in Fig.~\ref{fig:previous_studies}.
+We build upon previous efforts but will several important improvements.
+We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters.
+We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{Frankel+2018}.
+In contrast to many previous works, we provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
+Moreover, our binary population synthesis simulation is the most extensive of its kind, with 750 million binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
+In addition, we use the adaptive sampling algorithm STROOPWAFEL to further reduce our sampling noise \citep{Broekgaarden+2019}.
 
-In this paper, we present predictions for the detection rate and distribution of binary characteristics (masses, frequency, eccentricity, distance, merger time) of BHNS, BHBH and NSNS binaries formed through isolated binary evolution in the Milky Way using binaries synthesised with the \href{https://compas.science}{COMPAS} rapid population synthesis code \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019} in tandem with the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019}.
-Additionally, we use a model of the Milky Way that not only includes the radial birth profiles but also the star formation and enrichment history.
+In this paper, we present the most extensive simulations to date for predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
 We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results.
-In this study we consider three main questions: (1) how many of each type of DCO will LISA detect?
-(2) can we distinguish between different DCOs with LISA?
-(3) can we use detections in LISA to constrain uncertainties in binary evolution?
+We also discuss the effect of increasing the LISA mission length from 4 to 10 years and the possibility of distinguishing detections.
 
 In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
-In Section~\ref{sec:results}, we present our main results for each type of DCO and variation of physical assumptions.
-In Section~\ref{sec:discussion} we discuss these results and finish with our conclusions in Section~\ref{sec:conclusion}.
+We present our main results in Section~\ref{sec:results}, analysing our findings for each DCO type and variation of physical assumptions.
+In Section~\ref{sec:discussion} we discuss these results.
+In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2021-04-10 paper/tex/sections/results.tex
updates introduction and create comparison section

@@
 \subsection{Model variations}
-
-\subsection{Comparison with other studies}\label{sec:compare_studies}
-\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
-This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version.
-They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
-
-We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
-The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity.
-Both of these changes could decrease the rate since most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
-
-\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
-Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively.
-The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2020} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, model \modCaseBB{}) .
-The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.

### 2021-04-10 paper/tex/sections/appendix.tex
reorganise results: table to appendix, sc plot sooner

@@
-\section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
-In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.
+% \section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
+% In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.
 
-\subsection{Conversions and definitions}
-Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
-\begin{equation}\label{eq:chirpmass}
-    \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
-\end{equation}
-where $m_1$ and $m_2$ are the primary and secondary mass of the binary.
+% \subsection{Conversions and definitions}
+% Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
+% \begin{equation}\label{eq:chirpmass}
+%     \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
+% \end{equation}
+% where $m_1$ and $m_2$ are the primary and secondary mass of the binary.
 Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary.
 For convenience we show it here
-\begin{equation}\label{eq:kepler3rd}
-    a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
-\end{equation}
-As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important.
+% \begin{equation}\label{eq:kepler3rd}
+%     a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
+% \end{equation}
+% As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important.
 We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
-\begin{equation}\label{eq:g(n,e)}
-    \begin{aligned}
-        g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
-        &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
-    \end{aligned}
-\end{equation}
-where $J_{n}(v)$ is the Bessel function of the first kind.
+% \begin{equation}\label{eq:g(n,e)}
+%     \begin{aligned}
+%         g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
+%         &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
+%     \end{aligned}
+% \end{equation}
+% where $J_{n}(v)$ is the Bessel function of the first kind.
 Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary.
 This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
-\begin{equation}\label{eq:eccentricity_enhancement_factor}
-    F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
-\end{equation}
-Note that $F(0) = 1$ as one would expect.
+% \begin{equation}\label{eq:eccentricity_enhancement_factor}
+%     F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
+% \end{equation}
+% Note that $F(0) = 1$ as one would expect.
 A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.
 
-\subsection{Characteristic Strain}
-The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
-\begin{equation}\label{eq:char_strain_dedf}
-    h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
-\end{equation}
-where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
+% \subsection{Characteristic Strain}
+% The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
+% \begin{equation}\label{eq:char_strain_dedf}
+%     h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
+% \end{equation}
+% where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
 The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq.
 19]{Peters+1963}
-\begin{equation}\label{eq:edot_peters}
-    \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
-\end{equation}
-where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity.
+% \begin{equation}\label{eq:edot_peters}
+%     \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
+% \end{equation}
+% where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity.
 Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
-\begin{align}
-    \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
-    \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
-    \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
-\end{align}
-The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
-\begin{equation}\label{eq:fdot_chainrule}
-    \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
-\end{equation}
-The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
-\begin{align}
-    f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
-    \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
-\end{align}
-The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
-\begin{equation}\label{eq:dadt}
-    \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
-\end{equation}
-Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
-\begin{align}
-    \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
-    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
-\end{align}
-which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
-\begin{align}
-    \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
-    &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
-    \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
-\end{align}
-With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
-\begin{align}
-    h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
-    &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
-    h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
-\end{align}
+% \begin{align}
+%     \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
+%     \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
+%     \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
+% \end{align}
+% The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
+% \begin{equation}\label{eq:fdot_chainrule}
+%     \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
+% \end{equation}
+% The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
+% \begin{align}
+%     f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
+%     \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
+% \end{align}
+% The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
+% \begin{equation}\label{eq:dadt}
+%     \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
+% \end{equation}
+% Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
+% \begin{align}
+%     \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
+%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
+% \end{align}
+% which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
+% \begin{align}
+%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
+%     &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
+%     \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
+% \end{align}
+% With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
+% \begin{align}
+%     h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
+%     &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
+%     h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
+% \end{align}
 
-\subsection{Strain}
-The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles.
+% \subsection{Strain}
+% The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles.
 This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}.
@@
 
-Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
-\begin{equation}\label{eq:strain-to-charstrain}
-    h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
-\end{equation}
-Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
-\begin{align}
-    h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
-    h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
-    h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
-\end{align}
+% Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
+% \begin{equation}\label{eq:strain-to-charstrain}
+%     h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
+% \end{equation}
+% Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
+% \begin{align}
+%     h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
+%     h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
+%     h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
+% \end{align}
 
-\subsection{General Signal-to-Noise Ratio}
-We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
-\begin{equation}
-    \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
-\end{equation}
-where $z$ is the redshift.
+% \subsection{General Signal-to-Noise Ratio}
+% We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
+% \begin{equation}
+%     \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
+% \end{equation}
+% where $z$ is the redshift.
 We need to adjust this equation in a couple of key ways for LISA Galactic binaries.
@@
 Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
-\begin{equation}\label{eq:snr_abs}
-    \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
-\end{equation}
-It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
-\begin{equation}\label{eq:dedf}
-    \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
-\end{equation}
-where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
-We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
-\begin{align}
-    \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
-    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
-    &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
-    &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
-    \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
-\end{align}
-If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
-\begin{equation}
-    \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
-\end{equation}
-We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
-\begin{equation}\label{eq:snr_general}
-    \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
-\end{equation}
+% \begin{equation}\label{eq:snr_abs}
+%     \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
+% \end{equation}
+% It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
+% \begin{equation}\label{eq:dedf}
+%     \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
+% \end{equation}
+% where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
+% We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
+% \begin{align}
+%     \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
+%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
+%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
+%     &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
+%     \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
+% \end{align}
+% If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
+% \begin{equation}
+%     \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
+% \end{equation}
+% We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
+% \begin{equation}\label{eq:snr_general}
+%     \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
+% \end{equation}
 
-\subsection{Stationary Signal-to-Noise Ratio}
-For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission.
+% \subsection{Stationary Signal-to-Noise Ratio}
+% For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission.
 In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
-\begin{align}
-    \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
-    &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
-\end{align}
-Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
-\begin{equation}
-    \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
-\end{equation}
-where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}.
+% \begin{align}
+%     \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
+%     &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
+% \end{align}
+% Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
+% \begin{equation}
+%     \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
+% \end{equation}
+% where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}.
 This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
-\begin{equation}
-    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
-\end{equation}
+% \begin{equation}
+%     \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
+% \end{equation}
 
@@
 
-\section{Supplementary figures}
+\section{Supplementary material}
+
+\subsection{Detection rate table}
+\begin{table*}[htb]
+    \centering
+    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
+    \begin{tabular}{c|lll|lll}
+        \hline
+        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
+         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+        \hline
+        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
+        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
+        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
+        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
+        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
+        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
+        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
+        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
+        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
+        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
+        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
+        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
+        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
+        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
+        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
+        \hline
+    \end{tabular}
+    \label{tab:detection_rates}
+\end{table*}
 

### 2021-04-10 paper/tex/sections/results.tex
reorganise results: table to appendix, sc plot sooner

@@
+\subsection{Distribution on the sensitivity curve}
+
+We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
+The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
+We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
+The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{dcos_on_sc.png}
+    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
+We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
+If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
+In order to explain the edges of the distribution, we additionally plot lines of constant distance.
+The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
+    \label{fig:dcos_on_sc}
+\end{figure*}
+
 \subsection{Detection Rates}
@@
 
-\begin{table*}[htb]
-    \centering
-    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
-    \begin{tabular}{c|lll|lll}
-        \hline
-        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
-         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-        \hline
-        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
-        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
-        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
-        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
-        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
-        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
-        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
-        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
-        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
-        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
-        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
-        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
-        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
-        \hline
-    \end{tabular}
-    \label{tab:detection_rates}
-\end{table*}
-
-\subsection{Distribution on the sensitivity curve}
-
-We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
-We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
-The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
-We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
-If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-In order to explain the edges of the distribution, we additionally plot lines of constant distance.
-The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
-    \label{fig:dcos_on_sc}
-\end{figure*}
-
 \subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}

### 2021-04-10 paper/tex/sections/methods.tex
reorganise results: table to appendix, sc plot sooner
add LEGWORK details to methods

@@
 
-\subsubsection{Population Overview}
+\subsubsection{Population overview}
 
@@
 
-\subsubsection{Initial Conditions}
+\subsubsection{Initial conditions}
 
@@
 
-\subsection{Galaxy Synthesis}
+\subsection{Galaxy synthesis}
 
@@
 
-% \begin{figure}[t]
-%     \centering
-%     \includegraphics[width=\columnwidth]{galaxy_metallicity.png}
-%     \caption{A random instance of the Milky Way of $10^5$ binaries, created using distributions from \citet{Frankel+2018}.
-The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$).
-The top panel shows a side-on view and the bottom panels shows a view from above.}
-%     \label{fig:galaxy_metallicity}
-% \end{figure}
-
 We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by randomly drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.
@@
 
-\subsection{Gravitational Wave Inspiral}
+\subsection{Gravitational wave detection}
+We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability.
+For a full derivation of the equations given below please see the LEGWORK release paper (Wagg et al.
+in prep) or \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
+
+\subsubsection{Inspiral evolution}
 
@@
 
-\subsection{Detectability}
+\subsubsection{Binary detectability}
 
 We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
-The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following\footnote{For full derivations of the equations in this section, please see Appendix \ref{app:strain_snr_deriv}.} \citep[e.g.][]{Finn+2000}
+The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following \citep[e.g.][]{Finn+2000}
 \begin{equation}\label{eq:snr}
@@
 \end{equation}
-where $n$ is a harmonic of the gravitational wave signal, $f_n = n \cdot f_{\rm orb}$ is the frequency of the $n^{\rm th}$ harmonic of the gravitational wave signal, $f_{\rm orb}$ is the orbital frequency, $S_{\rm n}(f_n)$ is the LISA sensitivity curve at frequency $f_n$ \citep[e.g.][]{Robson+2019} and $h_{c,n}$ is the characteristic strain of the $n^{\rm th}$ harmonic, given by
+where $n$ is a harmonic of the gravitational wave signal, $f_n = n \cdot f_{\rm orb}$ is the frequency of the $n^{\rm th}$ harmonic of the gravitational wave signal, $f_{\rm orb}$ is the orbital frequency, $S_{\rm n}(f_n)$ is the LISA sensitivity curve at frequency $f_n$ \citep[e.g.][]{Robson+2019} and $h_{c,n}$ is the characteristic strain of the $n^{\rm th}$ harmonic, given by \citep[e.g.][]{Barack+2004}
 \begin{equation}\label{eq:charstrain}
-    h^2_{c,n} = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n,e)}{F(e)}
+    h^2_{c,n} = \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n,e)}{n F(e)},
 \end{equation}
-\citep[e.g.][]{Barack+2004}, where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters+1963} and $\mathcal{M}_c$ is the chirp mass, defined as
+where $D_L$ is the luminosity distance to the source, $f_{\rm orb}$ is the orbital frequency, $g(n, e)$ and $F(e)$ are given in \citet{Peters+1963} and $\mathcal{M}_c$ is the chirp mass, defined as
 \begin{equation}\label{eq:chirp_mass}
@@
 
-For the sake of computational efficiency, it is convenient to make the approximation that many of the binaries are stationary in frequency space on the timescale of the observing mission.
-This simplifies the signal-to-ratio equation to
-\begin{equation}\label{eq:snr_stat}
-    \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 \, T_{\rm obs} h_n^2}{S_n(f_n)},
+We use LEGWORK to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational wave luminosity remains below 1\%.
+
+\subsubsection{Detection rate calculation}
+For each physics variation model, we compute the total number of merging DCOs in the Milky Way today based on the COMPAS simulation.
+This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF.
+
+We determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation.
+We multiply this fraction by the total number in the Milky Way to find a detection rate.
+\begin{equation}
+    N_{\rm detect} = \frac{\sum_{i = 0}^{N_{\rm detect}} w_i}{\sum_{i = 0}^{N_{\rm DCO}} w_i} \cdot N_{\rm MW}
 \end{equation}
-where $T_{\rm obs}$ is the observing time and $h_n$ is the strain amplitude of gravitational waves emitted in the $n^{\rm th}$ harmonic, given by
-\begin{equation}
-    h_n^2 = \frac{2^{25/3}}{5} \frac{\left(G \mathcal{M}_{c}\right)^{10/3}}{c^{8}} \frac{\left(\pi f_{\mathrm{orb}}\right)^{4 / 3}}{D_L^2} \frac{g(n, e)}{n^2}.
-\end{equation}
-
-We consider a binary as stationary if its change in gravitational wave frequency is less than 1\% of the initial frequency.
-None binaries in our sample are in the non-stationary regime and therefore we believe that this is an acceptable approximation.
-
-\subsection{Detection rate}
-We calculate the detection rate for any one Milky Way instance by determining the fraction of binaries that are detectable and normalising to the true mass and IMF of the Milky Way in order to account for our relatively smaller galaxy size and restricted mass ranges.
 For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.

### 2021-04-11 paper/tex/sections/comparisons.tex
change comparison section

@@
-\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
+\todo{In this section I will discuss the information in the Figure~\ref{fig:previous_studies}}
+
+% \citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
 This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version.
@@
 
-We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
+% We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
 \citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
@@
 
-\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
+% \citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
 Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
@@
 The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{compare_dco_1.png}
+
+    \vspace{0.5cm}
+
+    \includegraphics[width=\textwidth]{compare_dco_2.png}
+    \caption{A table comparing previous studies of a similar nature to this work.
+The works listed in the table are \citet{Nelemans+2001,Belczynski+2010,Liu+2014,Lamberts+2018,Lau+2020,Breivik+2020,Sesana+2020}.}
+    \label{fig:previous_studies}
+\end{figure*}

### 2021-04-11 paper/tex/sections/methods.tex
update rate explanation

@@
 This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF.
+For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.
 
@@
 \end{equation}
-For a more in-depth discussion of this normalisation process see Appendix~\ref{app:rate_normalisation}.
+We calculate this detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 100,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.

### 2021-04-11 paper/tex/sections/results.tex
make figures better placed
results additions (sc plot and detect rate plot)

@@
+In this section we present our main results for the detectable LISA DCO population.
+We first show the distribution of the sources on the sensitivity curve before exploring the variations in the detection rate over different physics variations and analysing the parameter distributions for detectable sources in the fiducial model.
+
 \subsection{Distribution on the sensitivity curve}
@@
 We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-The shape of the distributions are bounded by the edge of the Milky Way and the scarcity of nearby DCOs.
-We indicate this with lines of constant distance that form as a boundary for the majority of DCOs, where the remaining scatter is due to variations in mass since lines are plotted for the average chirp mass of each respective DCO.
-The top edge is not a hard cutoff but is present because for any given distance there is a lower probability of drawing higher frequencies (since binaries spend more time at lower frequencies).
+In addition to the density distributions we plot grid lines of constant distance and inspiral time to explain the shape of the distribution.
+The straight diagonal lines show where a binary at a fixed distance would lie on the sensitivity curve for different frequencies and the average chirp mass (annotated in each panel).
+We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
+If we focus on the bottom panels with each individual DCO type, we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards around $2 \times 10^{-3} \unit{Hz}$.
+This offshoot is composed of eccentric binaries for which the circular distance contours will not apply.
+We therefore also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.97$ to show the differences for eccentric sources.
+We also note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
 
-\begin{figure*}[t]
+We also plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel).
+From these lines, it is clear why the density distribution decreases with increasing frequency, since high frequencies correspond to short inspiral times and thus DCOs will spend less time in these regimes.
+We also see that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances.
+This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency is better.
+
+\begin{figure*}[tp]
     \centering
     \includegraphics[width=\textwidth]{dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve \citep{Robson+2019}.
-We plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
+    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where the panels correspond to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
+In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
 If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-In order to explain the edges of the distribution, we additionally plot lines of constant distance.
-The dotted lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for a binary with $e = 0.9$}
+The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
+We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for an eccentric binary with $e = 0.97$.
+The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.}
     \label{fig:dcos_on_sc}
@@
 
-\subsection{Detection Rates}
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation.
-We find that on average, for our fiducial model, a four year LISA mission will detect 26 BHBH, 27 BHNS and 11 NSNS binaries.
-Increasing the LISA mission length to ten years changes the number of detections to 42, 45 and 19 respectively.
+\subsection{Detection rates}
+We find that on average, for our fiducial model, a four year LISA mission will detect \confinv{25.9}{11.1}{13.6} BHBHs, \confinv{26.7}{11.9}{14.8} BHNSs and \confinv{11.3}{6.4}{8.0} NSNSs where the error bars represent the 90\% confidence interval.
+Increasing the LISA mission length to ten years changes the number of detections to \confinv{42.0}{17.3}{17.3}, \confinv{44.5}{17.8}{20.7} and \confinv{19.3}{8.0}{9.7} respectively.
+In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
+We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.
+
+\subsubsection{BHBH detection rate trends}
+The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
+Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
+
+The exception to this statement is model \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
+A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
+Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
+
+\subsubsection{BHNS detection rate trends}
+In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
+Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
+There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
+
+As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
+This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
+However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
+
+\tom{@Selma, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
+We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke.
+I do see that the BHBH have a lot of only stable mass transfer and so reasonably are not too affected.
+NSNS basically only come through CE events and so sensibly are strongly affected but BHNS have $\sim 70\%$ classic channel and so should be affected strongly.
+But we don't see an increase with $\alpha = 2.0$.
+Any thoughts?}
+% For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
+\todo{Why isn't the opposite true for model \modAlphaHigh{}?
+It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
+
+Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
+This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
+For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
+This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
+
+The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed instead of BHBHs.
+For the same reason, increasing the maximum neutron star mass (model \modNSHigh{}) increases the detection rate and the inverse is true when it is decreased (model \modNSLow{}).
+
+Finally, models \modSigLow{}-\modNoBH{} show increased detection rates since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
+Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
+The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
+
+\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
+
+As $\beta$ increases the NSNS detection rate increases, the opposite trend to that seen in the BHNS rate.
+This is for two main reasons: firstly the ejection of a common envelope is less problematic for the less massive NSNS binaries.
+Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
+Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.
+
+There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
+This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
+As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).
+
+The vast majority of NSNSs in our sample are formed through the common envelope channel and thus changing the value of $\alpha_{\rm CE}$ has an effect on the rate.
+We see that decreasing $\alpha_{\rm CE}$ (model \modAlphaLow) leads to a lower rate as there is less energy available to eject the envelope and so more binaries result to stellar mergers rather than NSNSs and similarly we see an inverse trend when increasing $\alpha_{\rm CE}$ (model \modAlphaHigh).
+
+As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the PISN or BH kick prescription (models \modNoPISN{} and \modNoBH{}) of course has no effect on the NSNS population.
 
@@
 \end{figure*}
-
-\subsubsection{BHBH detection rate trends}
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-
-The exception to this statement is \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
-A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
-Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
-\tom{Can also mention slight trends in max NS mass and kicks that are explain in next paragraph}
-
-\subsubsection{BHNS detection rate trends}
-In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
-
-As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
-This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
-However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
-For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
-\todo{Why isn't the opposite true for model \modAlphaHigh{}?
-It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
-
-Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
-This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
-For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
-This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
-
-The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed.
-For the same reason, increasing the maximum neutron star mass increases the detection rate and the inverse is true when it is decreased (in models \modNSLow{} and \modNSHigh{}).
-
-Finally, models \modSigLow{}-\modNoBH{} show increased detection rates as lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
-The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-
-\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
-
-\todo{understand the $\beta$ trends}.
-There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
-This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
-As a result the total number of detections decreases, however interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).
-
-\todo{come back to CE ones once we understand the BHNS ones}.
-\todo{weirdly basically no change in rapid and max NS masses}.
-As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the BH kick (model \modNoBH{}) of course has no effect on the NSNS population.
 

### 2021-04-18 paper/tex/sections/introduction.tex
reorganise results: table to appendix, sc plot sooner
start intro feedback

@@
 
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) presents an exciting new lens through which to view the realm of gravitational waves.
-In the same way that radio telescopes produce a different, but complementary, view of the sky than optical telescopes, LISA will detect a different and complementary population of gravitational wave sources.
-LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and therefore focus on the inspiral phase of stellar mass binaries rather than the merger.
-This will allow LISA to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Gerosa+2019}.
-In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Breivik+2016}, differentiate between formation channels and distinguish between DCO types.
-The maxmimum detectable distance for stellar mass sources in LISA is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral than at the merger.
-This means that LISA stellar mass sources are an excellent probe for our galaxy's history and evolution.
+The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
+LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors.
+However, this frequency regime is also of great interest for the detection of local stellar mass binaries during their inspiral phase.
+This means that LISA will be able to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}, differentiate between formation channels and distinguish between DCO types.
+The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral than at the merger.
+This means that LISA stellar mass sources could be used as a probe for our galaxy's history and evolution \citep[e.g.][]{Korol+2019}.
 
-Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries \citep{Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
-However, whilst NS and BH binaries are rare, they provide an excellent probe for the endpoints of massive stars.
+Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
+More recently, interest has grown in the detection of NS and BH binaries.
+Although these sources are rare, they could be useful for learning more about the endpoints of massive stars.
 
@@
 We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results.
-We also discuss the effect of increasing the LISA mission length from 4 to 10 years and the possibility of distinguishing detections.
+We also discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
 
+Our paper is structured as follows.
 In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.

### 2021-04-18 paper/tex/sections/introduction.tex
add formation channel discussion

@@
 Although these sources are rare, they could be useful for learning more about the endpoints of massive stars.
+
+For the purposes of this paper, we focus only on the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection.
+There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016}.
 

### 2021-04-18 paper/tex/sections/introduction.tex
update BHBH section of intro

--- 2021-04-18 paper/tex/sections/introduction.tex
@@
 
-Double black hole (BHBH) binaries are the dominant source in ground-based gravitational wave detections and several studies have tried to model the black hole mass function as well as identify the pair instability mass gap \citep[e.g.][]{Baxter+2021}.
-In contrast, BHBHs in LISA are not biased towards higher masses and instead will probe lower mass black holes, potentially offering insight about the presence of a lower mass gap between neutron stars and black holes.
+For the purposes of this paper, we focus only on the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection.
+There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
 
@@
 
+Double black hole (BHBH) binaries in the Milky Way provide a greater observational challenge and, at the time of writing, no system of this nature has been identified.
+Thus, LISA could provide the first detection of a Galactic BHBH binary.
+Moreover, the mass distribution of stellar mass black holes is still uncertain.
+The only confirmed black holes (BH) in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
+This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
+The mass distribution of Galactic BHs has been investigated in detail, however the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) remains an open question \citep[e.g.][]{Ozel+2010,Farr+2011}.
+More recently there has been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019,Abdul-Masih+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
+A sample of BHBHs detected with LISA could possibly help to constrain these uncertainties in the stellar mass BH mass distribution.
+
 One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS).
 Of all the events detected by ground-based detectors, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
-Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
-These binaries are expected to have similar electromagnetic counterparts to NSNSs and so can studied in the same way.
-A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system as these could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to constrain uncertain binary evolution processes \citep{Chattopadhyay+2020}.
+Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
+These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs.
+A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
+These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
 
@@
 
-We build upon previous efforts but will several important improvements.
+We build upon previous efforts but with several important improvements.
 We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters.

### 2021-04-18 paper/tex/sections/introduction.tex
final (for now!) intro fixes after feedback

@@
 Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
-These detections offer exciting insights into the endpoints of massive stars and the investigation of population statistics provides an essential tool for constraining uncertainties in binary evolution and predicting distributions of observable parameters for different double compact object (DCO) types.
+These detections offer exciting insights into the evolution and endpoints of massive stars.
+The investigation of double compact object (DCO) population statistics will be an essential tool for predicting distributions of parameters that are observable with gravitational waves as well as constraining uncertainties in binary evolution.
 
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors.
+LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors.
 However, this frequency regime is also of great interest for the detection of local stellar mass binaries during their inspiral phase.
 This means that LISA will be able to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
-In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may provide further constraints on binary evolution \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}, differentiate between formation channels and distinguish between DCO types.
-The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral than at the merger.
-This means that LISA stellar mass sources could be used as a probe for our galaxy's history and evolution \citep[e.g.][]{Korol+2019}.
+In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may yield further constraints on binary evolution \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}, differentiate between formation channels and distinguish between DCO types.
+The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger.
+This means that LISA stellar mass sources can only be detected in local galaxies, with the majority residing in the Milky Way.
+Therefore, these sources could be used as a probe for our galaxy's history and evolution \citep[e.g.][]{Korol+2019}.
 
@@
 More recently, interest has grown in the detection of NS and BH binaries.
-Although these sources are rare, they could be useful for learning more about the endpoints of massive stars.
+Although these sources are rare, they could be useful for learning more about the evolution and endpoints of massive stars and thus we focus our paper on these sources.
 
-For the purposes of this paper, we focus only on the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection.
+For the purposes of this investigation, we consider only the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection.
 There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
@@
 The detection of a NSNS in LISA in which at least one NS is a pulsar could connect these two populations as the binary could be observed from inspiral to merger.
-NSNS binaries are excellent sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
+NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
-Double black hole (BHBH) binaries in the Milky Way provide a greater observational challenge and, at the time of writing, no system of this nature has been identified.
-Thus, LISA could provide the first detection of a Galactic BHBH binary.
+Double black hole (BHBH) binaries in the Milky Way present a greater observational challenge.
+To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH binary.
 Moreover, the mass distribution of stellar mass black holes is still uncertain.
-The only confirmed black holes (BH) in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
+The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
 This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
-The mass distribution of Galactic BHs has been investigated in detail, however the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) remains an open question \citep[e.g.][]{Ozel+2010,Farr+2011}.
-More recently there has been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019,Abdul-Masih+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
+These observations indicate the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which no black holes or neutron stars are observed \citep{Ozel+2010,Farr+2011} but its existence remains an open question \citep[e.g.][]{Woosley+2020}.
+Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019,Abdul-Masih+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
 A sample of BHBHs detected with LISA could possibly help to constrain these uncertainties in the stellar mass BH mass distribution.
@@
 The detection of DCOs with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
-Previous studies that investigate BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still rare.
+Previous studies that investigate BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
 Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
@@
 We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{Frankel+2018}.
+We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}.
 In contrast to many previous works, we provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind, with 750 million binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
-In addition, we use the adaptive sampling algorithm STROOPWAFEL to further reduce our sampling noise \citep{Broekgaarden+2019}.
+Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
+In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce our sampling noise.
 
@@
 In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.
+
+All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}.
+We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}.
+In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
+In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.

### 2021-04-19 paper/tex/sections/methods.tex
methods updates

@@
 
-We use a population of binaries synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
+We use a population of binaries recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
+(in prep).
+This population is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep[][Team COMPAS: J.
+Riley et al.
+(in prep)]{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
 COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}.
-Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using the single star evolution fitting formulae from \citet{Hurley+2000} to the models of \citet{Pols+1998}.
-In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
-This algorithm increases the prevalence of target DCOs (BHBH, BHNS and NSNS binaries in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
+Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using fitting formulae from \citet{Hurley+2000} to the single star models of \citet{Pols+1998}.
 
-\subsubsection{Population overview}
+\subsubsection{Initial conditions}
 
-The population of double compact objects used in this study was synthesised by \citet{Broekgaarden+2021}.
 One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
@@
 
-\subsubsection{Initial conditions}
-
 Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$ and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), therefore $p(m_1) \propto m_1^{-2.3}$.
+The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), $p(m_1) \propto m_1^{-2.3}$.
 The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
@@
 Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
+In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
+This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
 
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation and gravitational-wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL.
+for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL.
 We sample from these sets of parameters when creating synthetic galaxies.
@@
 
-We assume that stars that undergo case BB mass transfer experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
+We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
 For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).
 
-Stars with helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
+Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
 We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
@@
 We assume that kicks are isotropic in the frame of the collapsing star.
-The maximum neutron star mass is predicted to be between $2$-$3 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017}.
-We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
+We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
 
-\subsubsection{Physical assumptions in other models} \label{sec:variation_assumptions}
-In addition to our fiducial model, we explore 14 other models which change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions.
+\subsubsection{Model variations} \label{sec:variation_assumptions}
+In addition to our fiducial model for the formation of DCOs, we explore 14 other models in which we change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.
 
+Our fiducial model is labelled model \modFid{}.
 Models \modRangeMT{} focus on changes to the mass transfer physics.
@@
         \hline \hline
-        \modFid & -- \\
+        \modFid & Fiducial (see Section~\ref{sec:fiducial_physics}) \\
         \hline
@@
     \end{tabular}%
-    \caption{Adapted from \citet[][Table 2]{Broekgaarden+2021}, a description of the 15 binary population synthesis models used in this study.
-\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics.}
+    \caption{A description of the 15 binary population synthesis models used in this study.
+\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics \citep[c.f.][Table 2]{Broekgaarden+2021}.}
     \label{tab:physics_variations}
@@
 
-In order to produce a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries.
+In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries described in Section~\ref{sec:COMPAS_explained}.
 For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc.
@@
 
-\subsubsection{Milky Way disc model}
+\subsubsection{Milky Way disc model}\label{sec:disc_model}
 
@@
 They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}.
-The result of this work is a model for the Milky Way that is calibrated to observations and includes the star formation history, radial birth profile and chemical enrichment history of the galaxy.
+The result of this work is a model for the Milky Way that is calibrated to observations and which includes the star formation history, radial birth profile and chemical enrichment history of the galaxy.
 We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.
@@
 \begin{equation}\label{eq:galaxy_R}
-    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \cdot \frac{R_0}{[R_{\rm exp}(\tau)]^2},
+    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \frac{R_0}{[R_{\rm exp}(\tau)]^2},
 \end{equation}
@@
     \begin{split}
-        [{\rm Fe} / {\rm H}] (R, \tau) = &F_m + \nabla [{\rm Fe} / {\rm H}] R \\
+        [{\rm Fe} / {\rm H}] (R, \tau) &= F_m + \nabla [{\rm Fe} / {\rm H}] R \\
         &- \qty(F_m + \nabla [{\rm Fe} / {\rm H}] R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} ) f(\tau),
@@
 \begin{equation}\label{eq:galaxy_FeH_to_Z}
-    \log Z = 0.977 [{\rm Fe} / {\rm H}] + \log(Z_\odot).
+    \log_{10} (Z) = 0.977 [{\rm Fe} / {\rm H}] + \log_{10}(Z_\odot).
 \end{equation}
-Additionally, since the Frankel model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
+Additionally, since this model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
 \begin{equation}\label{eq:galaxy_z}
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using Eq.\,\ref{eq:galaxy_tau}-\ref{eq:galaxy_z}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:disc_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 Each binary is likely to move from its birth orbit.
-Although all stars in the Galactic disc experience some amount of radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks from instantaneous symmetric mass loss \citep{Blaauw+1961} and natal kicks from asymmetric supernovae \citep{Hobbs+2005}.
+Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep{Hobbs+2005}.
 

### 2021-04-20 simulation/slurm/run_all.sh
add new sims

@@ -3,9 +3,9 @@ python generate_scripts.py
 
 for type in BHBH BHNS NSNS
 do
-    for variation in fiducial optimistic alpha0_5 alpha2_0 unstableCaseBB massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 ccSNkick_100km_s ccSNkick_30km_s noBHkick rapid maxNSmass2_0 maxNSmass3_0 noPISN
+    for variation in fiducial optimistic alpha0_5 alpha2_0 unstableCaseBB massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 ccSNkick_100km_s ccSNkick_30km_s noBHkick rapid maxNSmass2_0 maxNSmass3_0 noPISN wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
     do
         sbatch --array=1-50 scripts/${type}_${variation}.sh
-        sleep 10
+        sleep 1
     done
 done

### 2021-04-20 simulation/src/variations.py
add new sims to variations

@@ -114,5 +114,19 @@ variations = np.array(
             "long": "No BH kicks",
             "colour": plt.get_cmap("tab20b")(18)
         },
+        {
+            "file": "wolf_rayet_multiplier_0_1",
+            "short": "P",
+            "med": r"$f_{\rm WR} = 0.1$",
+            "long": r"Wolf Rayet wind multiplier $= 0.1$",
+            "colour": "black"
+        },
+        {
+            "file": "wolf_rayet_multiplier_5",
+            "short": "P",
+            "med": r"$f_{\rm WR} = 5$",
+            "long": r"Wolf Rayet wind multiplier $= 5.0$",
+            "colour": "black"
+        }
     ]
 )

### 2021-04-20 simulation/output/combine_output.py
include total weights when combining

@@ -27,6 +27,7 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
     for v in range(len(variations)):
         full_data = None
         n_ten_year = np.array([], dtype=np.int)
+        total_weight = np.array([], dtype=np.float)
         n_runs = 0
         missing = []
 
@@ -41,6 +42,9 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                 with h5.File(fname, "r") as f:
                     n_curr = f["simulation"].attrs["n_ten_year"].astype(np.int)
                     n_ten_year = np.concatenate((n_ten_year, n_curr))
+
+                    total_temp = f["simulation"].attrs["total_MW_weight"].astype(np.int)
+                    total_weight = np.concatenate((total_weight, total_temp))
                     if full_data is None:
                         full_data = f["simulation"][...].squeeze()
                     else:
@@ -50,7 +54,7 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                         full_data[prev_len:] = add_data
             else:
                 missing.append(i)
-                
+
         # as long as there is at least one file
         if len(missing) != runs:
             # let the user know which ones are currently missing
@@ -65,9 +69,9 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
             with h5.File(floor_file, "r") as floor:
                 channels = identify_formation_channels(full_data["seed"],
                                                        floor)
-                
+
                 dco_seeds = floor["doubleCompactObjects"]["seed"][...].squeeze()
-    
+
                 index = np.argsort(dco_seeds)
                 sorted_dco_seeds = dco_seeds[index]
                 sorted_index = np.searchsorted(sorted_dco_seeds, full_data["seed"])
@@ -96,6 +100,7 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                     else:
                         file["simulation"][col] = full_data[col]
                 file["simulation"].attrs["n_ten_year"] = n_ten_year
+                file["simulation"].attrs["total_MW_weight"] = total_weight
         # otherwise make sure that the user knows no data is present
         else:
             print("No data found for {}".format(variations[v]["long"]))

### 2021-04-20 simulation/output/combine_output.py
floats not ints

@@ -43,7 +43,7 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                     n_curr = f["simulation"].attrs["n_ten_year"].astype(np.int)
                     n_ten_year = np.concatenate((n_ten_year, n_curr))
 
-                    total_temp = f["simulation"].attrs["total_MW_weight"].astype(np.int)
+                    total_temp = f["simulation"].attrs["total_MW_weight"]
                     total_weight = np.concatenate((total_weight, total_temp))
                     if full_data is None:
                         full_data = f["simulation"][...].squeeze()

### 2021-04-28 paper/tex/sections/introduction.tex
more comments from Selma on intro

@@
 Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
-These detections offer exciting insights into the evolution and endpoints of massive stars.
-The investigation of double compact object (DCO) population statistics will be an essential tool for predicting distributions of parameters that are observable with gravitational waves as well as constraining uncertainties in binary evolution.
+The detection of the mergers of these binaries have offered exciting insights into the evolution and endpoints of massive stars.
 
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors.
-However, this frequency regime is also of great interest for the detection of local stellar mass binaries during their inspiral phase.
-This means that LISA will be able to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
-In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may yield further constraints on binary evolution \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}, differentiate between formation channels and distinguish between DCO types.
+LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016}.
+However, this frequency regime is also of interest for the detection of local stellar mass binaries during their inspiral phase.
+This means that LISA will be able to detect, and possibly localise a binary on the sky, many years in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+In addition, LISA provides an opportunity to measure the eccentricities of double compact objects (DCO) that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
 The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger.
@@
 More recently, interest has grown in the detection of NS and BH binaries.
-Although these sources are rare, they could be useful for learning more about the evolution and endpoints of massive stars and thus we focus our paper on these sources.
+Although they are rare, LISA detections of these sources could be useful for learning more about the evolution and endpoints of massive stars.
+In this paper we focus on NS and BH binaries.
 
-For the purposes of this investigation, we consider only the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection.
+For the purposes of this investigation, we consider the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011}.
 There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
 
-Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been observed \citep[e.g.][]{Abbott+2017_NSNS}.
-The detection of a NSNS in LISA in which at least one NS is a pulsar could connect these two populations as the binary could be observed from inspiral to merger.
+Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been observed \citep[e.g.][]{Abbott+2017_NSNS}.
+The detection of a NSNS in LISA in which at least one NS is a pulsar could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
 NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
@@
 To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH binary.
-Moreover, the mass distribution of stellar mass black holes is still uncertain.
 The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
 This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
-These observations indicate the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which no black holes or neutron stars are observed \citep{Ozel+2010,Farr+2011} but its existence remains an open question \citep[e.g.][]{Woosley+2020}.
-Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019,Abdul-Masih+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
-A sample of BHBHs detected with LISA could possibly help to constrain these uncertainties in the stellar mass BH mass distribution.
+These observations suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which no black holes or neutron stars are observed \citep{Ozel+2010,Farr+2011} but its existence remains an open question \citep[e.g.][]{Kreidberg+2012}.
+Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged \citep{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
+A sample of BHBHs detected with LISA could possibly help to constrain the stellar mass BH mass distribution.
 
@@
 
-The detection of DCOs with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling.
-Previous studies that investigate BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
+The detection of DCOs with LISA has been investigated in several previous studies yet studies that focus on BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
 Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
@@
 We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}.
-In contrast to many previous works, we provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
-In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce our sampling noise.
+We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
+Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated massive binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
+We find that this large number of simulations is important to reduce the sampling noise.
+In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce this sampling noise.
 
-In this paper, we present the most extensive simulations to date for predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
-We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results.
-We also discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
+In this paper, we present predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
+We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
+
+All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}.
+We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}.
+In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
+In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 
@@
 In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.
-
-All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}.
-We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}.
-In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
-In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.

### 2021-04-28 paper/tex/sections/methods.tex
more methods comments done

@@
+To produce predictions for the DCOs that are detectable with LISA, we synthesise a population of DCOs using the population synthesis methods described in Section~\ref{sec:COMPAS_explained}.
+In order to obtain value for the uncertainty on the expected detection rates, we place this sample of DCOS in many different Monte Carlo sampled instances of the Milky Way, the model for which is described in Section~\ref{sec:galaxy_synthesis}.
+We evolve the orbit of each DCO in a Milky Way instance up to the LISA mission and calculate the detection rate for that instance using the methods presented in Section~\ref{sec:gw_detection}.
+
 \subsection{Binary population synthesis}\label{sec:COMPAS_explained}
@@
 (in prep).
-This population is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep[][Team COMPAS: J.
+This population is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
+COMPAS follows the approach of the pioneering population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of millions of binary systems.
+The code is open source and documented in the papers listed above and the on-line documentation.
+An extensive method paper is forthcoming (Team COMPAS: J.
 Riley et al.
-(in prep)]{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
-COMPAS broadly follows the approach of other codes, such as BSE \citep{Hurley+2002}.
-Each sampled binary is initialised as a zero-age main sequence (ZAMS) binary and each component star is evolved using fitting formulae from \citet{Hurley+2000} to the single star models of \citet{Pols+1998}.
+(in prep)) We summarize the main assumptions and settings relevant for this work in the following sections.
 
@@
 
-One million binaries, $N_{\rm binary} \sim 10^6$, were simulated for each of 50 metallicity bins equally spaced in log space with $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+One million binaries are simulated for 50 metallicity bins equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
 These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
@@
 Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, or the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), $p(m_1) \propto m_1^{-2.3}$.
+The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), $p(m_1) \propto m_1^{-2.3}$.
 The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
@@
 
-For each metallicity $Z$, we have a sample of binaries, each with a set of parameters
+For each metallicity $Z$, we thus have a sample of binaries, each with a set of parameters
 \begin{equation}
@@
 \subsubsection{Physical assumptions in fiducial model}\label{sec:fiducial_physics}
-In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see Section 2.1.2 and Table 1 of \citet{Broekgaarden+2021}.
+In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
+
+\textit{Stellar Evolution:} To follow the evolution of massive stars, COMPAS relies on fitting formula by \citet{Hurley+2000} to detailed single star models by \citet{Pols+1998}.
+COMPAS implements stellar wind mass loss using the prescriptions from \citet{Belczynski+2010b} and models the evolution of stars that lose or gain mass closely following the algorithms originally described in \citet{Tout+1996} and \citet{Hurley+2002}.
+For more information about the implementation of the single star evolution in COMPAS see the corresponding section in the upcoming methods paper (Team COMPAS: J.
+Riley et al.
+(in prep)).
 
@@
 \subsubsection{Model variations} \label{sec:variation_assumptions}
-In addition to our fiducial model for the formation of DCOs, we explore 14 other models in which we change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess their effect on the overall double compact object detection rates and distributions.
+In addition to our fiducial model for the formation of DCOs, we explore 14 other models in which we change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.
@@
 Our fiducial model is labelled model \modFid{}.
-Models \modRangeMT{} focus on changes to the mass transfer physics.
-We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate, in models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
+Models \modRangeMT{} focus on changes to the mass transfer physics assumptions.
+We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate.
+In models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
 In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.
@@
 
-Finally, models \modRangeSN{} make changes related to our assumptions about supernova physics.
+Finally, in models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
 Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
@@
 
-\subsection{Galaxy synthesis}
+\subsection{Galaxy synthesis}\label{sec:galaxy_synthesis}
 
@@
 
-\subsection{Gravitational wave detection}
+\subsection{Gravitational wave detection}\label{sec:gw_detection}
 We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability.
@@
 \subsubsection{Detection rate calculation}
-For each physics variation model, we compute the total number of merging DCOs in the Milky Way today based on the COMPAS simulation.
+For any one instance of the Milky Way, we calculate the detection rate
+
+For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
 This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF.
@@
 \end{equation}
-We calculate this detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 100,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.
+We calculate the detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 100,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.

### 2021-04-29 simulation/src/variations.py
update colors for variations

@@ -61,35 +61,35 @@ variations = np.array(
             "short": "H",
             "med": "optimistic\nCE",
             "long": "Optimistic CE",
-            "colour": plt.get_cmap("tab20")(4)
+            "colour": "darkgoldenrod"
         },
         {
             "file": "rapid",
             "short": "I",
             "med": "rapid SN",
             "long": "Fryer rapid prescription",
-            "colour": plt.get_cmap("tab20")(18)
+            "colour": "lightseagreen"
         },
         {
             "file": "maxNSmass2_0",
             "short": "J",
             "med": r"max $m_{\rm NS}$" + "\n" + r"$2.0 \, {\rm M_{\odot}}$",
             "long": r"Maximum neutron star mass = 2.0 ${\rm M_{\odot}}$",
-            "colour": plt.get_cmap("tab20")(1)
+            "colour": plt.get_cmap("tab20")(1/20)
         },
         {
             "file": "maxNSmass3_0",
             "short": "K",
             "med": r"max $m_{\rm NS}$" + "\n" + r"$3.0 \, {\rm M_{\odot}}$",
             "long": r"Maximum neutron star mass = 3.0 ${\rm M_{\odot}}$",
-            "colour": plt.get_cmap("tab20")(0)
+            "colour": plt.get_cmap("tab20")(0/20)
         },
         {
             "file": "noPISN",
             "short": "L",
             "med": "no PISN",
             "long": "No pair instability supernova",
-            "colour": plt.get_cmap("tab10")(4)
+            "colour": "deepskyblue"
         },
         {
             "file": "ccSNkick_100km_s",
@@ -97,7 +97,7 @@ variations = np.array(
             "med": r"$\sigma_{\rm cc}$" + "\n" + r"$100 \, {\rm km s^{-1}}$",
             "long": "SN kick dispersion "
                      + r"$\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$",
-            "colour": plt.get_cmap("tab20b")(2)
+            "colour": plt.get_cmap("tab20c")(11/20)
         },
         {
             "file": "ccSNkick_30km_s",
@@ -105,28 +105,28 @@ variations = np.array(
             "med": r"$\sigma_{\rm cc}$" + "\n" + r"$30 \, {\rm km s^{-1}}$",
             "long": "SN kick dispersion "
                      + r"$\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$",
[…]

### 2021-04-29 paper/tex/sections/appendix.tex
change comparison section
add formation channel plots
update appendix with plots/table

@@
         \hline
-        A & \confinv{25.9}{11.1}{13.6} & \confinv{26.7}{11.9}{14.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{17.3}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        B & \confinv{27.7}{12.6}{12.6} & \confinv{12.0}{6.0}{7.5} & \confinv{4.7}{2.7}{3.3} & \confinv{42.7}{17.6}{17.6} & \confinv{19.5}{7.5}{10.5} & \confinv{8.0}{3.3}{4.0}\\
-        C & \confinv{20.6}{9.4}{11.3} & \confinv{6.2}{2.8}{3.4} & \confinv{5.5}{2.7}{4.1} & \confinv{33.8}{13.1}{13.1} & \confinv{10.1}{3.9}{3.9} & \confinv{9.6}{4.1}{4.1}\\
-        D & \confinv{20.0}{8.3}{10.0} & \confinv{3.2}{1.6}{1.6} & \confinv{14.6}{8.3}{10.4} & \confinv{31.7}{11.7}{11.7} & \confinv{5.1}{1.9}{2.2} & \confinv{22.9}{10.4}{12.5}\\
-        E & \confinv{24.4}{12.2}{14.7} & \confinv{6.8}{3.8}{3.8} & \confinv{0.2}{0.1}{0.1} & \confinv{41.5}{17.1}{17.1} & \confinv{10.6}{3.8}{5.3} & \confinv{0.4}{0.1}{0.2}\\
-        F & \confinv{20.0}{10.0}{10.0} & \confinv{11.5}{6.6}{8.2} & \confinv{8.1}{3.6}{5.4} & \confinv{30.0}{12.0}{14.0} & \confinv{19.7}{9.9}{9.9} & \confinv{13.6}{5.4}{6.3}\\
-        G & \confinv{25.7}{9.9}{13.8} & \confinv{23.3}{10.6}{10.6} & \confinv{26.5}{15.1}{18.9} & \confinv{39.5}{13.8}{15.8} & \confinv{36.1}{12.7}{17.0} & \confinv{45.4}{18.9}{22.7}\\
-        H & \confinv{63.6}{31.8}{47.7} & \confinv{37.4}{20.8}{20.8} & \confinv{14.7}{8.4}{10.5} & \confinv{103.4}{39.8}{55.7} & \confinv{62.3}{24.9}{29.1} & \confinv{25.2}{12.6}{12.6}\\
-        I & \confinv{21.7}{10.9}{13.0} & \confinv{56.8}{31.6}{31.6} & \confinv{11.0}{5.5}{6.9} & \confinv{32.6}{13.0}{15.2} & \confinv{94.7}{37.9}{44.2} & \confinv{17.9}{8.3}{8.3}\\
-        J & \confinv{32.6}{16.3}{19.6} & \confinv{20.3}{9.0}{13.5} & \confinv{11.0}{6.3}{7.8} & \confinv{52.2}{19.6}{22.8} & \confinv{33.8}{11.3}{15.8} & \confinv{18.8}{7.8}{9.4}\\
-        K & \confinv{21.4}{9.7}{11.7} & \confinv{30.6}{13.6}{17.0} & \confinv{11.5}{6.6}{8.2} & \confinv{35.0}{13.6}{15.6} & \confinv{51.1}{20.4}{23.8} & \confinv{19.8}{8.2}{9.9}\\
-        L & \confinv{24.7}{9.9}{14.8} & \confinv{26.7}{14.8}{17.8} & \confinv{11.3}{6.4}{8.0} & \confinv{42.0}{14.8}{17.3} & \confinv{44.5}{17.8}{20.7} & \confinv{19.3}{8.0}{9.7}\\
-        M & \confinv{29.7}{13.2}{16.5} & \confinv{70.6}{39.2}{39.2} & \confinv{20.4}{11.7}{11.7} & \confinv{46.1}{19.8}{23.1} & \confinv{109.8}{39.2}{54.9} & \confinv{32.1}{14.6}{17.5}\\
-        N & \confinv{31.6}{15.8}{19.7} & \confinv{117.7}{58.8}{73.6} & \confinv{51.8}{29.6}{29.6} & \confinv{51.3}{23.7}{23.7} & \confinv{191.3}{73.6}{103.0} & \confinv{81.4}{37.0}{44.4}\\
-        O & \confinv{30.2}{15.1}{18.9} & \confinv{96.7}{48.3}{60.4} & \confinv{11.4}{6.5}{8.1} & \confinv{49.1}{22.7}{22.7} & \confinv{157.1}{60.4}{84.6} & \confinv{19.5}{9.7}{9.7}\\
+        A & \confinv{34.4}{20.9}{46.6} & \confinv{29.9}{20.1}{47.4} & \confinv{7.7}{5.0}{10.3} & \confinv{58.6}{31.0}{53.3} & \confinv{51.9}{28.0}{95.0} & \confinv{13.0}{6.8}{14.2}\\
+        B & \confinv{33.9}{19.7}{36.5} & \confinv{15.5}{9.6}{19.6} & \confinv{2.8}{1.9}{4.3} & \confinv{55.6}{27.7}{45.9} & \confinv{26.7}{13.8}{23.7} & \confinv{4.8}{2.7}{5.6}\\
+        C & \confinv{20.6}{11.1}{20.5} & \confinv{5.3}{3.0}{5.3} & \confinv{4.3}{3.1}{5.2} & \confinv{33.7}{15.7}{26.7} & \confinv{8.9}{4.2}{7.0} & \confinv{7.3}{4.5}{6.1}\\
+        D & \confinv{21.9}{14.7}{37.8} & \confinv{4.1}{2.6}{4.2} & \confinv{11.6}{8.3}{22.7} & \confinv{36.0}{21.6}{45.4} & \confinv{6.8}{3.4}{5.3} & \confinv{20.5}{12.7}{27.7}\\
+        E & \confinv{33.7}{19.4}{37.0} & \confinv{3.3}{2.3}{6.3} & \confinv{0.2}{0.1}{0.1} & \confinv{54.9}{26.7}{44.2} & \confinv{5.8}{3.5}{8.2} & \confinv{0.3}{0.1}{0.2}\\
+        F & \confinv{26.2}{16.0}{35.8} & \confinv{15.0}{11.4}{84.0} & \confinv{5.7}{3.8}{7.3} & \confinv{43.3}{22.2}{43.7} & \confinv{27.2}{18.2}{86.3} & \confinv{9.5}{5.2}{10.0}\\
+        G & \confinv{29.5}{15.9}{27.6} & \confinv{23.5}{14.0}{27.2} & \confinv{23.4}{15.2}{27.9} & \confinv{47.5}{21.4}{38.3} & \confinv{40.9}{20.7}{36.3} & \confinv{39.8}{21.4}{36.3}\\
+        H & \confinv{115.1}{98.0}{123.0} & \confinv{30.7}{21.4}{163.7} & \confinv{7.4}{4.8}{14.6} & \confinv{173.6}{117.7}{150.5} & \confinv{55.4}{32.8}{185.8} & \confinv{13.0}{6.8}{25.5}\\
+        I & \confinv{22.7}{12.4}{26.8} & \confinv{48.7}{30.9}{97.1} & \confinv{6.3}{4.0}{9.0} & \confinv{36.1}{16.8}{30.8} & \confinv{84.0}{45.0}{142.8} & \confinv{10.9}{5.8}{11.1}\\
+        J & \confinv{47.5}{31.6}{71.9} & \confinv{24.3}{16.3}{37.4} & \confinv{6.8}{4.4}{10.9} & \confinv{80.7}{46.8}{86.8} & \confinv{41.7}{22.9}{47.0} & \confinv{11.6}{6.2}{14.0}\\
+        K & \confinv{30.1}{18.0}{40.4} & \confinv{37.6}{24.6}{44.9} & \confinv{7.8}{5.1}{11.6} & \confinv{52.5}{28.2}{48.4} & \confinv{65.1}{35.0}{54.7} & \confinv{13.4}{7.1}{14.8}\\
+        L & \confinv{35.2}{21.3}{45.2} & \confinv{30.2}{19.9}{49.6} & \confinv{7.9}{5.0}{11.7} & \confinv{58.9}{31.0}{54.9} & \confinv{52.4}{28.5}{96.9} & \confinv{13.3}{7.1}{14.8}\\
+        M & \confinv{43.0}{28.3}{58.3} & \confinv{68.7}{43.4}{108.7} & \confinv{16.1}{10.4}{20.5} & \confinv{69.4}{38.1}{69.1} & \confinv{117.4}{61.8}{154.5} & \confinv{27.3}{14.5}{26.4}\\
+        N & \confinv{53.0}{34.1}{58.3} & \confinv{110.6}{71.3}{193.1} & \confinv{35.7}{23.6}{54.8} & \confinv{84.4}{44.9}{73.3} & \confinv{194.9}{102.6}{256.0} & \confinv{60.2}{32.7}{67.8}\\
+        O & \confinv{43.1}{27.0}{39.0} & \confinv{76.0}{43.9}{91.2} & \confinv{9.3}{6.0}{10.4} & \confinv{68.5}{35.8}{47.5} & \confinv{130.8}{62.9}{122.0} & \confinv{15.8}{8.4}{13.8}\\
+        P & \confinv{44.3}{28.4}{62.2} & \confinv{26.7}{17.0}{48.9} & \confinv{9.0}{5.6}{10.9} & \confinv{69.9}{38.0}{78.9} & \confinv{45.9}{25.9}{64.4} & \confinv{15.3}{7.4}{13.9}\\
+        Q & \confinv{0.0}{0.0}{0.0} & \confinv{6.3}{3.7}{6.1} & \confinv{7.8}{4.7}{8.0} & \confinv{0.0}{0.0}{0.0} & \confinv{10.8}{5.3}{7.6} & \confinv{13.0}{6.4}{10.4}\\
         \hline
@@
 
-\subsection{Detection rates}
+\subsection{Formation channels}
 
-\begin{figure*}[p]
+\begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{dco_detections_fractions.pdf}
-    \caption{As Figure~\ref{fig:detection_rates} except only showing the detectable \textit{fraction}.}
-    \label{fig:detection_fractions}
-\end{figure*}
+    \includegraphics[width=\textwidth]{formation_channels_BHBH.pdf}
+\end{figure}
 
-\begin{figure*}[p]
+\begin{figure}
     \centering
-    \includegraphics[width=\textwidth]{dco_merging.pdf}
-    \caption{The total number of merging DCOs in the Milky Way. When multiplied by Figure~\ref{fig:detection_fractions} this gives Figure~\ref{fig:detection_rates}.}
-    \label{fig:total_merging_dcos}
-\end{figure*}
+    \includegraphics[width=\textwidth]{formation_channels_BHNS.pdf}
+\end{figure}
 
-\subsection{Miscellaneous}
-
-\begin{figure*}[p]
+\begin{figure}
     \centering
-    \includegraphics[height=0.95\textheight]{previous_studies.png}
-    \caption{A table of previous studies of a similar nature to this work}
-    \label{fig:previous_studies}
-\end{figure*}
+    \includegraphics[width=\textwidth]{formation_channels_NSNS.pdf}
+\end{figure}

### 2021-04-29 paper/tex/sections/results.tex
update distribution grid with metallicity + more
updates to results, mainly in sc section

@@
 In this section we present our main results for the detectable LISA DCO population.
-We first show the distribution of the sources on the sensitivity curve before exploring the variations in the detection rate over different physics variations and analysing the parameter distributions for detectable sources in the fiducial model.
+We find that on average, for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs where the error bars represent the 90\% confidence interval.
+We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
 
-\subsection{Distribution on the sensitivity curve}
+\subsection{Distribution on the sensitivity curve}\label{sec:dcos_on_sc}
 
 We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-In addition to the density distributions we plot grid lines of constant distance and inspiral time to explain the shape of the distribution.
-The straight diagonal lines show where a binary at a fixed distance would lie on the sensitivity curve for different frequencies and the average chirp mass (annotated in each panel).
+This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel) and the more numerous WDWD population \citep[e.g.][]{Korol+2017}.
+This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency.
+This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs.
+There are several other notable features in these distributions and we plot grid lines of constant distance and inspiral time to help to explain the shape of the distribution.
+
+The straight diagonal lines show where a binary at a fixed distance and with the average chirp mass (annotated in each panel) would lie on the sensitivity curve for different frequencies.
 We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
-If we focus on the bottom panels with each individual DCO type, we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards around $2 \times 10^{-3} \unit{Hz}$.
-This offshoot is composed of eccentric binaries for which the circular distance contours will not apply.
-We therefore also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.97$ to show the differences for eccentric sources.
+From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards around $2 \times 10^{-3} \unit{Hz}$.
+This offshoot is composed of eccentric binaries for which the circular distance contours do not apply.
+For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines.
+We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.97$ to show the differences for eccentric sources.
 We also note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
@@
 We also see that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances.
-This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency is better.
+This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.
 
@@
 The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
-We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the dashed line shows the signal for an eccentric binary with $e = 0.97$.
-The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.}
+We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.97$.
+The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.
+In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}.
+In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
     \label{fig:dcos_on_sc}
@@
 
-\subsection{Detection rates}
-We find that on average, for our fiducial model, a four year LISA mission will detect \confinv{25.9}{11.1}{13.6} BHBHs, \confinv{26.7}{11.9}{14.8} BHNSs and \confinv{11.3}{6.4}{8.0} NSNSs where the error bars represent the 90\% confidence interval.
+\subsection{Detection rates}\label{sec:detection_rate_analysis}
+We find that for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs, where the error bars represent the 90\% confidence interval.
 Increasing the LISA mission length to ten years changes the number of detections to \confinv{42.0}{17.3}{17.3}, \confinv{44.5}{17.8}{20.7} and \confinv{19.3}{8.0}{9.7} respectively.
@@
 We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{dco_detections.pdf}
+    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
+Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals.
+The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.}
+    \label{fig:detection_rates}
+\end{figure*}
 
@@
 This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
-As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction (see Fig.~\ref{fig:detection_fractions}).
+As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction.
 
@@
 As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the PISN or BH kick prescription (models \modNoPISN{} and \modNoBH{}) of course has no effect on the NSNS population.
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1 (solid) and 2 (dotted) $\sigma$ uncertainties.
-The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in  Section~\ref{sec:fiducial_physics}}
-    \label{fig:detection_rates}
-\end{figure*}
 
@@
 \subsubsection{Inspiral Time}
-Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{explain the bumps}
+Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{finish this}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{distribution_grid.pdf}
-    \caption{Distributions for various parameters of the binaries that are detectable in a 4 year LISA mission in our fiducial model.
-Each line represents a kernel density estimator for the distribution and the colour denotes the double compact object type.
-The dotted curves in the black hole mass distribution show the primary and secondary mass distributions.
-In Section~\ref{sec:fiducial_distributions} we the features of the distributions.}
+    \includegraphics[width=\textwidth]{distribution_grid_4yr.pdf}
+    \caption{Distributions for various parameters of the DCOs that are detectable in a 4 year LISA mission in our fiducial model.
+Each panel shows the distribution of a single parameter, where the colour denotes the DCO type.
+We also plot the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping) with the dark and light shaded areas respectively.
+The first two rows (excluding metallicity) use kernel density estimators to show the distributions.
+The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines.
+The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a four year LISA mission.
+The dark shaded areas indicate regimes in which the quantity cannot be measured.
+The dotted lines in the angular resolution plot show the maximum angular resolution that can be covered by a single pointing of the labelled instrument.
+In Section~\ref{sec:fiducial_distributions} we discuss the features of the distributions.}
     \label{fig:fiducial_pdf_distributions}

### 2021-04-29 paper/tex/sections/comparisons.tex
add to comparisons section

--- 2021-04-10 paper/tex/sections/comparisons.tex
@@
-\citet{Lau+2020} find that the number of NSNS binaries in the Milky Way that would be detected by a 4 year LISA mission is 33, a factor of three times higher than our fiducial rate.
-This study incorporates \citet{Lau+2020} uses the same population synthesis code, COMPAS, as this study, though an earlier version.
-They make several different physical assumptions, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
+In Figure~\ref{fig:previous_studies}, we compare similar previous studies that have investigated the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
+The table details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
+This table not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
+
+In a seminal work, \citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
+Their predictions of the number of detectable DCOs are very different from our own, where we find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
+However, since their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which likely strongly affect the expected detections rates.
+
+\citet{Belczynski+2010} built upon this work by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
+They found a similar number of BHBH and BHNS detection to \citet{Nelemans+2001}, but a lower number of NSNS detections.
+The low total detection rate for all DCOs in this paper is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
+The reduced mission length means that the source signal has much less time to accumulate, whilst many fewer WDWDs can be resolved in this time, leading to a weaker signal and an increased Galactic confusion noise relative to our work.
+
+More recently, \citet{Lamberts+2018} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
+\citet{Sesana+2020} followed up on this paper using the same simulated BHBH population and presented updated results for the number of expected BHBH detections.
+They find significantly fewer BHBHs than our fiducial model despite using the same SNR threshold and LISA mission length.
+
+The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
+Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
+We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation}.
+
+\citet{Lau+2020} investigated the number of Galactic NSNS binaries that could be detected by LISA.
+Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version.
+Despite this, their study found a much larger number of detections.
+They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
 However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
@@
 We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} assumes constant star formation, solar metallicity and distribute binaries following the blue light luminosity of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
-The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity.
-Both of these changes could decrease the rate since most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
+\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
+The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity, both changes that could decrease the NSNS detection rate given that we find most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
 
-\citet{Breivik+2020} find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
+Finally, \citet{Breivik+2020} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
+\todo{what I write here will depend how much the numbers change in upcoming run.
+Long story short is that they only have two metallicity bins and use the optimistic CE model.}.
+
+% find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
 Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.

### 2021-05-03 simulation/notebooks/verification_binaries.py
add more details to verification binaries

@@ -1,62 +1,184 @@
 import astropy.units as u
 
 
-"""A list of the LISA verification binaries from Kupfer+18 with SNR > 7"""
+"""A list of the LISA verification binaries from Kupfer+18 (Table 1 and 2)"""
 
 verification_binaries = [
     {
         "label": "HM Cnc",
         "f_GW": 6.22 * u.mHz,
         "snr": 211.1,
+        "l_gal": 206.9246 * u.deg,
+        "b_gal": 23.3952 * u.deg,
+        "m_1": 0.55 * u.Msun,
+        "m_2": 0.27 * u.Msun,
+        "i": 38 * u.deg,
+        "dist": 5000 * u.pc,
     },
     {
         "label": "V407 Vul",
         "f_GW": 3.51 * u.mHz,
         "snr": 169.7,
+        "l_gal": 57.7281 * u.deg,
+        "b_gal": 6.4006 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.177 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1786 * u.pc,
     },
     {
         "label": "ES Cet",
         "f_GW": 3.22 * u.mHz,
         "snr": 154.3,
+        "l_gal": 168.9684 * u.deg,
+        "b_gal": -65.8632 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.161 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1584 * u.pc,
     },
     {
         "label": "SDSS J135154.46–064309.0",
         "f_GW": 2.12 * u.mHz,
         "snr": 21.8,
+        "l_gal": 328.5021 * u.deg,
+        "b_gal": 53.1240 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.1 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1317 * u.pc,
     },
     {
         "label": "AM CVn",
         "f_GW": 1.94 * u.mHz,
         "snr": 101.2,
+        "l_gal": 140.2343 * u.deg,
+        "b_gal": 78.9382 * u.deg,
+        "m_1": 0.68 * u.Msun,
+        "m_2": 0.125 * u.Msun,
+        "i": 43 * u.deg,
+        "dist": 299 * u.pc,
     },
     {
[…]

### 2021-05-05 simulation/notebooks/bootstrap.py
fix bootstrap warnings

@@ -51,7 +51,7 @@ def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None,
 
     # decide on x values to evaluate at (based on log scaling)
     if log_scale[0]:
-        print("WARNING: I think this doesn't work")
+        print("WARNING: I think this doesn't work", variable)
         x_vals = np.logspace(np.log10(np.min(variable)),
                              np.log10(np.max(variable)), x_count)
     else:
@@ -142,7 +142,6 @@ def bootstrapped_ecdf(variable, weights, seeds, ax,
 
     # decide on x values to evaluate at (based on log scaling)
     if log_scale[0]:
-        print("WARNING: I think this doesn't work")
         x_vals = np.logspace(np.log10(np.min(variable)),
                              np.log10(np.max(variable)), x_count)
     else:

### 2021-05-05 paper/tex/paper.tex
remove results I and relabel
updates introduction and create comparison section
final (for now!) intro fixes after feedback
add potential for coauthors
update affiliations

@@
 \usepackage{natbib}
+\usepackage{fontawesome5}
 
@@
 \newcommand{\todo}[1]{{\color{red}{[TODO: #1}]}}
-
-\newcommand{\floor}[1]{\textcolor{magenta}{[Floor: #1]}}
-\newcommand{\selma}[1]{\textcolor{pink}{[Selma: #1]}}
 \newcommand{\tom}[1]{\textcolor{ForestGreen}{[Tom: #1]}}
@@
 
+% affiliations
+\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
+\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
+\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
+\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
+
 \author[0000-0001-6147-5761]{T. Wagg}
-\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
+\affiliation{\cfa}
+\affiliation{\mpa}
 
 \author[0000-0002-4421-4962]{F. Broekgaarden}
-\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
+\affiliation{\cfa}
 
 \author[0000-0001-9336-2825]{S. E. de Mink}
-\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
-\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
+\affiliation{\cfa}
+\affiliation{\mpa}
+\affiliation{\UoA}
+
+\author{...TBD}
 
 \begin{abstract}{
-    \input{sections/abstract.tex}
+    % \input{sections/abstract.tex}
+    \noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\
 }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction} \label{sec:intro}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \input{sections/introduction.tex}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Method} \label{sec:method}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \input{sections/methods.tex}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results (I)  - Survey of the Problem} \label{sec:resultsI}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results} \label{sec:results}
+\input{sections/results.tex}
 
-\input{sections/resultsI.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results (II) - Synthetic Galaxy} \label{sec:resultsII}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\input{sections/resultsII.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion} \label{sec:discussion}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \input{sections/discussion.tex}
 
+\section{Comparison with previous studies}\label{sec:compare_studies}
+\input{sections/comparisons.tex}
+
 \section{Conclusion \& Summary} \label{sec:conclusion}
-
 \input{sections/conclusion.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \allowdisplaybreaks
-
 \appendix
-
 \input{sections/appendix.tex}

### 2021-05-05 paper/tex/sections/introduction.tex
update affiliations

@@
 
-All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}.
+All data produced in this study is publicly available on Zenodo \href{https://zenodo.org/record/4699713}{\faFileCode}\footnote{\url{https://zenodo.org/record/4699713}} as is the population used in our simulations \href{https://zenodo.org/record/4574727}{\faFileCode}\footnote{\url{https://zenodo.org/record/4574727}}.
 We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}.

### 2021-05-08 paper/tex/sections/abstract.tex
erase abstract

@@
-The Laser Interferometer Space Antenna (LISA) presents an exciting new lens through which to view the realm of gravitational waves.
-Detections of double compact objects with LISA may help to constrain uncertainties in binary evolution and understand the prevalence of electromagnetic counterparts to gravitational wave events.
-We estimate the number of Galactic DCOs that will be detected by LISA using a sample generated with the rapid population synthesis code COMPAS and a model of the Milky Way that includes not only the radial birth profiles but also the star formation and enrichment histories.
-We explore the effects of varying 15 physical assumptions that focus on key uncertainties in our understanding of mass transfer, common envelope and supernova physics.
-For our fiducial model, we find that over a 4 year mission, LISA will detect 26 BHBHs, 27 BHNSs and 12 NSNSs.
-These detection rates increase to 41, 45 and 19 respectively for a 10 year mission length.
-We present the distributions of the characteristics of the detectable binaries and explore how our different models affect them.
-We also discuss how well we can distinguish between different DCO types and methods for doing so.
+\noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\

### 2021-05-08 paper/tex/sections/appendix.tex
wrong MW mass paper
updates to appendix

@@
 \section{Detection Rate Normalisation}\label{app:rate_normalisation}
-From each instance of the Milky Way that we simulate we can extract the number of targets\footnote{By targets, we are referring to either BHBH, BHNS or NSNS that merge in a Hubble time} that are detectable.
-However, this number must be normalised in order to show the true detection rate for the Milky Way.
-Therefore, we write that the number of detectable targets in the Milky Way is
+In this section we explain in detail the normalisation process that we refer to in Section~\ref{sec:gw_detection}.
+From each instance of the Milky Way that we simulate we can extract the fraction of targets that are detectable, where we define a target as one of BHBH, BHNS or NSNS that merges in a Hubble time.
+Note that we complete this calculation separately for each DCO type and each model variations.
+
+We now explain how to convert the detectable fraction to a detection rate for the Milky Way. We write that the \textit{number} of detectable targets in the Milky Way is
 \begin{equation}\label{eq:norm_frame}
@@
 where $f_{\rm detect}$ is the fraction of targets in the instance that were detectable and $N_{\rm target, MW}$ is the total number of targets that have been formed in the Milky Way's history.
-We can find this total in two steps: (1) find the average number of targets formed per star forming mass (2) find the total star forming mass that has existed in the Milky Way's history.
+We can further break this total down into
+\begin{equation}
+    N_{\rm target, MW} = \avg{ \mathcal{R}_{\rm target} } \cdot M_{\rm SF, MW},
+\end{equation}
+where $\avg{ \mathcal{R}_{\rm target} }$ is the average number of targets formed per star forming mass and $M_{\rm SF, MW}$ is the total star forming mass that has existed in the Milky Way's history.
+We explain each of these terms in respective subsections below.
 
 \subsection{Average target formation rate}
-Since double compact object formation is strongly metallicity dependent, we can find the average rate as the integral over metallicity
+Double compact object formation is strongly metallicity dependent, so we must find the average rate as the integral over metallicity
 \begin{equation}\label{eq:norm_avg_target_formation}
@@
 \end{equation}
-where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ \citep{Frankel+2018} and $\mathcal{R}_{\rm target, Z}$ is defined as the number of targets formed per star forming mass.
+where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ (which can be found using the distribution in \citealp{Frankel+2018}) and $\mathcal{R}_{\rm target, Z}$ is the number of targets formed per star forming mass.
 \begin{equation}
-    \mathcal{R}_{\rm target, Z} =  N_{\rm target, Z} / M_{\rm SF, Z}.
+    \mathcal{R}_{\rm target, Z} =  \frac{N_{\rm target, Z}}{ M_{\rm SF, Z} }.
 \end{equation}
-The number of targets in our sample at a metallicity $Z$ can be written simply as the sum of the targets' weights:
+In reality, this integral is instead approximated as a sum over the metallicity bins that we use in our simulation.
+The number of targets in our sample at a metallicity $Z$, $N_{\rm target, Z}$, can be written simply as the sum of the targets' weights:
 \begin{equation}
@@
 \end{equation}
-where $w_i$ is the STROOPWAFEL weight assigned to a binary, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise 0.
-The total star forming mass at a metallicity $Z$ can be written as
+where $w_i$ is the adaptive importance sampling weight assigned to the binary by STROOPWAFEL, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise $0$.
+
+The total star forming mass at a metallicity $Z$, $M_{\rm SF, Z}$, can be written as
 \begin{equation}
@@
 \end{equation}
-where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass that COMPAS samples from given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
-The cuts applied to the distributions mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass is sampled from.
+where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
+The cuts applied to the distributions, mainly because only massive stars are sampled, mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass in the galaxy is sampled from.
 
 \subsection{Total star forming mass in the Milky Way}
-It is important to distinguish between the \textit{total} star forming mass in the Milky Way and the \textit{current} star forming mass in the Milky Way.
+It is important to distinguish between the \textit{total} star forming mass over the Milky Way's history and the \textit{current} star forming mass in the Milky Way.
 Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass.
-\citet{Licquia+2014} find that the total stellar mass today in the Milky Way disc is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$.
+\citet{Licquia+2015} find that the total stellar mass today in the Milky Way is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$.
 This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs.
@@
 \begin{equation}\label{eq:m_SF_MW}
-    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
+    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm \odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
 \end{equation}
@@
 \begin{equation}
-    \avg{m}_{\rm SF, total} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(t) \int_{0.01}^{200} \zeta(m)\ m \dd{m} \dd{t},
+    \avg{m}_{\rm SF, total} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.01}^{200} \zeta(m)\ m \dd{m} \dd{\tau},
 \end{equation}
-where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.\,4]{Frankel+2018}.
+where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.~4]{Frankel+2018}.
 The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)

### 2021-05-08 simulation/src/galaxy.py
improve galaxy comments

@@ -6,11 +6,140 @@ from scipy.special import lambertw
 __all__ = ["simulate_mw"]
 
 
+def draw_lookback_times(size, tm=12*u.Gyr, tsfr=6.8*u.Gyr):
+    """Inverse CDF sampling of lookback times using Frankel+2018 Eq. 4
+
+    Parameters
+    ----------
+    size : `int`
+        How many samples to draw
+    tsfr : `float`
+        Model parameter fit in Frankel+2018
+    tm : `float`, optional
+        Age of Milky Way, by default 12*u.Gyr
+
+    Returns
+    -------
+    tau: `float/array`
+        Random lookback times
+    """
+    # draw a random uniform variable
+    U = np.random.rand(size)
+
+    # compute the normalising coefficient
+    Nt = 1 / quad(lambda x: np.exp(-(tm.value - x) / tsfr.value),
+                  0, tm.value)[0]
+
+    # work out lookback times
+    tau = tm + tsfr * np.log((Nt * tsfr.value + U - 1) / (Nt * tsfr.value))
+    return tau
+
+
+def draw_radii(size, t, alpha=0.3):
+    """Inverse CDF sampling of lookback times using Frankel+2018 Eq. 5
+
+    Parameters
+    ----------
+    size : `int`
+        How many samples to draw
+    alpha : `float`, optional
+        Disc inside-out growth parameter, by default 0.3
+
+    Returns
+    -------
+    R: `float/array`
+        Random Galactocentric radius
+    """
+    # draw a random uniform variable
+    U = np.random.rand(size)
+
+    R = - 4 * u.kpc * (1 - alpha * (t / (8 * u.Gyr)))\
+        * (lambertw((U - 1) / np.exp(1), k=-1).real + 1)
+    return R
+
+
+def draw_heights(size, zd=0.3*u.kpc):
+    """Inverse CDF sampling of lookback times using McMillan 2011 Eq. 3
+
+    Parameters
+    ----------
+    size : `int`
+        How many samples to draw
+    zd : `float`, optional
+        Disc scale height, by default 0.3*u.kpc
+
+    Returns
+    -------
+    z: `float/array`
+        Random heights
+    """
+    # draw a random uniform variable
+    U = np.random.rand(size)
+    z = np.random.choice([-1, 1], len(U)) * zd * np.log(1 - U)
+    return z
+
[…]

### 2021-05-08 simulation/src/galaxy.py
fix the things I broke in galaxy

@@ -127,7 +127,7 @@ def distance_from_earth(R, z, theta, Rsun=8.2*u.kpc):
 
     Returns
     -------
-    D : `float/array` 
+    D : `float/array`
         Distances
     """
     D = np.sqrt(z**2 + R**2 + Rsun**2 - 2 * Rsun * R * np.cos(theta))
@@ -186,8 +186,8 @@ def simulate_mw(n_binaries, tm=12 * u.Gyr, tsfr=6.8 * u.Gyr, alpha=0.3,
     tau = draw_lookback_times(n_binaries, tm=tm, tsfr=tsfr)
     R = draw_radii(n_binaries, tau, alpha=alpha)
     z = draw_heights(n_binaries, zd=zd)
-    Z = metallicity(R, tau, tm=tm, Fm=Fm, gradient=gradient, Rnow=Rnow,
-                    gamma=gamma, zsun=zsun)
+    Z = get_metallicity(R, tau, tm=tm, Fm=Fm, gradient=gradient, Rnow=Rnow,
+                        gamma=gamma, zsun=zsun)
     theta = 2 * np.pi * np.random.rand(n_binaries)
     D = distance_from_earth(R, z, theta)
 

### 2021-05-10 paper/figure_notebooks/bootstrap.py
move notebooks around

@@ -1,0 +1,262 @@
+import numpy as np
+from scipy.stats import gaussian_kde
+from scipy.interpolate import interp1d
+
+
+def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None,
+                     bootstraps=200, x_count=500, log_scale=(False, False),
+                     color="tab:blue", label=None, **kwargs):
+    """Create a bootstrapped weighted KDE plot.
+
+    Parameters
+    ----------
+    variable : `float/array`
+        Variable that you want to make a KDE of.
+    weights : 'float/array'
+        Weights associated with each variable (see all to 1 for unweighted)
+    seeds : `int/array`
+        Seeds that make the binaries in COMPAS
+    ax : `matplotlib Axis`
+        Axis on which to plot
+    bw_adjust : `float`, optional
+        Factor by which to adjust the bandwidth, by default None
+    bootstraps : `int`, optional
+        How many bootstraps to do, by default 200
+    x_count : `int`, optional
+        How many x values to evaluate at, by default 500
+    log_scale : `tuple`, optional
+        Whether each axis should be log scaled, by default (False, False)
+    color : `str`, optional
+        Colour for the KDE, by default "tab:blue"
+    label : `str`, optional
+        Label for the plotted KDE, by default None
+
+    Returns
+    -------
+    ax : `matplotlib Axis`
+        Axis on which KDE is plotted
+    """
+
+    # store the KDE values for each bootstrap
+    kde_vals = np.zeros((bootstraps, x_count))
+
+    # make everything unique and adjust weights
+    _, uni_index, uni_count = np.unique(seeds,
+                                        return_index=True, return_counts=True)
+    variable = variable[uni_index]
+    weights = weights[uni_index] * uni_count
+
+    # record indices to sample from
+    indices = np.arange(len(variable))
+
+    # decide on x values to evaluate at (based on log scaling)
+    if log_scale[0]:
+        print("WARNING: I think this doesn't work", variable)
+        x_vals = np.logspace(np.log10(np.min(variable)),
+                             np.log10(np.max(variable)), x_count)
+    else:
+        x_vals = np.linspace(np.min(variable), np.max(variable), x_count)
+
+    # perform bootstrapping
+    for i in range(bootstraps):
+        # sample indices
[…]

### 2021-05-10 paper/figure_notebooks/seaborn_utility.py

@@ -1,0 +1,329 @@
+import operator
+import math
+
+from matplotlib.colors import to_rgba
+import matplotlib
+import numpy as np
+
+"""This file is copied from Seaborn source to reproduce cmaps"""
+
+
+def cmap_from_colour(colour):
+    r, g, b, _ = to_rgba(colour)
+    h, s, _ = rgb_to_husl(r, g, b)
+    xx = np.linspace(-1, 1, int(1.15 * 256))[:256]
+    ramp = np.zeros((256, 3))
+    ramp[:, 0] = h
+    ramp[:, 1] = s * np.cos(xx)
+    ramp[:, 2] = np.linspace(35, 80, 256)
+    colors = np.clip([husl_to_rgb(*hsl) for hsl in ramp], 0, 1)
+    return matplotlib.colors.ListedColormap(colors[::-1])
+
+
+m = [
+    [3.2406, -1.5372, -0.4986],
+    [-0.9689, 1.8758, 0.0415],
+    [0.0557, -0.2040, 1.0570]
+]
+
+m_inv = [
+    [0.4124, 0.3576, 0.1805],
+    [0.2126, 0.7152, 0.0722],
+    [0.0193, 0.1192, 0.9505]
+]
+
+# Hard-coded D65 illuminant
+refX = 0.95047
+refY = 1.00000
+refZ = 1.08883
+refU = 0.19784
+refV = 0.46834
+lab_e = 0.008856
+lab_k = 903.3
+
+
+# Public API
+
+def husl_to_rgb(h, s, l):
+    return lch_to_rgb(*husl_to_lch([h, s, l]))
+
+
+def husl_to_hex(h, s, l):
+    return rgb_to_hex(husl_to_rgb(h, s, l))
+
+
+def rgb_to_husl(r, g, b):
+    return lch_to_husl(rgb_to_lch(r, g, b))
+
+
+def hex_to_husl(hex):
+    return rgb_to_husl(*hex_to_rgb(hex))
+
+
+def huslp_to_rgb(h, s, l):
+    return lch_to_rgb(*huslp_to_lch([h, s, l]))
+
+
+def huslp_to_hex(h, s, l):
+    return rgb_to_hex(huslp_to_rgb(h, s, l))
+
+
+def rgb_to_huslp(r, g, b):
+    return lch_to_huslp(rgb_to_lch(r, g, b))
+
+
+def hex_to_huslp(hex):
[…]

### 2021-05-10 paper/figure_notebooks/verification_binaries.py

@@ -1,0 +1,184 @@
+import astropy.units as u
+
+
+"""A list of the LISA verification binaries from Kupfer+18 (Table 1 and 2)"""
+
+verification_binaries = [
+    {
+        "label": "HM Cnc",
+        "f_GW": 6.22 * u.mHz,
+        "snr": 211.1,
+        "l_gal": 206.9246 * u.deg,
+        "b_gal": 23.3952 * u.deg,
+        "m_1": 0.55 * u.Msun,
+        "m_2": 0.27 * u.Msun,
+        "i": 38 * u.deg,
+        "dist": 5000 * u.pc,
+    },
+    {
+        "label": "V407 Vul",
+        "f_GW": 3.51 * u.mHz,
+        "snr": 169.7,
+        "l_gal": 57.7281 * u.deg,
+        "b_gal": 6.4006 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.177 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1786 * u.pc,
+    },
+    {
+        "label": "ES Cet",
+        "f_GW": 3.22 * u.mHz,
+        "snr": 154.3,
+        "l_gal": 168.9684 * u.deg,
+        "b_gal": -65.8632 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.161 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1584 * u.pc,
+    },
+    {
+        "label": "SDSS J135154.46–064309.0",
+        "f_GW": 2.12 * u.mHz,
+        "snr": 21.8,
+        "l_gal": 328.5021 * u.deg,
+        "b_gal": 53.1240 * u.deg,
+        "m_1": 0.8 * u.Msun,
+        "m_2": 0.1 * u.Msun,
+        "i": 60 * u.deg,
+        "dist": 1317 * u.pc,
+    },
+    {
+        "label": "AM CVn",
+        "f_GW": 1.94 * u.mHz,
+        "snr": 101.2,
+        "l_gal": 140.2343 * u.deg,
+        "b_gal": 78.9382 * u.deg,
+        "m_1": 0.68 * u.Msun,
+        "m_2": 0.125 * u.Msun,
+        "i": 43 * u.deg,
+        "dist": 299 * u.pc,
+    },
+    {
[…]

### 2021-05-10 simulation/notebooks/bootstrap.py

@@ -1,262 +1,0 @@
-import numpy as np
-from scipy.stats import gaussian_kde
-from scipy.interpolate import interp1d
-
-
-def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None,
-                     bootstraps=200, x_count=500, log_scale=(False, False),
-                     color="tab:blue", label=None, **kwargs):
-    """Create a bootstrapped weighted KDE plot.
-
-    Parameters
-    ----------
-    variable : `float/array`
-        Variable that you want to make a KDE of.
-    weights : 'float/array'
-        Weights associated with each variable (see all to 1 for unweighted)
-    seeds : `int/array`
-        Seeds that make the binaries in COMPAS
-    ax : `matplotlib Axis`
-        Axis on which to plot
-    bw_adjust : `float`, optional
-        Factor by which to adjust the bandwidth, by default None
-    bootstraps : `int`, optional
-        How many bootstraps to do, by default 200
-    x_count : `int`, optional
-        How many x values to evaluate at, by default 500
-    log_scale : `tuple`, optional
-        Whether each axis should be log scaled, by default (False, False)
-    color : `str`, optional
-        Colour for the KDE, by default "tab:blue"
-    label : `str`, optional
-        Label for the plotted KDE, by default None
-
-    Returns
-    -------
-    ax : `matplotlib Axis`
-        Axis on which KDE is plotted
-    """
-
-    # store the KDE values for each bootstrap
-    kde_vals = np.zeros((bootstraps, x_count))
-
-    # make everything unique and adjust weights
-    _, uni_index, uni_count = np.unique(seeds,
-                                        return_index=True, return_counts=True)
-    variable = variable[uni_index]
-    weights = weights[uni_index] * uni_count
-
-    # record indices to sample from
-    indices = np.arange(len(variable))
-
-    # decide on x values to evaluate at (based on log scaling)
-    if log_scale[0]:
-        print("WARNING: I think this doesn't work", variable)
-        x_vals = np.logspace(np.log10(np.min(variable)),
-                             np.log10(np.max(variable)), x_count)
-    else:
-        x_vals = np.linspace(np.min(variable), np.max(variable), x_count)
-
-    # perform bootstrapping
-    for i in range(bootstraps):
-        # sample indices
[…]

### 2021-05-10 simulation/notebooks/seaborn_utility.py

@@ -1,329 +1,0 @@
-import operator
-import math
-
-from matplotlib.colors import to_rgba
-import matplotlib
-import numpy as np
-
-"""This file is copied from Seaborn source to reproduce cmaps"""
-
-
-def cmap_from_colour(colour):
-    r, g, b, _ = to_rgba(colour)
-    h, s, _ = rgb_to_husl(r, g, b)
-    xx = np.linspace(-1, 1, int(1.15 * 256))[:256]
-    ramp = np.zeros((256, 3))
-    ramp[:, 0] = h
-    ramp[:, 1] = s * np.cos(xx)
-    ramp[:, 2] = np.linspace(35, 80, 256)
-    colors = np.clip([husl_to_rgb(*hsl) for hsl in ramp], 0, 1)
-    return matplotlib.colors.ListedColormap(colors[::-1])
-
-
-m = [
-    [3.2406, -1.5372, -0.4986],
-    [-0.9689, 1.8758, 0.0415],
-    [0.0557, -0.2040, 1.0570]
-]
-
-m_inv = [
-    [0.4124, 0.3576, 0.1805],
-    [0.2126, 0.7152, 0.0722],
-    [0.0193, 0.1192, 0.9505]
-]
-
-# Hard-coded D65 illuminant
-refX = 0.95047
-refY = 1.00000
-refZ = 1.08883
-refU = 0.19784
-refV = 0.46834
-lab_e = 0.008856
-lab_k = 903.3
-
-
-# Public API
-
-def husl_to_rgb(h, s, l):
-    return lch_to_rgb(*husl_to_lch([h, s, l]))
-
-
-def husl_to_hex(h, s, l):
-    return rgb_to_hex(husl_to_rgb(h, s, l))
-
-
-def rgb_to_husl(r, g, b):
-    return lch_to_husl(rgb_to_lch(r, g, b))
-
-
-def hex_to_husl(hex):
-    return rgb_to_husl(*hex_to_rgb(hex))
-
-
-def huslp_to_rgb(h, s, l):
-    return lch_to_rgb(*huslp_to_lch([h, s, l]))
-
-
-def huslp_to_hex(h, s, l):
-    return rgb_to_hex(huslp_to_rgb(h, s, l))
-
-
-def rgb_to_huslp(r, g, b):
-    return lch_to_huslp(rgb_to_lch(r, g, b))
-
-
-def hex_to_huslp(hex):
[…]

### 2021-05-10 simulation/notebooks/verification_binaries.py

@@ -1,184 +1,0 @@
-import astropy.units as u
-
-
-"""A list of the LISA verification binaries from Kupfer+18 (Table 1 and 2)"""
-
-verification_binaries = [
-    {
-        "label": "HM Cnc",
-        "f_GW": 6.22 * u.mHz,
-        "snr": 211.1,
-        "l_gal": 206.9246 * u.deg,
-        "b_gal": 23.3952 * u.deg,
-        "m_1": 0.55 * u.Msun,
-        "m_2": 0.27 * u.Msun,
-        "i": 38 * u.deg,
-        "dist": 5000 * u.pc,
-    },
-    {
-        "label": "V407 Vul",
-        "f_GW": 3.51 * u.mHz,
-        "snr": 169.7,
-        "l_gal": 57.7281 * u.deg,
-        "b_gal": 6.4006 * u.deg,
-        "m_1": 0.8 * u.Msun,
-        "m_2": 0.177 * u.Msun,
-        "i": 60 * u.deg,
-        "dist": 1786 * u.pc,
-    },
-    {
-        "label": "ES Cet",
-        "f_GW": 3.22 * u.mHz,
-        "snr": 154.3,
-        "l_gal": 168.9684 * u.deg,
-        "b_gal": -65.8632 * u.deg,
-        "m_1": 0.8 * u.Msun,
-        "m_2": 0.161 * u.Msun,
-        "i": 60 * u.deg,
-        "dist": 1584 * u.pc,
-    },
-    {
-        "label": "SDSS J135154.46–064309.0",
-        "f_GW": 2.12 * u.mHz,
-        "snr": 21.8,
-        "l_gal": 328.5021 * u.deg,
-        "b_gal": 53.1240 * u.deg,
-        "m_1": 0.8 * u.Msun,
-        "m_2": 0.1 * u.Msun,
-        "i": 60 * u.deg,
-        "dist": 1317 * u.pc,
-    },
-    {
-        "label": "AM CVn",
-        "f_GW": 1.94 * u.mHz,
-        "snr": 101.2,
-        "l_gal": 140.2343 * u.deg,
-        "b_gal": 78.9382 * u.deg,
-        "m_1": 0.68 * u.Msun,
-        "m_2": 0.125 * u.Msun,
-        "i": 43 * u.deg,
-        "dist": 299 * u.pc,
-    },
-    {
[…]

### 2021-05-13 simulation/src/galaxy.py
update galaxy model and create new plots

@@ -8,7 +8,7 @@ __all__ = ["simulate_mw"]
 
 
 def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr,
-                        tsfr=6.8*u.Gyr):
+                        tsfr=6.8*u.Gyr, old=False):
     """Inverse CDF sampling of lookback times. Thin and thick discs uses
     Frankel+2018 Eq.4, separated at 8 Gyr. The bulge matches the distribution
     in Fig.7 of Bovy+19 but accounts for sample's bias.
@@ -32,7 +32,7 @@ def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr,
     if component == "thin_disc":
         U = np.random.rand(size)
         norm = 1 / quad(lambda x: np.exp(-(tm.value - x) / tsfr.value),
-                        0, 8)[0]
+                        0, 8 if not old else 12)[0]
         tau = tsfr * np.log((U * np.exp(tm / tsfr)) / (norm * tsfr.value) + 1)
     elif component == "thick_disc":
         U = np.random.rand(size)
@@ -85,7 +85,7 @@ def draw_heights(size, z_d=0.3*u.kpc):
         Random heights
     """
     U = np.random.rand(size)
-    z = np.random.choice([-1, 1], len(U)) * z_d * np.log(1 - U)
+    z = np.random.choice([-1, 1], size) * z_d * np.log(1 - U)
     return z
 
 
@@ -150,7 +150,7 @@ def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
                 tm=12 * u.Gyr, tsfr=6.8 * u.Gyr, alpha=0.3,
                 zd=0.3 * u.kpc, Fm=-1, gradient=-0.075 / u.kpc,
                 Rnow=8.7 * u.kpc, gamma=0.3, zsun=0.0142, Rsun=8.2 * u.kpc,
-                ret_pos=False, lookback=True):
+                ret_pos=False, lookback=True, old=False):
     """Draw a sample of birth times, distances and metallicities from a Milky
     Way model.
 
@@ -208,10 +208,10 @@ def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
     R = [None for i in range(len(components))]
     z = [None for i in range(len(components))]
     for i, com in enumerate(components):
-        tau[i] = draw_lookback_times(sizes[i], tm=tm, tsfr=tsfr, component=com)
[…]

### 2021-05-14 paper/tex/sections/methods.tex
rename figures
overhaul milky way model section with new details

@@
 
-In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample of the synthesised binaries described in Section~\ref{sec:COMPAS_explained}.
-For the distribution of the binaries, we make the simplification that the Milky Way is composed of only a single disc.
-We do not find that adding other components would significantly alter our results.
+In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample drawn (with replacement) from the synthesised binaries described in Section~\ref{sec:COMPAS_explained}.
 
-Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
-We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.
+\subsubsection{Milky Way model}\label{sec:mw_model}
+We assume that the Milky Way is composed of a thin disc, thick disc and a central bar/bulge.
+For each of these components we use a separate lookback time, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
+\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.91 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.17 \times 10^{10} \unit{M_\odot}$, which we split equally between the thin and thick disc.
+\todo{need citation for equal mass discs}
 
-\subsubsection{Milky Way disc model}\label{sec:disc_model}
-
-For the Milky Way thin disc, we use the model from \citet{Frankel+2018}.
-The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way.
-They did this by fitting the model to a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and Gaia \citep{GaiaCollaboration+2016}.
-The result of this work is a model for the Milky Way that is calibrated to observations and which includes the star formation history, radial birth profile and chemical enrichment history of the galaxy.
-We can therefore use this model to place binaries randomly in space and time and match these positions to a metallicity.
-
-The star formation history is given by the following  \citep[][Eq. 2]{Frankel+2018}
-\begin{equation}\label{eq:galaxy_tau}
+\textit{Star formation history:} For the thin and thick discs we use the star formation history given by \citet[][Eq.~2]{Frankel+2018},
+\begin{equation}\label{eq:thin_disc_tau}
     p(\tau) \propto \exp \qty(-\frac{(\tau_m - \tau)}{\tau_{\rm SFR}}),
 \end{equation}
-where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ was fit by \citet{Frankel+2018}.
-The radial birth profile of the galaxy is conditional upon its age and is given as \citep[][Eq.
-5]{Frankel+2018}
+where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ is the star formation timescale.
+Following \citet{Frankel+2018}, we assume that there is a transition from thick disc star formation to thin disc star formation $8 \unit{Gyr}$ ago and apply a sharp transition at this point.
+This has been shown to still reproduce the Milky Way structure well despite its simplicity \citep{Sharma+2020} \todo{I could write this bit better}.
+Therefore, for the thin disc we normalise this distribution on the range $[0, 8) \unit{Gyr}$ and for the thick disc we normalise on the range $[8, 12] \unit{Gyr}$.
+
+For the bulge, we base our distribution on the one presented in \citet[][Fig.~7]{Bovy+2019}.
+We adapt this distribution to account for the possible bias of the sample, where fainter older stars are not observed \todo{I don't understand this well enough to write}.
+We therefore approximate the distribution using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+
+\textit{Radial distribution:} For each of the three components we employ the same single exponential distribution (but with different scale lengths)
 \begin{equation}\label{eq:galaxy_R}
-    p(R_0 \vert \tau) = \exp(-\frac{R_0}{R_{\rm exp}(\tau)}) \frac{R_0}{[R_{\rm exp}(\tau)]^2},
+    p(R) = \exp(-\frac{R}{R_d}) \frac{R}{R_d^2},
 \end{equation}
-where $R_0$ is the birth Galactocentric radius, and\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}
+where $R$ is the Galactocentric radius and $R_d$ is the scale length of the component.
+For the thin disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
 \begin{equation}
@@
 \end{equation}
-where $\alpha_{R_{\rm exp}} = 0.3$ was fit by \citet{Frankel+2018}. Finally, the metallicity-radius-time relation is given as \citep[][Eq. 7]{Frankel+2018}
+where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}.
+This scale length accounts for the inside-out growth of the thin disc and hence is age dependent.
+We assume $R_d = (1 / 0.43) \unit{kpc}$ for the thick disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bulge \citep{Bovy+2019}.
+
+\textit{Vertical distribution}: Similar to the radial distribution, we use the same single exponential distribution (but with different scale heights) for each component
+\begin{equation}\label{eq:galaxy_z}
+    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
+\end{equation}
+where $z$ is the height above the Galactic plane and $z_d$ is the scale height.
+We set $z_d = 0.3 \unit{kpc}$ for the thin disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the thick disc \citep{Bovy+2016}.
+For the bulge, we set $z_d = 1.5 \unit{kpc}$ such that the probability of forming a star approaches zero at approximately the co-rotation radius of the Galactic bar/bulge \citep{Bovy+2019}.
+
+\textit{Metallicity-radius-time relation:} Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
+We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.
+For this purpose, we apply the metallicity-radius-time relation from \citet{Frankel+2018}.
+The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
+
+The metallicity-radius-time relation is given by \citep[][Eq. 7]{Frankel+2018}
 \begin{equation}\label{eq:galaxy_FeH}
@@
 \end{equation}
-$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$ and $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ are fit by \citet{Frankel+2018}.
-We can convert this to our representation of metallicity using \citep[e.g][]{Bertelli+1994}
+$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ set the time dependence of the chemical enrichment.
+We can convert this to the representation of metallicity that we use in this paper by applying \citep[e.g][]{Bertelli+1994}
 \begin{equation}\label{eq:galaxy_FeH_to_Z}
@@
 \end{equation}
-Additionally, since this model does not treat the vertical structure of the Milky Way disc, we can supplement it with the vertical distribution from \citet{McMillan+2011},
-\begin{equation}\label{eq:galaxy_z}
-    p(\abs{z}) = \frac{1}{z_d} \exp\qty(-\frac{z}{z_d}),
-\end{equation}
-where $z$ is the height above the Galactic plane and $z_d = 0.3 \unit{kpc}$.
-Equations \ref{eq:galaxy_tau}-\ref{eq:galaxy_z} summarise the model that we use for the Milky Way disc and we illustrate these distributions in Fig.~\ref{fig:galaxy_schematic}.
+
+Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
+    \caption{A schematic illustrating how we create a mock Milky Way galaxy.
+On the left, we show the various individual distributions for the different parameters.
+In the star formation history distribution, we also plot the separate distributions of each component with dotted lines to more clearly explain the shape.
+On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as point, where the colour of each point represents its metallicity.
+The top panel shows a side-on view and the bottom panel shows a view from above.}
+    \label{fig:galaxy_schematic}
+\end{figure*}
 
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:disc_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
 This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{galaxy_diagram.png}
-    \caption{A schematic showing how we create a mock Milky Way disc.
-On the left, we show the various distributions presented in \citet{Frankel+2018} and \citet{McMillan+2011}.
-On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points.
-The colour of each point represents its metallicity (with $Z \in [0.0001, 0.022]$).
-The top panel shows a side-on view and the bottom panel shows a view from above.}
-    \label{fig:galaxy_schematic}
-\end{figure*}
 

### 2021-05-17 paper/tex/paper.tex
updates to appendix
add coauthors and acknowledgements

@@
 \newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
-\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
+\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
 
@@
 \author[0000-0001-9336-2825]{S. E. de Mink}
+\affiliation{\mpa}
+\affiliation{\UoA}
+\affiliation{\cfa}
+
+\author[0000-0002-6411-8695]{N. Frankel}
+\affiliation{Max Planck Institute for Astronomy, Königstuhl 17, D-69117 Heidelberg, Germany}
+
+\author[0000-0001-5484-4987]{L. van Son}
 \affiliation{\cfa}
 \affiliation{\mpa}
-\affiliation{\UoA}
 
-\author{...TBD}
+\author[0000-0001-7969-1569]{S. Justham}
+\affiliation{School of Astronomy \& Space Science, University of the Chinese Academy of Sciences, Beijing 100012, China}
+\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
 
 \begin{abstract}{
-    % \input{sections/abstract.tex}
-    \noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\
+    \input{sections/abstract.tex}
 }
@@
 
-\acknowledgments{This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
+\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr and the members of the COMPAS collaboration for insightful discussions.
+This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.

### 2021-05-17 paper/tex/sections/methods.tex
add coauthors and acknowledgements

@@
 \end{equation}
-where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as it provides a better fit (correspondence with Neige Frankel)}.
+where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as NF finds that it provides a better fit to the original data}.
 This scale length accounts for the inside-out growth of the thin disc and hence is age dependent.

### 2021-05-17 paper/tex/sections/discussion.tex
move distinguishing section to discussion
updates to methods after selma feedback

@@
 \subsection{Caveats}
+Separate into three sections
+
+GCs don't produce DNSs well but the other ones yes
+
+Contribution of metal poor stars is not well known
+
 \begin{itemize}
@@
     \item No models for high $Z$ values in Frankel
+    \item Other channels
     \item Only a single disc for the Milky Way
@@
 
-\subsection{Can we distinguish them?}
+\subsection{Identification of GW sources}
+It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
+
+\subsubsection{Distinguishing from WDWD population}
+\subsubsection{Separating BHBHs, BHNSs and NSNSs}

### 2021-05-17 paper/tex/sections/methods.tex
updates to methods after selma feedback

@@
 In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample drawn (with replacement) from the synthesised binaries described in Section~\ref{sec:COMPAS_explained}.
+Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
+We improve upon this as the first study to use an empirically-informed analytical model of the Milky Way that takes into account the galaxy's enrichment history by applying the metallicity-radius-time relation from \citet{Frankel+2018}.
+The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
+
+In Section~\ref{sec:mw_model}, we outline our model for the Milky Way with each of the various distributions and in Section~\ref{sec:combining_pop_gal} we explain how we combine our population of synthesised DCOs with the Milky Way model.
 
 \subsubsection{Milky Way model}\label{sec:mw_model}
-We assume that the Milky Way is composed of a thin disc, thick disc and a central bar/bulge.
-For each of these components we use a separate lookback time, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
-\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.91 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.17 \times 10^{10} \unit{M_\odot}$, which we split equally between the thin and thick disc.
-\todo{need citation for equal mass discs}
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
+    \caption{A schematic illustrating how we create a mock Milky Way galaxy.
+On the left, we show the various individual distributions for the different parameters.
+In the star formation history distribution, we also plot the separate distributions of each component with dotted lines to more clearly explain the shape.
+On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as point, where the colour of each point represents its metallicity.
+The top panel shows a side-on view and the bottom panel shows a view from above.}
+    \label{fig:galaxy_schematic}
+\end{figure*}
+
+Our model for the Milky Way accounts for the thin disc, thick disc and central bar/bulge.
+For each of these components we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
+\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the thin and thick disc.
+\todo{@Neige, do you have a suggestion for a citation for having equal mass thin/thick discs}.
 
@@
 Following \citet{Frankel+2018}, we assume that there is a transition from thick disc star formation to thin disc star formation $8 \unit{Gyr}$ ago and apply a sharp transition at this point.
-This has been shown to still reproduce the Milky Way structure well despite its simplicity \citep{Sharma+2020} \todo{I could write this bit better}.
-Therefore, for the thin disc we normalise this distribution on the range $[0, 8) \unit{Gyr}$ and for the thick disc we normalise on the range $[8, 12] \unit{Gyr}$.
+Despite its simplicity, this has been shown to reproduce the Milky Way age and abundance distributions well \citep{Sharma+2020} \todo{@Neige, is this justification correct/relaying the results of Sharma+2020 properly?}.
+Therefore, for the thin disc we normalise this distribution on the range $[0, 8] \unit{Gyr}$ and for the thick disc we normalise on the range $[8, 12] \unit{Gyr}$.
 
 For the bulge, we base our distribution on the one presented in \citet[][Fig.~7]{Bovy+2019}.
-We adapt this distribution to account for the possible bias of the sample, where fainter older stars are not observed \todo{I don't understand this well enough to write}.
+This model is fit using the data from APOGEE and Gaia as \citet{Frankel+2018}.
+\todo{@Neige, I need a sentence here to explain what biases we account for and so why we shift it.
+I recall it's something to do with fainter stars being missed and the bright ones not being part of the bulge but I can't articulate it very well, could you please help me with this?}.
 We therefore approximate the distribution using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
@@
 For the bulge, we set $z_d = 1.5 \unit{kpc}$ such that the probability of forming a star approaches zero at approximately the co-rotation radius of the Galactic bar/bulge \citep{Bovy+2019}.
+\todo{@Neige, did I justify the bulge/bar height correctly?}
 
-\textit{Metallicity-radius-time relation:} Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
-We improve upon this as the first study to use an analytical model of the Milky Way that takes into account the galaxy's enrichment history.
-For this purpose, we apply the metallicity-radius-time relation from \citet{Frankel+2018}.
-The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
-
-The metallicity-radius-time relation is given by \citep[][Eq. 7]{Frankel+2018}
+\textit{Metallicity-radius-time relation:} The relation is given by \citep[][Eq. 7]{Frankel+2018}
 \begin{equation}\label{eq:galaxy_FeH}
@@
 \end{equation}
-$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disk at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ set the time dependence of the chemical enrichment.
+$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disc at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ set the time dependence of the chemical enrichment.
 We can convert this to the representation of metallicity that we use in this paper by applying \citep[e.g][]{Bertelli+1994}
@@
 
+Although \citet{Frankel+2018} only fit this model for the thin disc, we use this same metallicity-radius-time relation for each component of the galaxy.
+\citet{Sharma+2020} showed that using a simple continuous model for both the thin and thick disc the Milky Way abundance distributions well and hence we can apply this same relation to the thick disc.
+\citet{Bovy+2019} show in Fig.~7 that the abundance distribution and chemical tracks of the stars in the bulge/bar follow the same track as those outside and hence we can use the same metallicity-radius-time relation.
+
 Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
 
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
-    \caption{A schematic illustrating how we create a mock Milky Way galaxy.
-On the left, we show the various individual distributions for the different parameters.
-In the star formation history distribution, we also plot the separate distributions of each component with dotted lines to more clearly explain the shape.
-On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as point, where the colour of each point represents its metallicity.
-The top panel shows a side-on view and the bottom panel shows a view from above.}
-    \label{fig:galaxy_schematic}
-\end{figure*}
-
-\subsubsection{Combining population and galaxy synthesis}
+\subsubsection{Combining population and galaxy synthesis}\label{sec:combining_pop_gal}
 

### 2021-05-17 paper/tex/sections/discussion.tex
last updates before sending out draft

@@
 \subsection{Caveats}
-Separate into three sections
+\todo{This section is only an outline for now}
 
-GCs don't produce DNSs well but the other ones yes
-
-Contribution of metal poor stars is not well known
-
+\subsubsection{Population Synthesis Caveats}
 \begin{itemize}
     \item Standard pop synth limitations
+    \item Other channels
+\end{itemize}
+
+\subsubsection{Galaxy Caveats}
+\begin{itemize}
     \item Systemic kicks
     \item No models for high $Z$ values in Frankel
-    \item Other channels
-    \item Only a single disc for the Milky Way
+    \item No halo or GC considered %GC don't produce NSNS well but other maybe (Kremer+??)
+    \item Contribution of metal-poor stars not well known
+\end{itemize}
+
+\subsubsection{Detection Caveats}
+\begin{itemize}
+    \item None come to mind...?
 \end{itemize}

### 2021-05-17 paper/tex/sections/methods.tex
last updates before sending out draft

@@
 In order to estimate a detection rate of DCOs with statistical uncertainties, we create a series of random instances of the Milky Way, each populated with a subsample drawn (with replacement) from the synthesised binaries described in Section~\ref{sec:COMPAS_explained}.
+
 Most previous studies that predict a detection rate for LISA place binaries in the Milky Way independently of their age or evolution.
 We improve upon this as the first study to use an empirically-informed analytical model of the Milky Way that takes into account the galaxy's enrichment history by applying the metallicity-radius-time relation from \citet{Frankel+2018}.
-The authors developed this model in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
+The authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
 
-In Section~\ref{sec:mw_model}, we outline our model for the Milky Way with each of the various distributions and in Section~\ref{sec:combining_pop_gal} we explain how we combine our population of synthesised DCOs with the Milky Way model.
+In Section~\ref{sec:mw_model}, we outline our model for the Milky Way and in Section~\ref{sec:combining_pop_gal} we explain how we combine our population of synthesised DCOs with this Milky Way model.
 
@@
 In the star formation history distribution, we also plot the separate distributions of each component with dotted lines to more clearly explain the shape.
-On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as point, where the colour of each point represents its metallicity.
+On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points, where the colour of each point represents its metallicity.
 The top panel shows a side-on view and the bottom panel shows a view from above.}

### 2021-05-17 paper/tex/sections/results.tex
move distinguishing section to discussion
rename figures
last updates before sending out draft

@@
+\todo{Note that the numbers/errors are subject to change in this section once the larger high Z simulations are done (thank you Floor!)}
+
 In this section we present our main results for the detectable LISA DCO population.
@@
     \centering
-    \includegraphics[width=\textwidth]{dcos_on_sc.png}
+    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
     \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where the panels correspond to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
@@
     \centering
-    \includegraphics[width=\textwidth]{dco_detections.pdf}
+    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
     \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
@@
 The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.}
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
+\todo{@ALL, ignore models P and Q for now}}
     \label{fig:detection_rates}
@@
 
-\tom{@Selma, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
+\todo{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
 We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke.
@@
 But we don't see an increase with $\alpha = 2.0$.
-Any thoughts?}
+Any thoughts?
+(I'm leaving thinking about this for now in case it changes with the new data haha)}
 % For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
@@
 \subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}
+
+\todo{This section is not currently up to date, waiting for new sims before writing more}
 
@@
 \subsubsection{Inspiral Time}
-Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times. \todo{finish this}
+Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{distribution_grid_4yr.pdf}
+    \includegraphics[width=\textwidth]{4_distribution_grid_4yr.pdf}
     \caption{Distributions for various parameters of the DCOs that are detectable in a 4 year LISA mission in our fiducial model.
@@
 
-\subsection{Distinguishing DCOs}
-\todo{}
-
 \subsection{Model variations}

### 2021-05-17 paper/tex/sections/comparisons.tex
rename figures

@@
 Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation}.
+We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation, perhaps @Stephen knows?}.
 
@@
     \centering
-    \includegraphics[width=\textwidth]{compare_dco_1.png}
+    \includegraphics[width=\textwidth]{5_compare_dco_1.png}
 
@@
 
-    \includegraphics[width=\textwidth]{compare_dco_2.png}
+    \includegraphics[width=\textwidth]{5_compare_dco_2.png}
     \caption{A table comparing previous studies of a similar nature to this work.

### 2021-05-17 paper/tex/paper.tex
Updates from Overleaf
new title

@@
 
-\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}
+% selma's newest catchy one
+\title{Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries}
+
+% selma suggested removing BHNS
+% \title{Predictions for neutron star and black hole binaries with LISA}
+
+% original
+%\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}
 
@@
 \newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
-\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
+\newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
 
@@
 \affiliation{\mpa}
-\affiliation{\UoA}
+\affiliation{\UvA}
 \affiliation{\cfa}
@@
 
-\author[0000-0001-5484-4987]{L. van Son}
+\author[0000-0001-5484-4987]{L.A.C. van Son}
 \affiliation{\cfa}
+\affiliation{\UvA}
 \affiliation{\mpa}
@@
 \affiliation{School of Astronomy \& Space Science, University of the Chinese Academy of Sciences, Beijing 100012, China}
-\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}
+\affiliation{\UvA}
 

### 2021-05-19 simulation/output/combine_output.py
add eccentricity prior SN 2

@@ -82,10 +82,11 @@ for bt in ["BHBH", "BHNS", "NSNS"]:
                     "m_2_ZAMS": floor["doubleCompactObjects"]["M2ZAMS"][...].squeeze()[seeds_index],
                     "MT1_case": floor["doubleCompactObjects"]["PrimaryMTCase"][...].squeeze()[seeds_index],
                     "MT2_case": floor["doubleCompactObjects"]["SecondaryMTCase"][...].squeeze()[seeds_index],
-                    "a_pre_SN2": floor["doubleCompactObjects"]["separationPrior2ndSN"][...].squeeze()[seeds_index],
                     "a_ZAMS": floor["doubleCompactObjects"]["separationInitial"][...].squeeze()[seeds_index],
+                    "a_pre_SN2": floor["doubleCompactObjects"]["separationPrior2ndSN"][...].squeeze()[seeds_index],
                     "kick_1": floor["doubleCompactObjects"]["drawnKick1"][...].squeeze()[seeds_index],
                     "kick_2": floor["doubleCompactObjects"]["drawnKick2"][...].squeeze()[seeds_index],
+                    "e_pre_SN2": floor["doubleCompactObjects"]["eccentricityPrior2ndSN"][...].squeeze()[seeds_index],
                     "channel": channels
                 }
 

### 2021-06-02 paper/tex/sections/introduction.tex

@@
 The detection of the mergers of these binaries have offered exciting insights into the evolution and endpoints of massive stars.
+\floor{I would change it to something like: Since the first direct observation of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars (e.g.
+CITE GWTC-2 Population inference paper).}
 

### 2021-06-02 paper/tex/sections/methods.tex
Updates from Overleaf

@@
 We improve upon this as the first study to use an empirically-informed analytical model of the Milky Way that takes into account the galaxy's enrichment history by applying the metallicity-radius-time relation from \citet{Frankel+2018}.
-The authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017} and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
+The authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017}.
+%and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
 
@@
     \caption{A schematic illustrating how we create a mock Milky Way galaxy.
-On the left, we show the various individual distributions for the different parameters.
-In the star formation history distribution, we also plot the separate distributions of each component with dotted lines to more clearly explain the shape.
-On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points, where the colour of each point represents its metallicity.
-The top panel shows a side-on view and the bottom panel shows a view from above.}
+The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
+    On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points colour coded by metallicity.
+The top panel shows a side-on view and the bottom panel shows a face-on view.}
     \label{fig:galaxy_schematic}
@@
 
-Our model for the Milky Way accounts for the thin disc, thick disc and central bar/bulge.
-For each of these components we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
-\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the thin and thick disc.
-\todo{@Neige, do you have a suggestion for a citation for having equal mass thin/thick discs}.
+Our model for the Milky Way accounts for the low-$\alpha$ disc, high-$\alpha$ disc and central bar/bulge.
+For each of these components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
+\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-$\alpha$ discs \citep[e.g.,][]{Snaith+2014}.
 
-\textit{Star formation history:} For the thin and thick discs we use the star formation history given by \citet[][Eq.~2]{Frankel+2018},
+\textit{Star formation history:} 
+We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-$\alpha$ disks, where the two disks transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
 \begin{equation}\label{eq:thin_disc_tau}
@@
 where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ is the star formation timescale.
-Following \citet{Frankel+2018}, we assume that there is a transition from thick disc star formation to thin disc star formation $8 \unit{Gyr}$ ago and apply a sharp transition at this point.
-Despite its simplicity, this has been shown to reproduce the Milky Way age and abundance distributions well \citep{Sharma+2020} \todo{@Neige, is this justification correct/relaying the results of Sharma+2020 properly?}.
-Therefore, for the thin disc we normalise this distribution on the range $[0, 8] \unit{Gyr}$ and for the thick disc we normalise on the range $[8, 12] \unit{Gyr}$.
 
-For the bulge, we base our distribution on the one presented in \citet[][Fig.~7]{Bovy+2019}.
-This model is fit using the data from APOGEE and Gaia as \citet{Frankel+2018}.
-\todo{@Neige, I need a sentence here to explain what biases we account for and so why we shift it.
-I recall it's something to do with fainter stars being missed and the bright ones not being part of the bulge but I can't articulate it very well, could you please help me with this?}.
-We therefore approximate the distribution using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate.
+But the bulge was shown to contain stars with a range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
+To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$
 
@@
 where $R$ is the Galactocentric radius and $R_d$ is the scale length of the component.
-For the thin disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
+For the low-$\alpha$ disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
 \begin{equation}
@@
 where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as NF finds that it provides a better fit to the original data}.
-This scale length accounts for the inside-out growth of the thin disc and hence is age dependent.
-We assume $R_d = (1 / 0.43) \unit{kpc}$ for the thick disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bulge \citep{Bovy+2019}.
+This scale length accounts for the inside-out growth of the low-$\alpha$ disc and hence is age dependent.
+We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-$\alpha$ disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
 
@@
 where $z$ is the height above the Galactic plane and $z_d$ is the scale height.
-We set $z_d = 0.3 \unit{kpc}$ for the thin disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the thick disc \citep{Bovy+2016}.
+We set $z_d = 0.3 \unit{kpc}$ for the low-$\alpha$ disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the high-$\alpha$ disc \citep{Bovy+2016}.
+\todo{Neige to Tom: for bar, I will think more for your bar scale-height, but the exact value should not change your results much since they will only slightly change the distance distribution of your sources, but not the rates nor the normalization.}
 For the bulge, we set $z_d = 1.5 \unit{kpc}$ such that the probability of forming a star approaches zero at approximately the co-rotation radius of the Galactic bar/bulge \citep{Bovy+2019}.
-\todo{@Neige, did I justify the bulge/bar height correctly?}
+\todo{@Neige, did I justify the bulge/bar height correctly?
+A: The vertical distribution should not influence at which radius the bar should stop forming stars -- more later}
 
@@
 
-Although \citet{Frankel+2018} only fit this model for the thin disc, we use this same metallicity-radius-time relation for each component of the galaxy.
-\citet{Sharma+2020} showed that using a simple continuous model for both the thin and thick disc the Milky Way abundance distributions well and hence we can apply this same relation to the thick disc.
-\citet{Bovy+2019} show in Fig.~7 that the abundance distribution and chemical tracks of the stars in the bulge/bar follow the same track as those outside and hence we can use the same metallicity-radius-time relation.
+Although \citet{Frankel+2018} only fit this model for the low-$\alpha$ disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disk and the bar, but focusing on the chemical tracks more representative to the inner disk and large ages.
+\citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-$\alpha$ discs, the Milky Way abundance distributions could be well reproduced.
+Empirically, the chemical tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
 

### 2021-06-04 simulation/src/galaxy.py
galaxy code cleanup

@@ -8,7 +8,7 @@ __all__ = ["simulate_mw"]
 
 
 def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr,
-                        tsfr=6.8*u.Gyr, old=False):
+                        tsfr=6.8*u.Gyr):
     """Inverse CDF sampling of lookback times. Thin and thick discs uses
     Frankel+2018 Eq.4, separated at 8 Gyr. The bulge matches the distribution
     in Fig.7 of Bovy+19 but accounts for sample's bias.
@@ -32,7 +32,7 @@ def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr,
     if component == "thin_disc":
         U = np.random.rand(size)
         norm = 1 / quad(lambda x: np.exp(-(tm.value - x) / tsfr.value),
-                        0, 8 if not old else 12)[0]
+                        0, 8)[0]
         tau = tsfr * np.log((U * np.exp(tm / tsfr)) / (norm * tsfr.value) + 1)
     elif component == "thick_disc":
         U = np.random.rand(size)
@@ -148,9 +148,9 @@ def distance_from_earth(R, z, theta, Rsun=8.2*u.kpc):
 def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
                 masses=[2.585e10, 2.585e10, 0.91e10]*u.Msun,
                 tm=12 * u.Gyr, tsfr=6.8 * u.Gyr, alpha=0.3,
-                zd=0.3 * u.kpc, Fm=-1, gradient=-0.075 / u.kpc,
+                Fm=-1, gradient=-0.075 / u.kpc,
                 Rnow=8.7 * u.kpc, gamma=0.3, zsun=0.0142, Rsun=8.2 * u.kpc,
-                ret_pos=False, lookback=True, old=False):
+                ret_pos=False, lookback=True):
     """Draw a sample of birth times, distances and metallicities from a Milky
     Way model.
 
@@ -164,8 +164,6 @@ def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
         Star formation timescale, by default 6.8*u.Gyr
     alpha : `float`, optional
         Disc inside-out growth parameter, by default 0.3
-    zd : `float`, optional
-        Disc scale height, by default 0.3*u.kpc
     Fm : `int`, optional
         Metallicity at centre of disc at tm, by default -1
     gradient : `float`, optional
[…]

### 2021-06-08 paper/tex/sections/methods.tex
lots of results updates, mainly fiducial dists

@@
 
-We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
+We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
 We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
-For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ as in \citet{Pfahl+2002} and \citet{Podsiadlowski+2004}.
+For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
 
 We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
-For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with electron-capture supernovae).
+For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
 

### 2021-06-08 paper/tex/sections/results.tex
mini results change
lots of results updates, mainly fiducial dists

@@
-\todo{Note that the numbers/errors are subject to change in this section once the larger high Z simulations are done (thank you Floor!)}
-
 In this section we present our main results for the detectable LISA DCO population.
-We find that on average, for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs where the error bars represent the 90\% confidence interval.
+We find that, for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval.
 We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
@@
 
-We illustrate the distribution of detectable DCOs on the sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
+We illustrate the distribution of detectable DCOs on the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
 This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel) and the more numerous WDWD population \citep[e.g.][]{Korol+2017}.
@@
 We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
-From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards around $2 \times 10^{-3} \unit{Hz}$.
+From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$.
 This offshoot is composed of eccentric binaries for which the circular distance contours do not apply.
 For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines.
-We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.97$ to show the differences for eccentric sources.
-We also note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
+We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the differences for eccentric sources.
+Additionally, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
 
-We also plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel).
-From these lines, it is clear why the density distribution decreases with increasing frequency, since high frequencies correspond to short inspiral times and thus DCOs will spend less time in these regimes.
-We also see that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances.
+We plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel).
+From these lines we can understand the trend of the density distribution decreasing with increasing frequency.
+Sources with higher frequencies have shorter inspiral times and thus DCOs will spend less time in these regimes, meaning that more sources are detected at lower frequencies.
+Note that these inspiral time lines should only be used as guidelines for the population as a whole, as the inspiral time of each individual source will be a function of its mass and eccentricity.
+It is also evident for each DCO source that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances.
 This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.
@@
     \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where the panels correspond to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
+    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
 In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
@@
 The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
-We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.97$.
+We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$.
 The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.
@@
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-We find that for our fiducial model, a four year LISA mission will detect \confinv{34.4}{20.9}{46.6} BHBHs, \confinv{29.9}{20.1}{47.4} BHNSs and \confinv{7.7}{5.0}{10.3} NSNSs, where the error bars represent the 90\% confidence interval.
-Increasing the LISA mission length to ten years changes the number of detections to \confinv{42.0}{17.3}{17.3}, \confinv{44.5}{17.8}{20.7} and \confinv{19.3}{8.0}{9.7} respectively.
+\todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
+We find that for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval.
+Increasing the LISA mission length to ten years changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively.
 In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
@@
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
-\todo{@ALL, ignore models P and Q for now}}
+\todo{subject to change with the updated/new models}}
     \label{fig:detection_rates}
@@
 
-\todo{This section is not currently up to date, waiting for new sims before writing more}
-
 In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.
-
-\subsubsection{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $83\%$ and $90\%$ respectively below $10 \unit{M_{\odot}}$.
-This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation.
-The mass distribution also extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.
-Thus BHBHs and BHNSs detected by LISA could be ideal for ascertaining whether there exists a lower mass gap between neutron stars and black holes.
-
-The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios.
-The two peaks are from the primary and secondary black hole masses and we show their individual distributions with the dotted curves.
-
-The reasoning for these unequal mass ratio is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
-This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs.
-Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer.
-Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.
-
-\subsubsection{Neutron Star Mass}
-The neutron star mass distribution shows that most neutron stars have low masses, with $69\%$ and $87\%$ having masses below $1.5 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
-The lacks of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription.
-
-\subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
-This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often instead result in disrupted or too-wide binaries.
-In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
-This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
-
-\subsubsection{Orbital Frequency and Frequency Evolution}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution also has a tail that extends to $4 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries since eccentricity moves the dominant harmonic to higher frequencies.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
-
-\subsubsection{Luminosity Distance}
-Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-Each DCO also has a shoulder at lower distances since closer binaries are easier to detect.
-This shoulder is more prominent for the NSNS distribution since their lower relative masses require a smaller distance in order to be detected on average.
-
-\subsubsection{Inspiral Time}
-Each DCO has a strong peak at small inspiral times since higher metallicities lead to tighter binaries and thus shorter inspiral times.
 
@@
 The first two rows (excluding metallicity) use kernel density estimators to show the distributions.
+The dotted lines in the black hole mass panel show the individual distributions of the primary and secondary masses.
 The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines.
@@
 
+\subsubsection{Black Hole Mass}
+For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$.
+This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation.
+The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.
+Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
+Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.
+
+The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios.
+The two peaks are from the primary and secondary black hole masses, which peak around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively.
+We show these individual distributions as dotted curves below the main BHBH distribution.
+
+The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
+This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs.
+Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer.
+Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.
+
+\subsubsection{Neutron Star Mass}
+The neutron star mass distribution shows that most neutron stars have low masses, with $77\%$ and $91\%$ having masses below $1.7 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
+The lack of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription and do not have strong effects since the vast majority of NSs are formed with lower masses.
+
+Both distributions have notable peaks around $1.26 \unit{M_{\odot}}$, though more strongly in the NSNS case, which are a result of the combination of two effects.
+Firstly, we set the remnant mass for all electron-capture supernovae to $1.26 \unit{M_\odot}$ (see Sec.~\ref{sec:fiducial_physics}) and thus this leads to a pileup when many systems are formed through ECSN.
+In addition, the Fryer remnant mass prescription gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
+
+\subsubsection{Orbital Frequency}
+The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
+This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
+The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
+These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
+Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
+
+\subsubsection{Luminosity Distance}
+Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
+There is a clear bias in each distribution for systems at lower distances since closer binaries are easier to detect.
+This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.
+
+\subsubsection{Lookback Time}
+Although when creating each mock Milky Way galaxy the lookback time is drawn independently from other parameters, and in the same way for every DCO type, the distributions are clearly different for each type of DCO.
+This is because for a binary to be detectable, it must have an orbital frequency within the LISA band.
+Therefore a binary needs to have completed most of its inspiral to be visible in the LISA band and thus detectable systems will tend to have lookback time that are close to their merger times, which \textit{are} a function of other binary parameters.
+
+Since most of the DCOs are formed through common envelope events, their initial separations are relatively tight and so if a binary it given a long lookback time, it will have merged before the LISA mission.
+This explains the peak in each distribution at short lookback times.
+The later lookback times correspond to systems that are formed through channels in which mass transfer is only stable and no common envelope event occurs.
+
+The trends across the different DCO types can be explained by considering that the merger time is a function of the masses, frequency and eccentricity of th source.
+This dependence can be approximately written as $t_{\rm merge} \propto f_{\rm orb}^{-4} m_1^{-3} (1 - e^2)^{-7/2}$,  \citep[][Eq.~5.14]{Peters+1964}.
+Therefore, although NSNSs are the lowest mass systems, their relatively higher orbital frequencies means that they have the shortest merger times.
+This same logic implies that BHNSs should have the next shortest merger times and then BHBHs.
+This order is flipped due to the fact that high eccentricity results in a shorter merger time and we find that LISA detectable BHNSs are mostly circular, whilst BHBHs have a significant highly eccentric subpopulation.
+
+\subsubsection{Metallicity}
+\todo{Returning to this once I've made the plot that compares the Milky Way distribution and formation rates}
+
+\subsubsection{Eccentricity}
+The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
+This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
+However, these stronger kicks often instead result in disrupted or too-wide binaries in more weakly bound NSNSs.
+In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
+This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
+
+A significant fraction of DCOs in each population have eccentricities greater than 0.01, the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}, which we indicate with the shaded area.
+We discuss the estimation of the eccentricity uncertainty further in Section~\ref{sec:measurement_uncertainties}
+
+\subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
+\todo{will fill with info on eccentricity, chirp mass and angular resolution uncertainties}
+
 \subsection{Model variations}
+\todo{This will be about how the shapes change with model variations}

### 2021-06-09 paper/tex/sections/results.tex
eccentricity and chirp mass uncertainty

@@
 \subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
-\todo{will fill with info on eccentricity, chirp mass and angular resolution uncertainties}
+Although it is useful to investigate the underlying parameters of the detectable population, it is also important to consider what LISA will actually \textit{measure} during a detection.
+
+\subsubsection{Eccentricity uncertainty}\label{sec:ecc_unc}
+One of the main advantage of space-based gravitational wave detectors such as LISA is that systems may still have significant eccentricity during the LISA mission.
+Whilst also being useful a useful individual quantity for learning more about sources, the uncertainty on the eccentricity also affects the uncertainty on the chirp mass and so it is important to quantify this uncertainty.
+
+We follow a method used in previous works that uses the individually detectable harmonics of sources to determine the uncertainty of the eccentricity of a source \citep[e.g.][]{Lau+2020, Korol+2021}.
+Eccentric sources emit at several evenly spaced harmonic frequencies, each with a different fraction of the gravitational wave power and the distribution of the power over the harmonics changes with eccentricity.
+Therefore, by measuring the SNR of each individual harmonic and finding the ratio of the SNR of the two most detectable harmonics that are above the detection threshold, one can determine the eccentricity.
+The uncertainty on the eccentricity can therefore be written as a combination of the uncertainty on the SNR of the two most detectable harmonics.
+In the limit of large SNRs, the eccentricity uncertainty, $\Delta e$, can be written as
+\begin{equation}
+    \Delta e = \frac{1}{\rho_1} + \frac{1}{\rho_2},
+\end{equation}
+where $\rho_1$ and $\rho_2$ are the SNRs of the two most detectable harmonics.
+
+In some cases, sources may only have one individually detectable harmonics, or even none.
+In these cases one can only put a lower or upper bound on the eccentricity.
+For sources with only one detectable harmonic, the source is either a circular source or a source with a small enough eccentricity that most of the GW power is still concentrated in the $n = 2$.
+Therefore, we can use this information to place an upper bound on the eccentricity.
+Conversely, sources with no detectable harmonics must be eccentric such that the GW power has spread over so many harmonics that no single harmonic has a significantly stronger signal.
+Therefore, we can use this information to place a lower bound on the eccentricity.
+
+This method provides a pessimistic estimate of the eccentricity of sources since we do not consider the benefits of any sort of matched-filter analysis or similar methods.
+We discuss how the pessimism of this method affects our results and some possible alternative in Section~\ref{sec:caveats}.
+
+\subsubsection{Chirp mass uncertainty}
+The chirp mass uncertainty can be calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity.
+This is because the time derivative of the orbital frequency can be written as
+\begin{equation}
+    \dot{f}_{\rm orb} = \frac{48}{5 \pi} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} (2 \pi f_{\rm orb})^{11/3} F(e),
+\end{equation}
+where $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}) and $e$ is the eccentricity and
+\begin{equation}
+    F(e) = \frac{1 + \frac{73}{24} e^2 + \frac{37}{96} e^4}{(1 - e^2)^{7/2}},
+\end{equation}
+is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}.
+
+We can invert this and instead write that the chirp mass is
+\begin{equation}
+    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48} \frac{\dot{f}_{\rm orb}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
+\end{equation}
+and therefore that the chirp mass uncertainty is
+\begin{equation}\label{eq:chirp_mass_uncertainty}
+    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)}.
+\end{equation}
+
+We calculate the frequency uncertainties using \citet{Takahashi+2002}, such that
+\begin{align}
+    \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
+    \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm orb}},
+\end{align}
+where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length. Then we calculate the eccentricity certainty as discussed in Sec.~\ref{sec:ecc_unc} and propagate it so that
+\begin{equation}
+    \frac{\Delta F(e)}{F(e)} = \Delta e \cdot \frac{(1256 + 1608 e^2 + 111 e^4) e}{96 + 196 e^2 - 255 e^4 - 37 e^6}.
+\end{equation}
+
+We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in the lower centre panel of Fig.~\ref{fig:fiducial_pdf_distributions}.
+We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses.
+We find that approximately 10 BHBHs and BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
+We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.
+
+\subsubsection{Angular resolution}
 

### 2021-06-09 paper/tex/sections/discussion.tex
lots of results updates, mainly fiducial dists
eccentricity and chirp mass uncertainty
sky localisation

@@
-\subsection{Caveats}
+\subsection{Identification of GW sources}
+It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
+
+\subsubsection{Distinguishing from WDWD population}
+\subsubsection{Separating BHBHs, BHNSs and NSNSs}
+
+\subsection{Matching LISA detection to radio pulsars}\label{sec:pulsar_matching}
+
+\subsection{Caveats}\label{sec:caveats}
 \todo{This section is only an outline for now}
@@
     \item Contribution of metal-poor stars not well known
+    \item COMPAS models for naked helium stars are based on a single metallicity -- may be why NSNS rate is less dependent on MSSFR
 \end{itemize}
@@
 \begin{itemize}
-    \item None come to mind...?
+    \item Eccentricity uncertainty is pessimistic (doesn't actually seem to be the dominant problem)
 \end{itemize}
-
-\subsection{Identification of GW sources}
-It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
-
-\subsubsection{Distinguishing from WDWD population}
-\subsubsection{Separating BHBHs, BHNSs and NSNSs}

### 2021-06-09 paper/tex/sections/results.tex
sky localisation

@@
 
-\subsubsection{Angular resolution}
+\subsubsection{Sky localisation}
+We quantify the sky localisation of a source by calculating its angular resolution.
+Since we find that all potential sources are stationary on the timescale of the LISA mission, following \citet{Mandel+2018}, we can use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
+\begin{equation}
+    \sigma_{\theta} = 16.6^\circ \left(\frac{7}{\rho}\right) \left(\frac{5 \times 10^{-4} \unit{Hz}}{f_{\rm dom}}\right) \left( \frac{2 \unit{AU}}{L} \right),
+\end{equation}
+where $\rho$ is the signal-to-noise ratio, $f_{\rm dom}$ is the harmonic frequency with the strongest signal-to-noise ratio ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) and $L$ is the effective detector baseline.
+
+We plot the angular resolution in the last panel of Fig.~\ref{fig:fiducial_pdf_distributions} as a CDF normalised to the expected detection rate of each DCO.
+From this plot, we see that many sources can only be resolved to a patch with an area in excess of 100 square degrees \todo{make this positive}.
+The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (approximately the angular size of the moon).
+Applying this to the plot shows that about 20\% of DCOs can be covered by a single pointing of SKA.
+We will discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
 

### 2021-06-10 paper/tex/sections/discussion.tex
add caveats

--- 2021-05-17 paper/tex/sections/discussion.tex
@@
-\subsection{Caveats}
-Separate into three sections
-
-GCs don't produce DNSs well but the other ones yes
-
-Contribution of metal poor stars is not well known
-
-\begin{itemize}
-    \item Standard pop synth limitations
-    \item Systemic kicks
-    \item No models for high $Z$ values in Frankel
-    \item Other channels
-    \item Only a single disc for the Milky Way
-\end{itemize}
-
 \subsection{Identification of GW sources}
@@
 \subsubsection{Separating BHBHs, BHNSs and NSNSs}
+
+\subsection{Matching LISA detection to radio pulsars}\label{sec:pulsar_matching}
+
+\subsection{Caveats}\label{sec:caveats}
+\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar physics and the use of approximate fitting formulae.
+We cannot use detailed stellar evolution codes to produce such a large sample of DCOs in a reasonable amount of time.
+Therefore COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
+This means that some of the finer points of evolution may be approximated but generally the final product of the stars on a population as a whole is reasonably close to the true result.
+In addition, much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics.
+We attempt to understand the importance of these assumptions by creating many different physics variations.
+However, it is not reasonable to change every possible parameter (especially since many parts of the code have fixed assumptions) and therefore our results are subject to the accuracy of the assumptions made within the COMPAS code.
+
+\textit{Underlying helium star models:} One major weakness is that the \citet{Hurley+2000} fitting formulae for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
+A more detailed set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
+
+\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ and should not be extrapolated outside this region.
+On the scale of the Universe (more relevant for LIGO predictions), this does not usually pose a significant problem as the population is usually fairly low metallicity.
+However, for local GW detection in the Milky Way (based on the metallicity relation in \citet{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of formation occurs past $Z = 0.03$.
+Therefore, for our study we had to reassign any metallicities outside of COMPAS' range.
+For any metallicity below the minimum, we places it in our lowest metallicity bin.
+For any metallicity above the minimum we placed it uniformly randomly in one of the top 5 highest bins (since using a single bin for many binaries led to unphysical artifacts in our results).
+
+\textit{Other formation channels:} We also note that our findings are only the result of a single formation channel (isolated binary formation).
+We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions.
+For instance, \citet{Kremer+2018} showed that around $21$ systems could be detected in Milky Way globular clusters through dynamical formation and thus different channels can still contribute significantly to the detection rate.
+
+\textit{Halo and globular clusters:} Moreover, our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo or globular clusters.
+\citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
+The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates.
+
+\textit{Systemic kicks:} Another important consideration about our galaxy is that we do not include the effect of systemic kicks on the final location of the sources.
+This would require integrating the orbital evolution of the millions of binaries in our sample and thus was not computationally reasonable to include.
+We investigated the effect of kicks for a small grid of binaries and found that though they would result in a more spread out distribution within the galaxy (with a smaller concentration in the galaxy centre), the overall distribution of positions would be relatively unchanged and very few sources have strong enough kicks to reach escape velocity for the Milky Way.
+
+\textit{Eccentricity measurement uncertainty:} As noted in Sec.~\ref{sec:ecc_unc}, the method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable.
+In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data.
+For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as the same source.
+This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold.
+This would allow one to refine the measurement of the eccentricity uncertainty much further by comparing the many different harmonics.
+Therefore, the eccentricity uncertainty that we calculate in this study is a pessimistic estimate.
+Smaller eccentricity uncertainties would have two main effects on our results.
+Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty, however it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps.
+Secondly, it would improve our ability to distinguish between WDWDs and these higher mass DCOs.
+However, until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.

### 2021-06-10 paper/tex/sections/discussion.tex
some of pulsar matching

@@
 \subsection{Matching LISA detection to radio pulsars}\label{sec:pulsar_matching}
+Since the vast majority of the population will not merge for many years, the main type of electromagnetic counterparts for the LISA Galactic DCO population is pulsars.
+Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar.
+In this section we investigate how we can use SKA to match pulsars to LISA signals with some back-of-the-envelope estimates.
+
+First, we can consider how many pulsars SKA is likely to detect.
+\citet{Keane+2015} uses PSRPOPPy \citep{Bates+2014} to simulate the Milky Way pulsar population.
+They find that for SKA-1, approximately $10000$ pulsars will be discovered.
+The second phase of SKA should also have been approved and in operation by the time of the LISA mission and this phase would yield a total of $24000$-$30000$ pulsars \citep{Keane+2015}.
+Moreover, we are only interested in pulsars that are part of a binary system.
+We can estimate the pulsar binary fraction as the fraction of known pulsars that are in binaries using the ATNF Pulsar Catalogue\footnote{\url{https://www.atnf.csiro.au/research/pulsar/psrcat}} \citep{Manchester+2005}.
+$290$ of the $2872$ currently known pulsars are in binary systems and thus we can estimate the binary fraction of pulsars as $10\%$.
+
+Next, we find the total number of pulsars SKA will detect in a patch on the sky.
+The total sky area that the SKA mission covers is approximately $7200 \unit{deg^2}$, which is calculated based on SKA-mid covering Galactic latitudes of $\abs{b} < 10^\circ$ and SKA-low covering $\abs{b} < 5^\circ$ \citep{Keane+2015}.
+If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.14$ and $0.42$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.
+Note that this assumption is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide an upper bound on these estimates.
+
+Given these estimates, and by considering the last panel of Fig.~\ref{fig:fiducial_pdf_distributions}, approximately $10$ and $6$ (for SKA-1 and SKA-2) DCOs containing NSs will be localised well enough that \textit{if} the NS is a pulsar, SKA can unambiguously match it to the radio signal.
+
+Furthermore, both SKA and LISA will measure the frequency, frequency derivative and chirp mass of each of these systems.
+Therefore, they can independently calculate these parameters and use them to match a GW signal to a radio signal.
+In this way, there can be more than one pulsar within the sky localisation provided to LISA and it is still possible to match to the correct pulsar.
 

### 2021-06-14 paper/tex/sections/discussion.tex
finish/improve pulsar subsection

--- 2021-06-10 paper/tex/sections/discussion.tex
@@
 
-\subsection{Matching LISA detection to radio pulsars}\label{sec:pulsar_matching}
+\subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
+Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main form of electromagnetic counterpart for the this population is pulsars.
+Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar.
+The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
+A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
+Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magniute better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.
+
+In this section, we perform some back-of-the-envelope calculations to order to estimate how we can use SKA to match pulsars to LISA detections.
+
+First, we can consider how many pulsars SKA is likely to detect.
+\citet{Keane+2015} uses PSRPOPPy \citep{Bates+2014} to simulate the Milky Way pulsar population.
+They find that for SKA-1, approximately $10000$ pulsars will be discovered.
+The second phase of SKA, which should also have been approved and be in operation by the time of the LISA mission, would yield a total of $35000$-$41000$ pulsars \citep{Keane+2015}, where we use the average, $38000$, in further estimates below.
+Moreover, we are only interested in pulsars that are part of a binary system.
+We can estimate this pulsar binary fraction as the fraction of known pulsars that are in binaries using the ATNF Pulsar Catalogue\footnote{\url{https://www.atnf.csiro.au/research/pulsar/psrcat}} \citep{Manchester+2005}.
+$290$ of the $2872$ currently known pulsars are in binary systems and thus we can estimate the binary fraction of pulsars as $10\%$.
+
+Next, we can find the total number of pulsars SKA will detect in a patch on the sky.
+The total sky area that the SKA mission covers is approximately $7200 \unit{deg^2}$, which is calculated by integrating over the sky for all Galactic longitudes and Galactic latitudes limited to $\abs{b} < 10^\circ$, which are the limits on SKA-mid \citep{Keane+2015}.
+If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.14$ and $0.49$-$0.57$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.
+Note that the assumption assumption of a uniform distribution is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide an upper bound on these estimates.
+
+Alternatively, we could write that we expect a single pulsar per $7.2 \unit{deg^2}$ and $2.1$-$1.8 \unit{deg^2}$ for SKA-1 and SKA-2 respectively, which corresponds to angular resolutions of $\sigma_\theta = 1.51^\circ$ and $\sigma_\theta = 0.82$-$0.76^\circ$.
+Given these estimates, and by considering the last panel of Fig.~\ref{fig:fiducial_pdf_distributions}, approximately $10$ and $6$ (for SKA-1 and SKA-2) DCOs containing NSs will be localised well enough such that, \textit{if} the NS is a pulsar, SKA can unambiguously match it to the radio signal.
+
+If there is more than one pulsar in the region given by the LISA sky localisation, one can compare the measured parameters of the system in LISA and SKA.
+Both SKA and LISA will measure the orbital frequency to high precision, as well as the time derivative of the frequency and chirp mass to a lesser precision, of each of these systems.
+Therefore, one could perform a targetted search with SKA that checks the sky location given by LISA and only looking for binary pulsars with orbital frequencies within the errors.
+If there was \textit{still} more than one possible pulsar one could then also check against the chirp mass.
+In this way, it would still be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
+
+In order to assess the efficacy of this method, we would need to know the probability that two random binary pulsars would have orbital frequencies and chirp masses close enough that one could not tell which pulsar matches the LISA detection.
+This would require simulating the SKA population of pulsars with a code such as PSRPOPPy to find the frequency and chirp mass distribution and thus is beyond the scope of this paper.
+However, the uncertainty on the orbital frequency of a binary on the detection threshold ($\rho = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
+Therefore, we expect that SKA could likely isolate the correct binary pulsar to match to a LISA detection even when several are present in the sky localisation region.
 

### 2021-06-14 paper/tex/sections/results.tex
finish/improve pulsar subsection

@@
 We calculate the frequency uncertainties using \citet{Takahashi+2002}, such that
-\begin{align}
+\begin{align}\label{eq:f_orb_unc}
     \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
@@
 We plot the angular resolution in the last panel of Fig.~\ref{fig:fiducial_pdf_distributions} as a CDF normalised to the expected detection rate of each DCO.
-From this plot, we see that many sources can only be resolved to a patch with an area in excess of 100 square degrees \todo{make this positive}.
-The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (approximately the angular size of the moon).
+From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 square degrees.
+The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).
 Applying this to the plot shows that about 20\% of DCOs can be covered by a single pointing of SKA.

### 2021-06-14 paper/tex/sections/appendix.tex
Updates from Overleaf

@@
 \subsection{Total star forming mass in the Milky Way}
-It is important to distinguish between the \textit{total} star forming mass over the Milky Way's history and the \textit{current} star forming mass in the Milky Way.
+It is important to distinguish between the \textit{total} mass of stars formed over the Milky Way's history and the \textit{current} stellar mass in the Milky Way.
 Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass.
@@
 We calculate this by interpolating a grid of single stars in COMPAS over different masses and metallicities and seeing what final mass they get using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings.
-We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ main sequence lifetime of the star has passed, otherwise we just use the initial mass.
+We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ the main sequence lifetime of the star has passed, otherwise we just use the initial mass.
 Since we don't know the exact metallicity of each star we use the average metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}.

### 2021-06-14 paper/tex/sections/methods.tex

@@
 The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate.
-But the bulge was shown to contain stars with a range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
+But the bulge was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
 To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$ {\color{blue} \textbf{Stephen: I thought $2 \times 10^{5}$}?}, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
-This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy size and only sample from massive stars rather than the full IMF.
+This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy mass  and only sample from massive stars rather than the full IMF.
 For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.

### 2021-06-15 paper/tex/sections/discussion.tex
progress on distinguishing

@@
 \subsubsection{Distinguishing from WDWD population}
+The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
+It is therefore imperative that we consider how to distinguish from this much more numerous population of sources.
+
+The easiest way to check whether a source is a WDWD is to check its chirp mass.
+The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.44 \unit{M_\odot}$ \citep{Chandrasekhar+1931}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.25 \unit{M_{\odot}}$.
+Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.25 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
+We find that 17\%(23\%) of BHBHs, 20\%(24\%) of BHNSs and 2.4\%(2.5\%) of NSNSs for a 4(10)-year LISA mission satisfy this condition.
+
+\todo{Another bit about the fact that eccentric DCOs that are resolved within the disc can be quite confidently confirmed as not WDWDs}
+
 \subsubsection{Separating BHBHs, BHNSs and NSNSs}
+
+\todo{}
 
@@
 A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
-Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magniute better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.
+Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.
 

### 2021-06-15 paper/tex/sections/results.tex
progress on distinguishing

@@
 \begin{equation}\label{eq:chirp_mass_uncertainty}
-    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)}.
+    \qty( \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} )^2 = \left( \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta F(e)}{F(e)} \right)^2.
 \end{equation}
@@
 We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses.
-We find that approximately 10 BHBHs and BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
+We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
 We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.
@@
 \subsection{Model variations}
-\todo{This will be about how the shapes change with model variations}
+\todo{This will be about how the shapes of the parameter distributions change for the different model variations}

### 2021-06-16 paper/tex/sections/appendix.tex
updates to appendix from Stephen feedback

--- 2021-05-08 paper/tex/sections/appendix.tex
@@
 \end{equation}
-where $\avg{ \mathcal{R}_{\rm target} }$ is the average number of targets formed per star forming mass and $M_{\rm SF, MW}$ is the total star forming mass that has existed in the Milky Way's history.
-We explain each of these terms in respective subsections below.
+where $\avg{ \mathcal{R}_{\rm target} }$ is the average number of targets formed per star forming mass and $M_{\rm SF, MW}$ is the star forming mass of the Milky Way, meaning the total mass of every star ever formed in the Milky Way.
+We explain how to calculate each of these terms in respective subsections below.
 
@@
 \subsection{Total star forming mass in the Milky Way}
-It is important to distinguish between the \textit{total} star forming mass over the Milky Way's history and the \textit{current} star forming mass in the Milky Way.
-Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus decreasing the total stellar mass.
-\citet{Licquia+2015} find that the total stellar mass today in the Milky Way is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm odot}}$.
+It is important to distinguish between the \textit{total} mass of every star formed over the entire history of the Milky Way and the \textit{current} stellar mass in the Milky Way.
+Many stars born in the Milky Way are no longer living and have lost much of their mass to stellar winds and supernovae, thus the current stellar mass in the Milky Way is an underestimate of the total star forming mass.
+
+\citet{Licquia+2015} find that the total stellar mass today in the Milky Way is $6.08 \pm 1.14 \times 10^{10} \unit{M_{\odot}}$.
 This total includes all stars and stellar remnants (white dwarfs, neutrons stars and black holes) but \textit{excludes} brown dwarfs.
-We can write that the total star forming mass that has \textit{ever} existed in the Milky Way is
+We can write that the total mass of every star every formed in the Milky Way is
 \begin{equation}\label{eq:m_SF_MW}
@@
 \end{equation}
-where $\avg{m}_{\rm SF, total}$ is the average star forming mass over the history of the Milky Way and $\avg{m}_{\rm SF, today}$ is the average star forming mass of the mass remaining today.
-The former is defined as
+where $\avg{m}_{\rm SF, total}$ is the average mass of a star over the history of the Milky Way and is defined as
 \begin{equation}
@@
 \end{equation}
-where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ \citep[][Eq.~4]{Frankel+2018}.
-The average star forming mass of the mass \textit{remaining today} is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
+where $t_{\rm MW}$ is the age of the Milky Way, $\zeta(m)$ is the \citet{Kroupa+2001} IMF function and $p_{\rm birth}(\tau)$ is the probability of a star being formed at a lookback time $\tau$ (Eq.~\ref{eq:thin_disc_tau}).
+$\avg{m}_{\rm SF, today}$ is the average mass of all stars and stellar remnants (excluding brown dwarfs) present in the Milky Way today is defined as follows (note that we integrate from $0.08$ not $0.01$ since observations of today's Milky Way mass exclude brown dwarfs)
 \begin{equation}
@@
 \end{equation}
-where $m_{\rm today}(m, Z, \tau)$ is the mass of a star that was formed $\tau$ years ago at a metallicity $Z$.
-We calculate this by interpolating a grid of single stars in COMPAS over different masses and metallicities and seeing what final mass they get using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings.
-We only use the final mass if more than $\tau_{\rm MS}(m, Z)$ main sequence lifetime of the star has passed, otherwise we just use the initial mass.
-Since we don't know the exact metallicity of each star we use the average metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}.
-If we now evaluate Equation \ref{eq:m_SF_MW}, we find the that total star forming mass that ever existed in the Milky Way is
+where $m_{\rm today}(m, Z, \tau)$ is the current mass of a star that was formed $\tau$ years ago at a metallicity $Z$.
+We calculate $m_{\rm today}(m, Z, \tau)$ by interpolating the final masses given by COMPAS for a grid of single stars over different masses and metallicities using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings.
+We only use the final mass if more than the main sequence lifetime of the star has passed, otherwise we just use the initial mass.
+Since we don't know the exact metallicity of each star we use the average star forming metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}.
+If we now evaluate Equation \ref{eq:m_SF_MW}, we find that the total mass of every star that has ever formed in the Milky Way is
 \begin{equation}
@@
 \end{equation}
-an increase of approximately 50\% from the value still in stars today.
+an increase of approximately 50\% from the value still in stars today!
 
 \subsection{Normalisation summary}
-We can plug Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
+Finally, we can substitute Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
 \begin{equation}
-    N_{\rm detect} = 9.1 \times 10^{10} \unit{M_{\odot}} \cdot f_{\rm detect} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
+    N_{\rm detect} = f_{\rm detect} \cdot 9.1 \times 10^{10} \unit{M_{\odot}} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
 \end{equation}

### 2021-06-17 paper/tex/sections/methods.tex
responses to feedback

@@
 The authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017}.
-%and matched to stars in Gaia \citep{GaiaCollaboration+2016}.
 
@@
 
-Our model for the Milky Way accounts for the low-$\alpha$ disc, high-$\alpha$ disc and central bar/bulge.
+Our model for the Milky Way accounts for the low-$\alpha$ disc, high-$\alpha$ disc\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is not related to the common envelope efficiency $\alpha_{\rm CE}$.} \footnote{The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs.
+We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be split between the two components, as opposed to the vertical distribution which simply cannot be fit by a single exponential.} and central bar/bulge.
 For each of these components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 10^{5}$ {\color{blue} \textbf{Stephen: I thought $2 \times 10^{5}$}?}, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$ {\color{blue} \textbf{Stephen: I thought $2 \times 10^{5}$}?}, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 Each binary is likely to move from its birth orbit.
-Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep{Hobbs+2005}.
+Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep[e.g.][]{Hobbs+2005}.
 
@@
 For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
-This takes into account the true mass and IMF of the Milky Way since our simulations each have a slightly smaller galaxy mass  and only sample from massive stars rather than the full IMF.
+This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF.
 For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.
@@
 \end{equation}
-We calculate the detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 100,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.
+We calculate the detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 200,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.

### 2021-06-17 paper/tex/sections/introduction.tex
remove gaia mentions

@@
 We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}.
+We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}.
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.

### 2021-06-17 paper/tex/sections/introduction.tex
introduction proofread

--- 2021-05-05 paper/tex/sections/introduction.tex
@@
-Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}.
-The detection of the mergers of these binaries have offered exciting insights into the evolution and endpoints of massive stars.
+Since the first direct observation of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive binary stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
 
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors \citep[e.g.][]{Begelman+1980, Klein+2016}.
-However, this frequency regime is also of interest for the detection of local stellar mass binaries during their inspiral phase.
+LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
+Moreover, this frequency regime is also of interest for the detection of local stellar mass binaries during their inspiral phase.
 This means that LISA will be able to detect, and possibly localise a binary on the sky, many years in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
-In addition, LISA provides an opportunity to measure the eccentricities of double compact objects (DCO) that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
+In addition, LISA will be able to measure the eccentricities of double compact objects (DCO) that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
 The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger.
@@
 
-For the purposes of this investigation, we consider the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011}.
+For the purposes of this investigation, we consider the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011}.
 There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
 
-Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been observed \citep[e.g.][]{Abbott+2017_NSNS}.
+Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been detected \citep[e.g.][]{Abbott+2017_NSNS}.
 The detection of a NSNS in LISA in which at least one NS is a pulsar could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
@@
 
-The detection of DCOs with LISA has been investigated in several previous studies yet studies that focus on BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
+The detection of DCOs with LISA has been investigated in several previous studies, yet studies that focus on BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
 Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
@@
 We build upon previous efforts but with several important improvements.
-We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}.
+We explore the effect of varying binary physics assumptions by repeating our analysis for 20 different models and comparing the effect on the detection rate and distributions of source parameters.
+We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}.
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated massive binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
+Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with over a billion simulated massive binaries evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
 We find that this large number of simulations is important to reduce the sampling noise.

### 2021-06-17 paper/tex/sections/methods.tex
introduction proofread
methods proofread, add winds description

@@
 Riley et al.
-(in prep)) We summarize the main assumptions and settings relevant for this work in the following sections.
+(in prep)).
+We summarize the main assumptions and settings relevant for this work in the following sections.
 
@@
 These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
-This is repeated for 14 physics variations (see Section \ref{sec:variation_assumptions}) and so in total 750 million binaries were simulated.
+This is repeated for 19 physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
 
 Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} Initial Mass Function (IMF), $p(m_1) \propto m_1^{-2.3}$.
+The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
 The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
@@
 We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
+
+\textit{Wind mass loss:} We follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
+We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
+Additionally, we use a separate, higher wind mass loss rate for LBV stars, since these experience eruptive mass loss in addition to the regular line-driven winds and we follow \citet{Belczynski+2008} in setting $f_{\rm LBV} = 1.5$.
+We also use their Wolf-Rayet-like mass loss rate for helium stars and set $f_{\rm WR} = 1$.
+See Team COMPAS: J.
+Riley et al.
+(in prep), Section 3 for the explicit equations.
 

### 2021-06-17 paper/tex/sections/introduction.tex
add new models and change commands to match

@@
 We build upon previous efforts but with several important improvements.
-We explore the effect of varying binary physics assumptions by repeating our analysis for 20 different models and comparing the effect on the detection rate and distributions of source parameters.
+We explore the effect of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effect on the detection rate and distributions of source parameters.
 We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}.

### 2021-06-17 paper/tex/sections/methods.tex
add new models and change commands to match

@@
 These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
-This is repeated for 19 physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
+This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
 
@@
 \subsubsection{Model variations} \label{sec:variation_assumptions}
-In addition to our fiducial model for the formation of DCOs, we explore 14 other models in which we change various aspects of the mass transfer, common envelope and supernova physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
+In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.
@@
 Models \modRangeCE{} focus on altering the common envelope physics.
-We change the common envelope efficiency parameter in models \modAlphaLow{} and \modAlphaHigh{} to $\alpha = 0.5$ and $2.0$ respectively.
-In model \modOpt, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
+We change the common envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
+In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
+We combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
 
-Finally, in models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
+In models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
 Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
@@
 In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
-Finally, model \modNoBH{} removes the natal kick for all black holes.
+Lastly, model \modNoBH{} removes the natal kick for all black holes.
+
+Finally, in models \modRangeML{} we investigate the effect of changing our assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
+We vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
+These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations (e.g.
+\citet{Vink+2017}, \citet{Hamann+2019}, \citet{Shenar+2019}, \citet{Miller-Jones+2021} and van Son et al.
+(in prep)).
 
@@
         \modCaseBB & Case BB mass transfer is always unstable \\
+        \modCaseBBOpt & Model \modCaseBB{} + Model \modOpt{} \\
         \hline
+        \modAlphaLowest & CE efficiency parameter $\alpha = 0.1$ \\
         \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
         \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
+        \modAlphaHighest & CE efficiency parameter $\alpha = 10$   \\
         \modOpt & HG donor stars initiating a CE survive CE \\
@@
         \modNoBH & Black holes receive no natal kick \\
+        \hline
+        \modWRLow & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ \\
+        \modWRHigh & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ \\
         \hline \hline
     \end{tabular}%
-    \caption{A description of the 15 binary population synthesis models used in this study.
-\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics and \modRangeSN{} change supernova physics \citep[c.f.][Table 2]{Broekgaarden+2021}.}
+    \caption{A description of the \nModels{} binary population synthesis models used in this study.
+\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics , \modRangeSN{} change supernova physics and \modRangeML{} change wind mass loss \citep[c.f.][Table 2]{Broekgaarden+2021}.}
     \label{tab:physics_variations}

### 2021-06-17 paper/tex/sections/methods.tex
update galaxy schematic nomenclature

@@
 The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
-    On the right, we show an example instance of the Milky Way with $10^5$ binaries shown as points colour coded by metallicity.
+    On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity.
 The top panel shows a side-on view and the bottom panel shows a face-on view.}
@@
 
-Our model for the Milky Way accounts for the low-$\alpha$ disc, high-$\alpha$ disc\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is not related to the common envelope efficiency $\alpha_{\rm CE}$.} \footnote{The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs.
-We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be split between the two components, as opposed to the vertical distribution which simply cannot be fit by a single exponential.} and central bar/bulge.
-For each of these components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
+Our model for the Milky Way accounts for the low-$\alpha$\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is \textit{not} related to the common envelope efficiency $\alpha_{\rm CE}$.} disc, high-$\alpha$ disc and central bar/bulge.
+The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs.
+We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be easily decomposed into the two disc components, as opposed to the vertical distribution which cannot be fit by a single exponential but is not easy to split into separate components.
+For each of the three components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
 \citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-$\alpha$ discs \citep[e.g.,][]{Snaith+2014}.

### 2021-06-17 paper/tex/sections/methods.tex
finish methods proofread

@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$ {\color{blue} \textbf{Stephen: I thought $2 \times 10^{5}$}?}, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 
-Each binary loses orbital energy to gravitational waves throughout its lifetime.
+Ea ch binary loses orbital energy to gravitational waves throughout its lifetime.
 This causes the binary to shrink and circularise over time.
@@
 
-For each physics variation model, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
+For each physics variation model and DCO type, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
 This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF.

### 2021-06-17 paper/tex/sections/methods.tex
actually finish methods proofread

@@
 \subsubsection{Detection rate calculation}
-For any one instance of the Milky Way, we calculate the detection rate
-
 For each physics variation model and DCO type, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.

### 2021-06-17 paper/tex/sections/results.tex
move plots around
results proofread

@@
 \subsection{Distribution on the sensitivity curve}\label{sec:dcos_on_sc}
+
+\begin{figure*}[tp]
+    \centering
+    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
+    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
+In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
+If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
+The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
+We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$.
+The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.
+In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}.
+In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
+    \label{fig:dcos_on_sc}
+\end{figure*}
 
@@
 This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.
-
-\begin{figure*}[tp]
-    \centering
-    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
-In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
-If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
-We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$.
-The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.
-In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}.
-In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
-    \label{fig:dcos_on_sc}
-\end{figure*}
 
@@
 One of the main advantage of space-based gravitational wave detectors such as LISA is that systems may still have significant eccentricity during the LISA mission.
-Whilst also being useful a useful individual quantity for learning more about sources, the uncertainty on the eccentricity also affects the uncertainty on the chirp mass and so it is important to quantify this uncertainty.
+Whilst also being useful as an individual quantity for learning more about sources, the uncertainty on the eccentricity also affects the uncertainty on the chirp mass and so it is important to quantify this uncertainty.
 
@@
 
-In some cases, sources may only have one individually detectable harmonics, or even none.
+In some cases, sources may only have one individually detectable harmonic, or even none.
 In these cases one can only put a lower or upper bound on the eccentricity.
-For sources with only one detectable harmonic, the source is either a circular source or a source with a small enough eccentricity that most of the GW power is still concentrated in the $n = 2$.
+For sources with only one detectable harmonic, the source is either a circular source or a source with a small enough eccentricity that most of the GW power is still concentrated in the $n = 2$ harmonic.
 Therefore, we can use this information to place an upper bound on the eccentricity.
-Conversely, sources with no detectable harmonics must be eccentric such that the GW power has spread over so many harmonics that no single harmonic has a significantly stronger signal.
+Conversely, sources with no detectable harmonics must be eccentric enough such that the GW power has spread over so many harmonics that no single harmonic has a significantly stronger signal.
 Therefore, we can use this information to place a lower bound on the eccentricity.
@@
 This method provides a pessimistic estimate of the eccentricity of sources since we do not consider the benefits of any sort of matched-filter analysis or similar methods.
-We discuss how the pessimism of this method affects our results and some possible alternative in Section~\ref{sec:caveats}.
 
@@
 This is because the time derivative of the orbital frequency can be written as
-\begin{equation}
-    \dot{f}_{\rm orb} = \frac{48}{5 \pi} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} (2 \pi f_{\rm orb})^{11/3} F(e),
+\begin{equation}\label{eq:f_n_dot}
+    \dot{f}_{n} = \frac{48 n}{5 \pi} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} (2 \pi f_{\rm orb})^{11/3} F(e),
 \end{equation}
@@
 \begin{equation}
-    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48} \frac{\dot{f}_{\rm orb}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
+    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48 n} \frac{\dot{f}_{n}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
 \end{equation}
@@
 \begin{equation}\label{eq:chirp_mass_uncertainty}
-    \qty( \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} )^2 = \left( \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta F(e)}{F(e)} \right)^2.
+    \qty( \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} )^2 = \left( \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} \right)^2 + \left( \frac{3}{5} \frac{\Delta F(e)}{F(e)} \right)^2,
 \end{equation}
+where $f_{\rm dom}$ is the harmonic frequency with the strongest SNR as this will provide the best measurement.
 
@@
     \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
-    \frac{\Delta \dot{f}_{\rm orb}}{\dot{f}_{\rm orb}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm orb}},
+    \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm dom}},
 \end{align}
-where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length. Then we calculate the eccentricity certainty as discussed in Sec.~\ref{sec:ecc_unc} and propagate it so that
+where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length.
+Then we calculate the eccentricity certainty, $\Delta e$, as discussed in Sec.~\ref{sec:ecc_unc} and propagate it so that
 \begin{equation}
@@
 We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
-We emphasise that this is a pessimistic estimate due to the pessimistic nature of how we determine the eccentricity uncertainty.
+This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
 

### 2021-06-18 paper/tex/sections/discussion.tex
finish distinguishing

@@
 
-\subsubsection{Distinguishing from WDWD population}
+\subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
 The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
-It is therefore imperative that we consider how to distinguish from this much more numerous population of sources.
+It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
 
-The easiest way to check whether a source is a WDWD is to check its chirp mass.
+The simplest way to check whether a source is a WDWD is to check its chirp mass.
 The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.44 \unit{M_\odot}$ \citep{Chandrasekhar+1931}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.25 \unit{M_{\odot}}$.
 Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.25 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
-We find that 17\%(23\%) of BHBHs, 20\%(24\%) of BHNSs and 2.4\%(2.5\%) of NSNSs for a 4(10)-year LISA mission satisfy this condition.
+We find that for a 4(10)-year LISA mission, 17(23)\% of BHBHs, 20(24)\% of BHNSs and 2.4(2.5)\% of NSNSs satisfy this condition.
+As one would expect, this method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.
 
-\todo{Another bit about the fact that eccentric DCOs that are resolved within the disc can be quite confidently confirmed as not WDWDs}
+Another indicator that the source is not a WDWD would be that it is eccentric.
+WDWDs formed in the disc are thought to be formed through isolated binary formation and have little to no eccentricity \citep[e.g.][]{Nelemans+2001}.
+Therefore, if any system is detected with anything other than one detectable harmonic, this implies that the system is unlikely to be a WDWD.
+We find that for a 4(10)-year LISA mission, 55(61)\% of BHBHs, 27(28)\% of BHNSs and 65(69)\% of NSNSs are detected with multiple harmonics.
+Both the absolute percentage and the improvement with an extended LISA mission is lower for the BHNSs as we find that these DCOs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+
+However, we should also consider that eccentric WDWDs \textit{could} be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}.
+This means that it would not be valid to assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane.
+Therefore, we can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane.
+This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc.
+We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are 40(32)\% for BHBHs, 24(19)\% for BHNSs and 59(51)\% for NSNSs\footnote{Note that although the fractions are smaller for the 10 year mission, the \textit{absolute} number of detections is still greater.
+The fraction decreases because a 10 year mission detects more `marginal' sources that are just on the cusp of the detection threshold and these sources have the worst sky localisation and thus cannot be confirmed to lie within the Galactic plane.}.
+
+Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least 15(22) BHBHs, 12(18) BHNSs and 19(27) NSNSs that are distinguishable from the WDWD population.
 
@@
 
-\todo{}
+The problem of separating the BHBH, BHNS and NSNS population can be more difficult.
+We can follow a similar method to the WDWDs (see Sec.~\ref{sec:WDWD_distinguish}) by applying our knowledge of the maximum mass of a neutron star.
+Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
+For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is 5(11) for BHBHs, 4(8) for BHNSs and 11(21) for NSNSs.
+For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.
+
+Another possible solution would be the existence of electromagnetic counterparts to the gravitational wave signal.
+In the next section (Sec.~\ref{sec:pulsar_matching}) we consider the possibility of detecting a pulsar within a BHNS or NSNS system.
+This could be used to identify the type of the source, however it is unlikely that a large fraction of the population will contain pulsars that are beaming towards the Earth.
+
+One could also consider using the eccentric or orbital frequency to separate the populations since the distributions are reasonable different for each DCO type (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+This method would also pose a challenge as it would likely only favour one DCO type as the source of the signal rather than provide strong evidence as the chirp mass could.
 

### 2021-06-18 paper/tex/sections/results.tex
finish distinguishing

@@
 In this section we present our main results for the detectable LISA DCO population.
-We find that, for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval.
+We find that, for our fiducial model, a four 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval.
 We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
@@
 \todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
-We find that for our fiducial model, a four year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval.
-Increasing the LISA mission length to ten years changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively.
+We find that for our fiducial model, a 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval.
+Increasing to a 10-year LISA mission length changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively.
 In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
@@
 Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals.
-The left axis and grid lines show the number of detections in a four year LISA mission and the right axis shows an approximation of the number of detections in a 10 year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
+The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
@@
     \includegraphics[width=\textwidth]{4_distribution_grid_4yr.pdf}
-    \caption{Distributions for various parameters of the DCOs that are detectable in a 4 year LISA mission in our fiducial model.
+    \caption{Distributions for various parameters of the DCOs that are detectable in a 4-year LISA mission in our fiducial model.
 Each panel shows the distribution of a single parameter, where the colour denotes the DCO type.
@@
 The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines.
-The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a four year LISA mission.
+The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a 4-year LISA mission.
 The dark shaded areas indicate regimes in which the quantity cannot be measured.
@@
 \subsection{Model variations}
-\todo{This will be about how the shapes of the parameter distributions change for the different model variations}
+\todo{This will be about how the shapes of the parameter distributions change for the different model variations.
+I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}

### 2021-06-18 paper/tex/sections/comparisons.tex
update comparisons

@@
 This table not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
-
-In a seminal work, \citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
-Their predictions of the number of detectable DCOs are very different from our own, where we find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
-However, since their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which likely strongly affect the expected detections rates.
-
-\citet{Belczynski+2010} built upon this work by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
-They found a similar number of BHBH and BHNS detection to \citet{Nelemans+2001}, but a lower number of NSNS detections.
-The low total detection rate for all DCOs in this paper is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
-The reduced mission length means that the source signal has much less time to accumulate, whilst many fewer WDWDs can be resolved in this time, leading to a weaker signal and an increased Galactic confusion noise relative to our work.
-
-More recently, \citet{Lamberts+2018} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
-\citet{Sesana+2020} followed up on this paper using the same simulated BHBH population and presented updated results for the number of expected BHBH detections.
-They find significantly fewer BHBHs than our fiducial model despite using the same SNR threshold and LISA mission length.
-
-The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
-Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \todo{needs citation, perhaps @Stephen knows?}.
-
-\citet{Lau+2020} investigated the number of Galactic NSNS binaries that could be detected by LISA.
-Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version.
-Despite this, their study found a much larger number of detections.
-They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions significantly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
-
-We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
-The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity, both changes that could decrease the NSNS detection rate given that we find most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
-
-Finally, \citet{Breivik+2020} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
-\todo{what I write here will depend how much the numbers change in upcoming run.
-Long story short is that they only have two metallicity bins and use the optimistic CE model.}.
-
-% find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-Although these are significantly different from our fiducial results, we make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
-Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 70, 38 and 15 detections respectively.
-The discrepancy in the NSNS rate is likely due to the fact that we assume that case BB mass transfer onto a NS is always stable but \citet{Breivik+2020} does not and this would significantly decrease our rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, model \modCaseBB{}) .
-The remaining differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
+We additionally do not include papers that don't use population synthesis or do not simulate sources in the Galactic plane \citep[e.g.][]{Andrews+2020, Kremer+2018} such that we only compare with papers with similar methodology and focus.
 
@@
 \end{figure*}
+
+In a seminal work, \citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
+Their predictions of the number of detectable DCOs are very different from our own, where we find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
+However, since their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which likely strongly affect the expected detections rates.
+
+\citet{Belczynski+2010} built upon this work by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
+They found a similar number of BHBH and BHNS detection to \citet{Nelemans+2001}, but a lower number of NSNS detections.
+The low total detection rate for all DCOs in this paper is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
+The reduced mission length means that the source signal has much less time to accumulate, whilst also fewer WDWDs can be resolved in this time, leading to a weaker signal and an increased Galactic confusion noise relative to our work.
+
+More recently, \citet{Lamberts+2018} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
+\citet{Sesana+2020} followed up on this paper using the same simulated BHBH population and presented updated results for the number of expected BHBH detections.
+They find significantly fewer BHBHs than our fiducial model despite using the same SNR threshold and LISA mission length.
+
+The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
+Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
+We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (Kummer et al.
+(in prep)).
+
+\citet{Lau+2020} investigated the number of Galactic NSNS binaries that could be detected by LISA.
+Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version.
+Despite this, their study found a much larger number of detections.
+They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
+However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
+
+We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
+\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
+The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity, both changes that could decrease the NSNS detection rate given that we find most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
+
+Finally, \citet{Breivik+2020} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
+They find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
+They make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
+Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 118, 52 and 7 detections respectively.
+Thus the NSNS rate is consistent but we find higher rates for the BHBHs and BHNSs.
+These differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.

### 2021-06-18 paper/tex/sections/results.tex
add commands make things consistent, update table

@@
 In this section we present our main results for the detectable LISA DCO population.
-We find that, for our fiducial model, a four 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs where the error bars represent the 90\% confidence interval.
+We find that on average, for our fiducial model, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
 We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
@@
 \todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
-We find that for our fiducial model, a 4-year LISA mission will detect \confinv{30.6}{20.5}{51.1} BHBHs, \confinv{26.4}{17.3}{48.5} BHNSs and \confinv{7.1}{4.8}{10.8} NSNSs, where the error bars represent the 90\% confidence interval.
-Increasing to a 10-year LISA mission length changes the number of detections to \confinv{50.6}{29.2}{63.3}, \confinv{46.2}{25.7}{99.3} and \confinv{12.1}{6.9}{13.5} respectively.
+We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
+Increasing to a 10-year LISA mission length changes the number of detections to \BHBHTenYear{}, \BHNSTenYear{} and \NSNSTenYear{} respectively.
 In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
@@
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
-\todo{subject to change with the updated/new models}}
+\todo{subject to change with the updated/new models and new uncertainty estimates}}
     \label{fig:detection_rates}

### 2021-06-18 paper/tex/sections/discussion.tex
new subsection on simple MW
fix typos

@@
 
-Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least 15(22) BHBHs, 12(18) BHNSs and 19(27) NSNSs that are distinguishable from the WDWD population.
+Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
 
@@
 Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
-For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is 5(11) for BHBHs, 4(8) for BHNSs and 11(21) for NSNSs.
+For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) for BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) for BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) for NSNSs.
 For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.
@@
 
+\subsection{Assessing the effect of an improved Milky Way model}
+\tom{I'm going to run everything with a simple model (maybe copy Breivik+2020) and see how the results change.}
+
 \subsection{Caveats}\label{sec:caveats}

### 2021-06-18 paper/tex/sections/conclusion.tex
add conclusions

We used the rapid population synthesis code COMPAS to simulate over a billion binaries and place them in an empirically-informed analytical model of the Milky Way in order to estimate and investigate the LISA detectable population of BH and NS binaries.

\tom{I'm not sure exactly what to write here, but I figure perhaps something about what we did in the paper and why it is an improvement on previous work (similar to introduction)?}

Our main conclusions can be summarised as:
\begin{itemize}
    \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
    \item \textbf{Black hole mass distribution:} Due to the high metallicity of the Milky Way, we find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA is skewed heavily towards lower masses, with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively. Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
    \item \textbf{Eccentricity distribution:} Unlike the more numerous WDWD LISA population, we find that BH and NS binaries still have significant eccentricities during the LISA mission. It will therefore be important to consider the analysis of LISA data for eccentric sources as they may have many detectable harmonics. We find that 86(35)\% of BHBHs, 46(16)\% of BHNSs and 86(31)\% of NSNSs have eccentricity of $e > 0.01(0.1)$ at the start of the LISA mission.
    \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds. Conversely, the BHNS rate varies widely with physics variation, ranging from a mean of 4 to 138. The NSNS shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission, we estimate that of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD. Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
    \item \textbf{Joint SKA-LISA detections:} Using some analytical estimations, we approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6. This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
    \item \textbf{Importance of metallicity-dependent MW model:} \tom{I'll fill this in with whatever I find in my sim (see subsection in discussion)}
\end{itemize}

### 2021-06-18 paper/tex/sections/results.tex
add conclusions

@@
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-\todo{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
+\tom{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
 We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
@@
 
-\todo{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
+\tom{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
 We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke.
@@
 \subsubsection{Metallicity}
-\todo{Returning to this once I've made the plot that compares the Milky Way distribution and formation rates}
+\tom{Returning to this once I've made the plot that compares the Milky Way distribution and formation rates}
 
@@
 \subsection{Model variations}
-\todo{This will be about how the shapes of the parameter distributions change for the different model variations.
+\tom{This will be about how the shapes of the parameter distributions change for the different model variations.
 I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}

### 2021-06-19 simulation/src/galaxy.py
add simply milky way (Breivik) function

@@ -241,3 +241,75 @@ def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
         return tau, D, Z, (R, z, theta)
     else:
         return tau, D, Z
+
+def simulate_simple_mw(n_binaries, ret_pos=False):
+    """Generate a simple Milky Way based on the model used in Breivik+2020.
+
+    Parameters
+    ----------
+    n_binaries : `int`
+        How many binaries to place in the Milky Way
+    """
+
+    masses = [8.9e9, 4.32e10, 1.44e10]
+    m_tot = np.sum(masses)
+    totals = np.array([int((masses[i] / m_tot * n_binaries).round(0)) for i in range(len(masses))])
+    totals[-1] = n_binaries - np.sum(totals[:-1])
+
+    tau = np.zeros(n_binaries) * u.Gyr
+    radius = np.zeros(n_binaries) * u.kpc
+    height = np.zeros(n_binaries) * u.kpc
+    Z = np.array([0.02] * totals[0:2].sum() + [0.003] * totals[-1])
+
+    cursor = 0
+    # bulge
+    tau[cursor:cursor + totals[0]] = np.random.uniform(9, 10, totals[0]) * u.Gyr
+
+    # the following code block is taken from COSMIC Github
+    # https://github.com/COSMIC-PopSynth/COSMIC/blob/v3.3.0/cosmic/MC_samp.py#L266-L287
+    r_save = []
+    z_save = []
+    # sample double exp func and then rejection sample
+    while len(r_save) < totals[0]:
+        rcut = 2.1
+        q = 0.5
+        r0 = 0.075
+        alpha = -1.8
+        r = np.random.uniform(0, 5, totals[0] * 10)
+        z = np.random.uniform(0, 3, totals[0] * 10)
+        prob = np.random.uniform(0, 1, totals[0] * 10)
+        sample_func = np.exp(-(r**2 + (z / q)**2) / rcut**2)
+        actual_func = (1 + np.sqrt((r**2 + (z / q)**2)) / r0)**(alpha) * sample_func
+        indSave, = np.where(prob < actual_func)
+        for ii in indSave:
+            r_save.append(r[ii])
+            z_save.append(z[ii])
+    r = np.array(r_save[:totals[0]])
+    z = np.array(z_save[:totals[0]])
[…]

### 2021-06-19 simulation/src/simulate_DCO_detections.py
update simulation to allow simple mw

@@ -5,7 +5,7 @@ import getopt
 import sys
 
 from compas_processing import get_COMPAS_vars, mask_COMPAS_data
-from galaxy import simulate_mw
+from galaxy import simulate_mw, simulate_simple_mw
 import legwork as lw
 
 SNR_CUTOFF = 7
@@ -26,12 +26,13 @@ def usage():
 def main():
     # get command line arguments and exit if error
     try:
-        opts, _ = getopt.getopt(sys.argv[1:], "hi:o:n:t:f", ["help",
+        opts, _ = getopt.getopt(sys.argv[1:], "hi:o:n:t:fs", ["help",
                                                              "input=",
                                                              "output=",
                                                              "loops=",
                                                              "binary-type=",
-                                                             "opt-flag"])
+                                                             "opt-flag",
+                                                             "simple-mw"])
     except getopt.GetoptError as err:
         print(err)
         usage()
@@ -43,6 +44,7 @@ def main():
     loops = 10
     binary_type = "BHNS"
     pessimistic = True
+    use_simple_mw = False
 
     # change defaults based on input
     for option, value in opts:
@@ -59,12 +61,13 @@ def main():
             binary_type = value
         if option in ("-f", "--opt-flag"):
             pessimistic = False
+        if option in ("-s", "--simple-mw"):
+            use_simple_mw = True
 
     # open COMPAS file
     with h5.File(input_filepath, "r") as COMPAS_file:
         # mask only required DCOs
-        dco_mask = mask_COMPAS_data(COMPAS_file, binary_type, (True, True,
-                                                               pessimistic))
+        dco_mask = mask_COMPAS_data(COMPAS_file, binary_type, (True, True, pessimistic))
 
         # get all relevant variables
         compas_m_1, compas_m_2,\
@@ -86,9 +89,8 @@ def main():
 
     # work out metallicity bins
     compas_Z_unique = np.unique(compas_Z)
-    inner_bins = np.array([compas_Z_unique[i]
-                           + (compas_Z_unique[i+1] - compas_Z_unique[i])
-                           / 2 for i in range(len(compas_Z_unique) - 1)])
[…]

### 2021-06-19 simulation/slurm/generate_scripts.py
add simple mw script to generation

@@ -3,7 +3,9 @@ sys.path.append("../src/")
 from variations import variations
 
 
-def create_file(bt, file):
+def create_file(bt, file, simple_mw=False):
+    script_file = "scripts/{}_{}.sh".format(bt, file)
+
     lines = []
     lines.append("#!/bin/bash\n")
     lines.append("#SBATCH -J {}_{}\n".format(bt, file))
@@ -19,15 +21,22 @@ def create_file(bt, file):
 
     lines.append("module load Anaconda3/2020.11\n")
     lines.append("source activate lisa\n")
-    if file == "optimistic":
-        lines.append('python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/fiducial/COMPASOutputReduced.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 --opt-flag -t ' + '{}\n'.format(bt))
-    else :
-        lines.append('python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputReduced.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 -t ' + '{}\n'.format(bt))
 
-    with open("scripts/{}_{}.sh".format(bt, file), "w") as f:
+    main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputReduced.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 -t ' + '{}\n'.format(bt)
+    if file == "optimistic":
[…]

### 2021-06-19 simulation/slurm/generate_scripts.py
update to new files

@@ -22,16 +22,16 @@ def create_file(bt, file, simple_mw=False):
     lines.append("module load Anaconda3/2020.11\n")
     lines.append("source activate lisa\n")
 
-    main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputReduced.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 -t ' + '{}\n'.format(bt)
+    main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputCombined.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 -t ' + '{}\n'.format(bt)
     if file == "optimistic":
         main_line = main_line.replace("\n", " --opt-flag\n")
     if simple_mw:
-        main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputReduced.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/simple_mw_{0}_{1}_'.format(bt, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 --simple-mw -t ' + '{}\n'.format(bt)
[…]

### 2021-06-20 simulation/output/combine_output.py
update scripts for simple mw

@@ -18,90 +18,97 @@ dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("MT2_case", np.dtype(int)), ("a_ZAMS", dt), ("a_pre_SN2", dt),
          ("kick_1", dt), ("kick_2", dt), ("e_pre_SN2", dt)]
 
-runs = 50
-
 floor_path = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
 
-# loop over all binary types and physics variations
-for bt in ["BHBH", "BHNS", "NSNS"]:
-    for v in range(len(variations)):
-        full_data = None
-        n_ten_year = np.array([], dtype=np.int)
-        total_weight = np.array([], dtype=np.float)
-        n_runs = 0
-        missing = []
+def combine_data(dco_type, variation, simple_mw=False, runs=50):
+    full_data = None
+    n_ten_year = np.array([], dtype=np.int)
+    total_weight = np.array([], dtype=np.float)
+    n_runs = 0
+    missing = []
 
-        # loop over each run
-        for i in range(1, runs + 1):
-            # check individual file exists
-            fname = "{}_{}_{}.h5".format(bt, variations[v]["file"], i)
-            if isfile(fname):
-                n_runs += 1
-
-                # open file and copy contents
-                with h5.File(fname, "r") as f:
-                    n_curr = f["simulation"].attrs["n_ten_year"].astype(np.int)
-                    n_ten_year = np.concatenate((n_ten_year, n_curr))
-
-                    total_temp = f["simulation"].attrs["total_MW_weight"]
-                    total_weight = np.concatenate((total_weight, total_temp))
-                    if full_data is None:
-                        full_data = f["simulation"][...].squeeze()
-                    else:
-                        add_data = f["simulation"][...].squeeze()
-                        prev_len = len(full_data)
-                        full_data.resize(prev_len + len(add_data))
-                        full_data[prev_len:] = add_data
-            else:
-                missing.append(i)
-
-        # as long as there is at least one file
-        if len(missing) != runs:
-            # let the user know which ones are currently missing
-            print(v, len(missing), missing)
-
-            # work out the formation channels
-            model = variations[v]["file"]
-            if model == "optimistic":
-                model = "fiducial"
-            floor_file = floor_path \
-                + "{}/COMPASOutputReduced.h5".format(model)
[…]

### 2021-06-20 simulation/slurm/generate_scripts.py

@@ -3,32 +3,31 @@ sys.path.append("../src/")
 from variations import variations
 
 
-def create_file(bt, file, simple_mw=False):
-    script_file = "scripts/{}_{}.sh".format(bt, file)
+def create_file(dco_type, file, simple_mw=False):
+    script_file = "scripts/{}_{}.sh".format(dco_type, file)
 
     lines = []
     lines.append("#!/bin/bash\n")
-    lines.append("#SBATCH -J {}_{}\n".format(bt, file))
+    lines.append("#SBATCH -J {}_{}\n".format(dco_type, file))
     lines.append("#SBATCH -n 6\n")
     lines.append("#SBATCH -N 1\n")
     lines.append("#SBATCH -p serial_requeue\n")
     lines.append("#SBATCH --mem 6000\n")
     lines.append("#SBATCH -t 00-10:00\n")
-    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.out\n".format(bt, file))
-    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.err\n".format(bt, file))
+    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.out\n".format(dco_type, file))
+    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.err\n".format(dco_type, file))
     lines.append("#SBATCH --mail-user thomas.wagg@cfa.harvard.edu\n")
     lines.append("#SBATCH --mail-type ALL\n")
 
     lines.append("module load Anaconda3/2020.11\n")
     lines.append("source activate lisa\n")
 
[…]

### 2021-06-20 paper/tex/sections/discussion.tex
add discussion section about simple MW model

@@
 \subsection{Assessing the effect of an improved Milky Way model}
-\tom{I'm going to run everything with a simple model (maybe copy Breivik+2020) and see how the results change.}
+In this section, we repeat our analysis using a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model.
+For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in previous works.
+
+Their model can be summarised as follows: it is made up of three components, a thin disc, a thick disc and a bulge.
+The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}.
+\citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
+Most differently, only two metallicities are used and assigned independent of age or position.
+Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
+
+We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
+The two major differences we can see in these plots is that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
+In addition, though it can't be seen in these plots, the simpler prescriptions for the birth times mean that the star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and much more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
+    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \label{fig:simple_mw}
+\end{figure}
+
+We find that using this simpler Milky Way model with our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
+Thus the BHBH and BHNS detection rates are only marginally increased but the NSNS detection is overestimated by nearly a factor of 2.
+
+Moreover, the distribution of parameters within the population, especially the mass distributions are notably disparate.
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
+(in prep)).
+For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
+Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.
+Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions drop sharply to zero at lower masses than our fiducial results.
+
+The unphysical artifacts present in the mass distributions can have far-reaching effects since the masses of DCOs affect most other parameters.
+The inspiral time and SNR are directly dependent on the mass, whilst the uncertainty estimates depend on the SNR.
+This means that the artifacts can affect the predictions for most distributions of LISA detectable populations.
+
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \label{fig:bh_mass_simple_mw}
+\end{figure}
 

### 2021-06-20 paper/tex/sections/discussion.tex
proofread the simple mw subsection

@@
 
-\subsection{Assessing the effect of an improved Milky Way model}
-In this section, we repeat our analysis using a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model.
-For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in previous works.
+\subsection{Assessing the impact of Milky Way model choices}
+In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model.
+For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.
 
-Their model can be summarised as follows: it is made up of three components, a thin disc, a thick disc and a bulge.
+Their model can be summarised as follows: the Milky Way is assumed to comprise of three components, a thin disc, a thick disc and a bulge.
 The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}.
 \citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
-Most differently, only two metallicities are used and assigned independent of age or position.
+A major difference is that only two metallicities are used and they are assigned independent of age or position.
 Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
@@
 We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
-The two major differences we can see in these plots is that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
-In addition, though it can't be seen in these plots, the simpler prescriptions for the birth times mean that the star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and much more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
+The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
+In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
 
@@
 
-We find that using this simpler Milky Way model with our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
-Thus the BHBH and BHNS detection rates are only marginally increased but the NSNS detection is overestimated by nearly a factor of 2.
+We find that when applying this simpler Milky Way model and our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
+Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection is overestimated by nearly a factor of 2.
 
-Moreover, the distribution of parameters within the population, especially the mass distributions are notably disparate.
+Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
 By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
@@
 Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.
-Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions drop sharply to zero at lower masses than our fiducial results.
+Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.
 
@@
 
-\begin{figure}[b]
+Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.
+
+\begin{figure}[h]
     \centering

### 2021-06-20 paper/tex/sections/conclusion.tex
add simple MW conclusion

@@
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
-    \item \textbf{Importance of metallicity-dependent MW model:} \tom{I'll fill this in with whatever I find in my sim (see subsection in discussion)}
+    \item \textbf{Importance of metallicity-dependent MW model:} The use of Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position may lead to an overestimation of the LISA NSNS detection rate.
+It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.
 \end{itemize}

### 2021-06-20 paper/tex/sections/discussion.tex
justify calling it simpler a bit better

@@
 \subsection{Assessing the impact of Milky Way model choices}
-In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model.
+The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries.
+In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of these added features.
 For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.
@@
 The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
-In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
+% leaving this out for now as it didn't come up later
+%In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering

### 2021-06-20 paper/tex/sections/conclusion.tex
Updates from Overleaf

@@
 We used the rapid population synthesis code COMPAS to simulate over a billion binaries and place them in an empirically-informed analytical model of the Milky Way in order to estimate and investigate the LISA detectable population of BH and NS binaries.
-
-\tom{I'm not sure exactly what to write here, but I figure perhaps something about what we did in the paper and why it is an improvement on previous work (similar to introduction)?}
 
@@
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
-    \item \textbf{Importance of metallicity-dependent MW model:} The use of Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position may lead to an overestimation of the LISA NSNS detection rate.
+    \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
+The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate.
 It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.

### 2021-06-20 paper/tex/sections/abstract.tex
a first attempt at an abstract

@@
-\noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\
+We present predictions for the main properties of the LISA detectable population of Galactic double black holes (BHBH), black hole neutron stars (BHNS) and double neutron stars (NSNS).
+For calculating these predictions, we use an extensive sample of double compact objects (DCOs) produced using rapid population synthesis in tandem with an empirically-informed analytical model of the Milky Way that accounts for the chemical enrichment history of the galaxy.
+We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common envelope, supernova and wind mass loss physics.
+We find that for a 4(10)-year mission, LISA will detect on average \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
+The BHBH rate remains notably consistent under different physics assumptions, whilst in contrast the BHNS and NSNS rates each vary over 3 orders of magnitude.
+We discuss potential strategies for distinguishing this population from the more numerous double white dwarf population as well as for separating the BHBH, BHNS and NSNS populations from each other.
+We additionally assess the possibility of joint SKA-LISA detections for systems that contain pulsars.

### 2021-06-30 paper/tex/sections/abstract.tex
some feedback updates

@@
-We present predictions for the main properties of the LISA detectable population of Galactic double black holes (BHBH), black hole neutron stars (BHNS) and double neutron stars (NSNS).
-For calculating these predictions, we use an extensive sample of double compact objects (DCOs) produced using rapid population synthesis in tandem with an empirically-informed analytical model of the Milky Way that accounts for the chemical enrichment history of the galaxy.
+We present predictions for the properties of the LISA detectable population of Galactic double black holes (BHBH), black hole neutron stars (BHNS) and double neutron stars (NSNS).
+We use an extensive sample of double compact objects (DCOs) produced using rapid population synthesis in tandem with an empirically-informed analytical model of the Milky Way that accounts for the chemical enrichment history of the galaxy.
 We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common envelope, supernova and wind mass loss physics.

### 2021-06-30 paper/tex/sections/introduction.tex
some feedback updates

@@
-Since the first direct observation of gravitational waves by the LIGO scientific collaboration in 2015 \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive binary stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
+Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive binary stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
 
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
+The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new frequency regime of gravitational waves.
 LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
 Moreover, this frequency regime is also of interest for the detection of local stellar mass binaries during their inspiral phase.
-This means that LISA will be able to detect, and possibly localise a binary on the sky, many years in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
-In addition, LISA will be able to measure the eccentricities of double compact objects (DCO) that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
+LISA will be able to detect, and possibly localise a double compact object (DCO) on the sky many years in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+In addition, LISA will be able to measure the eccentricities of DCOs that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
 The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger.
 This means that LISA stellar mass sources can only be detected in local galaxies, with the majority residing in the Milky Way.
-Therefore, these sources could be used as a probe for our galaxy's history and evolution \citep[e.g.][]{Korol+2019}.
+Therefore, these sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.
 
-Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
+Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
 More recently, interest has grown in the detection of NS and BH binaries.
-Although they are rare, LISA detections of these sources could be useful for learning more about the evolution and endpoints of massive stars.
+Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars.
 In this paper we focus on NS and BH binaries.
 
-For the purposes of this investigation, we consider the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011}.
-There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
-
 Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been detected \citep[e.g.][]{Abbott+2017_NSNS}.
-The detection of a NSNS in LISA in which at least one NS is a pulsar could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
+The detection of a NSNS in LISA with a pulsar component could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
 NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
@@
 Double black hole (BHBH) binaries in the Milky Way present a greater observational challenge.
-To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH binary.
+To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH.
 The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
 This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
-These observations suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which no black holes or neutron stars are observed \citep{Ozel+2010,Farr+2011} but its existence remains an open question \citep[e.g.][]{Kreidberg+2012}.
+These observations of X-ray binaries suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which there are no strong candidates for either black holes or neutron stars \citep{Ozel+2010,Farr+2011} but the gap's existence remains an open question \citep[e.g.][]{Kreidberg+2012, Mandel+2020}.
 Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged \citep{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
@@
 A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
-These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
+These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
 
-The detection of DCOs with LISA has been investigated in several previous studies, yet studies that focus on BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon.
-Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
+For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
+We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.
+These channels include: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017, Toonen+2020} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
 
+Earlier work on BH and NS binaries in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
 We build upon previous efforts but with several important improvements.
 We explore the effect of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}.
+We use a model for the Milky Way that accounts for the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citet{Lamberts+2019, Sesana+2020}).
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.

### 2021-06-30 paper/tex/sections/methods.tex
move plots around
some feedback updates

@@
 
-We use a population of binaries recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
+We use the grid of binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
 (in prep).
-This population is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
-COMPAS follows the approach of the pioneering population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of millions of binary systems.
+This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
+COMPAS follows the approach of the pioneering population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
 The code is open source and documented in the papers listed above and the on-line documentation.
@@
 We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
-We assume that all binaries are circular at birth to reduce the dimensions of initial parameters.
+We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
 Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
@@
 
-For each metallicity $Z$, we thus have a sample of binaries, each with a set of parameters
+For each metallicity $Z$, the simulations result in a sample of binaries, each with a set of parameters
 \begin{equation}
@@
 
-\subsubsection{Physical assumptions in fiducial model}\label{sec:fiducial_physics}
+\subsubsection{Physical assumptions in the fiducial model}\label{sec:fiducial_physics}
 In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
@@
 We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
-The maximum accretion rate for double compact objects is limited to the Eddington accretion rate.
+The maximum accretion rate for compact objects is limited to the Eddington accretion rate.
 If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star, thus varying $\beta$ \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
@@
 In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
-Lastly, model \modNoBH{} removes the natal kick for all black holes.
+Model \modNoBH{} removes the natal kick for all black holes.
 
@@
 \textit{Star formation history:} 
-We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-$\alpha$ disks, where the two disks transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
+We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-$\alpha$ discs, where the two discs transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
 \begin{equation}\label{eq:thin_disc_tau}
@@
 
-Although \citet{Frankel+2018} only fit this model for the low-$\alpha$ disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disk and the bar, but focusing on the chemical tracks more representative to the inner disk and large ages.
+Although \citet{Frankel+2018} only fit this model for the low-$\alpha$ disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disc and the bar, but focusing on the chemical tracks more representative to the inner disc and large ages.
 \citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-$\alpha$ discs, the Milky Way abundance distributions could be well reproduced.
@@
 
-We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by randomly drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.
+We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.
 
@@
 For a full derivation of the equations given below please see the LEGWORK release paper (Wagg et al.
-in prep) or \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
+in prep) or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
 
@@
 
-Ea ch binary loses orbital energy to gravitational waves throughout its lifetime.
+Each binary loses orbital energy to gravitational waves throughout its lifetime.
 This causes the binary to shrink and circularise over time.
@@
 5.13]{Peters+1964} given the initial conditions.
-This additionally can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq.
+This can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq.
 5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.

### 2021-06-30 paper/tex/sections/introduction.tex
full methods feedback complete

@@
 
-Earlier work on BH and NS binaries in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
+In this paper, we present predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
+We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
+
+Earlier work on BHBHs, BHNSs and NSNSs in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
 We build upon previous efforts but with several important improvements.
 We explore the effect of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that accounts for the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citet{Lamberts+2019, Sesana+2020}).
+We use a model for the Milky Way that accounts for the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with over a billion simulated massive binaries evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}.
+Moreover, our binary population synthesis simulation is the most extensive of its kind to date and make use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.
+Overall we simulate over 2 billion massive binaries to produce the DCO populations used in this work.
 We find that this large number of simulations is important to reduce the sampling noise.
-In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce this sampling noise.
-
-In this paper, we present predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
-We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
 
@@
 In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
-In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+In a companion paper, Wagg et al.
+(in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 

### 2021-06-30 paper/tex/sections/methods.tex
full methods feedback complete

@@
 (in prep).
-This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS}\footnote{\url{https://compas.science}} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
+This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
 COMPAS follows the approach of the pioneering population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
-The code is open source and documented in the papers listed above and the on-line documentation.
-An extensive method paper is forthcoming (Team COMPAS: J.
+The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper (Team COMPAS: J.
 Riley et al.
@@
 
-One million binaries are simulated for 50 metallicity bins equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-These bins span the allowed metallicities range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
+Between 1 and 100 million massive binaries are simulated for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+More binaries are simulated for higher metallicities to account for the lower formation rate of DCOs.
+These bins span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
 This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
@@
 The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass is drawn using the mass ratio of the binary, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.
-with][]{Sana+2012}.
-We additionally restrict $m_2 \ge 0.1 \unit{M_{\odot}}$, since this is approximately the minimal mass for a main sequence star.
+The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.\ with][]{Sana+2012}.
+We additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
 We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
 We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised during mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
-In addition, we apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
+Since we focus on post-interaction binaries which will have circularised after mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
+
+We apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
 This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL.
+for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
 We sample from these sets of parameters when creating synthetic galaxies.
 
-\subsubsection{Physical assumptions in the fiducial model}\label{sec:fiducial_physics}
+\subsubsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
 In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
 
-\textit{Stellar Evolution:} To follow the evolution of massive stars, COMPAS relies on fitting formula by \citet{Hurley+2000} to detailed single star models by \citet{Pols+1998}.
-COMPAS implements stellar wind mass loss using the prescriptions from \citet{Belczynski+2010b} and models the evolution of stars that lose or gain mass closely following the algorithms originally described in \citet{Tout+1996} and \citet{Hurley+2002}.
-For more information about the implementation of the single star evolution in COMPAS see the corresponding section in the upcoming methods paper (Team COMPAS: J.
-Riley et al.
-(in prep)).
+\textit{Stellar Evolution:} To follow the evolution of massive stars, COMPAS relies on fitting formulae by \citet{Hurley+2000} to detailed single star models by \citet{Pols+1998}.
+COMPAS models the evolution of stars that lose or gain mass closely following the algorithms originally described in \citet{Tout+1996} and \citet{Hurley+2002}.
 
 \textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
-The mass transfer efficiency, $\beta = \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
+The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
 We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
 The maximum accretion rate for compact objects is limited to the Eddington accretion rate.
-If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star, thus varying $\beta$ \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
+If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
 We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.
@@
 For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004}.
+We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
 This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
-We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections.
+We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections, likely leading to a stellar merger.
 
@@
 We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
-Additionally, we use a separate, higher wind mass loss rate for LBV stars, since these experience eruptive mass loss in addition to the regular line-driven winds and we follow \citet{Belczynski+2008} in setting $f_{\rm LBV} = 1.5$.
-We also use their Wolf-Rayet-like mass loss rate for helium stars and set $f_{\rm WR} = 1$.
+Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observer LBV eruptions for stars with luminosities and  effective temperatures above the Humphrey Davidson limit.
+We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars and set $f_{\rm WR} = 1$.
 See Team COMPAS: J.
@@
 In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
-Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these are outlined in Table~\ref{tab:physics_variations}.
+Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
 
@@
 But the bulge was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
-To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$
+To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+We show these distributions in the first panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
 
@@
 We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-$\alpha$ disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
+We show the combination of these distributions in the second panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
 
@@
 \todo{@Neige, did I justify the bulge/bar height correctly?
-A: The vertical distribution should not influence at which radius the bar should stop forming stars -- more later}
+A: The vertical distribution should not influence at which radius the bar should stop forming stars -- more later}.
+We show the combination of these distributions in the last panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
 
-\textit{Metallicity-radius-time relation:} The relation is given by \citep[][Eq. 7]{Frankel+2018}
+\textit{Metallicity-radius-time relation:} To account for the chemical enrichment of star forming gas as the Milky Way evolves, we adopt the relation given by \citep[][Eq. 7]{Frankel+2018}
 \begin{equation}\label{eq:galaxy_FeH}
@@
 The magnitude of the systemic kicks are typically small compared to the initial circular velocity of a binary at each Galactocentric radius.
-Therefore, kicks will not significantly alter the overall distribution of their positions.
+Therefore, we expect that kicks will not significantly alter the overall distribution of their positions.
 Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.
@@
 
-Each binary loses orbital energy to gravitational waves throughout its lifetime.
+Each DCO loses orbital energy to gravitational waves throughout its lifetime.
 This causes the binary to shrink and circularise over time.

### 2021-06-30 paper/tex/sections/methods.tex

@@
 
-Each DCO loses orbital energy to gravitational waves throughout its lifetime.
+Each binary loses orbital energy to gravitational waves throughout its lifetime.
 This causes the binary to shrink and circularise over time.
@@
 This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF.
-For a more in-depth discussion of this process see Appendix~\ref{app:rate_normalisation}.
+For more details see Appendix~\ref{app:rate_normalisation}.
 

### 2021-06-30 paper/tex/sections/results.tex
update detection rate plot

@@
 In this section we present our main results for the detectable LISA DCO population.
-We find that on average, for our fiducial model, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
-We first show the distribution of the sources on the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
+We find that on average, for our fiducial model, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}).
+We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
 
@@
     \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
+    \caption{Density distribution of detectable BHBH, BHNS and NSNS binaries are shown together with the LISA sensitivity curve.
+In the top panel we show all systems with the LISA verification binaries over plotted (star symbols, \citealp{Kupfer+2018}).
+In the bottom panels we separate by type.
+Contours show the percentage of the population enclosed.
+The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight.
+For reference we show lines where a circular binary of average mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line).
+To highlight the role of eccentricity we further show the signal expected for an eccentric binary at 30 kpc.
+The coloured line in the bottom panels shows a contour that encloses 90\% of the population that is circular.
+See Sec.~\ref{sec:dcos_on_sc} for a discussion.}
     \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
@@
 
-We illustrate the distribution of detectable DCOs on the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel) and the more numerous WDWD population \citep[e.g.][]{Korol+2017}.
+We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
+This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel).
 This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency.
-This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs.
-There are several other notable features in these distributions and we plot grid lines of constant distance and inspiral time to help to explain the shape of the distribution.
+This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs probabilistically.
+There are several other notable features in these distributions and to understand these we overplot reference lines indicating where a circular binary with the average chirp mass (annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).
 
-The straight diagonal lines show where a binary at a fixed distance and with the average chirp mass (annotated in each panel) would lie on the sensitivity curve for different frequencies.
-We would therefore expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
+We would expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
 From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$.
@@
     \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 50\% (solid) and 90\% (dotted) confidence intervals.
+Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties.
+An arrow indicates that the error bar extends to zero.
 The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).

### 2021-06-30 paper/tex/sections/results.tex
reduce detectable properties grid to 6 panels
Updates from Overleaf

@@
 See Sec.~\ref{sec:dcos_on_sc} for a discussion.}
-    \caption{Density distribution of detectable DCOs plotted over the LISA sensitivity curve, where each panel corresponds to \textbf{top:} combined density plot for all DCO types (BHBH, BHNS and NSNS) \textbf{bottom:} three panels with individual density distribution of different DCO types.
-In each panel, we plot the total signal of binaries at their dominant frequency $n f_{\rm orb}$, such that $n$ is the harmonic that produces the most relative gravitational wave luminosity ($n = 2$ for circular binaries).
-If the density of points is below our lowest contour (2\%) then we plot the points as scatter points, where their sizes corresponds to their STROOPWAFEL weights.
-The inset colourbars indicate the percentage of the population represented by each contour and the annotated mass is the average chirp mass for all binaries in the panel, which is used in plotting the grid lines.
-We plot diagonal lines of constant distance, where the straight lines show the signal for a circular binary of average chirp mass, whilst the curved line shows the signal for an eccentric binary with $e = 0.98$.
-The vertical lines indicate the inspiral time for a circular binary with the average chirp mass.
-In the top panel we overlay the LISA verification binaries from \citet{Kupfer+2018}.
-In the bottom panels we add the 90\% contour line for only the circular sources to show how the distribution changes without eccentric sources present.}
     \label{fig:dcos_on_sc}
@@
 
-\subsection{Distributions for the fiducial model}\label{sec:fiducial_distributions}
+\subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
 
@@
 For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$.
-This is because, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation.
+Unlike ground-based detector, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
+In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting the less massive black holes.
 The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.

### 2021-06-30 paper/tex/sections/results.tex

@@
     \centering
-    \includegraphics[width=\textwidth]{4_distribution_grid_4yr.pdf}
-    \caption{Distributions for various parameters of the DCOs that are detectable in a 4-year LISA mission in our fiducial model.
-Each panel shows the distribution of a single parameter, where the colour denotes the DCO type.
-We also plot the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping) with the dark and light shaded areas respectively.
-The first two rows (excluding metallicity) use kernel density estimators to show the distributions.
-The dotted lines in the black hole mass panel show the individual distributions of the primary and secondary masses.
-The metallicity panel shows the distribution over the metallicity bins used in our population synthesis, which we show in the grid lines.
-The final three panels for the cumulative distribution functions for observables, normalised to the expected number of fiducial detections in a 4-year LISA mission.
-The dark shaded areas indicate regimes in which the quantity cannot be measured.
-The dotted lines in the angular resolution plot show the maximum angular resolution that can be covered by a single pointing of the labelled instrument.
-In Section~\ref{sec:fiducial_distributions} we discuss the features of the distributions.}
+    \includegraphics[width=\textwidth]{4_detectable_properties_4yr.pdf}
+    \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model.
+Each panel shows a kernel density estimator for a single property, coloured by DCO type.
+The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions.
+See Sec.~\ref{sec:fiducial_distributions} for a discussion.}
     \label{fig:fiducial_pdf_distributions}
 \end{figure*}
+
+\subsubsection{Orbital Frequency}
+The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
+This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
+The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
+These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
+Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
 
@@
 In addition, the Fryer remnant mass prescription gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
-
-\subsubsection{Orbital Frequency}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
-These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
 

### 2021-07-01 paper/tex/sections/abstract.tex
Updates from Overleaf

--- 2021-05-08 paper/tex/sections/abstract.tex
@@
-\noindent...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...\\
+We present predictions for the properties of the population of Galactic double black holes (BHBH), black hole neutron stars (BHNS) and double neutron stars (NSNS) that will be detectable by the planned space-based gravitational wave detector LISA.
+We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with an empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
+We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common envelope, supernova and wind mass loss physics.
+We find that for a 4(10)-year mission, LISA will detect on average about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
+The BHBH rate remains notably consistent under different physics assumptions, whilst in contrast the BHNS and NSNS rates each vary over 3 orders of magnitude.
+We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
+We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and SKA.

### 2021-07-01 paper/tex/sections/conclusion.tex
Updates from Overleaf

@@
-We used the rapid population synthesis code COMPAS to simulate over a billion binaries and place them in an empirically-informed analytical model of the Milky Way in order to estimate and investigate the LISA detectable population of BH and NS binaries.
+We used the rapid population synthesis code COMPAS to simulate over two billion massive binaries and place them in an empirically-informed analytical model of the Milky Way in order to estimate and investigate the LISA detectable population of BH and NS binaries.
 
@@
     \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-    \item \textbf{Black hole mass distribution:} Due to the high metallicity of the Milky Way, we find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA is skewed heavily towards lower masses, with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively.
+    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively.
 Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
-    \item \textbf{Eccentricity distribution:} Unlike the more numerous WDWD LISA population, we find that BH and NS binaries still have significant eccentricities during the LISA mission.
-It will therefore be important to consider the analysis of LISA data for eccentric sources as they may have many detectable harmonics.
-We find that 86(35)\% of BHBHs, 46(16)\% of BHNSs and 86(31)\% of NSNSs have eccentricity of $e > 0.01(0.1)$ at the start of the LISA mission.
+    \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities during the LISA mission, unlike the more numerous WDWD LISA population.
+We find that 86(20)\% of BHBHs, 46(8)\% of BHNSs and 86(12)\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
     \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
@@
 Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} Using some analytical estimations, we approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.
+    \item \textbf{Joint SKA-LISA detections:} We approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.

### 2021-07-01 paper/tex/sections/results.tex
Updates from Overleaf

@@
 
+\subsubsection{Eccentricity}
+The eccentricity distributions show that detectable BHBHs are the most likely to be highly eccentric of the three DCOs.
+This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
+However, these stronger kicks often instead result in disrupted or too-wide binaries in more weakly bound NSNSs.
+In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
+This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
+
+An eccentricity of $e = 0.01$ is the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}.
+We find that a significant fraction of DCOs (86\% of BHBHs, 46\% of BHNSs and 86\% of NSNSs) exceed this bound.
+This is in contrast to several previous work that assume all DCOs are circular once they reach the LISA mission.
+Moreover, we find that 20\%, 8\% and 12\% of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
+At this eccentricity the majority of the gravitational wave power is emitted in higher harmonics above the orbital frequency and thus the signal would appear at higher frequencies in LISA.
+
 \subsubsection{Luminosity Distance}
 Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-There is a clear bias in each distribution for systems at lower distances since closer binaries are easier to detect.
+There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect.
 This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.
+
+However, more surprisingly, we also see that the NSNS distribution extends to higher distances than the other DCOs.
+The reason for this is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.3$).
+The BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
+Therefore, despite their relatively higher masses, the maximum distance at which a source is detectable is generally lower than the eccentric NSNSs and hence the distribution tends to zero at smaller distances.
+Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$.
+Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA it must still be early in its evolution and thus have a low orbital frequencies.
+The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
+Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted.
+This means that NSNSs can be seen at the largest distances of the three DCO types.
 
@@
 This order is flipped due to the fact that high eccentricity results in a shorter merger time and we find that LISA detectable BHNSs are mostly circular, whilst BHBHs have a significant highly eccentric subpopulation.
-
-\subsubsection{Metallicity}
-\tom{Returning to this once I've made the plot that compares the Milky Way distribution and formation rates}
-
-\subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are the most eccentric of the three DCOs.
-This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often instead result in disrupted or too-wide binaries in more weakly bound NSNSs.
-In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
-This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
-
-A significant fraction of DCOs in each population have eccentricities greater than 0.01, the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}, which we indicate with the shaded area.
-We discuss the estimation of the eccentricity uncertainty further in Section~\ref{sec:measurement_uncertainties}
 
@@
 \subsubsection{Chirp mass uncertainty}
+
 The chirp mass uncertainty can be calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity.
@@
 
-We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in the lower centre panel of Fig.~\ref{fig:fiducial_pdf_distributions}.
-We show the distribution as a CDF that is normalised to the expected number of detections to better indicate the absolute number of detections that will have well determined chirp masses.
+We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
 We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/chirp_mass_uncertainty_4yr.pdf}
+    \caption{Cumulative distribution function for error on the chirp mass.
+Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+Shaded region indicates region with unmeasureable chirp mass.}
+    \label{fig:m_c_unc}
+\end{figure}
 
@@
 
-We plot the angular resolution in the last panel of Fig.~\ref{fig:fiducial_pdf_distributions} as a CDF normalised to the expected detection rate of each DCO.
+We plot the angular resolution in Fig.~\ref{fig:ang_res}.
 From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 square degrees.
@@
 
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{paper/figures/angular_resolution_4yr.pdf}
+    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
+    \label{fig:ang_res}
+\end{figure}
+
 \subsection{Model variations}

### 2021-07-01 paper/tex/paper.tex
Updates from Overleaf
eccentricity and chirp mass uncertainty
add new models and change commands to match
add commands make things consistent, update table
fix typos
add email
add corresponding author
make abstract centred (typo)
some feedback updates

@@
 \usepackage{fontawesome5}
+\usepackage{xcolor} % to add more color options
 
@@
 \newcommand{\tom}[1]{\textcolor{ForestGreen}{[Tom: #1]}}
-
+\newcommand{\floor}[1]{\textcolor{Bittersweet}{[Floor: #1]}}
 % custom function for adding units
@@
 \newcommand{\modCaseBB}{E}
-\newcommand{\modAlphaLow}{F}
-\newcommand{\modAlphaHigh}{G}
-\newcommand{\modOpt}{H}
-\newcommand{\modRapid}{I}
-\newcommand{\modNSLow}{J}
-\newcommand{\modNSHigh}{K}
-\newcommand{\modNoPISN}{L}
-\newcommand{\modSigLow}{M}
-\newcommand{\modSigLower}{N}
-\newcommand{\modNoBH}{O}
+\newcommand{\modCaseBBOpt}{F}
+\newcommand{\modAlphaLowest}{G}
+\newcommand{\modAlphaLow}{H}
+\newcommand{\modAlphaHigh}{I}
+\newcommand{\modAlphaHighest}{J}
+\newcommand{\modOpt}{K}
+\newcommand{\modRapid}{L}
+\newcommand{\modNSLow}{M}
+\newcommand{\modNSHigh}{N}
+\newcommand{\modNoPISN}{O}
+\newcommand{\modSigLow}{P}
+\newcommand{\modSigLower}{Q}
+\newcommand{\modNoBH}{R}
+\newcommand{\modWRLow}{S}
+\newcommand{\modWRHigh}{T}
 
-\newcommand{\modRangeMT}{B-E}
-\newcommand{\modRangeCE}{F-H}
-\newcommand{\modRangeSN}{I-O}
+\newcommand{\modRangeMT}{B-F}
+\newcommand{\modRangeCE}{G-K}
+\newcommand{\modRangeSN}{L-R}
+\newcommand{\modRangeML}{S-T}
+
+\newcommand{\nModels}{20}
+\newcommand{\nMinusOneModels}{19}
+
+\newcommand{\BHBHFourYear}{36}
+\newcommand{\BHNSFourYear}{33}
+\newcommand{\NSNSFourYear}{8}
+\newcommand{\BHBHTenYear}{56}
+\newcommand{\BHNSTenYear}{55}
+\newcommand{\NSNSTenYear}{13}
+
+\newcommand{\BHBHNotWDWDFour}{15}
+\newcommand{\BHNSNotWDWDFour}{10}
+\newcommand{\NSNSNotWDWDFour}{4}
+\newcommand{\BHBHNotWDWDTen}{22}
+\newcommand{\BHNSNotWDWDTen}{17}
+\newcommand{\NSNSNotWDWDTen}{7}
+
+\newcommand{\BHBHDistinguishedFour}{5}
+\newcommand{\BHNSDistinguishedFour}{4}
+\newcommand{\NSNSDistinguishedFour}{3}
+\newcommand{\BHBHDistinguishedTen}{11}
+\newcommand{\BHNSDistinguishedTen}{7}
+\newcommand{\NSNSDistinguishedTen}{5}
 
@@
 
+% \color{white}
+% \pagecolor{black}
+
 \begin{document}
@@
 % selma's newest catchy one
-\title{Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries}
+\title{Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA}
 
@@
 \affiliation{\UvA}
+\affiliation{\mpa}
 
-\begin{abstract}{
+\correspondingauthor{Tom Wagg}
+\email{tomjwagg@gmail.com}
+
+\begin{abstract}
     \input{sections/abstract.tex}
-}
 \end{abstract}
@@
 
-\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr and the members of the COMPAS collaboration for insightful discussions.
+\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions.
 This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.

### 2021-07-01 paper/tex/sections/appendix.tex
finish distinguishing
update appendix table
fix page positions in appendix

@@
 \section{Detection Rate Normalisation}\label{app:rate_normalisation}
-In this section we explain in detail the normalisation process that we refer to in Section~\ref{sec:gw_detection}.
-From each instance of the Milky Way that we simulate we can extract the fraction of targets that are detectable, where we define a target as one of BHBH, BHNS or NSNS that merges in a Hubble time.
-Note that we complete this calculation separately for each DCO type and each model variations.
+In this section we explain the normalisation process that we refer to in Section~\ref{sec:gw_detection}.
+From each simulated instance of the Milky Way we can extract the fraction of targets that are detectable, where we define a target as one of BHBH, BHNS or NSNS that merges in a Hubble time.
 
-We now explain how to convert the detectable fraction to a detection rate for the Milky Way. We write that the \textit{number} of detectable targets in the Milky Way is
+To convert the detectable fraction to a detection rate for the Milky Way, we write that the \textit{number} of detectable targets in the Milky Way is
 \begin{equation}\label{eq:norm_frame}
@@
 where $\avg{ \mathcal{R}_{\rm target} }$ is the average number of targets formed per star forming mass and $M_{\rm SF, MW}$ is the star forming mass of the Milky Way, meaning the total mass of every star ever formed in the Milky Way.
-We explain how to calculate each of these terms in respective subsections below.
 
 \subsection{Average target formation rate}
-Double compact object formation is strongly metallicity dependent, so we must find the average rate as the integral over metallicity
+Double compact object formation is metallicity dependent, so we find the average rate as the integral over metallicity, which is given by
 \begin{equation}\label{eq:norm_avg_target_formation}
@@
 \end{equation}
-where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ (which can be found using the distribution in \citealp{Frankel+2018}) and $\mathcal{R}_{\rm target, Z}$ is the number of targets formed per star forming mass.
+where $Z_{\rm min}, Z_{\rm max}$ are the minimum and maximum sampled metallicities, $p_Z$ is the probability of forming a star at the metallicity $Z$ (which can be found using the distribution in \citealp{Frankel+2018}) and $\mathcal{R}_{\rm target, Z}$ is the number of targets formed per star forming mass,
 \begin{equation}
@@
 \end{equation}
-In reality, this integral is instead approximated as a sum over the metallicity bins that we use in our simulation.
+In practice, this integral is instead approximated as a sum over the metallicity bins that we use in our simulation.
 The number of targets in our sample at a metallicity $Z$, $N_{\rm target, Z}$, can be written simply as the sum of the targets' weights:
@@
 \begin{equation}
-    M_{\rm SF, MW} = 6.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = 9.1 \pm 1.1 \times 10^{10} \unit{M_{\odot}},
+    M_{\rm SF, MW} = (6.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = (9.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}},
 \end{equation}
@@
 
+\newpage
+
 \section{Supplementary material}
@@
     \centering
-    \caption{The number of detectable binaries in a 4 and 10 year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
+    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
     \begin{tabular}{c|lll|lll}
@@
         \hline
-        A & \confinv{34.4}{20.9}{46.6} & \confinv{29.9}{20.1}{47.4} & \confinv{7.7}{5.0}{10.3} & \confinv{58.6}{31.0}{53.3} & \confinv{51.9}{28.0}{95.0} & \confinv{13.0}{6.8}{14.2}\\
-        B & \confinv{33.9}{19.7}{36.5} & \confinv{15.5}{9.6}{19.6} & \confinv{2.8}{1.9}{4.3} & \confinv{55.6}{27.7}{45.9} & \confinv{26.7}{13.8}{23.7} & \confinv{4.8}{2.7}{5.6}\\
-        C & \confinv{20.6}{11.1}{20.5} & \confinv{5.3}{3.0}{5.3} & \confinv{4.3}{3.1}{5.2} & \confinv{33.7}{15.7}{26.7} & \confinv{8.9}{4.2}{7.0} & \confinv{7.3}{4.5}{6.1}\\
-        D & \confinv{21.9}{14.7}{37.8} & \confinv{4.1}{2.6}{4.2} & \confinv{11.6}{8.3}{22.7} & \confinv{36.0}{21.6}{45.4} & \confinv{6.8}{3.4}{5.3} & \confinv{20.5}{12.7}{27.7}\\
-        E & \confinv{33.7}{19.4}{37.0} & \confinv{3.3}{2.3}{6.3} & \confinv{0.2}{0.1}{0.1} & \confinv{54.9}{26.7}{44.2} & \confinv{5.8}{3.5}{8.2} & \confinv{0.3}{0.1}{0.2}\\
-        F & \confinv{26.2}{16.0}{35.8} & \confinv{15.0}{11.4}{84.0} & \confinv{5.7}{3.8}{7.3} & \confinv{43.3}{22.2}{43.7} & \confinv{27.2}{18.2}{86.3} & \confinv{9.5}{5.2}{10.0}\\
-        G & \confinv{29.5}{15.9}{27.6} & \confinv{23.5}{14.0}{27.2} & \confinv{23.4}{15.2}{27.9} & \confinv{47.5}{21.4}{38.3} & \confinv{40.9}{20.7}{36.3} & \confinv{39.8}{21.4}{36.3}\\
-        H & \confinv{115.1}{98.0}{123.0} & \confinv{30.7}{21.4}{163.7} & \confinv{7.4}{4.8}{14.6} & \confinv{173.6}{117.7}{150.5} & \confinv{55.4}{32.8}{185.8} & \confinv{13.0}{6.8}{25.5}\\
-        I & \confinv{22.7}{12.4}{26.8} & \confinv{48.7}{30.9}{97.1} & \confinv{6.3}{4.0}{9.0} & \confinv{36.1}{16.8}{30.8} & \confinv{84.0}{45.0}{142.8} & \confinv{10.9}{5.8}{11.1}\\
-        J & \confinv{47.5}{31.6}{71.9} & \confinv{24.3}{16.3}{37.4} & \confinv{6.8}{4.4}{10.9} & \confinv{80.7}{46.8}{86.8} & \confinv{41.7}{22.9}{47.0} & \confinv{11.6}{6.2}{14.0}\\
-        K & \confinv{30.1}{18.0}{40.4} & \confinv{37.6}{24.6}{44.9} & \confinv{7.8}{5.1}{11.6} & \confinv{52.5}{28.2}{48.4} & \confinv{65.1}{35.0}{54.7} & \confinv{13.4}{7.1}{14.8}\\
-        L & \confinv{35.2}{21.3}{45.2} & \confinv{30.2}{19.9}{49.6} & \confinv{7.9}{5.0}{11.7} & \confinv{58.9}{31.0}{54.9} & \confinv{52.4}{28.5}{96.9} & \confinv{13.3}{7.1}{14.8}\\
-        M & \confinv{43.0}{28.3}{58.3} & \confinv{68.7}{43.4}{108.7} & \confinv{16.1}{10.4}{20.5} & \confinv{69.4}{38.1}{69.1} & \confinv{117.4}{61.8}{154.5} & \confinv{27.3}{14.5}{26.4}\\
-        N & \confinv{53.0}{34.1}{58.3} & \confinv{110.6}{71.3}{193.1} & \confinv{35.7}{23.6}{54.8} & \confinv{84.4}{44.9}{73.3} & \confinv{194.9}{102.6}{256.0} & \confinv{60.2}{32.7}{67.8}\\
-        O & \confinv{43.1}{27.0}{39.0} & \confinv{76.0}{43.9}{91.2} & \confinv{9.3}{6.0}{10.4} & \confinv{68.5}{35.8}{47.5} & \confinv{130.8}{62.9}{122.0} & \confinv{15.8}{8.4}{13.8}\\
-        P & \confinv{44.3}{28.4}{62.2} & \confinv{26.7}{17.0}{48.9} & \confinv{9.0}{5.6}{10.9} & \confinv{69.9}{38.0}{78.9} & \confinv{45.9}{25.9}{64.4} & \confinv{15.3}{7.4}{13.9}\\
-        Q & \confinv{0.0}{0.0}{0.0} & \confinv{6.3}{3.7}{6.1} & \confinv{7.8}{4.7}{8.0} & \confinv{0.0}{0.0}{0.0} & \confinv{10.8}{5.3}{7.6} & \confinv{13.0}{6.4}{10.4}\\
+        A & \confinv{39.6}{6.6}{6.4} & \confinv{36.5}{6.5}{6.5} & \confinv{8.7}{2.7}{3.3} & \confinv{62.9}{7.9}{8.1} & \confinv{60.7}{7.7}{7.3} & \confinv{14.4}{3.4}{3.6}\\
+        B & \confinv{37.1}{6.1}{5.9} & \confinv{17.4}{4.4}{4.6} & \confinv{3.3}{2.3}{1.7} & \confinv{58.7}{7.7}{7.3} & \confinv{28.7}{5.7}{5.3} & \confinv{5.3}{2.3}{2.7}\\
+        C & \confinv{22.4}{4.4}{4.6} & \confinv{5.8}{2.8}{2.2} & \confinv{4.7}{1.7}{2.3} & \confinv{35.8}{5.8}{6.2} & \confinv{9.4}{3.4}{2.6} & \confinv{7.6}{2.6}{2.4}\\
+        D & \confinv{26.2}{5.2}{4.8} & \confinv{4.3}{2.3}{1.7} & \confinv{14.1}{4.1}{3.9} & \confinv{40.5}{6.5}{6.5} & \confinv{7.1}{3.1}{2.9} & \confinv{23.2}{5.2}{4.8}\\
+        E & \confinv{36.9}{5.9}{6.1} & \confinv{4.2}{2.2}{1.8} & \confinv{0.2}{0.2}{0.8} & \confinv{58.6}{7.6}{7.4} & \confinv{6.6}{2.6}{2.4} & \confinv{0.3}{0.3}{0.7}\\
+        F & \confinv{30.2}{5.2}{5.8} & \confinv{22.9}{4.9}{5.1} & \confinv{6.4}{2.4}{2.6} & \confinv{47.5}{6.5}{6.5} & \confinv{35.5}{5.5}{5.5} & \confinv{10.4}{3.4}{3.6}\\
+        G & \confinv{31.8}{5.8}{5.2} & \confinv{25.9}{4.9}{5.1} & \confinv{25.9}{4.9}{5.1} & \confinv{50.5}{7.5}{7.5} & \confinv{43.5}{6.5}{6.5} & \confinv{42.4}{6.4}{6.6}\\
+        H & \confinv{117.8}{10.8}{11.2} & \confinv{51.7}{6.7}{7.3} & \confinv{10.1}{3.1}{2.9} & \confinv{181.6}{13.6}{13.4} & \confinv{87.7}{9.7}{9.3} & \confinv{16.7}{3.7}{4.3}\\
+        I & \confinv{25.5}{5.5}{5.5} & \confinv{62.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{39.1}{6.1}{5.9} & \confinv{102.3}{10.3}{9.7} & \confinv{11.9}{3.9}{3.1}\\
+        J & \confinv{55.5}{7.5}{7.5} & \confinv{27.9}{4.9}{5.1} & \confinv{8.0}{3.0}{3.0} & \confinv{87.8}{9.8}{9.2} & \confinv{45.7}{6.7}{6.3} & \confinv{13.0}{4.0}{4.0}\\
+        K & \confinv{34.8}{5.8}{6.2} & \confinv{42.4}{6.4}{6.6} & \confinv{9.0}{3.0}{3.0} & \confinv{56.0}{8.0}{7.0} & \confinv{69.5}{8.5}{8.5} & \confinv{14.8}{3.8}{4.2}\\
+        L & \confinv{39.8}{6.8}{6.2} & \confinv{36.7}{5.7}{6.3} & \confinv{9.1}{3.1}{2.9} & \confinv{63.4}{8.4}{7.6} & \confinv{61.9}{7.9}{8.1} & \confinv{14.7}{3.7}{3.3}\\
+        M & \confinv{48.2}{7.2}{6.8} & \confinv{80.8}{8.8}{9.2} & \confinv{18.0}{4.0}{4.0} & \confinv{75.3}{8.3}{8.7} & \confinv{134.5}{11.5}{11.5} & \confinv{29.5}{5.5}{5.5}\\
+        N & \confinv{57.5}{7.5}{7.5} & \confinv{138.2}{12.2}{11.8} & \confinv{41.9}{6.9}{6.1} & \confinv{89.5}{9.5}{9.5} & \confinv{227.5}{15.5}{15.5} & \confinv{67.4}{8.4}{8.6}\\
+        O & \confinv{45.7}{6.7}{6.3} & \confinv{85.3}{9.3}{9.7} & \confinv{10.2}{3.2}{2.8} & \confinv{70.9}{8.9}{8.1} & \confinv{141.6}{11.6}{12.4} & \confinv{16.8}{3.8}{4.2}\\
+        P & \confinv{50.8}{6.8}{7.2} & \confinv{32.7}{5.7}{5.3} & \confinv{10.0}{3.0}{3.0} & \confinv{77.6}{8.6}{8.4} & \confinv{53.1}{7.1}{6.9} & \confinv{16.5}{4.5}{4.5}\\
+        Q & \confinv{0.0}{0.0}{0.0} & \confinv{6.7}{2.7}{2.3} & \confinv{8.5}{2.5}{2.5} & \confinv{0.0}{0.0}{0.0} & \confinv{11.3}{3.3}{3.7} & \confinv{13.8}{3.8}{4.2}\\
         \hline

### 2021-07-01 paper/tex/sections/comparisons.tex
move figure AGAIN

@@
-In Figure~\ref{fig:previous_studies}, we compare similar previous studies that have investigated the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
-The table details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
-This table not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
-We additionally do not include papers that don't use population synthesis or do not simulate sources in the Galactic plane \citep[e.g.][]{Andrews+2020, Kremer+2018} such that we only compare with papers with similar methodology and focus.
-
 \begin{figure*}[p]
@@
 
-In a seminal work, \citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
+In Figure~\ref{fig:previous_studies}, we compare similar previous studies that have investigated the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
+The table details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
+This table not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
+We additionally do not include papers that don't use population synthesis or do not simulate sources in the Galactic plane \citep[e.g.][]{Andrews+2020, Kremer+2018} such that we only compare with papers with similar methodology and focus.
+
+\citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
 Their predictions of the number of detectable DCOs are very different from our own, where we find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
-However, since their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which likely strongly affect the expected detections rates.
+However, since the publication of their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which strongly affect the expected detections rates.
 
@@
 Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (Kummer et al.
-(in prep)).
+We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate.
 
-\citet{Lau+2020} investigated the number of Galactic NSNS binaries that could be detected by LISA.
+\citet{Lau+2020} focussed on the number of Galactic NSNS binaries that could be detected by LISA.
 Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version.

### 2021-07-01 paper/tex/sections/introduction.tex
we detected a BHNS!!

@@
 
-One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS).
-Of all the events detected by ground-based detectors, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}.
-Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
+One particularly interesting potential LISA source is a black hole neutron star binary (BHNS).
+With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.
+However, with only two detections (not including the low-confidence candidates GW190425 and GW190184 \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
+Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
 These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs.
 A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
-These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
+These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
 

### 2021-07-01 paper/tex/sections/methods.tex
we detected a BHNS!!

@@
 We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability.
-For a full derivation of the equations given below please see the LEGWORK release paper (Wagg et al.
-in prep) or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
+For a full derivation of the equations given below please see the LEGWORK release paper, Wagg et al.
+2021b (in prep), or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
 

### 2021-07-01 paper/tex/sections/results.tex
fix file paths
we detected a BHNS!!

@@
 We find that on average, for our fiducial model, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}).
-We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and analysing the parameter distributions for detectable sources in the fiducial model in Section~\ref{sec:fiducial_distributions}.
+We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions}.
 
@@
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
+See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
 \todo{subject to change with the updated/new models and new uncertainty estimates}}
@@
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/chirp_mass_uncertainty_4yr.pdf}
+    \includegraphics[width=\columnwidth]{chirp_mass_uncertainty_4yr.pdf}
     \caption{Cumulative distribution function for error on the chirp mass.
@@
     \centering
-    \includegraphics[width=\columnwidth]{paper/figures/angular_resolution_4yr.pdf}
+    \includegraphics[width=\columnwidth]{angular_resolution_4yr.pdf}
     \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}

### 2021-07-01 paper/tex/sections/introduction.tex
Updates from Overleaf

--- 2021-06-30 paper/tex/sections/introduction.tex
@@
 
-For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
+For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or a phase of highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
 We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.

### 2021-07-01 paper/tex/sections/appendix.tex
Move methods chunk to appendix, some changes to intro

@@
 % \end{equation}
+
+\section{Population Synthesis}\label{app:pop_synth}
+\subsection{Initial conditions}
+
+Between 1 and 100 million massive binaries are simulated for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+More binaries are simulated for higher metallicities to account for the lower formation rate of DCOs.
+These bins span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
+This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
+
+Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
+The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
+The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.\ with][]{Sana+2012}.
+We additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
+We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
+We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
+Since we focus on post-interaction binaries which will have circularised after mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
+
+We apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
+This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
+
+For each metallicity $Z$, the simulations result in a sample of binaries, each with a set of parameters
+\begin{equation}
+    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
+\end{equation}
+for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+We sample from these sets of parameters when creating synthetic galaxies.
+
+\subsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
+In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
+
+\textit{Stellar Evolution:} To follow the evolution of massive stars, COMPAS relies on fitting formulae by \citet{Hurley+2000} to detailed single star models by \citet{Pols+1998}.
+COMPAS models the evolution of stars that lose or gain mass closely following the algorithms originally described in \citet{Tout+1996} and \citet{Hurley+2002}.
+
+\textit{Wind mass loss:} We follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
+We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
+Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observer LBV eruptions for stars with luminosities and  effective temperatures above the Humphrey Davidson limit.
+We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars and set $f_{\rm WR} = 1$.
+See Team COMPAS: J.
+Riley et al.
+(in prep), Section 3 for the explicit equations.
+
+\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
+The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
+We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
+The maximum accretion rate for compact objects is limited to the Eddington accretion rate.
+If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
+We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.
+
+\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
+We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
+For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
+We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
+This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
+We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections, likely leading to a stellar merger.
+
+\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
+For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
+The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
+We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
+
+We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
+We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
+For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
+
+We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
+For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
+
+Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
+We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
+
+We assume that kicks are isotropic in the frame of the collapsing star.
+We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
+
+\subsection{Model variations} \label{sec:variation_assumptions}
+In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
+Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
+
+Our fiducial model is labelled model \modFid{}.
+Models \modRangeMT{} focus on changes to the mass transfer physics assumptions.
+We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate.
+In models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
+In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.
+
+Models \modRangeCE{} focus on altering the common envelope physics.
+We change the common envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
+In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
+We combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
+
+In models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
+Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
+We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses.
+Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae.
+In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
+Model \modNoBH{} removes the natal kick for all black holes.
+
+Finally, in models \modRangeML{} we investigate the effect of changing our assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
+We vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
+These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations (e.g.
+\citet{Vink+2017}, \citet{Hamann+2019}, \citet{Shenar+2019}, \citet{Miller-Jones+2021} and van Son et al.
+(in prep)).
+
+\begin{table}[htb]
+    \centering
+    \begin{tabular}{cl}
+        \hline \hline
+        Model & Physics Variation \\
+        \hline \hline
+        \modFid & Fiducial (see Section~\ref{sec:fiducial_physics}) \\
+        \hline
+        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
+        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
+        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
+        \modCaseBB & Case BB mass transfer is always unstable \\
+        \modCaseBBOpt & Model \modCaseBB{} + Model \modOpt{} \\
+        \hline
+        \modAlphaLowest & CE efficiency parameter $\alpha = 0.1$ \\
+        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
+        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
+        \modAlphaHighest & CE efficiency parameter $\alpha = 10$   \\
+        \modOpt & HG donor stars initiating a CE survive CE \\
+        \hline
+        \modRapid & Fryer rapid SN remnant mass prescription \\
+        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
+        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
+        \modNoPISN & PISN and pulsational-PISN not implemented \\
+        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
+        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
+        \modNoBH & Black holes receive no natal kick \\
+        \hline
+        \modWRLow & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ \\
+        \modWRHigh & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ \\
+        \hline \hline
+    \end{tabular}%
+    \caption{A description of the \nModels{} binary population synthesis models used in this study.
+\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics , \modRangeSN{} change supernova physics and \modRangeML{} change wind mass loss \citep[c.f.][Table 2]{Broekgaarden+2021}.}
+    \label{tab:physics_variations}
+\end{table}
 

### 2021-07-01 paper/tex/sections/introduction.tex
Move methods chunk to appendix, some changes to intro

@@
 
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new frequency regime of gravitational waves.
+The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
 LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
-Moreover, this frequency regime is also of interest for the detection of local stellar mass binaries during their inspiral phase.
-LISA will be able to detect, and possibly localise a double compact object (DCO) on the sky many years in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+Moreover, this frequency regime is also of interest for the detection of local stellar mass double compact objects (DCO) far in advance of their merger.
+This presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
 In addition, LISA will be able to measure the eccentricities of DCOs that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
-The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger.
-This means that LISA stellar mass sources can only be detected in local galaxies, with the majority residing in the Milky Way.
+Unlike ground-based detectors, LISA only detects stellar mass sources in local galaxies, with the majority residing in the Milky Way.
 Therefore, these sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.
@@
 Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars.
-In this paper we focus on NS and BH binaries.
+In this paper we focus on double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).
 
-Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been detected \citep[e.g.][]{Abbott+2017_NSNS}.
+Galactic NSNSs have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been detected \citep[e.g.][]{Abbott+2017_NSNS}.
 The detection of a NSNS in LISA with a pulsar component could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
@@
 
-Double black hole (BHBH) binaries in the Milky Way present a greater observational challenge.
+BHBHs in the Milky Way present a greater observational challenge.
 To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH.
@@
 
-One particularly interesting potential LISA source is a black hole neutron star binary (BHNS).
+One particularly interesting class of potential LISA sources are BHNSs.
 With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.

### 2021-07-01 paper/tex/sections/methods.tex
Move methods chunk to appendix, some changes to intro

@@
 (in prep)).
-We summarize the main assumptions and settings relevant for this work in the following sections.
-
-\subsubsection{Initial conditions}
-
-Between 1 and 100 million massive binaries are simulated for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-More binaries are simulated for higher metallicities to account for the lower formation rate of DCOs.
-These bins span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
-This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
-
-Each binary is sampled from initial distributions for the primary and secondary masses as well as the separation.
-The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.\ with][]{Sana+2012}.
-We additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
-We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
-We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised after mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
-
-We apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
-This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
-
-For each metallicity $Z$, the simulations result in a sample of binaries, each with a set of parameters
-\begin{equation}
-    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
-\end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
-We sample from these sets of parameters when creating synthetic galaxies.
-
-\subsubsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
-In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
-
-\textit{Stellar Evolution:} To follow the evolution of massive stars, COMPAS relies on fitting formulae by \citet{Hurley+2000} to detailed single star models by \citet{Pols+1998}.
-COMPAS models the evolution of stars that lose or gain mass closely following the algorithms originally described in \citet{Tout+1996} and \citet{Hurley+2002}.
-
-\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
-The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
-We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
-The maximum accretion rate for compact objects is limited to the Eddington accretion rate.
-If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
-We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.
-
-\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
-We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
-For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
-This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
-We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections, likely leading to a stellar merger.
-
-\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
-For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
-The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
-We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
-
-We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
-We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
-For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
-
-We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
-For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
-
-Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
-We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
-
-We assume that kicks are isotropic in the frame of the collapsing star.
-We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
-
-\textit{Wind mass loss:} We follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
-We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
-Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observer LBV eruptions for stars with luminosities and  effective temperatures above the Humphrey Davidson limit.
-We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars and set $f_{\rm WR} = 1$.
-See Team COMPAS: J.
-Riley et al.
-(in prep), Section 3 for the explicit equations.
-
-\subsubsection{Model variations} \label{sec:variation_assumptions}
-In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
-Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
-
-Our fiducial model is labelled model \modFid{}.
-Models \modRangeMT{} focus on changes to the mass transfer physics assumptions.
-We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate.
-In models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
-In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.
-
-Models \modRangeCE{} focus on altering the common envelope physics.
-We change the common envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
-In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
-We combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
-
-In models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
-Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
-We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses.
-Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae.
-In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
-Model \modNoBH{} removes the natal kick for all black holes.
-
-Finally, in models \modRangeML{} we investigate the effect of changing our assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
-We vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
-These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations (e.g.
-\citet{Vink+2017}, \citet{Hamann+2019}, \citet{Shenar+2019}, \citet{Miller-Jones+2021} and van Son et al.
-(in prep)).
-
-\begin{table}[htb]
-    \centering
-    \begin{tabular}{cl}
-        \hline \hline
-        Model & Physics Variation \\
-        \hline \hline
-        \modFid & Fiducial (see Section~\ref{sec:fiducial_physics}) \\
-        \hline
-        \modBetaLow & Fixed mass transfer efficiency of $\beta=0.25$ \\ 
-        \modBetaMed & Fixed mass transfer efficiency of $\beta=0.5$  \\ 
-        \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\ 
-        \modCaseBB & Case BB mass transfer is always unstable \\
-        \modCaseBBOpt & Model \modCaseBB{} + Model \modOpt{} \\
-        \hline
-        \modAlphaLowest & CE efficiency parameter $\alpha = 0.1$ \\
-        \modAlphaLow & CE efficiency parameter $\alpha = 0.5$ \\
-        \modAlphaHigh & CE efficiency parameter $\alpha = 2$   \\
-        \modAlphaHighest & CE efficiency parameter $\alpha = 10$   \\
-        \modOpt & HG donor stars initiating a CE survive CE \\
-        \hline
-        \modRapid & Fryer rapid SN remnant mass prescription \\
-        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
-        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
-        \modNoPISN & PISN and pulsational-PISN not implemented \\
-        \modSigLow & $\sigma_{\rm{rms}}^{\rm{1D}}=100 \unit{km}{s^{-1}}$ for core-collapse supernova \\  
-        \modSigLower & $\sigma_{\rm{rms}}^{\rm{1D}}=30  \unit{km}{s^{-1}}$ for core-collapse supernova \\ 
-        \modNoBH & Black holes receive no natal kick \\
-        \hline
-        \modWRLow & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ \\
-        \modWRHigh & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ \\
-        \hline \hline
-    \end{tabular}%
-    \caption{A description of the \nModels{} binary population synthesis models used in this study.
-\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics , \modRangeSN{} change supernova physics and \modRangeML{} change wind mass loss \citep[c.f.][Table 2]{Broekgaarden+2021}.}
-    \label{tab:physics_variations}
-\end{table}
+We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
 

### 2021-07-01 paper/tex/sections/appendix.tex
remove old commented out strain stuff
move b_Z,i back to methods

@@
-% \section{Derivation of Strain and SNR Equations}\label{app:strain_snr_deriv}
-% In this section we provide a full derivation/explanation of how we arrived at the equations used in our simulations.
+\section{Population Synthesis}\label{app:pop_synth}
 
-% \subsection{Conversions and definitions}
-% Each of these conversions and definitions are useful in the later derivations and we define them here for convenience. First, we define the chirp mass of a binary as 
-% \begin{equation}\label{eq:chirpmass}
-%     \mathcal{M}_c = \frac{(m_1 m_2)^{3/5}}{(m_1 + m_2)^{1/5}},
-% \end{equation}
-% where $m_1$ and $m_2$ are the primary and secondary mass of the binary.
-Kepler's third law is well known and allows one to convert between orbital frequency and the semi-major axis of a binary.
-For convenience we show it here
-% \begin{equation}\label{eq:kepler3rd}
-%     a = \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^{2}})^{1/3},\qquad f_{\rm orb} = \frac{1}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}.
-% \end{equation}
-% As we deal with eccentric binaries, the different harmonic frequencies of gravitational wave emission become important.
-We therefore write that the relative power radiated into the $n^{\rm th}$ harmonic for a binary with eccentricity $e$ is \citep[][Eq.\,20]{Peters+1963}
-% \begin{equation}\label{eq:g(n,e)}
-%     \begin{aligned}
-%         g(n, e) = \frac{n^{4}}{32} & \left\{ \left[ J_{n-2}(n e)-2 e J_{n-1}(n e)+\frac{2}{n} J_{n}(n e)+2 e J_{n+1}(n e)-J_{n+2}(n e)\right]^{2}\right.\\
-%         &\left.+\left(1-e^{2}\right)\left[J_{n-2}(n e)-2 J_{n}(n e)+J_{n+2}(n e)\right]^{2}+\frac{4}{3 n^{2}}\left[J_{n}(n e)\right]^{2}\right\},
-%     \end{aligned}
-% \end{equation}
-% where $J_{n}(v)$ is the Bessel function of the first kind.
-Thus, the sum of $g(n, e)$ over all harmonics gives the factor by which the gravitational wave emission is stronger for a binary of eccentricity $e$ over an otherwise identical circular binary.
-This enhancement factor is defined by Peters as \citep[][Eq.\,17]{Peters+1963}
-% \begin{equation}\label{eq:eccentricity_enhancement_factor}
-%     F(e) = \frac{1 + (73 / 24) e^2 + (37 / 96) e^4}{(1 - e^2)^{7/2}}.
-% \end{equation}
-% Note that $F(0) = 1$ as one would expect.
-A fun number to remember is that $F(0.5) \approx 5.0$, or in words, a binary with eccentricity $0.5$ loses energy to gravitational waves at a rate $5$ times higher than a similar circular binary.
+In this section we summarise the main assumptions and settings that we use when performing population synthesis for this work.
+For a more general overview of every setting see \citet{Broekgaarden+2021}.
 
-% \subsection{Characteristic Strain}
-% The characteristic strain from a binary in the $n^{\rm th}$ harmonic is defined as follows (e.g. \citealp[][Eq.\,56]{Barack+2004}; \citealp[][Eq.\,5.1]{ Flanagan+1998})
-% \begin{equation}\label{eq:char_strain_dedf}
-%     h_{c,n}^2 = \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\dot{E_n}}{\dot{f_n}} ),
-% \end{equation}
-% where $D_L$ is the luminosity distance to the binary, $\dot{E}_n$ is the power radiated in the $n^{\rm th}$ harmonic and $\dot{f}_n$ is the rate of change of the $n^{\rm th}$ harmonic frequency.
-The power radiated in the $n^{\rm th}$ harmonic is given by \citep[][Eq.
-19]{Peters+1963}
-% \begin{equation}\label{eq:edot_peters}
-%     \dot{E}_n = \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)}{a^{5}} g(n, e),
-% \end{equation}
-% where $m_1$ is the primary mass, $m_2$ is the secondary mass, $a$ is the semi-major axis of the binary and $e$ is the eccentricity.
-Using \eqref{eq:chirpmass} and \ref{eq:kepler3rd}, we can recast \eqref{eq:edot_peters} in a form more applicable for gravitational wave detections that is a function of only the chirp mass, orbital frequency and eccentricity.
-% \begin{align}
-%     \dot{E}_n &= \frac{32}{5} \frac{G^{4}}{c^5} \qty(m_{1}^{2} m_{2}^{2}\left(m_{1}+m_{2}\right)) g(n, e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{5/3} \\
-%     \dot{E}_n &= \frac{32}{5} \frac{G^{7/3}}{c^5} \frac{m_{1}^{2} m_{2}^{2}}{\left(m_{1}+m_{2}\right)^{2/3}} (2 \pi f_{\rm orb})^{10/3} g(n, e) \\
-%     \dot{E}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e) \label{eq:edot}
-% \end{align}
-% The last term needed to define the characteristic strain in \eqref{eq:char_strain_dedf} is the rate of change of the $n^{\rm th}$ harmonic frequency. We can first apply the chain rule and note that
-% \begin{equation}\label{eq:fdot_chainrule}
-%     \dot{f}_{n} = \dv{f_{n}}{a} \dv{a}{t}.
-% \end{equation}
-% The frequency of the $n^{\rm th}$ harmonic is simply defined as $f_n = n \cdot f_{\rm orb}$ and therefore we can find an expression for $\dd{f_{n}} / \dd{a}$ by rearranging and differentiating \eqref{eq:kepler3rd}
-% \begin{align}
-%     f_{n} &= \frac{n}{2 \pi} \sqrt{\frac{G(m_1 + m_2)}{a^3}}, \\
-%     \dv{f_{n}}{a} &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}}. \label{eq:dfda}
-% \end{align}
-% The rate at which the semi-major axis decreases is \citep[][Eq. 5.6]{Peters+1964}
-% \begin{equation}\label{eq:dadt}
-%     \dv{a}{t} = -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e).
-% \end{equation}
-% Substituting \eqref{eq:dfda} and \ref{eq:dadt} into \eqref{eq:fdot_chainrule} gives an expression for $\dot{f}_{n}$
-% \begin{align}
-%     \dot{f}_n &= -\frac{3 n}{4 \pi} \frac{\sqrt{G(m_1 + m_2)}}{a^{5/2}} \cdot -\frac{64}{5} \frac{G^{3} m_{1} m_{2}\left(m_{1}+m_{2}\right)}{c^{5} a^{3}} F(e), \\
-%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) \frac{F(e)}{a^{11/2}},
-% \end{align}
-% which, as above with $\dot{E}_n$, we can recast using Kepler's third law and the definition of the chirp mass
-% \begin{align}
-%     \dot{f}_n &= \frac{48 n}{5 \pi} \frac{G^{7/2}}{c^5} \qty(m_1 m_2 (m_1 + m_2)^{3/2}) F(e) \cdot \qty(\frac{(2 \pi f_{\rm orb})^{2}}{G(m_1 + m_2)})^{11/6}, \\
-%     &= \frac{48 n}{5 \pi} \frac{G^{5/3}}{c^5} \frac{m_1 m_2}{(m_1 + m_2)^{1/3}} \cdot (2 \pi f_{\rm orb})^{11/3} \cdot F(e), \\
-%     \dot{f}_n(\mathcal{M}_c, f_{\rm orb}, e) &= \frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \label{eq:fdot}
-% \end{align}
-% With definitions of both $\dot{E}_n$ and $\dot{f}_n$, we are now in a position to find an expression for the characteristic strain by plugging \eqref{eq:edot} and \ref{eq:fdot} into \ref{eq:char_strain}:
-% \begin{align}
-%     h^2_{c,n} &= \frac{1}{(\pi D_L)^2} \qty( \frac{2 G}{c^3} \frac{\frac{32}{5} \frac{G^{7 / 3}}{c^{5}}\left(2 \pi f_{\mathrm{orb}} \mathcal{M}_{c}\right)^{10 / 3} g(n, e)}{\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e)} ) \\
-%     &= \frac{1}{(\pi D_L)^2} \qty( \frac{2^{5/3} \pi^{2/3}}{3} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} ) \\
-%     h_{c,n}^2(\mathcal{M}_c, D_L, f_{\rm orb}, e) &= \frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{f_{\rm orb}^{1/3}} \frac{g(n, e)}{n F(e)} \label{eq:char_strain}
-% \end{align}
-
-% \subsection{Strain}
-% The strain can be found by dividing the characteristic strain by the square root of twice the number of cycles.
-This is explained in \citet{Finn+2000} and in further detail in \citet{Moore+2015}.
-The physical reasoning behind the idea is that the binary will spend a certain amount of time in the vicinity of some frequency $f$ and cause a similar gravitational wave strain.
-This leads to the signal 'accumulating' and resulting in a larger signal-to-noise ratio.
-Therefore, the characteristic strain represents the strain measured by the detector over the duration of the mission, whilst the strain is what is emitted by the binary at each instantaneous moment.
-
-% Following this logic, we can convert between characteristic strain and strain with \citep[e.g][see text before Eq.\,2.2]{Finn+2000}
-% \begin{equation}\label{eq:strain-to-charstrain}
-%     h_{c, n}^2 = \qty(\frac{2 f_n^2}{\dot{f}_n}) h_n^2.
-% \end{equation}
-% Therefore, using this, in addition to Eq. \ref{eq:fdot} and Eq. \ref{eq:char_strain}, we can write an expression for the strain amplitude of gravitational waves in the $n^{\rm th}$ harmonic
-% \begin{align}
-%     h_n^2 &= \qty(\frac{\dot{f}_n}{2 f_n^2}) h_{c, n}^2, \\
-%     h_n^2 &= \qty(\frac{48 n}{5 \pi} \frac{\qty(G \mathcal{M}_c)^{5/3}}{c^5} (2 \pi f_{\rm orb})^{11/3} F(e) \cdot \frac{1}{2 n^2 f_{\rm orb}^2}) \qty(\frac{2^{5/3}}{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)}), \\
-%     h_n^2(\mathcal{M}_c, f_{\rm orb}, D_L, e) &= \frac{2^{25/3}}{5} \frac{(G \mathcal{M}_c)^{10/3}}{c^8 D_L^2} \frac{g(n, e)}{n^2} \qty(\pi f_{\rm orb})^{4/3} . \label{eq:strain}
-% \end{align}
-
-% \subsection{General Signal-to-Noise Ratio}
-% We can start at the equation for the general signal-to-noise ratio from \citet{Flanagan+1998} (Eq. 2.30)
-% \begin{equation}
-%     \left\langle\rho^{2}\right\rangle=\frac{2(1+z)^{2}}{5 \pi^{2} D_L(z)^{2}} \int_{0}^{\infty} d f \frac{1}{f^{2} S_{n}(f)} \dv{E}{f}[(1 + z) f],
-% \end{equation}
-% where $z$ is the redshift.
-We need to adjust this equation in a couple of key ways for LISA Galactic binaries.
-First we multiply by 5 because of the way the signal response function is defined in LISA (converse to LIGO) -- \citet[see][]{Robson+2019} for a good explanation.
-Additionally we can set $z = 0$ for Galactic binaries, convert to SI units from geometric units (as is our convention in this document) and integrate over specific frequency limits.
-% \begin{equation}\label{eq:snr_abs}
-%     \avg{\rho_n^2} = \int_{f_{n, i}}^{f_{n, f}} \underbrace{\frac{2 G}{\pi^2 c^3 D_L^2} \dv{E_n}{f_n}}_{\text{signal}} \underbrace{\frac{1}{f_n^2 S_{\rm n}(f_n)}}_{\text{noise}} \dd{f_n}.
-% \end{equation}
-% It is now useful to inspect the `signal' term in the equation. We can do this specifically by first finding an expression for $\dd{E_n}/\dd{f_n}$ through the chain rule. We can write
-% \begin{equation}\label{eq:dedf}
-%     \dv{E_n}{f_n} = \dv{E_n}{t} \dv{a}{f_n} \dv{t}{a},
-% \end{equation}
-% where each term respectively comes from \eqref{eq:edot_peters}, the inverse of \eqref{eq:dfda} and the inverse of \eqref{eq:dadt}.
-% We can substitute these into Eq. \ref{eq:dedf} and simplify as follows
-% \begin{align}
-%     \dv{E_n}{f_n} &= \frac{32}{5} \frac{G^{4}}{c^5} \frac{m_1^2 m_2^2 \qty(m_1 + m_2)}{a^5} g(n, e) \cdot -\frac{4 \pi}{3 n} \frac{a^{5/2}}{(G(m_1 + m_2))^{1/2}} \cdot -\frac{5}{64} \frac{c^5 a^3}{G^3 m_1 m_2 (m_1 + m_2)} \frac{1}{F(e)}, \\
-%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot a^{1/2}, \\
-%     &= \frac{2 \pi}{3} \frac{G^{1/2} m_1 m_2}{(m_1 + m_2)^{1/2}} \frac{g(n, e)}{n F(e)} \cdot \qty(\frac{G(m_1 + m_2)}{(2 \pi f_{\rm orb})^2})^{1/6}, \\
-%     &= \frac{2^{2/3} \pi^{2/3}}{3} \frac{G^{2/3} m_1 m_2}{(m_1 + m_2)^{1/3}} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}, \\
-%     \dv{E_n}{f_n} &= \frac{2^{2/3} \pi^{2/3}}{3} G^{2/3} \mathcal{M}^{5/3} \frac{g(n, e)}{n F(e)} \cdot f_{\rm orb}^{-1/3}.
-% \end{align}
-% If we further multiply this by the prefactor in \eqref{eq:snr_abs}, we arrive at an expression for the `signal' portion of the equation, which notably is exactly the square of the characteristic strain (see \eqref{eq:char_strain}).
-% \begin{equation}
-%     \dv{E_n}{f_n} \frac{2 G}{\pi^2 c^3 D_L^2} = \frac{2^{5/3} }{3 \pi^{4/3}} \frac{(G \mathcal{M}_c)^{5/3}}{c^3 D_L^2} \frac{1}{n f_{\rm orb}^{1/3}} \frac{g(n, e)}{F(e)} = h_{c,n}^2.
-% \end{equation}
-% We can therefore write that the sky-averaged signal-to-noise ratio for a Galactic binary is
-% \begin{equation}\label{eq:snr_general}
-%     \boxed{ \rho^2 = \sum_{n=1}^{\infty}  \int_{f_{n, i}}^{f_{n, f}} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}. }
-% \end{equation}
-
-% \subsection{Stationary Signal-to-Noise Ratio}
-% For our sample, it was extremely useful to note that the vast majority of our binaries were stationary in frequency space on the timescale of a space-based observing mission.
-In this case, the start and end frequencies are only separated by a very small $\Delta f_n$ and so we can make the approximation that
-% \begin{align}
-%     \rho_n^2 &= \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_n(f_n)} \dd{f_n}, \nonumber \\
-%     &\approx \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_n(f_n)}.
-% \end{align}
-% Moreover, we can immediately write that $\Delta f_n = \dot{f}_n \Delta T$, where we know that $\Delta T = T_{\rm obs}$, such that
-% \begin{equation}
-%     \rho_n^2 = \left(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2 \right) \frac{T_{\rm obs}}{S_n(f_n)},
-% \end{equation}
-% where the term in parentheses can be replaced with $2 h_n^2$ using Equation \ref{eq:strain-to-charstrain}.
-This gives the final expression for the signal-to-noise ratio when the stationary approximation is applied (as shown in Equation \ref{eq:snr_stat})
-% \begin{equation}
-%     \rho_{\rm stat}^2 = \sum_{n=1}^{\infty} \frac{2 T_{\rm obs} h_n^2}{S_n(f_n)} .
-% \end{equation}
-
-\section{Population Synthesis}\label{app:pop_synth}
 \subsection{Initial conditions}
 
-Between 1 and 100 million massive binaries are simulated for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-More binaries are simulated for higher metallicities to account for the lower formation rate of DCOs.
-These bins span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
-This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over a billion binaries were simulated.
+We simulate between 1 and 100 million massive binaries for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+We simulate more binaries for higher metallicities to account for the lower formation rate of DCOs.
+These metallicities span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
+This is repeated for \nMinusOneModels{} physics variations (see Section \ref{sec:variation_assumptions}) and so in total over two billion binaries were simulated.
 
@@
 
-For each metallicity $Z$, the simulations result in a sample of binaries, each with a set of parameters
-\begin{equation}
-    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
-\end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
-We sample from these sets of parameters when creating synthetic galaxies.
-
 \subsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
-In this section we briefly summarise the main physical assumptions in our fiducial model. For more details see \citet{Broekgaarden+2021}.
 
@@
 We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
-
 We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
@@
 For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
-
 We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
 For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
-
-Stars with final helium core masses between $60$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
+Stars with final helium core masses between $35$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
 We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
-
 We assume that kicks are isotropic in the frame of the collapsing star.
@@
 
-\newpage
-
 \section{Supplementary material}
@@
 
+\newpage
+
 \subsection{Physics variation cumulative distributions}
 
-\begin{figure*}[h]
+\begin{figure*}[htb]
     \centering
@@
 
-\begin{figure*}[h]
+\begin{figure*}[p]
     \centering

### 2021-07-01 paper/tex/sections/methods.tex
move b_Z,i back to methods

@@
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
+
+The result of the simulations is a sample of binaries, which, for each metallicity $Z$, have the parameters
+\begin{equation}
+    \mathbf{b}_{{Z, i}} = \{m_1, m_2, a_{\rm DCO}, e_{\rm DCO}, t_{\rm evolve}, t_{\rm inspiral}, w\},
+\end{equation}
+for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+We sample from these sets of parameters when creating synthetic galaxies.
 

### 2021-07-01 paper/tex/sections/discussion.tex
Updates from Overleaf
massive restructuring, split results by fiducial and variations

--- 2021-06-20 paper/tex/sections/discussion.tex
@@
 
-\subsection{Assessing the effect of an improved Milky Way model}
-In this section, we repeat our analysis using a simpler model for the Milky Way in order to assess the effect of using a metallicity-dependent Milky Way model.
-For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in previous works.
-
-Their model can be summarised as follows: it is made up of three components, a thin disc, a thick disc and a bulge.
-The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}.
-\citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
-Most differently, only two metallicities are used and assigned independent of age or position.
-Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
-
-We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
-The two major differences we can see in these plots is that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
-In addition, though it can't be seen in these plots, the simpler prescriptions for the birth times mean that the star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and much more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
-    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
-    \label{fig:simple_mw}
-\end{figure}
-
-We find that using this simpler Milky Way model with our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
-Thus the BHBH and BHNS detection rates are only marginally increased but the NSNS detection is overestimated by nearly a factor of 2.
-
-Moreover, the distribution of parameters within the population, especially the mass distributions are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
-(in prep)).
-For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
-Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.
-Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions drop sharply to zero at lower masses than our fiducial results.
-
-The unphysical artifacts present in the mass distributions can have far-reaching effects since the masses of DCOs affect most other parameters.
-The inspiral time and SNR are directly dependent on the mass, whilst the uncertainty estimates depend on the SNR.
-This means that the artifacts can affect the predictions for most distributions of LISA detectable populations.
-
-\begin{figure}[b]
-    \centering
-    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
-    \label{fig:bh_mass_simple_mw}
-\end{figure}
-
 \subsection{Caveats}\label{sec:caveats}

### 2021-07-01 paper/tex/sections/results.tex
massive restructuring, split results by fiducial and variations

@@
-In this section we present our main results for the detectable LISA DCO population.
-We find that on average, for our fiducial model, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}).
-We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the variations in the detection rate over different physics variations in Section~\ref{sec:detection_rate_analysis} and the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions}.
+In this section we present our main results for the detectable LISA DCO population in our fiducial model.
+We find that on average, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}).
+We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions} and the measurement uncertainties in Section.~\ref{sec:measurement_uncertainties}.
 
@@
 
-\begin{figure*}[tp]
+\begin{figure*}[p]
     \centering
@@
 
-\subsection{Detection rates}\label{sec:detection_rate_analysis}
-\tom{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
-We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
-Increasing to a 10-year LISA mission length changes the number of detections to \BHBHTenYear{}, \BHNSTenYear{} and \NSNSTenYear{} respectively.
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
-We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties.
-An arrow indicates that the error bar extends to zero.
-The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
-See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\todo{subject to change with the updated/new models and new uncertainty estimates}}
-    \label{fig:detection_rates}
-\end{figure*}
-
-\subsubsection{BHBH detection rate trends}
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-
-The exception to this statement is model \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
-A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
-Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
-
-\subsubsection{BHNS detection rate trends}
-In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
-
-As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
-This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
-However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
-
-\tom{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
-We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke.
-I do see that the BHBH have a lot of only stable mass transfer and so reasonably are not too affected.
-NSNS basically only come through CE events and so sensibly are strongly affected but BHNS have $\sim 70\%$ classic channel and so should be affected strongly.
-But we don't see an increase with $\alpha = 2.0$.
-Any thoughts?
-(I'm leaving thinking about this for now in case it changes with the new data haha)}
-% For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
-\todo{Why isn't the opposite true for model \modAlphaHigh{}?
-It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
-
-Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
-This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
-For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
-This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
-
-The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed instead of BHBHs.
-For the same reason, increasing the maximum neutron star mass (model \modNSHigh{}) increases the detection rate and the inverse is true when it is decreased (model \modNSLow{}).
-
-Finally, models \modSigLow{}-\modNoBH{} show increased detection rates since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
-The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-
-\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
-
-As $\beta$ increases the NSNS detection rate increases, the opposite trend to that seen in the BHNS rate.
-This is for two main reasons: firstly the ejection of a common envelope is less problematic for the less massive NSNS binaries.
-Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
-Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.
-
-There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
-This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
-As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction.
-
-The vast majority of NSNSs in our sample are formed through the common envelope channel and thus changing the value of $\alpha_{\rm CE}$ has an effect on the rate.
-We see that decreasing $\alpha_{\rm CE}$ (model \modAlphaLow) leads to a lower rate as there is less energy available to eject the envelope and so more binaries result to stellar mergers rather than NSNSs and similarly we see an inverse trend when increasing $\alpha_{\rm CE}$ (model \modAlphaHigh).
-
-As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the PISN or BH kick prescription (models \modNoPISN{} and \modNoBH{}) of course has no effect on the NSNS population.
-
 \subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
@@
 
-\begin{figure*}[htbp]
+\subsubsection{Orbital Frequency}
+The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
+This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
+The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
+These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
+Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
+
+\begin{figure*}[t]
     \centering
@@
 \end{figure*}
-
-\subsubsection{Orbital Frequency}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
-These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
 
@@
 \end{figure}
-
-\subsection{Model variations}
-\tom{This will be about how the shapes of the parameter distributions change for the different model variations.
-I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}

### 2021-07-01 paper/tex/sections/variations.tex
massive restructuring, split results by fiducial and variations

In this section we explore the effect of varying our underlying physics assumptions and model for the Milky Way. In Section~\ref{sec:detection_rate_analysis} we explore the changes in the detection rate over different physics variations  and in Section~\ref{sec:property_variations} we consider how these model physics variations change the properties of detectable systems. Finally we demonstrate how different models for the Milky Way can affect our results in Section~\ref{sec:mw_changes}.

\subsection{Detection rates}\label{sec:detection_rate_analysis}
\tom{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}

We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs. Increasing to a 10-year LISA mission length changes the number of detections to \BHBHTenYear{}, \BHNSTenYear{} and \NSNSTenYear{} respectively. In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections. We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.

\begin{figure*}[p]
    \centering
    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
    \caption{The number of expected detections in the LISA mission for different DCO types and model variations. Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties. An arrow indicates that the error bar extends to zero. The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates). Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}. See Sec.~\ref{sec:detection_rate_analysis} for a discussion. \todo{subject to change with the updated/new models and new uncertainty estimates}}
    \label{fig:detection_rates}
\end{figure*}

\subsubsection{BHBH detection rate trends}
The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}). Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.

The exception to this statement is model \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events. A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events. Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.

\subsubsection{BHNS detection rate trends}
In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions. Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics. There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.

As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases. This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population. However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.

\tom{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$? We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke. I do see that the BHBH have a lot of only stable mass transfer and so reasonably are not too affected. NSNS basically only come through CE events and so sensibly are strongly affected but BHNS have $\sim 70\%$ classic channel and so should be affected strongly. But we don't see an increase with $\alpha = 2.0$. Any thoughts? (I'm leaving thinking about this for now in case it changes with the new data haha)}
% For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers. \todo{Why isn't the opposite true for model \modAlphaHigh{}? It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}

Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form. This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}. For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections. This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.

The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed instead of BHBHs. For the same reason, increasing the maximum neutron star mass (model \modNSHigh{}) increases the detection rate and the inverse is true when it is decreased (model \modNSLow{}).

Finally, models \modSigLow{}-\modNoBH{} show increased detection rates since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population. Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}. The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.

\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}

As $\beta$ increases the NSNS detection rate increases, the opposite trend to that seen in the BHNS rate. This is for two main reasons: firstly the ejection of a common envelope is less problematic for the less massive NSNS binaries. Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS. Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.

There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude. This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs. As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction.

The vast majority of NSNSs in our sample are formed through the common envelope channel and thus changing the value of $\alpha_{\rm CE}$ has an effect on the rate. We see that decreasing $\alpha_{\rm CE}$ (model \modAlphaLow) leads to a lower rate as there is less energy available to eject the envelope and so more binaries result to stellar mergers rather than NSNSs and similarly we see an inverse trend when increasing $\alpha_{\rm CE}$ (model \modAlphaHigh).

As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the PISN or BH kick prescription (models \modNoPISN{} and \modNoBH{}) of course has no effect on the NSNS population.

\subsection{Properties of detectable systems}\label{sec:property_variations}
\tom{This will be about how the shapes of the parameter distributions change for the different model variations. I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}

\subsection{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries. In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of these added features. For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.

Their model can be summarised as follows: the Milky Way is assumed to comprise of three components, a thin disc, a thick disc and a bulge. The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}. \citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge. A major difference is that only two metallicities are used and they are assigned independent of age or position. Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.

We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models. The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
%In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:simple_mw}
\end{figure}

We find that when applying this simpler Milky Way model and our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively. Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection is overestimated by nearly a factor of 2.

Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate. By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al. (in prep)). For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model. Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities. Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.

The unphysical artifacts present in the mass distributions can have far-reaching effects since the masses of DCOs affect most other parameters. The inspiral time and SNR are directly dependent on the mass, whilst the uncertainty estimates depend on the SNR. This means that the artifacts can affect the predictions for most distributions of LISA detectable populations.

Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.

\begin{figure}[h]
    \centering
    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
    \label{fig:bh_mass_simple_mw}
\end{figure}

### 2021-07-02 paper/tex/sections/results.tex
reduce discussion of eccentricity uncertainty

@@
 
-\subsubsection{Eccentricity uncertainty}\label{sec:ecc_unc}
-One of the main advantage of space-based gravitational wave detectors such as LISA is that systems may still have significant eccentricity during the LISA mission.
-Whilst also being useful as an individual quantity for learning more about sources, the uncertainty on the eccentricity also affects the uncertainty on the chirp mass and so it is important to quantify this uncertainty.
-
-We follow a method used in previous works that uses the individually detectable harmonics of sources to determine the uncertainty of the eccentricity of a source \citep[e.g.][]{Lau+2020, Korol+2021}.
-Eccentric sources emit at several evenly spaced harmonic frequencies, each with a different fraction of the gravitational wave power and the distribution of the power over the harmonics changes with eccentricity.
-Therefore, by measuring the SNR of each individual harmonic and finding the ratio of the SNR of the two most detectable harmonics that are above the detection threshold, one can determine the eccentricity.
-The uncertainty on the eccentricity can therefore be written as a combination of the uncertainty on the SNR of the two most detectable harmonics.
-In the limit of large SNRs, the eccentricity uncertainty, $\Delta e$, can be written as
-\begin{equation}
-    \Delta e = \frac{1}{\rho_1} + \frac{1}{\rho_2},
-\end{equation}
-where $\rho_1$ and $\rho_2$ are the SNRs of the two most detectable harmonics.
-
-In some cases, sources may only have one individually detectable harmonic, or even none.
-In these cases one can only put a lower or upper bound on the eccentricity.
-For sources with only one detectable harmonic, the source is either a circular source or a source with a small enough eccentricity that most of the GW power is still concentrated in the $n = 2$ harmonic.
-Therefore, we can use this information to place an upper bound on the eccentricity.
-Conversely, sources with no detectable harmonics must be eccentric enough such that the GW power has spread over so many harmonics that no single harmonic has a significantly stronger signal.
-Therefore, we can use this information to place a lower bound on the eccentricity.
-
-This method provides a pessimistic estimate of the eccentricity of sources since we do not consider the benefits of any sort of matched-filter analysis or similar methods.
-
 \subsubsection{Chirp mass uncertainty}
 
-The chirp mass uncertainty can be calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity.
-This is because the time derivative of the orbital frequency can be written as
-\begin{equation}\label{eq:f_n_dot}
-    \dot{f}_{n} = \frac{48 n}{5 \pi} \frac{(G \mathcal{M}_c)^{5/3}}{c^3} (2 \pi f_{\rm orb})^{11/3} F(e),
+The chirp mass uncertainty is important for identifying the source of a GW signal.
+It is calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity.
+This is because the chirp mass can be written as
+\begin{equation}
+    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48 n} \frac{\dot{f}_{n}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
 \end{equation}
@@
 \end{equation}
-is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}.
-
-We can invert this and instead write that the chirp mass is
-\begin{equation}
-    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48 n} \frac{\dot{f}_{n}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
-\end{equation}
-and therefore that the chirp mass uncertainty is
+is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}. Therefore that the chirp mass uncertainty is
 \begin{equation}\label{eq:chirp_mass_uncertainty}
@@
 \end{equation}
-where $f_{\rm dom}$ is the harmonic frequency with the strongest SNR as this will provide the best measurement.
+where $f_{\rm dom}$ is the harmonic frequency with the strongest SNR ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) as this will provide the best measurement.
 
@@
 where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length.
-Then we calculate the eccentricity certainty, $\Delta e$, as discussed in Sec.~\ref{sec:ecc_unc} and propagate it so that
+We calculate the eccentricity certainty, $\Delta e$, following the methods of \citet{Lau+2020} and \citet{Korol+2021}, which use the relative SNRs of different harmonics to work out the eccentricity.
+We propagate this uncertainty such that
 \begin{equation}
@@
 The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).
-Applying this to the plot shows that about 20\% of DCOs can be covered by a single pointing of SKA.
+Applying this to the plot shows that about 10-20\% of DCOs can be covered by a single pointing of SKA.
+However, since these LISA sources are essentially stationary in frequency space, observations need not be limited to a single pointing.
 We will discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.

### 2021-07-06 paper/tex/sections/discussion.tex
clear up caveats

@@
 
-\textit{Eccentricity measurement uncertainty:} As noted in Sec.~\ref{sec:ecc_unc}, the method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable.
+\textit{Eccentricity measurement uncertainty:} The method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable \citep[e.g.][]{Lau+2020}.
 In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data.

### 2021-07-06 paper/tex/sections/methods.tex

@@
 
-Our model for the Milky Way accounts for the low-$\alpha$\footnote{Note that $\alpha$ in this case refers to the abundance of $\alpha$ process elements and is \textit{not} related to the common envelope efficiency $\alpha_{\rm CE}$.} disc, high-$\alpha$ disc and central bar/bulge.
-The low- and high-$\alpha$ discs are often also referred to as the thin and thick discs.
-We use the $\alpha$ nomenclature as there is a clear bimodal distribution in the chemical plane, allowing stars to be easily decomposed into the two disc components, as opposed to the vertical distribution which cannot be fit by a single exponential but is not easy to split into separate components.
+Our model for the Milky Way accounts for the low-\achem\footnote{nomenclature used to describe the enhancement of $\alpha$ elements compared to iron in stellar atmospheres}~disc, high-\achem~disc and a central component approximating a bar/bulge.
+The low- and high-\achem~discs are often also referred to as the thin and thick discs because the stellar vertical distribution is better fit by a double exponential rather than a single one.
+However, it doesn't allow one to assign a star to either the thin or thick disk purely based on its height above the Galactic plane.
+Therefore, we use the chemical definition of the two disks with the \achem~nomenclature because there is a clear bimodal distribution in the chemical plane, allowing stars to be easily assigned to each of the disc components based on its chemical abundances.
 For each of the three components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
-\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-$\alpha$ discs \citep[e.g.,][]{Snaith+2014}.
+\citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-\achem~discs \citep[e.g.,][]{Snaith+2014}.
 
 \textit{Star formation history:} 
-We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-$\alpha$ discs, where the two discs transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
+We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-\achem~discs, where the two discs transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
 \begin{equation}\label{eq:thin_disc_tau}
@@
 The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate.
-But the bulge was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
-To model the bulge age distribution more realistically than in previous studies (assuming an older bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+But the central bar was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
+To model the bar's age distribution more realistically than in previous studies (assuming an old bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
 We show these distributions in the first panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
@@
 where $R$ is the Galactocentric radius and $R_d$ is the scale length of the component.
-For the low-$\alpha$ disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
+For the low-\achem~disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
 \begin{equation}
@@
 where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as NF finds that it provides a better fit to the original data}.
-This scale length accounts for the inside-out growth of the low-$\alpha$ disc and hence is age dependent.
-We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-$\alpha$ disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
+This scale length accounts for the inside-out growth of the low-\achem~disc and hence is age dependent.
+We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-\achem~disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
 We show the combination of these distributions in the second panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
@@
 where $z$ is the height above the Galactic plane and $z_d$ is the scale height.
-We set $z_d = 0.3 \unit{kpc}$ for the low-$\alpha$ disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the high-$\alpha$ disc \citep{Bovy+2016}.
-\todo{Neige to Tom: for bar, I will think more for your bar scale-height, but the exact value should not change your results much since they will only slightly change the distance distribution of your sources, but not the rates nor the normalization.}
-For the bulge, we set $z_d = 1.5 \unit{kpc}$ such that the probability of forming a star approaches zero at approximately the co-rotation radius of the Galactic bar/bulge \citep{Bovy+2019}.
-\todo{@Neige, did I justify the bulge/bar height correctly?
-A: The vertical distribution should not influence at which radius the bar should stop forming stars -- more later}.
-We show the combination of these distributions in the last panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
+We set $z_d = 0.3 \unit{kpc}$ for the low-\achem~disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the high-\achem~disc \citep{Bovy+2016}.
+For the bar, we set $z_d = 0.2 \unit{kpc}$ \citep{Wegg+15}. We show the combination of these distributions in the last panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
 
@@
 
-Although \citet{Frankel+2018} only fit this model for the low-$\alpha$ disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disc and the bar, but focusing on the chemical tracks more representative to the inner disc and large ages.
-\citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-$\alpha$ discs, the Milky Way abundance distributions could be well reproduced.
+Although \citet{Frankel+2018} only fit this model for the low-\achem~disc, we also use this metallicity-radius-time relation for the high-$\alpha$ disc and the bar, but focusing on the chemical tracks more representative to the inner disc and large ages.
+\citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-\achem~discs, the Milky Way abundance distributions could be well reproduced.
 Empirically, the chemical tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.

### 2021-07-06 paper/tex/sections/results.tex
lieke feedback section 3.1

@@
 We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-This shows that the detectable population of these massive DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel).
+This shows that the detectable population of these DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel).
 This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency.
-This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish these more massive DCOs from WDWDs probabilistically.
-There are several other notable features in these distributions and to understand these we overplot reference lines indicating where a circular binary with the average chirp mass (annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).
+This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish more massive DCOs from WDWDs probabilistically.
+There are several other notable features in these distributions.
+To understand these we overplot reference lines indicating where a circular binary with the average chirp mass ($\avg{\mathcal{M}_c}$, annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).
 
-We would expect that if a population was entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines (roughly the minimum and maximum distance to a source in the Milky Way).
-From inspection of the bottom panels with each individual DCO type we see that, though this is the true for a large fraction of the population, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$.
+Firstly, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
+Additionally, we expect that if a population is entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines, roughly the minimum and maximum distance to a source in the Milky Way.
+From inspection of the bottom panels with each individual DCO type we see that this is the true for a large fraction of the population.
+However, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$.
 This offshoot is composed of eccentric binaries for which the circular distance contours do not apply.
-For instance, we plot the 90\% contour of only the circular sources in our sample over the density distribution in each of the bottom panels and it is clear that the circular subsample is bounded by the distance lines.
-We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the differences for eccentric sources.
-Additionally, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
+For instance, we plot the 90\% contour of only the \textit{circular} sources in our sample over the density distribution in each of the bottom panels and it is indeed bounded by $0.1$--$30 \unit{kpc}$ the distance lines.
+We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the different limit for eccentric sources.
+To further illustrate this point, we show the same plot but with each point coloured by its eccentricity in Fig.~\ref{fig:dcos_on_sc_ecc_col}.
+Overall, we can see that eccentric sources tend to be located on a slightly different location on the sensitivity curve and so this could perhaps be used help in identifying them.
 

### 2021-07-06 paper/tex/sections/appendix.tex
add eccentric dco on sc plot

@@
 
+\subsection{Distribution of eccentric sources on sensitivity curve}
+\begin{figure*}[hb]
+    \centering
+    \includegraphics[width=\textwidth]{dcos_on_sc_eccentric_colours.png}
+    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
+We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.}
+    \label{fig:dcos_on_sc_ecc_col}
+\end{figure*}
+
 \newpage

### 2021-07-07 paper/tex/sections/results.tex
Lieke section 4

@@
 The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight.
-For reference we show lines where a circular binary of average mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line).
+For reference we show lines where a circular binary of average chirp mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line).
 To highlight the role of eccentricity we further show the signal expected for an eccentric binary at 30 kpc.
@@
 This offshoot is composed of eccentric binaries for which the circular distance contours do not apply.
-For instance, we plot the 90\% contour of only the \textit{circular} sources in our sample over the density distribution in each of the bottom panels and it is indeed bounded by $0.1$--$30 \unit{kpc}$ the distance lines.
+For illustrative purposes, we plot the 90\% contour of only the \textit{circular} sources in our sample over the density distribution in each of the bottom panels and this subsample is indeed bounded by $0.1$--$30 \unit{kpc}$ the distance lines.
 We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the different limit for eccentric sources.
@@
 \subsubsection{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends across relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$.
-Unlike ground-based detector, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
+For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$.
+Unlike ground-based detectors, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
 In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting the less massive black holes.
-The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass, since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription does not produce a mass gap between neutron stars and black holes.
+The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass.
+Since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription (applied in this work) does not produce a mass gap between neutron stars and black holes.
 Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
@@
 
-The bimodality of the BHBH distribution is a result of most detectable BHBHs in our sample having unequal mass ratios.
+The bimodality of the BHBH distribution is a result of unequal mass ratios.
 The two peaks are from the primary and secondary black hole masses, which peak around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively.
@@
 The neutron star mass distribution shows that most neutron stars have low masses, with $77\%$ and $91\%$ having masses below $1.7 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
-The lack of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are artifacts of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription and do not have strong effects since the vast majority of NSs are formed with lower masses.
+The lack of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are a result of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription but do not have strong effects on our results since the vast majority of NSs are formed with lower masses.
 
-Both distributions have notable peaks around $1.26 \unit{M_{\odot}}$, though more strongly in the NSNS case, which are a result of the combination of two effects.
+Both distributions have a notable peak around $1.26 \unit{M_{\odot}}$, which is a result of the combination of two effects.
 Firstly, we set the remnant mass for all electron-capture supernovae to $1.26 \unit{M_\odot}$ (see Sec.~\ref{sec:fiducial_physics}) and thus this leads to a pileup when many systems are formed through ECSN.
@@
 \subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are the most likely to be highly eccentric of the three DCOs.
+The eccentricity distributions show that detectable BHBHs are most likely to be highly eccentric of the three DCOs.
 This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often instead result in disrupted or too-wide binaries in more weakly bound NSNSs.
+However, these stronger kicks often result in disrupted or too-wide binaries in the more weakly bound NSNSs.
 In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
@@
 We find that a significant fraction of DCOs (86\% of BHBHs, 46\% of BHNSs and 86\% of NSNSs) exceed this bound.
-This is in contrast to several previous work that assume all DCOs are circular once they reach the LISA mission.
+This is in contrast to several previous work that assume all DCOs are circular once they reach the LISA mission \citep[e.g.][]{Lamberts+2018, Sesana+2020}.
 Moreover, we find that 20\%, 8\% and 12\% of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
@@
 Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$.
-Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA it must still be early in its evolution and thus have a low orbital frequencies.
+Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution and thus have a low orbital frequencies.
 The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
 Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted.
-This means that NSNSs can be seen at the largest distances of the three DCO types.
+This means that NSNSs can be seen out to the largest distances of the three DCO types.
 
@@
 \end{equation}
-is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}. Therefore that the chirp mass uncertainty is
+is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}. Therefore the chirp mass uncertainty is
 \begin{equation}\label{eq:chirp_mass_uncertainty}
@@
 We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
-This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
+This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
 

### 2021-07-07 paper/tex/sections/variations.tex
Lieke section 4

@@
-In this section we explore the effect of varying our underlying physics assumptions and model for the Milky Way.
+In this section we explore the effect of varying the underlying binary physics assumptions and the model for the Milky Way.
 In Section~\ref{sec:detection_rate_analysis} we explore the changes in the detection rate over different physics variations  and in Section~\ref{sec:property_variations} we consider how these model physics variations change the properties of detectable systems.
@@
 \citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
-A major difference is that only two metallicities are used and they are assigned independent of age or position.
+A major difference is that only two metallicities are used and they are assigned to binaries independent of age or position.
 Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
 
-We show this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
-The two main differences we can see in these plots are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
+We show the spatial metallicity distribution for this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
+The two main differences we can see between Fig.~\ref{fig:galaxy_schematic} and \ref{fig:simple_mw} are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
 %In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
@@
 
-We find that when applying this simpler Milky Way model and our fiducial physics assumptions (model \modFid{}), the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
-Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection is overestimated by nearly a factor of 2.
+When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
+Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection has increased by nearly a factor of 2.
 

### 2021-07-08 simulation/src/variations.py
update variations (not colours though)

@@ -43,57 +43,78 @@ variations = np.array(
             "colour": plt.get_cmap("tab20")(2)
         },
         {
-            "file": "alpha0_5",
+            "file": "unstableCaseBB_opt",
             "short": "F",
+            "med": "unstable\ncase BB optimistic",
+            "long": "Unstable case BB mass transfer with optimistic CE scenario",
+            "colour": plt.get_cmap("tab20")(2)
+        },
+        {
+            "file": "alpha0_1",
+            "short": "G",
+            "med": r"$\alpha_{\rm CE}=0.1$",
+            "long": r"CE efficiency $\alpha = 0.1$",
+            "colour": plt.get_cmap("tab20b")(11)
+        },
+        {
+            "file": "alpha0_5",
+            "short": "H",
             "med": r"$\alpha_{\rm CE}=0.5$",
             "long": r"CE efficiency $\alpha = 0.5$",
             "colour": plt.get_cmap("tab20b")(11)
         },
         {
             "file": "alpha2_0",
-            "short": "G",
+            "short": "I",
             "med": r"$\alpha_{\rm CE}=2.0$",
             "long": r"CE efficiency $\alpha = 2.0$",
             "colour": plt.get_cmap("tab20b")(10)
         },
         {
+            "file": "alpha10",
+            "short": "J",
+            "med": r"$\alpha_{\rm CE}=10.0$",
+            "long": r"CE efficiency $\alpha = 10.0$",
+            "colour": plt.get_cmap("tab20b")(10)
+        },
+        {
             "file": "optimistic",
-            "short": "H",
+            "short": "K",
             "med": "optimistic\nCE",
             "long": "Optimistic CE",
             "colour": "darkgoldenrod"
         },
         {
             "file": "rapid",
-            "short": "I",
+            "short": "L",
             "med": "rapid SN",
             "long": "Fryer rapid prescription",
             "colour": "lightseagreen"
         },
         {
             "file": "maxNSmass2_0",
-            "short": "J",
+            "short": "M",
             "med": r"max $m_{\rm NS}$" + "\n" + r"$2.0 \, {\rm M_{\odot}}$",
             "long": r"Maximum neutron star mass = 2.0 ${\rm M_{\odot}}$",
             "colour": plt.get_cmap("tab20")(1/20)
         },
         {
             "file": "maxNSmass3_0",
-            "short": "K",
+            "short": "N",
[…]

### 2021-07-08 simulation/slurm/combineHdf5.py
add combination script

@@ -1,0 +1,70 @@
+import numpy as np
+import h5py as h5
+import sys
+import getopt
+
+PATH_TO_FILES = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
+
+def combineMetallicities(zlist, dirname):
+    #-- Input files to be combined
+
+    print('combining the COMPASOutput files for the simulation in directory ', dirname)
+    z0 = zlist[0]
+    print(z0, 'z0')
+    h5File_0 = h5.File(PATH_TO_FILES + str(dirname) + "/Z_" + str(z0) + "/STROOPWAFELcombined/COMPASOutput.h5", 'r')
+
+    groups = list(h5File_0.keys())
+    print(groups)
+
+    #-- Output file
+    h5File3 = h5.File(PATH_TO_FILES + str(dirname) + "/COMPASOutputCombined.h5", 'w')
+    for group in groups:
+
+        #-- Create a group in the output
+        print('now at', group)
+        if group=='pulsarEvolution':
+            print(group)
+        else:
+            h5File3.create_group(group)
+
+            datasets = list(h5File_0[group].keys())
+
+            #-- Loop through datasets, combine and write
+            for dataset in datasets:
+                combined_dataset = h5File_0[group][dataset]
+                for ind, z in enumerate(zlist[1:]):
+                    print('at metallicity = ', z)
+
+                    ###-- Concatenate datasets
+                    h5File_z = h5.File(PATH_TO_FILES + str(dirname) +"/Z_" + str(z) + "/STROOPWAFELcombined/COMPASOutput.h5", 'r')
+                    combined_dataset = np.concatenate([combined_dataset, h5File_z[group][dataset]])
+
+                #-- Save datasets
+                h5File3[group][dataset] = combined_dataset
+
+# COMBINED HIGH Z AND OLD FOR TOM: 
[…]

### 2021-07-08 simulation/slurm/generate_combine_scripts.py
generate slurm scripts for combination

@@ -1,0 +1,36 @@
+import sys
+sys.path.append("../src/")
+from variations import variations
+
+
+def create_file(file):
+    script_file = "scripts/combine_{}.sh".format(file)
+
+    lines = []
+    lines.append("#!/bin/bash\n")
+    lines.append("#SBATCH -J combine_{}\n".format(file))
+    lines.append("#SBATCH -n 6\n")
+    lines.append("#SBATCH -N 1\n")
+    lines.append("#SBATCH -p serial_requeue\n")
+    lines.append("#SBATCH --mem 12000\n")
+    lines.append("#SBATCH -t 00-3:00\n")
+    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/combine_{}_%A_%a.out\n".format(file))
+    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/combine_{}_%A_%a.err\n".format(file))
+    lines.append("#SBATCH --mail-user thomas.wagg@cfa.harvard.edu\n")
+    lines.append("#SBATCH --mail-type ALL\n")
+
+    lines.append("module load Anaconda3/2020.11\n")
+    lines.append("source activate lisa\n")
+
+    main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/combineHdf5.py --dirname {}'.format(file)
+    lines.append(main_line)
+
+    with open(script_file, "w") as f:
+        f.writelines(lines)
+
+
+for v in variations:
+    if v["file"] in ["fiducial", "alpha0_1", "ccSNkick_100km_s", "ccSNkick_30km_s",
+                     "maxNSmass2_0", "maxNSmass3_0", "noPISN", "rapid",
+                     "wolf_rayet_multiplier_0_1", "wolf_rayet_multiplier_5"]:
+        create_file(v["file"])

### 2021-07-08 paper/tex/sections/discussion.tex
lieke feedback discussion

@@
 
-\subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
 The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
 It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
+In addition to distinguishing them from WDWDs, we must consider how to discriminate between BHBHs, BHNSs and NSNSs themselves.
 
+\subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
 The simplest way to check whether a source is a WDWD is to check its chirp mass.
@@
 Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.25 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
-We find that for a 4(10)-year LISA mission, 17(23)\% of BHBHs, 20(24)\% of BHNSs and 2.4(2.5)\% of NSNSs satisfy this condition.
-As one would expect, this method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.
+We find that for the detectable population of a 4(10)-year LISA mission, 17(23)\% of BHBHs, 20(24)\% of BHNSs and 2.4(2.5)\% of NSNSs satisfy this condition.
+This method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.
 
-Another indicator that the source is not a WDWD would be that it is eccentric.
+Another discriminator between WDWDs and other DCOs is the eccentricity.
 WDWDs formed in the disc are thought to be formed through isolated binary formation and have little to no eccentricity \citep[e.g.][]{Nelemans+2001}.
@@
 We find that for a 4(10)-year LISA mission, 55(61)\% of BHBHs, 27(28)\% of BHNSs and 65(69)\% of NSNSs are detected with multiple harmonics.
-Both the absolute percentage and the improvement with an extended LISA mission is lower for the BHNSs as we find that these DCOs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.
+\ref{sec:fiducial_distributions}).
 
-However, we should also consider that eccentric WDWDs \textit{could} be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}.
-This means that it would not be valid to assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane.
-Therefore, we can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane.
+However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}.
+This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane.
+We can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane.
 This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc.
@@
 
-\subsubsection{Separating BHBHs, BHNSs and NSNSs}
+\subsubsection{Discriminating between BHBHs, BHNSs and NSNSs}
 
-The problem of separating the BHBH, BHNS and NSNS population can be more difficult.
-We can follow a similar method to the WDWDs (see Sec.~\ref{sec:WDWD_distinguish}) by applying our knowledge of the maximum mass of a neutron star.
+The problem of discriminating between the BHBH, BHNS and NSNS populations can be more difficult than distinguishing them from WDWDs.
+For NSNSs, we can follow a similar method to the WDWDs (see Sec.~\ref{sec:WDWD_distinguish}) by applying our knowledge of the maximum mass of a neutron star.
 Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
 For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) for BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) for BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) for NSNSs.
+
 For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.
-
 Another possible solution would be the existence of electromagnetic counterparts to the gravitational wave signal.
-In the next section (Sec.~\ref{sec:pulsar_matching}) we consider the possibility of detecting a pulsar within a BHNS or NSNS system.
+In Section~\ref{sec:pulsar_matching} we consider the possibility of detecting a pulsar within a BHNS or NSNS system.
 This could be used to identify the type of the source, however it is unlikely that a large fraction of the population will contain pulsars that are beaming towards the Earth.
 
-One could also consider using the eccentric or orbital frequency to separate the populations since the distributions are reasonable different for each DCO type (see Fig.~\ref{fig:fiducial_pdf_distributions}).
-This method would also pose a challenge as it would likely only favour one DCO type as the source of the signal rather than provide strong evidence as the chirp mass could.
+One could also consider using the eccentricity or orbital frequency to separate the populations since the distributions are different for each DCO type (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+This method would also pose a challenge as it would likely only rule out some DCO types as the source of the signal rather than provide strong evidence of the exact type.
 
@@
 A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
-Altneratively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude better than other proposed observations \citep{Kyutoku+2019, Thrane+2020}.
+Alternatively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude more accurately than other proposed observational constraints \citep{Kyutoku+2019, Thrane+2020}.
 
-In this section, we perform some back-of-the-envelope calculations to order to estimate how we can use SKA to match pulsars to LISA detections.
+In this section, we perform some back-of-the-envelope calculations in order to estimate how we can use SKA to match pulsars to LISA detections.
 
-First, we can consider how many pulsars SKA is likely to detect.
+First, we consider how many pulsars SKA is likely to detect.
 \citet{Keane+2015} uses PSRPOPPy \citep{Bates+2014} to simulate the Milky Way pulsar population.
 They find that for SKA-1, approximately $10000$ pulsars will be discovered.
-The second phase of SKA, which should also have been approved and be in operation by the time of the LISA mission, would yield a total of $35000$-$41000$ pulsars \citep{Keane+2015}, where we use the average, $38000$, in further estimates below.
+The second phase of SKA, which should be in operation by the time of the LISA mission, would yield a total of $35000$-$41000$ pulsars \citep{Keane+2015}.
+We use the average, $38000$, in further estimates below.
 Moreover, we are only interested in pulsars that are part of a binary system.
 We can estimate this pulsar binary fraction as the fraction of known pulsars that are in binaries using the ATNF Pulsar Catalogue\footnote{\url{https://www.atnf.csiro.au/research/pulsar/psrcat}} \citep{Manchester+2005}.
-$290$ of the $2872$ currently known pulsars are in binary systems and thus we can estimate the binary fraction of pulsars as $10\%$.
+$290$ of the $2872$ currently known pulsars are in binary systems and thus we estimate the binary fraction of pulsars as $10\%$.
 
@@
 Therefore, one could perform a targetted search with SKA that checks the sky location given by LISA and only looking for binary pulsars with orbital frequencies within the errors.
-If there was \textit{still} more than one possible pulsar one could then also check against the chirp mass.
-In this way, it would still be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
+If there was \textit{still} more than one possible pulsar one could also check against the chirp mass.
+In this way, it will be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
 
 In order to assess the efficacy of this method, we would need to know the probability that two random binary pulsars would have orbital frequencies and chirp masses close enough that one could not tell which pulsar matches the LISA detection.
-This would require simulating the SKA population of pulsars with a code such as PSRPOPPy to find the frequency and chirp mass distribution and thus is beyond the scope of this paper.
+This would require simulating the SKA population of pulsars with a code such as PSRPOPPy to find the frequency and chirp mass distribution, which is beyond the scope of this paper.
 However, the uncertainty on the orbital frequency of a binary on the detection threshold ($\rho = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
@@
 \subsection{Caveats}\label{sec:caveats}
-\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar physics and the use of approximate fitting formulae.
-We cannot use detailed stellar evolution codes to produce such a large sample of DCOs in a reasonable amount of time.
-Therefore COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
-This means that some of the finer points of evolution may be approximated but generally the final product of the stars on a population as a whole is reasonably close to the true result.
-In addition, much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics.
-We attempt to understand the importance of these assumptions by creating many different physics variations.
-However, it is not reasonable to change every possible parameter (especially since many parts of the code have fixed assumptions) and therefore our results are subject to the accuracy of the assumptions made within the COMPAS code.
+\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
+COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
+Much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics.
+We attempt to understand the importance of these assumptions by varying over many different physics assumptions.
 
@@
 \textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ and should not be extrapolated outside this region.
-On the scale of the Universe (more relevant for LIGO predictions), this does not usually pose a significant problem as the population is usually fairly low metallicity.
-However, for local GW detection in the Milky Way (based on the metallicity relation in \citet{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of formation occurs past $Z = 0.03$.
+However, in the Milky Way (based on the metallicity relation in \citet{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
 Therefore, for our study we had to reassign any metallicities outside of COMPAS' range.
-For any metallicity below the minimum, we places it in our lowest metallicity bin.
-For any metallicity above the minimum we placed it uniformly randomly in one of the top 5 highest bins (since using a single bin for many binaries led to unphysical artifacts in our results).
+We expect that stellar winds will be reduced to such a degree that they are effectively zero for any metallicity below the minimum.
+Hence we set any metallicity below the minimum, $Z = 10^{-4}$, equal to the $Z = 10^{-4}$.
+Similarly, DCO formation is less efficient at high metallicity \citep[e.g.][]{Broekgaarden+2021} and so exploring metallicities above the COMPAS maximum is unlikely to contribute significantly to the observed rate.
+Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins (since using a single bin for many binaries leads to unphysical artifacts).
 
@@
 We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions.
-For instance, \citet{Kremer+2018} showed that around $21$ systems could be detected in Milky Way globular clusters through dynamical formation and thus different channels can still contribute significantly to the detection rate.
+For instance, \citet{Kremer+2018} predict that around $21$ systems could be detected in Milky Way globular clusters with LISA, formed through dynamical formation and thus different channels can still contribute significantly to the detection rate.
 
-\textit{Halo and globular clusters:} Moreover, our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo or globular clusters.
+\textit{Halo and globular clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo or globular clusters.
 \citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
@@
 
-\textit{Systemic kicks:} Another important consideration about our galaxy is that we do not include the effect of systemic kicks on the final location of the sources.
+\textit{Systemic kicks:} We do not include the effect of systemic kicks on the final location of the sources.
 This would require integrating the orbital evolution of the millions of binaries in our sample and thus was not computationally reasonable to include.
@@
 This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold.
-This would allow one to refine the measurement of the eccentricity uncertainty much further by comparing the many different harmonics.
+This would allow one to refine the measurement of the eccentricity uncertainty significantly by comparing the many different harmonics.
 Therefore, the eccentricity uncertainty that we calculate in this study is a pessimistic estimate.
 Smaller eccentricity uncertainties would have two main effects on our results.
-Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty, however it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps.
-Secondly, it would improve our ability to distinguish between WDWDs and these higher mass DCOs.
-However, until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.
+Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty.
+However, it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps.
+Secondly, it would improve our ability to distinguish between WDWDs and higher mass DCOs.
+Until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.

### 2021-07-08 paper/tex/sections/comparisons.tex
Updates from Overleaf

@@
 
-In Figure~\ref{fig:previous_studies}, we compare similar previous studies that have investigated the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
+In Figure~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
 The table details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
-This table not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
+This table does not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
 We additionally do not include papers that don't use population synthesis or do not simulate sources in the Galactic plane \citep[e.g.][]{Andrews+2020, Kremer+2018} such that we only compare with papers with similar methodology and focus.
 
-\citet{Nelemans+2001} were the first to investigate the population of LISA detectable stellar mass double compact objects.
-Their predictions of the number of detectable DCOs are very different from our own, where we find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
-However, since the publication of their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which strongly affect the expected detections rates.
+\citet{Nelemans+2001} were the first to investigate the population of LISA-detectable stellar mass double compact objects.
+Their predictions of the number of detectable DCOs are very different from our own, where  We find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
+However, Since the publication of their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which strongly affect the expected detections rates.
 
-\citet{Belczynski+2010} built upon this work by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
+\citet{Belczynski+2010} built upon the work of \citet{Nelemans+2001}, by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
 They found a similar number of BHBH and BHNS detection to \citet{Nelemans+2001}, but a lower number of NSNS detections.
@@
 They find significantly fewer BHBHs than our fiducial model despite using the same SNR threshold and LISA mission length.
-
-The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code, however we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
+%
+The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code.
+However, we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
 Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.

### 2021-07-08 paper/tex/sections/methods.tex
Updates from Overleaf

@@
 The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate.
-But the central bar was shown to contain stars with an age range of 6-12 Gyr \citep[e.g.,][]{Bovy+2019}, where the younger tail of ages might come from the growth of the Galactic bar.
-To model the bar's age distribution more realistically than in previous studies (assuming an old bulge coming from a single starburst), we choose to adopt a star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+But the central bar was shown to contain stars with an extended age range, with most observed stars between 6 and 12 Gyr \citep[e.g.,][]{Bovy+2019}, and a younger tail of ages that could come from the subsequent secular growth of the Galactic bar.
+To model the bar's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
 We show these distributions in the first panel in the left half of Fig.~\ref{fig:galaxy_schematic}.

### 2021-07-08 paper/tex/sections/conclusion.tex

@@
-We used the rapid population synthesis code COMPAS to simulate over two billion massive binaries and place them in an empirically-informed analytical model of the Milky Way in order to estimate and investigate the LISA detectable population of BH and NS binaries.
+We provide predictions for the detection rate and population properties of LISA detectable BHBH, BHNS and NSNS.
+To this end, we use the rapid population synthesis code COMPAS to simulate over two billion massive binaries, to explore the effect of parameters that are varied to represent the most common uncertainties in binary physics.
+We use an  empirically-informed analytical model to distribute the resulting BHBH, BHNS and NSNS populations in a Milky-Way like galaxy based on their birth metallicity, in order to estimate and investigate the LISA detectable population of BH and NS binaries.
 
@@
 Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
-    \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities during the LISA mission, unlike the more numerous WDWD LISA population.
+This implies that LISA will be able provide conclusive evidence about the existence of a lower-mass gap.
+    \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities when observable by the LISA mission, unlike the more numerous WDWD LISA population.
 We find that 86(20)\% of BHBHs, 46(8)\% of BHNSs and 86(12)\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
@@
 Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} We approximately predict that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.
+    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.

### 2021-07-08 paper/tex/sections/comparisons.tex

@@
     \caption{A table comparing previous studies of a similar nature to this work.
-The works listed in the table are \citet{Nelemans+2001,Belczynski+2010,Liu+2014,Lamberts+2018,Lau+2020,Breivik+2020,Sesana+2020}.}
+The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020} and \citet{Breivik+2020}.}
     \label{fig:previous_studies}
@@
 In Figure~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
-The table details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
-This table does not include the number papers on the LISA WDWD population as we do not make predictions for these DCOs.
-We additionally do not include papers that don't use population synthesis or do not simulate sources in the Galactic plane \citep[e.g.][]{Andrews+2020, Kremer+2018} such that we only compare with papers with similar methodology and focus.
+Figure~\ref{fig:previous_studies} details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
+We only include papers that are similar to our work, such that they use population synthesis and simulate sources in the Galactic plane.
+Moreovoer, Figure~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
 
-\citet{Nelemans+2001} were the first to investigate the population of LISA-detectable stellar mass double compact objects.
-Their predictions of the number of detectable DCOs are very different from our own, where  We find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
-However, Since the publication of their paper, there have been many changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution, which strongly affect the expected detections rates.
+\paragraph{\citet{Nelemans+2001}} were the first to investigate the population of LISA detectable stellar mass double compact objects.
+We find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.
+We can understand this difference from changes both to the specifications of LISA (such as the mission length and SNR threshold for detection) and our understanding of massive star evolution since the publication of their paper, which both strongly affect the expected detections rates.
 
-\citet{Belczynski+2010} built upon the work of \citet{Nelemans+2001}, by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
-They found a similar number of BHBH and BHNS detection to \citet{Nelemans+2001}, but a lower number of NSNS detections.
-The low total detection rate for all DCOs in this paper is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
+\paragraph{\citet{Belczynski+2010}} built upon the work of \citet{Nelemans+2001}, by using a different population synthesis code with two model variations and a multi-component model for the Milky Way.
+They find a much lower detection rate for BHNSs and NSNSs (and agreed on zero BHBHs) when compared to \citet{Nelemans+2001}.
+They claim that this discrepancy comes from differences in their population synthesis and an overall lower formation rate rather than any changes to LISA detectability.
+The low total detection rate for all DCOs in this paper compared to our work is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
 The reduced mission length means that the source signal has much less time to accumulate, whilst also fewer WDWDs can be resolved in this time, leading to a weaker signal and an increased Galactic confusion noise relative to our work.
 
-More recently, \citet{Lamberts+2018} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
+\paragraph{\citet{Liu+2014}} performed a similar investigation using a different population synthesis code and find higher rates than earlier works.
+Their lower detection threshold and longer mission length compared to \citet{Belczynski+2010} likely explains the relatively increased rates.
+Yet their rates are still significantly below what we find.
+This could be for several reasons; they assume all binaries are circular both in their evolution and for detection.
+This means that systems may not have inspiralled as far before the LISA mission or may appear to have weaker gravitational waves when eccentricity is not accounted for.
+They also use a simplified model for the Milky Way with a single disc of one metallicity and constant star formation, whilst also using a mission length half what we assume.
+Each of these factors likely contributes to the lower overall detection rates.
+
+\paragraph{\citet{Lamberts+2018}} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
 \citet{Sesana+2020} followed up on this paper using the same simulated BHBH population and presented updated results for the number of expected BHBH detections.
@@
 %
-The discrepancy between their results and ours could be a result of different implicit assumptions in their population synthesis code.
-However, we expect that BSE should be similar to COMPAS since it provided the basis of the COMPAS code.
-Another major difference is that, unlike this work, they assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-We also improve upon this work by using a larger number of metallicity bins since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate.
+The discrepancy between the results of \citet{Sesana+2020} and those presented in this work could be caused by different treatments of eccentricity.
+Unlike our work, \citet{Sesana+2020} assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
+This is especially relevant as we find that around 50\% of LISA detectable BHBHs are not circular and around 10\% have significant eccentricity.
+We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Section~\ref{sec:mw_changes}).
+Finally, it could be that different implicit assumptions in their population synthesis code lead to differences in our results \citep{Toonen+2014}.
 
-\citet{Lau+2020} focussed on the number of Galactic NSNS binaries that could be detected by LISA.
+\paragraph{\citet{Lau+2020}} focussed on the number of Galactic NSNS binaries that could be detected by LISA.
 Their study uses the same population synthesis code, COMPAS, as this work, though an earlier version.
-Despite this, their study found a much larger number of detections.
+Despite this, their study finds a much larger number of detections.
 They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.\,\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}).
+However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences.
+%
+We therefore surmise that the remaining difference between our results is likely due to way in which we simulate the Milky Way.
+\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Section~\ref{sec:mw_changes}.
+We find that this simpler model for the Milky Way could result in an overestimate of the NSNS detection rate and so this may explain the discrepancy between our results.
+\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger.
 
-We therefore surmise that the difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
+%\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
 The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity, both changes that could decrease the NSNS detection rate given that we find most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
 
-Finally, \citet{Breivik+2020} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
+\paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
 They find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.

### 2021-07-08 simulation/src/galaxy.py
update bulge scale height

@@ -214,7 +214,7 @@ def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
 
         scale_height = 0.3 * u.kpc if com == "thin_disc"\
             else 0.95 * u.kpc if com == "thick_disc"\
-            else 1.5 * u.kpc
+            else 0.2 * u.kpc
 
         z[i] = draw_heights(sizes[i], z_d=scale_height)
 

### 2021-07-08 paper/tex/sections/comparisons.tex
typo fix

@@
 We only include papers that are similar to our work, such that they use population synthesis and simulate sources in the Galactic plane.
-Moreovoer, Figure~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
+Moreover, Figure~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
 

### 2021-07-10 simulation/src/simulate_DCO_detections.py
add position params to sim, switch to just 4 year

@@ -102,20 +102,21 @@ def main():
     dt = np.dtype(float)
     dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
              ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
-             ("tau", dt), ("dist", dt), ("Z", dt), ("snr", dt), ("weight", dt),
+             ("tau", dt), ("Z", dt), ("R", dt), ("z", dt), ("theta", dt), ("snr", dt), ("weight", dt),
              ("seed", dt)]
     to_file = np.zeros(shape=(loops * MAX_HIGH,), dtype=dtype)
 
-    n_ten_year_list = np.zeros(loops)
+    n_detect_list = np.zeros(loops)
     total_MW_weight = np.zeros(loops)
-    tot_ten = 0
+    tot_detect = 0
     for milky_way in range(loops):
         if not use_simple_mw:
             # draw parameters from Frankel Model
-            tau, dist, Z_unbinned = simulate_mw(MW_SIZE)
+            tau, dist, Z_unbinned, pos = simulate_mw(MW_SIZE)
         else:
             # draw parameters from simple Milky Way (following Breivik+2020)
-            tau, dist, Z_unbinned = simulate_simple_mw(MW_SIZE)
+            tau, dist, Z_unbinned, pos = simulate_simple_mw(MW_SIZE)
+        R, z, theta = pos
 
         # work out COMPAS limits (and limit to Z=0.022)
         min_Z_compas = np.min(compas_Z_unique)
@@ -133,7 +134,8 @@ def main():
 
         # sort by metallicity so everything matches up well
         Z_order = np.argsort(Z_unbinned)
-        tau, dist, Z_unbinned = tau[Z_order], dist[Z_order], Z_unbinned[Z_order]
+        tau, dist, Z_unbinned, R, z, theta = tau[Z_order], dist[Z_order], Z_unbinned[Z_order],\
+            R[Z_order], z[Z_order], theta[Z_order]
 
         # bin the metallicities using Floor's bins
         h, _ = np.histogram(Z_unbinned, bins=Z_bins)
@@ -170,8 +172,9 @@ def main():
         insp = t_merge > (tau - t_evol)
 
         # trim out the merged binaries
[…]

### 2021-07-10 paper/tex/sections/results.tex
update text to match new properties grid

@@
 
+\subsubsection{Mass Ratio}
+The mass ratio distribution for each DCO type is relatively distinct from the others.
+The majority of NSNSs have a mass ratio close to unity, with 90\% of systems having $q > 0.8$.
+The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae or from low mass stars.
+We set the remnant mass for any system formed through ECSN to $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{sec:fiducial_physics}).
+The remnant mass prescription that we use gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
+This means that many NSs are formed with equal masses and hence we see a mass ratio distribution peaked around unity.
+
+In contrast, only 9\% of detectable BHBHs are formed with $q > 0.8$ and distribution peaks around $q = 0.4$.
 The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
@@
 
-\subsubsection{Neutron Star Mass}
-The neutron star mass distribution shows that most neutron stars have low masses, with $77\%$ and $91\%$ having masses below $1.7 \unit{M_{\odot}}$ for BHNSs and NSNSs respectively.
-The lack of neutron stars around $1.7 \unit{M_{\odot}}$ and the subsequent small peaks are a result of the discontinuous nature of the \citet{Fryer+2012} remnant mass prescription but do not have strong effects on our results since the vast majority of NSs are formed with lower masses.
-
-Both distributions have a notable peak around $1.26 \unit{M_{\odot}}$, which is a result of the combination of two effects.
-Firstly, we set the remnant mass for all electron-capture supernovae to $1.26 \unit{M_\odot}$ (see Sec.~\ref{sec:fiducial_physics}) and thus this leads to a pileup when many systems are formed through ECSN.
-In addition, the Fryer remnant mass prescription gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
+We find that detectable BHNSs have even more unequal mass ratios, such that the distribution is almost entire disjoint from that of NSNSs.
+Moreover, the mass ratio distribution is bimodal, where the two peaks arise from two distinct formation scenarios.
+Around two thirds of detectable BHNSs experience at least one common envelope event, whilst the last third are formed through only stable mass transfer.
+The first peak at $q = 0.18$ is from systems that experience at least one CE and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
+Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arise from the fraction of the population that underwent only stable mass transfer.
+The stability of mass transfer is strongly dependent on the mass ratio and thus these systems have a bias for more equal mass ratio systems, leading to a peak at higher $q$.
 
@@
 
-\subsubsection{Luminosity Distance}
-Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect.
-This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.
+\subsubsection{Time since formation}
+The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see Fig.~\ref{fig:galaxy_schematic}).
+In contrast, we find that the \textit{detectable} systems are primarily formed recently, with the majority formed in the past $2 \unit{Gyr}$, in addition to a tail of systems out to earlier times.
 
-However, more surprisingly, we also see that the NSNS distribution extends to higher distances than the other DCOs.
-The reason for this is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.3$).
-The BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
-Therefore, despite their relatively higher masses, the maximum distance at which a source is detectable is generally lower than the eccentric NSNSs and hence the distribution tends to zero at smaller distances.
-Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$.
-Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution and thus have a low orbital frequencies.
-The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
-Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted.
-This means that NSNSs can be seen out to the largest distances of the three DCO types.
+The peak at recent times is due to the fact that most binaries in our sample are formed with merger times on the order of a couple of Gyr (since most form through a common envelope phase that significantly tightens the binary).
+For a binary to be in the LISA band and detectable it must be near the end of its inspiral and so LISA will be most sensitive to sources that were formed a couple of Gyr ago.
 
-\subsubsection{Lookback Time}
-Although when creating each mock Milky Way galaxy the lookback time is drawn independently from other parameters, and in the same way for every DCO type, the distributions are clearly different for each type of DCO.
-This is because for a binary to be detectable, it must have an orbital frequency within the LISA band.
-Therefore a binary needs to have completed most of its inspiral to be visible in the LISA band and thus detectable systems will tend to have lookback time that are close to their merger times, which \textit{are} a function of other binary parameters.
+The peak is sharpest for NSNSs as they have the highest orbital frequencies and largest fraction of eccentric system, which result in shorter inspiral times and therefore later formation times.
+Conversely, the peak is less prominent for BHNSs as they are the most circular, have moderate orbital frequencies and masses.
 
-Since most of the DCOs are formed through common envelope events, their initial separations are relatively tight and so if a binary it given a long lookback time, it will have merged before the LISA mission.
-This explains the peak in each distribution at short lookback times.
-The later lookback times correspond to systems that are formed through channels in which mass transfer is only stable and no common envelope event occurs.
+\subsubsection{Time until merger}
+The final panel of Fig.~\ref{fig:fiducial_pdf_distributions} shows the remaining time until merger for each of the DCO types at the start of LISA mission.
+The distributions are strikingly similar and peak with merger times of around a Myr.
 
-The trends across the different DCO types can be explained by considering that the merger time is a function of the masses, frequency and eccentricity of th source.
-This dependence can be approximately written as $t_{\rm merge} \propto f_{\rm orb}^{-4} m_1^{-3} (1 - e^2)^{-7/2}$,  \citep[][Eq.~5.14]{Peters+1964}.
-Therefore, although NSNSs are the lowest mass systems, their relatively higher orbital frequencies means that they have the shortest merger times.
-This same logic implies that BHNSs should have the next shortest merger times and then BHBHs.
-This order is flipped due to the fact that high eccentricity results in a shorter merger time and we find that LISA detectable BHNSs are mostly circular, whilst BHBHs have a significant highly eccentric subpopulation.
+The merger time is a function of the mass, frequency and eccentricity of the sources, such that more massive, higher frequency and more eccentric sources merge faster \citep[][Eq.~5.14]{Peters+1964}.
+So, despite the fact that each DCO type often has higher values in any one of these properties, the convolution of all three tends to negate the differences.
+For example, NSNSs have the highest orbital frequencies and are mildly eccentric whilst BHNSs have moderate orbital frequencies and are more circular.
+However, BHNSs are more massive in general and so the overall merger times are distributed very similarly for both DCO types.
 

### 2021-07-10 paper/tex/sections/comparisons.tex
Updates from Overleaf

--- 2021-07-08 paper/tex/sections/comparisons.tex
@@
 Unlike our work, \citet{Sesana+2020} assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-This is especially relevant as we find that around 50\% of LISA detectable BHBHs are not circular and around 10\% have significant eccentricity.
+This is especially relevant as we find that around 86\% of LISA detectable BHBHs are not circular and around 20\% have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
 We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Section~\ref{sec:mw_changes}).

### 2021-07-10 paper/tex/sections/conclusion.tex
Updates from Overleaf

@@
 To this end, we use the rapid population synthesis code COMPAS to simulate over two billion massive binaries, to explore the effect of parameters that are varied to represent the most common uncertainties in binary physics.
-We use an  empirically-informed analytical model to distribute the resulting BHBH, BHNS and NSNS populations in a Milky-Way like galaxy based on their birth metallicity, in order to estimate and investigate the LISA detectable population of BH and NS binaries.
+We use an new empirically-informed analytical model to distribute the resulting BHBH, BHNS and NSNS populations in a Milky-Way like galaxy based on their birth metallicity, in order to estimate and investigate the LISA detectable population of BH and NS binaries.
 

### 2021-07-10 paper/tex/sections/results.tex
Updates from Overleaf

@@
 
+\subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
+In the first panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems.
+Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
+There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect.
+This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.
+
+However, more surprisingly, we also see that the NSNS distribution extends to higher distances than the other DCOs.
+The reason for this is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.3$).
+The BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
+Therefore, despite their relatively higher masses, the maximum distance at which a source is detectable is generally lower than the eccentric NSNSs and hence the distribution tends to zero at smaller distances.
+Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$.
+Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution and thus have a low orbital frequencies.
+The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
+Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted.
+This means that NSNSs can be seen out to the largest distances of the three DCO types.
+
+\todo{There will also be a little bit more text to explain the example distribution over galaxies in the latter three panels -- will make once Floor combines the latest fiducial simulation data}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
+    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
+    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
+    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
+    \caption{\textbf{First panel:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
+\textbf{Final three panels:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity.
+Stars represent an example of the detectable systems in a 4-year LISA mission.
+Each panel corresponds to a separate DCO type.
+\todo{make plots}}
+    \label{fig:detectable_distance_dist}
+\end{figure}
+
 \subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}

### 2021-07-11 paper/tex/sections/results.tex
update measurement uncertainty plots

@@
     \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
-    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
-    \includegraphics[width=\columnwidth, height=4.5cm]{example-image-a}
+    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
+    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
+    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
     \caption{\textbf{First panel:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
@@
 \end{equation}
-where $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}) and $e$ is the eccentricity and
+where $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}), $e$ is the eccentricity and
 \begin{equation}
@@
 \end{equation}
-where $\rho$ is the signal-to-noise ratio, $f_{\rm dom}$ is the harmonic frequency with the strongest signal-to-noise ratio ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) and $L$ is the effective detector baseline.
+where $L$ is the effective detector baseline, which for LISA is 2 AU since it will orbit the Sun.
 
 We plot the angular resolution in Fig.~\ref{fig:ang_res}.
-From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 square degrees.
+The area of a patch on the sky that can be attributed to a source is given by $A = \pi \sigma_\theta^2$.
+From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 degrees.
 The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).

### 2021-07-11 paper/figure_notebooks/bootstrap.py

@@ -136,12 +136,6 @@ def bootstrapped_ecdf(variable, weights, seeds, ax,
     # store the ECDF values for each bootstrap
     ecdf_vals = np.zeros((bootstraps, x_count))
 
-    # make everything unique and adjust weights
-    _, uni_index, uni_count = np.unique(seeds,
-                                        return_index=True, return_counts=True)
-    variable = variable[uni_index]
-    weights = weights[uni_index] * uni_count
-
     # record indices to sample from
     indices = np.arange(len(variable))
 
@@ -152,13 +146,26 @@ def bootstrapped_ecdf(variable, weights, seeds, ax,
     else:
         x_vals = np.linspace(np.min(variable), np.max(variable), x_count)
 
+    sorted_order = np.argsort(seeds)
+    sorted_seeds = seeds[sorted_order]
+
     # perform bootstrapping
     for i in range(bootstraps):
+        _, starts, counts = np.unique(sorted_seeds, return_counts=True, return_index=True)
+        res = np.split(sorted_order, starts[1:])
+        inds = np.array([np.random.choice(r) if len(r) > 1 else r[0] for r in res])
+
+        loop_variable = variable[inds]
+        loop_weights = weights[inds] * counts
+
+        # record indices to sample from
+        indices = np.arange(len(loop_variable))
+
         # sample indices
         boot_index = np.random.choice(indices, size=len(indices), replace=True)
 
-        boot_var = variable[boot_index]
-        boot_weight = weights[boot_index]
+        boot_var = loop_variable[boot_index]
+        boot_weight = loop_weights[boot_index]
 
         # create a CDF
         sorted_index = np.argsort(boot_var)
@@ -177,192 +184,14 @@ def bootstrapped_ecdf(variable, weights, seeds, ax,
     percentiles = np.percentile(ecdf_vals, [15.89, 84.1, 2.27, 97.725], axis=0)
 
     # plot uncertainties as filled areas
-    ax.fill_between(x_vals, percentiles[2], percentiles[3],
-                    alpha=0.15, color=color, **kwargs)
-    ax.fill_between(x_vals, percentiles[0], percentiles[1],
-                    alpha=0.3, color=color, **kwargs)
+    ax.fill_between(x_vals, percentiles[2], percentiles[3], alpha=0.15, color=color, **kwargs)
+    ax.fill_between(x_vals, percentiles[0], percentiles[1], alpha=0.3, color=color, **kwargs)
 
[…]

### 2021-07-11 paper/tex/sections/results.tex
add placeholder plot

@@
 
-\todo{There will also be a little bit more text to explain the example distribution over galaxies in the latter three panels -- will make once Floor combines the latest fiducial simulation data}
+\todo{There will also be a little bit more text to explain the example distribution over galaxies in the lower panel -- will make properly once Floor combines the latest fiducial simulation data (this plot is sampling uniformly rather than based on the distribution)}
 
-\begin{figure}[t]
+\begin{figure}[thb]
     \centering
     \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
-    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
-    \includegraphics[width=5.5cm, height=4.5cm]{example-image-a}
-    \caption{\textbf{First panel:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
-\textbf{Final three panels:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity.
-Stars represent an example of the detectable systems in a 4-year LISA mission.
-Each panel corresponds to a separate DCO type.
-\todo{make plots}}
+    \includegraphics[width=\columnwidth]{sources_on_mw.png}
+    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
+\textbf{Bottom:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity.
+The large $\odot$ shows the position of the Sun.
+Stars represent a typical example of the detectable systems in a 4-year LISA mission.
+\todo{make proper plot, maybe separate panels for different types (hard to arange then though), thoughts on black background?}}
     \label{fig:detectable_distance_dist}

### 2021-07-13 simulation/slurm/generate_scripts.py
prep scripts for main run!

@@ -24,7 +24,9 @@ def create_file(dco_type, file, simple_mw=False):
 
     main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputCombined.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/{0}_{1}_'.format(dco_type, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 -t ' + '{}\n'.format(dco_type)
     if file == "optimistic":
-        main_line = main_line.replace("\n", " --opt-flag\n")
+        main_line = main_line.replace("\n", " --opt-flag\n").replace("all_dco_legacy_CEbug_fix/optimistic", "all_dco_legacy_CEbug_fix/fiducial")
+    if file == "unstableCaseBB_opt":
+        main_line = main_line.replace("\n", " --opt-flag\n").replace("all_dco_legacy_CEbug_fix/unstableCaseBB_opt", "all_dco_legacy_CEbug_fix/unstableCaseBB")
     if simple_mw:
         main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/src/simulate_DCO_detections.py -i /n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/{1}/COMPASOutputCombined.h5 -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/output/simple_mw_{0}_{1}_'.format(dco_type, file) + '"${SLURM_ARRAY_TASK_ID}".h5 -n 50 --simple-mw -t ' + '{}\n'.format(dco_type)
         script_file = script_file.replace(".sh", "_simplemw.sh")
@@ -36,6 +38,6 @@ def create_file(dco_type, file, simple_mw=False):
 
 
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    create_file(dco_type, variations[0]["file"], simple_mw=True)
+    create_file(dco_type, "fiducial", simple_mw=True)
     for v in variations:
         create_file(dco_type, v["file"])

### 2021-07-13 simulation/slurm/run_all.sh

@@ -3,7 +3,7 @@ python generate_scripts.py
 
 for type in BHBH BHNS NSNS
 do
-    for variation in fiducial optimistic alpha0_5 alpha2_0 unstableCaseBB massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 ccSNkick_100km_s ccSNkick_30km_s noBHkick rapid maxNSmass2_0 maxNSmass3_0 noPISN wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
+    for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
     do
         sbatch --array=1-50 scripts/${type}_${variation}.sh
         sleep 1

### 2021-07-13 simulation/src/simulate_DCO_detections.py
don't forget to return positions!

@@ -112,10 +112,10 @@ def main():
     for milky_way in range(loops):
         if not use_simple_mw:
             # draw parameters from Frankel Model
-            tau, dist, Z_unbinned, pos = simulate_mw(MW_SIZE)
+            tau, dist, Z_unbinned, pos = simulate_mw(MW_SIZE, ret_pos=True)
         else:
             # draw parameters from simple Milky Way (following Breivik+2020)
-            tau, dist, Z_unbinned, pos = simulate_simple_mw(MW_SIZE)
+            tau, dist, Z_unbinned, pos = simulate_simple_mw(MW_SIZE, ret_pos=True)
         R, z, theta = pos
 
         # work out COMPAS limits (and limit to Z=0.022)

### 2021-07-13 paper/figure_notebooks/uncertainties.py
split up the fiducial notebook

@@ -1,0 +1,84 @@
+import numpy as np
+import h5py as h5
+import astropy.units as u
+import legwork
+
+dco_types = ["BHBH", "BHNS", "NSNS"]
+data_folder = "../../simulation/data/"
+sim_folder = data_folder + "simulation_high_res_double/"
+
+def get_ecc_uncertainty(t_obs=4*u.yr, source_threshold=7, harmonic_threshold=7, model="fiducial"):
+    detectable_harmonics = {"BHBH": None, "BHNS": None, "NSNS": None}
+    snr_uncertainty = {"BHBH": None, "BHNS": None, "NSNS": None}
+    ecc_uncertainty = {"BHBH": None, "BHNS": None, "NSNS": None}
+    max_harmonics = {"BHBH": None, "BHNS": None, "NSNS": None}
+
+    for i, dco_type in enumerate(dco_types):
+        with h5.File(sim_folder + "{}_{}_all.h5".format(dco_type, model), "r") as f:
+            full_data = f["simulation"][...].squeeze()
+            snr_mask = full_data["snr"] * np.sqrt(t_obs / (4 * u.yr)) > source_threshold
+            data = full_data[snr_mask]
+
+        sources = legwork.source.Source(m_1=data["m_1"] * u.Msun, m_2=data["m_2"] * u.Msun,
+                                        dist=data["dist"] * u.kpc, a=data["a_LISA"] * u.AU,
+                                        ecc=data["e_LISA"])
+
+        detectable_harmonics[dco_type] = np.zeros(len(data)).astype(int)
+        snr_uncertainty[dco_type] = np.zeros(len(data))
+        max_harmonics[dco_type] = np.zeros(len(data)).astype(int)
+
+        harmonics_required = sources.harmonics_required(sources.ecc)
+
+        harmonic_groups = [(1, 10), (10, 100), (100, 1000), (1000, 10000)]
+        for lower, upper in harmonic_groups:
+            match = np.logical_and(harmonics_required > lower, harmonics_required <= upper)
+            if match.any():
+                snr_n_2 = legwork.snr.snr_ecc_stationary(m_c=sources.m_c[match],
+                                                         f_orb=sources.f_orb[match],
+                                                         ecc=sources.ecc[match],
[…]

### 2021-07-14 simulation/output/combine_output.py
calculate distance on the fly during combination

@@ -7,11 +7,12 @@ sys.path.append("../src/")
 
 from formation_channels import identify_formation_channels
 from variations import variations
+from galaxy import distance_from_earth
 
 dt = np.dtype(float)
 dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
-         ("tau", dt), ("R", dt), ("z", dt), ("theta", dt), ("Z", dt), ("snr", dt), ("weight", dt),
+         ("tau", dt), ("dist", dt), ("R", dt), ("z", dt), ("theta", dt), ("Z", dt), ("snr", dt), ("weight", dt),
          ("seed", dt), ("channel", np.dtype(int)), ("m_1_ZAMS", dt),
          ("m_2_ZAMS", dt), ("MT1_case", np.dtype(int)),
          ("MT2_case", np.dtype(int)), ("a_ZAMS", dt), ("a_pre_SN2", dt),
@@ -85,6 +86,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
                 "e_pre_SN2": floor["doubleCompactObjects"]["eccentricityPrior2ndSN"][...].squeeze()[seeds_index],
                 "channel": channels
             }
+
+        full_data["dist"] = distance_from_earth(full_data["R"], full_data["z"], full_data["theta"])
 
         # write the rest of the files to a single file
         if simple_mw:

### 2021-07-14 simulation/output/combine_output.py
fix for simple mw

@@ -87,7 +87,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
                 "channel": channels
             }
 
-        full_data["dist"] = distance_from_earth(full_data["R"], full_data["z"], full_data["theta"])
+        if not simple_mw:
+            full_data["dist"] = distance_from_earth(full_data["R"], full_data["z"], full_data["theta"])
 
         # write the rest of the files to a single file
         if simple_mw:

### 2021-07-14 simulation/output/combine_output.py
units issue fix

@@ -1,6 +1,7 @@
 import h5py as h5
 import numpy as np
 from os.path import isfile
+import astropy.units as u
 
 import sys
 sys.path.append("../src/")
@@ -88,7 +89,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
             }
 
         if not simple_mw:
-            full_data["dist"] = distance_from_earth(full_data["R"], full_data["z"], full_data["theta"])
+            full_data["dist"] = distance_from_earth(full_data["R"] * u.kpc, full_data["z"] * u.kpc,
+                                                    full_data["theta"]).to(u.kpc).value
 
         # write the rest of the files to a single file
         if simple_mw:

### 2021-07-14 simulation/output/combine_output.py
try using supp data instead

@@ -85,11 +85,12 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
                 "kick_1": floor["doubleCompactObjects"]["drawnKick1"][...].squeeze()[seeds_index],
                 "kick_2": floor["doubleCompactObjects"]["drawnKick2"][...].squeeze()[seeds_index],
                 "e_pre_SN2": floor["doubleCompactObjects"]["eccentricityPrior2ndSN"][...].squeeze()[seeds_index],
-                "channel": channels
+                "channel": channels,
+                "dist": np.zeros(len(channels))
             }
 
         if not simple_mw:
-            full_data["dist"] = distance_from_earth(full_data["R"] * u.kpc, full_data["z"] * u.kpc,
+            supp_data["dist"] = distance_from_earth(full_data["R"] * u.kpc, full_data["z"] * u.kpc,
                                                     full_data["theta"]).to(u.kpc).value
 
         # write the rest of the files to a single file

### 2021-07-14 simulation/output/combine_output.py
stop combining simple mw

@@ -89,9 +89,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
                 "dist": np.zeros(len(channels))
             }
 
-        if not simple_mw:
-            supp_data["dist"] = distance_from_earth(full_data["R"] * u.kpc, full_data["z"] * u.kpc,
-                                                    full_data["theta"]).to(u.kpc).value
+        supp_data["dist"] = distance_from_earth(full_data["R"] * u.kpc, full_data["z"] * u.kpc,
+                                                full_data["theta"]).to(u.kpc).value
 
         # write the rest of the files to a single file
         if simple_mw:
@@ -115,5 +114,5 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
     for variation in range(len(variations)):
         combine_data(dco_type, variation)
-        if variation == 0:
-            combine_data(dco_type, variation, simple_mw=True)
+        # if variation == 0:
+        #     combine_data(dco_type, variation, simple_mw=True)

### 2021-07-14 simulation/output/combine_output.py
and also exclude the bad files

@@ -64,6 +64,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
         model = variations[variation]["file"]
         if model == "optimistic":
             model = "fiducial"
+        elif model == "unstableCaseBB_opt":
+            model = "unstableCaseBB"
         floor_file = floor_path + "{}/COMPASOutputCombined.h5".format(model)
         with h5.File(floor_file, "r") as floor:
             channels = identify_formation_channels(full_data["seed"], floor)
@@ -112,7 +114,7 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
 
 # loop over all binary types and physics variations
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    for variation in range(len(variations)):
+    for variation in [0, 1, 2, 3, 4, 5, 7, 10, 11, 12, 13, 14, 15, 16, 18]:
         combine_data(dco_type, variation)
         # if variation == 0:
         #     combine_data(dco_type, variation, simple_mw=True)

### 2021-07-17 paper/figure_notebooks/bootstrap.py
update plots to latest data

@@ -2,9 +2,67 @@ import numpy as np
 from scipy.stats import gaussian_kde
 from scipy.interpolate import interp1d
 
+def kde(variable, weights, bw_adjust=1.0, x_min=None, x_max=None, x_count=200, x_vals=None,
+        lower_bound=None, upper_bound=None, verbose=False):
+    # if a range of x values at which to evaluate have not been provided then create one
+    if x_vals is None:
+        if x_min is None:
+            x_min = np.min(variable)
+        if x_max is None:
+            x_max = np.max(variable)
+        x_vals = np.linspace(x_min, x_max, x_count)
+    else:
+        x_min, x_max = x_vals[0], x_vals[-1]
 
-def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None,
-                     bootstraps=200, x_count=500, x_min=None, x_max=None, log_scale=(False, False),
+    # calculate the covariance factor using Scott's rule
+    cv = (1 / np.sum((weights / np.sum(weights))**2))**(-1./(1+4))
+
+    # work out the bandwidth for the original data
+    bw = cv * np.std(variable)
+
+    # check if either bound is surpassed given this bandwidth
+    exceeds_lower_bound = lower_bound is not None and np.min(variable) < lower_bound + bw
+    exceeds_upper_bound = upper_bound is not None and np.max(variable) > upper_bound - bw
+
+    # mirror data as necessary and adjust height based on how much added
+    if exceeds_lower_bound and exceeds_upper_bound:
+        if verbose:
+            print("exceeds both bounds")
+        variable = np.concatenate((2 * lower_bound - variable, variable, 2 * upper_bound - variable))
+        weights = np.repeat(weights, 3)
+        height_adjust = 3
+    elif exceeds_lower_bound:
+        if verbose:
+            print("exceeds lower bounds")
+        variable = np.concatenate((variable, 2 * lower_bound - variable))
+        weights = np.concatenate((weights, weights))
+        height_adjust = 2
+    elif exceeds_upper_bound:
+        if verbose:
+            print("exceeds upper bounds")
+        variable = np.concatenate((variable, 2 * upper_bound - variable))
+        weights = np.concatenate((weights, weights))
+        height_adjust = 2
+    else:
+        height_adjust = 1
+
+    # calculate the KDE
[…]

### 2021-07-17 simulation/src/variations.py

@@ -45,7 +45,7 @@ variations = np.array(
         {
             "file": "unstableCaseBB_opt",
             "short": "F",
-            "med": "unstable\ncase BB optimistic",
+            "med": "E+K",
             "long": "Unstable case BB mass transfer with optimistic CE scenario",
             "colour": plt.get_cmap("tab20")(2)
         },

### 2021-07-19 paper/tex/sections/appendix.tex
update text to match new properties grid
clean up appendix

@@
 \subsection{Detection rate table}
-\begin{table*}[htb]
+\begin{table}[htb]
     \centering
-    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the 15 different model variations and each DCO type. Each value shows the median and the 90\% confidence interval.}
+    \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type.
+Each value shows the mean and the 90\% confidence interval.}
     \begin{tabular}{c|lll|lll}
@@
     \label{tab:detection_rates}
-\end{table*}
+\end{table}
 
 \subsection{Distribution of eccentric sources on sensitivity curve}
-\begin{figure*}[hb]
+\begin{figure}[hb]
     \centering
@@
     \label{fig:dcos_on_sc_ecc_col}
-\end{figure*}
-
-\newpage
-
-\subsection{Physics variation cumulative distributions}
-
-\begin{figure*}[htb]
-    \centering
-    \includegraphics[width=\textwidth]{variations_cdf_1_3.pdf}
-    \caption{Cumulative distribution functions for the black hole mass, neutron star mass, eccentricity during the LISA mission and merger time for each DCO type and physics variation.
-In colour we show the fiducial populations compared to changing the mass transfer efficiency $\beta$.
-We additionally show the other physics variations in the background in light grey.}
-    \label{fig:variations_cdf_1_3}
-\end{figure*}
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{variations_cdf_4_6.pdf}
-    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models using different values for $\alpha_{\rm CE}$ and changing the stability of case BB mass transfer.}
-    \label{fig:variations_cdf_4_6}
-\end{figure*}
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{variations_cdf_7_10.pdf}
-    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the maximum neutron star mass, remnant mass prescription and survivability of common envelope events initiated by Hertzsprung gap donors.}
-    \label{fig:variations_cdf_7_10}
-\end{figure*}
-
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{variations_cdf_11_14.pdf}
-    \caption{As Fig.~\ref{fig:variations_cdf_1_3}, except comparing the fiducial population with models changing the core-collapse supernova kick distributions and the presence of BH kicks and PISNs.}
-    \label{fig:variations_cdf_11_14}
-\end{figure*}
+\end{figure}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{formation_channels_BHBH.pdf}
+    \includegraphics[height=0.3\textheight]{formation_channels_BHBH.pdf}
+    \includegraphics[height=0.3\textheight]{formation_channels_BHNS.pdf}
+    \includegraphics[height=0.3\textheight]{formation_channels_NSNS.pdf}
+    \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
+Channels are described in detail in \citet{Broekgaarden+2021}.
+The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
+\todo{Update with new models}}
+    \label{fig:formation_channels}
 \end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{formation_channels_BHNS.pdf}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{formation_channels_NSNS.pdf}
-\end{figure}

### 2021-07-19 paper/tex/sections/appendix.tex
rearrange appendix to 2col, move mw compare

@@
 If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
-We assume that all mass transfer phases from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole are unstable \citep{Tauris+2015}.
+We assume that all mass transfer from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole is unstable \citep{Tauris+2015}.
 
@@
 In this section we explain the normalisation process that we refer to in Section~\ref{sec:gw_detection}.
-From each simulated instance of the Milky Way we can extract the fraction of targets that are detectable, where we define a target as one of BHBH, BHNS or NSNS that merges in a Hubble time.
-
+From each simulated instance of the Milky Way we extract the fraction of targets that are detectable, where we define a target as one of BHBH, BHNS or NSNS that merges in a Hubble time.
 To convert the detectable fraction to a detection rate for the Milky Way, we write that the \textit{number} of detectable targets in the Milky Way is
@@
 where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
-The cuts applied to the distributions, mainly because only massive stars are sampled, mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass in the galaxy is sampled from.
+These truncations mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass in the galaxy is sampled from.
 
@@
 \begin{equation}
-    \avg{m}_{\rm SF, today} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.08}^{200} \zeta(m)\ m_{\rm today}(m, \avg{Z}_\tau, \tau) \dd{m} \dd{\tau},
+    \avg{m}_{\rm SF, today} = \int_{0}^{t_{\rm MW}} p_{\rm birth}(\tau) \int_{0.08}^{200} \zeta(m)\ m_{\rm today} \dd{m} \dd{\tau},
 \end{equation}
@@
 We calculate $m_{\rm today}(m, Z, \tau)$ by interpolating the final masses given by COMPAS for a grid of single stars over different masses and metallicities using the \citet{Fryer+2012} delayed prescription and default wind mass loss settings.
-We only use the final mass if more than the main sequence lifetime of the star has passed, otherwise we just use the initial mass.
-Since we don't know the exact metallicity of each star we use the average star forming metallicity in the Milky Way at a lookback time $\tau$ using the birth radius distribution and metallicity equation from \citet{Frankel+2018}.
-If we now evaluate Equation \ref{eq:m_SF_MW}, we find that the total mass of every star that has ever formed in the Milky Way is
-\begin{equation}
-    M_{\rm SF, MW} = (6.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}} = (9.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}},
-\end{equation}
+For $Z$, we use the average star forming metallicity in the Milky Way at a lookback time $\tau$ using our galaxy model.
+Evaluating Equation~\ref{eq:m_SF_MW}, we find that the total mass of every star that has ever formed in the Milky Way is
+\begin{align}
+    M_{\rm SF, MW} &= (6.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}}, \nonumber \\
+    &= (9.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}},
+\end{align}
 an increase of approximately 50\% from the value still in stars today!
@@
 Finally, we can substitute Equations~\ref{eq:norm_avg_target_formation} and \ref{eq:m_SF_MW} into \ref{eq:norm_frame} and write that the overall normalisation of the detection rate is calculated as
-\begin{equation}
-    N_{\rm detect} = f_{\rm detect} \cdot 9.1 \times 10^{10} \unit{M_{\odot}} \cdot \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}
-\end{equation}
+\begin{align}
+    N_{\rm detect} &= f_{\rm detect} \cdot 9.1 \times 10^{10} \unit{M_{\odot}} \nonumber \\
+    &\times \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \nonumber \\
+    &\times \qty(\frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i)^{-1}.
+\end{align}
+
+\subsection{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
+The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries.
+In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of these added features.
+For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.
+
+Their model can be summarised as follows: the Milky Way is assumed to comprise of three components, a thin disc, a thick disc and a bulge.
+The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}.
+\citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
+A major difference is that only two metallicities are used and they are assigned to binaries independent of age or position.
+Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
+
+We show the spatial metallicity distribution for this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
+The two main differences we can see between Fig.~\ref{fig:galaxy_schematic} and \ref{fig:simple_mw} are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
+    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \label{fig:simple_mw}
+\end{figure}
+
+When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
+Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection has increased by nearly a factor of 2.
+
+Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
+(in prep)).
+For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
+Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.
+Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.
+
+The unphysical artifacts present in the mass distributions can have far-reaching effects since the masses of DCOs affect most other parameters.
+The inspiral time and SNR are directly dependent on the mass, whilst the uncertainty estimates depend on the SNR.
+This means that the artifacts can affect the predictions for most distributions of LISA detectable populations.
+
+Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \label{fig:bh_mass_simple_mw}
+\end{figure}
+
+\onecolumngrid
 
@@
 \subsection{Detection rate table}
-\begin{table}[htb]
+\begin{table*}[htb]
     \centering
@@
     \label{tab:detection_rates}
-\end{table}
+\end{table*}
 
 \subsection{Distribution of eccentric sources on sensitivity curve}
-\begin{figure}[hb]
+\begin{figure*}[hb]
     \centering
@@
     \label{fig:dcos_on_sc_ecc_col}
-\end{figure}
+\end{figure*}
 

### 2021-07-19 paper/tex/sections/variations.tex
rearrange appendix to 2col, move mw compare

@@
 I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}
-
-\subsection{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
-The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries.
-In this section, we repeat our main analysis but instead apply a simpler model for the Milky Way in order to assess the effect of these added features.
-For this purpose, we use model for the Milky Way used in \citet{Breivik+2020} as this is representative of the models used in most previous works.
-
-Their model can be summarised as follows: the Milky Way is assumed to comprise of three components, a thin disc, a thick disc and a bulge.
-The spatial distributions and relative masses for these components are given in \citet{McMillan+2011}.
-\citet{Breivik+2020} assume constant star formation over 10 Gyr for the thin disc, a 1 Gyr burst of star formation 11 Gyr ago for the thick disc and a 1 Gyr burst of star formation 10 Gyr ago for the bulge.
-A major difference is that only two metallicities are used and they are assigned to binaries independent of age or position.
-Binaries formed in the thin disc and bulge are assumed to have a metallicity of $Z = 0.02$ and those formed in the thick disc are assumed to have $Z = 0.003$.
-
-We show the spatial metallicity distribution for this model in Fig.~\ref{fig:simple_mw} in the same form as Fig.~\ref{fig:galaxy_schematic} for ease of comparison between our models.
-The two main differences we can see between Fig.~\ref{fig:galaxy_schematic} and \ref{fig:simple_mw} are that the \citet{Breivik+2020} model is more centrally concentrated and only has two fixed metallicity populations.
-%In addition, though it can't be seen in these plots, the simpler prescriptions for the star formation histories mean that the overall star formation history is highly discontinuous at $\tau = 9 \unit{Gyr}$ and significantly more star formation occurs from $\tau = 9 \unit{Gyr}$ to $\tau = 11 \unit{Gyr}$.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
-    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
-    \label{fig:simple_mw}
-\end{figure}
-
-When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
-Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection has increased by nearly a factor of 2.
-
-Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
-(in prep)).
-For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
-Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.
-Moreover, the lack of lower metallicities systems means that higher mass systems are not formed and so we see the distributions do not include a high mass tail such as in our fiducial results.
-
-The unphysical artifacts present in the mass distributions can have far-reaching effects since the masses of DCOs affect most other parameters.
-The inspiral time and SNR are directly dependent on the mass, whilst the uncertainty estimates depend on the SNR.
-This means that the artifacts can affect the predictions for most distributions of LISA detectable populations.
-
-Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
-    \label{fig:bh_mass_simple_mw}
-\end{figure}

### 2021-07-20 paper/tex/sections/appendix.tex
add Milky Way mass calculation

@@
 \begin{equation}\label{eq:m_SF_MW}
-    M_{\rm SF, MW} = 6.08 \pm 1.14 \times 10^{10} \unit{M_{\rm \odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
+    M_{\rm SF, MW} = (6.08 \pm 1.14) \times 10^{10} \unit{M_{\rm \odot}} \cdot \frac{\avg{m}_{\rm SF, total}}{\avg{m}_{\rm SF, today}},
 \end{equation}
@@
 \begin{align}
-    M_{\rm SF, MW} &= (6.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.384 \unit{M_{\odot}}}{0.257 \unit{M_{\odot}}}, \nonumber \\
-    &= (9.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}},
+    M_{\rm SF, MW} &= (6.1 \pm 1.1) \times 10^{10} \unit{M_{\odot}} \cdot \frac{0.378 \unit{M_{\odot}}}{0.221 \unit{M_{\odot}}}, \nonumber \\
+    &= (10.4 \pm 1.1) \times 10^{10} \unit{M_{\odot}},
 \end{align}
-an increase of approximately 50\% from the value still in stars today!
+an increase of approximately 70\% from the value still in stars today!
 

### 2021-07-20 paper/tex/sections/appendix.tex
trim old bits

@@
 \begin{align}
-    N_{\rm detect} &= f_{\rm detect} \cdot 9.1 \times 10^{10} \unit{M_{\odot}} \nonumber \\
+    N_{\rm detect} &= f_{\rm detect} \cdot 10.4 \times 10^{10} \unit{M_{\odot}} \nonumber \\
     &\times \sum_{Z=Z_{\rm min}}^{Z_{\rm max}} p_{Z} \qty(\sum_{i=1}^{N_{\rm binaries, Z}} w_i \theta_{\rm target, i}) \nonumber \\

### 2021-07-20 paper/tex/sections/appendix.tex
make the discussion make sense again

@@
 
-\subsection{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
+\section{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
 The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries.
@@
 
-\begin{figure}[ht]
+\begin{figure}[htb]
     \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[htb]
     \centering
@@
 
+\section{Estimating the number of pulsars for a given sky area in SKA}\label{app:ska_area}
+
+In this section, we perform some back-of-the-envelope calculations in order to estimate the number of pulsars that SKA will observe within a given sky area.
+
+First, we consider how many pulsars SKA is likely to detect.
+\citet{Keane+2015} uses PSRPOPPy \citep{Bates+2014} to simulate the Milky Way pulsar population.
+They find that for SKA-1, approximately $10000$ pulsars will be discovered.
+The second phase of SKA, which should be in operation by the time of the LISA mission, would yield a total of $35000$-$41000$ pulsars \citep{Keane+2015}.
+We use the average, $38000$, in further estimates below.
+Moreover, we are only interested in pulsars that are part of a binary system.
+We estimate this pulsar binary fraction as the fraction of known pulsars that are in binaries using the ATNF Pulsar Catalogue\footnote{\url{https://www.atnf.csiro.au/research/pulsar/psrcat}} \citep{Manchester+2005}.
+$290$ of the $2872$ currently known pulsars are in binary systems and thus we estimate the binary fraction of pulsars as $10\%$.
+Therefore, we expect that SKA-1 and SKA-2 will detect approximately $1000$ and $3800$ binary pulsars respectively.
+
+Next, we can find the total number of pulsars SKA will detect in a patch on the sky.
+The total sky area that the SKA mission covers is approximately $5700 \unit{deg^2}$, which is calculated by integrating over the sky for all Galactic longitudes and Galactic latitudes limited to $\abs{b} < 10^\circ$ and $\delta < 45^\circ$, which are the limits on SKA-mid \citep{Keane+2015}.
+If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.2$ and $0.7$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.
+Note that the assumption of a uniform distribution is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide an upper bound on these estimates.
+
+Overall, we therefore expect a single pulsar per $5.7 \unit{deg^2}$ and $1.5 \unit{deg^2}$ for SKA-1 and SKA-2 respectively, which correspond to angular resolutions of $\sigma_\theta = 1.3^\circ$ and $\sigma_\theta = 0.7^\circ$.
+
+\clearpage
 \onecolumngrid
@@
 
+\clearpage
+
 \subsection{Formation channels}
 
-\begin{figure}
+\begin{figure}[thb]
     \centering
-    \includegraphics[height=0.3\textheight]{formation_channels_BHBH.pdf}
-    \includegraphics[height=0.3\textheight]{formation_channels_BHNS.pdf}
-    \includegraphics[height=0.3\textheight]{formation_channels_NSNS.pdf}
+    \includegraphics[height=0.28\textheight]{formation_channels_BHBH.pdf}
+    \includegraphics[height=0.28\textheight]{formation_channels_BHNS.pdf}
+    \includegraphics[height=0.28\textheight]{formation_channels_NSNS.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.

### 2021-07-20 paper/tex/sections/discussion.tex
make the discussion make sense again

@@
 
-In this section, we perform some back-of-the-envelope calculations in order to estimate how we can use SKA to match pulsars to LISA detections.
-
-First, we consider how many pulsars SKA is likely to detect.
-\citet{Keane+2015} uses PSRPOPPy \citep{Bates+2014} to simulate the Milky Way pulsar population.
-They find that for SKA-1, approximately $10000$ pulsars will be discovered.
-The second phase of SKA, which should be in operation by the time of the LISA mission, would yield a total of $35000$-$41000$ pulsars \citep{Keane+2015}.
-We use the average, $38000$, in further estimates below.
-Moreover, we are only interested in pulsars that are part of a binary system.
-We can estimate this pulsar binary fraction as the fraction of known pulsars that are in binaries using the ATNF Pulsar Catalogue\footnote{\url{https://www.atnf.csiro.au/research/pulsar/psrcat}} \citep{Manchester+2005}.
-$290$ of the $2872$ currently known pulsars are in binary systems and thus we estimate the binary fraction of pulsars as $10\%$.
-
-Next, we can find the total number of pulsars SKA will detect in a patch on the sky.
-The total sky area that the SKA mission covers is approximately $7200 \unit{deg^2}$, which is calculated by integrating over the sky for all Galactic longitudes and Galactic latitudes limited to $\abs{b} < 10^\circ$, which are the limits on SKA-mid \citep{Keane+2015}.
-If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.14$ and $0.49$-$0.57$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.
-Note that the assumption assumption of a uniform distribution is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide an upper bound on these estimates.
-
-Alternatively, we could write that we expect a single pulsar per $7.2 \unit{deg^2}$ and $2.1$-$1.8 \unit{deg^2}$ for SKA-1 and SKA-2 respectively, which corresponds to angular resolutions of $\sigma_\theta = 1.51^\circ$ and $\sigma_\theta = 0.82$-$0.76^\circ$.
+We estimate on average, a LISA DCO localised with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ (for SKA-1 and SKA-2) will never contain more than one pulsar in its sky localisation region (see Appendix~\ref{app:ska_area}).
 Given these estimates, and by considering the last panel of Fig.~\ref{fig:fiducial_pdf_distributions}, approximately $10$ and $6$ (for SKA-1 and SKA-2) DCOs containing NSs will be localised well enough such that, \textit{if} the NS is a pulsar, SKA can unambiguously match it to the radio signal.

### 2021-07-20 paper/tex/sections/appendix.tex
update detection table

@@
     \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type.
-Each value shows the mean and the 90\% confidence interval.}
-    \begin{tabular}{c|lll|lll}
+Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.}
+    \begin{tabular}{cl|lll|lll}
         \hline
-        \multirow{2}{*}{Model} & \multicolumn{3}{c|}{LISA (4 year)} & \multicolumn{3}{c}{LISA (10 year)} \\ \cline{2-7}
-         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
+        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
         \hline
-        A & \confinv{39.6}{6.6}{6.4} & \confinv{36.5}{6.5}{6.5} & \confinv{8.7}{2.7}{3.3} & \confinv{62.9}{7.9}{8.1} & \confinv{60.7}{7.7}{7.3} & \confinv{14.4}{3.4}{3.6}\\
-        B & \confinv{37.1}{6.1}{5.9} & \confinv{17.4}{4.4}{4.6} & \confinv{3.3}{2.3}{1.7} & \confinv{58.7}{7.7}{7.3} & \confinv{28.7}{5.7}{5.3} & \confinv{5.3}{2.3}{2.7}\\
-        C & \confinv{22.4}{4.4}{4.6} & \confinv{5.8}{2.8}{2.2} & \confinv{4.7}{1.7}{2.3} & \confinv{35.8}{5.8}{6.2} & \confinv{9.4}{3.4}{2.6} & \confinv{7.6}{2.6}{2.4}\\
-        D & \confinv{26.2}{5.2}{4.8} & \confinv{4.3}{2.3}{1.7} & \confinv{14.1}{4.1}{3.9} & \confinv{40.5}{6.5}{6.5} & \confinv{7.1}{3.1}{2.9} & \confinv{23.2}{5.2}{4.8}\\
-        E & \confinv{36.9}{5.9}{6.1} & \confinv{4.2}{2.2}{1.8} & \confinv{0.2}{0.2}{0.8} & \confinv{58.6}{7.6}{7.4} & \confinv{6.6}{2.6}{2.4} & \confinv{0.3}{0.3}{0.7}\\
-        F & \confinv{30.2}{5.2}{5.8} & \confinv{22.9}{4.9}{5.1} & \confinv{6.4}{2.4}{2.6} & \confinv{47.5}{6.5}{6.5} & \confinv{35.5}{5.5}{5.5} & \confinv{10.4}{3.4}{3.6}\\
-        G & \confinv{31.8}{5.8}{5.2} & \confinv{25.9}{4.9}{5.1} & \confinv{25.9}{4.9}{5.1} & \confinv{50.5}{7.5}{7.5} & \confinv{43.5}{6.5}{6.5} & \confinv{42.4}{6.4}{6.6}\\
-        H & \confinv{117.8}{10.8}{11.2} & \confinv{51.7}{6.7}{7.3} & \confinv{10.1}{3.1}{2.9} & \confinv{181.6}{13.6}{13.4} & \confinv{87.7}{9.7}{9.3} & \confinv{16.7}{3.7}{4.3}\\
-        I & \confinv{25.5}{5.5}{5.5} & \confinv{62.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{39.1}{6.1}{5.9} & \confinv{102.3}{10.3}{9.7} & \confinv{11.9}{3.9}{3.1}\\
-        J & \confinv{55.5}{7.5}{7.5} & \confinv{27.9}{4.9}{5.1} & \confinv{8.0}{3.0}{3.0} & \confinv{87.8}{9.8}{9.2} & \confinv{45.7}{6.7}{6.3} & \confinv{13.0}{4.0}{4.0}\\
-        K & \confinv{34.8}{5.8}{6.2} & \confinv{42.4}{6.4}{6.6} & \confinv{9.0}{3.0}{3.0} & \confinv{56.0}{8.0}{7.0} & \confinv{69.5}{8.5}{8.5} & \confinv{14.8}{3.8}{4.2}\\
-        L & \confinv{39.8}{6.8}{6.2} & \confinv{36.7}{5.7}{6.3} & \confinv{9.1}{3.1}{2.9} & \confinv{63.4}{8.4}{7.6} & \confinv{61.9}{7.9}{8.1} & \confinv{14.7}{3.7}{3.3}\\
-        M & \confinv{48.2}{7.2}{6.8} & \confinv{80.8}{8.8}{9.2} & \confinv{18.0}{4.0}{4.0} & \confinv{75.3}{8.3}{8.7} & \confinv{134.5}{11.5}{11.5} & \confinv{29.5}{5.5}{5.5}\\
-        N & \confinv{57.5}{7.5}{7.5} & \confinv{138.2}{12.2}{11.8} & \confinv{41.9}{6.9}{6.1} & \confinv{89.5}{9.5}{9.5} & \confinv{227.5}{15.5}{15.5} & \confinv{67.4}{8.4}{8.6}\\
-        O & \confinv{45.7}{6.7}{6.3} & \confinv{85.3}{9.3}{9.7} & \confinv{10.2}{3.2}{2.8} & \confinv{70.9}{8.9}{8.1} & \confinv{141.6}{11.6}{12.4} & \confinv{16.8}{3.8}{4.2}\\
-        P & \confinv{50.8}{6.8}{7.2} & \confinv{32.7}{5.7}{5.3} & \confinv{10.0}{3.0}{3.0} & \confinv{77.6}{8.6}{8.4} & \confinv{53.1}{7.1}{6.9} & \confinv{16.5}{4.5}{4.5}\\
-        Q & \confinv{0.0}{0.0}{0.0} & \confinv{6.7}{2.7}{2.3} & \confinv{8.5}{2.5}{2.5} & \confinv{0.0}{0.0}{0.0} & \confinv{11.3}{3.3}{3.7} & \confinv{13.8}{3.8}{4.2}\\
+        A & Fiducial & \confinv{73.7}{8.7}{8.3} & \confinv{42.1}{6.1}{6.9} & \confinv{7.9}{2.9}{3.1}\\
+        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.6}{8.6}{8.4} & \confinv{22.3}{4.3}{4.7} & \confinv{2.9}{1.9}{2.1}\\
+        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{46.8}{6.8}{7.2} & \confinv{8.2}{3.2}{2.8} & \confinv{3.9}{1.9}{2.1}\\
+        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.8}{6.8}{7.2} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3}\\
+        E & Case BB mass transfer is always unstable & \confinv{69.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{0.2}{0.2}{0.8}\\
+        F & Model E + Model K & \confinv{153.8}{12.8}{12.2} & \confinv{147.8}{11.8}{12.2} & \confinv{18.2}{4.2}{3.8}\\
+        G & CE efficiency $\alpha = 0.1$ & \confinv{27.8}{4.8}{5.2} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8}\\
+        H & CE efficiency $\alpha = 0.5$ & \confinv{61.7}{7.7}{8.3} & \confinv{28.1}{5.1}{4.9} & \confinv{6.2}{2.2}{2.8}\\
+        I & CE efficiency $\alpha = 2.0$ & \confinv{71.6}{8.6}{8.4} & \confinv{38.1}{6.1}{5.9} & \confinv{31.1}{5.1}{5.9}\\
+        J & CE efficiency $\alpha = 10.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
+        K & HG donor stars initiating a CE survive CE & \confinv{154.1}{12.1}{12.9} & \confinv{58.9}{7.9}{8.1} & \confinv{9.6}{2.6}{3.4}\\
+        L & Fryer rapid SN remnant mass prescription & \confinv{50.2}{7.2}{6.8} & \confinv{70.0}{8.0}{8.0} & \confinv{6.6}{2.6}{2.4}\\
+        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{95.9}{9.9}{10.1} & \confinv{30.0}{5.0}{5.0} & \confinv{7.1}{3.1}{2.9}\\
+        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.1}{8.1}{7.9} & \confinv{51.7}{6.7}{7.3} & \confinv{8.2}{3.2}{2.8}\\
+        O & PISN and pulsational-PISN not implemented & \confinv{75.1}{9.1}{8.9} & \confinv{43.2}{6.2}{6.8} & \confinv{7.9}{2.9}{3.1}\\
+        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.4}{9.4}{8.6} & \confinv{86.3}{9.3}{9.7} & \confinv{15.4}{4.4}{3.6}\\
+        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.5}{9.5}{9.5} & \confinv{142.4}{12.4}{11.6} & \confinv{33.4}{5.4}{5.6}\\
+        R & Black holes receive not natal kick & \confinv{85.9}{8.9}{9.1} & \confinv{95.8}{9.8}{10.2} & \confinv{9.7}{2.7}{3.3}\\
+        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.4}{8.4}{8.6} & \confinv{33.9}{5.9}{6.1} & \confinv{8.8}{2.8}{3.2}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{14.9}{3.9}{4.1} & \confinv{9.6}{3.6}{3.4}\\
         \hline

### 2021-07-20 simulation/src/variations.py

@@ -18,35 +18,35 @@ variations = np.array(
             "file": "massTransferEfficiencyFixed_0_25",
             "short": "B",
             "med": r"$\beta=0.25$",
-            "long": r"Mass transfer efficiency fixed $\beta=0.25$",
+            "long": r"Fixed mass transfer efficiency of $\beta=0.25$",
             "colour": plt.get_cmap("tab20b")(15)
         },
         {
             "file": "massTransferEfficiencyFixed_0_5",
             "short": "C",
             "med": r"$\beta=0.5$",
-            "long": r"Mass transfer efficiency fixed $\beta=0.50$",
+            "long": r"Fixed mass transfer efficiency of $\beta=0.5$",
             "colour": plt.get_cmap("tab20b")(14)
         },
         {
             "file": "massTransferEfficiencyFixed_0_75",
             "short": "D",
             "med": r"$\beta=0.75$",
-            "long": r"Mass transfer efficiency fixed $\beta=0.75$",
+            "long": r"Fixed mass transfer efficiency of $\beta=0.75$",
             "colour": plt.get_cmap("tab20b")(13)
         },
         {
             "file": "unstableCaseBB",
             "short": "E",
             "med": "unstable\ncase BB",
-            "long": "Unstable case BB mass transfer",
+            "long": "Case BB mass transfer is always unstable",
             "colour": plt.get_cmap("tab20")(2)
         },
         {
             "file": "unstableCaseBB_opt",
             "short": "F",
             "med": "E+K",
-            "long": "Unstable case BB mass transfer with optimistic CE scenario",
+            "long": "Model E + Model K",
             "colour": plt.get_cmap("tab20")(2)
         },
         {
@@ -81,72 +81,70 @@ variations = np.array(
             "file": "optimistic",
             "short": "K",
             "med": "optimistic\nCE",
-            "long": "Optimistic CE",
+            "long": "HG donor stars initiating a CE survive CE",
             "colour": "darkgoldenrod"
         },
         {
             "file": "rapid",
             "short": "L",
             "med": "rapid SN",
-            "long": "Fryer rapid prescription",
+            "long": "Fryer rapid SN remnant mass prescription",
             "colour": "lightseagreen"
         },
         {
[…]

### 2021-07-21 paper/tex/sections/conclusion.tex
update numbers

@@
     \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with 88\% and 91\% having masses less than $11 \unit{M_\odot}$ respectively.
-Moreover, we find that for LISA detectable DCOs, 35\% of BHBHs and 39\% of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
+    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with $\BHBHmBHBelowEleven{}$ and $\BHNSmBHBelowEleven{}$ having masses less than $11 \unit{M_\odot}$ respectively.
+Moreover, we find that for LISA detectable DCOs, $\BHBHLowerMassGap{}$ of BHBHs and $\BHNSLowerMassGap{}$ of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
 This implies that LISA will be able provide conclusive evidence about the existence of a lower-mass gap.
     \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities when observable by the LISA mission, unlike the more numerous WDWD LISA population.
-We find that 86(20)\% of BHBHs, 46(8)\% of BHNSs and 86(12)\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
+We find that \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
     \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
-Conversely, the BHNS rate varies widely with physics variation, ranging from a mean of 4 to 138.
+Conversely, the BHNS rate varies widely with physics variation, ranging across three orders of magnitude.
 The NSNS shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.

### 2021-07-21 paper/tex/sections/results.tex
update numbers

@@
 \subsubsection{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with $88\%$ and $90\%$ respectively below $11 \unit{M_{\odot}}$.
+For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with $\BHBHmBHBelowEleven{}$ and $\BHNSmBHBelowEleven{}$ respectively below $11 \unit{M_{\odot}}$.
 Unlike ground-based detectors, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
@@
 Since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription (applied in this work) does not produce a mass gap between neutron stars and black holes.
-Indeed we expect $35\%$ and $39\%$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
+Indeed we expect $\BHBHLowerMassGap{}$ and $\BHNSLowerMassGap{}$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
 Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.
@@
 The mass ratio distribution for each DCO type is relatively distinct from the others.
-The majority of NSNSs have a mass ratio close to unity, with 90\% of systems having $q > 0.8$.
+The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
 The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae or from low mass stars.
@@
 
-In contrast, only 9\% of detectable BHBHs are formed with $q > 0.8$ and distribution peaks around $q = 0.4$.
+In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and distribution peaks around $q = 0.4$.
 The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
@@
 An eccentricity of $e = 0.01$ is the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}.
-We find that a significant fraction of DCOs (86\% of BHBHs, 46\% of BHNSs and 86\% of NSNSs) exceed this bound.
+We find that a significant fraction of DCOs ($\BHBHNotCirc{}$ of BHBHs, $\BHNSNotCirc{}$ of BHNSs and $\NSNSNotCirc{}$ of NSNSs) exceed this bound.
 This is in contrast to several previous work that assume all DCOs are circular once they reach the LISA mission \citep[e.g.][]{Lamberts+2018, Sesana+2020}.
-Moreover, we find that 20\%, 8\% and 12\% of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
+Moreover, we find that $\BHBHHighlyEccentric{}$, $\BHNSHighlyEccentric{}$ and $\NSNSHighlyEccentric{}$ of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
 At this eccentricity the majority of the gravitational wave power is emitted in higher harmonics above the orbital frequency and thus the signal would appear at higher frequencies in LISA.
@@
 We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
-We find that approximately 10 BHBHs, 10 BHNSs and 5 NSNSs have measurable chirp masses (as indicated by the shaded region).
+We find that approximately $\BHBHChirpMassMeasureable{}$ BHBHs, $\BHNSChirpMassMeasureable{}$ BHNSs and $\NSNSChirpMassMeasureable{}$ NSNSs have measurable chirp masses (as indicated by the shaded region).
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.

### 2021-07-21 paper/figure_notebooks/uncertainties.py

@@ -5,7 +5,7 @@ import legwork
 
 dco_types = ["BHBH", "BHNS", "NSNS"]
 data_folder = "../../simulation/data/"
-sim_folder = data_folder + "simulation_high_res_double/"
+sim_folder = data_folder + "simulation/"
 
 def get_ecc_uncertainty(t_obs=4*u.yr, source_threshold=7, harmonic_threshold=7, model="fiducial"):
     detectable_harmonics = {"BHBH": None, "BHNS": None, "NSNS": None}

### 2021-07-21 paper/tex/sections/results.tex
add new galaxy plot

@@
 
-\todo{There will also be a little bit more text to explain the example distribution over galaxies in the lower panel -- will make properly once Floor combines the latest fiducial simulation data (this plot is sampling uniformly rather than based on the distribution)}
+In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy.
+We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun.
+Yet we also show that systems are detectable out to the edges of the galaxy and this is especially true for NSNSs.
 
@@
     \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=\columnwidth]{sources_on_mw.png}
+    \includegraphics[width=\columnwidth]{galaxy_density_distribution.png}
     \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
-\textbf{Bottom:} A face-on view of an example Milky Way galaxy, where each point is coloured by its metallicity.
-The large $\odot$ shows the position of the Sun.
-Stars represent a typical example of the detectable systems in a 4-year LISA mission.
-\todo{make proper plot, maybe separate panels for different types (hard to arange then though), thoughts on black background?}}
+\textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs.
+We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights.
+The coloured lines show the 90\% contour for each of the individual DCO types.
+The `x' shows the centre of the galaxy, whilst the $\odot$ shows the position of the Sun.}
     \label{fig:detectable_distance_dist}

### 2021-07-21 paper/tex/sections/results.tex
update galaxy plot and remove old one

@@
 We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun.
-Yet we also show that systems are detectable out to the edges of the galaxy and this is especially true for NSNSs.
+Yet we also show that systems are detectable out to the edges of the galaxy.
+This is especially true for NSNSs, as we highlight by plotting the 75\% contour for the individual DCO types.
 
@@
 We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights.
-The coloured lines show the 90\% contour for each of the individual DCO types.
-The `x' shows the centre of the galaxy, whilst the $\odot$ shows the position of the Sun.}
+The coloured lines show the 75\% contour for each of the individual DCO types.
+The $\odot$ shows the position of the Sun.}
     \label{fig:detectable_distance_dist}

### 2021-07-21 paper/tex/sections/methods.tex
updates to 3.1 and 3.2 from Selma

@@
 
-We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
+We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio (SNR) of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
 The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following \citep[e.g.][]{Finn+2000}

### 2021-07-21 paper/tex/sections/results.tex
updates to 3.1 and 3.2 from Selma

@@
-In this section we present our main results for the detectable LISA DCO population in our fiducial model.
-We find that on average, a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (c.f.\ Table~\ref{tab:detection_rates}).
-We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions} and the measurement uncertainties in Section.~\ref{sec:measurement_uncertainties}.
-
-\subsection{Distribution on the sensitivity curve}\label{sec:dcos_on_sc}
-
+Based on our fiducial simulations, we expect that a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (see Table~\ref{tab:detection_rates} for confidence intervals).
+In this section we discuss the properties of the detectable sources based on our fiducial simulation.
+%We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions} and the measurement uncertainties in Section.~\ref{sec:measurement_uncertainties}.
+\subsection{The LISA sensitivity curve and the population of detectable sources}\label{sec:dcos_on_sc}
 \begin{figure*}[p]
@@
     \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
-    \caption{Density distribution of detectable BHBH, BHNS and NSNS binaries are shown together with the LISA sensitivity curve.
-In the top panel we show all systems with the LISA verification binaries over plotted (star symbols, \citealp{Kupfer+2018}).
-In the bottom panels we separate by type.
+    \caption{The LISA sensitivity curve is shown together with the density distribution of the characteristic strain and the dominant frequency for all detectable sources in our simulations (top) and separated by type (bottom).
 Contours show the percentage of the population enclosed.
 The remaining 2\% of the population is shown as dots with a size that scales with the sampling weight.
-For reference we show lines where a circular binary of average chirp mass $\avg{\mathcal{M}_c}$ would reside for a given remaining inspiral time (vertical lines) and distance (diagonal line).
-To highlight the role of eccentricity we further show the signal expected for an eccentric binary at 30 kpc.
-The coloured line in the bottom panels shows a contour that encloses 90\% of the population that is circular.
-See Sec.~\ref{sec:dcos_on_sc} for a discussion.}
+To guide the interpretation, we show reference lines marking where a circular binary would reside for a given distance (diagonal line) and remaining inspiral time (vertical lines), assuming an average chirp mass $\avg{\mathcal{M}_c}$, orientation and sky location.
+The curved reference line shows the signal expected for an eccentric binary at 30 kpc.
+The coloured lines in the bottom panels show a contour that encloses 90\% of the population that is circular.
+LISA verification binaries are overplotted in the top panel (star symbols).
+See also Fig.~\ref{fig:dcos_on_sc_ecc_col} and Sec.~\ref{sec:dcos_on_sc} for a discussion.}
     \label{fig:dcos_on_sc}
 \end{figure*}
+We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Fig.~\ref{fig:dcos_on_sc} for all sources combined in the top panel and separated by type in the three lower panels.
+For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines), assuming they are circular and the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
+We observe several features worthwhile discussing, some that earlier studies have touched upon (see Sec.~\ref{sec:compare_studies}), as well as some new findings related to eccentricity.
 
-We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Figure~\ref{fig:dcos_on_sc}.
-This shows that the detectable population of these DCOs is concentrated at comparatively lower frequencies than the LISA verification binaries (shown as stars in the top panel).
-This is expected since producing the same SNR as a BHBH, BHNS or NSNS with a relatively lower mass (circular) WDWD requires a higher frequency.
-This finding is in agreement with \citet{Sesana+2020} and as noted in that work, this could possibly be used to distinguish more massive DCOs from WDWDs probabilistically.
-There are several other notable features in these distributions.
-To understand these we overplot reference lines indicating where a circular binary with the average chirp mass ($\avg{\mathcal{M}_c}$, annotated in each panel) would reside for a given remaining inspiral time (vertical lines) and a given distance (diagonal lines).
+Firstly, we note that the detectable population is concentrated on the left side of LISA's sensitivity window.
+The peak is located at a frequency of about $0.4 \unit{mHz}$, which is much lower than the frequency where LISA will be most sensitive (about $10 \unit{mHz}$).
+This can be understood as an evolutionary effect.
+DCOs typically form with wide orbits (low frequencies) that would not be detectable yet.
+Their orbits shrink as they lose angular momentum in the form of gravitational waves leading to an increase of their orbital frequency until they become detectable.
+Even though the signal emitted by a more compact binary is stronger, such systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates.
+The vertical grid lines show these rapidly decreasing inspiral times at increasing frequencies.
+Most of the population is thus expected to reside at low frequencies.
 
-Firstly, we note that the peak of the density distribution coincides with the centre of the Milky Way as expected, since binaries are most likely to be formed towards the centre of the Galaxy.
-Additionally, we expect that if a population is entirely circular, it should be bounded approximately between the $0.1$--$30 \unit{kpc}$ lines, roughly the minimum and maximum distance to a source in the Milky Way.
-From inspection of the bottom panels with each individual DCO type we see that this is the true for a large fraction of the population.
-However, there is a distinct subpopulation of binaries that extend downwards, especially around $2 \unit{mHz}$.
-This offshoot is composed of eccentric binaries for which the circular distance contours do not apply.
-For illustrative purposes, we plot the 90\% contour of only the \textit{circular} sources in our sample over the density distribution in each of the bottom panels and this subsample is indeed bounded by $0.1$--$30 \unit{kpc}$ the distance lines.
-We also plot a line of constant distance at $30 \unit{kpc}$ for an eccentric binary with $e = 0.98$ to show the different limit for eccentric sources.
-To further illustrate this point, we show the same plot but with each point coloured by its eccentricity in Fig.~\ref{fig:dcos_on_sc_ecc_col}.
-Overall, we can see that eccentric sources tend to be located on a slightly different location on the sensitivity curve and so this could perhaps be used help in identifying them.
+We further note that there is an empty band that separates the LISA sensitivity curve and the detectable population.
+This is the direct result of the criteria for detection where we require $\rm{SNR} > 7$.
+For circular systems the SNR is directly given by the height of a system above the curve.
+For eccentric systems this is also approximately true because, though we have plotted them at the frequency of the dominant harmonic, the y-coordinate indicates the signal from \textit{all} harmonics.
 
-We plot vertical lines that give the inspiral time for a circular binary with the average chirp mass (annotated in each panel).
-From these lines we can understand the trend of the density distribution decreasing with increasing frequency.
-Sources with higher frequencies have shorter inspiral times and thus DCOs will spend less time in these regimes, meaning that more sources are detected at lower frequencies.
-Note that these inspiral time lines should only be used as guidelines for the population as a whole, as the inspiral time of each individual source will be a function of its mass and eccentricity.
-It is also evident for each DCO source that the tail of the high frequency sources is more numerous near to the Galactic centre than at short distances.
-This is simply because there are more sources in the galactic centre and so the chances of `catching' a binary at high frequency are better.
+Comparing the lower three panels, one can observe the shift in the frequency at which the peak is located, at $0.3 \unit{mHz}$, $0.7 \unit{mHz}$ and $1 \unit{mHz}$ for BHBH, BHNS and NSNS systems respectively.
+This is a result of the difference in chirp mass.
+A higher mass system can emit at lower frequency and still produce the minimum SNR needed for detection.
+This effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically \citep[e.g.][]{Sesana+2020}.
+In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries (star symbols, \citealt{Kupfer+2018}).
+
+Finally we note that the peak of the density distribution of observable sources coincides with the reference line for circular systems at $8 \unit{kpc}$, as expected since this is the distance to the centre of the Milky Way.
+As can be seen best in the lower panels, the reference lines for $0.1$ and $30 \unit{kpc}$ enclose the majority of systems as expected given the dimensions of our Milky Way.
+There is, however, a distinct subpopulation of binaries that extend downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
+This offshoot is almost uniquely composed of eccentric binaries, as can be seen most clearly in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix.
+This can also be seen in Fig.~\ref{fig:dcos_on_sc} from the contour that encompasses 90\% of the \textit{circular} sources in our population, where systems in the offshoot are missing.
+We also provide a curved reference line that indicates the signal emitted by an eccentric binaries with $e = 0.98$ at a distance of $30 \unit{kpc}$ and average chirp mass.
+We therefore show that eccentric sources are located in a different region on the sensitivity curve.
 
 \subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
+In Figure~\ref{fig:fiducial_pdf_distributions}, we show kernel density estimators of the 1D distribution of the individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+We have applied a simple correction for edge effects due to bounded support by mirroring the sample \citep{Schuster+1985}.
 
-In Figure~\ref{fig:fiducial_pdf_distributions}, we show the distribution of the individual parameters of the population of detectable binaries and discuss the various features in the following sections.
-
-\subsubsection{Orbital Frequency}
-The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
-This is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The BHBH distribution has a tail that extends to $8 \times 10^{-6} \unit{Hz}$, which is comprised of highly eccentric binaries.
-These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics at higher frequencies that are located in the LISA band.
-Similar tails are not as prevalent for BHNSs and NSNSs as they do not have as many eccentric binaries.
+\paragraph{Orbital Frequency} The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
+As already mentioned above, this is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
+The distributions appear nearly symmetric, but closer inspections shows that the left hand side is more populated, which can be seen most clearly in the curve for the BHBHs.
+This is because of the contribution of highly eccentric binaries, which are most abundant in the BHBH population.
+These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics, therefore concentrating it at higher frequencies that are located in the LISA band.
 
@@
 
-\subsubsection{Black Hole Mass}
+\paragraph{Black Hole Mass}
 For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with $\BHBHmBHBelowEleven{}$ and $\BHNSmBHBelowEleven{}$ respectively below $11 \unit{M_{\odot}}$.
@@
 
-\subsubsection{Mass Ratio}
-The mass ratio distribution for each DCO type is relatively distinct from the others.
+\paragraph{Mass Ratio} The mass ratio distribution for each DCO type is relatively distinct from the others.
 The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
@@
 
-\subsubsection{Eccentricity}
-The eccentricity distributions show that detectable BHBHs are most likely to be highly eccentric of the three DCOs.
+\paragraph{Eccentricity} The eccentricity distributions show that detectable BHBHs are most likely to be highly eccentric of the three DCOs.
 This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
@@
 
-\subsubsection{Time since formation}
-The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see Fig.~\ref{fig:galaxy_schematic}).
+\paragraph{Time since formation} The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see Fig.~\ref{fig:galaxy_schematic}).
 In contrast, we find that the \textit{detectable} systems are primarily formed recently, with the majority formed in the past $2 \unit{Gyr}$, in addition to a tail of systems out to earlier times.
@@
 
-\subsubsection{Time until merger}
-The final panel of Fig.~\ref{fig:fiducial_pdf_distributions} shows the remaining time until merger for each of the DCO types at the start of LISA mission.
+\paragraph{Time until merger} The final panel of Fig.~\ref{fig:fiducial_pdf_distributions} shows the remaining time until merger for each of the DCO types at the start of LISA mission.
 The distributions are strikingly similar and peak with merger times of around a Myr.

### 2021-07-22 paper/tex/sections/introduction.tex
changes from Stephen feedback on intro and methods

@@
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
+LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors, such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
 Moreover, this frequency regime is also of interest for the detection of local stellar mass double compact objects (DCO) far in advance of their merger.
 This presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
-In addition, LISA will be able to measure the eccentricities of DCOs that may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
+In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
 Unlike ground-based detectors, LISA only detects stellar mass sources in local galaxies, with the majority residing in the Milky Way.
@@
 
-Galactic NSNSs have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975, Tauris+2017,Vigna-Gomez+2018} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been detected \citep[e.g.][]{Abbott+2017_NSNS}.
+Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.
+\citealp{Hulse+1975}, see also refs.\ in \citealp{Tauris+2017,Vigna-Gomez+2018}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
 The detection of a NSNS in LISA with a pulsar component could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
-NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
+NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
@@
 These observations of X-ray binaries suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which there are no strong candidates for either black holes or neutron stars \citep{Ozel+2010,Farr+2011} but the gap's existence remains an open question \citep[e.g.][]{Kreidberg+2012, Mandel+2020}.
-Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged \citep{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
+Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged (\citealp{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020}, see also \citealp{Liu+2020}) and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
 A sample of BHBHs detected with LISA could possibly help to constrain the stellar mass BH mass distribution.
 
-One particularly interesting class of potential LISA sources are BHNSs.
+One particularly interesting class of potential LISA sources is BHNSs.
 With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.
@@
 A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
-These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which will help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
+These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
 
-For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through common envelope ejection or a phase of highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
+For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which double compact objects are formed following common envelope ejection or a phase of highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
 We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.
@@
 In this paper, we present predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
-We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.
+We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the prospects for distinguishing DCO detections from the WDWD background.
 
@@
 We explore the effect of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effect on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that accounts for the chemical enrichment history and calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
+We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind to date and make use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.
+Moreover, our binary population synthesis simulation is the most extensive of its kind to date and makes use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.
 Overall we simulate over 2 billion massive binaries to produce the DCO populations used in this work.
@@
 In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
-We present our main results in Section~\ref{sec:results}, analysing our findings for each DCO type and variation of physical assumptions.
+We present the main results for our fiducial model in Section~\ref{sec:results}, before exploring the variations in the detectable population when changing our physical assumptions in Section~\ref{sec:variations}.
 In Section~\ref{sec:discussion} we discuss these results.

### 2021-07-22 paper/tex/sections/methods.tex
changes from Stephen feedback on intro and methods

@@
 To produce predictions for the DCOs that are detectable with LISA, we synthesise a population of DCOs using the population synthesis methods described in Section~\ref{sec:COMPAS_explained}.
-In order to obtain value for the uncertainty on the expected detection rates, we place this sample of DCOS in many different Monte Carlo sampled instances of the Milky Way, the model for which is described in Section~\ref{sec:galaxy_synthesis}.
+In order to obtain values for the uncertainty on the expected detection rates, we place this sample of DCOS in many different Monte Carlo sampled instances of the Milky Way, the model for which is described in Section~\ref{sec:galaxy_synthesis}.
 We evolve the orbit of each DCO in a Milky Way instance up to the LISA mission and calculate the detection rate for that instance using the methods presented in Section~\ref{sec:gw_detection}.
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger, $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
 We sample from these sets of parameters when creating synthetic galaxies.
@@
 
-Our model for the Milky Way accounts for the low-\achem\footnote{nomenclature used to describe the enhancement of $\alpha$ elements compared to iron in stellar atmospheres}~disc, high-\achem~disc and a central component approximating a bar/bulge.
+Our model for the Milky Way accounts for the low-\achem\footnote{Nomenclature used to describe the enhancement of $\alpha$ elements compared to iron in stellar atmospheres}~disc, high-\achem~disc and a central component approximating a bar/bulge.
 The low- and high-\achem~discs are often also referred to as the thin and thick discs because the stellar vertical distribution is better fit by a double exponential rather than a single one.
-However, it doesn't allow one to assign a star to either the thin or thick disk purely based on its height above the Galactic plane.
-Therefore, we use the chemical definition of the two disks with the \achem~nomenclature because there is a clear bimodal distribution in the chemical plane, allowing stars to be easily assigned to each of the disc components based on its chemical abundances.
+However, this doesn't allow one to assign a star to either the thin or thick disk purely based on its height above the Galactic plane.
+Therefore, we use the chemical definition of the two disks with the \achem~nomenclature because there is a clear bimodal distribution in the chemical plane, allowing stars to be assigned to each of the disc components based on their chemical abundances.
 For each of the three components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
@@
 \citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-\achem~discs, the Milky Way abundance distributions could be well reproduced.
-Empirically, the chemical tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
+Empirically, the abundance tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
 

### 2021-07-22 paper/tex/sections/discussion.tex
add 2 new caveats

@@
 \subsection{Caveats}\label{sec:caveats}
+\textit{Binary fraction and other normalisation choices}: For the normalisation of the detection rate we conservatively chose to set the binary fraction of all stars to 50\%.
+The binary fraction is uncertain and not well constrained, though we know it is higher for more massive stars \citep[e.g.][]{Sana+2012}.
+However, the choice of the binary fraction has a strong effect on our results.
+Increasing it to 70\% and 100\% would increase our expected detection rates for every physics variation by 30\% and 67\% respectively.
+We assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results.
+We highlight the uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change drastically as our understanding shifts, however changes to this normalisation would affect every variation equally and so the trends across variations are more robust.
+
 \textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
@@
 A more detailed set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
+
+\textit{Large progenitor masses:} Due to the high metallicity population within the Milky Way, many of the black holes that are formed in our sample come from progenitors with large initial masses.
+39\% of BHBHs contain a BH with a progenitor mass in excess of $100 \unit{M_\odot}$, as do $13\%$ of BHNSs.
+The fitting formulae upon with COMPAS is based need to be extrapolated for stars of this mass and so their true evolution may not follow the results of population synthesis.
 

### 2021-07-22 paper/tex/sections/appendix.tex
fix odot typos
update comparisons, simple mw, add Shao+2021

@@
         \modRapid & Fryer rapid SN remnant mass prescription \\
-        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm odot}}$ \\
-        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm odot}}$ \\
+        \modNSLow & Maximum NS mass is fixed to $2\unit{M_{\rm \odot}}$ \\
+        \modNSHigh & Maximum NS mass is fixed to $3\unit{M_{\rm \odot}}$ \\
         \modNoPISN & PISN and pulsational-PISN not implemented \\
@@
 
-When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $39$, $39$ and $14$ respectively.
-Thus the BHBH and BHNS detection rates are only marginally increased from our main findings, but the NSNS detection has increased by nearly a factor of 2.
+When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $52$, $22$ and $11$ respectively.
+Thus the BHBH and BHNS detection rates are decreased from our main findings, but the NSNS detection has marginally increased.
 
@@
 
-Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly overestimate the LISA NSNS detection rate as well as contain unphysical artifacts in their parameter distributions.
+Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly underestimate the LISA BHBH and BHNS rates whilst overestimating the NSNS detection rate and may also contain unphysical artifacts in their parameter distributions.
 

### 2021-07-22 paper/tex/sections/comparisons.tex
update comparisons, simple mw, add Shao+2021

--- 2021-07-08 paper/tex/sections/comparisons.tex
@@
     \caption{A table comparing previous studies of a similar nature to this work.
-The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020} and \citet{Breivik+2020}.}
+The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.}
     \label{fig:previous_studies}
@@
 Unlike our work, \citet{Sesana+2020} assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-This is especially relevant as we find that around 50\% of LISA detectable BHBHs are not circular and around 10\% have significant eccentricity.
+This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
 We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Section~\ref{sec:mw_changes}).
@@
 However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences.
+It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could have affected the formation rate of NSNSs.
 %
-We therefore surmise that the remaining difference between our results is likely due to way in which we simulate the Milky Way.
-\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Section~\ref{sec:mw_changes}.
+It is also possible that the remaining difference between our results is due to way in which we simulate the Milky Way.
+\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}.
 We find that this simpler model for the Milky Way could result in an overestimate of the NSNS detection rate and so this may explain the discrepancy between our results.
-\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger.
-
-%\citet{Lau+2020} assumes constant star formation, solar metallicity and distributes binaries without any considerations of the chemical enrichment history of the Milky Way, whilst we use the distributions from \citet{Frankel+2018} for the star formation rate, metallicity and positions.
-The \citet{Frankel+2018} star formation rate decreases over time and the metallicity distribution peaks above solar metallicity, both changes that could decrease the NSNS detection rate given that we find most NSNS binaries in our sample have short inspiral times compared to the age of the Milky Way and higher metallicity would lead to increased stellar winds and hence less massive DCOs.
+\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger as their results will have no contribution from lower metallicity systems.
 
@@
 They find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-They make many different physical assumptions, the most notable being that \citet{Breivik+2020} assumes the optimistic CE scenario.
-Thus it would be more prudent to compare to our results from model \modOpt{} in which we find 118, 52 and 7 detections respectively.
-Thus the NSNS rate is consistent but we find higher rates for the BHBHs and BHNSs.
+They make many different physical assumptions, the most notable being that \citet{Breivik+2020} assume the optimistic CE scenario and that case BB mass transfer is always unstable.
+Thus it would be more prudent to compare to our results from model \modCaseBBOpt{} in which we find 154, 148 and 18 detections respectively.
+\todo{I am in the process of running some sims using Katie's MW model to compare more easily, will update soon}%Thus the NSNS rate is consistent but we find higher rates for the BHBHs and BHNSs.
 These differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
+
+\paragraph{\citet{Shao+2021}} most recently investigated the detectability binaries containing BHs in LISA using BSE and a relatively simple model for the Milky Way (assuming a uniform flat disc, constant star formation and a single metallicity).
+They assume that kicks for NSs formed through ECSN are slightly higher than our work ($50 \unit{km}{s^{-1}}$ instead of $30 \unit{km}{s^{-1}}$).
+This may account for their particular low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
+It is however difficult to compare further due to our vastly different assumptions about the Milky Way, particularly their assumption of only solar metallicity which eliminates any contribution from low metallicity systems.

### 2021-07-22 simulation/slurm/generate_scripts.py
add some simple mw scripts

@@ -4,18 +4,18 @@ from variations import variations
 
 
 def create_file(dco_type, file, simple_mw=False):
-    script_file = "scripts/{}_{}.sh".format(dco_type, file)
+    script_file = "scripts/{}_{}{}.sh".format(dco_type, file, "_simplemw" if simple_mw else "")
 
     lines = []
     lines.append("#!/bin/bash\n")
-    lines.append("#SBATCH -J {}_{}\n".format(dco_type, file))
+    lines.append("#SBATCH -J {}_{}{}\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
     lines.append("#SBATCH -n 6\n")
     lines.append("#SBATCH -N 1\n")
     lines.append("#SBATCH -p serial_requeue\n")
     lines.append("#SBATCH --mem 6000\n")
     lines.append("#SBATCH -t 00-10:00\n")
-    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.out\n".format(dco_type, file))
-    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}_%A_%a.err\n".format(dco_type, file))
+    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.out\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
+    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.err\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
     lines.append("#SBATCH --mail-user thomas.wagg@cfa.harvard.edu\n")
     lines.append("#SBATCH --mail-type ALL\n")
 
@@ -23,13 +23,13 @@ def create_file(dco_type, file, simple_mw=False):
     lines.append("source activate lisa\n")
 
[…]

### 2021-07-22 simulation/src/variations.py
update colormap of variations

@@ -40,7 +40,7 @@ variations = np.array(
             "short": "E",
             "med": "unstable\ncase BB",
             "long": "Case BB mass transfer is always unstable",
-            "colour": plt.get_cmap("tab20")(2)
+            "colour": plt.get_cmap("tab20")(3)
         },
         {
             "file": "unstableCaseBB_opt",
@@ -61,28 +61,28 @@ variations = np.array(
             "short": "H",
             "med": r"$\alpha_{\rm CE}=0.5$",
             "long": r"CE efficiency $\alpha = 0.5$",
-            "colour": plt.get_cmap("tab20b")(11)
+            "colour": plt.get_cmap("tab20b")(10)
         },
         {
             "file": "alpha2_0",
             "short": "I",
             "med": r"$\alpha_{\rm CE}=2.0$",
             "long": r"CE efficiency $\alpha = 2.0$",
-            "colour": plt.get_cmap("tab20b")(10)
+            "colour": plt.get_cmap("tab20b")(9)
         },
         {
             "file": "alpha10",
             "short": "J",
             "med": r"$\alpha_{\rm CE}=10.0$",
             "long": r"CE efficiency $\alpha = 10.0$",
-            "colour": plt.get_cmap("tab20b")(10)
+            "colour": plt.get_cmap("tab20b")(8)
         },
         {
             "file": "optimistic",
             "short": "K",
             "med": "optimistic\nCE",
             "long": "HG donor stars initiating a CE survive CE",
-            "colour": "darkgoldenrod"
+            "colour": plt.get_cmap("tab20")(11)
         },
         {
             "file": "rapid",

### 2021-07-22 paper/tex/sections/results.tex
update comparisons, simple mw, add Shao+2021
create new detection rate plot

@@
 Indeed we expect $\BHBHLowerMassGap{}$ and $\BHNSLowerMassGap{}$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
+During the preparation of this paper \citet{Shao+2021} also noted this, claiming that $30\%$ and $70\%$ of merging BHBHs and BHNSs respectively have BHs in the lower mass gap (when using the delayed remnant mass prescription).
 Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.
@@
 \textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs.
-We only show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their STROOPWAFEL weights.
+We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights.
 The coloured lines show the 75\% contour for each of the individual DCO types.
-The $\odot$ shows the position of the Sun.}
+The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
     \label{fig:detectable_distance_dist}

### 2021-07-23 paper/tex/sections/appendix.tex
update simple mw comparison (again hehe)

@@
 
-When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $52$, $22$ and $11$ respectively.
-Thus the BHBH and BHNS detection rates are decreased from our main findings, but the NSNS detection has marginally increased.
+When applying this simpler Milky Way model in combination with our fiducial binary physics assumptions (model \modFid{}), we find that the expected number of detections for BHBHs, BHNSs and NSNSs for a 4-year LISA mission is $52$, $25$ and $17$ respectively.
+Thus the BHBH detection has decreased slightly compared to our main findings, whilst for BHNSs and NSNSs the rate has approximately halved and doubled respectively.
 
@@
 
-Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly underestimate the LISA BHBH and BHNS rates whilst overestimating the NSNS detection rate and may also contain unphysical artifacts in their parameter distributions.
+Overall, we find that previous studies that use Milky Way models analogous to this simpler model may significantly underestimate the LISA BHNS rate whilst overestimating the NSNS detection rate.
+They may also miss higher mass systems (particular for BHNSs) and contain unphysical artifacts in their parameter distributions.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/BH_mass_dist_simple_mw.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \includegraphics[width=\columnwidth]{../figures/mBH_simple_mw_variation.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.
+Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.}
     \label{fig:bh_mass_simple_mw}

### 2021-07-23 paper/tex/sections/comparisons.tex
update comparisons based on new info on simple mw

@@
 However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences.
-It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could have affected the formation rate of NSNSs.
+It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
 %
-It is also possible that the remaining difference between our results is due to way in which we simulate the Milky Way.
+It is most likely the remaining difference between our results is due to way in which we simulate the Milky Way.
 \citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}.
-We find that this simpler model for the Milky Way could result in an overestimate of the NSNS detection rate and so this may explain the discrepancy between our results.
+We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results.
 \citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger as their results will have no contribution from lower metallicity systems.
@@
 \paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
-They find that LISA will detect 93 BHBH, 33 BHNS and 8 NSNS binaries in the Milky Way over a 4 year mission.
-They make many different physical assumptions, the most notable being that \citet{Breivik+2020} assume the optimistic CE scenario and that case BB mass transfer is always unstable.
-Thus it would be more prudent to compare to our results from model \modCaseBBOpt{} in which we find 154, 148 and 18 detections respectively.
-\todo{I am in the process of running some sims using Katie's MW model to compare more easily, will update soon}%Thus the NSNS rate is consistent but we find higher rates for the BHBHs and BHNSs.
-These differences are likely due to using a different population synthesis code (COSMIC) and using a different model for the Milky Way, particularly the assumptions of two fixed metallicities.
+They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
+\citet{Breivik+2020} make many different physical assumptions, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{sec:mw_changes}).
+Thus for better comparison we ran our simulation using model \modCaseBBOpt{} and the Milky Way model from \citet{Breivik+2020}.
+This results in 97, 101 and 43 detections for BHBHs, BHNSs and NSNSs respectively.
+Therefore, though we are in very good agreement for BHBHs, we predict much higher rates for BHNSs and NSNSs.
+These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS.
+It is possible that the two codes handle NSs differently given our strong agreement for BHBHs.
 
@@
 They assume that kicks for NSs formed through ECSN are slightly higher than our work ($50 \unit{km}{s^{-1}}$ instead of $30 \unit{km}{s^{-1}}$).
-This may account for their particular low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
-It is however difficult to compare further due to our vastly different assumptions about the Milky Way, particularly their assumption of only solar metallicity which eliminates any contribution from low metallicity systems.
+This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
+As we show in Appendix~\ref{sec:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an overestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.

### 2021-07-23 paper/tex/sections/comparisons.tex
typo fixes now that I am more awake

@@
 However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences.
-It is also important to highlight that COMPAS has had many improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
+It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
 %
-It is most likely the remaining difference between our results is due to way in which we simulate the Milky Way.
+Yet it is most likely that the remaining difference between our results is due to way in which we simulate the Milky Way.
 \citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}.
@@
 They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
-\citet{Breivik+2020} make many different physical assumptions, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{sec:mw_changes}).
+\citet{Breivik+2020} make many different physical assumptions from us, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{sec:mw_changes}).
 Thus for better comparison we ran our simulation using model \modCaseBBOpt{} and the Milky Way model from \citet{Breivik+2020}.
@@
 These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS.
-It is possible that the two codes handle NSs differently given our strong agreement for BHBHs.
+Given our strong agreement for BHBHs, it is possible that COSMIC and COMPAS handle NSs differently and thus lead to different detection rates for DCOs containing NSs.
+However checking this would require a more in-depth study of the intrinsic formation rate of DCOs containing NSs in the two codes.
 
@@
 This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
-As we show in Appendix~\ref{sec:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an overestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.
+As we show in Appendix~\ref{sec:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.

### 2021-07-23 paper/tex/sections/conclusion.tex
ensure all stats are up to date

@@
     \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with $\BHBHmBHBelowEleven{}$ and $\BHNSmBHBelowEleven{}$ having masses less than $11 \unit{M_\odot}$ respectively.
+    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with 90\% having BH masses less than $11 \unit{M_\odot}$.
 Moreover, we find that for LISA detectable DCOs, $\BHBHLowerMassGap{}$ of BHBHs and $\BHNSLowerMassGap{}$ of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
@@
     \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission, we estimate that of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
-Additionally, we predict that we will be able to determine whether \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) NSNSs are signals from a binary that contains a black hole.
+Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole.
     \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.

### 2021-07-23 paper/tex/sections/discussion.tex
ensure all stats are up to date

@@
 The simplest way to check whether a source is a WDWD is to check its chirp mass.
-The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.44 \unit{M_\odot}$ \citep{Chandrasekhar+1931}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.25 \unit{M_{\odot}}$.
-Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.25 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
-We find that for the detectable population of a 4(10)-year LISA mission, 17(23)\% of BHBHs, 20(24)\% of BHNSs and 2.4(2.5)\% of NSNSs satisfy this condition.
+The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$.
+Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
+We find that for the detectable population of a 4(10)-year LISA mission, \BHBHAboveMaxWDWDFourPerc{}(\BHBHAboveMaxWDWDTenPerc{})\% of BHBHs, \BHNSAboveMaxWDWDFourPerc{}(\BHNSAboveMaxWDWDTenPerc{})\% of BHNSs and \NSNSAboveMaxWDWDFourPerc{}(\NSNSAboveMaxWDWDTenPerc{})\% of NSNSs satisfy this condition.
 This method is not particularly effective for NSNSs since their average chirp mass, $1.17 \unit{M_\odot}$, is below the Chandrasekhar limit.
@@
 Therefore, if any system is detected with anything other than one detectable harmonic, this implies that the system is unlikely to be a WDWD.
-We find that for a 4(10)-year LISA mission, 55(61)\% of BHBHs, 27(28)\% of BHNSs and 65(69)\% of NSNSs are detected with multiple harmonics.
+We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics.
 Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.
@@
 This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc.
-We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are 40(32)\% for BHBHs, 24(19)\% for BHNSs and 59(51)\% for NSNSs\footnote{Note that although the fractions are smaller for the 10 year mission, the \textit{absolute} number of detections is still greater.
-The fraction decreases because a 10 year mission detects more `marginal' sources that are just on the cusp of the detection threshold and these sources have the worst sky localisation and thus cannot be confirmed to lie within the Galactic plane.}.
+We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs.
+Note that although the fractions are smaller for the 10-year mission, the \textit{absolute} number of detections is still greater.
+The fraction decreases because a 10-year mission detects more `marginal' sources that are just on the cusp of the detection threshold and these sources have the worst sky localisation and thus cannot be confirmed to lie within the Galactic plane.
 
@@
 Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
-For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit by more than $2 \Delta \mathcal{M}_c$ is 15(20)\% for BHBHs, 12(14)\% for BHNSs and 34(40)\% of NSNSs, which in terms of absolute detections is \BHBHDistinguishedFour{}(\BHBHDistinguishedTen{}) for BHBHs, \BHNSDistinguishedFour{}(\BHNSDistinguishedTen{}) for BHNSs and \NSNSDistinguishedFour{}(\NSNSDistinguishedTen{}) for NSNSs.
+For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit (and thus \textit{must} contain or not contain a BH component respectively) by more than $2 \Delta \mathcal{M}_c$ is \BHBHEitherBHOrNSFourPerc{}(\BHBHEitherBHOrNSTenPerc{})\% for BHBHs, \BHNSEitherBHOrNSFourPerc{}(\BHNSEitherBHOrNSTenPerc{})\% for BHNSs and \NSNSEitherBHOrNSFourPerc{}(\NSNSEitherBHOrNSTenPerc{})\% of NSNSs, which in terms of absolute detections is \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) for BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) for BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) for NSNSs.
 

### 2021-07-23 paper/tex/sections/results.tex
ensure all stats are up to date

@@
 \paragraph{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with $\BHBHmBHBelowEleven{}$ and $\BHNSmBHBelowEleven{}$ respectively below $11 \unit{M_{\odot}}$.
+For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with about $90\%$ of BHs below $11 \unit{M_{\odot}}$.
 Unlike ground-based detectors, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.

### 2021-07-23 paper/tex/sections/appendix.tex
round 2 of feedback from Stephen

@@
 
-\section{Assessing the impact of Milky Way model choices}\label{sec:mw_changes}
+\section{Assessing the impact of Milky Way model choices}\label{app:mw_changes}
 The model that we use for the Milky Way adds several layers of complexity, accounting for the inside-out growth of the thin disc, using empirically informed star formation histories that are a function of time and assigning metallicities based on the position and age of binaries.

### 2021-07-23 paper/tex/sections/comparisons.tex
round 2 of feedback from Stephen

@@
 This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
-We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Section~\ref{sec:mw_changes}).
+We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Appendix~\ref{app:mw_changes}).
 Finally, it could be that different implicit assumptions in their population synthesis code lead to differences in our results \citep{Toonen+2014}.
@@
 Yet it is most likely that the remaining difference between our results is due to way in which we simulate the Milky Way.
-\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{sec:mw_changes}.
+\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{app:mw_changes}.
 We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results.
@@
 They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
-\citet{Breivik+2020} make many different physical assumptions from us, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{sec:mw_changes}).
+\citet{Breivik+2020} make many different physical assumptions from us, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{app:mw_changes}).
 Thus for better comparison we ran our simulation using model \modCaseBBOpt{} and the Milky Way model from \citet{Breivik+2020}.
@@
 This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
-As we show in Appendix~\ref{sec:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.
+As we show in Appendix~\ref{app:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.

### 2021-07-23 paper/tex/sections/discussion.tex
round 2 of feedback from Stephen

@@
 
-Another discriminator between WDWDs and other DCOs is the eccentricity.
+Another discriminator between WDWDs and other DCOs is eccentricity.
 WDWDs formed in the disc are thought to be formed through isolated binary formation and have little to no eccentricity \citep[e.g.][]{Nelemans+2001}.
-Therefore, if any system is detected with anything other than one detectable harmonic, this implies that the system is unlikely to be a WDWD.
+Therefore, if any system is detected with anything other than one detectable harmonic, this suggests that the system is unlikely to be a WDWD.
 We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics.
-Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.
-\ref{sec:fiducial_distributions}).
+Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.~\ref{sec:fiducial_distributions}).
 
@@
 
-For separating the BHBH and BHNS population one could consider the range of mass ratios that could result in the chirp mass and assume that those that are likely close to unity must be BHBHs.
+For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency, mass ratio and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+This method would pose a challenge however as it would likely only rule out some DCO types as the source of the signal rather than provide strong evidence of the exact type.
+
 Another possible solution would be the existence of electromagnetic counterparts to the gravitational wave signal.
@@
 This could be used to identify the type of the source, however it is unlikely that a large fraction of the population will contain pulsars that are beaming towards the Earth.
-
-One could also consider using the eccentricity or orbital frequency to separate the populations since the distributions are different for each DCO type (see Fig.~\ref{fig:fiducial_pdf_distributions}).
-This method would also pose a challenge as it would likely only rule out some DCO types as the source of the signal rather than provide strong evidence of the exact type.
 
@@
 The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
-A pulsar(PSR)+BH can be provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
+A pulsar(PSR)+BH can provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
 Alternatively, an ultrarelativstic PSR+NS system could be used to measure the neutron star equation of state up to an order of magnitude more accurately than other proposed observational constraints \citep{Kyutoku+2019, Thrane+2020}.
 
-We estimate on average, a LISA DCO localised with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ (for SKA-1 and SKA-2) will never contain more than one pulsar in its sky localisation region (see Appendix~\ref{app:ska_area}).
-Given these estimates, and by considering the last panel of Fig.~\ref{fig:fiducial_pdf_distributions}, approximately $10$ and $6$ (for SKA-1 and SKA-2) DCOs containing NSs will be localised well enough such that, \textit{if} the NS is a pulsar, SKA can unambiguously match it to the radio signal.
+We estimate on average, given the number of detectable pulsars and SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
+Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA.
+By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) will satisfy this constraint.
 
@@
 Both SKA and LISA will measure the orbital frequency to high precision, as well as the time derivative of the frequency and chirp mass to a lesser precision, of each of these systems.
-Therefore, one could perform a targetted search with SKA that checks the sky location given by LISA and only looking for binary pulsars with orbital frequencies within the errors.
+Therefore, one could perform a targeted search with SKA that checks the sky location given by LISA and only looking for binary pulsars with orbital frequencies within the uncertainties.
 If there was \textit{still} more than one possible pulsar one could also check against the chirp mass.
-In this way, it will be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
+In this way, we expect it will be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
 
@@
 \textit{Underlying helium star models:} One major weakness is that the \citet{Hurley+2000} fitting formulae for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
-A more detailed set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
+A more comprehensive set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
 
@@
 \textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ and should not be extrapolated outside this region.
-However, in the Milky Way (based on the metallicity relation in \citet{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
+However, in the Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
 Therefore, for our study we had to reassign any metallicities outside of COMPAS' range.
@@
 Similarly, DCO formation is less efficient at high metallicity \citep[e.g.][]{Broekgaarden+2021} and so exploring metallicities above the COMPAS maximum is unlikely to contribute significantly to the observed rate.
-Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins (since using a single bin for many binaries leads to unphysical artifacts).
+Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
 
@@
 This would require integrating the orbital evolution of the millions of binaries in our sample and thus was not computationally reasonable to include.
-We investigated the effect of kicks for a small grid of binaries and found that though they would result in a more spread out distribution within the galaxy (with a smaller concentration in the galaxy centre), the overall distribution of positions would be relatively unchanged and very few sources have strong enough kicks to reach escape velocity for the Milky Way.
+We investigated the effect of kicks for a small grid of binaries and found that, though they would result in a more spread out distribution (with a smaller concentration in the Galactic centre) and larger heights above the plane, the overall distribution of positions would be relatively unchanged and very few sources have strong enough kicks to reach escape velocity for the Milky Way.
 
@@
 In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data.
-For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as the same source.
+For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as originating from the same source.
 This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold.
@@
 Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty.
-However, it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary and so have extremely small chirps.
+However, it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary in frequency.
 Secondly, it would improve our ability to distinguish between WDWDs and higher mass DCOs.

### 2021-07-25 simulation/src/galaxy.py
change code nomenclature

@@ -7,8 +7,8 @@ from scipy.stats import beta
 __all__ = ["simulate_mw"]
 
 
-def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr, tsfr=6.8*u.Gyr):
-    """Inverse CDF sampling of lookback times. Thin and thick discs uses Frankel+2018 Eq.4,
+def draw_lookback_times(size, component="low_alpha_disc", tm=12*u.Gyr, tsfr=6.8*u.Gyr):
+    """Inverse CDF sampling of lookback times. low_alpha and high_alpha discs uses Frankel+2018 Eq.4,
     separated at 8 Gyr. The bulge matches the distribution in Fig.7 of Bovy+19 but accounts for sample's bias.
 
     Parameters
@@ -27,11 +27,11 @@ def draw_lookback_times(size, component="thin_disc", tm=12*u.Gyr, tsfr=6.8*u.Gyr
     tau: `float/array`
         Random lookback times
     """
-    if component == "thin_disc":
+    if component == "low_alpha_disc":
         U = np.random.rand(size)
         norm = 1 / quad(lambda x: np.exp(-(tm.value - x) / tsfr.value), 0, 8)[0]
         tau = tsfr * np.log((U * np.exp(tm / tsfr)) / (norm * tsfr.value) + 1)
-    elif component == "thick_disc":
+    elif component == "high_alpha_disc":
         U = np.random.rand(size)
         norm = 1 / quad(lambda x: np.exp(-(tm.value - x) / tsfr.value), 8, 12)[0]
         tau = tsfr * np.log((U * np.exp(tm / tsfr)) / (norm * tsfr.value) + np.exp(8 * u.Gyr / tsfr))
@@ -139,7 +139,7 @@ def distance_from_earth(R, z, theta, Rsun=8.2*u.kpc):
     return D
 
 
-def simulate_mw(n_binaries, components=["thin_disc", "thick_disc", "bulge"],
+def simulate_mw(n_binaries, components=["low_alpha_disc", "high_alpha_disc", "bulge"],
                 masses=[2.585e10, 2.585e10, 0.91e10]*u.Msun, tm=12 * u.Gyr, tsfr=6.8 * u.Gyr, alpha=0.3,
                 Fm=-1, gradient=-0.075 / u.kpc, Rnow=8.7 * u.kpc, gamma=0.3, zsun=0.0142, Rsun=8.2 * u.kpc,
                 ret_pos=False, lookback=True):
[…]

### 2021-07-25 simulation/src/galaxy.py
make code keep track of which component

@@ -198,7 +198,7 @@ def simulate_mw(n_binaries, components=["low_alpha_disc", "high_alpha_disc", "bu
         sizes[i] = np.round(mass_fractions[i] * n_binaries)
     sizes[-1] = n_binaries - np.sum(sizes)
 
-    components = ["low_alpha"]
+    which_comp = np.concatenate([[components[i]] * sizes[i] for i in range(len(components))])
 
     tau = [None for i in range(len(components))]
     R = [None for i in range(len(components))]
@@ -240,7 +240,7 @@ def simulate_mw(n_binaries, components=["low_alpha_disc", "high_alpha_disc", "bu
 
     # return positions as well as rest if requested
     if ret_pos:
-        return tau, D, Z, (R, z, theta)
+        return tau, D, Z, (R, z, theta), which_comp
     else:
         return tau, D, Z
 
@@ -257,6 +257,9 @@ def simulate_simple_mw(n_binaries, ret_pos=False):
     m_tot = np.sum(masses)
     totals = np.array([int((masses[i] / m_tot * n_binaries).round(0)) for i in range(len(masses))])
     totals[-1] = n_binaries - np.sum(totals[:-1])
+
+    components = ["bulge", "thin_disc", "thick_disc"]
+    which_comp = np.concatenate([[components[i]] * totals[i] for i in range(len(components))])
 
     tau = np.zeros(n_binaries) * u.Gyr
     radius = np.zeros(n_binaries) * u.kpc
@@ -312,6 +315,6 @@ def simulate_simple_mw(n_binaries, ret_pos=False):
     dist = distance_from_earth(radius, height, theta)
 
     if ret_pos:
-        return tau, dist, Z, (radius, height, theta)
+        return tau, dist, Z, (radius, height, theta), which_comp
     else:
         return tau, dist, Z

### 2021-07-25 simulation/src/simulate_DCO_detections.py

@@ -102,8 +102,8 @@ def main():
     dt = np.dtype(float)
     dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
              ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
-             ("tau", dt), ("Z", dt), ("R", dt), ("z", dt), ("theta", dt), ("snr", dt), ("weight", dt),
-             ("seed", dt)]
+             ("tau", dt), ("Z", dt), ("R", dt), ("z", dt), ("theta", dt), ("component", np.dtype(str)),
+             ("snr", dt), ("weight", dt), ("seed", dt)]
     to_file = np.zeros(shape=(loops * MAX_HIGH,), dtype=dtype)
 
     n_detect_list = np.zeros(loops)
@@ -112,10 +112,16 @@ def main():
     for milky_way in range(loops):
         if not use_simple_mw:
             # draw parameters from Frankel Model
-            tau, dist, Z_unbinned, pos = simulate_mw(MW_SIZE, ret_pos=True)
+            tau, dist, Z_unbinned, pos, component = simulate_mw(MW_SIZE, ret_pos=True)
+            component[component == "low_alpha_disc"] = '0'
+            component[component == "high_alpha_disc"] = '1'
+            component[component == "bulge"] = '2'
         else:
             # draw parameters from simple Milky Way (following Breivik+2020)
-            tau, dist, Z_unbinned, pos = simulate_simple_mw(MW_SIZE, ret_pos=True)
+            tau, dist, Z_unbinned, pos, component = simulate_simple_mw(MW_SIZE, ret_pos=True)
+            component[component == "thin_disc"] = '0'
+            component[component == "thick_disc"] = '1'
+            component[component == "bulge"] = '2'
         R, z, theta = pos
 
         # work out COMPAS limits (and limit to Z=0.022)
@@ -134,8 +140,8 @@ def main():
 
         # sort by metallicity so everything matches up well
         Z_order = np.argsort(Z_unbinned)
-        tau, dist, Z_unbinned, R, z, theta = tau[Z_order], dist[Z_order], Z_unbinned[Z_order],\
-            R[Z_order], z[Z_order], theta[Z_order]
[…]

### 2021-07-25 simulation/src/simulate_DCO_detections.py
change compnent dtype

@@ -102,7 +102,7 @@ def main():
     dt = np.dtype(float)
     dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
              ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
-             ("tau", dt), ("Z", dt), ("R", dt), ("z", dt), ("theta", dt), ("component", np.dtype(str)),
+             ("tau", dt), ("Z", dt), ("R", dt), ("z", dt), ("theta", dt), ("component", np.dtype(int)),
              ("snr", dt), ("weight", dt), ("seed", dt)]
     to_file = np.zeros(shape=(loops * MAX_HIGH,), dtype=dtype)
 
@@ -113,15 +113,15 @@ def main():
         if not use_simple_mw:
             # draw parameters from Frankel Model
             tau, dist, Z_unbinned, pos, component = simulate_mw(MW_SIZE, ret_pos=True)
-            component[component == "low_alpha_disc"] = '0'
-            component[component == "high_alpha_disc"] = '1'
-            component[component == "bulge"] = '2'
+            component[component == "low_alpha_disc"] = 0
+            component[component == "high_alpha_disc"] = 1
+            component[component == "bulge"] = 2
         else:
             # draw parameters from simple Milky Way (following Breivik+2020)
             tau, dist, Z_unbinned, pos, component = simulate_simple_mw(MW_SIZE, ret_pos=True)
-            component[component == "thin_disc"] = '0'
-            component[component == "thick_disc"] = '1'
-            component[component == "bulge"] = '2'
+            component[component == "thin_disc"] = 0
+            component[component == "thick_disc"] = 1
+            component[component == "bulge"] = 2
         R, z, theta = pos
 
         # work out COMPAS limits (and limit to Z=0.022)

### 2021-07-26 paper/tex/sections/methods.tex
more stephen feedback

@@
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
-This shows how these distributions translate to positions in the Milky and illustrates the gradient in metallicity over radius.
+This shows how these distributions translate to positions and illustrates the gradient in metallicity over radius.
 
@@
 Each binary is likely to move from its birth orbit.
-Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, double compact objects generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep[e.g.][]{Hobbs+2005}.
+Although all stars in the Galactic disc experience radial migration \citep{Sellwood+2002, Frankel+2018}, DCOs generally experience stronger dynamical evolution as a result of the effects of both Blaauw kicks \citep{Blaauw+1961} and natal kicks \citep[e.g.][]{Hobbs+2005}.
 
 The magnitude of the systemic kicks are typically small compared to the initial circular velocity of a binary at each Galactocentric radius.
-Therefore, we expect that kicks will not significantly alter the overall distribution of their positions.
+Therefore, we expect that kicks will not significantly alter the overall distribution of their positions (see however e.g.\ \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
 Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.

### 2021-07-26 paper/tex/sections/comparisons.tex
stephen comparison feedback

@@
 They find a much lower detection rate for BHNSs and NSNSs (and agreed on zero BHBHs) when compared to \citet{Nelemans+2001}.
-They claim that this discrepancy comes from differences in their population synthesis and an overall lower formation rate rather than any changes to LISA detectability.
+They state that this discrepancy from \citet{Nelemans+2001} comes from differences in their population synthesis and an overall lower formation rate rather than any changes to LISA detectability.
 The low total detection rate for all DCOs in this paper compared to our work is unsurprising given the relatively high SNR threshold of 10 and short mission length of 1 year.
@@
 
-\paragraph{\citet{Lamberts+2018}} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way, thus being the first paper in this area to incorporate metallicity dependence into their Milky Way model.
+\paragraph{\citet{Lamberts+2018}} presented a new approach to the problem by using the FIRE simulation \citep{Hopkins+2014} to distribute their sources rather than an analytical model of the Milky Way and were the first paper in this area to incorporate metallicity dependence into their Milky Way model.
 \citet{Sesana+2020} followed up on this paper using the same simulated BHBH population and presented updated results for the number of expected BHBH detections.
@@
 Yet it is most likely that the remaining difference between our results is due to way in which we simulate the Milky Way.
-\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we used to estimate how impactful the choice of MW model was in Appendix~\ref{app:mw_changes}.
+\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we use to estimate the impact of the choice of MW model is in Appendix~\ref{app:mw_changes}.
 We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results.
-\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so this effect could be even stronger as their results will have no contribution from lower metallicity systems.
+\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so the overestimation could be even stronger as their results will have no contribution from lower metallicity systems.
 
@@
 These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS.
-Given our strong agreement for BHBHs, it is possible that COSMIC and COMPAS handle NSs differently and thus lead to different detection rates for DCOs containing NSs.
+Given our strong agreement for BHBHs, it is possible that COSMIC and COMPAS handle NSs differently and so lead to different detection rates for DCOs containing NSs.
 However checking this would require a more in-depth study of the intrinsic formation rate of DCOs containing NSs in the two codes.

### 2021-07-26 paper/tex/sections/conclusion.tex
stephen feedback conclusions

@@
 We provide predictions for the detection rate and population properties of LISA detectable BHBH, BHNS and NSNS.
-To this end, we use the rapid population synthesis code COMPAS to simulate over two billion massive binaries, to explore the effect of parameters that are varied to represent the most common uncertainties in binary physics.
+To this end, we use the rapid population synthesis code COMPAS to simulate over two billion massive binaries, to explore the effect of varying underlying physics assumptions that represent the most common uncertainties in binary physics.
 We use an new empirically-informed analytical model to distribute the resulting BHBH, BHNS and NSNS populations in a Milky-Way like galaxy based on their birth metallicity, in order to estimate and investigate the LISA detectable population of BH and NS binaries.
@@
     \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in ground-based detectors), with 90\% having BH masses less than $11 \unit{M_\odot}$.
+    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in current ground-based detectors), with 90\% having BH masses less than $11 \unit{M_\odot}$.
 Moreover, we find that for LISA detectable DCOs, $\BHBHLowerMassGap{}$ of BHBHs and $\BHNSLowerMassGap{}$ of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
-This implies that LISA will be able provide conclusive evidence about the existence of a lower-mass gap.
+This implies that LISA will be able provide conclusive evidence about the existence of a lower mass gap.
     \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities when observable by the LISA mission, unlike the more numerous WDWD LISA population.
-We find that \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
+We predict that for the observed population \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
     \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
-Conversely, the BHNS rate varies widely with physics variation, ranging across three orders of magnitude.
-The NSNS shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
-    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission, we estimate that of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
+Conversely, the BHNS detection rate varies widely with physics variation, ranging across three orders of magnitude.
+The NSNS detection rate shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
+    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission we estimate that, of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
 Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} the binary contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of pulsars that could crowd the sky in SKA-2 means that this total decreases to 6.
+    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} a LISA detectable DCO contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.

### 2021-07-26 simulation/output/combine_output.py
add component to combine file

@@ -13,7 +13,8 @@ from galaxy import distance_from_earth
 dt = np.dtype(float)
 dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
          ("a_LISA", dt), ("e_LISA", dt), ("t_evol", dt), ("t_merge", dt),
-         ("tau", dt), ("dist", dt), ("R", dt), ("z", dt), ("theta", dt), ("Z", dt), ("snr", dt), ("weight", dt),
+         ("tau", dt), ("dist", dt), ("R", dt), ("z", dt), ("theta", dt), ("Z", dt),
+         ("component", np.dtype(int)), ("snr", dt), ("weight", dt),
          ("seed", dt), ("channel", np.dtype(int)), ("m_1_ZAMS", dt),
          ("m_2_ZAMS", dt), ("MT1_case", np.dtype(int)),
          ("MT2_case", np.dtype(int)), ("a_ZAMS", dt), ("a_pre_SN2", dt),

### 2021-07-26 simulation/output/combine_output.py
change which files to combine

@@ -115,7 +115,7 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
 
 # loop over all binary types and physics variations
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    for variation in [0, 1, 2, 3, 4, 5, 7, 10, 11, 12, 13, 14, 15, 16, 18]:
+    for variation in [0]:#, 1, 2, 3, 4, 5, 6, 10, 11, 12, 13, 14, 15, 16, 18]:
         combine_data(dco_type, variation)
-        # if variation == 0:
-        #     combine_data(dco_type, variation, simple_mw=True)
+        #if variation == 0 or variation == 5:
+        #    combine_data(dco_type, variation, simple_mw=True)

### 2021-07-26 paper/tex/sections/variations.tex
create new detection rate plot
round 2 of feedback from Stephen
update variation section, reorganise mass transfer

@@
-In this section we explore the effect of varying the underlying binary physics assumptions and the model for the Milky Way.
-In Section~\ref{sec:detection_rate_analysis} we explore the changes in the detection rate over different physics variations  and in Section~\ref{sec:property_variations} we consider how these model physics variations change the properties of detectable systems.
-Finally we demonstrate how different models for the Milky Way can affect our results in Section~\ref{sec:mw_changes}.
+In this section we explore the effect of varying the underlying binary physics assumptions, both on the detection rate (Section~\ref{sec:detection_rate_analysis}) and the properties of the detectable systems (Section~\ref{sec:property_variations}).
 
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-\tom{I will be updating this section once the other physics variations are done running. There will be a couple of new models and the current ones will have better high Z resolution.}
+In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
+For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates}.
 
-We find that for our fiducial model on average, a 4-year LISA mission will detect \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs.
-Increasing to a 10-year LISA mission length changes the number of detections to \BHBHTenYear{}, \BHNSTenYear{} and \NSNSTenYear{} respectively.
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
-We show the rates and uncertainties plotted in this figure in Table~\ref{tab:detection_rates}.
+The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the expected detections in most models staying within 25\% of the fiducial rate.
+In contrast, the BHNS detection rate is very sensitive to all changes in binary physics assumptions, varying across two orders of magnitude in the middle pane of Figure~\ref{fig:detection_rates}.
+Finally, in the last panel of Figure~\ref{fig:detection_rates} we show that the NSNS detection is only moderately sensitive to certain changes in physics assumptions, varying by up to an order of magnitude, whilst showing no change for many models.
 
@@
 See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\todo{subject to change with the updated/new models and new uncertainty estimates}}
+\todo{Will add H, I, J, R, T once Floor says that they are done}}
     \label{fig:detection_rates}
@@
 
+\subsubsection{Mass transfer trends}
+
+In models \modBetaLow{}-\modBetaHigh{}, we set the mass transfer efficiency $\beta$ to a fixed value.
+For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease.
+This may seem unintuitive since one may assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population.
+However, this contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
+Moreover, one must consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018}.
+
+In contrast, for the NSNSs, the detection rate increases with increasing $\beta$.
+This is for two main reasons: firstly the ejection of a common envelope is less problematic for NSNSs as they are less massive \citep[e.g.][]{Kruckow+2018}.
+Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
+Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.
+
+Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) has little effect on the BHBH detection rate whilst moderately and drastically decreasing the detection rates of BHNSs and NSNSs respectively.
+This is because a large fraction of NSs (and the majority of NSNS binaries are formed) through case BB mass transfer.
+Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic CE scenario by default.
+
+If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types.
+This is both from the natural increases from using the optimistic CE scenario (see Sec.~\ref{sec:detection_rate_CE_trends} in which we discuss model \modOpt{}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer.
+This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.
+
+\subsubsection{Common envelope trends}\label{sec:detection_rate_CE_trends}
+
+\subsubsection{Remnant mass prescription trends}
+
+\subsubsection{Supernova kick trends}
+
+\subsubsection{Stellar wind trends}
+
 \subsubsection{BHBH detection rate trends}
-The BHBH detection rate is markedly robust across physics variations, with the expected detections in each model staying within 25\% of the fiducial rate (with the exception of model \modOpt{}).
-Thus even if there are changes in our understanding of the underlying physics before the LISA mission commences, the expected BHBH detection rate is unlikely to change significantly.
-
 The exception to this statement is model \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
@@
 \subsubsection{BHNS detection rate trends}
-In contrast, the BHNS detection rate is very sensitive to changes in binary physics assumptions.
-Therefore, once LISA flies and we know the actual number of detections, we can compare to each model and possibly provide some constraint on binary evolution physics.
-There are several notable trends in the BHNS detection rate in the middle pane of Figure~\ref{fig:detection_rates}.
 
-As $\beta$ increases in models \modBetaLow{}-\modBetaHigh{}, the BHNS detection rate steadily decreases.
-This may seem unintuitive since a higher mass transfer efficiency should lead to more massive compact objects and thus a more detectable population.
-However, one must also consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable BHNSs \citep[e.g.][]{Kruckow+2018}.
+For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
+This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
 
@@
 (I'm leaving thinking about this for now in case it changes with the new data haha)}
-% For a similar reason, the rate is decreased when $\alpha$ is decreased in model \modAlphaLow{}, as this reduces the amount of orbital energy that is used to eject the envelope and thus leads to more stellar mergers.
-\todo{Why isn't the opposite true for model \modAlphaHigh{}?
-It seems the number of bound DCOs \textit{does} increase but the merging total decreases...?}
-
-Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) decreases the detection rate as fewer NSs are produced and thus fewer BHNSs form.
-This is explained in further detail in Section~\ref{sec:NSNS_detection_trends}.
-For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
-This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
 
@@
 
-As $\beta$ increases the NSNS detection rate increases, the opposite trend to that seen in the BHNS rate.
-This is for two main reasons: firstly the ejection of a common envelope is less problematic for the less massive NSNS binaries.
-Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
-Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.
-
-There is a drastic decrease in detections for model \modCaseBB{} by nearly two orders of magnitude.
-This is because the majority of NSNS binaries are formed through case BB mass transfer and setting this mass transfer to be always unstable results in many of these binaries to merge before they could become NSNSs.
-As a result the total number of detections decreases, however, interestingly the remaining population represent more massive progenitors (that would not go through case BB mass transfer) and thus is skewed to higher masses and has a \textit{higher} detectable fraction.
-
 The vast majority of NSNSs in our sample are formed through the common envelope channel and thus changing the value of $\alpha_{\rm CE}$ has an effect on the rate.

### 2021-07-26 paper/tex/sections/variations.tex
big updates to 4.1 trends discussion

@@
 
-\subsubsection{Mass transfer trends}
+\subsubsection{Mass transfer variation trends}
 
@@
 
-\subsubsection{Common envelope trends}\label{sec:detection_rate_CE_trends}
+\subsubsection{Common envelope variation trends}\label{sec:detection_rate_CE_trends}
 
-\subsubsection{Remnant mass prescription trends}
+\todo{Discuss $\alpha_{\rm CE}$ changes once Floor ready}
 
-\subsubsection{Supernova kick trends}
+We explore the optimistic CE scenario in model \modOpt{}, meaning that we allow Hertzsprung gap donors to survive CE events.
+A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events.
+Therefore, though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
+This increase is less significant for BHNSs since their progenitors tend to be less massive and thus initiate CE events during the Hertzsprung gap less frequently.
+For the same reason, the NSNS detection rate shows little significant change.
 
-\subsubsection{Stellar wind trends}
+\subsubsection{Supernova variation trends}
 
-\subsubsection{BHBH detection rate trends}
-The exception to this statement is model \modOpt{}, in which we allow Hertzsprung gap donors to survive common envelope events.
-A large fraction of the progenitors of BHs in this mass range expand significantly during the Hertzsprung gap phase and initiate common envelope events.
-Therefore, though the detectable fraction does not change significantly, the increased population of BHBHs in the Milky Way leads to this model predicting 2.5 times more detections.
+Changes to the remnant mass prescription (models \modRapid{}-\modNSHigh{}) have no effect on the NSNS detection rate for two reasons.
+A large fraction of the NSs in our sample are formed through ECSN, in which case their masses are set to $1.26 \unit{M_\odot}$ regardless of the remnant mass prescription.
+Secondly, the majority of the remaining NSs have such low progenitor masses that they are set to the lowest remnant mass in the prescription ($1.28 \unit{M_\odot}$ for the delayed prescription and $1.1 \unit{M_\odot}$).
+This means that changing the upper portion of the mass range of NSs in the remnant mass prescription has little effect.
 
-\subsubsection{BHNS detection rate trends}
+This is not the case for BHBHs and BHNSs.
+The different remnant mass prescriptions and maximum neutron star masses change whether a progenitor becomes a black hole or a neutron star.
+Hence, using the rapid prescription (model \modRapid{}) or increasing the maximum neutron star mass (model \modNSHigh{}), means that more progenitors form high mass NSs rather than low mass BHs and so more BHNSs are formed.
+This explains the higher detection rates for BHNSs and lower detection rates for BHBHs in these models.
+The inverse is true for model \modNSLow{}, where instead more BHBHs are formed and detected.
 
-For the same reason as the BHBH rate, model \modOpt{} has a higher number of detections.
-This change is less prominent than in the BHBH case as the progenitors tend to be lower masses and initiate a CE event less frequently during the Hertzsprung gap phase.
+Additionally, we find that not implementing PISN and PPISN (model \modNoPISN{}) has no effect on the results for any DCO type.
+This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.
 
-\tom{@ALL, the trend with common envelopes still confuses me, specifially, why does it not increase when $\alpha=2.0$?
-We never quite resolved this in the thread in zpro\_tom\_wagg with me and Lieke.
-I do see that the BHBH have a lot of only stable mass transfer and so reasonably are not too affected.
-NSNS basically only come through CE events and so sensibly are strongly affected but BHNS have $\sim 70\%$ classic channel and so should be affected strongly.
-But we don't see an increase with $\alpha = 2.0$.
-Any thoughts?
-(I'm leaving thinking about this for now in case it changes with the new data haha)}
+Decreasing the core-collapse supernova velocity dispersion (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
+This increase is least prominent for BHBHs since their increased mass mean that disruptions are less frequent than, for instance, in NSNSs.
+It is also notable that \citet{Broekgaarden+2021} found that these two models best matched the detection rates from LIGO.
+Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.
 
-The Fryer \textit{rapid} prescription (model \modRapid{}) leads to a higher detection rate for BHNSs because progenitors that would become black holes in the \textit{delayed} prescription, instead become neutron stars and so more BHNSs are formed instead of BHBHs.
-For the same reason, increasing the maximum neutron star mass (model \modNSHigh{}) increases the detection rate and the inverse is true when it is decreased (model \modNSLow{}).
+\todo{dicuss no BH kick when done}
+%The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
 
-Finally, models \modSigLow{}-\modNoBH{} show increased detection rates since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-Following this logic it makes sense that model \modSigLower{} produces more detections than model \modSigLow{}.
-The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-
-\subsubsection{NSNS detection rate trends}\label{sec:NSNS_detection_trends}
-
-The vast majority of NSNSs in our sample are formed through the common envelope channel and thus changing the value of $\alpha_{\rm CE}$ has an effect on the rate.
-We see that decreasing $\alpha_{\rm CE}$ (model \modAlphaLow) leads to a lower rate as there is less energy available to eject the envelope and so more binaries result to stellar mergers rather than NSNSs and similarly we see an inverse trend when increasing $\alpha_{\rm CE}$ (model \modAlphaHigh).
-
-As we found in the BHNS trends, a lower value for the core-collapse supernova velocity dispersion increases the detection rate in models \modSigLow{} and \modSigLower{}, whilst changing the PISN or BH kick prescription (models \modNoPISN{} and \modNoBH{}) of course has no effect on the NSNS population.
+\subsubsection{Stellar wind variation trends}
+\todo{}
 

### 2021-07-26 paper/tex/sections/variations.tex
add in the new variation figures

@@
 \subsection{Properties of detectable systems}\label{sec:property_variations}
-\tom{This will be about how the shapes of the parameter distributions change for the different model variations.
-I won't detail every variation but I'll point out anything that stands out and leave the rest in the appendix plots.}
+\todo{Describe the plots -- also explore whether there is anything interesting the CE ones once they are done}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{lower_mass_gap_rapid_variation.pdf}
+    \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
+Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}}
+    \label{fig:lower_mass_gap_variation}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{ecc_low_kick_variation.pdf}
+    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model as dashed lines.}
+    \label{fig:ecc_low_kick_variation}
+\end{figure}
+
+% \begin{table}[htb]
+%     \centering
+%     \begin{tabular}{l|cccc}
+%         \hline
+%         \multirow{2}{*}{Component} & At Formation & \multicolumn{3}{c}{LISA detectable (4 year)} \\ \cline{2-5}
+%         & All & BHBH & BHNS & NSNS \\
+%         \hline
+%         Low-$\alpha$ disc & 42.5\% & 88.6\% & 81.8\% & 84.9\%\\
+%         High-$\alpha$ disc & 42.5\% & 5.2\% & 8.1\% & 12.0\%\\
+%         Bulge & 15.0\% & 6.2\% & 10.1\% & 3.1\%\\
+%     \end{tabular}
+%     \caption{Percentage of systems in each Galactic component.}
+% \end{table}

### 2021-07-27 paper/tex/sections/appendix.tex
stephen feedback app, update formation channel plt

@@
 
-We simulate between 1 and 100 million massive binaries for 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-We simulate more binaries for higher metallicities to account for the lower formation rate of DCOs.
+We simulate between 1 and 100 million massive binaries for each of 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+We simulate more binaries for higher metallicities so that large enough sample of DCOs at each metallicity (since DCOs are formed at a lower rate at higher metallicities).
 These metallicities span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
@@
 The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[consistent e.g.\ with][]{Sana+2012}.
+The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[e.g.\ consistent with][]{Sana+2012}.
 We additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
@@
 We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised after mass transfer this is a reasonable assumption and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
+Since we focus on post-interaction binaries which will have circularised after mass transfer we argue this is an reasonable assumption (as many studies have in the past) and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
 
 We apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
-This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing it without STROOPWAFEL in effect.
+This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing the DCO without STROOPWAFEL in effect.
 
@@
 We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
-Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observer LBV eruptions for stars with luminosities and  effective temperatures above the Humphrey Davidson limit.
-We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars and set $f_{\rm WR} = 1$.
+Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observed LBV eruptions for stars with luminosities and effective temperatures above the Humphreys-Davidson limit.
+We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars, and set $f_{\rm WR} = 1$.
 See Team COMPAS: J.
@@
 For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
-The \textit{delayed} prescription does not reproduce the neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
+The \textit{delayed} prescription does not reproduce a neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
 We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
@@
 where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
-These truncations mean that only $f_{\rm trunc} \approx 0.2$ of the stellar mass in the galaxy is sampled from.
+These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from and the rest is contained in lower mass stars that are not relevant for forming the DCOs studies in this paper.
 
@@
 Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer at al.
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer et al.
 (in prep)).
@@
 If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.2$ and $0.7$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.
-Note that the assumption of a uniform distribution is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide an upper bound on these estimates.
+Note that the assumption of a uniform distribution is not realistic as pulsars will tend to be far more concentrated in the Galactic centre but we use it to provide a slightly optimistic estimate.
 
@@
     \centering
-    \includegraphics[height=0.28\textheight]{formation_channels_BHBH.pdf}
-    \includegraphics[height=0.28\textheight]{formation_channels_BHNS.pdf}
-    \includegraphics[height=0.28\textheight]{formation_channels_NSNS.pdf}
+    \includegraphics[width=\textwidth]{formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
@@
 The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
-\todo{Update with new models}}
+\todo{Update H, I, J, K, T}}
     \label{fig:formation_channels}

### 2021-07-28 paper/tex/sections/methods.tex
update galaxy diagram with new bulge

@@
     \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
-    \caption{A schematic illustrating how we create a mock Milky Way galaxy.
-The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, age-metallicity-radius relation, and vertical distribution.
+    \caption{A schematic illustrating how we create a mock Milky Way.
+The left side illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, metallicity-radius-time relation, and vertical distribution.
     On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity.

### 2021-07-29 paper/tex/paper.tex
massive restructuring, split results by fiducial and variations
Updates from Overleaf
rearrange appendix to 2col, move mw compare
make the discussion make sense again
update numbers
updates to 3.1 and 3.2 from Selma
ensure all stats are up to date
change title to two lines, fix names

@@
-\documentclass[twocolumn]{aastex63}
+\documentclass[twocolumn, twocolappendix]{aastex63}
 \received{\today}
@@
 \usepackage{xcolor} % to add more color options
+\usepackage{wrapfig}
 
@@
 
-\newcommand{\BHBHFourYear}{36}
-\newcommand{\BHNSFourYear}{33}
+\newcommand{\BHBHFourYear}{74}
+\newcommand{\BHNSFourYear}{42}
 \newcommand{\NSNSFourYear}{8}
-\newcommand{\BHBHTenYear}{56}
-\newcommand{\BHNSTenYear}{55}
-\newcommand{\NSNSTenYear}{13}
+\newcommand{\BHBHTenYear}{TODO}
+\newcommand{\BHNSTenYear}{TODO}
+\newcommand{\NSNSTenYear}{TODO}
 
-\newcommand{\BHBHNotWDWDFour}{15}
-\newcommand{\BHNSNotWDWDFour}{10}
-\newcommand{\NSNSNotWDWDFour}{4}
-\newcommand{\BHBHNotWDWDTen}{22}
-\newcommand{\BHNSNotWDWDTen}{17}
-\newcommand{\NSNSNotWDWDTen}{7}
+% number of systems that are definitely not WDWDs
+\newcommand{\BHBHNotWDWDFour}{33}
+\newcommand{\BHNSNotWDWDFour}{16}
+\newcommand{\NSNSNotWDWDFour}{5}
+\newcommand{\BHBHNotWDWDTen}{TODO}
+\newcommand{\BHNSNotWDWDTen}{TODO}
+\newcommand{\NSNSNotWDWDTen}{TODO}
 
-\newcommand{\BHBHDistinguishedFour}{5}
-\newcommand{\BHNSDistinguishedFour}{4}
-\newcommand{\NSNSDistinguishedFour}{3}
-\newcommand{\BHBHDistinguishedTen}{11}
-\newcommand{\BHNSDistinguishedTen}{7}
-\newcommand{\NSNSDistinguishedTen}{5}
+% percentage of systems above Chandrasekhar mass
+\newcommand{\BHBHAboveMaxWDWDFourPerc}{17}
+\newcommand{\BHNSAboveMaxWDWDFourPerc}{21}
+\newcommand{\NSNSAboveMaxWDWDFourPerc}{3}
+\newcommand{\BHBHAboveMaxWDWDTenPerc}{TODO}
+\newcommand{\BHNSAboveMaxWDWDTenPerc}{TODO}
+\newcommand{\NSNSAboveMaxWDWDTenPerc}{TODO}
+
+% number of systems that can be determined as either a BH or NS
+\newcommand{\BHBHEitherBHOrNSFour}{11}
+\newcommand{\BHNSEitherBHOrNSFour}{6}
+\newcommand{\NSNSEitherBHOrNSFour}{3}
+\newcommand{\BHBHEitherBHOrNSTen}{TODO}
+\newcommand{\BHNSEitherBHOrNSTen}{TODO}
+\newcommand{\NSNSEitherBHOrNSTen}{TODO}
+\newcommand{\BHBHEitherBHOrNSFourPerc}{14}
+\newcommand{\BHNSEitherBHOrNSFourPerc}{13}
+\newcommand{\NSNSEitherBHOrNSFourPerc}{35}
+\newcommand{\BHBHEitherBHOrNSTenPerc}{TODO}
+\newcommand{\BHNSEitherBHOrNSTenPerc}{TODO}
+\newcommand{\NSNSEitherBHOrNSTenPerc}{TODO}
+
+% percentage of systems in lower mass gap
+\newcommand{\BHBHLowerMassGap}{35\%}
+\newcommand{\BHNSLowerMassGap}{38\%}
+
+% percentage of systems with q > 0.8
+\newcommand{\BHBHqAbovePointEight}{8\%}
+\newcommand{\BHNSqAbovePointEight}{0\%}
+\newcommand{\NSNSqAbovePointEight}{90\%}
+
+% percentage of systems with e > 0.01
+\newcommand{\BHBHNotCirc}{86\%}
+\newcommand{\BHNSNotCirc}{47\%}
+\newcommand{\NSNSNotCirc}{86\%}
+
+% percentage of systems with e > 0.3
+\newcommand{\BHBHHighlyEccentric}{22\%}
+\newcommand{\BHNSHighlyEccentric}{8\%}
+\newcommand{\NSNSHighlyEccentric}{12\%}
+
+% percentage of systems with something other than 1 detectable harmonic
+\newcommand{\BHBHMultipleHarmonicsFourPerc}{55}
+\newcommand{\BHNSMultipleHarmonicsFourPerc}{28}
+\newcommand{\NSNSMultipleHarmonicsFourPerc}{66}
+\newcommand{\BHBHMultipleHarmonicsTenPerc}{TODO}
+\newcommand{\BHNSMultipleHarmonicsTenPerc}{TODO}
+\newcommand{\NSNSMultipleHarmonicsTenPerc}{TODO}
+
+% percentage of systems with >1 harmonic and in disc
+\newcommand{\BHBHEccInDiscFourPerc}{40}
+\newcommand{\BHNSEccInDiscFourPerc}{25}
+\newcommand{\NSNSEccInDiscFourPerc}{60}
+\newcommand{\BHBHEccInDiscTenPerc}{TODO}
+\newcommand{\BHNSEccInDiscTenPerc}{TODO}
+\newcommand{\NSNSEccInDiscTenPerc}{TODO}
+
+% percentage of systems with fractional chirp mass uncertainty < 1
+\newcommand{\BHBHChirpMassMeasureable}{20}
+\newcommand{\BHNSChirpMassMeasureable}{17}
+\newcommand{\NSNSChirpMassMeasureable}{4}
 
@@
 
-% \color{white}
-% \pagecolor{black}
+% Milky Way notation
+\newcommand{\achem}{\ensuremath{[\alpha/\mathrm{Fe}]}}
 
@@
 
-% selma's newest catchy one
-\title{Gravitational wave sources in our Galactic backyard: Predictions for BH and NS binaries in LISA}
-
-% selma suggested removing BHNS
-% \title{Predictions for neutron star and black hole binaries with LISA}
-
-% original
-%\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}
+\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA}}
 
@@
 
-\author[0000-0002-4421-4962]{F. Broekgaarden}
+\author[0000-0002-4421-4962]{F.S. Broekgaarden}
 \affiliation{\cfa}
 
-\author[0000-0001-9336-2825]{S. E. de Mink}
+\author[0000-0001-9336-2825]{S.E. de Mink}
 \affiliation{\mpa}
@@
 
-\keywords{LISA, black hole, neutron star, binary}
+\keywords{LISA, gravitational waves, black hole, neutron star, binary}
 
@@
 
-\section{Results} \label{sec:results}
+\section{Results I - Fiducial} \label{sec:results}
 \input{sections/results.tex}
+
+\section{Results II - Model variations} \label{sec:variations}
+\input{sections/variations.tex}
 
@@
 \acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions.
+TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
 This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.

### 2021-07-29 paper/tex/sections/abstract.tex
floor feedback: abstract

@@
-We present predictions for the properties of the population of Galactic double black holes (BHBH), black hole neutron stars (BHNS) and double neutron stars (NSNS) that will be detectable by the planned space-based gravitational wave detector LISA.
+We present predictions for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
 We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with an empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
 We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common envelope, supernova and wind mass loss physics.
-We find that for a 4(10)-year mission, LISA will detect on average about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-The BHBH rate remains notably consistent under different physics assumptions, whilst in contrast the BHNS and NSNS rates each vary over 3 orders of magnitude.
+We predict that for a 4(10)-year mission, LISA will (typically) detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
+The predicted BHBH rate remains notably consistent under different physics assumptions, whilst in contrast the BHNS and NSNS rates each vary over 3 orders of magnitude.
 We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population as well as for disentangling the BHBH, BHNS and NSNS populations from each other.

### 2021-07-29 paper/tex/sections/comparisons.tex
floor feedback: intro

@@
 
-In Figure~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
+In Figure~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar-mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
 Figure~\ref{fig:previous_studies} details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
@@
 
-\paragraph{\citet{Nelemans+2001}} were the first to investigate the population of LISA detectable stellar mass double compact objects.
+\paragraph{\citet{Nelemans+2001}} were the first to investigate the population of LISA detectable stellar-mass double compact objects.
 We find a significantly higher detection rate for BHBHs and BHNSs, as well as a slightly lower rate for NSNSs.

### 2021-07-29 paper/tex/sections/introduction.tex
change title to two lines, fix names
floor feedback: intro

@@
-Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive binary stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
+Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
 
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe at lower frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of sources that are undetectable with ground-based detectors, such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
-Moreover, this frequency regime is also of interest for the detection of local stellar mass double compact objects (DCO) far in advance of their merger.
-This presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+LISA will observe at lower frequencies ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) than ground-based detectors and so will enable the study of sources that are imperceptible by ground-based detectors, such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
+Moreover, this frequency regime is also of interest for the detection of \textit{local} stellar-mass double compact objects (DCO) millions of years before their merger.
+This presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband gravitational wave detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
 In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
-Unlike ground-based detectors, LISA only detects stellar mass sources in local galaxies, with the majority residing in the Milky Way.
-Therefore, these sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.
+Unlike ground-based detectors, LISA only detects stellar-mass sources in local galaxies, with the majority residing in the Milky Way.
+These sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.
 
-Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
+Traditionally, investigations into detecting stellar-mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
 More recently, interest has grown in the detection of NS and BH binaries.
 Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars.
-In this paper we focus on double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).
+In this paper we focus on making LISA predictions for double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).
 
+The detection of NSNSs in LISA could improve our understanding of many phenomena.
 Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.
 \citealp{Hulse+1975}, see also refs.\ in \citealp{Tauris+2017,Vigna-Gomez+2018}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
-The detection of a NSNS in LISA with a pulsar component could potentially connect these two populations if the binary is close to merging, as the binary could be observed from inspiral to merger.
-NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
+A LISA detectable NSNS with a pulsar component close to merger would be ideal for connecting these population, as the binary could be observed from inspiral to merger.
+NSNS (and possible BHNS) binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Berger+2014}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
 BHBHs in the Milky Way present a greater observational challenge.
-To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH.
+To date, no BH has been observed in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH.
 The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
@@
 Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged (\citealp{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020}, see also \citealp{Liu+2020}) and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
-A sample of BHBHs detected with LISA could possibly help to constrain the stellar mass BH mass distribution.
+A sample of BHBHs detected with LISA could possibly help to constrain the BH mass distribution.
 
@@
 With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.
-However, with only two detections (not including the low-confidence candidates GW190425 and GW190184 \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
+However, with only two detections (not including the low-confidence candidate GW190426 \citep{Abbott+2020_GWTC2} or GW190425 and GW190814 which have not been ruled out as BHNSs \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
 Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
-These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs.
+Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts.
 A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
@@
 We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.
-These channels include: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017, Toonen+2020} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.
+These channels include: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015}, young/open star clusters \citep[e.g.][]{Ziosi+2014, DiCarlo+2020, Rastello+2020, Rastello+2021} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated (hierarchical) triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017, Toonen+2020},  and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009,Mandel+2016,Marchant+2016,Marchant+2017,duBuisson+2020}.
 
@@
 In a companion paper, Wagg et al.
-(in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+(in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 

### 2021-07-29 paper/tex/sections/methods.tex
floor feedback: methods

@@
 To produce predictions for the DCOs that are detectable with LISA, we synthesise a population of DCOs using the population synthesis methods described in Section~\ref{sec:COMPAS_explained}.
-In order to obtain values for the uncertainty on the expected detection rates, we place this sample of DCOS in many different Monte Carlo sampled instances of the Milky Way, the model for which is described in Section~\ref{sec:galaxy_synthesis}.
+In Section~\ref{sec:galaxy_synthesis} we describe our model for the Milky Way and how we place DCOs in randomly sampled Milky Way instances.
 We evolve the orbit of each DCO in a Milky Way instance up to the LISA mission and calculate the detection rate for that instance using the methods presented in Section~\ref{sec:gw_detection}.
@@
 
-We use the grid of binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
+We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
 (in prep).
-This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Stevenson+2019}.
-COMPAS follows the approach of the pioneering population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
-The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper (Team COMPAS: J.
-Riley et al.
-(in prep)).
+This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}.
+COMPAS follows the approach of the population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
+The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper (Team COMPAS: J.\ Riley et al.\ in prep).
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
 
-The result of the simulations is a sample of binaries, which, for each metallicity $Z$, have the parameters
+The result of the simulations is a sample of binaries, which, for each metallicity $Z$, have $N_{\rm binaries}$ binaries with parameters
 \begin{equation}
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binary}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+for $i = 1, 2, \dots, N_{\rm binaries}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
 We sample from these sets of parameters when creating synthetic galaxies.
@@
 
+Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
+
 \begin{figure*}[t]
@@
     \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
-    \caption{A schematic illustrating how we create a mock Milky Way.
-The left side illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), spatial distribution at birth, metallicity-radius-time relation, and vertical distribution.
-    On the right, we show an example instance of the Milky Way with $250000$ binaries shown as points colour coded by metallicity.
-The top panel shows a side-on view and the bottom panel shows a face-on view.}
+    \caption{A schematic illustrating how we model the Milky Way.
+The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
+The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
+The top panel shows a side-on view and the bottom panel a face-on view.}
     \label{fig:galaxy_schematic}
@@
 Therefore, we use the chemical definition of the two disks with the \achem~nomenclature because there is a clear bimodal distribution in the chemical plane, allowing stars to be assigned to each of the disc components based on their chemical abundances.
-For each of the three components, we use a separate star formation history, radial and vertical distribution, which we combine into a single model, weighting each component by its stellar mass.
+For each of the three components, we use a separate star formation history and spatial distribution, which we combine into a single model, weighting each component by its stellar mass.
 \citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-\achem~discs \citep[e.g.,][]{Snaith+2014}.
@@
 \textit{Star formation history:} 
-We use an exponentially declining star formation history \citep{Frankel+2018} (a priori inspired by average the cosmic star formation history) for the combined low- and high-\achem~discs, where the two discs transition at about 8 Gyr ago, and re-normalize the produced mass to be equal in each of the two components.
+We use an exponentially declining star formation history \citep{Frankel+2018} (inspired by the average cosmic star formation history) for the combined low- and high-\achem~discs,
 \begin{equation}\label{eq:thin_disc_tau}
@@
 \end{equation}
-where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ is the star formation timescale.
+where $\tau$ is the lookback time (the amount of time elapsed between the binary's zero-age main sequence and today), $\tau_m = 12 \unit{Gyr}$ is the assumed age of the Milky Way and $\tau_{\rm SFR} = 6.8 \unit{Gyr}$ is the star formation timescale \citep{Frankel+2018}.
+The two discs form stars in mutually exclusive time periods, such that the high-\achem~disc forms stars in the early history of the galaxy ($8$--$12 \unit{Gyr}$ ago) and the low-\achem~disc forms stars more recently ($0$--$8 \unit{Gyr}$ ago).
+We normalize both distributions so that an equal amount of mas sis formed in each of the two components over their respective star forming periods.
 
-The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms still under debate.
-But the central bar was shown to contain stars with an extended age range, with most observed stars between 6 and 12 Gyr \citep[e.g.,][]{Bovy+2019}, and a younger tail of ages that could come from the subsequent secular growth of the Galactic bar.
+The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to the (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms that are still under debate.
+However, the central bar was shown to contain stars with an extended age range, with most observed stars between $6$ and $12 \unit{Gyr}$ with a younger tail of ages that could come from the subsequent secular growth of the Galactic bar \citep[e.g.,][]{Bovy+2019}.
 To model the bar's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
-We show these distributions in the first panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
+We show these distributions in the top left panel of Fig.~\ref{fig:galaxy_schematic}.
 
@@
 We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-\achem~disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
-We show the combination of these distributions in the second panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
+We show the combination of these distributions in the second panel on the left in Fig.~\ref{fig:galaxy_schematic}.
 
-\textit{Vertical distribution}: Similar to the radial distribution, we use the same single exponential distribution (but with different scale heights) for each component
+\textit{Vertical distribution}: Similar to the radial distribution, we use the same single exponential distribution (but with different scale heights) for each component, given by
 \begin{equation}\label{eq:galaxy_z}
@@
 \end{equation}
-where $z$ is the height above the Galactic plane and $z_d$ is the scale height.
+where $z$ is the vertical displacement above the Galactic plane and $z_d$ is the scale height.
 We set $z_d = 0.3 \unit{kpc}$ for the low-\achem~disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the high-\achem~disc \citep{Bovy+2016}.
-For the bar, we set $z_d = 0.2 \unit{kpc}$ \citep{Wegg+15}. We show the combination of these distributions in the last panel in the left half of Fig.~\ref{fig:galaxy_schematic}.
+For the bar, we set $z_d = 0.2 \unit{kpc}$ \citep{Wegg+15}.
+We show the combination of these distributions in the bottom left panel of Fig.~\ref{fig:galaxy_schematic}.
 
@@
 
-Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
-
 \subsubsection{Combining population and galaxy synthesis}\label{sec:combining_pop_gal}
@@
 \begin{equation}
-    \mathbf{g}_{{i}} = \{\tau, R, Z, z, \theta\}
+    \mathbf{g}_{{j}} = \{\tau, R, Z, z, \theta\}
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $j = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 
-We match each set of galaxy parameters $\mathbf{g}_{{i}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by drawing a set of binary parameters from the closest metallicity bin to the metallicity in $\mathbf{g}_{{i}}$.
+We match each set of galaxy parameters $\mathbf{g}_{{j}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by drawing a binary from the closest metallicity bin to the metallicity in $\mathbf{g}_{{j}}$.
 
@@
 This can be converted to the semi-major axis at the start of LISA, $a_{\rm LISA} $\citep[][Eq.
-5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law.
+5.11]{Peters+1964}, which in turn gives the orbital frequency, $f_{\rm orb, LISA}$, by Kepler's third law since we know the component masses.
 
@@
 
+Note that the length of the LISA mission affects how much a binary will evolve over the mission and thus changes the frequency limits in Eq.~\ref{eq:snr}.
+The SNR generally scales as $\sqrt{T_{\rm obs}}$ (with exceptions for sources very close to merging) and thus the SNR of a typical source in a 10-year LISA mission is approximately $1.58 (=\sqrt{10/4})$ times stronger than in a 4-year mission.
+
 We use LEGWORK to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational wave luminosity remains below 1\%.
@@
 \subsubsection{Detection rate calculation}
-For each physics variation model and DCO type, we compute the total number of merging DCOs in the Milky Way today, $N_{\rm MW}$, based on the COMPAS simulation.
-This takes into account the true mass and IMF of the Milky Way since our simulations may each have a slightly different galaxy mass and only ever sample from massive stars rather than the full IMF.
+For each physics variation model and DCO type, we first convert the COMPAS simulation results into a total number of DCOs in the Milky Way, $N_{\rm DCO}$.
+We do this by integrating the full mass and period distributions and stars and normalising to the total Milky Way mass.
 For more details see Appendix~\ref{app:rate_normalisation}.
 
-We determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation.
-We multiply this fraction by the total number in the Milky Way to find a detection rate.
+We then determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation.
+We multiply this fraction by the total number in the Milky Way to find a detection rate (which we write as a total number of detections per LISA mission)
 \begin{equation}
-    N_{\rm detect} = \frac{\sum_{i = 0}^{N_{\rm detect}} w_i}{\sum_{i = 0}^{N_{\rm DCO}} w_i} \cdot N_{\rm MW}
+    N_{\rm detect} = \frac{\sum_{i = 0}^{N_{\rm MW}} w_i \phi(i)}{\sum_{i = 0}^{N_{\rm MW}} w_i} N_{\rm DCO},
 \end{equation}
+where $\phi(i) = 1$ if a binary is detectable and $0$ otherwise.
 We calculate the detection rate by Monte Carlo sampling 2500 Milky Way instances (each containing 200,000 DCOs) for each DCO type and every physics variation in order to obtain values for the uncertainty on the expected detection rate.

### 2021-07-29 paper/tex/sections/appendix.tex
floor feedback: results

@@
 
-\subsection{Physical assumptions in our fiducial model}\label{sec:fiducial_physics}
+\subsection{Physical assumptions in our fiducial model}\label{app:fiducial_physics}
 
@@
 In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
-Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{sec:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
+Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{app:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
 
@@
         \hline \hline
-        \modFid & Fiducial (see Section~\ref{sec:fiducial_physics}) \\
+        \modFid & Fiducial (see Section~\ref{app:fiducial_physics}) \\
         \hline

### 2021-07-29 paper/tex/sections/results.tex
update variation section, reorganise mass transfer
floor feedback: results

@@
-Based on our fiducial simulations, we expect that a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (see Table~\ref{tab:detection_rates} for confidence intervals).
+Based on our fiducial model (described in App~\ref{app:fiducial_physics}), we expect that a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (see Table~\ref{tab:detection_rates} for confidence intervals).
 In this section we discuss the properties of the detectable sources based on our fiducial simulation.
-%We first show the distribution of the sources together with the sensitivity curve in Section~\ref{sec:dcos_on_sc}, before exploring the parameter distributions for detectable sources in Section~\ref{sec:fiducial_distributions} and the measurement uncertainties in Section.~\ref{sec:measurement_uncertainties}.
+
 \subsection{The LISA sensitivity curve and the population of detectable sources}\label{sec:dcos_on_sc}
@@
 We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Fig.~\ref{fig:dcos_on_sc} for all sources combined in the top panel and separated by type in the three lower panels.
-For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines), assuming they are circular and the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
+For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines).
+For each line we assume the binary is circular and has the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
 We observe several features worthwhile discussing, some that earlier studies have touched upon (see Sec.~\ref{sec:compare_studies}), as well as some new findings related to eccentricity.
@@
 Their orbits shrink as they lose angular momentum in the form of gravitational waves leading to an increase of their orbital frequency until they become detectable.
-Even though the signal emitted by a more compact binary is stronger, such systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates.
+Even though the signal emitted by a more compact binary is stronger, such systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates \citep{Peters+1964}.
 The vertical grid lines show these rapidly decreasing inspiral times at increasing frequencies.
@@
 Unlike ground-based detectors, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
-In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting the less massive black holes.
-The mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass.
+In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting in less massive black holes.
+For these reasons, the mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass.
 Since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription (applied in this work) does not produce a mass gap between neutron stars and black holes.
@@
 The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
-The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae or from low mass stars.
-We set the remnant mass for any system formed through ECSN to $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{sec:fiducial_physics}).
+The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae or from low mass stars in our simulations.
+We set the remnant mass for any system formed through ECSN to $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{app:fiducial_physics}).
 The remnant mass prescription that we use gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
@@
 
-In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and distribution peaks around $q = 0.4$.
+In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$.
 The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
@@
 Around two thirds of detectable BHNSs experience at least one common envelope event, whilst the last third are formed through only stable mass transfer.
-The first peak at $q = 0.18$ is from systems that experience at least one CE and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
-Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arise from the fraction of the population that underwent only stable mass transfer.
+The first peak at $q = 0.18$ is from systems that experience at least one common envelope and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
+Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arise from the fraction of the population that underwent only stable mass transfer phases.
 The stability of mass transfer is strongly dependent on the mass ratio and thus these systems have a bias for more equal mass ratio systems, leading to a peak at higher $q$.
@@
 Moreover, we find that $\BHBHHighlyEccentric{}$, $\BHNSHighlyEccentric{}$ and $\NSNSHighlyEccentric{}$ of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
-At this eccentricity the majority of the gravitational wave power is emitted in higher harmonics above the orbital frequency and thus the signal would appear at higher frequencies in LISA.
+At this eccentricity the majority of the gravitational wave power is emitted in higher harmonics above the orbital frequency \citep[Eq.~20]{Peters+1963} and thus the signal would appear at higher frequencies in LISA.
 
-\paragraph{Time since formation} The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see Fig.~\ref{fig:galaxy_schematic}).
+\paragraph{Time since formation} The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see top left panel of Fig.~\ref{fig:galaxy_schematic}).
 In contrast, we find that the \textit{detectable} systems are primarily formed recently, with the majority formed in the past $2 \unit{Gyr}$, in addition to a tail of systems out to earlier times.
@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
-In the first panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems.
+In the top panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems.
 Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
@@
 Although it is useful to investigate the underlying parameters of the detectable population, it is also important to consider what LISA will actually \textit{measure} during a detection.
+To this end, we discuss the most relevant uncertainties below.
 
@@
 We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
-We find that approximately $\BHBHChirpMassMeasureable{}$ BHBHs, $\BHNSChirpMassMeasureable{}$ BHNSs and $\NSNSChirpMassMeasureable{}$ NSNSs have measurable chirp masses (as indicated by the shaded region).
+We find that approximately $\BHBHChirpMassMeasureable{}$ BHBHs, $\BHNSChirpMassMeasureable{}$ BHNSs and $\NSNSChirpMassMeasureable{}$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}).
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
@@
 Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-Shaded region indicates region with unmeasureable chirp mass.}
+The shaded region indicates region with unmeasureable chirp mass.}
     \label{fig:m_c_unc}
@@
 \subsubsection{Sky localisation}
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{angular_resolution_4yr.pdf}
+    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
+    \label{fig:ang_res}
+\end{figure}
+
 We quantify the sky localisation of a source by calculating its angular resolution.
@@
 From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 degrees.
-The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).
+The size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).
 Applying this to the plot shows that about 10-20\% of DCOs can be covered by a single pointing of SKA.
@@
 We will discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\columnwidth]{angular_resolution_4yr.pdf}
-    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
-    \label{fig:ang_res}
-\end{figure}

### 2021-07-29 paper/tex/sections/variations.tex
floor feedback: results

@@
 The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{sec:fiducial_physics}.
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
 See Sec.~\ref{sec:detection_rate_analysis} for a discussion.

### 2021-07-29 paper/tex/sections/variations.tex
floor feedback: variations

@@
 
-The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the expected detections in most models staying within 25\% of the fiducial rate.
-In contrast, the BHNS detection rate is very sensitive to all changes in binary physics assumptions, varying across two orders of magnitude in the middle pane of Figure~\ref{fig:detection_rates}.
+The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the mean detections in three quarters of our models staying within 25\% of the fiducial rate.
+In contrast, the BHNS detection rate is very sensitive to all changes that we made in our binary physics assumptions, varying across two orders of magnitude in the middle panel of Figure~\ref{fig:detection_rates}.
 Finally, in the last panel of Figure~\ref{fig:detection_rates} we show that the NSNS detection is only moderately sensitive to certain changes in physics assumptions, varying by up to an order of magnitude, whilst showing no change for many models.
@@
 This is because a large fraction of NSs (and the majority of NSNS binaries are formed) through case BB mass transfer.
-Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic CE scenario by default.
+Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common envelope (CE) scenario by default.
 

### 2021-07-29 paper/tex/sections/discussion.tex
Floor feedback: discussion

@@
 
-\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ and should not be extrapolated outside this region.
+\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ (due to the limits of the underlying models in \citet{Hurley+2000}) and should not be extrapolated outside this region.
 However, in the Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.

### 2021-07-29 paper/tex/paper.tex
floor feedback: abstract
floor feedback: software

@@
 
-\keywords{LISA, gravitational waves, black hole, neutron star, binary}
+\keywords{gravitational waves, LISA, black hole, neutron star, binary}
 
@@
 
-\software{COMPAS (version 02.12.00) \url{http://github.com/TeamCOMPAS/COMPAS}.
-\citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}, \texttt{Python} available from \url{python.org}, matplotlib \citep{Hunter+2007},  \texttt{NumPy} \citep{vanderWalt+2011},
-Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.}
+\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
+Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}.
+The simulations performed in this work were simulated with a COMPAS version that predates the publicly available code.
+Our version of the code is most similar to version 02.13.01 of the publicly available COMPAS code.
+Requests for the original code can be made to Floor Broekgaarden.
+The authors used {\sc{STROOPWAFEL}} from \citep{Broekgaarden+2019}, publicly available at \url{https://github.com/FloorBroekgaarden/STROOPWAFEL}\footnote{For the latest pip installable version of STROOPWAFEL please contact Floor Broekgaarden.}.
+The authors also made use of Python from the Python Software Foundation.
+Python Language Reference, version 3.6.
+Available at \url{http://www.python.org}.
+In addition the following Python packages were used: matplotlib \citep{Hunter+2007},  {NumPy} \citep{vanderWalt+2011}, SciPy \citep{Virtanen+2020}, Jupyter Lab \citep{Kluyver+2016}, seaborn \citep{Waskom+2020}, h5py \citep{Collette+2021} and Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.
+This research has made use of NASA’s Astrophysics Data System Bibliographic Services.
+We also made use of the computational facilities from the Harvard FAS Research Computing cluster.}
 

### 2021-07-29 paper/tex/sections/appendix.tex
change all figure names to organise

@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/random_simple_galaxy.png}
+    \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
     \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/mBH_simple_mw_variation.pdf}
+    \includegraphics[width=\columnwidth]{../figures/fig12_mBH_simple_mw_variation.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.
@@
     \centering
-    \includegraphics[width=\textwidth]{dcos_on_sc_eccentric_colours.png}
+    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
     \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
@@
     \centering
-    \includegraphics[width=\textwidth]{formation_channels.pdf}
+    \includegraphics[width=\textwidth]{fig14_formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.

### 2021-07-29 paper/tex/sections/results.tex
change all figure names to organise

@@
     \centering
-    \includegraphics[width=\textwidth]{2_dcos_on_sc.png}
+    \includegraphics[width=\textwidth]{fig2_dcos_on_sc.png}
     \caption{The LISA sensitivity curve is shown together with the density distribution of the characteristic strain and the dominant frequency for all detectable sources in our simulations (top) and separated by type (bottom).
@@
     \centering
-    \includegraphics[width=\textwidth]{4_detectable_properties_4yr.pdf}
+    \includegraphics[width=\textwidth]{fig3_detectable_properties_4yr.pdf}
     \caption{Properties of detectable systems for a 4-year LISA mission in our fiducial model.
@@
     \centering
-    \includegraphics[width=\columnwidth]{detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=\columnwidth]{galaxy_density_distribution.png}
+    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
+    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
     \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
@@
     \centering
-    \includegraphics[width=\columnwidth]{chirp_mass_uncertainty_4yr.pdf}
+    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
     \caption{Cumulative distribution function for error on the chirp mass.
@@
     \centering
-    \includegraphics[width=\columnwidth]{angular_resolution_4yr.pdf}
+    \includegraphics[width=\columnwidth]{fig6_angular_resolution_4yr.pdf}
     \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}

### 2021-07-29 paper/tex/sections/results.tex
move figures around into more sensible positions

@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
+    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
+    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
+\textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs.
+We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights.
+The coloured lines show the 75\% contour for each of the individual DCO types.
+The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
+    \label{fig:detectable_distance_dist}
+\end{figure}
+
 In the top panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems.
@@
 
-\begin{figure}[thb]
-    \centering
-    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
-    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
-\textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs.
-We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights.
-The coloured lines show the 75\% contour for each of the individual DCO types.
-The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
-    \label{fig:detectable_distance_dist}
-\end{figure}
-
 \subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
@@
 \subsubsection{Chirp mass uncertainty}
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
+    \caption{Cumulative distribution function for error on the chirp mass.
+Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+The shaded region indicates region with unmeasureable chirp mass.}
+    \label{fig:m_c_unc}
+\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
-    \caption{Cumulative distribution function for error on the chirp mass.
-Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-The shaded region indicates region with unmeasureable chirp mass.}
-    \label{fig:m_c_unc}
-\end{figure}
-
 \subsubsection{Sky localisation}

### 2021-07-29 paper/tex/sections/appendix.tex
move figures around into more sensible positions
add quick links to plots

@@
 \end{equation}
-where $w_i$ is the adaptive importance sampling weight assigned to the binary by STROOPWAFEL, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is a step function that is only $1$ when the binary is a target and otherwise $0$.
+where $w_i$ is the binary's adaptive importance sampling weight assigned, $N_{\rm binaries, Z}$ is the number of binaries at metallicity $Z$ in our sample and $\theta_{\rm target, i}$ is only $1$ when the binary is a target and otherwise $0$.
 
@@
 where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
-These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from and the rest is contained in lower mass stars that are not relevant for forming the DCOs studies in this paper.
+These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from.
 
@@
     \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
-    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.}
+    \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
     \label{fig:simple_mw}
@@
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.
-Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.}
+Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:bh_mass_simple_mw}
@@
     \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type.
-Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.}
+Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
     \begin{tabular}{cl|lll|lll}
@@
     \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
-We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.}
+We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
     \label{fig:dcos_on_sc_ecc_col}
@@
 
-\begin{figure}[thb]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{fig14_formation_channels.pdf}
+    \includegraphics[height=0.85\textheight]{fig14_formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
@@
 The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
-\todo{Update H, I, J, K, T}}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_formation_channels.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.
+\todo{Update R and T}}
     \label{fig:formation_channels}

### 2021-07-29 paper/tex/sections/comparisons.tex
change all figure names to organise
add quick links to plots

@@
     \centering
-    \includegraphics[width=\textwidth]{5_compare_dco_1.png}
+    \includegraphics[width=\textwidth]{fig10_1_compare_dco.png}
 
@@
 
-    \includegraphics[width=\textwidth]{5_compare_dco_2.png}
+    \includegraphics[width=\textwidth]{fig10_2_compare_dco.png}
     \caption{A table comparing previous studies of a similar nature to this work.
-The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.}
+The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_w_compare_dco.png}{\faFileImage}.}
     \label{fig:previous_studies}

### 2021-07-29 paper/tex/sections/methods.tex
change all figure names to organise
move figures around into more sensible positions
add quick links to plots

@@
 We evolve the orbit of each DCO in a Milky Way instance up to the LISA mission and calculate the detection rate for that instance using the methods presented in Section~\ref{sec:gw_detection}.
+
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{fig1_galaxy_diagram.png}
+    \caption{A schematic illustrating how we model the Milky Way.
+The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
+The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
+The top panel shows a side-on view and the bottom panel a face-on view.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig1_galaxy_diagram.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+    \label{fig:galaxy_schematic}
+\end{figure*}
 
@@
 Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{1_galaxy_diagram.png}
-    \caption{A schematic illustrating how we model the Milky Way.
-The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
-The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
-The top panel shows a side-on view and the bottom panel a face-on view.}
-    \label{fig:galaxy_schematic}
-\end{figure*}
 

### 2021-07-29 paper/tex/sections/results.tex
add quick links to plots

@@
 LISA verification binaries are overplotted in the top panel (star symbols).
-See also Fig.~\ref{fig:dcos_on_sc_ecc_col} and Sec.~\ref{sec:dcos_on_sc} for a discussion.}
+See also Fig.~\ref{fig:dcos_on_sc_ecc_col} and Sec.~\ref{sec:dcos_on_sc} for a discussion.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig2_dcos_on_sc.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
     \label{fig:dcos_on_sc}
@@
 The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions.
-See Sec.~\ref{sec:fiducial_distributions} for a discussion.}
+See Sec.~\ref{sec:fiducial_distributions} for a discussion.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:fiducial_pdf_distributions}
@@
 The coloured lines show the 75\% contour for each of the individual DCO types.
-The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.}
+The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
     \label{fig:detectable_distance_dist}
@@
 Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-The shaded region indicates region with unmeasureable chirp mass.}
+The shaded region indicates region with unmeasureable chirp mass.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:m_c_unc}
@@
     \includegraphics[width=\columnwidth]{fig6_angular_resolution_4yr.pdf}
-    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.}
+    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:ang_res}

### 2021-07-29 paper/tex/sections/variations.tex
change all figure names to organise
add quick links to plots

@@
     \centering
-    \includegraphics[width=\textwidth]{3_dco_detections.pdf}
+    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
     \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
@@
 See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\todo{Will add H, I, J, R, T once Floor says that they are done}}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.
+\todo{Will add R, T once Floor says that they are done}}
     \label{fig:detection_rates}
@@
     \centering
-    \includegraphics[width=\columnwidth]{lower_mass_gap_rapid_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig8_lower_mass_gap_rapid_variation.pdf}
     \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
-Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}}
+Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:lower_mass_gap_variation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{ecc_low_kick_variation.pdf}
-    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}. For comparison, we show the mean distribution for the fiducial model as dashed lines.}
+    \includegraphics[width=\columnwidth]{fig9_ecc_low_kick_variation.pdf}
+    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}.
+For comparison, we show the mean distribution for the fiducial model as dashed lines.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:ecc_low_kick_variation}

### 2021-07-30 paper/tex/sections/abstract.tex
add hyphen to CE

@@
 We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with an empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
-We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common envelope, supernova and wind mass loss physics.
+We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics.
 We predict that for a 4(10)-year mission, LISA will (typically) detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.

### 2021-07-30 paper/tex/sections/appendix.tex
add hyphen to CE

@@
 
-\textit{Common Envelope:} A common envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
+\textit{Common Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
 We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
 For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
-This follows the `pessimistic' common envelope scenario \citep[c.f.][]{Belczynski+2007}.
-We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common envelope phase as we treat these as failed common envelope ejections, likely leading to a stellar merger.
+We assume that any Hertzsprung gap donor stars that initiate a common-envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
+This follows the `pessimistic' common-envelope scenario \citep[c.f.][]{Belczynski+2007}.
+We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common-envelope phase as we treat these as failed common-envelope ejections, likely leading to a stellar merger.
 
@@
 \subsection{Model variations} \label{sec:variation_assumptions}
-In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
+In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common-envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{app:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
@@
 
-Models \modRangeCE{} focus on altering the common envelope physics.
-We change the common envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
-In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common envelope events, thereby following the `optimistic' common envelope scenario.
+Models \modRangeCE{} focus on altering the common-envelope physics.
+We change the common-envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
+In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common-envelope events, thereby following the `optimistic' common-envelope scenario.
 We combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
@@
     \caption{A description of the \nModels{} binary population synthesis models used in this study.
-\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common envelope physics , \modRangeSN{} change supernova physics and \modRangeML{} change wind mass loss \citep[c.f.][Table 2]{Broekgaarden+2021}.}
+\modFid{} is the fiducial model, \modRangeMT{} change mass transfer physics, \modRangeCE{} change common-envelope physics , \modRangeSN{} change supernova physics and \modRangeML{} change wind mass loss \citep[c.f.][Table 2]{Broekgaarden+2021}.}
     \label{tab:physics_variations}
@@
 Channels are described in detail in \citet{Broekgaarden+2021}.
-The classic, single core CEE and double core CEE channels all require at least one common envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
+The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_formation_channels.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.

### 2021-07-30 paper/tex/sections/introduction.tex
add hyphen to CE

@@
 
-For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which double compact objects are formed following common envelope ejection or a phase of highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
+For the purposes of this investigation, we consider the `classical' isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Smarr+1976,Srinivasan+1989,Kalogera+2007,Belczynski+2016} in which double compact objects are formed following common-envelope ejection or a phase of highly non-conservative mass transfer \citep{Heuvel+2011, vandenHeuvel+2017}.
 We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.

### 2021-07-30 paper/tex/sections/results.tex
add hyphen to CE

@@
 Moreover, the mass ratio distribution is bimodal, where the two peaks arise from two distinct formation scenarios.
-Around two thirds of detectable BHNSs experience at least one common envelope event, whilst the last third are formed through only stable mass transfer.
-The first peak at $q = 0.18$ is from systems that experience at least one common envelope and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
+Around two thirds of detectable BHNSs experience at least one common-envelope event, whilst the last third are formed through only stable mass transfer.
+The first peak at $q = 0.18$ is from systems that experience at least one common-envelope and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
 Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arise from the fraction of the population that underwent only stable mass transfer phases.
@@
 
-The peak at recent times is due to the fact that most binaries in our sample are formed with merger times on the order of a couple of Gyr (since most form through a common envelope phase that significantly tightens the binary).
+The peak at recent times is due to the fact that most binaries in our sample are formed with merger times on the order of a couple of Gyr (since most form through a common-envelope phase that significantly tightens the binary).
 For a binary to be in the LISA band and detectable it must be near the end of its inspiral and so LISA will be most sensitive to sources that were formed a couple of Gyr ago.
@@
 In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy.
-We see that most sources are concentrated in the Galactic center, with a bias towards to the position of the Sun.
+We see that most sources are concentrated in the Galactic center, with a bias towards the position of the Sun.
 Yet we also show that systems are detectable out to the edges of the galaxy.

### 2021-07-30 paper/tex/sections/variations.tex
add hyphen to CE

@@
 However, this contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
-Moreover, one must consider that most of these DCOs are formed through a common envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018}.
+Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018}.
 
 In contrast, for the NSNSs, the detection rate increases with increasing $\beta$.
-This is for two main reasons: firstly the ejection of a common envelope is less problematic for NSNSs as they are less massive \citep[e.g.][]{Kruckow+2018}.
+This is for two main reasons: firstly the ejection of a common-envelope is less problematic for NSNSs as they are less massive \citep[e.g.][]{Kruckow+2018}.
 Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
@@
 This is because a large fraction of NSs (and the majority of NSNS binaries are formed) through case BB mass transfer.
-Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common envelope (CE) scenario by default.
+Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common-envelope (CE) scenario by default.
 
@@
 
-\subsubsection{Common envelope variation trends}\label{sec:detection_rate_CE_trends}
+\subsubsection{Common-envelope variation trends}\label{sec:detection_rate_CE_trends}
 

### 2021-07-30 paper/tex/sections/introduction.tex
add decadal survey citation

@@
 
-The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves.
+The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017, Colpi+2019}) will provide observations in an entirely new regime of gravitational waves.
 LISA will observe at lower frequencies ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) than ground-based detectors and so will enable the study of sources that are imperceptible by ground-based detectors, such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.

### 2021-07-30 paper/tex/sections/appendix.tex
fix equation b6 description

@@
 
-\textit{Common Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
+\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
 We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
@@
 \begin{equation}
-    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} \sum_{i=1}^{N_{\rm binaries, Z}} w_i,
+    M_{\rm SF, Z} = \frac{\avg{m}_{\rm COMPAS, Z}}{f_{\rm trunc}} N_{\rm binaries, Z},
 \end{equation}
-where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in our sample and $f_{\rm trunc}$ is the fraction of the total stellar mass from which COMPAS samples, given its truncated mass and separation ranges (see Section \ref{sec:COMPAS_explained}).
+where $\avg{m}_{\rm COMPAS}$ is the average star forming mass of a binary in a simulation using our cutoffs (discussed in Section~\ref{sec:COMPAS_explained}) and $f_{\rm trunc}$ is the fraction of the total stellar mass from which our COMPAS simulations sample, given our truncated mass and separation ranges (see Section~\ref{sec:COMPAS_explained}).
 These truncations mean that only $f_{\rm trunc} \approx 0.17$ of the stellar mass in the galaxy is sampled from.

### 2021-07-30 paper/tex/sections/results.tex
floor feedback: variations (part II)

@@
 The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
-The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae or from low mass stars in our simulations.
+The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae (ECSN) or from low mass stars in our simulations.
 We set the remnant mass for any system formed through ECSN to $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{app:fiducial_physics}).

### 2021-07-30 paper/tex/sections/variations.tex
floor feedback: variations (part II)

@@
 However, this contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
-Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018}.
+Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.
 
@@
 Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) has little effect on the BHBH detection rate whilst moderately and drastically decreasing the detection rates of BHNSs and NSNSs respectively.
-This is because a large fraction of NSs (and the majority of NSNS binaries are formed) through case BB mass transfer.
+This is because a large fraction of NSs (and the majority of NSNS binaries) are formed through case BB mass transfer.
 Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common-envelope (CE) scenario by default.
@@
 A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events.
-Therefore, though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
-This increase is less significant for BHNSs since their progenitors tend to be less massive and thus initiate CE events during the Hertzsprung gap less frequently.
+This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased.
+Therefore, we find that, though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
+
+The progenitors of BHNSs tend to be less massive than those of BHBHs.
+Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase.
+This explains why the relative increase in model \modOpt{} compared to the fiducial model is lower for BHNSs.
 For the same reason, the NSNS detection rate shows little significant change.
@@
 A large fraction of the NSs in our sample are formed through ECSN, in which case their masses are set to $1.26 \unit{M_\odot}$ regardless of the remnant mass prescription.
-Secondly, the majority of the remaining NSs have such low progenitor masses that they are set to the lowest remnant mass in the prescription ($1.28 \unit{M_\odot}$ for the delayed prescription and $1.1 \unit{M_\odot}$).
+Secondly, the majority of the remaining NSs have such low progenitor masses that they are set to the lowest remnant mass in the prescription ($1.28 \unit{M_\odot}$ for the delayed prescription and $1.1 \unit{M_\odot}$ for the rapid prescription).
 This means that changing the upper portion of the mass range of NSs in the remnant mass prescription has little effect.
@@
 
-Additionally, we find that not implementing PISN and PPISN (model \modNoPISN{}) has no effect on the results for any DCO type.
+Additionally, we find that not implementing pair-instability supernovae (PISN) pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the results for any DCO type.
 This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.
@@
 This increase is least prominent for BHBHs since their increased mass mean that disruptions are less frequent than, for instance, in NSNSs.
-It is also notable that \citet{Broekgaarden+2021} found that these two models best matched the detection rates from LIGO.
+It is also notable that these two models best match the detection rates from LIGO (Broekgaarden et al.\ in prep).
 Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.

### 2021-07-30 paper/tex/sections/comparisons.tex
floor feedback: discussion (part II) + comparisons

@@
 This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
-As we show in Appendix~\ref{app:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.
+As we show in Appendix~\ref{app:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.\\
+
+\noindent{}Overall, since the work of \citet{Nelemans+2001}, in additions to the LISA mission specifications, the methods that we use to simulate binaries and the Milky Way have all changed significantly.
+We now predict that LISA detections of these massive DCOs are dominated by BHBHs, rather than NSNSs, whilst the absolute detection rates for BHBHs and BHNSs are much higher.
+Further studies in this area could improve on this work by including the effects of systemic kicks on the position of systems in the Milky Way and accounting for contributions from other formation channels.

### 2021-07-30 paper/tex/sections/discussion.tex
add hyphen to CE
floor feedback: discussion (part II) + comparisons

@@
-\subsection{Identification of GW sources}
+In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}).
+
+\subsection{Identification of GW sources}\label{sec:identify_sources}
 It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
-
-The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
+The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
 It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
@@
 The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$.
-Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + 2 \Delta \mathcal{M}_c$ must not be a WDWD.
+Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is calculated using Eq.~\ref{eq:chirp_mass_uncertainty}).
 We find that for the detectable population of a 4(10)-year LISA mission, \BHBHAboveMaxWDWDFourPerc{}(\BHBHAboveMaxWDWDTenPerc{})\% of BHBHs, \BHNSAboveMaxWDWDFourPerc{}(\BHNSAboveMaxWDWDTenPerc{})\% of BHNSs and \NSNSAboveMaxWDWDFourPerc{}(\NSNSAboveMaxWDWDTenPerc{})\% of NSNSs satisfy this condition.
@@
 Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
-For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit (and thus \textit{must} contain or not contain a BH component respectively) by more than $2 \Delta \mathcal{M}_c$ is \BHBHEitherBHOrNSFourPerc{}(\BHBHEitherBHOrNSTenPerc{})\% for BHBHs, \BHNSEitherBHOrNSFourPerc{}(\BHNSEitherBHOrNSTenPerc{})\% for BHNSs and \NSNSEitherBHOrNSFourPerc{}(\NSNSEitherBHOrNSTenPerc{})\% of NSNSs, which in terms of absolute detections is \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) for BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) for BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) for NSNSs.
+For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit (and thus \textit{must} contain or not contain a BH component respectively) by more than $\Delta \mathcal{M}_c$ is \BHBHEitherBHOrNSFourPerc{}(\BHBHEitherBHOrNSTenPerc{})\% for BHBHs, \BHNSEitherBHOrNSFourPerc{}(\BHNSEitherBHOrNSTenPerc{})\% for BHNSs and \NSNSEitherBHOrNSFourPerc{}(\NSNSEitherBHOrNSTenPerc{})\% of NSNSs, which in terms of absolute detections is \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) for BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) for BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) for NSNSs.
 
 For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency, mass ratio and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}).
-This method would pose a challenge however as it would likely only rule out some DCO types as the source of the signal rather than provide strong evidence of the exact type.
+This method would pose a challenge however as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.
 
@@
 In Section~\ref{sec:pulsar_matching} we consider the possibility of detecting a pulsar within a BHNS or NSNS system.
-This could be used to identify the type of the source, however it is unlikely that a large fraction of the population will contain pulsars that are beaming towards the Earth.
+This could be used to identify the type of the source.
 
@@
 Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA.
-By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) will satisfy this constraint.
+By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) DCOs will satisfy this constraint.
 
@@
 In order to assess the efficacy of this method, we would need to know the probability that two random binary pulsars would have orbital frequencies and chirp masses close enough that one could not tell which pulsar matches the LISA detection.
-This would require simulating the SKA population of pulsars with a code such as PSRPOPPy to find the frequency and chirp mass distribution, which is beyond the scope of this paper.
-However, the uncertainty on the orbital frequency of a binary on the detection threshold ($\rho = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
+This would require simulating the SKA population of pulsars with a code such as PSRPOPPy \citep{Bates+2014} to find the frequency and chirp mass distribution, which is beyond the scope of this paper.
+However, the uncertainty on the orbital frequency of a binary on the detection threshold (${\rm SNR} = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
 Therefore, we expect that SKA could likely isolate the correct binary pulsar to match to a LISA detection even when several are present in the sky localisation region.
@@
 \subsection{Caveats}\label{sec:caveats}
-\textit{Binary fraction and other normalisation choices}: For the normalisation of the detection rate we conservatively chose to set the binary fraction of all stars to 50\%.
+\textit{Binary fraction and other normalisation choices}: The choice of the binary fraction has a strong effect on our results.
+For the normalisation of the detection rate we conservatively choose to set the binary fraction of all stars to 50\%.
 The binary fraction is uncertain and not well constrained, though we know it is higher for more massive stars \citep[e.g.][]{Sana+2012}.
-However, the choice of the binary fraction has a strong effect on our results.
 Increasing it to 70\% and 100\% would increase our expected detection rates for every physics variation by 30\% and 67\% respectively.
-We assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results.
-We highlight the uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change drastically as our understanding shifts, however changes to this normalisation would affect every variation equally and so the trends across variations are more robust.
+Moreover, we assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results.
+We highlight this uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change drastically as our understanding shifts.
+However, changes to this normalisation would affect every variation equally and so the trends across variations are more robust.
 
@@
 COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
-Much of the underlying physics is uncertain, such as the common envelope evolution and mass transfer physics.
+Much of the underlying physics is uncertain, such as the common-envelope evolution and mass transfer physics.
 We attempt to understand the importance of these assumptions by varying over many different physics assumptions.

### 2021-07-30 simulation/src/simulate_DCO_detections.py
allow extended missions (10 year)

@@ -26,13 +26,14 @@ def usage():
 def main():
     # get command line arguments and exit if error
     try:
-        opts, _ = getopt.getopt(sys.argv[1:], "hi:o:n:t:fs", ["help",
+        opts, _ = getopt.getopt(sys.argv[1:], "hi:o:n:t:fse", ["help",
                                                              "input=",
                                                              "output=",
                                                              "loops=",
                                                              "binary-type=",
                                                              "opt-flag",
-                                                             "simple-mw"])
+                                                             "simple-mw",
+                                                             "extended-mission"])
     except getopt.GetoptError as err:
         print(err)
         usage()
@@ -45,6 +46,7 @@ def main():
     binary_type = "BHNS"
     pessimistic = True
     use_simple_mw = False
+    t_obs = 4 * u.yr
 
     # change defaults based on input
     for option, value in opts:
@@ -63,6 +65,8 @@ def main():
             pessimistic = False
         if option in ("-s", "--simple-mw"):
             use_simple_mw = True
+        if option in ("-e", "--extended-mission"):
+            t_obs = 10 * u.yr
 
     # open COMPAS file
     with h5.File(input_filepath, "r") as COMPAS_file:
@@ -191,8 +195,9 @@ def main():
         a_LISA = a_LISA[:, -1]
         f_orb_LISA = f_orb_LISA[:, -1]
 
-        sources = lw.source.Source(m_1=m_1, m_2=m_2, ecc=e_LISA, dist=dist, f_orb=f_orb_LISA)
-        snr = sources.get_snr(verbose=True)
+        sources = lw.source.Source(m_1=m_1, m_2=m_2, ecc=e_LISA, dist=dist, f_orb=f_orb_LISA,
+                                   sc_params={"t_obs": t_obs})
+        snr = sources.get_snr(t_obs=t_obs)
 
         detectable = snr > SNR_CUTOFF
         n_detect = len(snr[detectable])

### 2021-07-30 paper/tex/sections/discussion.tex
add ysc caveat

@@
 
-\textit{Halo and globular clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo or globular clusters.
+\textit{Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters.
 \citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
 The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates.
+Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.
 

### 2021-07-30 simulation/slurm/combineHdf5.py
remove combination hdf5 stuff

@@ -1,70 +1,0 @@
-import numpy as np
-import h5py as h5
-import sys
-import getopt
-
-PATH_TO_FILES = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
-
-def combineMetallicities(zlist, dirname):
-    #-- Input files to be combined
-
-    print('combining the COMPASOutput files for the simulation in directory ', dirname)
-    z0 = zlist[0]
-    print(z0, 'z0')
-    h5File_0 = h5.File(PATH_TO_FILES + str(dirname) + "/Z_" + str(z0) + "/STROOPWAFELcombined/COMPASOutput.h5", 'r')
-
-    groups = list(h5File_0.keys())
-    print(groups)
-
-    #-- Output file
-    h5File3 = h5.File(PATH_TO_FILES + str(dirname) + "/COMPASOutputCombined.h5", 'w')
-    for group in groups:
-
-        #-- Create a group in the output
-        print('now at', group)
-        if group=='pulsarEvolution':
-            print(group)
-        else:
-            h5File3.create_group(group)
-
-            datasets = list(h5File_0[group].keys())
-
-            #-- Loop through datasets, combine and write
-            for dataset in datasets:
-                combined_dataset = h5File_0[group][dataset]
-                for ind, z in enumerate(zlist[1:]):
-                    print('at metallicity = ', z)
-
-                    ###-- Concatenate datasets
-                    h5File_z = h5.File(PATH_TO_FILES + str(dirname) +"/Z_" + str(z) + "/STROOPWAFELcombined/COMPASOutput.h5", 'r')
-                    combined_dataset = np.concatenate([combined_dataset, h5File_z[group][dataset]])
-
-                #-- Save datasets
-                h5File3[group][dataset] = combined_dataset
-
-# COMBINED HIGH Z AND OLD FOR TOM: 
[…]

### 2021-07-30 simulation/slurm/generate_combine_scripts.py

@@ -1,36 +1,0 @@
-import sys
-sys.path.append("../src/")
-from variations import variations
-
-
-def create_file(file):
-    script_file = "scripts/combine_{}.sh".format(file)
-
-    lines = []
-    lines.append("#!/bin/bash\n")
-    lines.append("#SBATCH -J combine_{}\n".format(file))
-    lines.append("#SBATCH -n 6\n")
-    lines.append("#SBATCH -N 1\n")
-    lines.append("#SBATCH -p serial_requeue\n")
-    lines.append("#SBATCH --mem 12000\n")
-    lines.append("#SBATCH -t 00-3:00\n")
-    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/combine_{}_%A_%a.out\n".format(file))
-    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/combine_{}_%A_%a.err\n".format(file))
-    lines.append("#SBATCH --mail-user thomas.wagg@cfa.harvard.edu\n")
-    lines.append("#SBATCH --mail-type ALL\n")
-
-    lines.append("module load Anaconda3/2020.11\n")
-    lines.append("source activate lisa\n")
-
-    main_line = 'python /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/combineHdf5.py --dirname {}'.format(file)
-    lines.append(main_line)
-
-    with open(script_file, "w") as f:
-        f.writelines(lines)
-
-
-for v in variations:
-    if v["file"] in ["fiducial", "alpha0_1", "ccSNkick_100km_s", "ccSNkick_30km_s",
-                     "maxNSmass2_0", "maxNSmass3_0", "noPISN", "rapid",
-                     "wolf_rayet_multiplier_0_1", "wolf_rayet_multiplier_5"]:
-        create_file(v["file"])

### 2021-07-30 simulation/slurm/generate_scripts.py
generate all scripts

@@ -3,19 +3,20 @@ sys.path.append("../src/")
 from variations import variations
 
 
-def create_file(dco_type, file, simple_mw=False):
-    script_file = "scripts/{}_{}{}.sh".format(dco_type, file, "_simplemw" if simple_mw else "")
+def create_file(dco_type, file, simple_mw=False, extend_mission=False):
+    extra = "_simplemw" if simple_mw else "_10yr" if extend_mission else ""
+    script_file = "scripts/{}_{}{}.sh".format(dco_type, file, extra)
 
     lines = []
     lines.append("#!/bin/bash\n")
-    lines.append("#SBATCH -J {}_{}{}\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
+    lines.append("#SBATCH -J {}_{}{}\n".format(dco_type, file, extra))
     lines.append("#SBATCH -n 6\n")
     lines.append("#SBATCH -N 1\n")
     lines.append("#SBATCH -p serial_requeue\n")
     lines.append("#SBATCH --mem 6000\n")
     lines.append("#SBATCH -t 00-10:00\n")
-    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.out\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
-    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.err\n".format(dco_type, file, "_simplemw" if simple_mw else ""))
+    lines.append("#SBATCH -o /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.out\n".format(dco_type, file, extra))
+    lines.append("#SBATCH -e /n/home09/twagg/detecting-DCOs-in-LISA/simulation/slurm/logs/{}_{}{}_%A_%a.err\n".format(dco_type, file, extra))
     lines.append("#SBATCH --mail-user thomas.wagg@cfa.harvard.edu\n")
     lines.append("#SBATCH --mail-type ALL\n")
 
@@ -26,6 +27,9 @@ def create_file(dco_type, file, simple_mw=False):
 
     if simple_mw:
[…]

### 2021-07-30 simulation/slurm/run_all_extended.sh

@@ -5,7 +5,7 @@ for type in BHBH BHNS NSNS
 do
     for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s noBHkick wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
     do
-        sbatch --array=1-50 scripts/${type}_${variation}.sh
+        sbatch --array=1-50 scripts/${type}_${variation}_10yr.sh
         sleep 1
     done
 done

### 2021-07-30 simulation/slurm/run_all_simple.sh

@@ -1,0 +1,11 @@
+rm scripts/*.sh
+python generate_scripts.py
+
+for type in BHBH BHNS NSNS
+do
+    for variation in fiducial unstableCaseBB_opt
+    do
+        sbatch --array=1-50 scripts/${type}_${variation}_simplemw.sh
+        sleep 1
+    done
+done

### 2021-07-30 simulation/slurm/run_all.sh
remove missing models

@@ -3,7 +3,7 @@ python generate_scripts.py
 
 for type in BHBH BHNS NSNS
 do
-    for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s noBHkick wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
+    for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s wolf_rayet_multiplier_0_1
     do
         sbatch --array=1-50 scripts/${type}_${variation}.sh
         sleep 1

### 2021-07-30 simulation/slurm/run_all_extended.sh

@@ -3,7 +3,7 @@ python generate_scripts.py
 
 for type in BHBH BHNS NSNS
 do
-    for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s noBHkick wolf_rayet_multiplier_0_1 wolf_rayet_multiplier_5
+    for variation in fiducial massTransferEfficiencyFixed_0_25 massTransferEfficiencyFixed_0_5 massTransferEfficiencyFixed_0_75 unstableCaseBB unstableCaseBB_opt alpha0_1 alpha0_5 alpha2_0 alpha10 optimistic rapid maxNSmass2_0 maxNSmass3_0 noPISN ccSNkick_100km_s ccSNkick_30km_s wolf_rayet_multiplier_0_1
     do
         sbatch --array=1-50 scripts/${type}_${variation}_10yr.sh
         sleep 1

### 2021-07-30 paper/tex/sections/appendix.tex
add relative rate figure

@@
 
+\subsection{Detection rates relative to fiducial model}
+\begin{figure*}[hb]
+    \centering
+    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
+    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
+The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
+    \label{fig:dcos_on_sc_ecc_col}
+\end{figure*}
+
 \clearpage
@@
     \centering
-    \includegraphics[height=0.85\textheight]{fig14_formation_channels.pdf}
+    \includegraphics[height=0.85\textheight]{fig15_formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
@@
 The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_formation_channels.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.
 \todo{Update R and T}}

### 2021-07-30 paper/tex/sections/appendix.tex
fix file extensions

@@
 Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:bh_mass_simple_mw}

### 2021-07-30 paper/tex/sections/results.tex
floor feedback: discussion (part II) + comparisons
fix file extensions

@@
 See Sec.~\ref{sec:fiducial_distributions} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig3_detectable_properties_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:fiducial_pdf_distributions}
@@
 The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
     \label{fig:detectable_distance_dist}
@@
 The shaded region indicates region with unmeasureable chirp mass.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:m_c_unc}
@@
 \begin{equation}\label{eq:chirp_mass_uncertainty}
-    \qty( \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} )^2 = \left( \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} \right)^2 + \left( \frac{3}{5} \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} \right)^2 + \left( \frac{3}{5} \frac{\Delta F(e)}{F(e)} \right)^2,
+    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)},
 \end{equation}
@@
     \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_4yr.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:ang_res}

### 2021-07-30 paper/tex/sections/variations.tex
add relative rate figure
fix file extensions

@@
 \subsubsection{Stellar wind variation trends}
-\todo{}
 
@@
 Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:lower_mass_gap_variation}
@@
 For comparison, we show the mean distribution for the fiducial model as dashed lines.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:ecc_low_kick_variation}

### 2021-07-31 paper/tex/sections/variations.tex
minor changes to variations

@@
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
-See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
+See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.
@@
 If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types.
-This is both from the natural increases from using the optimistic CE scenario (see Sec.~\ref{sec:detection_rate_CE_trends} in which we discuss model \modOpt{}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer.
+This is both from the natural increases from using the optimistic CE scenario (see discussion of model \modOpt{} in Sec.~\ref{sec:detection_rate_CE_trends}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer.
 This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.
@@
 
-\todo{Discuss $\alpha_{\rm CE}$ changes once Floor ready}
+\todo{Discuss $\alpha_{\rm CE}$ changes once I understand them (:}
 
@@
 Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase.
-This explains why the relative increase in model \modOpt{} compared to the fiducial model is lower for BHNSs.
+For these reasons, as can be seen most clearly in Fig.~\ref{fig:dco_relative_rates}, the relative increase in model \modOpt{} compared to the fiducial model is lower than BHBHs for BHNSs.
 For the same reason, the NSNS detection rate shows little significant change.
@@
 
-\todo{dicuss no BH kick when done}
-%The model with no BH kick (\modNoBH{}) is slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
+\todo{ensure this noBHkick description still applies} In model \modNoBH{} we do not give black holes natal kicks.
+Rate is higher than fiducial for BHBH and BHNS but slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
+NSNSs are unaffected as one would assume.
 

### 2021-07-31 simulation/output/combine_output.py
update combine output to work on extended missions

@@ -22,7 +22,7 @@ dtype = [("m_1", dt), ("m_2", dt), ("a_DCO", dt), ("e_DCO", dt),
 
 floor_path = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
 
-def combine_data(dco_type, variation, simple_mw=False, runs=50):
+def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, runs=50):
     full_data = None
     n_detect = np.array([], dtype=np.int)
     total_weight = np.array([], dtype=np.float)
@@ -34,6 +34,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
         # check individual file exists
         if simple_mw:
             fname = "simple_mw_{}_{}_{}.h5".format(dco_type, variations[variation]["file"], i)
+        elif extended_mission:
+            fname = "{}_{}_10yr_{}.h5".format(dco_type, variations[variation]["file"], i)
         else:
             fname = "{}_{}_{}.h5".format(dco_type, variations[variation]["file"], i)
         if isfile(fname):
@@ -56,10 +58,12 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
         else:
             missing.append(i)
 
-    # as long as there is at least one file
+    # as long as there is at least one file then try to combine
     if len(missing) != runs:
         # let the user know which ones are currently missing
-        print(variation, len(missing), missing)
+        print(variations[variation]["file"],
+              " simple mw" if simple_mw else " 10yr" if extended_mission else "",
+              " : ", len(missing), missing)
 
         # work out the formation channels
         model = variations[variation]["file"]
@@ -98,6 +102,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
         # write the rest of the files to a single file
         if simple_mw:
             fname = "../data/simple_mw_{}_{}_all.h5".format(dco_type, variations[variation]["file"])
+        elif simple_mw:
+            fname = "../data/{}_{}_10yr_all.h5".format(dco_type, variations[variation]["file"])
         else:
             fname = "../data/{}_{}_all.h5".format(dco_type, variations[variation]["file"])
         with h5.File(fname, "w") as file:
@@ -115,7 +121,8 @@ def combine_data(dco_type, variation, simple_mw=False, runs=50):
 
[…]

### 2021-07-31 simulation/output/combine_output.py
messed up write file name

@@ -61,9 +61,9 @@ def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, r
     # as long as there is at least one file then try to combine
     if len(missing) != runs:
         # let the user know which ones are currently missing
-        print(variations[variation]["file"],
-              " simple mw" if simple_mw else " 10yr" if extended_mission else "",
-              " : ", len(missing), missing)
+        print(len(missing), missing, ":",
+              variations[variation]["file"],
+              "simple mw" if simple_mw else "10yr" if extended_mission else "")
 
         # work out the formation channels
         model = variations[variation]["file"]
@@ -102,7 +102,7 @@ def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, r
         # write the rest of the files to a single file
         if simple_mw:
             fname = "../data/simple_mw_{}_{}_all.h5".format(dco_type, variations[variation]["file"])
-        elif simple_mw:
+        elif extended_mission:
             fname = "../data/{}_{}_10yr_all.h5".format(dco_type, variations[variation]["file"])
         else:
             fname = "../data/{}_{}_all.h5".format(dco_type, variations[variation]["file"])
@@ -121,8 +121,8 @@ def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, r
 
 # loop over all binary types and physics variations
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    for variation in [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 18]:
+    for variation in [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19]:
         # combine_data(dco_type, variation)
         combine_data(dco_type, variation, extended_mission=True)
-        #if variation == 0 or variation == 5:
+        # if variation == 0 or variation == 5:
         #    combine_data(dco_type, variation, simple_mw=True)

### 2021-07-31 paper/figure_notebooks/uncertainties.py
update notebooks with extended mission data

@@ -4,19 +4,17 @@ import astropy.units as u
 import legwork
 
 dco_types = ["BHBH", "BHNS", "NSNS"]
-data_folder = "../../simulation/data/"
-sim_folder = data_folder + "simulation/"
 
-def get_ecc_uncertainty(t_obs=4*u.yr, source_threshold=7, harmonic_threshold=7, model="fiducial"):
+def get_ecc_uncertainty(t_obs=4*u.yr, source_threshold=7, harmonic_threshold=7, model="fiducial", folder="../../simulation/data/simulation/", suffix=""):
     detectable_harmonics = {"BHBH": None, "BHNS": None, "NSNS": None}
     snr_uncertainty = {"BHBH": None, "BHNS": None, "NSNS": None}
     ecc_uncertainty = {"BHBH": None, "BHNS": None, "NSNS": None}
     max_harmonics = {"BHBH": None, "BHNS": None, "NSNS": None}
 
     for i, dco_type in enumerate(dco_types):
-        with h5.File(sim_folder + "{}_{}_all.h5".format(dco_type, model), "r") as f:
+        with h5.File(folder + "{}_{}{}_all.h5".format(dco_type, model, suffix), "r") as f:
             full_data = f["simulation"][...].squeeze()
-            snr_mask = full_data["snr"] * np.sqrt(t_obs / (4 * u.yr)) > source_threshold
+            snr_mask = full_data["snr"] > source_threshold
             data = full_data[snr_mask]
 
         sources = legwork.source.Source(m_1=data["m_1"] * u.Msun, m_2=data["m_2"] * u.Msun,

### 2021-07-31 paper/tex/sections/discussion.tex
add long awaited extended mission results

@@
 We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs.
-Note that although the fractions are smaller for the 10-year mission, the \textit{absolute} number of detections is still greater.
-The fraction decreases because a 10-year mission detects more `marginal' sources that are just on the cusp of the detection threshold and these sources have the worst sky localisation and thus cannot be confirmed to lie within the Galactic plane.
+Note that although the fractions are the same for the 10-year mission, the \textit{absolute} number of detections is still greater.
 
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
+We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by even more since each of the more numerous sources are better measured.
 

### 2021-07-31 paper/tex/sections/results.tex
add long awaited extended mission results

@@
 We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
-We find that approximately $\BHBHChirpMassMeasureable{}$ BHBHs, $\BHNSChirpMassMeasureable{}$ BHNSs and $\NSNSChirpMassMeasureable{}$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}).
+We find that for a 4(10)-year LISA mission, approximately $\BHBHChirpMassMeasureableFour{}(\BHBHChirpMassMeasureableTen{})$ BHBHs, $\BHNSChirpMassMeasureableFour{}(\BHNSChirpMassMeasureableTen{})$ BHNSs and $\NSNSChirpMassMeasureableFour{}(\NSNSChirpMassMeasureableTen{})$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}).
+Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.

### 2021-07-31 paper/tex/sections/appendix.tex
minor changes to variations
add 10yr nums to table (only missing 2 sims now)

@@
         \hline
-        A & Fiducial & \confinv{73.7}{8.7}{8.3} & \confinv{42.1}{6.1}{6.9} & \confinv{7.9}{2.9}{3.1}\\
-        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.6}{8.6}{8.4} & \confinv{22.3}{4.3}{4.7} & \confinv{2.9}{1.9}{2.1}\\
-        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{46.8}{6.8}{7.2} & \confinv{8.2}{3.2}{2.8} & \confinv{3.9}{1.9}{2.1}\\
-        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.8}{6.8}{7.2} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3}\\
-        E & Case BB mass transfer is always unstable & \confinv{69.0}{8.0}{8.0} & \confinv{7.2}{2.2}{2.8} & \confinv{0.2}{0.2}{0.8}\\
-        F & Model E + Model K & \confinv{153.8}{12.8}{12.2} & \confinv{147.8}{11.8}{12.2} & \confinv{18.2}{4.2}{3.8}\\
-        G & CE efficiency $\alpha = 0.1$ & \confinv{27.8}{4.8}{5.2} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8}\\
-        H & CE efficiency $\alpha = 0.5$ & \confinv{61.7}{7.7}{8.3} & \confinv{28.1}{5.1}{4.9} & \confinv{6.2}{2.2}{2.8}\\
-        I & CE efficiency $\alpha = 2.0$ & \confinv{71.6}{8.6}{8.4} & \confinv{38.1}{6.1}{5.9} & \confinv{31.1}{5.1}{5.9}\\
-        J & CE efficiency $\alpha = 10.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
-        K & HG donor stars initiating a CE survive CE & \confinv{154.1}{12.1}{12.9} & \confinv{58.9}{7.9}{8.1} & \confinv{9.6}{2.6}{3.4}\\
-        L & Fryer rapid SN remnant mass prescription & \confinv{50.2}{7.2}{6.8} & \confinv{70.0}{8.0}{8.0} & \confinv{6.6}{2.6}{2.4}\\
-        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{95.9}{9.9}{10.1} & \confinv{30.0}{5.0}{5.0} & \confinv{7.1}{3.1}{2.9}\\
-        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.1}{8.1}{7.9} & \confinv{51.7}{6.7}{7.3} & \confinv{8.2}{3.2}{2.8}\\
-        O & PISN and pulsational-PISN not implemented & \confinv{75.1}{9.1}{8.9} & \confinv{43.2}{6.2}{6.8} & \confinv{7.9}{2.9}{3.1}\\
-        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.4}{9.4}{8.6} & \confinv{86.3}{9.3}{9.7} & \confinv{15.4}{4.4}{3.6}\\
-        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.5}{9.5}{9.5} & \confinv{142.4}{12.4}{11.6} & \confinv{33.4}{5.4}{5.6}\\
-        R & Black holes receive not natal kick & \confinv{85.9}{8.9}{9.1} & \confinv{95.8}{9.8}{10.2} & \confinv{9.7}{2.7}{3.3}\\
-        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.4}{8.4}{8.6} & \confinv{33.9}{5.9}{6.1} & \confinv{8.8}{2.8}{3.2}\\
-        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{14.9}{3.9}{4.1} & \confinv{9.6}{3.6}{3.4}\\
+        A & Fiducial & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
+        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
+        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
+        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
+        E & Case BB mass transfer is always unstable & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
+        F & Model E + Model K & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
+        G & CE efficiency $\alpha = 0.1$ & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
+        H & CE efficiency $\alpha = 0.5$ & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
+        I & CE efficiency $\alpha = 2.0$ & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
+        J & CE efficiency $\alpha = 10.0$ & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
+        K & HG donor stars initiating a CE survive CE & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
+        L & Fryer rapid SN remnant mass prescription & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
+        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
+        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
+        O & PISN and pulsational-PISN not implemented & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
+        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
+        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
+        R & Black holes receive not natal kick & \confinv{133.8}{11.8}{11.2} & \confinv{159.6}{12.6}{12.4} & \confinv{16.0}{4.0}{4.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
+        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{25.3}{5.3}{4.7} & \confinv{15.6}{3.6}{4.4} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
         \hline
@@
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
-    \label{fig:dcos_on_sc_ecc_col}
+    \label{fig:dco_relative_rates}
 \end{figure*}

### 2021-08-06 paper/tex/sections/variations.tex
add description of lower mass gap plot

@@
 \subsection{Properties of detectable systems}\label{sec:property_variations}
-\todo{Describe the plots -- also explore whether there is anything interesting the CE ones once they are done}
 
-\begin{figure}[htb]
+In this section, we consider how varying underlying physics assumptions changes the properties of detectable systems.
+We focus on several key differences across physics variations rather than showing the differences in every model and thus this section is by no means exhaustive.
+
+\subsubsection{Using LISA to investigate the lower mass gap}
+
+\begin{figure}[tb]
     \centering
@@
     \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
-Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}.
+Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
@@
 
-\begin{figure}[htb]
+In Figure~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions.
+The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption.
+This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap.
+Overall, weighting by the relative detection rates, this gives that 55\% of our predicted LISA DCO detections  would have at least one component in the lower mass gap when using this remnant mass prescription.
+
+Alternatively, the blue curve in Fig.~\ref{fig:lower_mass_gap_variation} shows the same distribution but for the \textit{rapid} remnant mass prescription \citep{Fryer+2012}, which we use in model \modRapid{}.
+In this case, no compact objects are formed (and therefore, detected) in the lower mass gap.
+From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.
+
+However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them.
+And thus, LISA could be a useful instrument for providing evidence for the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.
+
+\subsubsection{Effect of natal kicks on eccentricity distribution}
+
+\begin{figure}[tb]
     \centering
@@
 \end{figure}
+
+In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks as a result of core-collapse supernovae affects the eccentricity distribution of detectable DCOs.
+For reference, we show the fiducial distributions from the lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions} as dashed lines.
+In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (using model \modSigLower{} instead of \modFid{}).
+
+\subsubsection{Other interesting features}
+\todo{explore whether there is anything interesting the CE ones}
 

### 2021-08-06 paper/tex/sections/variations.tex
add description of natal kick-ecc plot

@@
     \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}.
-For comparison, we show the mean distribution for the fiducial model as dashed lines.
+For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
@@
 
-In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks as a result of core-collapse supernovae affects the eccentricity distribution of detectable DCOs.
-For reference, we show the fiducial distributions from the lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions} as dashed lines.
-In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (using model \modSigLower{} instead of \modFid{}).
+In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs.
+For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions} for full comparison).
+In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (model \modSigLower{}).
+
+We find that the LISA detectable BHBHs are significantly less eccentric with weaker kicks, such that the population above $e = 0.2$ is nearly completely eliminated.
+This is because BHBHs are often massive enough to withstand strong natal kicks without disrupting and these kicks tend to impart significant eccentricity.
+In model \modSigLower{}, very few systems are ever given such strong kicks and thus very few BHBHs are detected with significant eccentricity.
+
+Since BHNSs are less massive than BHBHs and have more unequal mass ratios, they are more vulnerable to disruption during supernova kicks.
+BHNSs can only withstand strong kicks when they are aimed in the correct direction and so only a small `lucky' fraction of the fiducial population is highly eccentric.
+Therefore in model \modSigLower{}, although we see that the population of highly eccentric BHNS systems is eliminated (similar to BHBHs), the peak of the distribution actually shifts to \textit{higher} eccentricity.
+This is because a larger fraction of systems are given weaker kicks that BHNSs can withstand and these impart much more moderate eccentricities.
+
+Finally, we find that the NSNS distribution is relatively unchanged between model \modFid{} and \modSigLower{}.
+This is not surprising however since the majority of NSNSs are formed through electron-capture supernovae and ultra-stripped supernovae and for these types of supernovae we use $\sigma^{\rm 1D}_{\rm rms} = 30 \unit{km}{s^{-1}}$ already (see App.~\ref{app:fiducial_physics}) and thus there is little difference between the models.
+
+Overall, we find that decreasing supernova natal kicks, though it strongly increases the number of detections (see Fig.~\ref{fig:detection_rates}), strongly \textit{decreases} the fraction of highly eccentric systems that are detected.
 
 \subsubsection{Other interesting features}
-\todo{explore whether there is anything interesting the CE ones}
+\todo{maybe add CE model stuff}
 

### 2021-08-17 paper/tex/sections/appendix.tex
BIG COMMIT: lots of changes from Selma

@@
 
+\section{Calculation of the uncertainties in the chirp mass for detectable sources}\label{app:chirp_mass_uncertainty}
+
+How accurately the chirp mass of a detected binary can be determined depends on the signal to noise ratio, duration of the mission, its orbital frequency and the time derivative of the orbital frequency.
+
+Here we describe how we estimate the uncertainty of the chirp mass . First, consider the chirp mass, which can be expressed as
+\begin{equation}
+    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48 n} \frac{\dot{f}_{n}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
+\end{equation}
+where ${f}_{n}$ is the frequency of the n-th harmonic,  $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}), $e$ is the eccentricity and
+\begin{equation}\label{eq:peters_f}
+    F(e) = \frac{1 + \frac{73}{24} e^2 + \frac{37}{96} e^4}{(1 - e^2)^{7/2}},
+\end{equation}
+is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}. 
+%
+In practice, we will use the dominating harmonic, with $n=n_{\rm dom}$ and $f_n =  f_{\rm dom}$.
+The dominating harmonic for circular binaries is $n_{\rm dom} = 2$ and the dominating frequency is twice the orbital frequency.
+
+Therefore the chirp mass uncertainty can be estimated as
+\begin{equation}\label{eq:chirp_mass_uncertainty}
+    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)},
+\end{equation}
+%where $f_{\rm dom}$ is the harmonic frequency with the strongest SNR ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) as this will provide the best measurement.
+
+We estimate the frequency uncertainties using \citet{Takahashi+2002}, such that
+\begin{align}\label{eq:f_orb_unc}
+    \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
+    \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm dom}},
+\end{align}
+where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length.
+We estimate the eccentricity certainty, $\Delta e$, following the methods of \citet{Lau+2020} and \citet{Korol+2021}, which use the relative SNRs of different harmonics to work out the eccentricity.
+We propagate this uncertainty such that
+\begin{equation}
+    \frac{\Delta F(e)}{F(e)} = \Delta e \cdot \frac{(1256 + 1608 e^2 + 111 e^4) e}{96 + 196 e^2 - 255 e^4 - 37 e^6}.
+\end{equation}
+
+We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO type in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
+
 \section{Assessing the impact of Milky Way model choices}\label{app:mw_changes}

### 2021-08-17 paper/tex/sections/methods.tex
BIG COMMIT: lots of changes from Selma

@@
 Note that the length of the LISA mission affects how much a binary will evolve over the mission and thus changes the frequency limits in Eq.~\ref{eq:snr}.
-The SNR generally scales as $\sqrt{T_{\rm obs}}$ (with exceptions for sources very close to merging) and thus the SNR of a typical source in a 10-year LISA mission is approximately $1.58 (=\sqrt{10/4})$ times stronger than in a 4-year mission.
+The SNR generally scales as $\sqrt{T_{\rm obs}}$ (with exceptions for sources very close to merging) and thus the SNR of a typical source in a 10-year LISA mission is approximately $1.58$ (=$\sqrt{10/4}$) times stronger than in a 4-year mission.
 

### 2021-08-17 paper/tex/sections/results.tex
BIG COMMIT: lots of changes from Selma

@@
-Based on our fiducial model (described in App~\ref{app:fiducial_physics}), we expect that a 4-year LISA mission will detect about \BHBHFourYear{} BHBHs, \BHNSFourYear{} BHNSs and \NSNSFourYear{} NSNSs (see Table~\ref{tab:detection_rates} for confidence intervals).
-In this section we discuss the properties of the detectable sources based on our fiducial simulation.
+In this section we present our predictions for the population of detectable LISA sources.
+In total we expect $124$ detections in a 4-year LISA mission, of which $\BHBHFourYear{}$, $\BHNSFourYear{}$ and $\NSNSFourYear{}$ are BHBHs, BHNSs and NSNSs respectively, based on our fiducial simulations.
+In the remainder of this section, we discuss where the sources are expected relative to LISA's sensitivity curve (Sec.~\ref{sec:dcos_on_sc}), their properties (Sec.~\ref{sec:fiducial_distributions}), their locations in the Milky Way (Sec.~\ref{sec:mw_detectable_distribution}), their progenitors and formation channels (Sec.~\ref{sec:progenitors_and_formation}) and finally we discuss the expected SNR and how accurately we expect that the parameters can be measured (Sec.~\ref{sec:measurement_uncertainties}).
+Note that all results shown in this section are based on our fiducial simulations.
+A discussion of the impact of variations in the physics assumptions is provided in Sec.~\ref{sec:variations}.
 
@@
 \end{figure*}
-We show the expected distribution of detectable DCOs together with the LISA sensitivity curve in Fig.~\ref{fig:dcos_on_sc} for all sources combined in the top panel and separated by type in the three lower panels.
-For reference, we overplot dotted lines to indicate where a binary system would reside for a given distance (diagonal lines) and a remaining inspiral time (vertical lines).
-For each line we assume the binary is circular and has the average chirp mass of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
-We observe several features worthwhile discussing, some that earlier studies have touched upon (see Sec.~\ref{sec:compare_studies}), as well as some new findings related to eccentricity.
+We show the expected LISA sensitivity curve \citep{Robson+2019} in Fig.~\ref{fig:dcos_on_sc} and overplot our predictions for the distribution of detectable sources.
+Eccentric systems emit gravitational waves in multiple harmonic frequencies ($n f_{\rm orb}$, with $n = 2, 3, \dots $).
+We choose to plot them at the $x$-coordinate that corresponds to the frequency of the harmonic that dominates the SNR.
+For circular systems, the $x$-coordinate simply corresponds to $2 f_{\rm orb}$.
+The $y$-coordinate indicates the strength of the signal (or to be more precise, the amplitude spectral density, ASD), including the contribution from \textit{all} harmonics.
 
-Firstly, we note that the detectable population is concentrated on the left side of LISA's sensitivity window.
+For reference, we show dotted lines to indicate where a hypothetical binary system would reside assuming a given distance (diagonal lines) and a fixed remaining inspiral time (vertical lines).
+For each line we assume the binary is circular and has a chirp mass equal to the average of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
+We also overplot the LISA verification binaries (star symbols, \citealt{Kupfer+2018}).
+
+\vspace{1em}
+
+We observe several features in Fig.~\ref{fig:dcos_on_sc} that are worth discussing and explaining.
+We note that some of these have also been described in earlier studies (see Sec.~\ref{sec:compare_studies}).
+Firstly, we note the empty band that separates the LISA sensitivity curve and the detectable population.
+This is the result of the criteria for detection where we require $\rm{SNR} > 7$.
+
+We further note that the detectable population is concentrated on the left side of LISA's sensitivity window.
 The peak is located at a frequency of about $0.4 \unit{mHz}$, which is much lower than the frequency where LISA will be most sensitive (about $10 \unit{mHz}$).
@@
 
-We further note that there is an empty band that separates the LISA sensitivity curve and the detectable population.
-This is the direct result of the criteria for detection where we require $\rm{SNR} > 7$.
-For circular systems the SNR is directly given by the height of a system above the curve.
-For eccentric systems this is also approximately true because, though we have plotted them at the frequency of the dominant harmonic, the y-coordinate indicates the signal from \textit{all} harmonics.
-
-Comparing the lower three panels, one can observe the shift in the frequency at which the peak is located, at $0.3 \unit{mHz}$, $0.7 \unit{mHz}$ and $1 \unit{mHz}$ for BHBH, BHNS and NSNS systems respectively.
+In the lower three panels, we show the contributions of the different types of sources.
+Comparing them, one can observe the shift in the frequency at which the peak is located, at $0.3 \unit{mHz}$, $0.7 \unit{mHz}$ and $1 \unit{mHz}$ for BHBH, BHNS and NSNS systems respectively.
 This is a result of the difference in chirp mass.
 A higher mass system can emit at lower frequency and still produce the minimum SNR needed for detection.
-This effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically \citep[e.g.][]{Sesana+2020}.
-In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries (star symbols, \citealt{Kupfer+2018}).
+We note that this effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically \citep[e.g.][]{Sesana+2020}.
+In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries (star symbols.
 
-Finally we note that the peak of the density distribution of observable sources coincides with the reference line for circular systems at $8 \unit{kpc}$, as expected since this is the distance to the centre of the Milky Way.
+Inspecting the dotted reference lines, we note that the peak of the density distribution of observable sources coincides with the location expected for circular systems at $8 \unit{kpc}$, which is the distance to the centre of the Milky Way.
 As can be seen best in the lower panels, the reference lines for $0.1$ and $30 \unit{kpc}$ enclose the majority of systems as expected given the dimensions of our Milky Way.
-There is, however, a distinct subpopulation of binaries that extend downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
-This offshoot is almost uniquely composed of eccentric binaries, as can be seen most clearly in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix.
-This can also be seen in Fig.~\ref{fig:dcos_on_sc} from the contour that encompasses 90\% of the \textit{circular} sources in our population, where systems in the offshoot are missing.
-We also provide a curved reference line that indicates the signal emitted by an eccentric binaries with $e = 0.98$ at a distance of $30 \unit{kpc}$ and average chirp mass.
-We therefore show that eccentric sources are located in a different region on the sensitivity curve.
+
+There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extend downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
+This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix, which shows a similar figure but colouring individual systems by their eccentricity.
+This can also be seen, albeit indirectly, from the contours shown in the bottom panels of Fig.~\ref{fig:dcos_on_sc}, which encompass 90\% of the \textit{circular} sources in each population.
+This contour does not include the offshoot.
+We conclude that eccentric sources occupy a very different region in this diagram.
+
+\todo{Remove curved line.}
 
 \subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
-In Figure~\ref{fig:fiducial_pdf_distributions}, we show kernel density estimators of the 1D distribution of the individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-We have applied a simple correction for edge effects due to bounded support by mirroring the sample \citep{Schuster+1985}.
+In Figure~\ref{fig:fiducial_pdf_distributions}, we show the 1D distribution of several individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties obtained via bootstrapping.
+The distributions shown here are approximated by kernel density estimators, corrected for edge effects by mirroring the sample \citep{Schuster+1985}.
 
-\paragraph{Orbital Frequency} The orbital frequency distributions for BHBHs, BHNSs and NSNSs peak at progressively increasing frequencies.
+\paragraph{Orbital Frequency} The orbital frequency distributions for BHBHs, BHNSs and NSNSs (Fig.~\ref{fig:fiducial_pdf_distributions}a) peak at progressively increasing frequencies.
 As already mentioned above, this is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
@@
 This is because of the contribution of highly eccentric binaries, which are most abundant in the BHBH population.
-These systems are still detectable by LISA as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics, therefore concentrating it at higher frequencies that are located in the LISA band.
+These systems are still detectable by LISA, despite their low orbital frequency, as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics, where LISA is more sensitive.
 
@@
 \paragraph{Black Hole Mass}
-For both the BHBHs and BHNSs, the black hole mass distribution extends to relatively low masses, with about $90\%$ of BHs below $11 \unit{M_{\odot}}$.
-Unlike ground-based detectors, LISA is not biased to higher masses and so the mass distribution more closely follows the IMF.
-In addition, at the high metallicities in the Milky Way, stellar winds are much stronger and strip away much of the stellar mass before BH formation, resulting in less massive black holes.
-For these reasons, the mass distribution extends down to $2.5 \unit{M_{\odot}}$, our fiducial maximum neutron star mass.
-Since the \citet{Fryer+2012} \textit{delayed} remnant mass prescription (applied in this work) does not produce a mass gap between neutron stars and black holes.
-Indeed we expect $\BHBHLowerMassGap{}$ and $\BHNSLowerMassGap{}$ of detected BHBH and BHNS systems to contain a black hole in the lower mass gap.
-During the preparation of this paper \citet{Shao+2021} also noted this, claiming that $30\%$ and $70\%$ of merging BHBHs and BHNSs respectively have BHs in the lower mass gap (when using the delayed remnant mass prescription).
-Therefore, LISA could help to confirm or rule out the existence of the lower mass gap.
+In Fig.~\ref{fig:fiducial_pdf_distributions}b, we show the distribution masses of individual black holes that are part of BHNS and BHBH systems. 
+The distribution for BHBH shows a bimodality.
+This results from the two contributions of the more and less massive BHs in BHBH systems, which peak at around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively as shown by the dotted lines (see also our discussion of the mass ratios below).
 
-The bimodality of the BHBH distribution is a result of unequal mass ratios.
-The two peaks are from the primary and secondary black hole masses, which peak around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively.
-We show these individual distributions as dotted curves below the main BHBH distribution.
+For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses.
+About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here.
+This is in stark contrast with the masses of the BHs that have been detected so far by ground-based GW detectors, where heavy BHs, with masses of about $30\unit{M_{\odot}}$ and higher have been common.
+Ground-based detectors are strongly biased towards high mass systems, since they can be detected out to larger distances.
+Instead, LISA is, in principle, sensitive to inspiraling BHBHs throughout the entire Milky Way regardless of their mass, as long as we catch them at the right time when their dominant frequencies coincide with the range where LISA is sensitive.
 
-\paragraph{Mass Ratio} The mass ratio distribution for each DCO type is relatively distinct from the others.
+A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Appendix~XX).
+Stellar winds are stronger at high metallicity leading to increased mass loss.
+This affects the mass of the most massive black holes that can be formed \citep{Belczynski+2010}.
+
+We also note that our BH mass distribution extends down below $5\unit{M_{\odot}}$ to $2.5 \unit{M_{\odot}}$ which is our fiducial maximum neutron star mass.
+The BHs in this simulation fill the so-called ``lower mass gap'' marked as a grey band \citep{Ozel+2010,Farr+2011}, see also \citet{Shao+2021} who recently pointed this out.
+This prediction is sensitive to adopted model for fall back during the SN explosion as we discuss this further in Sec.~\ref{sec:lower_mass_gap}
+
+\paragraph{Mass Ratio} The mass ratio distributions for each DCO type are very distinct from one another, as can be seen in Fig.~\ref{fig:fiducial_pdf_distributions}c.
 The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
 The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae (ECSN) or from low mass stars in our simulations.
-We set the remnant mass for any system formed through ECSN to $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{app:fiducial_physics}).
-The remnant mass prescription that we use gives a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs are given the identical mass of $1.278 \unit{M_\odot}$ in the \textit{delayed} prescription \citep[see][Eq.~19]{Fryer+2012}.
+We assume a remnant mass for any NS formed through ECSN of $1.26 \unit{M_{\odot}}$ (see Sec.~\ref{app:fiducial_physics}).
+The remnant mass prescription that we use assumes a fixed fallback mass for any star with a CO core mass less than $2.5 \unit{M_\odot}$, such that many NSs end up with an identical mass of $1.278 \unit{M_\odot}$ \citep[see][Eq.~19]{Fryer+2012}.
 This means that many NSs are formed with equal masses and hence we see a mass ratio distribution peaked around unity.
@@
 In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$.
-The reasoning for these unequal mass ratio systems is as follows: in order to produce a BHBH, most formation channels require at least the first mass transfer to be stable.
-This stability is strongly dependent on the mass ratio such that equal mass ratios (at the moment of mass transfer) are preferred for creating BHBHs.
-Yet, since stellar winds are so strong at high metallicity, and even stronger for more massive stars, the primary star will experience significant mass loss and so an initially \textit{unequal} mass ratio is preferred so that the masses are more balanced at the first instance of mass transfer.
-Since mass transfer occurs after the end of the main sequence for most of our BHBHs, the star will have a well defined core and these core masses, which go on to form BHs, will reflect the initially unequal mass ratios.
+After closer inspection of the binary simulations, we find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this.
 
-We find that detectable BHNSs have even more unequal mass ratios, such that the distribution is almost entire disjoint from that of NSNSs.
+BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations, see Sec.~\ref{sec:progenitors_and_formation}).
+The primary in such systems experiences strong mass loss by winds before filling its Roche lobe.
+This mostly happens during its early hydrogen-shell burning phase.
+The wind mainly reduces the mass of the envelope, but does not have a very strong effect on the core.
+By the time the primary fills its Roche lobe, it has become less massive and the mass ratio is closer to one.
+This favours stable mass transfer.
+The massive core of the primary star typically becomes the more massive BH.
+Accretion on the secondary star is limited and the secondary eventually provides the less massive black hole.
+
+At the same time, stellar wind mass loss disfavours the formation of black holes with comparable masses.
+Such systems would have originated from progenitors that also started with comparable masses.
+The rather massive secondaries in these systems (especially after they accreted from the primary) experience very strong stellar wind mass loss.
+This limits the amount by which they can expand.
+At the same time, wind mass loss (and also stable and more conservative mas transfer in these systems) lead to widening of the orbit.
+Both effects, the reduced expansion and increased widening of the orbit, tend to prevent the secondaries from being able to fill their Roche lobe.
+This thus limits the number of systems that experience the reverse mass transfer or common envelope phase needed shrink the orbits and make them tight enough to be detected as gravitational wave sources.
+
+We find that detectable BHNSs have even more unequal mass ratios.
 Moreover, the mass ratio distribution is bimodal, where the two peaks arise from two distinct formation scenarios.
@@
 The first peak at $q = 0.18$ is from systems that experience at least one common-envelope and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
-Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arise from the fraction of the population that underwent only stable mass transfer phases.
-The stability of mass transfer is strongly dependent on the mass ratio and thus these systems have a bias for more equal mass ratio systems, leading to a peak at higher $q$.
+Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arises from the fraction of the population that underwent only stable mass transfer phases.
+The stability of mass transfer depends on the mass ratio, leading to a bias for more equal mass ratio systems, resulting in a peak at higher $q$.
 
-\paragraph{Eccentricity} The eccentricity distributions show that detectable BHBHs are most likely to be highly eccentric of the three DCOs.
-This may seem counter-intuitive since neutron stars receive stronger natal kicks, which cause the orbit to become eccentric.
-However, these stronger kicks often result in disrupted or too-wide binaries in the more weakly bound NSNSs.
-In contrast, BHBHs can receive strong kicks that impart high eccentricity without disrupting and thus tend to be more eccentric.
-This effect is compounded by the fact that we can see BHBHs at lower orbital frequencies, meaning that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
+\paragraph{Eccentricity} In Fig.~\ref{fig:fiducial_pdf_distributions}d we show the eccentricity distributions.
+We find that most systems (73\%) will have eccentricities larger than $0.01$ during the LISA mission, which should in principle be detectable according to \citet{Nishizawa+2016}.
+This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources (see Sec.~\ref{sec:WDWD_distinguish}).
+We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}.
+See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption
 
-An eccentricity of $e = 0.01$ is the lower bound on the measurable eccentricity with LISA proposed by \citet{Nishizawa+2016}.
-We find that a significant fraction of DCOs ($\BHBHNotCirc{}$ of BHBHs, $\BHNSNotCirc{}$ of BHNSs and $\NSNSNotCirc{}$ of NSNSs) exceed this bound.
-This is in contrast to several previous work that assume all DCOs are circular once they reach the LISA mission \citep[e.g.][]{Lamberts+2018, Sesana+2020}.
-Moreover, we find that $\BHBHHighlyEccentric{}$, $\BHNSHighlyEccentric{}$ and $\NSNSHighlyEccentric{}$ of BHBHs, BHNSs and NSNSs respectively have $e > 0.3$.
-At this eccentricity the majority of the gravitational wave power is emitted in higher harmonics above the orbital frequency \citep[Eq.~20]{Peters+1963} and thus the signal would appear at higher frequencies in LISA.
+For systems with eccentricities higher than $e\gtrsim0.3$, most gravitational wave energy is emitted in higher harmonics.
+Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of systems.
 
-\paragraph{Time since formation} The progenitors of Galactic DCOs in our sample are formed throughout the history of the Milky Way, with more formed at earlier times (see top left panel of Fig.~\ref{fig:galaxy_schematic}).
-In contrast, we find that the \textit{detectable} systems are primarily formed recently, with the majority formed in the past $2 \unit{Gyr}$, in addition to a tail of systems out to earlier times.
+These BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel \citep{vandenHeuvel+2017}.
+These systems are still relatively wide just prior to formation of the second BH.
+If the kick is oriented roughly in opposite direction to the orbital motion and has a velocity that is of similar magnitude as the orbital velocity, it will lead to the formation of a highly eccentric system.
 
-The peak at recent times is due to the fact that most binaries in our sample are formed with merger times on the order of a couple of Gyr (since most form through a common-envelope phase that significantly tightens the binary).
-For a binary to be in the LISA band and detectable it must be near the end of its inspiral and so LISA will be most sensitive to sources that were formed a couple of Gyr ago.
+It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH.
+The kicks of BHs are reduced and they are thus less likely to disrupt the system.
+Moreover, because of their higher masses, BHBHs can be observed already at lower orbital frequencies.
+This means that they have not had as much time to circularise and so still have significant eccentricity by the time of the LISA mission.
+Finally, LISA favours the detection of eccentric systems, if all other properties are held fixed.
+This is because the gravitational wave emission is stronger (Eq.~\ref{eq:peters_f}) and the energy is emitted at higher frequencies \citep[Eq.~20]{Peters+1963} where LISA is more sensitive.
 
-The peak is sharpest for NSNSs as they have the highest orbital frequencies and largest fraction of eccentric system, which result in shorter inspiral times and therefore later formation times.
-Conversely, the peak is less prominent for BHNSs as they are the most circular, have moderate orbital frequencies and masses.
+The lower abundance of highly eccentric systems among the NSNS and BHNS systems may seem counter-intuitive since neutron stars receive stronger natal kicks, which one may expect to lead to more eccentric systems.
+However, in practice, these stronger kicks often disrupt these systems.
+
+\paragraph{Time since formation} 
+In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the DCOs detectable by LISA formed.
+For comparison we show the star formation history we have assumed in our Milky Way model (grey line).
+Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.
+In contrast, the DCOs detectable by LISA primarily formed in the relatively \textit{recent} history of our Milky Way, about $2 \unit{Gyr}$ ago.
+This reflects the fact that binaries in our simulation typically take about a Gyr to merge, a result as is commonly found also in other population synthesis studies.
+
+When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBH and then BHNS.
+To understand this it is helpful to consider how the inspiral time scales with various parameters
+\begin{equation}
+    t_{\rm inspiral} = \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
+\end{equation}
+The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}.
+The NSNS systems have the tightest orbits at DCO formation.
+The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations.
+This results in increase of the inspiral time by a factor of about 4000:80:1.
+The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured.
+The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations.
+The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and is not of interest.
+The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$.
+The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}.
+%
+We conclude that the shorter median separations at DCO formation are the main reason why NSNS are most strongly peaked at short delay times, followed by BHBH where the inspiral timescales are short because of their high masses and substantial eccentricities.
+
+In addition to the peak at recent times, we see that all three distributions have a large extended tail of systems that formed through out the history of the milky way, most prominently for the BHNS systems.
+For the BHBH and BHNS we find that the peak at very recent formation times comes from systems formed through stable mass transfer that obtained very high eccentricities.
+The long tail is a mixture of channels.
+
+\todo{Can we do a little better in understanding the tail?}
+
+\todo{I also think this section has become \textit{very} dense...but can't see how to make it better}
 
@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
+For our Milky way model we considered three different components, a low-$\alpha$ (``thin'') disc, an older high-$\alpha$ (``thick'') disc and a bulge/bar.
+In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components.
+Despite the fact that only $42.5\%$ of systems are formed in the low-$\alpha$ disc, we find that $86\%$ of the detections originate from this component.
+This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}) and so the high-$\alpha$ disc and bulge are effectively too old to contribute many detectable systems.
+Nevertheless, we do find a significant fraction of detectable systems originate in the high-$\alpha$ disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).
 
+\begin{table}[tb]
+    \centering
+    \begin{tabular}{l|ccccc}
+        \hline
+        \multirow{2}{*}{Component} & Formation & \multicolumn{4}{c}{Detectable} \\ \cline{2-6}
+        & {\scriptsize All} & {\scriptsize All} & {\scriptsize BHBH} & {\scriptsize BHNS} & {\scriptsize NSNS} \\
+        \hline
+        Low-$\alpha$ disc & 42.5\% & 86\% & 89\% & 82\% & 85\%\\
+        High-$\alpha$ disc & 42.5\% & 6\% & 5\% & 8\% & 12\%\\
+        Bulge/bar & 15.0\% & 8\% & 6\% & 10\% & 3\%\\
+    \end{tabular}
+    \caption{Percentage of systems in each Galactic component.}
+    \label{tab:component_fractions}
+\end{table}
 \begin{figure}[tb]
     \centering
+    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
     \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
-    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
-    \caption{\textbf{Top:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
-\textbf{Bottom:} A face-on view of the Galactic density distribution for detectable DCOs.
+    \caption{
+    \textbf{Top:} A face-on view of the Galactic density distribution for detectable DCOs.
 We show the density distribution for the top 95\% of the sources, the rest are indicated by scatter points whose sizes correspond to their sampling weights.
@@
 The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+    \textbf{Bottom:}   As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:detectable_distance_dist}
@@
 
-In the top panel of Fig.~\ref{fig:detectable_distance_dist} we show the distribution of the luminosity distance of detectable systems.
-Each DCO's luminosity distance distribution peaks around $8 \unit{kpc}$ since this is the distance to the centre of the Milky Way and thus the most dense location of DCOs.
-There is a bias in each distribution for systems at lower distances since closer binaries are easier to detect.
-This bias is most prominent for the NSNS distribution since, on average, their lower relative masses require a smaller distance in order to be detected.
+In the top panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy.
+We see that most detectable sources are concentrated towards the Galactic centre, with a strong bias towards sources that are on our side of the Milky Way in the vicinity of the solar system (indicated with the $\odot$ symbol).
+In principle, systems are detectable out to large distances of about $20\unit{kpc}$ and more, although they become increasingly rare, as can be seen from the 95\% contour.
 
-However, more surprisingly, we also see that the NSNS distribution extends to higher distances than the other DCOs.
-The reason for this is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.3$).
-The BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
-Therefore, despite their relatively higher masses, the maximum distance at which a source is detectable is generally lower than the eccentric NSNSs and hence the distribution tends to zero at smaller distances.
-Conversely, the BHBH population has a higher fraction of \textit{high} eccentricity systems $e > 0.3$.
-Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution and thus have a low orbital frequencies.
-The result of this is that high eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
+The differences between different DCO types can be seen more clearly in the bottom panel of Fig.~\ref{fig:detectable_distance_dist} where we show the distribution of the distances, $D$, from earth to the detectable systems.
+Each distribution peaks around $8\unit{kpc}$, which is the distance to the centre of the Milky Way.
+The distribution for BHBH and BHNS systems follow a very similar shape, favouring the detection of systems with distance $<8\unit{kpc}$, but with a tail extending out to about $20\unit{kpc}$.
+
+The distribution for NSNS stands out by being flatter, making them more common nearby and, surprisingly, also at larger distances.
+This may seem counter intuitive as one might naively expect the less massive NSNS systems would not be observable out to larger distances than the more massive BHNS and NSNS systems.
+To understand the differences we need to consider not only the mass distribution of binaries, but also their eccentricity and frequency distributions.
+Since, each parameter contributes to the calculation of the SNR (and thus affects the maximum distance at which systems can be detected).
+
+The reason that the NSNSs are favoured at higher distances is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.03$).
+In contrast, the BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
+Therefore, despite their typically higher masses, the distance at which a BHNS source is detectable is generally lower than for the mildly eccentric NSNS.
+
+Conversely, the BHBH population has the highest fraction of highly eccentric systems ($e > 0.3$).
+Although one may naively expect that this would result in stronger signals (and so further distances), for a system to have these high eccentricities in LISA, it must still be early in its evolution (otherwise it would have circularised) and thus have a low orbital frequency.
+The result of this is that highest eccentricity systems tend to have lower SNRs and so cannot be detected at large distances.
+
 Overall we see that the eccentricity distribution of NSNSs occupies a ``sweet spot'' where the gravitational wave power is increased compared to circular systems, but it isn't too high that the frequency is significantly impacted.
@@
 
-In the lower panel of Fig.~\ref{fig:detectable_distance_dist}, we show the density distribution for detectable DCOs in the galaxy.
-We see that most sources are concentrated in the Galactic center, with a bias towards the position of the Sun.
-Yet we also show that systems are detectable out to the edges of the galaxy.
-This is especially true for NSNSs, as we highlight by plotting the 75\% contour for the individual DCO types.
+\subsection{Progenitors and formation channel \label{sec:progenitors_and_formation}}
+\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}
 
-\subsection{Measurement Uncertainties}\label{sec:measurement_uncertainties}
-Although it is useful to investigate the underlying parameters of the detectable population, it is also important to consider what LISA will actually \textit{measure} during a detection.
-To this end, we discuss the most relevant uncertainties below.
+\subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
+So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
+However, many sources will only be barely detectable.
+Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters.
+Below we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.
 
-\subsubsection{Chirp mass uncertainty}
+\paragraph{Signal-to-noise ratio}
+
+{\bf SdM: proposed to add this paragraph and plot. Draft text provided}
+In Fig.~X we show the cumulative distribution of SNR expected together with the $1$ and $2\sigma$ uncertainties.
+We assumed a detection threshold of {\bf 8}.
+Of the total number of 140 {\bf check} detections SNRs larger than 10, 50, 100 respectively for 85, 16, and 9 sytems, where the high SNR systems are typically, but not only, the more massive BHBH systems.
+
+{\bf Quote with errors. }
+
+\paragraph{Chirp mass}
 
@@
 
-The chirp mass uncertainty is important for identifying the source of a GW signal.
-It is calculated using the uncertainty on the orbital frequency, the time derivative of the orbital frequency and the eccentricity.
-This is because the chirp mass can be written as
-\begin{equation}
-    \mathcal{M}_c = \frac{c^3}{G} \left( \frac{5 \pi}{48 n} \frac{\dot{f}_{n}}{F(e)} \right)^{3/5} \frac{1}{(2 \pi f_{\rm orb})^{11/5}},
-\end{equation}
-where $f_{\rm orb}$ is the orbital frequency, $\mathcal{M}_{c}$ is the chirp mass (defined in Eq.~\ref{eq:chirp_mass}), $e$ is the eccentricity and
-\begin{equation}
-    F(e) = \frac{1 + \frac{73}{24} e^2 + \frac{37}{96} e^4}{(1 - e^2)^{7/2}},
-\end{equation}
-is the enhancement factor of gravitational wave emission for an eccentric binary over an otherwise identical circular binary \citep[][Eq.~17]{Peters+1963}. Therefore the chirp mass uncertainty is
-\begin{equation}\label{eq:chirp_mass_uncertainty}
-    \frac{\Delta \mathcal{M}_c}{\mathcal{M}_c} = \frac{11}{5} \frac{\Delta f_{\rm orb}}{f_{\rm orb}} + \frac{3}{5} \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} + \frac{3}{5} \frac{\Delta F(e)}{F(e)},
-\end{equation}
-where $f_{\rm dom}$ is the harmonic frequency with the strongest SNR ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) as this will provide the best measurement.
+The chirp mass is important for identifying the type of the source of a detected GW signal.
+The uncertainty of the chirp mass depends on the uncertainty in the measured orbital frequency, the time derivative of the orbital frequency and the eccentricity as detailed in Appendix~\ref{app:chirp_mass_uncertainty}.
 
-We calculate the frequency uncertainties using \citet{Takahashi+2002}, such that
-\begin{align}\label{eq:f_orb_unc}
-    \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
-    \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm dom}},
-\end{align}
-where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length.
-We calculate the eccentricity certainty, $\Delta e$, following the methods of \citet{Lau+2020} and \citet{Korol+2021}, which use the relative SNRs of different harmonics to work out the eccentricity.
-We propagate this uncertainty such that
-\begin{equation}
-    \frac{\Delta F(e)}{F(e)} = \Delta e \cdot \frac{(1256 + 1608 e^2 + 111 e^4) e}{96 + 196 e^2 - 255 e^4 - 37 e^6}.
-\end{equation}
-
-We use Eq.~\ref{eq:chirp_mass_uncertainty} to calculate the chirp mass uncertainty for each DCO in our sample and plot it in Fig.~\ref{fig:m_c_unc}.
 We find that for a 4(10)-year LISA mission, approximately $\BHBHChirpMassMeasureableFour{}(\BHBHChirpMassMeasureableTen{})$ BHBHs, $\BHNSChirpMassMeasureableFour{}(\BHNSChirpMassMeasureableTen{})$ BHNSs and $\NSNSChirpMassMeasureableFour{}(\NSNSChirpMassMeasureableTen{})$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}).
@@
 
-\subsubsection{Sky localisation}
+\paragraph{Eccentricities}
+
+\todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}
+
+\paragraph{Sky localisation}
 
@@
 
-We quantify the sky localisation of a source by calculating its angular resolution.
-Since we find that all potential sources are stationary on the timescale of the LISA mission, following \citet{Mandel+2018}, we can use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
+An accurate sky localisation will be essential to possibly identify electromagnetic counterparts or distinguish sources that come from different components of our Milky Way.
+
+We quantify the sky localisation of a source by estimating the angular resolution for the detectable sources.
+Since all potential sources are effectively stationary on the timescale of the LISA mission, which can follow \citet{Mandel+2018} and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
 \begin{equation}
@@
 
-We plot the angular resolution in Fig.~\ref{fig:ang_res}.
-The area of a patch on the sky that can be attributed to a source is given by $A = \pi \sigma_\theta^2$.
-From this plot, we see that the majority of sources can be resolved to an angular resolution of 10 degrees.
-The size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (which, for intuition, is approximately the angular size of the moon).
-Applying this to the plot shows that about 10-20\% of DCOs can be covered by a single pointing of SKA.
-However, since these LISA sources are essentially stationary in frequency space, observations need not be limited to a single pointing.
-We will discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
+We plot the distribution of expected angular resolutions in Fig.~\ref{fig:ang_res}.
+We see that only {\bf x, x, and x\% [quote numbers pref.
+with errorbars] } of the sources can be resolved to an angular resolution better than 1 degree, for NSNS, BHNS and BHBH respectively.
+The fraction is higher for NSNS systems {\bf SdM: Do we understand why?}, which is will be of interest for counter part searches.
+
+For comparison, the size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees \citep{Smits+2009}, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (similar to the angular size of the moon).
+We will further discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.

### 2021-08-17 paper/figure_notebooks/bootstrap.py
make KDE code better

@@ -2,64 +2,58 @@ import numpy as np
 from scipy.stats import gaussian_kde
 from scipy.interpolate import interp1d
 
-def kde(variable, weights, bw_adjust=1.0, x_min=None, x_max=None, x_count=200, x_vals=None,
-        lower_bound=None, upper_bound=None, verbose=False):
-    # if a range of x values at which to evaluate have not been provided then create one
-    if x_vals is None:
-        if x_min is None:
-            x_min = np.min(variable)
-        if x_max is None:
-            x_max = np.max(variable)
-        x_vals = np.linspace(x_min, x_max, x_count)
-    else:
-        x_min, x_max = x_vals[0], x_vals[-1]
+class MirroredKDE(gaussian_kde):
+    """ KDE class that mirrors data at boundaries to account for bounded support """
 
-    # calculate the covariance factor using Scott's rule
-    cv = (1 / np.sum((weights / np.sum(weights))**2))**(-1./(1+4))
+    def __init__(self, data, weights=None, lower_bound=None, upper_bound=None,
+                 bw_method=None, bw_adjust=None):
+        """ instantiate class in similar way to scipy but with some additions """
+        super().__init__(data, weights=weights, bw_method=bw_method)
 
-    # work out the bandwidth for the original data
-    bw = cv * np.std(variable)
+        # also store the lower and upper bounds
+        self._lower_bound = lower_bound
+        self._upper_bound = upper_bound
 
-    # check if either bound is surpassed given this bandwidth
-    exceeds_lower_bound = lower_bound is not None and np.min(variable) < lower_bound + bw
-    exceeds_upper_bound = upper_bound is not None and np.max(variable) > upper_bound - bw
+        # allow adjustment of the default bandwidth similar to seaborn
+        if bw_adjust is not None:
+            self.set_bandwidth(self.factor * bw_adjust)
 
-    # mirror data as necessary and adjust height based on how much added
-    if exceeds_lower_bound and exceeds_upper_bound:
-        if verbose:
-            print("exceeds both bounds")
-        variable = np.concatenate((2 * lower_bound - variable, variable, 2 * upper_bound - variable))
-        weights = np.repeat(weights, 3)
-        height_adjust = 3
-    elif exceeds_lower_bound:
-        if verbose:
-            print("exceeds lower bounds")
[…]

### 2021-08-17 paper/tex/sections/results.tex
add another line to distance plot

@@
     \centering
-    \includegraphics[width=\columnwidth]{fig4_2_galaxy_density_distribution.png}
-    \includegraphics[width=\columnwidth]{fig4_1_detectable_distance_distribution_4yr.pdf}
+    \includegraphics[width=\columnwidth]{fig4_1_galaxy_density_distribution.png}
+    \includegraphics[width=\columnwidth]{fig4_2_detectable_distance_distribution_4yr.pdf}
     \caption{

### 2021-08-17 paper/tex/sections/results.tex
add snr plot

@@
 
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{fig5_snr_cumulative_all.pdf}
+    \caption{Cumulative number of LISA detections with a given signal-to-noise ratio.
+Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \label{fig:snr_dist}
+\end{figure}
+
 {\bf SdM: proposed to add this paragraph and plot. Draft text provided}

### 2021-08-17 paper/tex/sections/results.tex
update chirp mass unc and ang res to match

@@
     \centering
-    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_4yr.pdf}
-    \caption{Cumulative distribution function for error on the chirp mass.
-Colours indicate DCO type and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-The shaded region indicates region with unmeasureable chirp mass.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_all.pdf}
+    \caption{As Fig.~\ref{fig:snr_dist}, but for the chirp mass uncertainty.
+The shaded areas indicate regions with more than 10\% and 100\% uncertainty.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:m_c_unc}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig6_angular_resolution_4yr.pdf}
-    \caption{As Fig.~\ref{fig:m_c_unc}, but for the angular resolution.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \includegraphics[width=\columnwidth]{fig6_angular_resolution_all.pdf}
+    \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:ang_res}

### 2021-08-18 paper/tex/sections/results.tex
update text to match in uncertainty section

@@
 In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the DCOs detectable by LISA formed.
-For comparison we show the star formation history we have assumed in our Milky Way model (grey line).
+For comparison we show the star formation history we have assumed in our Milky Way model (grey dotted line).
 Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.
@@
 
-\subsection{Progenitors and formation channel \label{sec:progenitors_and_formation}}
+\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
 \todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}
@@
 
-{\bf SdM: proposed to add this paragraph and plot. Draft text provided}
-In Fig.~X we show the cumulative distribution of SNR expected together with the $1$ and $2\sigma$ uncertainties.
-We assumed a detection threshold of {\bf 8}.
-Of the total number of 140 {\bf check} detections SNRs larger than 10, 50, 100 respectively for 85, 16, and 9 sytems, where the high SNR systems are typically, but not only, the more massive BHBH systems.
-
-{\bf Quote with errors. }
+In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR.
+Although many have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs.
+We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27) and 9(14) systems have SNRs greater than 10, 50 and 100 respectively.
+These high SNR systems are typically, but not only, the more massive BHBH systems.
 
@@
 
-We find that for a 4(10)-year LISA mission, approximately $\BHBHChirpMassMeasureableFour{}(\BHBHChirpMassMeasureableTen{})$ BHBHs, $\BHNSChirpMassMeasureableFour{}(\BHNSChirpMassMeasureableTen{})$ BHNSs and $\NSNSChirpMassMeasureableFour{}(\NSNSChirpMassMeasureableTen{})$ NSNSs have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the shaded region in Fig.~\ref{fig:m_c_unc}).
+We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
+This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
+
 Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
-This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
+The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.
 
@@
 We plot the distribution of expected angular resolutions in Fig.~\ref{fig:ang_res}.
-We see that only {\bf x, x, and x\% [quote numbers pref.
-with errorbars] } of the sources can be resolved to an angular resolution better than 1 degree, for NSNS, BHNS and BHBH respectively.
-The fraction is higher for NSNS systems {\bf SdM: Do we understand why?}, which is will be of interest for counter part searches.
+We see that, for a 4(10)-year LISA mission, approximately 82(123) sources can be resolved to an angular resolution better than 10 degrees and only 16(23) better than 1 degree.
 

### 2021-08-18 paper/tex/sections/appendix.tex
add more appendix figures and rearrange to match

@@
 
-\subsection{Detection rate table}
+% \subsection{Detection rate table}
 \begin{table*}[htb]
@@
 
-\subsection{Distribution of eccentric sources on sensitivity curve}
-\begin{figure*}[hb]
+% \subsection{Distribution of eccentric sources on sensitivity curve}
+\begin{figure*}[b]
     \centering
@@
 
-\subsection{Detection rates relative to fiducial model}
-\begin{figure*}[hb]
-    \centering
-    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
-    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
-The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
-    \label{fig:dco_relative_rates}
-\end{figure*}
+% \subsection{Formation channels}
 
-\clearpage
-
-\subsection{Formation channels}
-
-\begin{figure}[h]
+\begin{figure}[p]
     \centering
@@
 \end{figure}
+
+% \subsection{Properties of detectable systems (progenitors and at DCO formation)}
+\begin{figure*}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{progenitor_distributions.pdf}
+    \includegraphics[width=0.66\textwidth]{dco_formation_distributions.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row).
+Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \label{fig:progenitor_and_dco_properties}
+\end{figure*}
+
+% \subsection{Detection rates relative to fiducial model}
+\begin{figure*}[hb]
+    \centering
+    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
+    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
+The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
+\todo{add R and T}.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
+    \label{fig:dco_relative_rates}
+\end{figure*}

### 2021-08-18 paper/tex/sections/results.tex
add more appendix figures and rearrange to match

@@
 \end{equation}
-The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}.
+The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:progenitor_and_dco_properties}.
 The NSNS systems have the tightest orbits at DCO formation.
@@
 The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$.
-The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:fiducial_pdf_distributions}{\bf X}.
+The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:progenitor_and_dco_properties}.
 %
@@
 \subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
+
+Formation channel figure is Fig.~\ref{fig:formation_channels}.
+
+Progenitor distribution figure is Fig.~\ref{fig:progenitor_and_dco_properties}.
+
 \todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}

### 2021-08-18 simulation/src/simulate_DCO_detections.py
missed brackets

@@ -134,7 +134,7 @@ def main():
 
         # change metallicities above COMPAS limits to between solar and upper
         too_big = Z_unbinned > max_Z_compas
-        Z_unbinned[too_big] = 10**(np.random.uniform(np.log10(np.min(0.01416, max_Z_compas)),
+        Z_unbinned[too_big] = 10**(np.random.uniform(np.log10(np.min([0.01416, max_Z_compas])),
                                                      np.log10(max_Z_compas),
                                                      len(Z_unbinned[too_big])))
 

### 2021-08-19 simulation/output/combine_output.py
adjust which to combine

@@ -121,7 +121,7 @@ def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, r
 
 # loop over all binary types and physics variations
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    for variation in range(len(variations)):
+    for variation in [17, 19]:#range(len(variations)):
         combine_data(dco_type, variation)
         combine_data(dco_type, variation, extended_mission=True)
         if variation == 0 or variation == 5:

### 2021-08-19 paper/tex/sections/appendix.tex
add final simulations (update plots) :D

@@
         Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
-        R & Black holes receive not natal kick & \confinv{133.8}{11.8}{11.2} & \confinv{159.6}{12.6}{12.4} & \confinv{16.0}{4.0}{4.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
+        R & Black holes receive not natal kick & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
         S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
-        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{0.0}{0.0}{0.0} & \confinv{25.3}{5.3}{4.7} & \confinv{15.6}{3.6}{4.4} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0} & \confinv{0.0}{0.0}{0.0}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \confinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
         \hline
@@
 The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.
-\todo{Update R and T}}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
     \label{fig:formation_channels}
@@
 The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
-\todo{add R and T}.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}

### 2021-08-19 simulation/output/combine_output.py

@@ -121,7 +121,7 @@ def combine_data(dco_type, variation, simple_mw=False, extended_mission=False, r
 
 # loop over all binary types and physics variations
 for dco_type in ["BHBH", "BHNS", "NSNS"]:
-    for variation in [17, 19]:#range(len(variations)):
+    for variation in range(len(variations)):
         combine_data(dco_type, variation)
         combine_data(dco_type, variation, extended_mission=True)
         if variation == 0 or variation == 5:

### 2021-08-19 paper/tex/paper.tex
floor feedback: discussion (part II) + comparisons
add long awaited extended mission results
add description of lower mass gap plot
BIG COMMIT: lots of changes from Selma
change software citations

@@
 \newcommand{\NSNSFourYear}{8}
-\newcommand{\BHBHTenYear}{TODO}
-\newcommand{\BHNSTenYear}{TODO}
-\newcommand{\NSNSTenYear}{TODO}
-
-% number of systems that are definitely not WDWDs
-\newcommand{\BHBHNotWDWDFour}{33}
-\newcommand{\BHNSNotWDWDFour}{16}
-\newcommand{\NSNSNotWDWDFour}{5}
-\newcommand{\BHBHNotWDWDTen}{TODO}
-\newcommand{\BHNSNotWDWDTen}{TODO}
-\newcommand{\NSNSNotWDWDTen}{TODO}
-
-% percentage of systems above Chandrasekhar mass
-\newcommand{\BHBHAboveMaxWDWDFourPerc}{17}
-\newcommand{\BHNSAboveMaxWDWDFourPerc}{21}
-\newcommand{\NSNSAboveMaxWDWDFourPerc}{3}
-\newcommand{\BHBHAboveMaxWDWDTenPerc}{TODO}
-\newcommand{\BHNSAboveMaxWDWDTenPerc}{TODO}
-\newcommand{\NSNSAboveMaxWDWDTenPerc}{TODO}
-
-% number of systems that can be determined as either a BH or NS
-\newcommand{\BHBHEitherBHOrNSFour}{11}
-\newcommand{\BHNSEitherBHOrNSFour}{6}
-\newcommand{\NSNSEitherBHOrNSFour}{3}
-\newcommand{\BHBHEitherBHOrNSTen}{TODO}
-\newcommand{\BHNSEitherBHOrNSTen}{TODO}
-\newcommand{\NSNSEitherBHOrNSTen}{TODO}
-\newcommand{\BHBHEitherBHOrNSFourPerc}{14}
-\newcommand{\BHNSEitherBHOrNSFourPerc}{13}
-\newcommand{\NSNSEitherBHOrNSFourPerc}{35}
-\newcommand{\BHBHEitherBHOrNSTenPerc}{TODO}
-\newcommand{\BHNSEitherBHOrNSTenPerc}{TODO}
-\newcommand{\NSNSEitherBHOrNSTenPerc}{TODO}
+\newcommand{\BHBHTenYear}{118}
+\newcommand{\BHNSTenYear}{71}
+\newcommand{\NSNSTenYear}{13}
 
@@
 \newcommand{\BHBHLowerMassGap}{35\%}
-\newcommand{\BHNSLowerMassGap}{38\%}
+\newcommand{\BHNSLowerMassGap}{39\%}
 
@@
 % percentage of systems with e > 0.01
-\newcommand{\BHBHNotCirc}{86\%}
-\newcommand{\BHNSNotCirc}{47\%}
+\newcommand{\BHBHNotCirc}{87\%}
+\newcommand{\BHNSNotCirc}{46\%}
 \newcommand{\NSNSNotCirc}{86\%}
@@
 % percentage of systems with e > 0.3
-\newcommand{\BHBHHighlyEccentric}{22\%}
+\newcommand{\BHBHHighlyEccentric}{21\%}
 \newcommand{\BHNSHighlyEccentric}{8\%}
@@
 
+% number of systems with fractional chirp mass uncertainty < 1
+\newcommand{\BHBHChirpMassMeasureableFour}{20}
+\newcommand{\BHNSChirpMassMeasureableFour}{17}
+\newcommand{\NSNSChirpMassMeasureableFour}{4}
+\newcommand{\BHBHChirpMassMeasureableTen}{52}
+\newcommand{\BHNSChirpMassMeasureableTen}{44}
+\newcommand{\NSNSChirpMassMeasureableTen}{9}
+
+% percentage of systems above Chandrasekhar mass
+\newcommand{\BHBHAboveMaxWDWDFourPerc}{24}
+\newcommand{\BHNSAboveMaxWDWDFourPerc}{28}
+\newcommand{\NSNSAboveMaxWDWDFourPerc}{4}
+\newcommand{\BHBHAboveMaxWDWDTenPerc}{38}
+\newcommand{\BHNSAboveMaxWDWDTenPerc}{41}
+\newcommand{\NSNSAboveMaxWDWDTenPerc}{5}
+
 % percentage of systems with something other than 1 detectable harmonic
 \newcommand{\BHBHMultipleHarmonicsFourPerc}{55}
-\newcommand{\BHNSMultipleHarmonicsFourPerc}{28}
+\newcommand{\BHNSMultipleHarmonicsFourPerc}{27}
 \newcommand{\NSNSMultipleHarmonicsFourPerc}{66}
-\newcommand{\BHBHMultipleHarmonicsTenPerc}{TODO}
-\newcommand{\BHNSMultipleHarmonicsTenPerc}{TODO}
-\newcommand{\NSNSMultipleHarmonicsTenPerc}{TODO}
+\newcommand{\BHBHMultipleHarmonicsTenPerc}{61}
+\newcommand{\BHNSMultipleHarmonicsTenPerc}{29}
+\newcommand{\NSNSMultipleHarmonicsTenPerc}{68}
 
@@
 \newcommand{\BHBHEccInDiscFourPerc}{40}
-\newcommand{\BHNSEccInDiscFourPerc}{25}
-\newcommand{\NSNSEccInDiscFourPerc}{60}
-\newcommand{\BHBHEccInDiscTenPerc}{TODO}
-\newcommand{\BHNSEccInDiscTenPerc}{TODO}
-\newcommand{\NSNSEccInDiscTenPerc}{TODO}
+\newcommand{\BHNSEccInDiscFourPerc}{23}
+\newcommand{\NSNSEccInDiscFourPerc}{59}
+\newcommand{\BHBHEccInDiscTenPerc}{40}
+\newcommand{\BHNSEccInDiscTenPerc}{23}
+\newcommand{\NSNSEccInDiscTenPerc}{59}
 
-% percentage of systems with fractional chirp mass uncertainty < 1
-\newcommand{\BHBHChirpMassMeasureable}{20}
-\newcommand{\BHNSChirpMassMeasureable}{17}
-\newcommand{\NSNSChirpMassMeasureable}{4}
+% number of systems that are definitely not WDWDs
+\newcommand{\BHBHNotWDWDFour}{37}
+\newcommand{\BHNSNotWDWDFour}{18}
+\newcommand{\NSNSNotWDWDFour}{5}
+\newcommand{\BHBHNotWDWDTen}{70}
+\newcommand{\BHNSNotWDWDTen}{38}
+\newcommand{\NSNSNotWDWDTen}{8}
+
+% number of systems that can be determined as either a BH or NS
+\newcommand{\BHBHEitherBHOrNSFour}{16}
+\newcommand{\BHNSEitherBHOrNSFour}{7}
+\newcommand{\NSNSEitherBHOrNSFour}{4}
+\newcommand{\BHBHEitherBHOrNSTen}{39}
+\newcommand{\BHNSEitherBHOrNSTen}{17}
+\newcommand{\NSNSEitherBHOrNSTen}{8}
+\newcommand{\BHBHEitherBHOrNSFourPerc}{21}
+\newcommand{\BHNSEitherBHOrNSFourPerc}{18}
+\newcommand{\NSNSEitherBHOrNSFourPerc}{47}
+\newcommand{\BHBHEitherBHOrNSTenPerc}{33}
+\newcommand{\BHNSEitherBHOrNSTenPerc}{24}
+\newcommand{\NSNSEitherBHOrNSTenPerc}{62}
+
+\newcommand{\BHBHatLeastOneLowerMassGapPerc}{69}
+\newcommand{\BHNSatLeastOneLowerMassGapPerc}{39}
+\newcommand{\NSNSatLeastOneLowerMassGapPerc}{0}
+\newcommand{\ALLatLeastOneLowerMassGapPerc}{55}
 
@@
 
-\section{Results I - Fiducial} \label{sec:results}
+\section{Results I - Predictions for LISA sources} \label{sec:results}
 \input{sections/results.tex}
 
-\section{Results II - Model variations} \label{sec:variations}
+\section{Results II - Impact of physics assumptions} \label{sec:variations}
 \input{sections/variations.tex}
@@
 Available at \url{http://www.python.org}.
-In addition the following Python packages were used: matplotlib \citep{Hunter+2007},  {NumPy} \citep{vanderWalt+2011}, SciPy \citep{Virtanen+2020}, Jupyter Lab \citep{Kluyver+2016}, seaborn \citep{Waskom+2020}, h5py \citep{Collette+2021} and Astropy \citep[\url{http://www.astropy.org}][]{AstropyCollaboration+2013, AstropyCollaboration+2018}.
+In addition the following Python packages were used: matplotlib (\url{https://matplotlib.org/}), {NumPy} (\url{https://numpy.org/}), SciPy (\url{https://www.scipy.org/}), Jupyter Lab (\url{https://jupyter.org/}), seaborn (\url{https://seaborn.pydata.org/}), h5py (https://www.h5py.org/) and Astropy (\url{http://www.astropy.org}).
 This research has made use of NASA’s Astrophysics Data System Bibliographic Services.

### 2021-08-19 paper/tex/sections/variations.tex
BIG COMMIT: lots of changes from Selma
update variations to match noBHkick models

@@
 See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.
-\todo{Will add R, T once Floor says that they are done}}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:detection_rates}
@@
 
-\todo{Discuss $\alpha_{\rm CE}$ changes once I understand them (:}
+\todo{Discuss $\alpha_{\rm CE}$ changes}
 
@@
 
-\todo{ensure this noBHkick description still applies} In model \modNoBH{} we do not give black holes natal kicks.
-Rate is higher than fiducial for BHBH and BHNS but slightly lower than model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
+In model \modNoBH{} we do not give black holes natal kicks.
+For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample.
+For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
 NSNSs are unaffected as one would assume.
@@
 
-\subsubsection{Using LISA to investigate the lower mass gap}
+\subsubsection{Using LISA to investigate the lower mass gap}\label{sec:lower_mass_gap}
 
@@
 
-% \begin{table}[htb]
-%     \centering
-%     \begin{tabular}{l|cccc}
-%         \hline
-%         \multirow{2}{*}{Component} & At Formation & \multicolumn{3}{c}{LISA detectable (4 year)} \\ \cline{2-5}
-%         & All & BHBH & BHNS & NSNS \\
-%         \hline
-%         Low-$\alpha$ disc & 42.5\% & 88.6\% & 81.8\% & 84.9\%\\
-%         High-$\alpha$ disc & 42.5\% & 5.2\% & 8.1\% & 12.0\%\\
-%         Bulge & 15.0\% & 6.2\% & 10.1\% & 3.1\%\\
-%     \end{tabular}
-%     \caption{Percentage of systems in each Galactic component.}
-% \end{table}
+\subsubsection{Effect mass loss rate multiplier on the (chirp) mass distribution}
+
+{\bf Selma would like this one}

### 2021-08-19 paper/tex/sections/results.tex
update variations to match noBHkick models
WR wind text and more

@@
 
-\todo{Remove curved line.}
-
 \subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
@@
 
-A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Appendix~XX).
+A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Fig.~\ref{fig:progenitor_and_dco_properties}).
 Stellar winds are stronger at high metallicity leading to increased mass loss.
@@
 
+\todo{@Selma suggests we return to this section. NSs do \textbf{NOT} receive stronger natal kicks in our simulations since most are formed through ECSN e.g. and have 30km/s instead of 265km/s. }
+
 \paragraph{Time since formation} 
@@
 Nevertheless, we do find a significant fraction of detectable systems originate in the high-$\alpha$ disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).
+
+% \newcolumntype{Y}{>{\centering\arraybackslash}X}
+% \begin{table}[tb]
+%     \centering
+%     \begin{tabularx}{\columnwidth}{l|Y Y Y}
+%         \hline
+%         \multirow{2}{*}{Threshold} & \multicolumn{3}{c}{Individually detectable harmonics} \\ \cline{2-4}
+%         & 0 & 1 & 2+ \\
+%         \hline
+%         $\mathrm{SNR} > 7$ & 18\%  & 67\% & 15\% \\
+%         $\mathrm{SNR} > 3$ &  8\%  & 54\% & 38\% \\
+%         $\mathrm{SNR} > 1$ &  4\%  & 30\% & 66\% \\
+%     \end{tabularx}
+%     \caption{Percentage of systems with individual harmonics above different SNR thresholds.}
+%     \label{tab:test}
+% \end{table}
 
@@
 Progenitor distribution figure is Fig.~\ref{fig:progenitor_and_dco_properties}.
-
-\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}
 

### 2021-08-19 paper/tex/sections/variations.tex
WR wind text and more

@@
 \subsubsection{Stellar wind variation trends}
+We decrease the efficiency of Wolf-Rayet winds to 10\% in model \modWRLow{}.
+We find that decreasing the efficiency of these winds actually has very little effect on our predicted detection rates.
+This due to a combination of cancelling effects.
+
+Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA.
+Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries.
+However, though this \textit{is} the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at \textit{lower} frequencies than in our fiducial model.
+This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times.
+This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.
+Finally, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged).
+The increase in eccentricity for NSNSs comes from the same reason as the lower frequency, more recent birth times mean that binaries have less time to circularise.
+The same is not true for BHBHs as the more massive systems are less affected by supernova kicks and so fewer high eccentricity systems are formed.
+
+Overall, despite the large differences in the system properties, these three effects in combination leave the detection rates relatively unchanged.
+
+In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5.
+In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged.
+Increasing the efficiency of WR winds strongly decreases the final masses of DCOs.
+This means that many progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH (therefore this effect is stronger on BHBHs than NSNSs).
+Moreover, DCOs that are formed tend to be less massive and therefore less detectable.
 
@@
 
-{\bf Selma would like this one}
+\todo{Selma would like this one}

### 2021-08-19 paper/tex/sections/variations.tex
add wr variation plot

@@
 
-\todo{Discuss $\alpha_{\rm CE}$ changes}
+\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here}
 
@@
     \includegraphics[width=\columnwidth]{fig9_ecc_low_kick_variation.pdf}
-    \caption{As lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions}, but for model \modSigLower{}.
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}d, but for model \modSigLower{}.
 For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines.
@@
 
+\subsubsection{Effect of mass loss efficiency on mass distribution}
+
+\begin{figure}[tb]
+    \centering
+    \includegraphics[width=\columnwidth]{wr_wind_mass_variations.pdf}
+    \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}).
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+    \label{fig:wr_wind_mass_variations}
+\end{figure}
+
+In Fig.~\ref{fig:wr_wind_mass_variations} we show the effect that changing the efficiency of Wolf-Rayet winds has on the individual component mass distribution.
+Decreasing the Wolf-Rayet wind efficiency allows the formation of more massive DCOs in the Milky Way and, indeed, we see that the distribution extends to $25 \unit{M_{\odot}}$ and fewer detectable systems are formed at low masses.
+By contrast, increasing the Wolf-Rayet efficiency by a factor of 5 strongly disfavours the formation of systems at high masses and approximately 85\% of detectable systems have masses below $5 \unit{M_{\odot}}$.
+These three distributions are very distinct and so it is possible that the mass distribution of LISA could help to constrain the efficiency of Wolf-Rayet winds.
+
 \subsubsection{Other interesting features}
 \todo{maybe add CE model stuff}
-
-\subsubsection{Effect mass loss rate multiplier on the (chirp) mass distribution}
-
-\todo{Selma would like this one}

### 2021-08-27 paper/tex/sections/introduction.tex
small changes from comments

@@
 
-Traditionally, investigations into detecting stellar-mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
+Traditionally, predictions about the detection of stellar-mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}.
 More recently, interest has grown in the detection of NS and BH binaries.

### 2021-08-27 paper/tex/sections/variations.tex
small changes from comments

@@
 
-\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here}
+\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here.
+UPDATE: this is almost entirely a formation rate thing rather than a detection rate trend so we can focus on that}
 

### 2021-08-27 paper/figure_notebooks/bootstrap.py
remove a todo

@@ -55,7 +55,8 @@ class MirroredKDE(gaussian_kde):
             return kde_vals
 
 
-def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None, lower_bound=None, upper_bound=None,
+def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None, normalisation=1,
+                     lower_bound=None, upper_bound=None,
                      bootstraps=200, x_min=None, x_max=None, x_count=200, log_scale=(False, False),
                      color="tab:blue", label=None, **kwargs):
     """Create a bootstrapped weighted KDE plot.
@@ -124,7 +125,7 @@ def bootstrapped_kde(variable, weights, seeds, ax, bw_adjust=None, lower_bound=N
 
         kde = MirroredKDE(loop_variable[boot_index], weights=loop_weights[boot_index],
                           lower_bound=lower_bound, upper_bound=upper_bound, bw_adjust=bw_adjust)
-        kde_vals[i] = kde.evaluate(x_vals)
+        kde_vals[i] = kde.evaluate(x_vals) * normalisation
 
     # calculate 1- and 2- sigma percentiles
     percentiles = np.percentile(kde_vals, [15.89, 84.1, 2.27, 97.725], axis=0)

### 2021-09-28 paper/tex/sections/appendix.tex
random changes

@@
 \end{figure*}
+
+\begin{sidewaystable}
+    \centering
+    \begin{tabular}{c|ccccccccc|ccccccccc}
+        \hline
+        \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
+        \cline{2-9} \cline{10-19}
+        & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
+        \cline{2-9} \cline{10-19}
+        & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+        \hline
+        A & 0.15 & 0.11 & 0.68 & 0.23 & 0.15 & 0.65 & 0.29 & 0.24 & 0.61 & 0.12 & 0.10 & 0.59 & 0.18 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
+B & 0.15 & 0.10 & 0.68 & 0.22 & 0.16 & 0.66 & 0.31 & 0.23 & 0.48 & 0.13 & 0.10 & 0.59 & 0.17 & 0.13 & 0.55 & 0.24 & 0.20 & 0.48 \\
+C & 0.15 & 0.10 & 0.69 & 0.20 & 0.14 & 0.68 & 0.29 & 0.24 & 0.49 & 0.13 & 0.10 & 0.59 & 0.16 & 0.12 & 0.58 & 0.24 & 0.20 & 0.49 \\
+D & 0.18 & 0.09 & 0.64 & 0.21 & 0.13 & 0.65 & 0.31 & 0.24 & 0.44 & 0.16 & 0.08 & 0.54 & 0.17 & 0.11 & 0.53 & 0.25 & 0.20 & 0.47 \\
+E & 0.15 & 0.12 & 0.70 & 0.14 & 0.15 & 0.76 & 0.22 & 0.25 & 0.76 & 0.12 & 0.10 & 0.61 & 0.11 & 0.14 & 0.67 & 0.17 & 0.22 & 0.74 \\
+F & 0.19 & 0.09 & 0.63 & 0.08 & 0.22 & 0.91 & 0.04 & 0.35 & 0.96 & 0.16 & 0.07 & 0.53 & 0.07 & 0.24 & 0.86 & 0.04 & 0.36 & 0.96 \\
+G & 0.15 & 0.10 & 0.68 & 0.17 & 0.17 & 0.75 & 0.27 & 0.24 & 0.55 & 0.13 & 0.09 & 0.59 & 0.14 & 0.14 & 0.66 & 0.22 & 0.20 & 0.57 \\
+H & 0.14 & 0.11 & 0.69 & 0.19 & 0.20 & 0.70 & 0.32 & 0.24 & 0.37 & 0.12 & 0.09 & 0.59 & 0.16 & 0.18 & 0.60 & 0.26 & 0.20 & 0.40 \\
+I & 0.14 & 0.10 & 0.69 & 0.24 & 0.16 & 0.65 & 0.28 & 0.24 & 0.64 & 0.12 & 0.09 & 0.60 & 0.18 & 0.13 & 0.54 & 0.22 & 0.19 & 0.63 \\
+J & 0.14 & 0.11 & 0.70 & 0.17 & 0.16 & 0.75 & 0.29 & 0.24 & 0.49 & 0.12 & 0.10 & 0.60 & 0.13 & 0.14 & 0.67 & 0.23 & 0.20 & 0.51 \\
+K & 0.19 & 0.08 & 0.64 & 0.25 & 0.15 & 0.63 & 0.25 & 0.24 & 0.67 & 0.16 & 0.08 & 0.53 & 0.18 & 0.12 & 0.53 & 0.19 & 0.19 & 0.63 \\
+L & 0.18 & 0.08 & 0.63 & 0.22 & 0.15 & 0.68 & 0.27 & 0.24 & 0.66 & 0.16 & 0.08 & 0.53 & 0.17 & 0.12 & 0.57 & 0.21 & 0.21 & 0.67 \\
+M & 0.14 & 0.13 & 0.72 & 0.23 & 0.16 & 0.64 & 0.28 & 0.24 & 0.59 & 0.12 & 0.11 & 0.62 & 0.19 & 0.13 & 0.53 & 0.23 & 0.20 & 0.60 \\
+N & 0.16 & 0.10 & 0.66 & 0.22 & 0.14 & 0.66 & 0.28 & 0.23 & 0.61 & 0.14 & 0.09 & 0.57 & 0.18 & 0.13 & 0.55 & 0.21 & 0.19 & 0.60 \\
+O & 0.15 & 0.11 & 0.69 & 0.23 & 0.15 & 0.65 & 0.28 & 0.24 & 0.61 & 0.13 & 0.10 & 0.59 & 0.18 & 0.12 & 0.54 & 0.22 & 0.19 & 0.61 \\
+P & 0.19 & 0.09 & 0.64 & 0.24 & 0.14 & 0.64 & 0.27 & 0.22 & 0.61 & 0.15 & 0.08 & 0.53 & 0.19 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
+Q & 0.18 & 0.09 & 0.64 & 0.26 & 0.15 & 0.60 & 0.29 & 0.23 & 0.57 & 0.17 & 0.08 & 0.54 & 0.20 & 0.12 & 0.49 & 0.22 & 0.19 & 0.56 \\
+R & 0.15 & 0.10 & 0.68 & 0.24 & 0.15 & 0.63 & 0.27 & 0.23 & 0.60 & 0.12 & 0.10 & 0.59 & 0.19 & 0.12 & 0.50 & 0.21 & 0.18 & 0.59 \\
+S & 0.18 & 0.08 & 0.65 & 0.20 & 0.13 & 0.68 & 0.23 & 0.22 & 0.71 & 0.16 & 0.08 & 0.54 & 0.17 & 0.12 & 0.57 & 0.18 & 0.19 & 0.70 \\
+T & 0.16 & 0.09 & 0.70 & 0.23 & 0.15 & 0.62 & 0.33 & 0.25 & 0.43 & 0.13 & 0.08 & 0.60 & 0.18 & 0.12 & 0.50 & 0.26 & 0.20 & 0.45 \\
+        \hline
+    \end{tabular}
+    \caption{A table}
+\end{sidewaystable}

### 2021-09-28 paper/tex/paper.tex
WR wind text and more

@@
 \usepackage{wrapfig}
+\usepackage{tabularx}
+\usepackage[figuresright]{rotating}
 
@@
 TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
-This project was funded in part by the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
+This project was funded in part by the National Science Foundation under Grant No.
+(NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
 715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.

### 2021-09-28 paper/tex/sections/methods.tex

@@
 \citet{Sharma+2020} showed that using a simple continuous model for both the low- and high-\achem~discs, the Milky Way abundance distributions could be well reproduced.
-Empirically, the abundance tracks in the [$\alpha$/Fe]-[Fe/H] plane of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
+Empirically, the abundance tracks in the [$\alpha$/Fe]-[Fe/H] plane (and other elements) of the stars in the bulge/bar follow the same track as those of the old stars in the Solar neighbourhood \citep[][Fig.~7,]{Griffith+2021,Bovy+2019}, which motivates our modelling choice to use the same metallicity-radius-time relation.
 

### 2021-09-30 paper/tex/sections/variations.tex
remove a todo
ce trends

--- 2021-08-19 paper/tex/sections/variations.tex
@@
 
-\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here}
+Models \modAlphaLowest{}-\modAlphaHighest{} alter $\alpha_{\rm CE}$, the common-envelope efficiency parameter, to $0.1, 0.5, 2.0$ and $10.0$ respectively (where the fiducial model has $\alpha_{\rm CE} = 1.0$).
+Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remain largely unchanged.
+Therefore, any changes in the detection rate are due to changes in the \textit{formation} rate of the DCOs.
+
+\todo{Explain formation rate differences with $\alpha_{\rm CE}$ changes.
+I'm pretty sure this comes down to higher alpha leading to larger separations but also fewer stellar mergers and this affects NSNSs and BHBH/BHNSs differently since the ejection of the envelope is very mass dependent.
+I'm making plots to show this (got sidetracked by orientation)}
 
@@
 This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased.
-Therefore, we find that, though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
+Therefore, similar to models \modAlphaLowest{}-\modAlphaHighest{}, we find that though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
 
@@
 These three distributions are very distinct and so it is possible that the mass distribution of LISA could help to constrain the efficiency of Wolf-Rayet winds.
-
-\subsubsection{Other interesting features}
-\todo{maybe add CE model stuff}

### 2021-10-10 paper/tex/sections/variations.tex
update ce trend explanation

@@
 In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
-For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates}.
+For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates} and for a plot of the rates relative to the fiducial model see Fig.~\ref{fig:dco_relative_rates}.
 
@@
 Models \modAlphaLowest{}-\modAlphaHighest{} alter $\alpha_{\rm CE}$, the common-envelope efficiency parameter, to $0.1, 0.5, 2.0$ and $10.0$ respectively (where the fiducial model has $\alpha_{\rm CE} = 1.0$).
-Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remain largely unchanged.
+Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remains largely unchanged.
 Therefore, any changes in the detection rate are due to changes in the \textit{formation} rate of the DCOs.
 
-\todo{Explain formation rate differences with $\alpha_{\rm CE}$ changes.
-I'm pretty sure this comes down to higher alpha leading to larger separations but also fewer stellar mergers and this affects NSNSs and BHBH/BHNSs differently since the ejection of the envelope is very mass dependent.
-I'm making plots to show this (got sidetracked by orientation)}
+Altering $\alpha_{\rm CE}$ has two major effects on the formation rate of double compact objects.
+Recall that $\alpha_{\rm CE}$ represents the fraction of the orbital energy that is available for the ejection of the common-envelope.
+Therefore, increasing $\alpha_{\rm CE}$ allows common-envelope ejection to occur at larger separations (since more energy is available at any given separation).
+A second effect of increasing $\alpha_{\rm CE}$ is that common-envelopes are less likely to result in stellar mergers as more energy is available for envelope ejection.
+We can understand the trends in formation rate of the three DCO types by considering these two effects.
+
+The BHBH rate peaks for $\alpha_{\rm CE} = 1$ (model \modFid{}) and reduces whether we increase \textit{or} decrease $\alpha_{\rm CE}$.
+This is because the increase in $\alpha_{\rm CE}$ shifts a significant fraction of the population to such large separations that they no longer merge within a Hubble time.
+Although the number of stellar mergers decreases as well, the overall change in the merging BHBH formation rate is negative.
+The inverse is also true for decreasing $\alpha_{\rm CE}$, where BHBHs have shorter separations but stellar mergers are more frequent.
+Thus we find that $\alpha_{\rm CE} = 1$ seems to be optimal for BHBHs by balancing these two effects most effectively.
+
+The BHNS rate follows the same pattern as BHBHs.
+This is expected since the BH is formed first for every BHNS in our sample and so the common-envelope event is due to a RLOF of BH progenitor, just as with BHBHs.
+However, given the similarity in the BHNS rates between $\alpha_{\rm CE} = 1$ and $\alpha_{\rm CE} = 2$ (models \modFid{} and \modAlphaHigh{}), the `optimal' $\alpha_{\rm CE}$ for BHNSs seems to be somewhere between 1 and 2 rather than very close to 1 as with BHBHs.
+
+In contrast, $\alpha_{\rm CE} = 1$ is far from optimal for NSNSs.
+Increasing $\alpha_{\rm CE}$ (models \modAlphaHigh{} and \modAlphaHighest{}) results in significantly higher rates.
+This is because LISA detectable NSNSs tend to have been formed very recently before detection (see Fig.~\ref{fig:fiducial_pdf_distributions}e).
+Therefore, though higher $\alpha_{\rm CE}$ results in larger \textit{initial} separations, this does not adversely affect the NSNS rate as the systems are simply detected later after their formation compared to the fiducial model.
+So for models \modAlphaHigh{} and \modAlphaHighest{}, fewer systems result in stellar mergers and the overall population remains within the LISA band, producing much higher detection rates.
+%Finally, for model \modAlphaLowest{}, the reduction in common-envelope efficiency is strong enough that a sufficient number of systems are formed at shorter separations to offset those lost to stellar mergers.
 

### 2021-10-10 paper/tex/sections/results.tex
fix explanation of NSNS no high ecc systems

@@
 We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}.
-See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption
+See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption.
 
@@
 
-The lower abundance of highly eccentric systems among the NSNS and BHNS systems may seem counter-intuitive since neutron stars receive stronger natal kicks, which one may expect to lead to more eccentric systems.
-However, in practice, these stronger kicks often disrupt these systems.
-
-\todo{@Selma suggests we return to this section. NSs do \textbf{NOT} receive stronger natal kicks in our simulations since most are formed through ECSN e.g. and have 30km/s instead of 265km/s. }
+The lower abundance of highly eccentric systems among the NSNS and BHNS systems may seem counter-intuitive since neutron stars are lower mass and would be more strongly affected by natal kicks, which one may expect to lead to more eccentric systems.
+However, the majority of NSs in our simulations are formed through ECSN and USSN and for these types of supernovae we draw from a Maxwellian with $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$.
+Thus the kicks received by NSs in our simulations are often much smaller than for BHs.
 

### 2021-10-10 paper/tex/sections/results.tex
clean up time since formation section

@@
 \paragraph{Time since formation} 
-In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the DCOs detectable by LISA formed.
+In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the LISA detectable DCOs formed.
 For comparison we show the star formation history we have assumed in our Milky Way model (grey dotted line).
 Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.
-In contrast, the DCOs detectable by LISA primarily formed in the relatively \textit{recent} history of our Milky Way, about $2 \unit{Gyr}$ ago.
-This reflects the fact that binaries in our simulation typically take about a Gyr to merge, a result as is commonly found also in other population synthesis studies.
+In contrast, the LISA detectable DCOs primarily formed in the relatively \textit{recent} history of our Milky Way, about $2 \unit{Gyr}$ ago.
+This reflects the fact that binaries in our simulation typically take about a Gyr to merge.
 
@@
 \begin{equation}
-    t_{\rm inspiral} = \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
+    t_{\rm inspiral} \propto \frac{a^4}{(m_1 + m_2)^{3}} \cdot \frac{q}{(1+q)^2} \cdot (1 - e^2)^{-7/2}.
 \end{equation}
-The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly, see Fig.~\ref{fig:progenitor_and_dco_properties}.
+The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:progenitor_and_dco_properties}).
 The NSNS systems have the tightest orbits at DCO formation.
@@
 The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations.
-The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and is not of interest.
+The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest.
 The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$.
 The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:progenitor_and_dco_properties}.
-%
-We conclude that the shorter median separations at DCO formation are the main reason why NSNS are most strongly peaked at short delay times, followed by BHBH where the inspiral timescales are short because of their high masses and substantial eccentricities.
 
-In addition to the peak at recent times, we see that all three distributions have a large extended tail of systems that formed through out the history of the milky way, most prominently for the BHNS systems.
-For the BHBH and BHNS we find that the peak at very recent formation times comes from systems formed through stable mass transfer that obtained very high eccentricities.
-The long tail is a mixture of channels.
-
-\todo{Can we do a little better in understanding the tail?}
-
-\todo{I also think this section has become \textit{very} dense...but can't see how to make it better}
+We conclude that the shorter median separations at DCO formation are the main reason why NSNS are most strongly peaked at short delay times.
+They are followed by BHBHs rather than BHNSs due to the high masses and substantial eccentricities of BHBHs.
 

### 2021-10-12 paper/tex/sections/variations.tex
minor changes to variations

@@
 
-\begin{figure*}[p]
-    \centering
-    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
-    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
-Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties.
-An arrow indicates that the error bar extends to zero.
-The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
-See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
-    \label{fig:detection_rates}
-\end{figure*}
-
 \subsubsection{Mass transfer variation trends}
@@
 For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease.
-This may seem unintuitive since one may assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population.
-However, this contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
+This may seem unintuitive since one might assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population.
+However, this increase contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
 Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.
@@
 This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.
+
+\begin{figure*}[p]
+    \centering
+    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
+    \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
+Error bars show the 1- (solid) and 2-$\sigma$ (dotted) Poisson uncertainties.
+An arrow indicates that the error bar extends to zero.
+The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
+Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
+See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+    \label{fig:detection_rates}
+\end{figure*}
 
@@
 For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-NSNSs are unaffected as one would assume.
+NSNSs are unaffected as one would assume due to the absence of BHs.
 
@@
 In Figure~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions.
-The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption.
+The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption (model \modFid{}).
 This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap.
@@
 In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs.
-For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see lower left panel of Fig.~\ref{fig:fiducial_pdf_distributions} for full comparison).
+For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see Fig.~\ref{fig:fiducial_pdf_distributions}d for full comparison).
 In the main curves, we reduce the velocity dispersion for core-collapse supernovae from $265 \unit{km}{s^{-1}}$ to $30 \unit{km}{s^{-1}}$ (model \modSigLower{}).

### 2021-10-12 paper/tex/sections/methods.tex
add methods paper bib entry

@@
 
-We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.
-(in prep).
+We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in prep).
 This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}.
 COMPAS follows the approach of the population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
-The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper (Team COMPAS: J.\ Riley et al.\ in prep).
+The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper \citep{COMPAS:2021methodsPaper}.
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.

### 2021-10-12 paper/tex/sections/appendix.tex
prep the big table
add methods paper bib entry
add lieke paper to bib file

@@
 We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars, and set $f_{\rm WR} = 1$.
-See Team COMPAS: J.
-Riley et al.
-(in prep), Section 3 for the explicit equations.
+See \citet{COMPAS:2021methodsPaper}, Section 3 for the explicit equations.
 
@@
 We vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
-These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations (e.g.
-\citet{Vink+2017}, \citet{Hamann+2019}, \citet{Shenar+2019}, \citet{Miller-Jones+2021} and van Son et al.
-(in prep)).
+These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations \citep[e.g.][]{Vink+2017, Hamann+2019, Shenar+2019, Miller-Jones+2021, vanSon+2021}.
 
@@
 
+% \begin{sidewaystable}
+%     \centering
+%     \begin{tabular}{c|ccccccccc|ccccccccc}
+%         \hline
+%         \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
+%         \cline{2-9} \cline{10-19}
+%         & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
+%         \cline{2-9} \cline{10-19}
+%         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+%         \hline
+%         A & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} \\
+%         \hline
+%     \end{tabular}
+%     \caption{A table}
+% \end{sidewaystable}
+
 \begin{sidewaystable}

### 2021-10-12 paper/tex/sections/introduction.tex
add lieke paper to bib file

@@
 In a companion paper, Wagg et al.
-(in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+2021b (in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 

### 2021-10-12 paper/tex/sections/discussion.tex
minor discussion changes

@@
 It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
-The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of more massive DCOs on which we focus in this paper \citep[e.g.][]{Korol+2017}.
+The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}.
 It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
@@
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
-We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by even more since each of the more numerous sources are better measured.
+
+We highlight here that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by a greater factor since each of the more numerous sources are better measured.
+This further underlines the benefits of extending the LISA mission to 10 years.
 
@@
 Following our fiducial assumption, we can take the maximum mass of a neutron star as $2.5 \unit{M_{\odot}}$ and thus the maximum chirp mass that a system can attain without one of the components being a black hole is $\mathcal{M}_{c} = 2.2 \unit{M_\odot}$.
-For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit (and thus \textit{must} contain or not contain a BH component respectively) by more than $\Delta \mathcal{M}_c$ is \BHBHEitherBHOrNSFourPerc{}(\BHBHEitherBHOrNSTenPerc{})\% for BHBHs, \BHNSEitherBHOrNSFourPerc{}(\BHNSEitherBHOrNSTenPerc{})\% for BHNSs and \NSNSEitherBHOrNSFourPerc{}(\NSNSEitherBHOrNSTenPerc{})\% of NSNSs, which in terms of absolute detections is \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) for BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) for BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) for NSNSs.
+For a 4(10)-year LISA mission, the fraction of systems that are above or below this limit (and thus \textit{must} respectively contain or not contain a BH component) by more than $\Delta \mathcal{M}_c$ is \BHBHEitherBHOrNSFourPerc{}(\BHBHEitherBHOrNSTenPerc{})\% for BHBHs, \BHNSEitherBHOrNSFourPerc{}(\BHNSEitherBHOrNSTenPerc{})\% for BHNSs and \NSNSEitherBHOrNSFourPerc{}(\NSNSEitherBHOrNSTenPerc{})\% of NSNSs, which in terms of absolute detections is \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) for BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) for BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) for NSNSs.
 
@@
 \subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
-Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main form of electromagnetic counterpart for the this population is pulsars.
+Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main type of electromagnetic counterpart for this population is pulsars.
 Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar.

### 2021-10-12 paper/tex/sections/conclusion.tex
clean up conclusions

@@
 Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} a LISA detectable DCO contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
+    \item \textbf{Benefits of extended LISA mission:} We show that the number of detections scales approximately as $\sqrt{T_{\rm obs}}$ and that population parameters are better measured when extending the LISA mission, in agreement with previous papers.
+We additionally highlight that the number of detections that are distinguishable from WDWDs scales more strongly with $T_{\rm obs}$ than $\sqrt{T_{\rm obs}}$.
+    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} a LISA detectable DCO contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 11 LISA DCOs that contain a NS, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
 This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
     \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
-The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate.
+The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate and an underestimation of the BHNS detection rate.
 It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.

### 2021-10-12 paper/tex/sections/abstract.tex
update abstract

@@
 We present predictions for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
-We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with an empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
+We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
 We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics.
 We predict that for a 4(10)-year mission, LISA will (typically) detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-The predicted BHBH rate remains notably consistent under different physics assumptions, whilst in contrast the BHNS and NSNS rates each vary over 3 orders of magnitude.
+The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions).
+We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged.
 We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population as well as for disentangling the BHBH, BHNS and NSNS populations from each other.

### 2021-10-12 paper/tex/sections/conclusion.tex
updates to conclusion with Selma

--- 2021-07-26 paper/tex/sections/conclusion.tex
@@
 Our main conclusions can be summarised as:
-\begin{itemize}
-    \item \textbf{Detection rate:} We find that on average, for our fiducial model, a 4(10)-year LISA mission will detect \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs and \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-    \item \textbf{Black hole mass distribution:} We find that the black hole mass distribution for both BHBHs and BHNSs that are detectable with LISA are not skewed towards heavier masses (as in current ground-based detectors), with 90\% having BH masses less than $11 \unit{M_\odot}$.
-Moreover, we find that for LISA detectable DCOs, $\BHBHLowerMassGap{}$ of BHBHs and $\BHNSLowerMassGap{}$ of BHNSs have masses in the theoretical lower mass gap between NSs and BHs.
-This implies that LISA will be able provide conclusive evidence about the existence of a lower mass gap.
-    \item \textbf{Eccentricity distribution:} We find that BH and NS binaries still have significant eccentricities when observable by the LISA mission, unlike the more numerous WDWD LISA population.
-We predict that for the observed population \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
-    \item \textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
+\begin{enumerate}
+    \item \textbf{Detections:} We predict 30-300 detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
+Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered.
+
+    Specifically, our fiducial model predicts a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs.
+The errors quoted here are the $1$-$\sigma$ Poisson uncertainties resulting from the random initialisation of the Milky Way (see Table~\ref{tab:detection_rates}).
+
+    \item \textbf{Benefits of extended LISA mission} Increasing the LISA mission length to 10 years results increases the number of detections to about 50-500 detections, a 60\% increase, because the number of detections scale approximately as $T_{\rm obs}^{0.5}$.
+%    
+    However, the real benefit is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$  for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
+
+    We find an increase of a factor 2.4 for the number of systems with chirp masses that can be measured better than 10\%. 
+%    
+    The number of systems with a sky localisation better than one degree increases by about 50\%.
+%    
+    The number of sources that can be unambiguously distinguished from WDWDs increases by almost a factor 2 (see Section~\ref{sec:WDWD_distinguish}).
+
+    \item \textbf{Probing the black hole mass distribution and the lower mass gap:} We expect LISA to predominantly detect lower mass BHs (with 90\% of BHBH and BHNSs having BH masses lower than $11 \unit{M_\odot}$ in our fiducial simulations) in stark contrast to current ground-based detectors which are heavily biased towards high mass systems.
+This implies that LISA can potentially make important contributions to the debate about the existence of a lower mass gap (\citealt{Shao+2021} and see our Fig.~\ref{fig:lower_mass_gap_variation}).
+
+    \item \textbf{Eccentricity distribution:} We find that for all DCO types a large fraction of detectable systems still have nonzero eccentricities ($e = 0.01$) when entering the LISA band, unlike what is expected for the more numerous WDWD LISA population.
+In particular, we find that this is the case for the vast majority of BHBHs and NSNSs and nearly half of BHNSs.
+Furthermore, over a fifth of detectable BHBHs have eccentricities large enough such that their primary gravitational wave emission occurs in a higher harmonic ($e > 0.3$).
+
+    % We predict that for the observed population \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
+    \item \sout{\textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
 Conversely, the BHNS detection rate varies widely with physics variation, ranging across three orders of magnitude.
-The NSNS detection rate shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.
-    \item \textbf{Distinguishable sources:} For a 4(10)-year LISA mission we estimate that, of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
+The NSNS detection rate shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.} - We have now said most of this is point 1.
+We could additionally talk about \textit{which} assumptions are causing the largest variations.
+    \item \textbf{Source identification:} For a 4(10)-year LISA mission we estimate that, of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
 Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} a LISA detectable DCO contains a pulsar that is beaming towards Earth, SKA-1 will be able to detect at least 10 LISA DCOs that contain a NS, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
-This total could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
+    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} every LISA detectable DCO contained a pulsar that is beaming towards Earth, SKA-1 would be able to detect at least 11 of these objects, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
+This number is a pessimistic estimate and could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
     \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
-The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate.
+The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate and an underestimation of the BHNS detection rate.
 It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.
-\end{itemize}
+\end{enumerate}

### 2021-10-13 paper/tex/sections/appendix.tex
updates to conclusion with Selma
update detection rate table

@@
     \frac{\Delta f_{\rm orb}}{f_{\rm orb}} &= 4 \sqrt{3} \cdot \frac{1}{\rho} \frac{1}{T_{\rm obs}} \frac{1}{f_{\rm orb}}, \\
-    \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm dom}},
+    \frac{\Delta \dot{f}_{\rm dom}}{\dot{f}_{\rm dom}} &= 6 \sqrt{5} \cdot \frac{1}{\rho} \left(\frac{1}{T_{\rm obs}} \right)^2 \frac{1}{\dot{f}_{\rm dom}},\label{eq:f_orb_dot_unc}
 \end{align}
@@
 % \subsection{Detection rate table}
+
 \begin{table*}[htb]
@@
     \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type.
+The `All' column contains the total expected detections when summed over the three types.
 Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
-    \begin{tabular}{cl|lll|lll}
+    \begin{tabular}{cl|cccc|cccc}
         \hline
-        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{3}{c|}{LISA detections (4 year)} & \multicolumn{3}{c}{LISA detections (10 year)} \\ \cline{3-8}
-        & & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+        \multirow{2}{*}{Model} & \multirow{2}{*}{DESC} & \multicolumn{4}{c|}{LISA detections (4 year)} & \multicolumn{4}{c}{LISA detections (10 year)} \\ \cline{3-10}
+        & & {All} & {BHBH} & {BHNS} & {NSNS} &
+        {All} &
+        {BHBH} & {BHNS} & {NSNS} \\
         \hline
-        A & Fiducial & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
-        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
-        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
-        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
-        E & Case BB mass transfer is always unstable & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
-        F & Model E + Model K & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
-        G & CE efficiency $\alpha = 0.1$ & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
-        H & CE efficiency $\alpha = 0.5$ & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
-        I & CE efficiency $\alpha = 2.0$ & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
-        J & CE efficiency $\alpha = 10.0$ & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
-        K & HG donor stars initiating a CE survive CE & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
-        L & Fryer rapid SN remnant mass prescription & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
-        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
-        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
-        O & PISN and pulsational-PISN not implemented & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
-        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
-        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for core-collapse supernova & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
-        R & Black holes receive not natal kick & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
-        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
-        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \confinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
+        A & Fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
+        B & $\beta=0.25$ & \confinv{94.1}{10.1}{9.9} & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{149.3}{12.3}{12.7} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
+        C & $\beta=0.5$ & \confinv{59.2}{8.2}{7.8} & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{95.9}{9.9}{10.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
+        D & $\beta=0.75$ & \confinv{67.0}{8.0}{8.0} & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{104.5}{10.5}{10.5} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
+        E & Case BB unstable & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
+        F & E+K & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
+        G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
+        H & $\alpha_{\rm CE}=0.5$ & \confinv{85.9}{8.9}{9.1} & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{136.2}{11.2}{11.8} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
+        I & $\alpha_{\rm CE}=2.0$ & \confinv{133.3}{11.3}{11.7} & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{218.4}{14.4}{14.6} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
+        J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
+        K & Optimistic
+        CE & \confinv{218.3}{15.3}{14.7} & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{341.5}{18.5}{18.5} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
+        L & Fryer Rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
+        M & Max $m_{\rm NS}$
+        $2.0 \, {\rm M_{\odot}}$ & \confinv{133.5}{11.5}{11.5} & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{215.2}{14.2}{14.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
+        N & Max $m_{\rm NS}$
+        $3.0 \, {\rm M_{\odot}}$ & \confinv{118.4}{10.4}{10.6} & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{189.9}{13.9}{14.1} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
+        O & No PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
+        P & $\sigma_{\rm cc}$
+        $100 \, {\rm km s^{-1}}$ & \confinv{184.6}{13.6}{13.4} & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{300.8}{17.8}{17.2} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
+        Q & $\sigma_{\rm cc}$
+        $30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
+        R & No BH
+        kicks & \confinv{230.2}{15.2}{14.8} & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{372.7}{19.7}{19.3} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
+        S & $f_{\rm WR} = 0.1$ & \confinv{118.5}{10.5}{10.5} & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{182.5}{13.5}{13.5} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
+        T & $f_{\rm WR} = 5$ & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
         \hline

### 2021-10-13 paper/tex/sections/appendix.tex
add min/max to table

@@
 The `All' column contains the total expected detections when summed over the three types.
+The final two rows show the minimum and maximum rates across all model variations.
 Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.
@@
         \hline
-        \multirow{2}{*}{Model} & \multirow{2}{*}{DESC} & \multicolumn{4}{c|}{LISA detections (4 year)} & \multicolumn{4}{c}{LISA detections (10 year)} \\ \cline{3-10}
+        \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{4}{c|}{LISA detections (4 year)} & \multicolumn{4}{c}{LISA detections (10 year)} \\ \cline{3-10}
         & & {All} & {BHBH} & {BHNS} & {NSNS} &
@@
         \hline
+        - & Minimum rate & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{2.1}{1.1}{1.9} & \confinv{0.2}{0.2}{0.8} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{3.5}{1.5}{1.5} & \confinv{0.4}{0.4}{0.6} \\
+        - & Maximum rate & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{34.9}{5.9}{6.1} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{229.0}{15.0}{15.0} & \confinv{57.2}{7.2}{7.8} \\
+        \hline
+
     \end{tabular}
@@
 
-\begin{sidewaystable}
-    \centering
-    \begin{tabular}{c|ccccccccc|ccccccccc}
-        \hline
-        \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
-        \cline{2-9} \cline{10-19}
-        & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
-        \cline{2-9} \cline{10-19}
-        & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-        \hline
-        A & 0.15 & 0.11 & 0.68 & 0.23 & 0.15 & 0.65 & 0.29 & 0.24 & 0.61 & 0.12 & 0.10 & 0.59 & 0.18 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
-B & 0.15 & 0.10 & 0.68 & 0.22 & 0.16 & 0.66 & 0.31 & 0.23 & 0.48 & 0.13 & 0.10 & 0.59 & 0.17 & 0.13 & 0.55 & 0.24 & 0.20 & 0.48 \\
-C & 0.15 & 0.10 & 0.69 & 0.20 & 0.14 & 0.68 & 0.29 & 0.24 & 0.49 & 0.13 & 0.10 & 0.59 & 0.16 & 0.12 & 0.58 & 0.24 & 0.20 & 0.49 \\
-D & 0.18 & 0.09 & 0.64 & 0.21 & 0.13 & 0.65 & 0.31 & 0.24 & 0.44 & 0.16 & 0.08 & 0.54 & 0.17 & 0.11 & 0.53 & 0.25 & 0.20 & 0.47 \\
-E & 0.15 & 0.12 & 0.70 & 0.14 & 0.15 & 0.76 & 0.22 & 0.25 & 0.76 & 0.12 & 0.10 & 0.61 & 0.11 & 0.14 & 0.67 & 0.17 & 0.22 & 0.74 \\
-F & 0.19 & 0.09 & 0.63 & 0.08 & 0.22 & 0.91 & 0.04 & 0.35 & 0.96 & 0.16 & 0.07 & 0.53 & 0.07 & 0.24 & 0.86 & 0.04 & 0.36 & 0.96 \\
-G & 0.15 & 0.10 & 0.68 & 0.17 & 0.17 & 0.75 & 0.27 & 0.24 & 0.55 & 0.13 & 0.09 & 0.59 & 0.14 & 0.14 & 0.66 & 0.22 & 0.20 & 0.57 \\
-H & 0.14 & 0.11 & 0.69 & 0.19 & 0.20 & 0.70 & 0.32 & 0.24 & 0.37 & 0.12 & 0.09 & 0.59 & 0.16 & 0.18 & 0.60 & 0.26 & 0.20 & 0.40 \\
-I & 0.14 & 0.10 & 0.69 & 0.24 & 0.16 & 0.65 & 0.28 & 0.24 & 0.64 & 0.12 & 0.09 & 0.60 & 0.18 & 0.13 & 0.54 & 0.22 & 0.19 & 0.63 \\
-J & 0.14 & 0.11 & 0.70 & 0.17 & 0.16 & 0.75 & 0.29 & 0.24 & 0.49 & 0.12 & 0.10 & 0.60 & 0.13 & 0.14 & 0.67 & 0.23 & 0.20 & 0.51 \\
-K & 0.19 & 0.08 & 0.64 & 0.25 & 0.15 & 0.63 & 0.25 & 0.24 & 0.67 & 0.16 & 0.08 & 0.53 & 0.18 & 0.12 & 0.53 & 0.19 & 0.19 & 0.63 \\
-L & 0.18 & 0.08 & 0.63 & 0.22 & 0.15 & 0.68 & 0.27 & 0.24 & 0.66 & 0.16 & 0.08 & 0.53 & 0.17 & 0.12 & 0.57 & 0.21 & 0.21 & 0.67 \\
-M & 0.14 & 0.13 & 0.72 & 0.23 & 0.16 & 0.64 & 0.28 & 0.24 & 0.59 & 0.12 & 0.11 & 0.62 & 0.19 & 0.13 & 0.53 & 0.23 & 0.20 & 0.60 \\
-N & 0.16 & 0.10 & 0.66 & 0.22 & 0.14 & 0.66 & 0.28 & 0.23 & 0.61 & 0.14 & 0.09 & 0.57 & 0.18 & 0.13 & 0.55 & 0.21 & 0.19 & 0.60 \\
-O & 0.15 & 0.11 & 0.69 & 0.23 & 0.15 & 0.65 & 0.28 & 0.24 & 0.61 & 0.13 & 0.10 & 0.59 & 0.18 & 0.12 & 0.54 & 0.22 & 0.19 & 0.61 \\
-P & 0.19 & 0.09 & 0.64 & 0.24 & 0.14 & 0.64 & 0.27 & 0.22 & 0.61 & 0.15 & 0.08 & 0.53 & 0.19 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
-Q & 0.18 & 0.09 & 0.64 & 0.26 & 0.15 & 0.60 & 0.29 & 0.23 & 0.57 & 0.17 & 0.08 & 0.54 & 0.20 & 0.12 & 0.49 & 0.22 & 0.19 & 0.56 \\
-R & 0.15 & 0.10 & 0.68 & 0.24 & 0.15 & 0.63 & 0.27 & 0.23 & 0.60 & 0.12 & 0.10 & 0.59 & 0.19 & 0.12 & 0.50 & 0.21 & 0.18 & 0.59 \\
-S & 0.18 & 0.08 & 0.65 & 0.20 & 0.13 & 0.68 & 0.23 & 0.22 & 0.71 & 0.16 & 0.08 & 0.54 & 0.17 & 0.12 & 0.57 & 0.18 & 0.19 & 0.70 \\
-T & 0.16 & 0.09 & 0.70 & 0.23 & 0.15 & 0.62 & 0.33 & 0.25 & 0.43 & 0.13 & 0.08 & 0.60 & 0.18 & 0.12 & 0.50 & 0.26 & 0.20 & 0.45 \\
-        \hline
-    \end{tabular}
-    \caption{A table}
-\end{sidewaystable}
+% \begin{sidewaystable}
+%     \centering
+%     \begin{tabular}{c|ccccccccc|ccccccccc}
+%         \hline
+%         \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
+%         \cline{2-9} \cline{10-19}
+%         & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
+%         \cline{2-9} \cline{10-19}
+%         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
+%         \hline
+%         A & 0.15 & 0.11 & 0.68 & 0.23 & 0.15 & 0.65 & 0.29 & 0.24 & 0.61 & 0.12 & 0.10 & 0.59 & 0.18 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
+% B & 0.15 & 0.10 & 0.68 & 0.22 & 0.16 & 0.66 & 0.31 & 0.23 & 0.48 & 0.13 & 0.10 & 0.59 & 0.17 & 0.13 & 0.55 & 0.24 & 0.20 & 0.48 \\
+% C & 0.15 & 0.10 & 0.69 & 0.20 & 0.14 & 0.68 & 0.29 & 0.24 & 0.49 & 0.13 & 0.10 & 0.59 & 0.16 & 0.12 & 0.58 & 0.24 & 0.20 & 0.49 \\
+% D & 0.18 & 0.09 & 0.64 & 0.21 & 0.13 & 0.65 & 0.31 & 0.24 & 0.44 & 0.16 & 0.08 & 0.54 & 0.17 & 0.11 & 0.53 & 0.25 & 0.20 & 0.47 \\
+% E & 0.15 & 0.12 & 0.70 & 0.14 & 0.15 & 0.76 & 0.22 & 0.25 & 0.76 & 0.12 & 0.10 & 0.61 & 0.11 & 0.14 & 0.67 & 0.17 & 0.22 & 0.74 \\
+% F & 0.19 & 0.09 & 0.63 & 0.08 & 0.22 & 0.91 & 0.04 & 0.35 & 0.96 & 0.16 & 0.07 & 0.53 & 0.07 & 0.24 & 0.86 & 0.04 & 0.36 & 0.96 \\
+% G & 0.15 & 0.10 & 0.68 & 0.17 & 0.17 & 0.75 & 0.27 & 0.24 & 0.55 & 0.13 & 0.09 & 0.59 & 0.14 & 0.14 & 0.66 & 0.22 & 0.20 & 0.57 \\
+% H & 0.14 & 0.11 & 0.69 & 0.19 & 0.20 & 0.70 & 0.32 & 0.24 & 0.37 & 0.12 & 0.09 & 0.59 & 0.16 & 0.18 & 0.60 & 0.26 & 0.20 & 0.40 \\
+% I & 0.14 & 0.10 & 0.69 & 0.24 & 0.16 & 0.65 & 0.28 & 0.24 & 0.64 & 0.12 & 0.09 & 0.60 & 0.18 & 0.13 & 0.54 & 0.22 & 0.19 & 0.63 \\
+% J & 0.14 & 0.11 & 0.70 & 0.17 & 0.16 & 0.75 & 0.29 & 0.24 & 0.49 & 0.12 & 0.10 & 0.60 & 0.13 & 0.14 & 0.67 & 0.23 & 0.20 & 0.51 \\
+% K & 0.19 & 0.08 & 0.64 & 0.25 & 0.15 & 0.63 & 0.25 & 0.24 & 0.67 & 0.16 & 0.08 & 0.53 & 0.18 & 0.12 & 0.53 & 0.19 & 0.19 & 0.63 \\
+% L & 0.18 & 0.08 & 0.63 & 0.22 & 0.15 & 0.68 & 0.27 & 0.24 & 0.66 & 0.16 & 0.08 & 0.53 & 0.17 & 0.12 & 0.57 & 0.21 & 0.21 & 0.67 \\
+% M & 0.14 & 0.13 & 0.72 & 0.23 & 0.16 & 0.64 & 0.28 & 0.24 & 0.59 & 0.12 & 0.11 & 0.62 & 0.19 & 0.13 & 0.53 & 0.23 & 0.20 & 0.60 \\
+% N & 0.16 & 0.10 & 0.66 & 0.22 & 0.14 & 0.66 & 0.28 & 0.23 & 0.61 & 0.14 & 0.09 & 0.57 & 0.18 & 0.13 & 0.55 & 0.21 & 0.19 & 0.60 \\
+% O & 0.15 & 0.11 & 0.69 & 0.23 & 0.15 & 0.65 & 0.28 & 0.24 & 0.61 & 0.13 & 0.10 & 0.59 & 0.18 & 0.12 & 0.54 & 0.22 & 0.19 & 0.61 \\
+% P & 0.19 & 0.09 & 0.64 & 0.24 & 0.14 & 0.64 & 0.27 & 0.22 & 0.61 & 0.15 & 0.08 & 0.53 & 0.19 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
+% Q & 0.18 & 0.09 & 0.64 & 0.26 & 0.15 & 0.60 & 0.29 & 0.23 & 0.57 & 0.17 & 0.08 & 0.54 & 0.20 & 0.12 & 0.49 & 0.22 & 0.19 & 0.56 \\
+% R & 0.15 & 0.10 & 0.68 & 0.24 & 0.15 & 0.63 & 0.27 & 0.23 & 0.60 & 0.12 & 0.10 & 0.59 & 0.19 & 0.12 & 0.50 & 0.21 & 0.18 & 0.59 \\
+% S & 0.18 & 0.08 & 0.65 & 0.20 & 0.13 & 0.68 & 0.23 & 0.22 & 0.71 & 0.16 & 0.08 & 0.54 & 0.17 & 0.12 & 0.57 & 0.18 & 0.19 & 0.70 \\
+% T & 0.16 & 0.09 & 0.70 & 0.23 & 0.15 & 0.62 & 0.33 & 0.25 & 0.43 & 0.13 & 0.08 & 0.60 & 0.18 & 0.12 & 0.50 & 0.26 & 0.20 & 0.45 \\
+%         \hline
+%     \end{tabular}
+%     \caption{A table}
+% \end{sidewaystable}

### 2021-10-14 paper/tex/sections/conclusion.tex
change most of the conclusions with selma :)

@@
 We provide predictions for the detection rate and population properties of LISA detectable BHBH, BHNS and NSNS.
-To this end, we use the rapid population synthesis code COMPAS to simulate over two billion massive binaries, to explore the effect of varying underlying physics assumptions that represent the most common uncertainties in binary physics.
-We use an new empirically-informed analytical model to distribute the resulting BHBH, BHNS and NSNS populations in a Milky-Way like galaxy based on their birth metallicity, in order to estimate and investigate the LISA detectable population of BH and NS binaries.
-
-Our main conclusions can be summarised as:
+%
+We use a novel empirically-informed analytical model for the metallicity dependent star formation history of the Milky Way, calibrated against large-scale, stellar spectroscopic survey APOGEE.
+(Sec.~\ref{sec:galaxy_synthesis}).
+We use this to model Monte-Carlo realisations of the present-day BHBH, BHNS and NSNS populations in our Milky Way.
+%
+For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS.
+These simulations have been optimised with the adaptive sampling algorithm STROOPWAFEL to preferentially sample NS and BH binaries.
+In total these comprise over two billion massive binaries that span 20 physics variations, which represent the most common uncertainties in binary physics.
+%
+To determine the detectability of sources with LISA we use LEGWORK package (Wagg et al.\ in prep), that was specifically developed for this purpose and is publicly available. 
+%
+We investigate the results expected for a 4- and 10-year LISA mission. Our main conclusions can be summarised as:
 \begin{enumerate}
@@
 
-    \item \textbf{Benefits of extended LISA mission} Increasing the LISA mission length to 10 years results increases the number of detections to about 50-500 detections, a 60\% increase, because the number of detections scale approximately as $T_{\rm obs}^{0.5}$.
+    \item \textbf{Benefits of extended LISA mission:} Increasing the LISA mission length to 10 years results increases the number of detections to about 50-500 detections, a 60\% increase, because the number of detections scale approximately as $T_{\rm obs}^{0.5}$.
+
+    The real benefit, however, is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$  for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
 %    
-    However, the real benefit is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$  for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
-
     We find an increase of a factor 2.4 for the number of systems with chirp masses that can be measured better than 10\%. 
@@
     % We predict that for the observed population \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
-    \item \sout{\textbf{Physics variations:} For BHBHs, we find that the detection rate is largely unaffected by changes in underlying physics assumptions, except for the optimistic CE scenario and increased Wolf-Rayet winds.
-Conversely, the BHNS detection rate varies widely with physics variation, ranging across three orders of magnitude.
-The NSNS detection rate shows some variation but only shows large changes under the assumption that case BB mass transfer is unstable and that core-collapse supernovae produce weaker kicks.} - We have now said most of this is point 1.
-We could additionally talk about \textit{which} assumptions are causing the largest variations.
-    \item \textbf{Source identification:} For a 4(10)-year LISA mission we estimate that, of the detectable population, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
-Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole.
-    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} every LISA detectable DCO contained a pulsar that is beaming towards Earth, SKA-1 would be able to detect at least 11 of these objects, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
+    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related the onset of the common-envelope phase and the efficiency of ejection have a strong impact on the rate predictions.
+This is also true for models where we reduce the natal kicks.
+Finally, our models where we have increased the strength of the Wolf-Rayet winds, drastically reduces the number of systems containing a BH (see Fig.~\ref{fig:detection_rates})
+    \item \textbf{Distinguishing from WDWD sources:} For about half of all detections we expect that we will be able to confidently determine the type of compact objects involved (and this increases to 60\% for a 10-year LISA mission), see Sec.~\ref{sec:WDWD_distinguish}.
+
+    \item \textbf{Chirp mass determinations:} For about 10\% of systems we expect to be able to determine the chirp mass better than 10\% (and this increases to 15\% for a 10-year LISA mission), see Fig.~\ref{fig:m_c_unc}.
+
+%    Based on our fiducial model we estimate that, for a 4(10)-year LISA mission, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
+%    Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole (see Sec.~\ref{sec:identify_sources}).
+The absolute number of systems that we can distinguish in different models changes, but the relative fraction remains roughly constant.
+
+    \item \textbf{Prospects for finding EM counterparts:} We expect about 13\% of detections with a sky localisation better than 1 degree.
+Increasing the LISA mission length increases the number, but the fraction stays roughly the same.
+This will be of interest for electromagnetic counterpart searches, in particular for radio pulsar searches with SKA.
+
+%    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} every LISA detectable DCO contained a pulsar that is beaming towards Earth, SKA-1 would be able to detect at least 11 of these objects, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
 This number is a pessimistic estimate and could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
-    \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
+
+ %   \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
 The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate and an underestimation of the BHNS detection rate.

### 2021-10-16 paper/tex/sections/conclusion.tex
final conclusion changes

@@
 %
-We use a novel empirically-informed analytical model for the metallicity dependent star formation history of the Milky Way, calibrated against large-scale, stellar spectroscopic survey APOGEE.
-(Sec.~\ref{sec:galaxy_synthesis}).
+We use a novel empirically-informed analytical model for the metallicity dependent star formation history of the Milky Way, calibrated against the APOGEE stellar spectroscopic survey.
 We use this to model Monte-Carlo realisations of the present-day BHBH, BHNS and NSNS populations in our Milky Way.
@@
 \begin{enumerate}
-    \item \textbf{Detections:} We predict 30-300 detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
+    \item \textbf{Total detections:} We predict 30-300 detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
+This increases to about 50-500 for a 10-year LISA mission.
 Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered.
 
-    Specifically, our fiducial model predicts a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs.
+     \item \textbf{Detections by type:} Specifically, our fiducial model predicts a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs.
 The errors quoted here are the $1$-$\sigma$ Poisson uncertainties resulting from the random initialisation of the Milky Way (see Table~\ref{tab:detection_rates}).
 
-    \item \textbf{Benefits of extended LISA mission:} Increasing the LISA mission length to 10 years results increases the number of detections to about 50-500 detections, a 60\% increase, because the number of detections scale approximately as $T_{\rm obs}^{0.5}$.
-
-    The real benefit, however, is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$  for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
-%    
-    We find an increase of a factor 2.4 for the number of systems with chirp masses that can be measured better than 10\%. 
-%    
-    The number of systems with a sky localisation better than one degree increases by about 50\%.
-%    
-    The number of sources that can be unambiguously distinguished from WDWDs increases by almost a factor 2 (see Section~\ref{sec:WDWD_distinguish}).
+    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related the onset of the common-envelope phase and the efficiency of ejection have a strong impact on the rate predictions.
+This is also true for models where we reduce the natal kicks.
+Finally, our models where we have increased the strength of the Wolf-Rayet winds, drastically reduces the number of systems containing a BH (see Fig.~\ref{fig:detection_rates})
 
@@
 
-    \item \textbf{Eccentricity distribution:} We find that for all DCO types a large fraction of detectable systems still have nonzero eccentricities ($e = 0.01$) when entering the LISA band, unlike what is expected for the more numerous WDWD LISA population.
-In particular, we find that this is the case for the vast majority of BHBHs and NSNSs and nearly half of BHNSs.
-Furthermore, over a fifth of detectable BHBHs have eccentricities large enough such that their primary gravitational wave emission occurs in a higher harmonic ($e > 0.3$).
+    \item \textbf{Eccentricity distribution:} We find that for all DCO types a large fraction of detectable systems still have nonzero eccentricities ($e = 0.01$) when entering the LISA band, which can be used to distinguish them from the more numerous WDWD binaries, which are largely expected to be circular.
+In particular, for our fiducial model, we find that this is the case for around three quarters of detectable binaries.
+Furthermore, around 16\% of detectable binaries have eccentricities that are so high that the emission at frequencies corresponding to higher order harmonics start to dominate ($e > 0.3$).
 
-    % We predict that for the observed population \BHBHNotCirc{}(\BHBHHighlyEccentric{}) of BHBHs, \BHNSNotCirc{}(\BHNSHighlyEccentric{}) of BHNSs and \NSNSNotCirc{}(\NSNSHighlyEccentric{})\% of NSNSs have eccentricity of $e > 0.01(0.3)$ at the start of the LISA mission.
-    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related the onset of the common-envelope phase and the efficiency of ejection have a strong impact on the rate predictions.
-This is also true for models where we reduce the natal kicks.
-Finally, our models where we have increased the strength of the Wolf-Rayet winds, drastically reduces the number of systems containing a BH (see Fig.~\ref{fig:detection_rates})
     \item \textbf{Distinguishing from WDWD sources:} For about half of all detections we expect that we will be able to confidently determine the type of compact objects involved (and this increases to 60\% for a 10-year LISA mission), see Sec.~\ref{sec:WDWD_distinguish}.
@@
 It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.
+
+   \item \textbf{Benefits of extended LISA mission:} The number of detections scale approximately as $T_{\rm obs}^{0.5}$, where $T_{\rm obs}$ is the mission length.
+Therefore, extending the LISA mission from 4- to 10-years increases the number of detections by about 60\%.
+   A further important benefit is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$ for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
+   We find that the number of systems with chirp masses that can be measured better than 10\% increases by a factor of 2.4.
+   In addition, the number of systems with a sky localisation better than one degree increases by a factor of 1.5.
+   Overall, the number of sources that can be unambiguously distinguished from WDWDs increases by almost a factor of 2 (see Section~\ref{sec:WDWD_distinguish}).
 \end{enumerate}

### 2021-10-16 paper/tex/sections/appendix.tex
change most of the conclusions with selma :)
clean up all of the figures

@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/fig11_random_simple_galaxy.png}
+    \includegraphics[width=\columnwidth]{fig14_random_simple_galaxy.png}
     \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
     \label{fig:simple_mw}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../figures/fig12_mBH_simple_mw_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig15_mBH_simple_mw_variation.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.
 Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:bh_mass_simple_mw}
@@
         \hline
-        A & Fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
+        A & fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
 B & $\beta=0.25$ & \confinv{94.1}{10.1}{9.9} & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{149.3}{12.3}{12.7} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
@@
 D & $\beta=0.75$ & \confinv{67.0}{8.0}{8.0} & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{104.5}{10.5}{10.5} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
-        E & Case BB unstable & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \confinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \confinv{0.4}{0.4}{0.6}\\
-        F & E+K & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
-        G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \confinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \confinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
+E & unstable
+case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
+F & E+K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
+G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \boldconfinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \boldconfinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
 H & $\alpha_{\rm CE}=0.5$ & \confinv{85.9}{8.9}{9.1} & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{136.2}{11.2}{11.8} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
 I & $\alpha_{\rm CE}=2.0$ & \confinv{133.3}{11.3}{11.7} & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{218.4}{14.4}{14.6} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
-        J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \confinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \confinv{57.2}{7.2}{7.8}\\
-        K & Optimistic
+J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \boldconfinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \boldconfinv{57.2}{7.2}{7.8}\\
+K & optimistic
 CE & \confinv{218.3}{15.3}{14.7} & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{341.5}{18.5}{18.5} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
-        L & Fryer Rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
-        M & Max $m_{\rm NS}$
+L & rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
+M & max $m_{\rm NS}$
 $2.0 \, {\rm M_{\odot}}$ & \confinv{133.5}{11.5}{11.5} & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{215.2}{14.2}{14.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
-        N & Max $m_{\rm NS}$
+N & max $m_{\rm NS}$
 $3.0 \, {\rm M_{\odot}}$ & \confinv{118.4}{10.4}{10.6} & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{189.9}{13.9}{14.1} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
-        O & No PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
+O & no PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
 P & $\sigma_{\rm cc}$
@@
 Q & $\sigma_{\rm cc}$
-        $30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \confinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
-        R & No BH
+$30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \boldconfinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
+R & no BH
 kicks & \confinv{230.2}{15.2}{14.8} & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{372.7}{19.7}{19.3} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
 S & $f_{\rm WR} = 0.1$ & \confinv{118.5}{10.5}{10.5} & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{182.5}{13.5}{13.5} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
-        T & $f_{\rm WR} = 5$ & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
+T & $f_{\rm WR} = 5$ & \boldconfinv{29.7}{5.7}{5.3} & \boldconfinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \boldconfinv{48.8}{6.8}{7.2} & \boldconfinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
 \hline 
@@
         \hline
-
     \end{tabular}
@@
 \end{table*}
-
-% \subsection{Distribution of eccentric sources on sensitivity curve}
-\begin{figure*}[b]
-    \centering
-    \includegraphics[width=\textwidth]{fig13_dcos_on_sc_eccentric_colours.png}
-    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
-We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
-    \label{fig:dcos_on_sc_ecc_col}
-\end{figure*}
 
@@
     \centering
-    \includegraphics[height=0.85\textheight]{fig15_formation_channels.pdf}
+    \includegraphics[height=0.85\textheight]{fig16_formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
@@
 The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig16_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
     \label{fig:formation_channels}
 \end{figure}
+
+% \subsection{Distribution of eccentric sources on sensitivity curve}
+\begin{figure*}[b]
+    \centering
+    \includegraphics[width=\textwidth]{fig17_dcos_on_sc_eccentric_colours.png}
+    \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
+We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig17_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
+    \label{fig:dcos_on_sc_ecc_col}
+\end{figure*}
 
@@
     \centering
-    \includegraphics[width=\textwidth]{progenitor_distributions.pdf}
-    \includegraphics[width=0.66\textwidth]{dco_formation_distributions.pdf}
+    \includegraphics[width=0.66\textwidth]{fig18_dco_formation_distributions.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row).
 Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig18_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:progenitor_and_dco_properties}
@@
     \centering
-    \includegraphics[width=\textwidth]{fig14_dco_relative_rates.pdf}
+    \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}
     \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
 The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig19_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
     \label{fig:dco_relative_rates}

### 2021-10-16 paper/tex/sections/comparisons.tex
clean up all of the figures

@@
     \centering
-    \includegraphics[width=\textwidth]{fig10_1_compare_dco.png}
+    \includegraphics[width=\textwidth]{fig13_1_compare_dco.png}
 
@@
 
-    \includegraphics[width=\textwidth]{fig10_2_compare_dco.png}
+    \includegraphics[width=\textwidth]{fig13_2_compare_dco.png}
     \caption{A table comparing previous studies of a similar nature to this work.
 The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_w_compare_dco.png}{\faFileImage}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_w_compare_dco.png}{\faFileImage}.}
     \label{fig:previous_studies}

### 2021-10-16 paper/tex/sections/results.tex
adjust other todos
clean up all of the figures

@@
 
+In Figure~\ref{fig:progenitor_properties}, we show some properties of the progenitors of the LISA detectable DCOs.
+The top panel shows the inital primary mass and is plotted on a log-scale.
+We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$.
+In contrast,
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{fig5_progenitor_distributions.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and inital mass ratio (bottom).
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \label{fig:progenitor_properties}
+\end{figure}
+
 Formation channel figure is Fig.~\ref{fig:formation_channels}.
 
-Progenitor distribution figure is Fig.~\ref{fig:progenitor_and_dco_properties}.
+\todo{@Selma will review this section}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig5_snr_cumulative_all.pdf}
+    \includegraphics[width=\columnwidth]{fig6_snr_cumulative_all.pdf}
     \caption{Cumulative number of LISA detections with a given signal-to-noise ratio.
 Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:snr_dist}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig5_chirp_mass_uncertainty_all.pdf}
+    \includegraphics[width=\columnwidth]{fig7_chirp_mass_uncertainty_all.pdf}
     \caption{As Fig.~\ref{fig:snr_dist}, but for the chirp mass uncertainty.
 The shaded areas indicate regions with more than 10\% and 100\% uncertainty.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:m_c_unc}
@@
 
-\paragraph{Eccentricities}
+% \paragraph{Eccentricities}
 
-\todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}
+% \todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig6_angular_resolution_all.pdf}
+    \includegraphics[width=\columnwidth]{fig8_angular_resolution_all.pdf}
     \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:ang_res}

### 2021-10-16 paper/tex/sections/variations.tex
clean up all of the figures

@@
     \centering
-    \includegraphics[width=\textwidth]{fig7_dco_detections.pdf}
+    \includegraphics[width=\textwidth]{fig9_dco_detections.pdf}
     \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
@@
 See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
     \label{fig:detection_rates}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig8_lower_mass_gap_rapid_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig10_lower_mass_gap_rapid_variation.pdf}
     \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
 Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:lower_mass_gap_variation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig9_ecc_low_kick_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig11_ecc_low_kick_variation.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}d, but for model \modSigLower{}.
 For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:ecc_low_kick_variation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{wr_wind_mass_variations.pdf}
+    \includegraphics[width=\columnwidth]{fig12_wr_wind_mass_variations.pdf}
     \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}).
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:wr_wind_mass_variations}

### 2021-10-16 paper/tex/sections/appendix.tex
further fixes to figure refs/links

@@
     \includegraphics[width=\columnwidth]{fig15_mBH_simple_mw_variation.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions} (top left panel), but for the Milky Way model used in \citet{Breivik+2020}.
-Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions} for comparison.
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}b, but for the Milky Way model used in \citet{Breivik+2020}.
+Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions}b for comparison.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
@@
 % \subsection{Distribution of eccentric sources on sensitivity curve}
-\begin{figure*}[b]
+\begin{figure*}[p]
     \centering
@@
     \label{fig:dcos_on_sc_ecc_col}
-\end{figure*}
 
-% \subsection{Properties of detectable systems (progenitors and at DCO formation)}
-\begin{figure*}[ht]
-    \centering
-    \includegraphics[width=0.66\textwidth]{fig18_dco_formation_distributions.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the progentiors of detectable systems (top row) and the properties of the detectable systems at DCO formation (bottom row).
-Note that the $m_{1, {\rm ZAMS}}$ panel uses a log scaled $y$-axis.
+    \includegraphics[width=0.8\textwidth]{fig18_dco_formation_distributions.pdf}
+    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the detectable systems at DCO formation.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig18_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
-    \label{fig:progenitor_and_dco_properties}
-\end{figure*}
+    \label{fig:dco_formation_properties}
 
-% \subsection{Detection rates relative to fiducial model}
-\begin{figure*}[hb]
-    \centering
     \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}

### 2021-10-16 paper/tex/sections/comparisons.tex
further fixes to figure refs/links

@@
 The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_w_compare_dco.png}{\faFileImage}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_2_compare_dco.png}{\faFileImage}.}
     \label{fig:previous_studies}

### 2021-10-16 paper/tex/sections/results.tex
further fixes to figure refs/links

@@
 
-A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Fig.~\ref{fig:progenitor_and_dco_properties}).
+A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations.
 Stellar winds are stronger at high metallicity leading to increased mass loss.
@@
 \end{equation}
-The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:progenitor_and_dco_properties}).
+The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}).
 The NSNS systems have the tightest orbits at DCO formation.
@@
 The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$.
-The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:progenitor_and_dco_properties}.
+The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.
 
@@
 
-\paragraph{Time until merger} The final panel of Fig.~\ref{fig:fiducial_pdf_distributions} shows the remaining time until merger for each of the DCO types at the start of LISA mission.
+\paragraph{Time until merger} Fig.~\ref{fig:fiducial_pdf_distributions}f shows the remaining time until merger for each of the DCO types at the start of LISA mission.
 The distributions are strikingly similar and peak with merger times of around a Myr.
@@
 Despite the fact that only $42.5\%$ of systems are formed in the low-$\alpha$ disc, we find that $86\%$ of the detections originate from this component.
-This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}) and so the high-$\alpha$ disc and bulge are effectively too old to contribute many detectable systems.
+This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}e) and so the high-$\alpha$ disc and bulge are effectively too old to contribute many detectable systems.
 Nevertheless, we do find a significant fraction of detectable systems originate in the high-$\alpha$ disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).
@@
     \textbf{Bottom:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:detectable_distance_dist}
@@
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and inital mass ratio (bottom).
+Note that the y-axis is log-scaled for the initial primary mass.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}

### 2021-10-16 paper/tex/sections/variations.tex
further fixes to figure refs/links

@@
 See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
     \label{fig:detection_rates}

### 2021-10-16 paper/tex/sections/results.tex
add progenitor description

@@
 We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$.
-In contrast,
+In contrast, BHNSs and BHBHs have extremely high primary progenitor masses, particularly given their final BH masses (see Fig.~\ref{fig:fiducial_pdf_distributions}b).
+These large progenitor masses are often necessary as the high metallicity environment of the Milky Way leads to greater mass loss due to stellar winds and so a greater initial mass is needed to still produce a BH.
+
+The bottom panel of Fig.~\ref{fig:progenitor_properties} shows the initial mass ratio.
+Overall, we find that the progenitors of detectable systems tend to have more unequal mass ratios compared to the final DCOs (c.f.\ Fig.~\ref{fig:fiducial_pdf_distributions}c).
+This is because mass loss due to stellar winds tends to bring the mass ratio closer to unity as the systems evolve.
+Additionally, in contrast to Fig.~\ref{fig:fiducial_pdf_distributions}c, the BHNS distribution is unimodal.
 
@@
 \end{figure}
+
+We show the formation channels through which the detectable DCOs formed in
 

### 2021-10-16 paper/tex/sections/results.tex
add formation channel description

@@
 \subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
+\todo{@Selma will review this section}
 
@@
 
-We show the formation channels through which the detectable DCOs formed in
+We show the fraction of detectable DCOs that formed through different formation channels in Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model that we describe in this section.
+Approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}.
+Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the `classic' channel and the rest are mainly formed through only stable mass transfer.
 
-Formation channel figure is Fig.~\ref{fig:formation_channels}.
-
-\todo{@Selma will review this section}
+In contrast, detectable NSNSs are very rarely formed through only stable mass transfer.
+Approximately half of systems are formed through the `classic' channel and the rest are formed through a double-core common-envelope event \citep{Brown+1995} where both progenitors evolve on a similar timescale and initiate a double-core common-envelope event whilst they are on the giant branch.
+All detectable DCOs show a small fraction of systems are formed through a channel that does not fit into the other categories and hence are labelled `other'.
+These systems tend to be formed through `lucky' supernova kicks that happen to shrink the binary significantly by chance.
 
@@
 
+The chirp mass is important for identifying the type of the source of a detected GW signal.
+The uncertainty of the chirp mass depends on the uncertainty in the measured orbital frequency, the time derivative of the orbital frequency and the eccentricity as detailed in Appendix~\ref{app:chirp_mass_uncertainty}.
+
+We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
+This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
+
+Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
+The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.
+
 \begin{figure}[tb]
@@
 
-The chirp mass is important for identifying the type of the source of a detected GW signal.
-The uncertainty of the chirp mass depends on the uncertainty in the measured orbital frequency, the time derivative of the orbital frequency and the eccentricity as detailed in Appendix~\ref{app:chirp_mass_uncertainty}.
-
-We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
-This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
-
-Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
-The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.
-
-% \paragraph{Eccentricities}
-
-% \todo{SdM: Proposed additional paragraph.... can we say something compact?  You made a large number of plots and estimates..}
-
 \paragraph{Sky localisation}
-
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{fig8_angular_resolution_all.pdf}
-    \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
-    \label{fig:ang_res}
-\end{figure}
 
@@
 We will further discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
+
+\begin{figure}[htb]
+    \centering
+    \includegraphics[width=\columnwidth]{fig8_angular_resolution_all.pdf}
+    \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+    \label{fig:ang_res}
+\end{figure}

### 2021-10-16 paper/tex/sections/appendix.tex
minor updates to appendix captions
resolve outstanding overleaf comments

@@
 %
-In practice, we will use the dominating harmonic, with $n=n_{\rm dom}$ and $f_n =  f_{\rm dom}$.
-The dominating harmonic for circular binaries is $n_{\rm dom} = 2$ and the dominating frequency is twice the orbital frequency.
+In practice, we will use the dominating harmonic, with $n=n_{\rm dom}$ and $f_n = n_{\rm dom} f_{\rm orb} = f_{\rm dom}$.
+The dominating harmonic for circular binaries is $n_{\rm dom} = 2$ and so the dominating frequency is twice the orbital frequency.
 
@@
 The final two rows show the minimum and maximum rates across all model variations.
+We embolden the corresponding rate for convenience of seeing which variation results in the minimum/maximum.
 Each value shows the mean and the 1-$\sigma$ Poisson uncertainty.
@@
         \multirow{2}{*}{Model} & \multirow{2}{*}{Description} & \multicolumn{4}{c|}{LISA detections (4 year)} & \multicolumn{4}{c}{LISA detections (10 year)} \\ \cline{3-10}
-        & & {All} & {BHBH} & {BHNS} & {NSNS} &
-        {All} &
-        {BHBH} & {BHNS} & {NSNS} \\
+        & & {All} & {BHBH} & {BHNS} & {NSNS} & {All} & {BHBH} & {BHNS} & {NSNS} \\
         \hline
@@
 
-% \subsection{Formation channels}
-
 \begin{figure}[p]
@@
 
-% \subsection{Distribution of eccentric sources on sensitivity curve}
 \begin{figure*}[p]
@@
 \end{figure*}
-
-% \begin{sidewaystable}
-%     \centering
-%     \begin{tabular}{c|ccccccccc|ccccccccc}
-%         \hline
-%         \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
-%         \cline{2-9} \cline{10-19}
-%         & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
-%         \cline{2-9} \cline{10-19}
-%         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-%         \hline
-%         A & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} & \scriptsize{42} \\
-%         \hline
-%     \end{tabular}
-%     \caption{A table}
-% \end{sidewaystable}
-
-% \begin{sidewaystable}
-%     \centering
-%     \begin{tabular}{c|ccccccccc|ccccccccc}
-%         \hline
-%         \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
-%         \cline{2-9} \cline{10-19}
-%         & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
-%         \cline{2-9} \cline{10-19}
-%         & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
-%         \hline
-%         A & 0.15 & 0.11 & 0.68 & 0.23 & 0.15 & 0.65 & 0.29 & 0.24 & 0.61 & 0.12 & 0.10 & 0.59 & 0.18 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
-% B & 0.15 & 0.10 & 0.68 & 0.22 & 0.16 & 0.66 & 0.31 & 0.23 & 0.48 & 0.13 & 0.10 & 0.59 & 0.17 & 0.13 & 0.55 & 0.24 & 0.20 & 0.48 \\
-% C & 0.15 & 0.10 & 0.69 & 0.20 & 0.14 & 0.68 & 0.29 & 0.24 & 0.49 & 0.13 & 0.10 & 0.59 & 0.16 & 0.12 & 0.58 & 0.24 & 0.20 & 0.49 \\
-% D & 0.18 & 0.09 & 0.64 & 0.21 & 0.13 & 0.65 & 0.31 & 0.24 & 0.44 & 0.16 & 0.08 & 0.54 & 0.17 & 0.11 & 0.53 & 0.25 & 0.20 & 0.47 \\
-% E & 0.15 & 0.12 & 0.70 & 0.14 & 0.15 & 0.76 & 0.22 & 0.25 & 0.76 & 0.12 & 0.10 & 0.61 & 0.11 & 0.14 & 0.67 & 0.17 & 0.22 & 0.74 \\
-% F & 0.19 & 0.09 & 0.63 & 0.08 & 0.22 & 0.91 & 0.04 & 0.35 & 0.96 & 0.16 & 0.07 & 0.53 & 0.07 & 0.24 & 0.86 & 0.04 & 0.36 & 0.96 \\
-% G & 0.15 & 0.10 & 0.68 & 0.17 & 0.17 & 0.75 & 0.27 & 0.24 & 0.55 & 0.13 & 0.09 & 0.59 & 0.14 & 0.14 & 0.66 & 0.22 & 0.20 & 0.57 \\
-% H & 0.14 & 0.11 & 0.69 & 0.19 & 0.20 & 0.70 & 0.32 & 0.24 & 0.37 & 0.12 & 0.09 & 0.59 & 0.16 & 0.18 & 0.60 & 0.26 & 0.20 & 0.40 \\
-% I & 0.14 & 0.10 & 0.69 & 0.24 & 0.16 & 0.65 & 0.28 & 0.24 & 0.64 & 0.12 & 0.09 & 0.60 & 0.18 & 0.13 & 0.54 & 0.22 & 0.19 & 0.63 \\
-% J & 0.14 & 0.11 & 0.70 & 0.17 & 0.16 & 0.75 & 0.29 & 0.24 & 0.49 & 0.12 & 0.10 & 0.60 & 0.13 & 0.14 & 0.67 & 0.23 & 0.20 & 0.51 \\
-% K & 0.19 & 0.08 & 0.64 & 0.25 & 0.15 & 0.63 & 0.25 & 0.24 & 0.67 & 0.16 & 0.08 & 0.53 & 0.18 & 0.12 & 0.53 & 0.19 & 0.19 & 0.63 \\
-% L & 0.18 & 0.08 & 0.63 & 0.22 & 0.15 & 0.68 & 0.27 & 0.24 & 0.66 & 0.16 & 0.08 & 0.53 & 0.17 & 0.12 & 0.57 & 0.21 & 0.21 & 0.67 \\
-% M & 0.14 & 0.13 & 0.72 & 0.23 & 0.16 & 0.64 & 0.28 & 0.24 & 0.59 & 0.12 & 0.11 & 0.62 & 0.19 & 0.13 & 0.53 & 0.23 & 0.20 & 0.60 \\
-% N & 0.16 & 0.10 & 0.66 & 0.22 & 0.14 & 0.66 & 0.28 & 0.23 & 0.61 & 0.14 & 0.09 & 0.57 & 0.18 & 0.13 & 0.55 & 0.21 & 0.19 & 0.60 \\
-% O & 0.15 & 0.11 & 0.69 & 0.23 & 0.15 & 0.65 & 0.28 & 0.24 & 0.61 & 0.13 & 0.10 & 0.59 & 0.18 & 0.12 & 0.54 & 0.22 & 0.19 & 0.61 \\
-% P & 0.19 & 0.09 & 0.64 & 0.24 & 0.14 & 0.64 & 0.27 & 0.22 & 0.61 & 0.15 & 0.08 & 0.53 & 0.19 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
-% Q & 0.18 & 0.09 & 0.64 & 0.26 & 0.15 & 0.60 & 0.29 & 0.23 & 0.57 & 0.17 & 0.08 & 0.54 & 0.20 & 0.12 & 0.49 & 0.22 & 0.19 & 0.56 \\
-% R & 0.15 & 0.10 & 0.68 & 0.24 & 0.15 & 0.63 & 0.27 & 0.23 & 0.60 & 0.12 & 0.10 & 0.59 & 0.19 & 0.12 & 0.50 & 0.21 & 0.18 & 0.59 \\
-% S & 0.18 & 0.08 & 0.65 & 0.20 & 0.13 & 0.68 & 0.23 & 0.22 & 0.71 & 0.16 & 0.08 & 0.54 & 0.17 & 0.12 & 0.57 & 0.18 & 0.19 & 0.70 \\
-% T & 0.16 & 0.09 & 0.70 & 0.23 & 0.15 & 0.62 & 0.33 & 0.25 & 0.43 & 0.13 & 0.08 & 0.60 & 0.18 & 0.12 & 0.50 & 0.26 & 0.20 & 0.45 \\
-%         \hline
-%     \end{tabular}
-%     \caption{A table}
-% \end{sidewaystable}

### 2021-10-16 paper/tex/sections/comparisons.tex
add excel file link

@@
 The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_2_compare_dco.png}{\faFileImage}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_2_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/previous_BH_NS_studies.xlsx}{\faFileExcel}.}
     \label{fig:previous_studies}

### 2021-10-17 simulation/src/simulate_DCO_detections.py
update usage string

@@ -13,12 +13,29 @@ MW_SIZE = 200000
 
 
 def usage():
-    print("usage: python full_simulation.py [options]")
-    print("\toptions:")
-    print("\t\t-h, --help  : print usage instructions")
-    print("\t\t-i, --input : path to COMPAS h5 input file")
-    print("\t\t-n, --loops : number of simulations to run")
-    print("\t\t-o, --output: path to output h5 file")
+    ansi_codes = {
+        "green": '\033[92m',
+        "red": '\u001b[31m',
+        "reset": '\033[0m'
+    }
+    print()
+    print("{}usage:{} python simulation_DCO_detections.py {}[options]{}".format(ansi_codes["green"],
+                                                                                ansi_codes["reset"],
+                                                                                ansi_codes["red"],
+                                                                                ansi_codes["reset"]))
+    print()
+    print("{}options:{}".format(ansi_codes["red"], ansi_codes["reset"]))
+    print("      Option names      :                       Description                        : Default value")
+    print("------------------------:----------------------------------------------------------:--------------")
+    print("  -h, --help            : print usage instructions                                 : -")
+    print("  -i, --input           : path to COMPAS h5 input file                             : 'COMPASOutput.h5'")
+    print("  -o, --output          : path to output h5 file                                   : 'COMPASOutput_testing.h5'")
+    print("  -n, --loops           : number of simulations to run                             : 10")
+    print("  -t, --binary-type     : which binary type to simulation ['BHBH', 'BHNS', 'NSNS'] : 'BHNS'")
+    print("  -f, --opt-flag        : whether to use the optimistic CE scenario                : -")
+    print("  -s, --simple-mw       : whether to use the simple MW model                       : -")
+    print("  -e, --extended-mission: whether to assume an extended (10 yr) LISA mission       : -")
+    print()
 
 #####################################################################
 

### 2021-10-30 paper/tex/sections/__variations_before.tex

--- 2021-10-16 paper/tex/sections/variations.tex
@@
-In this section we explore the effect of varying the underlying binary physics assumptions, both on the detection rate (Section~\ref{sec:detection_rate_analysis}) and the properties of the detectable systems (Section~\ref{sec:property_variations}).
+In this section we explore the effect of varying the underlying physics assumptions, both on the detection rate (Section~\ref{sec:detection_rate_analysis}) and the properties of the detectable systems (Section~\ref{sec:property_variations}).
 
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
-For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates} and for a plot of the rates relative to the fiducial model see Fig.~\ref{fig:dco_relative_rates}.
+In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for BHBH, BHNS and NSNS in the top, middle and bottom panel respectively.
+We discuss the prominent trends in the following sections.
+For the rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates}.
+We also provide a plot showing the same information, but plotted relative to the rate of the fiducial model see Fig.~\ref{fig:dco_relative_rates}.
 
-The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the mean detections in three quarters of our models staying within 25\% of the fiducial rate.
+%The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the mean detections in three quarters of our models staying within 25\% of the fiducial rate.
 In contrast, the BHNS detection rate is very sensitive to all changes that we made in our binary physics assumptions, varying across two orders of magnitude in the middle panel of Figure~\ref{fig:detection_rates}.
@@
     \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}).
+The curve for $f_{\rm WR} = 5$ has much higher uncertainties as there are many fewer systems formed in this model (the inverse reasoning also explains the lower uncertainties for $f_{\rm WR} = 0.1$).
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}

### 2021-10-30 paper/tex/sections/discussion.tex

@@
 \subsection{Caveats}\label{sec:caveats}
-\textit{Binary fraction and other normalisation choices}: The choice of the binary fraction has a strong effect on our results.
+
+\textit{Population synthesis limitations:} As with any study involving a rapid population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
+COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
+Much of the underlying physics is uncertain, such as the common-envelope evolution and mass transfer physics.
+We attempt to understand the importance of some these assumptions by varying over many different physics assumptions.
+
+\textit{Large progenitor masses:} Many of the black holes that are formed in our sample come from progenitors with large initial masses.
+The primary stars in systems that form  BHNSs and BHBHs have very primary progenitor masses that peak around 50\Msun and 80\Msun, but they extend well beyond that.
+The evolution of such massive progenitor stars is very poorly understood and observational constraints are very scarce in this mass range and practically non existent for the later rapid evolutionary phases.
+This is reason for very substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
+Additionally, the COMPAS code relies on fitting formula tat need to be extrapolated to create tracks are extrapolations at these higher masses.
+
+\textit{Underlying helium star models:} One source of weakness is that the \citet{Hurley+2000} fitting formulae for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
+A more comprehensive set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
+
+\textit{Limited metallicity range:} The stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ \citep{Hurley+2000} and should not be extrapolated too far outside this range.
+However, in our simulated Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
+
+For metallicities below our range we assume they evolve similar to our lowest metallicity models. DCO formation at metallicities above $Z = 0.03$ is 
+less efficient at high metallicity and so higher metallicities are unlikely to contribute significantly.
+Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
+
+\textit{Normalisation choices}: The choice of the binary fraction has a strong effect on our results.
 For the normalisation of the detection rate we conservatively choose to set the binary fraction of all stars to 50\%.
@@
 However, changes to this normalisation would affect every variation equally and so the trends across variations are more robust.
-
-\textit{Population synthesis limitations:} As with any study involving a population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
-COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
-Much of the underlying physics is uncertain, such as the common-envelope evolution and mass transfer physics.
-We attempt to understand the importance of these assumptions by varying over many different physics assumptions.
-
-\textit{Underlying helium star models:} One major weakness is that the \citet{Hurley+2000} fitting formulae for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
-A more comprehensive set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
-
-\textit{Large progenitor masses:} Due to the high metallicity population within the Milky Way, many of the black holes that are formed in our sample come from progenitors with large initial masses.
-39\% of BHBHs contain a BH with a progenitor mass in excess of $100 \unit{M_\odot}$, as do $13\%$ of BHNSs.
-The fitting formulae upon with COMPAS is based need to be extrapolated for stars of this mass and so their true evolution may not follow the results of population synthesis.
-
-\textit{Limited metallicity range:} Another limitation of the stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ (due to the limits of the underlying models in \citet{Hurley+2000}) and should not be extrapolated outside this region.
-However, in the Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
-Therefore, for our study we had to reassign any metallicities outside of COMPAS' range.
-We expect that stellar winds will be reduced to such a degree that they are effectively zero for any metallicity below the minimum.
-Hence we set any metallicity below the minimum, $Z = 10^{-4}$, equal to the $Z = 10^{-4}$.
-Similarly, DCO formation is less efficient at high metallicity \citep[e.g.][]{Broekgaarden+2021} and so exploring metallicities above the COMPAS maximum is unlikely to contribute significantly to the observed rate.
-Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
-
-\textit{Other formation channels:} We also note that our findings are only the result of a single formation channel (isolated binary formation).
-We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions.
-For instance, \citet{Kremer+2018} predict that around $21$ systems could be detected in Milky Way globular clusters with LISA, formed through dynamical formation and thus different channels can still contribute significantly to the detection rate.
-
-\textit{Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters.
-\citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
-The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates.
-Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.
 
@@
 Until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.
+
+%\textit{Other formation channels:} We also note that our findings are only the result of a single formation channel (isolated binary formation).
+We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions.
+For instance, \citet{Kremer+2018} predict that around $21$ systems could be detected in Milky Way globular clusters with LISA, formed through dynamical formation and thus different channels can still contribute significantly to the detection rate.
+
+\textit{Other formation channels, the Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters.
+\citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
+The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates.
+Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.

### 2021-10-30 paper/tex/sections/results.tex
resolve outstanding overleaf comments

@@
 In total we expect $124$ detections in a 4-year LISA mission, of which $\BHBHFourYear{}$, $\BHNSFourYear{}$ and $\NSNSFourYear{}$ are BHBHs, BHNSs and NSNSs respectively, based on our fiducial simulations.
-In the remainder of this section, we discuss where the sources are expected relative to LISA's sensitivity curve (Sec.~\ref{sec:dcos_on_sc}), their properties (Sec.~\ref{sec:fiducial_distributions}), their locations in the Milky Way (Sec.~\ref{sec:mw_detectable_distribution}), their progenitors and formation channels (Sec.~\ref{sec:progenitors_and_formation}) and finally we discuss the expected SNR and how accurately we expect that the parameters can be measured (Sec.~\ref{sec:measurement_uncertainties}).
+In the remainder of this section, we discuss where the sources are expected relative to LISA's sensitivity curve (Sec.~\ref{sec:dcos_on_sc}), their properties (Sec.~\ref{sec:fiducial_distributions}), their locations in the Milky Way (Sec.~\ref{sec:mw_detectable_distribution}), their formation channels (Sec.~\ref{sec:progenitors_and_formation}) and finally we discuss the expected SNR and how accurately we expect that the parameters can be measured (Sec.~\ref{sec:measurement_uncertainties}).
 Note that all results shown in this section are based on our fiducial simulations.
@@
 In Figure~\ref{fig:fiducial_pdf_distributions}, we show the 1D distribution of several individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties obtained via bootstrapping.
+These uncertainties represent the fluctuations in our results over different random instances of the Milky Way.
 The distributions shown here are approximated by kernel density estimators, corrected for edge effects by mirroring the sample \citep{Schuster+1985}.
@@
 
-BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations, see Sec.~\ref{sec:progenitors_and_formation}).
+BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations.
 The primary in such systems experiences strong mass loss by winds before filling its Roche lobe.
@@
 
-\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
-\todo{@Selma will review this section}
+%\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
+%Our simulations also provide information about the properties of the progenitor systems.
+In Figure~\ref{fig:progenitor_properties}, we show the distribution of initial primary masses and initial mass ratios of the progenitors of the LISA detectable DCOs in the top and bottom panel respectively.
 
-In Figure~\ref{fig:progenitor_properties}, we show some properties of the progenitors of the LISA detectable DCOs.
-The top panel shows the inital primary mass and is plotted on a log-scale.
-We see that the vast majority of NSNSs are formed with progenitor masses below $15 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$.
-In contrast, BHNSs and BHBHs have extremely high primary progenitor masses, particularly given their final BH masses (see Fig.~\ref{fig:fiducial_pdf_distributions}b).
-These large progenitor masses are often necessary as the high metallicity environment of the Milky Way leads to greater mass loss due to stellar winds and so a greater initial mass is needed to still produce a BH.
+%We see that the vast majority of NSNSs are formed with progenitor masses below $20 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$.
+In contrast, the primary stars in systems that form  BHNSs and BHBHs have very primary progenitor masses that peak around 50\Msun and 80\Msun.
+We note that the evolution of such massive progenitor stars is poorly understood which is reason for substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
 
-The bottom panel of Fig.~\ref{fig:progenitor_properties} shows the initial mass ratio.
-Overall, we find that the progenitors of detectable systems tend to have more unequal mass ratios compared to the final DCOs (c.f.\ Fig.~\ref{fig:fiducial_pdf_distributions}c).
-This is because mass loss due to stellar winds tends to bring the mass ratio closer to unity as the systems evolve.
-Additionally, in contrast to Fig.~\ref{fig:fiducial_pdf_distributions}c, the BHNS distribution is unimodal.
+%Concerning, the mass ratios we see that, in our fiducial simulations, NSNS tend to form from systems with initial mass ratios close to unity.
+BHBH and BHNS systems tend to form from systems with initial mass ratios of around 0.3, similar to the trend shown in the final mass final for the DCOs (c.f.\ Fig.~\ref{fig:fiducial_pdf_distributions}c).
 
-\begin{figure}[htb]
-    \centering
-    \includegraphics[width=\columnwidth]{fig5_progenitor_distributions.pdf}
-    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and inital mass ratio (bottom).
+%\begin{figure}[htb]
+%    \centering
+%    \includegraphics[width=\columnwidth]{fig5_progenitor_distributions.pdf}
+%    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and initial mass ratio (bottom).
 Note that the y-axis is log-scaled for the initial primary mass.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
-    \label{fig:progenitor_properties}
-\end{figure}
+ %   \label{fig:progenitor_properties}
+%\end{figure}
 
+\subsection{Formation channels}\label{sec:progenitors_and_formation}
 We show the fraction of detectable DCOs that formed through different formation channels in Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model that we describe in this section.

### 2021-10-30 paper/tex/sections/appendix.tex
Updates from Overleaf

@@
 
-    \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}
-    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
+%    \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}
+%    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
 The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig19_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
-    \label{fig:dco_relative_rates}
+%   \label{fig:dco_relative_rates}
 \end{figure*}

### 2021-10-30 paper/tex/sections/conclusion.tex
Updates from Overleaf

@@
 This increases to about 50-500 for a 10-year LISA mission.
-Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered.
+Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered (see Table~\ref{tab:detection_rates}).
 
@@
     \item \textbf{Probing the black hole mass distribution and the lower mass gap:} We expect LISA to predominantly detect lower mass BHs (with 90\% of BHBH and BHNSs having BH masses lower than $11 \unit{M_\odot}$ in our fiducial simulations) in stark contrast to current ground-based detectors which are heavily biased towards high mass systems.
-This implies that LISA can potentially make important contributions to the debate about the existence of a lower mass gap (\citealt{Shao+2021} and see our Fig.~\ref{fig:lower_mass_gap_variation}).
+This implies that LISA can potentially make important contributions to the debate about the existence of a lower mass gap (see Fig.~\ref{fig:lower_mass_gap_variation}).
 
@@
 In particular, for our fiducial model, we find that this is the case for around three quarters of detectable binaries.
-Furthermore, around 16\% of detectable binaries have eccentricities that are so high that the emission at frequencies corresponding to higher order harmonics start to dominate ($e > 0.3$).
+Furthermore, around 16\% of detectable binaries have eccentricities that are so high ($e > 0.3$) that the emission at frequencies corresponding to higher order harmonics start to dominate (see Fig.~\ref{fig:fiducial_pdf_distributions}).
 
-    \item \textbf{Distinguishing from WDWD sources:} For about half of all detections we expect that we will be able to confidently determine the type of compact objects involved (and this increases to 60\% for a 10-year LISA mission), see Sec.~\ref{sec:WDWD_distinguish}.
+    \item \textbf{Distinguishing from WDWD sources:} For about half of all detections we expect that we will be able to confidently determine the type of compact objects involved and this increases to 60\% for a 10-year LISA mission (see Sec.~\ref{sec:WDWD_distinguish}).
 
-    \item \textbf{Chirp mass determinations:} For about 10\% of systems we expect to be able to determine the chirp mass better than 10\% (and this increases to 15\% for a 10-year LISA mission), see Fig.~\ref{fig:m_c_unc}.
+    \item \textbf{Chirp mass determinations:} For about 10\% of systems we expect to be able to determine the chirp mass better than 10\% and this increases to 15\% for a 10-year LISA mission (see Fig.~\ref{fig:m_c_unc}).
 
@@
     \item \textbf{Prospects for finding EM counterparts:} We expect about 13\% of detections with a sky localisation better than 1 degree.
-Increasing the LISA mission length increases the number, but the fraction stays roughly the same.
-This will be of interest for electromagnetic counterpart searches, in particular for radio pulsar searches with SKA.
+This fraction remains the same for a 10-year LISA mission, meaning that the number increases proportionally.
+    This will be of interest for electromagnetic searches for counterparts, in particular for radio pulsar searches with SKA (see Fig.~\ref{sec:pulsar_matching}).
 
-%    \item \textbf{Joint SKA-LISA detections:} We expect that \textit{if} every LISA detectable DCO contained a pulsar that is beaming towards Earth, SKA-1 would be able to detect at least 11 of these objects, whilst the increased number of detectable pulsars that could crowd the sky with SKA-2 sensitivity means that this total decreases to 6.
-This number is a pessimistic estimate and could be much higher if we consider that SKA and LISA could match their orbital frequency estimates to select the correct pulsar from a crowded field.
-
- %   \item \textbf{Importance of choice of MW model:} Many studies use Milky Way models that use fixed metallicity populations which are assigned irrespective of birth time or position, do not account for the inside-out growth of the thin disc and use constant star formation rates.
-The use of these simpler MW models may lead to an overestimation of the LISA NSNS detection rate and an underestimation of the BHNS detection rate.
-It may also introduce unphysical artifacts into DCO parameter distributions, particularly the mass distributions, which lead to inaccurate predictions.
-
-   \item \textbf{Benefits of extended LISA mission:} The number of detections scale approximately as $T_{\rm obs}^{0.5}$, where $T_{\rm obs}$ is the mission length.
+   \item \textbf{Benefits of extending the LISA mission:} The number of detections scale approximately as $T_{\rm obs}^{0.5}$, where $T_{\rm obs}$ is the mission length.
 Therefore, extending the LISA mission from 4- to 10-years increases the number of detections by about 60\%.

### 2021-10-30 paper/tex/sections/variations.tex
add formation channel description
Updates from Overleaf

@@
-In this section we explore the effect of varying the underlying binary physics assumptions, both on the detection rate (Section~\ref{sec:detection_rate_analysis}) and the properties of the detectable systems (Section~\ref{sec:property_variations}).
+In this section we explore the effect of varying the uncertain assumptions governing the evolution of binary system and the formation of compact objects.
+For this we use the model variations presented in \citet{Broekgaarden+2021}.
+
+We first discuss the robustness of our predictions for the number of detectable systems (Section~\ref{sec:detection_rate_analysis}).
+We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe about the physics of double compact object formation (Section~\ref{sec:property_variations}).
+
+%We note that impact of physics variations cannot always be easily understood in simple terms as the evolutionary path of a progenitor of a detectable source involves multiple interactions stages.
+Providing full explanations is beyond our current scope, but we hope nevertheless that this section gives the reader an impression of the impact of the physics variations on the rates.
 
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections for each model variation and discuss the prominent trends in the following sections.
-For the exact rates and uncertainties plotted in this figure see Table~\ref{tab:detection_rates} and for a plot of the rates relative to the fiducial model see Fig.~\ref{fig:dco_relative_rates}.
+In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as predicted by our simulations considering variations in the physical assumptions.
+We show predictions for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively.
+All the rates and their uncertainties plotted in this figure are also provided in Table~\ref{tab:detection_rates}.
+In the sections that follow, we briefly explain the variations considered and discuss the most prominent trends.
 
-The BHBH detection rate is markedly robust across variations of physics assumptions, as can be seen in the top panel of Figure~\ref{fig:detection_rates}, with the mean detections in three quarters of our models staying within 25\% of the fiducial rate.
-In contrast, the BHNS detection rate is very sensitive to all changes that we made in our binary physics assumptions, varying across two orders of magnitude in the middle panel of Figure~\ref{fig:detection_rates}.
-Finally, in the last panel of Figure~\ref{fig:detection_rates} we show that the NSNS detection is only moderately sensitive to certain changes in physics assumptions, varying by up to an order of magnitude, whilst showing no change for many models.
+\subsubsection{Efficiency of mass transfer}
 
-\subsubsection{Mass transfer variation trends}
+The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}.
+In our fiducial model A, we use a prescription where the
+accretion rate onto stellar companions is regulated by their thermal timescale, i.e.
+the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
 
-In models \modBetaLow{}-\modBetaHigh{}, we set the mass transfer efficiency $\beta$ to a fixed value.
-For the BHBHs and BHNSs, as we increase $\beta$ the detection rates steadily decrease.
-This may seem unintuitive since one might assume that a higher mass transfer efficiency would lead to more massive compact objects and thus a more detectable population.
-However, this increase contributes to the envelope mass and so without increasing the core mass or fallback rate, the final compact object mass is relatively unaffected.
-Moreover, one must consider that most of these DCOs are formed through a common-envelope event and so retaining more of the envelope during mass transfer means that the eventual ejection of the envelope is much more difficult, thus leading to more stellar mergers and fewer detectable systems \citep[e.g.][]{Kruckow+2018,Broekgaarden+2021}.
+In models \modBetaLow{}-\modBetaHigh{}, we adopt a fixed value for the mass transfer efficiency, $\beta$, from $\beta=0.25$ up to 0.75, in cases of stable mass transfer onto a stellar companion.
+For accretion onto NS and BH we still assume that their accretion is limited to the Eddington rate.
 
-In contrast, for the NSNSs, the detection rate increases with increasing $\beta$.
-This is for two main reasons: firstly the ejection of a common-envelope is less problematic for NSNSs as they are less massive \citep[e.g.][]{Kruckow+2018}.
-Moreover, the increased mass transfer efficiency means that systems that were previously below the mass necessary to become a NS can now accrete enough mass to form a NS.
-Although the same is true for more massive stars becoming BHs instead of NSs, due to the IMF, there is a net flux of more stars becoming NSs.
+Nearly all systems that can be detected form through channels where the very first interaction is stable mass transfer.
+Generally, higher mass transfer efficiencies lead to higher masses for the accreting stars, but also leads to wider orbits \citep{Soberman+1997, vanSon+2020}.
+Changing $\beta$ thus already affects the masses and orbital separation after the first interaction phase, which in turn changes the starting conditions and outcome of all subsequent interactions phases.
+This makes it complicated to fully understand the impact of varying $\beta$ in simple terms, but we can distinguish two main patterns for higher and lower mass systems respectively.
 
-Enforcing that case BB mass transfer is always unstable (model \modCaseBB{}) has little effect on the BHBH detection rate whilst moderately and drastically decreasing the detection rates of BHNSs and NSNSs respectively.
-This is because a large fraction of NSs (and the majority of NSNS binaries) are formed through case BB mass transfer.
-Therefore, setting this mass transfer to be always unstable results in many of these binaries to merge before they could become DCOs since we assume the pessimistic common-envelope (CE) scenario by default.
+For the most massive progenitors, increasing $\beta$ leads to secondary stars that are so massive and luminous that they experience strong wind mass loss.
+This leads to further widening of the orbit and it limits the amount by which the secondaries expand.
+Both of these effects can prevent secondaries from filling their Roche lobe.
+This means that they cannot initiate the reverse interaction needed to shrink the binary system and eventually produce a detectable compact binary system.
+We indeed see that increasing the mass transfer efficiency leads to
+a decrease of the expected number of detections for BHBHs and BHNSs, which originate from the most massive progenitors.
 
-If we instead use the optimistic CE scenario when setting case BB mass transfer to be unstable (model \modCaseBBOpt{}) we find that the rates instead uniformly increase across DCO types.
-This is both from the natural increases from using the optimistic CE scenario (see discussion of model \modOpt{} in Sec.~\ref{sec:detection_rate_CE_trends}), as well as additional increases from adding more DCOs formed through CE events after case BB mass transfer.
-This explains why we see more detections for BHNSs and NSNSs in model \modCaseBBOpt{} than in model \modOpt{}.
+For lower mass progenitors, which primarily produce NSNS systems, we find the opposite.
+Increasing $\beta$ leads to an increase of detectable systems.
+This is in part because the increased mass of the secondary stars allows stars that would have other wise ended their life as a WD, can now become massive enough to form a NS.
+The same effect also allows some NS progenitors to become massive enough to BH progenitors, but this effect is less strong.
+Furthermore, the changes in secondary mass and orbital widening, affects the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
+Indeed, the net effect is an increase of NSNS systems with increasing $\beta$.
 
@@
 
-\subsubsection{Common-envelope variation trends}\label{sec:detection_rate_CE_trends}
+\subsubsection{Common-envelope evolution}\label{sec:detection_rate_CE_trends}
 
-Models \modAlphaLowest{}-\modAlphaHighest{} alter $\alpha_{\rm CE}$, the common-envelope efficiency parameter, to $0.1, 0.5, 2.0$ and $10.0$ respectively (where the fiducial model has $\alpha_{\rm CE} = 1.0$).
-Although we see that there are large variations in the LISA detection rates when changing $\alpha_{\rm CE}$, the detectable \textit{fraction} of systems remains largely unchanged.
-Therefore, any changes in the detection rate are due to changes in the \textit{formation} rate of the DCOs.
+The common-envelope phase constitutes the most challenging phase in the evolution of interacting binary systems \citep{Ivanova+2013}.
+The debate concerns the conditions required for the onset of a common envelope phase and, if a common envelope phase occurs, what the outcome is.
+Rapid populations synthesis simulations such as ours approximate both questions in a crude way.
+We therefore consider several model variations.
 
-Altering $\alpha_{\rm CE}$ has two major effects on the formation rate of double compact objects.
-Recall that $\alpha_{\rm CE}$ represents the fraction of the orbital energy that is available for the ejection of the common-envelope.
-Therefore, increasing $\alpha_{\rm CE}$ allows common-envelope ejection to occur at larger separations (since more energy is available at any given separation).
-A second effect of increasing $\alpha_{\rm CE}$ is that common-envelopes are less likely to result in stellar mergers as more energy is available for envelope ejection.
-We can understand the trends in formation rate of the three DCO types by considering these two effects.
+\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}.
+Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit it used in an optimal way to unbind the envelope \citep{Webbink+1984}.
+There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged.
+Therefore we consider variations in this parameter.
 
-The BHBH rate peaks for $\alpha_{\rm CE} = 1$ (model \modFid{}) and reduces whether we increase \textit{or} decrease $\alpha_{\rm CE}$.
-This is because the increase in $\alpha_{\rm CE}$ shifts a significant fraction of the population to such large separations that they no longer merge within a Hubble time.
-Although the number of stellar mergers decreases as well, the overall change in the merging BHBH formation rate is negative.
-The inverse is also true for decreasing $\alpha_{\rm CE}$, where BHBHs have shorter separations but stellar mergers are more frequent.
-Thus we find that $\alpha_{\rm CE} = 1$ seems to be optimal for BHBHs by balancing these two effects most effectively.
+In models \modAlphaLowest{}-\modAlphaHighest{} we alter the common-envelope efficiency parameter $\alpha_{\rm CE}$ to $0.1, 0.5, 2.0$ and $10.0$ respectively.
+Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta.
+Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion.
+The variations can also be seen as a way to cover uncertainties in estimates for the binding energy itself.
 
-The BHNS rate follows the same pattern as BHBHs.
-This is expected since the BH is formed first for every BHNS in our sample and so the common-envelope event is due to a RLOF of BH progenitor, just as with BHBHs.
-However, given the similarity in the BHNS rates between $\alpha_{\rm CE} = 1$ and $\alpha_{\rm CE} = 2$ (models \modFid{} and \modAlphaHigh{}), the `optimal' $\alpha_{\rm CE}$ for BHNSs seems to be somewhere between 1 and 2 rather than very close to 1 as with BHBHs.
+Increasing $\alpha_{\rm CE}$ makes common-envelope ejection more efficient or, in other words, less orbital shrinkage is needed to successfully eject the envelope.
+This has two consequences.
+(1) Firstly, a larger fraction of systems avoids merging during the CE phase.
+This increases the overall number of double compact object binaries.
+(2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources.
+So, while the first consequence favours the formation of double compact object systems, the second consequence disfavours the subset of those close enough to be detected.
 
-In contrast, $\alpha_{\rm CE} = 1$ is far from optimal for NSNSs.
-Increasing $\alpha_{\rm CE}$ (models \modAlphaHigh{} and \modAlphaHighest{}) results in significantly higher rates.
-This is because LISA detectable NSNSs tend to have been formed very recently before detection (see Fig.~\ref{fig:fiducial_pdf_distributions}e).
-Therefore, though higher $\alpha_{\rm CE}$ results in larger \textit{initial} separations, this does not adversely affect the NSNS rate as the systems are simply detected later after their formation compared to the fiducial model.
-So for models \modAlphaHigh{} and \modAlphaHighest{}, fewer systems result in stellar mergers and the overall population remains within the LISA band, producing much higher detection rates.
-%Finally, for model \modAlphaLowest{}, the reduction in common-envelope efficiency is strong enough that a sufficient number of systems are formed at shorter separations to offset those lost to stellar mergers.
+These two opposing effect result in fine tuning situation.
+Only a very small subset of progenitor systems that have the right orbital parameters prior to the CE phase to successfully produce detectable systems.
+Changing  $\alpha_{\rm CE}$ moves and changes this window in the parameter space that successfully leads to the formation of detectable systems.
+How the number of the detectable systems changes depends on whether the relevant parameter space grows or shrinks and on how well the relevant part of the parameters space is populated.
+Fully unravelling these effects and how they interplay with the assumed star formation history is beyond our scope (and possibly not even of large relevance given the severe simplifications).
+We will limit the further discussions to simply stating the trends we observe.
 
-We explore the optimistic CE scenario in model \modOpt{}, meaning that we allow Hertzsprung gap donors to survive CE events.
-A large fraction of the progenitors of the BHs in our sample expand significantly during the Hertzsprung gap phase and initiate CE events.
-This means that, when we assume the optimistic CE scenario, the formation rate of BHs is greatly increased.
-Therefore, similar to models \modAlphaLowest{}-\modAlphaHighest{}, we find that though the detectable \textit{fraction} does not change significantly, the increased formation rate of BHs in the Milky Way leads to this model predicting significantly more BHBH detections.
+We find that the BHBH rate peaks for $\alpha_{\rm CE} = 1$ (model \modFid{}) and reduces whether we increase \textit{or} decrease $\alpha_{\rm CE}$.
+The BHNS rate follows the same pattern as BHBHs although the value of $\alpha_{\rm CE}$ which maximises BHNSs seems to be between 1 and 2.
+In contrast, for NSNSs we find that increasing $\alpha_{\rm CE}$ (models \modAlphaHigh{} and \modAlphaHighest{}) results in significantly higher rates.
 
-The progenitors of BHNSs tend to be less massive than those of BHBHs.
-Less massive stars expand less during the Hertzsprung gap and thus initiate CE events less frequently in this phase.
-For these reasons, as can be seen most clearly in Fig.~\ref{fig:dco_relative_rates}, the relative increase in model \modOpt{} compared to the fiducial model is lower than BHBHs for BHNSs.
-For the same reason, the NSNS detection rate shows little significant change.
+\paragraph{The ``optimistic'' CE treatment} We further explore a model variation introduced by \citet{Belczynski+2007} often referred to as the ``optimistic'' CE scenario.
+This model also considers donor stars that are on the Hertzsprung as the progenitors for CE events.
 
-\subsubsection{Supernova variation trends}
+In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect.
+This is because BHBHs originate from the most massive progenitors, which in expand very significantly during the Hertzsprung gap phase in our simulations.
+The progenitors are likely initiate interaction during this phase.
+Our predictions for the number of detectable systems increases by a factor 2.
+The less massive progenitors of BHNSs are less strongly affected, and for NSNS we do not see a significant increase.
 
-Changes to the remnant mass prescription (models \modRapid{}-\modNSHigh{}) have no effect on the NSNS detection rate for two reasons.
-A large fraction of the NSs in our sample are formed through ECSN, in which case their masses are set to $1.26 \unit{M_\odot}$ regardless of the remnant mass prescription.
-Secondly, the majority of the remaining NSs have such low progenitor masses that they are set to the lowest remnant mass in the prescription ($1.28 \unit{M_\odot}$ for the delayed prescription and $1.1 \unit{M_\odot}$ for the rapid prescription).
-This means that changing the upper portion of the mass range of NSs in the remnant mass prescription has little effect.
+\paragraph{Case BB mass transfer} For completeness and consistency with \citet{Broekgaarden+2021}, we have also included model variations that consider uncertainties in case BB mass transfer.
+his is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}.
+This is of particular interest for the formation of NS stars, as their lower mass progenitors are swelling the most during this phase \citet[e.g.][and references therein]{Laplace+2020}.
+Nearly all NSNS systems from through case BB mass transfer
 
-This is not the case for BHBHs and BHNSs.
-The different remnant mass prescriptions and maximum neutron star masses change whether a progenitor becomes a black hole or a neutron star.
-Hence, using the rapid prescription (model \modRapid{}) or increasing the maximum neutron star mass (model \modNSHigh{}), means that more progenitors form high mass NSs rather than low mass BHs and so more BHNSs are formed.
-This explains the higher detection rates for BHNSs and lower detection rates for BHBHs in these models.
-The inverse is true for model \modNSLow{}, where instead more BHBHs are formed and detected.
+In model \modCaseBB{} we effectively exclude any systems that evolve through case BB mass transfer.
+As expected, this kills nearly all NSNS systems.
+We also find a heavy reduction of the BHNS systems y a factor 6.
+The BHBH systems are not affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.
 
-Additionally, we find that not implementing pair-instability supernovae (PISN) pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the results for any DCO type.
-This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.
+Finally, in model {[\bf TOM..
+please add label]} [=F] we consider a situation where case BB mass transfer always leads to unstable mass transfer and initiates a CE phase combined with the optimistic treatment for CE.
+This model leads to the highest predictions for the detection's among all variations that we have considered.
 
-Decreasing the core-collapse supernova velocity dispersion (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-This increase is least prominent for BHBHs since their increased mass mean that disruptions are less frequent than, for instance, in NSNSs.
-It is also notable that these two models best match the detection rates from LIGO (Broekgaarden et al.\ in prep).
+\subsubsection{Supernovae and compact remnants}
+
+The formation of compact remnants and and their associated natal kicks also constitute important uncertainties.
+
+In model \modRapid{} we consider the so-called ``rapid'' remnant mass function by \citet{Fryer+2015} as an alternative to the ``delayed'' description used in our detailed simulations.
+This affects the mass distribution (see Section~\ref{XX}), but the effects on the number of detectable systems is modest for BHBH and BHNS, and negligible for NSNS.
+
+The same is true for changing the impact of changing the assumed maximum neutron star mass, $m_{\rm ns}$ (\modNSLow{} and \modNSHigh{}).
+Lowering $m_{\rm ns}$  increases the number of detections involving BHs and vice versa, but has no significant effect on the number of NSNS detections.
+
+In Model \modNoPISN{}, we ignore pair instability supernovae, which has no significant effect on the predictions for the number of detections with LISA.
+This is not a surprise as the typical metallicity of the progenitors in our Milky Way is rather high.
+The detectable systems are dominated by systems with final core masses that are well below the mass regime for pair instability supernovae.
+
+Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
+The NSNS systems are most strongly affected.
+The impact on BHNS systems is mild and even insignificant for BHBH systems.
+This is because, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back, which is large in the case of BHs.
+
+In model \modNoBH{} we assume BHs form without any kick, while using our fiducial assumption for the natal kicks of neutron stars.
+This increases the predictions for BHNS by a factor 3.
+The impact on BHBH systems is much smaller, This is because they mostly form from more massive cores which are already assumed to form with low kicks in our simulations.
+As expected, the NSNS population is not affected.
+
+%We note that the these two models best match the detection rates from LIGO (Broekgaarden et al.\ subm).
 Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.
 
-In model \modNoBH{} we do not give black holes natal kicks.
-For BHBHs, the rate is approximately equal to that of model \modSigLower{} since kicks of $30 \unit{km}{s^{-1}}$ are equivalent to no kicks for massive BHs in our sample.
-For BHNSs, this model's rate is still well above the fiducial but decreases slightly relative to model \modSigLower{} as the number of surviving binaries is limited by the neutron star kick more than the black hole kick.
-NSNSs are unaffected as one would assume due to the absence of BHs.
+\subsubsection{Stellar winds}
+Mass loss in the form of stellar winds or eruptions are also a main incertainty. It affects by how much stars can grow in size and it affects the final core masses.
 
-\subsubsection{Stellar wind variation trends}
-We decrease the efficiency of Wolf-Rayet winds to 10\% in model \modWRLow{}.
-We find that decreasing the efficiency of these winds actually has very little effect on our predicted detection rates.
-This due to a combination of cancelling effects.
+\citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by hot and luminous Wolf-Rayet stars.
+We find that a reduction of the wind mass loss  has very little effect on our predictions.
+It turns out that this is the consequence of several effects that cancel each other.
 
@@
 Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries.
-However, though this \textit{is} the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at \textit{lower} frequencies than in our fiducial model.
+However, though this is the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at lower frequencies than in our fiducial model.
 This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times.
 This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.
-Finally, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged).
+
+In addition, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged).
 The increase in eccentricity for NSNSs comes from the same reason as the lower frequency, more recent birth times mean that binaries have less time to circularise.
 The same is not true for BHBHs as the more massive systems are less affected by supernova kicks and so fewer high eccentricity systems are formed.
-
 Overall, despite the large differences in the system properties, these three effects in combination leave the detection rates relatively unchanged.
@@
 In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5.
+We note that there is currently no observational support for such a strong increase in the stellar winds of Wolf-Rayet stars, but it is nevertheless still interesting to consider.
 In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged.
@@
 
-\subsubsection{Effect of mass loss efficiency on mass distribution}
+\subsubsection{Effect of Wolf-Rayet winds on mass distribution}
 

### 2021-11-01 paper/tex/sections/discussion.tex
minor caveat rearrangement

@@
 
-%\textit{Other formation channels:} We also note that our findings are only the result of a single formation channel (isolated binary formation).
-We do not consider other channels such as dynamical formation or chemically homogeneous evolution, which could increase the detection rate and alter the parameter distributions.
-For instance, \citet{Kremer+2018} predict that around $21$ systems could be detected in Milky Way globular clusters with LISA, formed through dynamical formation and thus different channels can still contribute significantly to the detection rate.
-
 \textit{Other formation channels, the Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters.
 \citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
-The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we again highlight the work of \citet{Kremer+2018} that investigated these rates.
+The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we highlight the work of \citet{Kremer+2018} that investigated these rates.
 Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.

### 2021-11-01 simulation/src/variations.py
change variation labels

@@ -38,15 +38,15 @@ variations = np.array(
         {
             "file": "unstableCaseBB",
             "short": "E",
-            "med": "unstable\ncase BB",
-            "long": "Case BB mass transfer is always unstable",
+            "med": "No Case BB",
+            "long": "Case BB mass transfer systems are removed",
             "colour": plt.get_cmap("tab20")(3)
         },
         {
             "file": "unstableCaseBB_opt",
             "short": "F",
-            "med": "E+K",
-            "long": "Model E + Model K",
+            "med": "Case BB\nUnstable + K",
+            "long": "Case BB Unstable + Optimistic CE",
             "colour": plt.get_cmap("tab20")(2)
         },
         {

### 2021-11-02 paper/tex/sections/variations.tex
proof read variations

@@
 The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}.
-In our fiducial model A, we use a prescription where the
-accretion rate onto stellar companions is regulated by their thermal timescale, i.e.
-the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
+In our fiducial model A, we use a prescription in which the accretion rate onto stellar companions is regulated by their thermal timescale, i.e.\ the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
 
-In models \modBetaLow{}-\modBetaHigh{}, we adopt a fixed value for the mass transfer efficiency, $\beta$, from $\beta=0.25$ up to 0.75, in cases of stable mass transfer onto a stellar companion.
+In models \modBetaLow{}-\modBetaHigh{}, we instead adopt a fixed value for the mass transfer efficiency, $\beta$, from $\beta=0.25$ up to 0.75, in cases of stable mass transfer onto a stellar companion.
 For accretion onto NS and BH we still assume that their accretion is limited to the Eddington rate.
@@
 Both of these effects can prevent secondaries from filling their Roche lobe.
-This means that they cannot initiate the reverse interaction needed to shrink the binary system and eventually produce a detectable compact binary system.
-We indeed see that increasing the mass transfer efficiency leads to
-a decrease of the expected number of detections for BHBHs and BHNSs, which originate from the most massive progenitors.
+This means that they cannot initiate the reverse interaction needed to shrink the binary system and eventually produce a detectable double compact object.
+We indeed see that increasing $\beta$ leads to a decrease of the expected number of detections for BHBHs and BHNSs, which originate from the most massive progenitors.
 
-For lower mass progenitors, which primarily produce NSNS systems, we find the opposite.
-Increasing $\beta$ leads to an increase of detectable systems.
-This is in part because the increased mass of the secondary stars allows stars that would have other wise ended their life as a WD, can now become massive enough to form a NS.
+For lower mass progenitors, which primarily produce NSNS systems, we find the opposite: increasing $\beta$ leads to an \textit{increase} in the number of detectable NSNS systems.
+This is in part because the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS.
 The same effect also allows some NS progenitors to become massive enough to BH progenitors, but this effect is less strong.
 Furthermore, the changes in secondary mass and orbital widening, affects the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
-Indeed, the net effect is an increase of NSNS systems with increasing $\beta$.
 
@@
 The debate concerns the conditions required for the onset of a common envelope phase and, if a common envelope phase occurs, what the outcome is.
-Rapid populations synthesis simulations such as ours approximate both questions in a crude way.
+Rapid population synthesis simulations such as ours approximate both questions in a crude way.
 We therefore consider several model variations.
@@
 \paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}.
-Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit it used in an optimal way to unbind the envelope \citep{Webbink+1984}.
+Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope \citep{Webbink+1984}.
 There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged.
@@
 (1) Firstly, a larger fraction of systems avoids merging during the CE phase.
-This increases the overall number of double compact object binaries.
+This increases the overall number of DCOs.
 (2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources.
-So, while the first consequence favours the formation of double compact object systems, the second consequence disfavours the subset of those close enough to be detected.
+So, while the first consequence favours the formation of DCOs, the second consequence disfavours the subset that are tight enough to be detected.
 
-These two opposing effect result in fine tuning situation.
+These two opposing effect result in a fine tuning situation.
 Only a very small subset of progenitor systems that have the right orbital parameters prior to the CE phase to successfully produce detectable systems.
@@
 \paragraph{The ``optimistic'' CE treatment} We further explore a model variation introduced by \citet{Belczynski+2007} often referred to as the ``optimistic'' CE scenario.
-This model also considers donor stars that are on the Hertzsprung as the progenitors for CE events.
+This variation (model \modOpt{}) relaxes our restriction that donor stars that are on the Hertzsprung cannot survive common-envelope events.
 
@@
 \paragraph{Case BB mass transfer} For completeness and consistency with \citet{Broekgaarden+2021}, we have also included model variations that consider uncertainties in case BB mass transfer.
-his is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}.
-This is of particular interest for the formation of NS stars, as their lower mass progenitors are swelling the most during this phase \citet[e.g.][and references therein]{Laplace+2020}.
+This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}.
+This is of particular interest for the formation of NS stars, as their lower mass progenitors are swelling the most during this phase \citep[e.g.][and references therein]{Laplace+2020}.
 Nearly all NSNS systems from through case BB mass transfer
@@
 As expected, this kills nearly all NSNS systems.
-We also find a heavy reduction of the BHNS systems y a factor 6.
+We also find a heavy reduction of the BHNS systems by a factor 6.
 The BHBH systems are not affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.
 
-Finally, in model {[\bf TOM..
-please add label]} [=F] we consider a situation where case BB mass transfer always leads to unstable mass transfer and initiates a CE phase combined with the optimistic treatment for CE.
-This model leads to the highest predictions for the detection's among all variations that we have considered.
+Finally, in model \modCaseBBOpt{}, we consider a situation where case BB mass transfer always leads to unstable mass transfer and initiates a CE phase in combination with the optimistic treatment for CE.
+This model leads to the highest predictions for the detections among all variations that we have considered.
 
@@
 
-The formation of compact remnants and and their associated natal kicks also constitute important uncertainties.
+The formation of compact remnants and their associated natal kicks also constitute important uncertainties.
 
-In model \modRapid{} we consider the so-called ``rapid'' remnant mass function by \citet{Fryer+2015} as an alternative to the ``delayed'' description used in our detailed simulations.
-This affects the mass distribution (see Section~\ref{XX}), but the effects on the number of detectable systems is modest for BHBH and BHNS, and negligible for NSNS.
+In model \modRapid{} we consider the so-called ``rapid'' remnant mass function by \citet{Fryer+2015} as an alternative to the ``delayed'' description used in our fiducial simulations.
+This affects the mass distribution (see Sec.~\ref{sec:lower_mass_gap}), but the effects on the number of detectable systems is modest for BHBH and BHNS, and negligible for NSNS.
 
-The same is true for changing the impact of changing the assumed maximum neutron star mass, $m_{\rm ns}$ (\modNSLow{} and \modNSHigh{}).
-Lowering $m_{\rm ns}$  increases the number of detections involving BHs and vice versa, but has no significant effect on the number of NSNS detections.
+The same is true for the impact of changing the assumed maximum neutron star mass, $m_{\rm NS, max}$ (\modNSLow{} and \modNSHigh{}).
+Lowering $m_{\rm NS, max}$ increases the number of detections involving BHs (since more stars form BHs instead of NSs) and vice versa, but has no significant effect on the number of NSNS detections since the vast majority are formed from low mass NSs.
 
-In Model \modNoPISN{}, we ignore pair instability supernovae, which has no significant effect on the predictions for the number of detections with LISA.
-This is not a surprise as the typical metallicity of the progenitors in our Milky Way is rather high.
-The detectable systems are dominated by systems with final core masses that are well below the mass regime for pair instability supernovae.
+We find that not implementing pair-instability supernovae (PISN) ot pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the number of detections with LISA.
+This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.
 
 Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
-The NSNS systems are most strongly affected.
-The impact on BHNS systems is mild and even insignificant for BHBH systems.
-This is because, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back, which is large in the case of BHs.
+The BHNS and NSNS systems are strongly affected whilst the impact on BHBH systems is insignificant.
+The reason that BHBHs are relatively unaffected is that, in our models, the natal kicks for BHs are scaled down with the amount of mass that falls back.
+In the case of BHBHs, the black holes have very massive cores and thus low kicks.
 
 In model \modNoBH{} we assume BHs form without any kick, while using our fiducial assumption for the natal kicks of neutron stars.
-This increases the predictions for BHNS by a factor 3.
-The impact on BHBH systems is much smaller, This is because they mostly form from more massive cores which are already assumed to form with low kicks in our simulations.
+This increases the predictions for BHNS by a factor 3 but the impact on BHBH systems is much smaller for the same reason as for models \modSigLow{}-\modSigLower{}.
 As expected, the NSNS population is not affected.
 
-%We note that the these two models best match the detection rates from LIGO (Broekgaarden et al.\ subm).
-Therefore we find the best matching models for the LIGO detection rates also produce the highest LISA detection rates.
-
 \subsubsection{Stellar winds}
-Mass loss in the form of stellar winds or eruptions are also a main incertainty. It affects by how much stars can grow in size and it affects the final core masses.
-
+Mass loss in the form of stellar winds or eruptions is also a main uncertainty.
+It affects by how much stars can grow in size and it affects the final core masses.
 \citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by hot and luminous Wolf-Rayet stars.
 We find that a reduction of the wind mass loss has very little effect on our predictions.
-It turns out that this is the consequence of several effects that cancel each other.
+This is the consequence of several effects that cancel each other.
 
@@
 In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5.
-We note that there is currently no observational support for such a strong increase in the stellar winds of Wolf-Rayet stars, but it is nevertheless still interesting to consider.
+We note that though there is currently no observational support for such a strong increase in the stellar winds of Wolf-Rayet stars, it is nevertheless still interesting to consider.
 In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged.

### 2021-11-10 paper/tex/sections/introduction.tex
Updates from Overleaf

--- 2021-08-27 paper/tex/sections/introduction.tex
@@
-Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
+Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
 
 The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017, Colpi+2019}) will provide observations in an entirely new regime of gravitational waves.
-LISA will observe at lower frequencies ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) than ground-based detectors and so will enable the study of sources that are imperceptible by ground-based detectors, such as the mergers of supermassive black holes and extreme mass ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
-Moreover, this frequency regime is also of interest for the detection of \textit{local} stellar-mass double compact objects (DCO) millions of years before their merger.
-This presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband gravitational wave detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+LISA will observe at lower frequencies ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) than ground-based detectors and so will enable the study of sources that are imperceptible by ground-based detectors, such as the mergers of supermassive black holes and extreme mass-ratio inspirals \citep[e.g.][]{Begelman+1980, Klein+2016}.
+Moreover, this frequency regime is also of interest for the detection of \textit{local} stellar-mass double compact objects (DCOs) millions of years before their merger.
+This presents an opportunity for both multi-messenger detections to search for electromagnetic counterparts and multiband gravitational-wave detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
 In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
@@
 Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars.
-In this paper we focus on making LISA predictions for double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).
+In this paper we focus on making LISA predictions for double black hole binaries (BHBHs), black hole neutron star binaries (BHNSs) and double neutron star binaries (NSNSs).
 
@@
 Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.
-\citealp{Hulse+1975}, see also refs.\ in \citealp{Tauris+2017,Vigna-Gomez+2018}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
-A LISA detectable NSNS with a pulsar component close to merger would be ideal for connecting these population, as the binary could be observed from inspiral to merger.
-NSNS (and possible BHNS) binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Berger+2014}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
+\citealp{Hulse+1975, Antoniadis+2016}, see also refs.\ in \citealp{Tauris+2017}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational-wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
+A LISA detectable NSNS with a pulsar component close to merger would be ideal for connecting these populations, as the binary could be observed from inspiral to merger.
+NSNS (and possible BHNS) binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational-wave signals, such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Berger+2014}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
 BHBHs in the Milky Way present a greater observational challenge.
-To date, no BH has been observed in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH.
+To date, no BH has been observed in a BHBH binary in the Milky Way, and so LISA could provide the first detection of a Galactic BHBH.
 The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}.
-This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
+These detections have observed BHs with masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to contain at least one BH with a mass greater than $10 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
 These observations of X-ray binaries suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which there are no strong candidates for either black holes or neutron stars \citep{Ozel+2010,Farr+2011} but the gap's existence remains an open question \citep[e.g.][]{Kreidberg+2012, Mandel+2020}.
@@
 With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.
-However, with only two detections (not including the low-confidence candidate GW190426 \citep{Abbott+2020_GWTC2} or GW190425 and GW190814 which have not been ruled out as BHNSs \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
-Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
+However, with only two detections (not including the low-confidence candidate GW190426 \citealt{Abbott+2020_GWTC2} or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1} ) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
+Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
 Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts.
-A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}.
+A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
 These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
@@
 We build upon previous efforts but with several important improvements.
-We explore the effect of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effect on the detection rate and distributions of source parameters.
+We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters.
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
@@
 Overall we simulate over 2 billion massive binaries to produce the DCO populations used in this work.
-We find that this large number of simulations is important to reduce the sampling noise.
+We find that this large number of simulations is important to reduce the sampling noise even when using adaptive importance sampling.
 
@@
 In a companion paper, Wagg et al.
-(in prep), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+2021b (in preparation), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 

### 2021-11-10 paper/tex/paper.tex
updates to conclusion with Selma
update detection rate table
change most of the conclusions with selma :)

@@
 \usepackage{fontawesome5}
-\usepackage{xcolor} % to add more color options
+\usepackage{xcolor}
 \usepackage{wrapfig}
-\usepackage{tabularx}
 \usepackage[figuresright]{rotating}
@@
 \makeatother
+
+\newcommand{\Rsun}{\ensuremath{\,\rm{R_\odot}}\xspace}
+\newcommand{\Msun}{\ensuremath{\,\rm{M}_{\odot}}\xspace}
 
@@
 \newcommand{\confinv}[3]{$#1${\raisebox{0.5ex}{\tiny$_{-#2}^{+#3}$}}}
+\newcommand{\boldconfinv}[3]{$\mathbf{#1}${\raisebox{0.5ex}{\tiny$\mathbf{_{-#2}^{+#3}}$}}}
 
@@
 \newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}
+\newcommand{\UW}{Department of Astronomy, University of Washington, Seattle, WA, 98195}
 
 \author[0000-0001-6147-5761]{T. Wagg}
+\affiliation{\UW}
 \affiliation{\cfa}
@@
 
-\keywords{gravitational waves, LISA, black hole, neutron star, binary}
+\keywords{gravitational waves, LISA, black hole, neutron star, binary stars}
 
@@
 TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
+Portions of this study were inspired by the LISA Sprint at the Center for Computational Astrophysics of the Flatiron Institute, supported by the Simons Foundation.
 This project was funded in part by the National Science Foundation under Grant No.
@@
 
+\restartappendixnumbering
+
 \allowdisplaybreaks

### 2021-11-10 paper/tex/sections/abstract.tex

@@
 We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged.
-We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
+We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
 We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and SKA.

### 2021-11-10 paper/tex/sections/methods.tex

@@
     \caption{A schematic illustrating how we model the Milky Way.
-The left panel illustrates the different model aspects: star formation history of 3 galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
+The left panel illustrates the different model aspects: star formation history of three galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
 The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
@@
 
-We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in prep).
+We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in preparation).
 This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}.
 COMPAS follows the approach of the population synthesis code BSE \citep{Hurley+2000,Hurley+2002} and uses fitting formula and rapid algorithms to efficiently predict the final fate of binary systems.
-The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the upcoming methods paper \citep{COMPAS:2021methodsPaper}.
+The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the methods paper \citep{COMPAS:2021methodsPaper}.
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
@@
 However, this doesn't allow one to assign a star to either the thin or thick disk purely based on its height above the Galactic plane.
-Therefore, we use the chemical definition of the two disks with the \achem~nomenclature because there is a clear bimodal distribution in the chemical plane, allowing stars to be assigned to each of the disc components based on their chemical abundances.
+Therefore, we instead use the chemical definition of the two disks (applying the \achem~nomenclature) as there is a clear bimodal distribution in the chemical plane, allowing stars to be assigned to each of the disc components based on their chemical abundances.
 For each of the three components, we use a separate star formation history and spatial distribution, which we combine into a single model, weighting each component by its stellar mass.
@@
 The two discs form stars in mutually exclusive time periods, such that the high-\achem~disc forms stars in the early history of the galaxy ($8$--$12 \unit{Gyr}$ ago) and the low-\achem~disc forms stars more recently ($0$--$8 \unit{Gyr}$ ago).
-We normalize both distributions so that an equal amount of mas sis formed in each of the two components over their respective star forming periods.
+We normalise both distributions so that an equal amount of mass is formed in each of the two components over their respective star forming periods.
 
@@
 For a full derivation of the equations given below please see the LEGWORK release paper, Wagg et al.
-2021b (in prep), or the \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{documentation}.
+2021b (in preparation), or the documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
 
@@
 
-We use LEGWORK to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational wave luminosity remains below 1\%.
+We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational wave luminosity remains below 1\%.
 
@@
 
-We then determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7 and dividing by the total weights in the simulation.
+We then determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7, and dividing by the total weights in the simulation.
 We multiply this fraction by the total number in the Milky Way to find a detection rate (which we write as a total number of detections per LISA mission)

### 2021-11-10 paper/tex/sections/results.tex

@@
 To guide the interpretation, we show reference lines marking where a circular binary would reside for a given distance (diagonal line) and remaining inspiral time (vertical lines), assuming an average chirp mass $\avg{\mathcal{M}_c}$, orientation and sky location.
-The curved reference line shows the signal expected for an eccentric binary at 30 kpc.
 The coloured lines in the bottom panels show a contour that encloses 90\% of the population that is circular.
@@
 
-For reference, we show dotted lines to indicate where a hypothetical binary system would reside assuming a given distance (diagonal lines) and a fixed remaining inspiral time (vertical lines).
+For reference, we show dotted lines to indicate where a hypothetical binary system would reside assuming a given distance from earth (diagonal lines) and a fixed remaining inspiral time (vertical lines).
 For each line we assume the binary is circular and has a chirp mass equal to the average of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
@@
 Their orbits shrink as they lose angular momentum in the form of gravitational waves leading to an increase of their orbital frequency until they become detectable.
-Even though the signal emitted by a more compact binary is stronger, such systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates \citep{Peters+1964}.
+These systems are increasingly rare because they evolve faster and faster towards higher frequency as the inspiral accelerates, even though the signal emitted by a more compact binary is stronger \citep{Peters+1964}.
 The vertical grid lines show these rapidly decreasing inspiral times at increasing frequencies.
@@
 We note that this effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically \citep[e.g.][]{Sesana+2020}.
-In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries (star symbols.
+In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries.
 
@@
 The distributions appear nearly symmetric, but closer inspections shows that the left hand side is more populated, which can be seen most clearly in the curve for the BHBHs.
-This is because of the contribution of highly eccentric binaries, which are most abundant in the BHBH population.
+This is due to the contribution of highly eccentric binaries, which are most abundant in the BHBH population.
 These systems are still detectable by LISA, despite their low orbital frequency, as the high eccentricity means that the majority of the GW signal is emitted at higher harmonics, where LISA is more sensitive.
@@
 
-A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations.
+A further reason that we predict that LISA will not detect high mass systems is that the population of BHs that are detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations.
 Stellar winds are stronger at high metallicity leading to increased mass loss.
@@
 In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$.
-After closer inspection of the binary simulations, we find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this.
+We find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this.
 
@@
 Such systems would have originated from progenitors that also started with comparable masses.
-The rather massive secondaries in these systems (especially after they accreted from the primary) experience very strong stellar wind mass loss.
-This limits the amount by which they can expand.
+The rather massive secondaries in these systems (especially after they accreted from the primary) experience very strong stellar wind mass loss due to LBV-like eruptions.
+This limits the amount by which they can expand \citep[e.g.][]{vanSon+2021}.
 At the same time, wind mass loss (and also stable and more conservative mas transfer in these systems) lead to widening of the orbit.
@@
 Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arises from the fraction of the population that underwent only stable mass transfer phases.
-The stability of mass transfer depends on the mass ratio, leading to a bias for more equal mass ratio systems, resulting in a peak at higher $q$.
+The stability of mass transfer depends on the mass ratio, preferentially forming systems with more equal masses, i.e.\ at higher $q$.
 
@@
 We find that most systems (73\%) will have eccentricities larger than $0.01$ during the LISA mission, which should in principle be detectable according to \citet{Nishizawa+2016}.
-This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources (see Sec.~\ref{sec:WDWD_distinguish}).
+This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources, which are expected to have little to no eccentricity (see Sec.~\ref{sec:WDWD_distinguish}).
 We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}.
@@
 
-% \newcolumntype{Y}{>{\centering\arraybackslash}X}
-% \begin{table}[tb]
-%     \centering
-%     \begin{tabularx}{\columnwidth}{l|Y Y Y}
-%         \hline
-%         \multirow{2}{*}{Threshold} & \multicolumn{3}{c}{Individually detectable harmonics} \\ \cline{2-4}
-%         & 0 & 1 & 2+ \\
-%         \hline
-%         $\mathrm{SNR} > 7$ & 18\%  & 67\% & 15\% \\
-%         $\mathrm{SNR} > 3$ &  8\%  & 54\% & 38\% \\
-%         $\mathrm{SNR} > 1$ &  4\%  & 30\% & 66\% \\
-%     \end{tabularx}
-%     \caption{Percentage of systems with individual harmonics above different SNR thresholds.}
-%     \label{tab:test}
-% \end{table}
-
 \begin{table}[tb]
@@
 
-%\subsection{Progenitors and formation channels}\label{sec:progenitors_and_formation}
-%Our simulations also provide information about the properties of the progenitor systems.
-In Figure~\ref{fig:progenitor_properties}, we show the distribution of initial primary masses and initial mass ratios of the progenitors of the LISA detectable DCOs in the top and bottom panel respectively.
-
-%We see that the vast majority of NSNSs are formed with progenitor masses below $20 \unit{M_{\rm \odot}}$ and none are formed with masses greater than $30 \unit{M_{\rm \odot}}$.
-In contrast, the primary stars in systems that form  BHNSs and BHBHs have very primary progenitor masses that peak around 50\Msun and 80\Msun.
-We note that the evolution of such massive progenitor stars is poorly understood which is reason for substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
-
-%Concerning, the mass ratios we see that, in our fiducial simulations, NSNS tend to form from systems with initial mass ratios close to unity.
-BHBH and BHNS systems tend to form from systems with initial mass ratios of around 0.3, similar to the trend shown in the final mass final for the DCOs (c.f.\ Fig.~\ref{fig:fiducial_pdf_distributions}c).
-
-%\begin{figure}[htb]
-%    \centering
-%    \includegraphics[width=\columnwidth]{fig5_progenitor_distributions.pdf}
-%    \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the initial primary mass (top) and initial mass ratio (bottom).
-Note that the y-axis is log-scaled for the initial primary mass.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_progenitor_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
- %   \label{fig:progenitor_properties}
-%\end{figure}
-
 \subsection{Formation channels}\label{sec:progenitors_and_formation}
-We show the fraction of detectable DCOs that formed through different formation channels in Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model that we describe in this section.
-Approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}.
+In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}.
 Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the `classic' channel and the rest are mainly formed through only stable mass transfer.
@@
 These systems tend to be formed through `lucky' supernova kicks that happen to shrink the binary significantly by chance.
+
+The fraction of detectable DCOs that formed through different formation channels in other model variations are shown Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model described above.
 

### 2021-11-12 paper/tex/sections/comparisons.tex
all Neige email comments done

@@
 They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for our differences.
+However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for the differences.
 It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
@@
 Yet it is most likely that the remaining difference between our results is due to way in which we simulate the Milky Way.
-\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we use to estimate the impact of the choice of MW model is in Appendix~\ref{app:mw_changes}.
+\citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we use to estimate the impact of the choice of MW model in Appendix~\ref{app:mw_changes}.
 We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results.
@@
 They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
-\citet{Breivik+2020} make many different physical assumptions from us, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{app:mw_changes}).
+\citet{Breivik+2020} make many physical assumptions that differ from our fiducial model, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{app:mw_changes}).
 Thus for better comparison we ran our simulation using model \modCaseBBOpt{} and the Milky Way model from \citet{Breivik+2020}.
@@
 
-\noindent{}Overall, since the work of \citet{Nelemans+2001}, in additions to the LISA mission specifications, the methods that we use to simulate binaries and the Milky Way have all changed significantly.
+\noindent{}Overall, since the work of \citet{Nelemans+2001}, in addition to the LISA mission specifications, the methods that we use to simulate binaries and the Milky Way have all changed significantly.
 We now predict that LISA detections of these massive DCOs are dominated by BHBHs, rather than NSNSs, whilst the absolute detection rates for BHBHs and BHNSs are much higher.

### 2021-11-12 paper/tex/sections/discussion.tex
all Neige email comments done

@@
 \subsubsection{Distinguishing from WDWD population}\label{sec:WDWD_distinguish}
-The simplest way to check whether a source is a WDWD is to check its chirp mass.
+The simplest way to check whether a source is a WDWD is to evaluate its chirp mass.
 The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$.
@@
 This is reason for very substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
-Additionally, the COMPAS code relies on fitting formula tat need to be extrapolated to create tracks are extrapolations at these higher masses.
+Additionally, the COMPAS code relies on fitting formula that are heavily extrapolated to be able to create evolutionary tracks for these higher mass progenitors.
 
@@
 
-\textit{Limited metallicity range:} The stellar evolution fitting formulae that COMPAS uses is that they are limited to a metallicity range of $10^{-4} \le Z \le 0.03$ \citep{Hurley+2000} and should not be extrapolated too far outside this range.
+\textit{Limited metallicity range:} The stellar evolution fitting formulae that COMPAS uses is limited to a metallicity range of $10^{-4} \le Z \le 0.03$ \citep{Hurley+2000} and should not be extrapolated too far outside this range.
 However, in our simulated Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
 
-For metallicities below our range we assume they evolve similar to our lowest metallicity models. DCO formation at metallicities above $Z = 0.03$ is 
-less efficient at high metallicity and so higher metallicities are unlikely to contribute significantly.
+For metallicities below the metallicity range allowed by COMPAS, we assume that binaries evolve similar to our lowest metallicity models.
+DCO formation at metallicities above $Z = 0.03$ becomes significantly less efficient for increasing metallicity.
+And so, higher metallicities are unlikely to contribute significantly.
+Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest metallicity bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
+# (old text for easy comparison): 
+#For metallicities below our range we assume they evolve similar to our lowest metallicity models.
+DCO formation at metallicities above $Z = 0.03$ is less efficient at high metallicity and so higher metallicities are unlikely to contribute significantly.
 Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).

### 2021-11-12 paper/tex/sections/introduction.tex
all Neige email comments done

@@
 We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters.
-We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the latest APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
+We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
 We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
@@
 
-All data produced in this study is publicly available on Zenodo \href{https://zenodo.org/record/4699713}{\faFileCode}\footnote{\url{https://zenodo.org/record/4699713}} as is the population used in our simulations \href{https://zenodo.org/record/4574727}{\faFileCode}\footnote{\url{https://zenodo.org/record/4574727}}.
+All data related to the predictions made in this study are publicly available on Zenodo at \citet{Wagg+2021_zenodo}, as are the populations used in our simulations at \citet[][BHBH]{Broekgaarden:2021-zenodo-BHBH} \citet[][BHNS]{Broekgaarden:2021-zenodo-BHNS} and  \citet[][NSNS]{Broekgaarden:2021-zenodo-NSNS}.
 We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}.

### 2021-11-12 paper/tex/sections/methods.tex
all Neige email comments done

@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binaries}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+for $i = 1, 2, \dots, N_{\rm binaries}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational-wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
 We sample from these sets of parameters when creating synthetic galaxies.
@@
 We improve upon this as the first study to use an empirically-informed analytical model of the Milky Way that takes into account the galaxy's enrichment history by applying the metallicity-radius-time relation from \citet{Frankel+2018}.
-The authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017}.
+Those authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017}.
 
@@
 Therefore, we instead use the chemical definition of the two disks (applying the \achem~nomenclature) as there is a clear bimodal distribution in the chemical plane, allowing stars to be assigned to each of the disc components based on their chemical abundances.
-For each of the three components, we use a separate star formation history and spatial distribution, which we combine into a single model, weighting each component by its stellar mass.
+For each of the three components, we use a separate star formation history and spatial distribution, which we combine into a single model, weighting each component by its present-day stellar mass.
 \citet{Licquia+2015} gives that the stellar mass of the bulge is $0.9 \times 10^{10} \unit{M_{\odot}}$ and the stellar mass of the disc is $5.2 \times 10^{10} \unit{M_\odot}$, which we split equally between the low- and high-\achem~discs \citep[e.g.,][]{Snaith+2014}.
@@
 where $R$ is the Galactocentric radius and $R_d$ is the scale length of the component.
-For the low-\achem~disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~5]{Frankel+2018}
+For the low-\achem~disc, we set $R_d = R_{\rm exp}(\tau)$, where $R_{\rm exp}(\tau)$ is the scale length presented in \citet[][Eq.~6]{Frankel+2018}
 \begin{equation}
@@
 \end{equation}
-where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{In $R_{\rm exp}(\tau)$, we use 4 kpc instead of 3 kpc for the 0 Gyr exponential scale-length of the disc as NF finds that it provides a better fit to the original data}.
+where $\alpha_{R_{\rm exp}} = 0.3$ is the inside-out growth parameter\footnote{We find that $R_{\rm exp}(\tau) = 4$ kpc fits the data well and adopt this value rather than the 3 kpc quoted in \cite{Frankel+2018}, which was a fixed parameter (not a fit).}
+
 This scale length accounts for the inside-out growth of the low-\achem~disc and hence is age dependent.
@@
 \end{equation}
-$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disc at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ set the time dependence of the chemical enrichment.
-We can convert this to the representation of metallicity that we use in this paper by applying \citep[e.g][]{Bertelli+1994}
+$F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disc at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ sets the time dependence of the chemical enrichment.
+We can convert this to the representation of metallicity that we use in this paper by applying \citep[e.g.][]{Bertelli+1994}
 \begin{equation}\label{eq:galaxy_FeH_to_Z}
@@
 \end{equation}
-for $j = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the polar angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
+for $j = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the azimuthal angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
 Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
@@
 The magnitude of the systemic kicks are typically small compared to the initial circular velocity of a binary at each Galactocentric radius.
-Therefore, we expect that kicks will not significantly alter the overall distribution of their positions (see however e.g.\ \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
+Therefore, we expect that kicks will not significantly alter the overall distribution of their positions (see however, e.g., \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
 Given this, and for the sake of computational efficiency, we do not account for the displacement due to systemic kicks in our analysis.
@@
 
-Note that the length of the LISA mission affects how much a binary will evolve over the mission and thus changes the frequency limits in Eq.~\ref{eq:snr}.
+Note that increasing the length of the LISA mission allows more time for a DCO to evolve over the mission.
+Therefore the frequency limits in Eq.~\ref{eq:snr} are dictated by the LISA mission length.
 The SNR generally scales as $\sqrt{T_{\rm obs}}$ (with exceptions for sources very close to merging) and thus the SNR of a typical source in a 10-year LISA mission is approximately $1.58$ (=$\sqrt{10/4}$) times stronger than in a 4-year mission.
 
-We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational wave luminosity remains below 1\%.
+We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational-wave luminosity remains below 1\%.
 

### 2021-11-12 paper/tex/sections/results.tex
all Neige email comments done

@@
 The peak is located at a frequency of about $0.4 \unit{mHz}$, which is much lower than the frequency where LISA will be most sensitive (about $10 \unit{mHz}$).
-This can be understood as an evolutionary effect.
+This can be understood from the acceleration of inspiraling DCOs as they evolve towards higher frequencies.
 DCOs typically form with wide orbits (low frequencies) that would not be detectable yet.
@@
 
-There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extend downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
+There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extends downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
 This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix, which shows a similar figure but colouring individual systems by their eccentricity.
@@
 The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-The dotted lines in the black hole mass panel show the individual primary and secondary mass distributions.
+The dotted lines in panel b show the individual primary and secondary mass distributions.
+The dotted line in panel e shows the star formation history we have assumed in our Milky Way model.
 See Sec.~\ref{sec:fiducial_distributions} for a discussion.
@@
 This results from the two contributions of the more and less massive BHs in BHBH systems, which peak at around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively as shown by the dotted lines (see also our discussion of the mass ratios below).
+
+% For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses. About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here. 
+% Unlike the current network of ground-based GW observatories, LISA will be equally sensitive to inspiraling BHBHs throughout the entire Milky Way, regardless of their mass (given that all inspiraling BHBH pass through the LISA sensitivity band \todo{citation?}).
+% Hence we expect LISA to provide us with an unbiased view of the distribution of BH masses in inspiraling compact object binaries.
 
@@
 For systems with eccentricities higher than $e\gtrsim0.3$, most gravitational wave energy is emitted in higher harmonics.
-Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of systems.
+Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of the systems.
 
-These BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel \citep{vandenHeuvel+2017}.
+The BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel. %\citep{vandenHeuvel+2017}. 
 These systems are still relatively wide just prior to formation of the second BH.
@@
 
-It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH.
-The kicks of BHs are reduced and they are thus less likely to disrupt the system.
+It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH systems.
+The kicks of BHs are reduced by fallback and they are thus less likely to disrupt the system.
 Moreover, because of their higher masses, BHBHs can be observed already at lower orbital frequencies.
@@
 
-When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBH and then BHNS.
-To understand this it is helpful to consider how the inspiral time scales with various parameters
+When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBHs and then BHNSs.
+To understand this it is helpful to consider that the inspiral time scales with various parameters
 \begin{equation}
@@
 The eccentricity term is not of importance for mildly eccentric systems, $f(e_{\rm DCO} \le 0.3)  \le 1.4$ but of large importance for the very eccentric  $f(e_{\rm DCO} \ge 0.9) \ge 300$.
-The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\$ and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.
+The fraction of highly eccentric systems with $e_{\rm DCO}>0.9$ is 33\%, 16\%, and 8\% of for BHBH, BHNS and NSNS respectively, see also Fig.~\ref{fig:dco_formation_properties}.
 
@@
 \paragraph{Time until merger} Fig.~\ref{fig:fiducial_pdf_distributions}f shows the remaining time until merger for each of the DCO types at the start of LISA mission.
-The distributions are strikingly similar and peak with merger times of around a Myr.
+The distributions are strikingly similar and peak with merger times of around one Myr.
 
@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
-For our Milky way model we considered three different components, a low-$\alpha$ (``thin'') disc, an older high-$\alpha$ (``thick'') disc and a bulge/bar.
+For our Milky way model we considered three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar.
 In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components.
-Despite the fact that only $42.5\%$ of systems are formed in the low-$\alpha$ disc, we find that $86\%$ of the detections originate from this component.
-This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}e) and so the high-$\alpha$ disc and bulge are effectively too old to contribute many detectable systems.
-Nevertheless, we do find a significant fraction of detectable systems originate in the high-$\alpha$ disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).
+Despite the fact that only $42.5\%$ of systems are formed in the low-\achem~disc, we find that $86\%$ of the detections originate from this component.
+This is because most detectable systems were formed relatively recently (see Fig.~\ref{fig:fiducial_pdf_distributions}e) and so the high-\achem~disc and bulge are effectively too old to contribute many detectable systems.
+Nevertheless, we do find a significant fraction of detectable systems originate in the high-\achem~disc and bulge, indicating that it is still important to include these components, as was ignored in some earlier works (see Sec.~\ref{sec:compare_studies}).
 
@@
 \subsection{Formation channels}\label{sec:progenitors_and_formation}
-In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarly formed through the `classic' channel \citep{Bhattacharya+1991}.
-Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the `classic' channel and the rest are mainly formed through only stable mass transfer.
+In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarily formed through the `classic' CE channel \citep{Bhattacharya+1991}.
+Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the classic channel and the rest are mainly formed through only stable mass transfer.
 
@@
 \subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
-So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
+% So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
 However, many sources will only be barely detectable.
 Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters.
-Below we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.
+Below
+Here we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.
 
@@
 In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR.
-Although many have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs.
-We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27) and 9(14) systems have SNRs greater than 10, 50 and 100 respectively.
+Although many LISA sources have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs.
+We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27), and 9(14) systems have SNRs greater than 10, 50 and 100, respectively.
 These high SNR systems are typically, but not only, the more massive BHBH systems.
@@
 
-We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
+We find that for a 4(10)-year LISA mission, approximately 41(105) detections have chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
-
+%
 Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
@@
 We quantify the sky localisation of a source by estimating the angular resolution for the detectable sources.
-Since all potential sources are effectively stationary on the timescale of the LISA mission, which can follow \citet{Mandel+2018} and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
+Since all potential sources are effectively stationary on the timescale of the LISA mission, we can follow \citet{Mandel+2018}, and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
 \begin{equation}
@@
 For comparison, the size of a pencil beam for a $15 \unit{m}$ diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees \citep{Smits+2009}, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (similar to the angular size of the moon).
-We will further discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
+We will further discuss the prospects of matching LISA detections to radio pulsars with SKA in Sec.~\ref{sec:pulsar_matching}.
 

### 2021-11-12 paper/tex/sections/variations.tex
all Neige email comments done

@@
 We first discuss the robustness of our predictions for the number of detectable systems (Section~\ref{sec:detection_rate_analysis}).
-We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe about the physics of double compact object formation (Section~\ref{sec:property_variations}).
+We then discuss examples of how the observable properties of the detectable systems, such as the distribution of masses and eccentricities, are affected and can potentially be used to probe the physics of double compact object formation (Section~\ref{sec:property_variations}).
 
@@
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as predicted by our simulations considering variations in the physical assumptions.
-We show predictions for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively.
+In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as calculated by our simulations considering variations in the physical assumptions.
+We show the expected number of detections for  BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively.
 All the rates and their uncertainties plotted in this figure are also provided in Table~\ref{tab:detection_rates}.
@@
 This is in part because the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS.
-The same effect also allows some NS progenitors to become massive enough to BH progenitors, but this effect is less strong.
-Furthermore, the changes in secondary mass and orbital widening, affects the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
+The same effect also allows some NS progenitors to become massive enough to become BH progenitors, but this effect is weaker.
+Furthermore, the changes in secondary mass and the orbital widening, affect the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
 
@@
 Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
-See also Fig.~\ref{fig:dco_relative_rates} and Sec.~\ref{sec:detection_rate_analysis} for a discussion.
+See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
@@
 There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged.
-Therefore we consider variations in this parameter.
+Therefore we consider large variations in this parameter.
 
@@
 (2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources.
-So, while the first consequence favours the formation of DCOs, the second consequence disfavours the subset that are tight enough to be detected.
+So, while the first consequence favours the formation of DCOs, the second consequence disfavours the formation of DCOs that are tight enough to be detected.
 
@@
 In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect.
-This is because BHBHs originate from the most massive progenitors, which in expand very significantly during the Hertzsprung gap phase in our simulations.
-The progenitors are likely initiate interaction during this phase.
+This is because BHBHs originate from the most massive progenitors, which expand significantly during the Hertzsprung gap phase in our simulations.
+The progenitors likely initiate interaction during this phase.
 Our predictions for the number of detectable systems increases by a factor 2.
@@
 
-We find that not implementing pair-instability supernovae (PISN) ot pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the number of detections with LISA.
-This is because the average metallicity of the Milky Way is high enough than no progenitor retains enough mass to initiate a PISN or PPISN.
+We find that not implementing pair-instability supernovae (PISN) or pulsational pair-instability supernovae (PPISN) in model \modNoPISN{} has no effect on the number of detections with LISA.
+This is because the average metallicity of the Milky Way is high enough such that no progenitor retains enough mass to initiate a PISN or PPISN.
 
-Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
+Decreasing the natal kicks for all core-collapse supernovae (models \modSigLow{}-\modSigLower{}) increases the detection rates for each DCO type, since lower kicks result in fewer disrupted binaries and hence a more numerous detectable population.
 The BHNS and NSNS systems are strongly affected whilst the impact on BHBH systems is insignificant.
@@
 
-Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA.
+Firstly, the decreased Wolf-Rayet like winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA.
 Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries.
-However, though this is the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at lower frequencies than in our fiducial model.
+However, though this is the case at DCO formation, we find that by the time the sources have evolved until the LISA mission they emit GW  at lower frequencies than in our fiducial model.
 This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times.

### 2021-11-16 paper/tex/paper.tex
all Neige email comments done
most comments up to variations resolved

@@
 
-\newcommand{\modRangeMT}{B-F}
-\newcommand{\modRangeCE}{G-K}
+\newcommand{\modRangeMT}{B-D}
+\newcommand{\modRangeCE}{E-K}
 \newcommand{\modRangeSN}{L-R}
@@
 
-\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA}}
+\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA}}
 
@@
 
+\acknowledgments{We thank Katie Brevik, Will Farr, Rob Farmer, Valeriya Korol, Floris Kummer, Eva Laplace, Mike Lau, Tyson Littenberg, Ilya Mandel, Mathieu Renzo, Alberto Sesana, Katie Sharpe, Simon Stevenson, the CCA GW group and COMPAS collaboration for insightful discussions.
+TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
+Portions of this study were inspired by the LISA Sprint at the Center for Computational Astrophysics of the Flatiron Institute, supported by the Simons Foundation.
+This project was funded in part by the National Science Foundation under Grant No.
+(NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
+715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.
+We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}
+
 \software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
@@
 
-\acknowledgments{We thank Mike Lau, Floris Kummer, Eva Laplace, Rob Farmer, Katie Sharpe, Mathieu Renzo, Katie Brevik, Alberto Sesana, Valeriya Korol, Will Farr, Tyson Littenberg and the members of the COMPAS collaboration for insightful discussions.
-TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
-Portions of this study were inspired by the LISA Sprint at the Center for Computational Astrophysics of the Flatiron Institute, supported by the Simons Foundation.
-This project was funded in part by the National Science Foundation under Grant No.
-(NSF grant number 2009131), the European Union’s Horizon 2020 research and innovation program from the European Research Council (ERC, Grant agreement No.
-715063), and by the Netherlands Organization for Scientific Research (NWO) as part of the Vidi research program BinWaves with project number 639.042.728.
-We further acknowledge the Black Hole Initiative funded by a generous contribution of the John Templeton Foundation and the Gordon and Betty Moore Foundation.}
-
 \clearpage

### 2021-11-16 paper/tex/sections/abstract.tex
most comments up to variations resolved

@@
-We present predictions for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
+We present models for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
 We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
 We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics.
-We predict that for a 4(10)-year mission, LISA will (typically) detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions).
+We predict that, on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
+The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all of our assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions).
 We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged.
 We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
-We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and SKA.
+We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the SKA.

### 2021-11-16 paper/tex/sections/appendix.tex
update labels in appendix tables
proof read variations
most comments up to variations resolved

--- 2021-10-16 paper/tex/sections/appendix.tex
@@
 
-In this section we summarise the main assumptions and settings that we use when performing population synthesis for this work.
-For a more general overview of every setting see \citet{Broekgaarden+2021}.
+In this section we summarise the main assumptions and settings from the population synthesis simulation from Broekgaarden et al.\ (2021a, 2021b).
 
@@
 
-We simulate between 1 and 100 million massive binaries for each of 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
-We simulate more binaries for higher metallicities so that large enough sample of DCOs at each metallicity (since DCOs are formed at a lower rate at higher metallicities).
+Broekgaarden et al.\ (2021a, 2021b) simulate between 1 and 100 million massive binaries for each of 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+They simulate more binaries for higher metallicities so that large enough sample of DCOs at each metallicity (since DCOs are formed at a lower rate at higher metallicities).
 These metallicities span the allowed metallicity range for the original fitting formulae on which COMPAS is based \citep{Hurley+2000}.
@@
 The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which we assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[e.g.\ consistent with][]{Sana+2012}.
-We additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
-We assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
-We assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
-Since we focus on post-interaction binaries which will have circularised after mass transfer we argue this is an reasonable assumption (as many studies have in the past) and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
+The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which Broekgaarden et al.\ (2021a, 2021b) assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[e.g.\ consistent with][]{Sana+2012}.
+They additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
+They assume that the initial separation follows a flat in the log distribution with $p(a_i) \propto 1 / a_i$ and $a_i \in [0.01, 1000] \unit{AU}$ \citep{Opik+1924, Abt+1983}.
+They assume that all binary orbits are circular at birth to reduce the dimensions of initial parameters.
+Since they focus on post-interaction binaries which will have circularised after mass transfer they argue this is an reasonable assumption (as many studies have in the past) and is likely not critical for predicting detection rates \citep{Hurley+2002, deMink+2015}.
 
-We apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of our sample.
+Broekgaarden et al.\ (2021a, 2021b) apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of their sample.
 This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing the DCO without STROOPWAFEL in effect.
 
-\subsection{Physical assumptions in our fiducial model}\label{app:fiducial_physics}
+\subsection{Physical assumptions in the fiducial model}\label{app:fiducial_physics}
 
@@
 
-\textit{Wind mass loss:} We follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
-We use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
-Additionally, we use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observed LBV eruptions for stars with luminosities and effective temperatures above the Humphreys-Davidson limit.
-We use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars, and set $f_{\rm WR} = 1$.
+\textit{Wind mass loss:} Broekgaarden et al.\ (2021a, 2021b) follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
+They use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
+Additionally, they use a separate, higher wind mass loss rate for luminous blue variable (LBV) stars, following \citet{Belczynski+2008}, to mimic observed LBV eruptions for stars with luminosities and effective temperatures above the Humphreys-Davidson limit.
+They use the Wolf-Rayet-like mass loss rate from \citet{Hamann+1998} with an additional metallicity scaling from \citet{Vink+2005} for helium stars, and set $f_{\rm WR} = 1$.
 See \citet{COMPAS:2021methodsPaper}, Section 3 for the explicit equations.
 
-\textit{Mass Transfer:} In determining the stability of mass transfer we use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
-The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is defined as the fraction of the mass transferred by the donor that is actually accreted by the accretor.
-We limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
+\textit{Mass Transfer:} In determining the stability of mass transfer Broekgaarden et al.\ (2021a, 2021b) use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
+The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is the fraction of the mass transferred by the donor that is actually accreted by the accretor.
+They limit the maximum accretion rate for stars to $\Delta M_{\rm acc} / \Delta t \le 10 M_{\rm acc} / \tau_{\rm KH}$, where $\tau_{\rm KH}$ is the Kelvin-Helmholtz timescale of the star \citep{Paczynski+1972, Hurley+2002}.
 The maximum accretion rate for compact objects is limited to the Eddington accretion rate.
-If more mass than these rates is accreted then we assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
-We assume that all mass transfer from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole is unstable \citep{Tauris+2015}.
+If more mass than these rates is accreted then they assume that the excess is lost through isotropic re-emission in the vicinity of the accreting star \citep[e.g.][]{Massevitch+1975, Soberman+1997}.
+They assume that all mass transfer from a stripped post-helium-burning-star (case BB) onto a neutron star or black hole is unstable \citep{Tauris+2015}.
 
-\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and we parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
-We assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
-For $\lambda$ we use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
-We assume that any Hertzsprung gap donor stars that initiate a common-envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
+\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and Broekgaarden et al.\ (2021a, 2021b) parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
+They assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
+For $\lambda$ they use the fitting formulae from \citet{Xu+2010, Xu+2010a}.
+They assume that any Hertzsprung gap donor stars that initiate a common-envelope phase will not survive this phase due to a lack of a steep density gradient between the core and envelope \citep{Taam+2000, Ivanova+2004, Klencki+2021}.
 This follows the `pessimistic' common-envelope scenario \citep[c.f.][]{Belczynski+2007}.
-We remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common-envelope phase as we treat these as failed common-envelope ejections, likely leading to a stellar merger.
+They remove any binaries where the secondary immediately fills its Roche lobe upon the conclusion of the common-envelope phase as they treat these as failed common-envelope ejections, likely leading to a stellar merger.
 
-\textit{Supernovae:} We draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
-For stars undergoing a general core-collapse supernova, we use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
-The \textit{delayed} prescription does not reproduce a neutron star black hole mass gap and we use this as our default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
-We draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
-We assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
-We set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
-For these supernovae, we set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
-We assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
-For these supernovae we calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
+\textit{Supernovae:} Broekgaarden et al.\ (2021a, 2021b) draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
+For stars undergoing a general core-collapse supernova, they use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
+The \textit{delayed} prescription does not reproduce a neutron star black hole mass gap and they use this as their default as it has been shown to provide a better fit for observed populations of DCOs \citep[e.g.][]{Vigna-Gomez+2018}.
+They draw the natal kick magnitudes from a Maxwellian velocity distribution with a one-dimensional root-mean-square velocity dispersion of $\sigma_{\rm rms}^{\rm 1D} = 265 \unit{km}{s^{-1}}$ \citep{Lyne+1994, Hobbs+2005}.
+They assume that stars with helium core masses between $1.6$--$2.25 \unit{M_{\odot}}$ \citep{Hurley+2002} experience electron-capture supernovae (ECSN) \citep{Nomoto+1984, Nomoto+1987, Ivanova+2008}.
+They set all remnant masses to $1.26 \unit{M_{\odot}}$ in this case as an approximation of the solution to Equation 8 of \citet{Timmes+1996}.
+For these supernovae, they set $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ \citep[e.g.][]{Pfahl+2002, Podsiadlowski+2004}.
+They assume that stars that undergo case BB mass transfer \citep{Dewi+2002} experience extreme stripping which leads to an ultra-stripped supernova \citep{Tauris+2013, Tauris+2015}.
+For these supernovae they calculate the remnant mass using the \citet{Fryer+2012} prescription and use $\sigma_{\rm rms}^{\rm 1D} = 30 \unit{km}{s^{-1}}$ (as with ECSN).
 Stars with final helium core masses between $35$-$135 \unit{M_{\odot}}$ are presumed to undergo a pair-instability, or pulsational pair-instability supernova \citep[e.g.][]{Woosley+2007, Farmer+2019}.
-We follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
-We assume that kicks are isotropic in the frame of the collapsing star.
-We adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
+They follow the prescription from \citet{Marchant+2019} as implemented in \citep{Stevenson+2019} for these supernovae.
+They assume that kicks are isotropic in the frame of the collapsing star.
+They adopt a maximum neutron star mass of $2.5 \unit{M_{\odot}}$ \citep[e.g.][]{Kalogera+1996, Fryer+2015, Margalit+2017} for the fiducial model and change the \citet{Fryer+2012} prescription accordingly.
 
 \subsection{Model variations} \label{sec:variation_assumptions}
-In addition to our fiducial model for the formation of DCOs, we explore \nMinusOneModels{} other models in which we change various aspects of the mass transfer, common-envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
+In addition to their fiducial model for the formation of DCOs, Broekgaarden et al.\ (2021a, 2021b) explore \nMinusOneModels{} other models in which they change various aspects of the mass transfer, common-envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{app:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
 
-Our fiducial model is labelled model \modFid{}.
+Their fiducial model is labelled model \modFid{}.
 Models \modRangeMT{} focus on changes to the mass transfer physics assumptions.
-We explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate.
-In models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which we set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
-In model \modCaseBB{} we investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole is always stable rather than always unstable.
+They explore the effect of fixing the mass transfer efficiency $\beta$ to a constant value, rather than allowing it to vary based on the maximum accretion rate.
+In models \modBetaLow{}, \modBetaMed{}, \modBetaHigh{}, in which they set the value of $\beta$ to $0.25$, $0.5$ and $0.75$ respectively.
 
 Models \modRangeCE{} focus on altering the common-envelope physics.
-We change the common-envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
-In model \modOpt{}, we relax our restriction that Hertzsprung gap donor stars cannot survive common-envelope events, thereby following the `optimistic' common-envelope scenario.
-We combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
+In model \modCaseBB{} Broekgaarden et al.\ (2021a, 2021b) investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole always leads to a stellar merger.
+They change the common-envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
+In model \modOpt{}, they relax their restriction that Hertzsprung gap donor stars cannot survive common-envelope events, thereby following the `optimistic' common-envelope scenario.
+They combine this with model \modCaseBB{} in model \modCaseBBOpt{}.
 
-In models \modRangeSN{} we consider changes related to our assumptions about supernova physics.
+In models \modRangeSN{} they consider changes related to their assumptions about supernova physics.
 Model \modRapid{} uses the alternate \textit{rapid} remnant mass prescription from \citet{Fryer+2012} instead of the \textit{delayed} prescription.
-We change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses.
+They change the maximum neutron star mass in models \modNSLow{} and \modNSHigh{} to $2$ and $3 \unit{M_{\odot}}$ respectively to account for the range of predicted maximum neutron star masses.
 Model \modNoPISN{} removes the implementation of pair-instability and pulsational pair-instability supernovae.
-In models \modSigLow{} and \modSigLower{} we decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
+In models \modSigLow{} and \modSigLower{} they decrease the root-mean-square velocity dispersion for core-collapse supernovae to explore the effect of lower kicks.
 Model \modNoBH{} removes the natal kick for all black holes.
 
-Finally, in models \modRangeML{} we investigate the effect of changing our assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
-We vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
+Finally, in models \modRangeML{} Broekgaarden et al.\ (2021a, 2021b) investigate the effect of changing their assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
+They vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.
 These values approximately span the current range of possible Wolf-Rayet wind efficiencies suggested from observations \citep[e.g.][]{Vink+2017, Hamann+2019, Shenar+2019, Miller-Jones+2021, vanSon+2021}.
@@
         \modBetaHigh & Fixed mass transfer efficiency of $\beta=0.75$ \\
-        \modCaseBB & Case BB mass transfer is always unstable \\
-        \modCaseBBOpt & Model \modCaseBB{} + Model \modOpt{} \\
         \hline
+        \modCaseBB & Exclude Case BB mass transfer \\
+        \modCaseBBOpt & Case BB always unstable + Optimistic CE \\
         \modAlphaLowest & CE efficiency parameter $\alpha = 0.1$ \\
@@
 Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (Kummer et al.
-(in prep)).
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (e.g.\ \citealt{Dominik+2015, Neijssel+2019}, Kummer et al.
+2021).
 For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
@@
     \caption{The number of detectable binaries in a 4- and 10-year LISA mission for the \nModels{} different model variations and each DCO type.
+Each model variation is discussed in App.~\ref{sec:variation_assumptions} and the trends in detection rates are discussed in Sec.~\ref{sec:detection_rate_analysis}.
 The `All' column contains the total expected detections when summed over the three types.
@@
         D & $\beta=0.75$ & \confinv{67.0}{8.0}{8.0} & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{104.5}{10.5}{10.5} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
-        E & unstable
-        case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
-        F & E+K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
+        E & no case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
+        F & E + K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
         G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \boldconfinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \boldconfinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
@@
 Channels are described in detail in \citet{Broekgaarden+2021}.
-The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only `only stable' consists of only stable mass transfer and `other' contains the remaining binaries which are mainly formed from `lucky' supernova kicks that shrink the binary.
+The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only ``only stable'' consists of only stable mass transfer and ``other'' contains the remaining binaries which are mainly formed from case A ``classic'' binaries as well as ``lucky'' supernova kicks that shrink the binary.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig16_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
@@
     \label{fig:dco_formation_properties}
-
-    \includegraphics[width=\textwidth]{fig19_dco_relative_rates.pdf}
-    \caption{Similar to Fig.~\ref{fig:detection_rates}, this shows the \textit{relative} detection rates compared to the fiducial model in order to emphasise how much each DCO is affected by model variations compared to other DCOs.
-The scatter points show the mean and the shaded areas show the 1-$\sigma$ uncertainty range.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig19_dco_relative_rates.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
-    \label{fig:dco_relative_rates}
 \end{figure*}

### 2021-11-16 paper/tex/sections/comparisons.tex
most comments up to variations resolved

@@
     \caption{A table comparing previous studies of a similar nature to this work.
+In the detection rate section darker shades of blue indicate higher detection rates.
+In other sections, darker shades of green indicate more detailed models or more accurate choices.
+Entries in detection rates with two values listed correspond to the different mission lengths (penultimate column).
 The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
@@
 This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
-We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate (see Appendix~\ref{app:mw_changes}).
+We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \citep[see][ and also appendix~\ref{app:mw_changes} for further discussion]{Dominik+2015, Neijssel+2019}.
 Finally, it could be that different implicit assumptions in their population synthesis code lead to differences in our results \citep{Toonen+2014}.

### 2021-11-16 paper/tex/sections/discussion.tex
most comments up to variations resolved

@@
 It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
-The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}.
+The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of the more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}.
 It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
@@
 However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}.
-This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane.
+This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane (though even then there is a chance they were formed dynamically).
 We can use the sky localisation, scale height of the disc and distance to the source to estimate what fraction of eccentric sources can be localised to the Galactic plane.
@@
 Note that although the fractions are the same for the 10-year mission, the \textit{absolute} number of detections is still greater.
-
+%
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
@@
 For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency, mass ratio and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}).
-This method would pose a challenge however as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.
+This method would pose a challenge, however, as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.
 
@@
 
-We estimate on average, given the number of detectable pulsars and SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
+We estimate that on average, given the number of detectable pulsars and SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
 Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA.
@@
 Both SKA and LISA will measure the orbital frequency to high precision, as well as the time derivative of the frequency and chirp mass to a lesser precision, of each of these systems.
-Therefore, one could perform a targeted search with SKA that checks the sky location given by LISA and only looking for binary pulsars with orbital frequencies within the uncertainties.
+Therefore, one could perform a targeted search with SKA that checks the sky location given by LISA, only looking for binary pulsars with orbital frequencies within the uncertainties.
 If there was \textit{still} more than one possible pulsar one could also check against the chirp mass.
@@
 \textit{Large progenitor masses:} Many of the black holes that are formed in our sample come from progenitors with large initial masses.
-The primary stars in systems that form  BHNSs and BHBHs have very primary progenitor masses that peak around 50\Msun and 80\Msun, but they extend well beyond that.
-The evolution of such massive progenitor stars is very poorly understood and observational constraints are very scarce in this mass range and practically non existent for the later rapid evolutionary phases.
-This is reason for very substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
-Additionally, the COMPAS code relies on fitting formula that are heavily extrapolated to be able to create evolutionary tracks for these higher mass progenitors.
+The primary stars in systems that form BHNSs and BHBHs have very large primary progenitor masses that peak around 50\Msun and 80\Msun, but they extend well beyond that.
+The evolution of such massive progenitor stars is very poorly understood and observational constraints are very scarce in this mass range and practically non-existent for the later rapid evolutionary phases.
+For these reasons, the COMPAS code relies heavily extrapolated on fitting formulae to create evolutionary tracks for these higher mass progenitors.
+This leads to substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
 
-\textit{Underlying helium star models:} One source of weakness is that the \citet{Hurley+2000} fitting formulae for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
+\textit{Underlying helium star models:} One source of weakness is that the \citet{Hurley+2000} fitting formulae (used by COMPAS) for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
 A more comprehensive set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
@@
 
-For metallicities below the metallicity range allowed by COMPAS, we assume that binaries evolve similar to our lowest metallicity models.
-DCO formation at metallicities above $Z = 0.03$ becomes significantly less efficient for increasing metallicity.
+For metallicities below the range allowed by COMPAS, we assume that binaries evolve similar to our lowest metallicity models.
+DCO formation at metallicities above $Z = 0.03$ is significantly less efficient for increasing metallicity.
 And so, higher metallicities are unlikely to contribute significantly.
 Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest metallicity bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
-# (old text for easy comparison): 
-#For metallicities below our range we assume they evolve similar to our lowest metallicity models.
-DCO formation at metallicities above $Z = 0.03$ is less efficient at high metallicity and so higher metallicities are unlikely to contribute significantly.
-Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
 

### 2021-11-16 paper/tex/sections/introduction.tex
most comments up to variations resolved

@@
-Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}, offering exciting insights into the formation, lives and deaths of massive (binary) stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
+Since the first direct observation of gravitational waves \citep{Abbott+2016_first_detection}, the number of black hole (BH) and neutron star (NS) binaries observed by ground-based gravitational-wave detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2,Abbott+2021_GWTC3}, offering exciting insights into the formation, lives and deaths of massive (binary) stars \citep[e.g.][]{Abbott+2021_GWTC2_inference}.
 
@@
 
-In this paper, we present predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
+In this paper, we present models for the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
 We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the prospects for distinguishing DCO detections from the WDWD background.
@@
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
-We provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
+We provide a detailed treatment of the eccentricity of detectable sources, both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
 Moreover, our binary population synthesis simulation is the most extensive of its kind to date and makes use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.

### 2021-11-16 paper/tex/sections/results.tex
most comments up to variations resolved

@@
-In this section we present our predictions for the population of detectable LISA sources.
-In total we expect $124$ detections in a 4-year LISA mission, of which $\BHBHFourYear{}$, $\BHNSFourYear{}$ and $\NSNSFourYear{}$ are BHBHs, BHNSs and NSNSs respectively, based on our fiducial simulations.
+In this section we present our predictions for the population of detectable LISA sources for our fiducial model.
+In total we expect, on average, $124$ detections in a 4-year LISA mission, of which $\BHBHFourYear{}$, $\BHNSFourYear{}$ and $\NSNSFourYear{}$ are BHBHs, BHNSs and NSNSs respectively, based on our fiducial simulations.
 In the remainder of this section, we discuss where the sources are expected relative to LISA's sensitivity curve (Sec.~\ref{sec:dcos_on_sc}), their properties (Sec.~\ref{sec:fiducial_distributions}), their locations in the Milky Way (Sec.~\ref{sec:mw_detectable_distribution}), their formation channels (Sec.~\ref{sec:progenitors_and_formation}) and finally we discuss the expected SNR and how accurately we expect that the parameters can be measured (Sec.~\ref{sec:measurement_uncertainties}).
@@
 
-% For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses. About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here. 
-% Unlike the current network of ground-based GW observatories, LISA will be equally sensitive to inspiraling BHBHs throughout the entire Milky Way, regardless of their mass (given that all inspiraling BHBH pass through the LISA sensitivity band \todo{citation?}).
-% Hence we expect LISA to provide us with an unbiased view of the distribution of BH masses in inspiraling compact object binaries.
-
 For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses.
 About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here.
-This is in stark contrast with the masses of the BHs that have been detected so far by ground-based GW detectors, where heavy BHs, with masses of about $30\unit{M_{\odot}}$ and higher have been common.
-Ground-based detectors are strongly biased towards high mass systems, since they can be detected out to larger distances.
-Instead, LISA is, in principle, sensitive to inspiraling BHBHs throughout the entire Milky Way regardless of their mass, as long as we catch them at the right time when their dominant frequencies coincide with the range where LISA is sensitive.
-
-A further reason that we predict that LISA will not detect high mass systems is that the population of BHs that are detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations.
+This is in stark contrast with observations from ground-based GW detectors, where heavy BHs with masses of about $30\unit{M_{\odot}}$ and higher have been common.
+There are two main reasons for this discrepancy.
+First, the population of BHs in the Milky Way (and, in particular, those detectable by LISA due to their recent formation times, see Figure~\ref{fig:fiducial_pdf_distributions}e) primarily come from progenitors that formed from high metallicity gas according to our simulations.
 Stellar winds are stronger at high metallicity leading to increased mass loss.
 This affects the mass of the most massive black holes that can be formed \citep{Belczynski+2010}.
+Secondly, ground-based detectors are strongly biased towards high mass systems, since they can be detected out to larger distances and thus a greater volume is probed.
+In contrast, LISA has no such bias and is, in principle, sensitive to inspiraling BHBHs throughout the entire Milky Way regardless of their mass, as long as we catch them when they are emitting in the LISA band.
+For this reason, LISA is more likely to detect the more common lower mass BHBHs.
 
@@
 The BHs in this simulation fill the so-called ``lower mass gap'' marked as a grey band \citep{Ozel+2010,Farr+2011}, see also \citet{Shao+2021} who recently pointed this out.
-This prediction is sensitive to adopted model for fall back during the SN explosion as we discuss this further in Sec.~\ref{sec:lower_mass_gap}
+This prediction is sensitive to adopted model for fallback during the SN explosion as we discuss this further in Section~\ref{sec:lower_mass_gap}
 
 \paragraph{Mass Ratio} The mass ratio distributions for each DCO type are very distinct from one another, as can be seen in Fig.~\ref{fig:fiducial_pdf_distributions}c.
-The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$.
+The majority of NSNSs have a mass ratio close to unity, with $\NSNSqAbovePointEight{}$ of systems having $q > 0.8$, where $q \equiv m_2 / m_1$.
 The reason for the concentration around equal masses is that most NSs are formed either through electron-capture supernovae (ECSN) or from low mass stars in our simulations.
@@
 Both effects, the reduced expansion and increased widening of the orbit, tend to prevent the secondaries from being able to fill their Roche lobe.
-This thus limits the number of systems that experience the reverse mass transfer or common envelope phase needed shrink the orbits and make them tight enough to be detected as gravitational wave sources.
+This thus limits the number of systems that experience the reverse mass transfer or common-envelope phase needed shrink the orbits and make them tight enough to be detected as gravitational-wave sources.
 
@@
 Around two thirds of detectable BHNSs experience at least one common-envelope event, whilst the last third are formed through only stable mass transfer.
-The first peak at $q = 0.18$ is from systems that experience at least one common-envelope and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
+The first peak at $q = 0.18$ is from systems that experience at least one common-envelope phase and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
 Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arises from the fraction of the population that underwent only stable mass transfer phases.
@@
 We find that most systems (73\%) will have eccentricities larger than $0.01$ during the LISA mission, which should in principle be detectable according to \citet{Nishizawa+2016}.
-This means that we will potentially be able to use eccentricity to distinguish these sources from WD sources, which are expected to have little to no eccentricity (see Sec.~\ref{sec:WDWD_distinguish}).
+This means that we will potentially be able to use eccentricity to distinguish these sources from WDWDs, which are expected to have little to no eccentricity (see Sec.~\ref{sec:WDWD_distinguish}).
 We note that several previous studies assumed all systems to be circular when calculating the detection rates \citep[e.g.][]{Liu+2014, Lamberts+2018, Sesana+2020}.
-See Sec.~\ref{sec:compare_studies} for a discussion of the impact of this assumption.
+We discuss the impact of this assumption in Section~\ref{sec:compare_studies}.
 
 For systems with eccentricities higher than $e\gtrsim0.3$, most gravitational wave energy is emitted in higher harmonics.
-Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of the systems.
-
-The BHBHs that are still eccentric when reaching the LISA band are primarily systems formed through the stable mass transfer channel. %\citep{vandenHeuvel+2017}. 
-These systems are still relatively wide just prior to formation of the second BH.
+Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of systems.
+Detectable BHBHs in our simulation (and, in particular, those that are eccentric) are primarily systems formed through the stable mass transfer channel (see Section~\ref{fig:formation_channels}).
+These systems are still relatively wide (compared to those formed through the CE channel) immediately prior to formation of the second BH, which makes them more easily affected by kicks.
 If the kick is oriented roughly in opposite direction to the orbital motion and has a velocity that is of similar magnitude as the orbital velocity, it will lead to the formation of a highly eccentric system.
 
-It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBH systems.
+It is rare to get such a ``lucky kick'', but there are a few effects that favour this for BHBHs.
 The kicks of BHs are reduced by fallback and they are thus less likely to disrupt the system.
@@
 Finally, LISA favours the detection of eccentric systems, if all other properties are held fixed.
-This is because the gravitational wave emission is stronger (Eq.~\ref{eq:peters_f}) and the energy is emitted at higher frequencies \citep[Eq.~20]{Peters+1963} where LISA is more sensitive.
+This is because the gravitational-wave emission is stronger (Eq.~\ref{eq:peters_f}) and the energy is emitted at higher frequencies \citep[Eq.~20]{Peters+1963} where LISA is more sensitive.
 
@@
 In Fig.~\ref{fig:fiducial_pdf_distributions}e we show how long ago the LISA detectable DCOs formed.
-For comparison we show the star formation history we have assumed in our Milky Way model (grey dotted line).
 Star formation was highest at early times $6-12\unit{Gyr}$ ago, after which it declined.
@@
 When comparing the distribution of formation times for the three different DCO types we see that NSNSs are most strongly concentrated at recent times, followed by BHBHs and then BHNSs.
-To understand this it is helpful to consider that the inspiral time scales with various parameters
+To understand this it is helpful to consider how the inspiral time scales with various parameters \citep{Peters+1964}
 \begin{equation}
@@
 The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}).
-The NSNS systems have the tightest orbits at DCO formation.
-The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for BHBH:BHNS:NSNS in our simulations.
+The detectable NSNS systems have the tightest orbits at DCO formation.
+The median of the distribution of separations at DCO formation, $\langle a_{\rm DCO} \rangle_{\rm med}$, relate as 8:3:1 for detectable BHBH:BHNS:NSNS in our simulations.
 This results in increase of the inspiral time by a factor of about 4000:80:1.
 The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured.
-The median total masses differ by ratios of 6:4:1 for BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations.
+The median total masses differ by ratios of 6:4:1 for detectable BHBH:BHNS:NSNS in our simulations, impacting the inspiral times such that they are a factor of 200:60:1 shorter, partially counteracting the effect of the separations.
 The term depending on the mass ratio $q$ only varies by about 30\% for the mass ratio ranges considered here and so is not of interest.
@@
 \paragraph{Time until merger} Fig.~\ref{fig:fiducial_pdf_distributions}f shows the remaining time until merger for each of the DCO types at the start of LISA mission.
-The distributions are strikingly similar and peak with merger times of around one Myr.
+The distributions are strikingly similar and peak with merger times of around a Myr.
 
@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
-For our Milky way model we considered three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar.
+For our Milky way model we consider three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar.
 In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components.
@@
     \centering
-    \begin{tabular}{l|ccccc}
+    \begin{tabular}{l|c|cccc}
         \hline
@@
 The reason that the NSNSs are favoured at higher distances is that the NSNS population has the highest fraction of ``mildly'' eccentric systems ($0.01 < e < 0.03$).
-In contrast, the BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational wave compared to equivalent eccentric systems.
+In contrast, the BHNS population has a much higher fraction of effectively circular systems ($e < 0.01$), which emit weaker gravitational waves compared to equivalent eccentric systems.
 Therefore, despite their typically higher masses, the distance at which a BHNS source is detectable is generally lower than for the mildly eccentric NSNS.
@@
 \subsection{Formation channels}\label{sec:progenitors_and_formation}
-In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel \citep{vandenHeuvel+2017}, whilst the remaining third are primarily formed through the `classic' CE channel \citep{Bhattacharya+1991}.
+In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel, whilst the remaining third are primarily formed through the `classic' CE channel.
 Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the classic channel and the rest are mainly formed through only stable mass transfer.
@@
 \subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
-% So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
+So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
 However, many sources will only be barely detectable.
 Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters.
-Below
-Here we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.
+Below we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.
 
@@
 In Fig.~\ref{fig:snr_dist} we show the cumulative number of detections with a given SNR.
-Although many LISA sources have SNRs around the our assumed detection threshold of 7, many systems are detection with very high SNRs.
-We find that for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27), and 9(14) systems have SNRs greater than 10, 50 and 100, respectively.
+Although many a large fraction of sources have SNRs around our assumed detection threshold of 7, many systems are detected with very high SNRs.
+We find that on average for a 4(10)-year LISA mission, of the 124(202) detections, 85(138), 16(27) and 9(14) systems have SNRs greater than 10, 50 and 100, respectively.
 These high SNR systems are typically, but not only, the more massive BHBH systems.
@@
 
-We find that for a 4(10)-year LISA mission, approximately 41(105) detections have chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\%.
+We find that for a 4(10)-year LISA mission, approximately 41(105) detections have measurable chirp masses ($\Delta \mathcal{M}_c / \mathcal{M}_c < 1$, indicated by the dark shaded region in Fig.~\ref{fig:m_c_unc}) whilst 13(31) have chirp mass uncertainties below 10\% ($\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$, indicated by the light shaded region in Fig.~\ref{fig:m_c_unc}).
 This uncertainty is generally dominated by the uncertainty on the time derivative of the frequency, since most of the binaries are too early in their inspiral for LISA to measure a strong chirp.
 %
-Note that increasing the mission length significantly increases the number of detections for which we can measure the mass.
-The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the total number of detections \textit{with well measured masses} scales approximately as $T_{\rm obs}$.
+Note from Fig.~\ref{fig:m_c_unc} that increasing the mission length significantly increases the number of detections for which the chirp mass uncertainty is below 100\%.
+The total number of detections only scales as $\sqrt{T_{\rm obs}}$, yet we find that the the total number of detections with a chirp mass uncertainty is below 100\% and 10\% both scale approximately as $T_{\rm obs}$.
 
@@
 We quantify the sky localisation of a source by estimating the angular resolution for the detectable sources.
-Since all potential sources are effectively stationary on the timescale of the LISA mission, we can follow \citet{Mandel+2018}, and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
+Since all potential sources are effectively stationary on the timescale of the LISA mission, we can follow \citet{Mandel+2018} and use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
 \begin{equation}
@@
 \end{equation}
-where $L$ is the effective detector baseline, which for LISA is 2 AU since it will orbit the Sun.
+where $L$ is the effective detector baseline, which for LISA is 2 AU in the frame of the solar system, since it will orbit the Sun.
 

### 2021-11-16 paper/tex/sections/variations.tex
most comments up to variations resolved

@@
 In this section we explore the effect of varying the uncertain assumptions governing the evolution of binary system and the formation of compact objects.
-For this we use the model variations presented in \citet{Broekgaarden+2021}.
+For this we use the population synthesis simulations and model variations presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ 2021b (in prep.).
 
@@
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-In Figure~\ref{fig:detection_rates}, we show the number of LISA detections as calculated by our simulations considering variations in the physical assumptions.
+In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections based on our simulations considering variations in the physical assumptions.
 We show the expected number of detections for BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively.
@@
 
-The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}.
+The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche-lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}.
 In our fiducial model A, we use a prescription in which the accretion rate onto stellar companions is regulated by their thermal timescale, i.e.\ the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
@@
 For the most massive progenitors, increasing $\beta$ leads to secondary stars that are so massive and luminous that they experience strong wind mass loss.
-This leads to further widening of the orbit and it limits the amount by which the secondaries expand.
-Both of these effects can prevent secondaries from filling their Roche lobe.
+This leads to further widening of the orbit.
+In addition the more massive secondaries may not be able to fully expand as mass loss may prematurely remove their hydrogen envelope.
+Both of these effects tend to prevent the most massive secondaries from filling their Roche lobe.
 This means that they cannot initiate the reverse interaction needed to shrink the binary system and eventually produce a detectable double compact object.
@@
 For lower mass progenitors, which primarily produce NSNS systems, we find the opposite: increasing $\beta$ leads to an \textit{increase} in the number of detectable NSNS systems.
-This is in part because the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS.
-The same effect also allows some NS progenitors to become massive enough to become BH progenitors, but this effect is weaker.
-Furthermore, the changes in secondary mass and the orbital widening, affect the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
+This is in part because  the changes in secondary mass and the orbital widening, affect the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
+Furthermore, the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS \citep[e.g.\,][]{Zapartas+2017}.
+The same effect also allows some NS progenitors to become massive enough to become BH progenitors, which partially cancels the extra progenitors that would have originally been destined to become WDs.
 
@@
 
-The common-envelope phase constitutes the most challenging phase in the evolution of interacting binary systems \citep{Ivanova+2013}.
-The debate concerns the conditions required for the onset of a common envelope phase and, if a common envelope phase occurs, what the outcome is.
+The common-envelope phase constitutes a highly uncertain phase in the evolution of interacting binary systems \citep[e.g.\ ][]{Ivanova+2013}.
+The uncertainties concerns the conditions required for the onset of a common-envelope phase and, if a common-envelope phase occurs, what the outcome is.
 Rapid population synthesis simulations such as ours approximate both questions in a crude way.
@@
 
-\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy  \citep{Webbink+1984}.
-Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope \citep{Webbink+1984}.
-There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations, but no consistent picture has emerged.
+\paragraph{The efficiency parameter $\alpha_{\rm CE}$} To estimate the outcome of a CE phase, we use a simple consideration of the binding energy and orbital energy \citep{Webbink+1984, deKool+1990}.
+Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope.
+There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations \citep[e.g.\ ][]{DeMarco+2011, Fragos+2019, Law-Smith+2020}, but no consistent picture has emerged.
 Therefore we consider large variations in this parameter.
@@
 This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}.
-This is of particular interest for the formation of NS stars, as their lower mass progenitors are swelling the most during this phase \citep[e.g.][and references therein]{Laplace+2020}.
-Nearly all NSNS systems from through case BB mass transfer
+This is of particular interest for the formation of NSs, as their lower mass progenitors are swelling the most during this phase \citep[e.g.][and references therein]{Laplace+2020}.
+Population synthesis studies find that nearly all NSNS systems might from through a phase of case BB mass transfer \citep{Vigna-Gomez+2018}.
 
@@
 It affects by how much stars can grow in size and it affects the final core masses.
-\citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by hot and luminous Wolf-Rayet stars.
+\citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by naked helium (Wolf-Rayet like) stars.
 We find that a reduction of the wind mass loss has very little effect on our predictions.
@@
 Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries.
-However, though this is the case at DCO formation, we find that by the time the sources have evolved until the LISA mission they emit GW  at lower frequencies than in our fiducial model.
+However, though this is the case at DCO formation, we find that by the time the sources have evolved until they are observable by the LISA mission, they have lower orbital frequencies than in our fiducial model.
 This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times.
@@
 From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.
-
+%
 However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them.
@@
     \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}).
-The curve for $f_{\rm WR} = 5$ has much higher uncertainties as there are many fewer systems formed in this model (the inverse reasoning also explains the lower uncertainties for $f_{\rm WR} = 0.1$).
+The curve for $f_{\rm WR} = 5$ has much higher uncertainties as there are many fewer DCO systems formed in this model (the inverse reasoning also explains the lower uncertainties for $f_{\rm WR} = 0.1$).
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}

### 2021-11-16 paper/tex/sections/appendix.tex
reduce sig figs

@@
         \hline
-        A & fiducial & \confinv{124.3}{11.3}{10.7} & \confinv{74.0}{9.0}{9.0} & \confinv{42.4}{6.4}{6.6} & \confinv{7.9}{2.9}{3.1} & \confinv{202.2}{14.2}{13.8} & \confinv{117.9}{10.9}{11.1} & \confinv{71.3}{8.3}{8.7} & \confinv{13.0}{4.0}{4.0}\\
-        B & $\beta=0.25$ & \confinv{94.1}{10.1}{9.9} & \confinv{68.8}{7.8}{8.2} & \confinv{22.4}{4.4}{4.6} & \confinv{2.9}{1.9}{2.1} & \confinv{149.3}{12.3}{12.7} & \confinv{107.8}{10.8}{10.2} & \confinv{36.9}{5.9}{6.1} & \confinv{4.6}{1.6}{2.4}\\
-        C & $\beta=0.5$ & \confinv{59.2}{8.2}{7.8} & \confinv{47.0}{7.0}{7.0} & \confinv{8.3}{3.3}{2.7} & \confinv{3.9}{1.9}{2.1} & \confinv{95.9}{9.9}{10.1} & \confinv{75.8}{8.8}{9.2} & \confinv{13.6}{3.6}{3.4} & \confinv{6.4}{2.4}{2.6}\\
-        D & $\beta=0.75$ & \confinv{67.0}{8.0}{8.0} & \confinv{46.9}{6.9}{7.1} & \confinv{7.4}{2.4}{2.6} & \confinv{12.7}{3.7}{3.3} & \confinv{104.5}{10.5}{10.5} & \confinv{71.2}{8.2}{8.8} & \confinv{12.1}{3.1}{3.9} & \confinv{21.1}{4.1}{4.9}\\
-        E & no case BB & \confinv{76.7}{8.7}{8.3} & \confinv{69.3}{8.3}{8.7} & \confinv{7.3}{2.3}{2.7} & \boldconfinv{0.2}{0.2}{0.8} & \confinv{121.4}{11.4}{10.6} & \confinv{109.3}{10.3}{10.7} & \confinv{11.8}{3.8}{3.2} & \boldconfinv{0.4}{0.4}{0.6}\\
-        F & E + K & \boldconfinv{320.9}{17.9}{18.1} & \boldconfinv{154.3}{12.3}{12.7} & \boldconfinv{148.4}{12.4}{12.6} & \confinv{18.2}{4.2}{3.8} & \boldconfinv{483.7}{21.7}{22.3} & \boldconfinv{239.5}{15.5}{15.5} & \confinv{216.8}{14.8}{15.2} & \confinv{27.4}{5.4}{5.6}\\
-        G & $\alpha_{\rm CE}=0.1$ & \confinv{40.2}{6.2}{6.8} & \confinv{27.9}{4.9}{5.1} & \boldconfinv{2.1}{1.1}{1.9} & \confinv{10.2}{3.2}{2.8} & \confinv{64.1}{8.1}{7.9} & \confinv{43.9}{6.9}{7.1} & \boldconfinv{3.5}{1.5}{1.5} & \confinv{16.7}{3.7}{4.3}\\
-        H & $\alpha_{\rm CE}=0.5$ & \confinv{85.9}{8.9}{9.1} & \confinv{58.3}{7.3}{7.7} & \confinv{21.8}{4.8}{4.2} & \confinv{5.9}{2.9}{2.1} & \confinv{136.2}{11.2}{11.8} & \confinv{91.6}{9.6}{9.4} & \confinv{34.9}{5.9}{6.1} & \confinv{9.7}{2.7}{3.3}\\
-        I & $\alpha_{\rm CE}=2.0$ & \confinv{133.3}{11.3}{11.7} & \confinv{67.6}{8.6}{8.4} & \confinv{38.0}{6.0}{6.0} & \confinv{27.7}{5.7}{5.3} & \confinv{218.4}{14.4}{14.6} & \confinv{109.6}{10.6}{10.4} & \confinv{62.7}{7.7}{8.3} & \confinv{46.0}{7.0}{7.0}\\
-        J & $\alpha_{\rm CE}=10.0$ & \confinv{77.9}{8.9}{9.1} & \confinv{26.7}{4.7}{5.3} & \confinv{16.3}{4.3}{3.7} & \boldconfinv{34.9}{5.9}{6.1} & \confinv{126.2}{11.2}{10.8} & \confinv{42.4}{6.4}{6.6} & \confinv{26.6}{5.6}{5.4} & \boldconfinv{57.2}{7.2}{7.8}\\
-        K & optimistic
-        CE & \confinv{218.3}{15.3}{14.7} & \confinv{151.5}{12.5}{12.5} & \confinv{56.8}{7.8}{7.2} & \confinv{9.9}{2.9}{3.1} & \confinv{341.5}{18.5}{18.5} & \confinv{229.7}{14.7}{15.3} & \confinv{96.1}{10.1}{9.9} & \confinv{15.8}{3.8}{4.2}\\
-        L & rapid SN & \confinv{127.3}{11.3}{11.7} & \confinv{50.4}{7.4}{6.6} & \confinv{70.2}{8.2}{8.8} & \confinv{6.7}{2.7}{2.3} & \confinv{204.9}{13.9}{14.1} & \confinv{76.6}{8.6}{8.4} & \confinv{117.4}{10.4}{10.6} & \confinv{10.8}{2.8}{3.2}\\
-        M & max $m_{\rm NS}$
-        $2.0 \, {\rm M_{\odot}}$ & \confinv{133.5}{11.5}{11.5} & \confinv{96.2}{10.2}{9.8} & \confinv{30.1}{5.1}{5.9} & \confinv{7.2}{2.2}{2.8} & \confinv{215.2}{14.2}{14.8} & \confinv{153.7}{12.7}{12.3} & \confinv{49.9}{6.9}{7.1} & \confinv{11.6}{3.6}{3.4}\\
-        N & max $m_{\rm NS}$
-        $3.0 \, {\rm M_{\odot}}$ & \confinv{118.4}{10.4}{10.6} & \confinv{58.3}{7.3}{7.7} & \confinv{51.9}{6.9}{7.1} & \confinv{8.2}{3.2}{2.8} & \confinv{189.9}{13.9}{14.1} & \confinv{91.6}{9.6}{9.4} & \confinv{84.8}{8.8}{9.2} & \confinv{13.5}{3.5}{3.5}\\
-        O & no PISN & \confinv{126.7}{11.7}{11.3} & \confinv{75.3}{8.3}{8.7} & \confinv{43.4}{6.4}{6.6} & \confinv{8.0}{3.0}{3.0} & \confinv{205.7}{14.7}{14.3} & \confinv{120.5}{10.5}{10.5} & \confinv{72.3}{8.3}{8.7} & \confinv{12.8}{3.8}{3.2}\\
-        P & $\sigma_{\rm cc}$
-        $100 \, {\rm km s^{-1}}$ & \confinv{184.6}{13.6}{13.4} & \confinv{82.7}{8.7}{9.3} & \confinv{86.6}{9.6}{9.4} & \confinv{15.4}{4.4}{3.6} & \confinv{300.8}{17.8}{17.2} & \confinv{130.1}{11.1}{11.9} & \confinv{145.1}{12.1}{11.9} & \confinv{25.6}{4.6}{5.4}\\
-        Q & $\sigma_{\rm cc}$
-        $30 \, {\rm km s^{-1}}$ & \confinv{268.3}{16.3}{16.7} & \confinv{91.8}{9.8}{9.2} & \confinv{142.9}{11.9}{12.1} & \confinv{33.6}{5.6}{5.4} & \confinv{426.8}{20.8}{21.2} & \confinv{142.9}{11.9}{12.1} & \boldconfinv{229.0}{15.0}{15.0} & \confinv{54.9}{7.9}{7.1}\\
-        R & no BH
-        kicks & \confinv{230.2}{15.2}{14.8} & \confinv{90.8}{9.8}{9.2} & \confinv{132.1}{11.1}{11.9} & \confinv{7.2}{2.2}{2.8} & \confinv{372.7}{19.7}{19.3} & \confinv{142.3}{12.3}{11.7} & \confinv{218.6}{14.6}{14.4} & \confinv{11.8}{3.8}{3.2}\\
-        S & $f_{\rm WR} = 0.1$ & \confinv{118.5}{10.5}{10.5} & \confinv{75.7}{8.7}{8.3} & \confinv{34.0}{6.0}{6.0} & \confinv{8.8}{2.8}{3.2} & \confinv{182.5}{13.5}{13.5} & \confinv{112.4}{10.4}{10.6} & \confinv{55.8}{7.8}{7.2} & \confinv{14.3}{4.3}{3.7}\\
-        T & $f_{\rm WR} = 5$ & \boldconfinv{29.7}{5.7}{5.3} & \boldconfinv{5.7}{2.7}{2.3} & \confinv{15.5}{3.5}{3.5} & \confinv{8.5}{2.5}{2.5} & \boldconfinv{48.8}{6.8}{7.2} & \boldconfinv{9.2}{3.2}{2.8} & \confinv{26.2}{5.2}{4.8} & \confinv{13.4}{3.4}{3.6}\\
+        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{9} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{14}{14} & \confinv{118}{11}{11} & \confinv{71}{8}{9} & \confinv{13}{4}{4}\\
+        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{8}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{13} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
+        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{10} & \confinv{76}{9}{9} & \confinv{14}{4}{3} & \confinv{6}{2}{3}\\
+        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{9} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
+        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \confinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \confinv{0}{0}{1}\\
+        F & Case BB Unstable + Optimistic CE & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{18}{4}{4} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
+        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \confinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \confinv{3}{1}{2} & \confinv{17}{4}{4}\\
+        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{9}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{11}{12} & \confinv{92}{10}{9} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
+        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{11}{12} & \confinv{68}{9}{8} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{14}{15} & \confinv{110}{11}{10} & \confinv{63}{8}{8} & \confinv{46}{7}{7}\\
+        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \confinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \confinv{57}{7}{8}\\
+        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{15} & \confinv{152}{13}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{341}{18}{19} & \confinv{230}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
+        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{12} & \confinv{50}{7}{7} & \confinv{70}{8}{9} & \confinv{7}{3}{2} & \confinv{205}{14}{14} & \confinv{77}{9}{8} & \confinv{117}{10}{11} & \confinv{11}{3}{3}\\
+        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{6} & \confinv{7}{2}{3} & \confinv{215}{14}{15} & \confinv{154}{13}{12} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
+        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{10}{11} & \confinv{58}{7}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{190}{14}{14} & \confinv{92}{10}{9} & \confinv{85}{9}{9} & \confinv{13}{3}{4}\\
+        O & No PISN and pulsational-PISN & \confinv{127}{12}{11} & \confinv{75}{8}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{206}{15}{14} & \confinv{121}{11}{10} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
+        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{185}{14}{13} & \confinv{83}{9}{9} & \confinv{87}{10}{9} & \confinv{15}{4}{4} & \confinv{301}{18}{17} & \confinv{130}{11}{12} & \confinv{145}{12}{12} & \confinv{26}{5}{5}\\
+        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \confinv{229}{15}{15} & \confinv{55}{8}{7}\\
+        R & Black holes receive not natal kick & \confinv{230}{15}{15} & \confinv{91}{10}{9} & \confinv{132}{11}{12} & \confinv{7}{2}{3} & \confinv{373}{20}{19} & \confinv{142}{12}{12} & \confinv{219}{15}{14} & \confinv{12}{4}{3}\\
+        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{10}{11} & \confinv{76}{9}{8} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{13}{14} & \confinv{112}{10}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\
         \hline 
-        - & Minimum rate & \confinv{29.7}{5.7}{5.3} & \confinv{5.7}{2.7}{2.3} & \confinv{2.1}{1.1}{1.9} & \confinv{0.2}{0.2}{0.8} & \confinv{48.8}{6.8}{7.2} & \confinv{9.2}{3.2}{2.8} & \confinv{3.5}{1.5}{1.5} & \confinv{0.4}{0.4}{0.6} \\
-        - & Maximum rate & \confinv{320.9}{17.9}{18.1} & \confinv{154.3}{12.3}{12.7} & \confinv{148.4}{12.4}{12.6} & \confinv{34.9}{5.9}{6.1} & \confinv{483.7}{21.7}{22.3} & \confinv{239.5}{15.5}{15.5} & \confinv{229.0}{15.0}{15.0} & \confinv{57.2}{7.2}{7.8} \\
+        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{0}{0}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{0}{0}{1} \\
+        - & Maximum rate & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{35}{6}{6} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{229}{15}{15} & \confinv{57}{7}{8} \\
         \hline

### 2021-11-19 paper/tex/sections/appendix.tex
Updates from Overleaf
WDWD changes in discussion

@@
 Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses (e.g.\ \citealt{Dominik+2015, Neijssel+2019}, Kummer et al.
-2021).
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.\ ][]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
 For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
@@
 
-% \subsection{Detection rate table}
-
 \begin{table*}[htb]
@@
         D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{9} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
-        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \confinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \confinv{0}{0}{1}\\
-        F & Case BB Unstable + Optimistic CE & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{18}{4}{4} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
-        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \confinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \confinv{3}{1}{2} & \confinv{17}{4}{4}\\
+        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \boldconfinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \boldconfinv{0}{0}{1} \\
+        F & Case BB Unstable + Optimistic CE & \boldconfinv{321}{18}{18} & \boldconfinv{154}{12}{13} & \boldconfinv{148}{12}{13} & \confinv{18}{4}{4} & \boldconfinv{484}{22}{22} & \boldconfinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
+        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \boldconfinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \boldconfinv{3}{1}{2} & \confinv{17}{4}{4}\\
         H & CE efficiency $\alpha = 0.5$ & \confinv{86}{9}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{11}{12} & \confinv{92}{10}{9} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
         I & CE efficiency $\alpha = 2.0$ & \confinv{133}{11}{12} & \confinv{68}{9}{8} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{14}{15} & \confinv{110}{11}{10} & \confinv{63}{8}{8} & \confinv{46}{7}{7}\\
-        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \confinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \confinv{57}{7}{8}\\
+        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \boldconfinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \boldconfinv{57}{7}{8}\\
         K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{15} & \confinv{152}{13}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{341}{18}{19} & \confinv{230}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
@@
         P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{185}{14}{13} & \confinv{83}{9}{9} & \confinv{87}{10}{9} & \confinv{15}{4}{4} & \confinv{301}{18}{17} & \confinv{130}{11}{12} & \confinv{145}{12}{12} & \confinv{26}{5}{5}\\
-        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \confinv{229}{15}{15} & \confinv{55}{8}{7}\\
+        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \boldconfinv{229}{15}{15} & \confinv{55}{8}{7}\\
         R & Black holes receive not natal kick & \confinv{230}{15}{15} & \confinv{91}{10}{9} & \confinv{132}{11}{12} & \confinv{7}{2}{3} & \confinv{373}{20}{19} & \confinv{142}{12}{12} & \confinv{219}{15}{14} & \confinv{12}{4}{3}\\
         S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{10}{11} & \confinv{76}{9}{8} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{13}{14} & \confinv{112}{10}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
-        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \boldconfinv{30}{6}{5} & \boldconfinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \boldconfinv{49}{7}{7} & \boldconfinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\
         \hline 

### 2021-11-19 paper/tex/sections/comparisons.tex
WDWD changes in discussion

@@
 This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
-We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \citep[see][ and also appendix~\ref{app:mw_changes} for further discussion]{Dominik+2015, Neijssel+2019}.
+We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \citep[see][ and also appendix~\ref{app:mw_changes} for further discussion]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
 Finally, it could be that different implicit assumptions in their population synthesis code lead to differences in our results \citep{Toonen+2014}.
@@
 \citet{Lau+2020} use a model for the Milky Way similar to that of \citet{Breivik+2020}, which we use to estimate the impact of the choice of MW model in Appendix~\ref{app:mw_changes}.
-We find that this simpler model for the Milky Way could result in an overestimation of the NSNS detection rate by at least a factor of two and so this may explain the discrepancy between our results.
-\citet{Lau+2020} additionally only uses a single metallicity rather than the two used in \citet{Breivik+2020} and so the overestimation could be even stronger as their results will have no contribution from lower metallicity systems.
+The Milky Way model by \cite{Breivik+2020} applies only two metallicity bins, while we consider a range of metallicities between $10^{-4}$ and $0.03$.
+When applying the simpler model for the Milky Way, we find that the NSNS detection rate is increased by at least a factor of two.
+\citet{Lau+2020} only uses a single metallicity, and so assuming that all star formation happens at a single high metallicity (which has a high efficiency of producing NSNS), could lead to an even greater overestimate of the detection rate.
+Hence, we expect the low number of metallicity bins in their Milky Way model to be the main driver behind the discrepancy between our results.
 

### 2021-11-19 paper/tex/sections/conclusion.tex
WDWD changes in discussion

@@
 %
-To determine the detectability of sources with LISA we use LEGWORK package (Wagg et al.\ in prep), that was specifically developed for this purpose and is publicly available. 
+To determine the detectability of sources with LISA we use the LEGWORK package (Wagg et al.\ in prep), that was specifically developed for this purpose and is publicly available. 
 %
@@
 
-%    Based on our fiducial model we estimate that, for a 4(10)-year LISA mission, at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs will produce signals that are distinguishable from a signal produced by a WDWD.
-%    Additionally, we predict that we will be able to determine whether \BHBHEitherBHOrNSFour{}(\BHBHEitherBHOrNSTen{}) BHBHs, \BHNSEitherBHOrNSFour{}(\BHNSEitherBHOrNSTen{}) BHNSs and \NSNSEitherBHOrNSFour{}(\NSNSEitherBHOrNSTen{}) NSNSs are signals from a binary that contains a black hole (see Sec.~\ref{sec:identify_sources}).
-The absolute number of systems that we can distinguish in different models changes, but the relative fraction remains roughly constant.
-
     \item \textbf{Prospects for finding EM counterparts:} We expect about 13\% of detections with a sky localisation better than 1 degree.

### 2021-11-19 paper/tex/sections/discussion.tex
WDWD changes in discussion

@@
 It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
-The population of Galactic WDWDs detectable with LISA will be several orders of magnitude larger than the population of the more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}.
+LISA can detect a variety of sources, from exoplanets \citep[e.g.][]{Tamanini+2019} to common-envelopes \citep[e.g.][]{Ginat+2020, Renzo+2021} that may cause confusion.
+However, by far the most prominent will be the population of Galactic WDWDs detectable with LISA, which will be several orders of magnitude larger than the population of the more massive DCOs that we focus on in this paper \citep[e.g.][]{Korol+2017}.
 It is therefore imperative that we consider how to distinguish NS and BH binaries from this much more numerous population of sources.
@@
 Another discriminator between WDWDs and other DCOs is eccentricity.
-WDWDs formed in the disc are thought to be formed through isolated binary formation and have little to no eccentricity \citep[e.g.][]{Nelemans+2001}.
+WDWDs formed in the disc are thought to be formed mainly through isolated binary formation and have little to no eccentricity (e.g.\ \citealt{Nelemans+2001}, see however \citealt{Dosopoulou+2016a, Dosopoulou+2016b, Gosnell+2019}).
+This is because WDWDs formed through isolated binary evolution all experience a phase of mass transfer or a common envelope, which circularises the binary \citep[e.g.][]{Marsh+2004}.
+However, in contrast to the more massive DCOs that we study, WDWDs do not experience strong natal kicks which we find to be the main source of eccentricity.
 Therefore, if any system is detected with anything other than one detectable harmonic, this suggests that the system is unlikely to be a WDWD.
@@
 Note that although the fractions are the same for the 10-year mission, the \textit{absolute} number of detections is still greater.
-%
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
@@
 This would require simulating the SKA population of pulsars with a code such as PSRPOPPy \citep{Bates+2014} to find the frequency and chirp mass distribution, which is beyond the scope of this paper.
-However, the uncertainty on the orbital frequency of a binary on the detection threshold (${\rm SNR} = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
+However, the uncertainty in the orbital frequency of a binary on the detection threshold (${\rm SNR} = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
 Therefore, we expect that SKA could likely isolate the correct binary pulsar to match to a LISA detection even when several are present in the sky localisation region.
@@
 \textit{Population synthesis limitations:} As with any study involving a rapid population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
-COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars.
+COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars \citep{COMPAS:2021methodsPaper}.
 Much of the underlying physics is uncertain, such as the common-envelope evolution and mass transfer physics.
@@
 \textit{Large progenitor masses:} Many of the black holes that are formed in our sample come from progenitors with large initial masses.
-The primary stars in systems that form BHNSs and BHBHs have very large primary progenitor masses that peak around 50\Msun and 80\Msun, but they extend well beyond that.
+The primary stars in systems that form BHNSs and BHBHs have very large primary progenitor masses that peak around 50\Msun and 80\Msun, but these masses extend up to 150\Msun.
 The evolution of such massive progenitor stars is very poorly understood and observational constraints are very scarce in this mass range and practically non-existent for the later rapid evolutionary phases.
-For these reasons, the COMPAS code relies heavily extrapolated on fitting formulae to create evolutionary tracks for these higher mass progenitors.
+For these reasons, the COMPAS code relies on heavily extrapolated fitting formulae to create evolutionary tracks for these higher mass progenitors.
 This leads to substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
@@
 Moreover, we assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results.
-We highlight this uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change drastically as our understanding shifts.
+We highlight this uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change as our understanding shifts.
 However, changes to this normalisation would affect every variation equally and so the trends across variations are more robust.

### 2021-11-19 paper/tex/sections/results.tex
WDWD changes in discussion

@@
 \subsection{How accurately will we be able to infer the parameters of detected systems?}\label{sec:measurement_uncertainties}
-So far we have discussed the properties of the detectable sources that can, in principle, be inferred from observations.
-However, many sources will only be barely detectable.
-Here we discuss for how many systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters.
+So far we have discussed the properties of the all detectable sources.
+However, only for a subset of systems we expect to get high enough SNR to obtain accurate and useful measurements of these parameters.
 Below we discuss the expected SNR distribution and the typical uncertainties expected for the most relevant parameters, namely, the chirp mass and sky localisation.

### 2021-11-19 paper/tex/sections/variations.tex
WDWD changes in discussion

@@
 In models \modAlphaLowest{}-\modAlphaHighest{} we alter the common-envelope efficiency parameter $\alpha_{\rm CE}$ to $0.1, 0.5, 2.0$ and $10.0$ respectively.
-Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta.
-Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion.
+Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta \citep[e.g.\ ][]{Ivanova+2013, Nandez+2016}.
+Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion \citep[e.g.\,][]{Schreier+2021}.
 The variations can also be seen as a way to cover uncertainties in estimates for the binding energy itself.
@@
 This has two consequences.
-(1) Firstly, a larger fraction of systems avoids merging during the CE phase.
+(1) A larger fraction of systems avoids merging during the CE phase.
 This increases the overall number of DCOs.
-(2) Secondly, the systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources.
+(2) The systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources \citep[e.g.\,][]{Klencki+2021}.
 So, while the first consequence favours the formation of DCOs, the second consequence disfavours the formation of DCOs that are tight enough to be detected.
@@
 These two opposing effect result in a fine tuning situation.
-Only a very small subset of progenitor systems that have the right orbital parameters prior to the CE phase to successfully produce detectable systems.
+Only a very small subset of progenitor systems have the right orbital parameters prior to the CE phase to successfully produce detectable systems.
 Changing $\alpha_{\rm CE}$ moves and changes this window in the parameter space that successfully leads to the formation of detectable systems.
@@
 
-In agreement with other studies, we find that this treatment leads to a large increase formation rate of BHBHs and with it the number of systems that LISA can detect.
-This is because BHBHs originate from the most massive progenitors, which expand significantly during the Hertzsprung gap phase in our simulations.
-The progenitors likely initiate interaction during this phase.
-Our predictions for the number of detectable systems increases by a factor 2.
-The less massive progenitors of BHNSs are less strongly affected, and for NSNS we do not see a significant increase.
+In agreement with other studies, we find that this treatment leads to a significant increase in the formation rate of BHBHs, by a factor of two.
+This is because the progenitors expand significantly during the Hertzsprung gap phase in our simulations.
+In our fiducial simulation, all progenitors that initiate unstable interaction during this phase would end as stellar mergers, while in this variation they will survive.
+The progenitors of BHNSs and NSNSs are less strongly affected with an increase about 30\% increase.
 
-\paragraph{Case BB mass transfer} For completeness and consistency with \citet{Broekgaarden+2021}, we have also included model variations that consider uncertainties in case BB mass transfer.
-This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Vigna-Gomez+2018}.
+\paragraph{Case BB mass transfer} In models \modCaseBB{} and \modCaseBBOpt{} we consider uncertainties in case BB mass transfer.
+This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Tauris+2015, Tauris+2017}.
 This is of particular interest for the formation of NSs, as their lower mass progenitors are swelling the most during this phase \citep[e.g.][and references therein]{Laplace+2020}.
-Population synthesis studies find that nearly all NSNS systems might from through a phase of case BB mass transfer \citep{Vigna-Gomez+2018}.
+Population synthesis studies find that nearly all NSNS systems form through a phase of case BB mass transfer \citep{Vigna-Gomez+2018}.
 
-In model \modCaseBB{} we effectively exclude any systems that evolve through case BB mass transfer.
-As expected, this kills nearly all NSNS systems.
+In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE.
+This effectively excludes any systems that evolve through case BB mass transfer since all common-envelopes initiated in this way have donors in the Hertzsprung gap and thus end as stellar mergers under the pessimistic CE assumption.
+Therefore, this kills nearly all NSNS systems.
 We also find a heavy reduction of the BHNS systems by a factor 6.
@@
 
-Finally, in model \modCaseBBOpt{}, we consider a situation where case BB mass transfer always leads to unstable mass transfer and initiates a CE phase in combination with the optimistic treatment for CE.
-This model leads to the highest predictions for the detections among all variations that we have considered.
+Finally, in model \modCaseBBOpt{}, we again enforce that case BB mass transfer is always unstable, but in combination with the optimistic treatment for CE (essentially combining models \modCaseBB{} and \modOpt{}).
+This allows the systems formed through case BB (as well as any other systems that have HG donors for common-envelopes) to survive the CE phase.
+We find that this model leads to the highest predictions for the detections among all variations that we have considered.
 
@@
 It affects by how much stars can grow in size and it affects the final core masses.
-\citet{Broekgaarden+2021} provides us with model variations that consider variations in the mass loss by naked helium (Wolf-Rayet like) stars.
+We consider variations in the mass loss by naked helium (Wolf-Rayet like) stars and choose to vary the efficiency of these winds between $0.1$ and $5$, to account for uncertainties in the derived rates \citep[e.g.][]{Vink+2017, Shenar+2019, Hamann+2019, Sander+2020}.
+
 We find that a reduction of the wind mass loss has very little effect on our predictions.
 This is the consequence of several effects that cancel each other.
-
 Firstly, the decreased Wolf-Rayet like winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA.
@@
 This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times.
-This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.
+This means that most DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable.
 
@@
 In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5.
-We note that though there is currently no observational support for such a strong increase in the stellar winds of Wolf-Rayet stars, it is nevertheless still interesting to consider.
 In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged.
-Increasing the efficiency of WR winds strongly decreases the final masses of DCOs.
-This means that many progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH (therefore this effect is stronger on BHBHs than NSNSs).
+Increasing the efficiency of WR winds widens the orbit and decreases the final masses of DCOs.
+This means that some progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH.
+The effect is strongest for the progenitors of black holes, since these are most strongly affected by Wolf-Rayet winds.
+This effect is less pronounced in NSs since the rate of mass loss for the progenitors of these systems is low enough that changing by a factor of 5 still does not impact the final fate.
 Moreover, DCOs that are formed tend to be less massive and therefore less detectable.
@@
 From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.
-%
+
 However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them.
@@
 In Fig.~\ref{fig:wr_wind_mass_variations} we show the effect that changing the efficiency of Wolf-Rayet winds has on the individual component mass distribution.
-Decreasing the Wolf-Rayet wind efficiency allows the formation of more massive DCOs in the Milky Way and, indeed, we see that the distribution extends to $25 \unit{M_{\odot}}$ and fewer detectable systems are formed at low masses.
+Decreasing the Wolf-Rayet wind efficiency allows the formation of more massive DCOs in the Milky Way and, indeed, we see that the distribution extends to $25 \unit{M_{\odot}}$ and relatively fewer detectable systems are formed at low masses.
 By contrast, increasing the Wolf-Rayet efficiency by a factor of 5 strongly disfavours the formation of systems at high masses and approximately 85\% of detectable systems have masses below $5 \unit{M_{\odot}}$.

### 2021-11-19 paper/tex/sections/comparisons.tex
Change Figure->Fig.

@@
 
-In Figure~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar-mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
-Figure~\ref{fig:previous_studies} details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
+In Fig.~\ref{fig:previous_studies}, we compare our results to similar previous studies that investigate the population of stellar-mass BHBHs, BHNSs and NSNSs that are detectable with LISA.
+Fig.~\ref{fig:previous_studies} details the expected detection rates predicted by each paper as well as their assumptions regarding their Milky Way galaxy model, binary population synthesis simulation and LISA mission specifications.
 We only include papers that are similar to our work, such that they use population synthesis and simulate sources in the Galactic plane.
-Moreover, Figure~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
+Moreover, Fig.~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
 

### 2021-11-19 paper/tex/sections/results.tex
Change Figure->Fig.

@@
 \subsection{Properties of the detectable systems}\label{sec:fiducial_distributions}
-In Figure~\ref{fig:fiducial_pdf_distributions}, we show the 1D distribution of several individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties obtained via bootstrapping.
+In Fig.~\ref{fig:fiducial_pdf_distributions}, we show the 1D distribution of several individual parameters of the population of detectable binaries together with the 1- and 2-$\sigma$ uncertainties obtained via bootstrapping.
 These uncertainties represent the fluctuations in our results over different random instances of the Milky Way.
@@
 There are two main reasons for this discrepancy.
-First, the population of BHs in the Milky Way (and, in particular, those detectable by LISA due to their recent formation times, see Figure~\ref{fig:fiducial_pdf_distributions}e) primarily come from progenitors that formed from high metallicity gas according to our simulations.
+First, the population of BHs in the Milky Way (and, in particular, those detectable by LISA due to their recent formation times, see Fig.~\ref{fig:fiducial_pdf_distributions}e) primarily come from progenitors that formed from high metallicity gas according to our simulations.
 Stellar winds are stronger at high metallicity leading to increased mass loss.
@@
 The large cross passes through (0, 0) and helps to highlight the bias towards the position of the sun, which is indicated by the $\odot$.
-    \textbf{Bottom:} As Figure~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
+    \textbf{Bottom:} As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the luminosity distance.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_1_galaxy_density_distribution.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig4_2_detectable_distance_distribution_4yr.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}

### 2021-11-19 paper/tex/sections/variations.tex
Change Figure->Fig.

@@
 \subsection{Detection rates}\label{sec:detection_rate_analysis}
-In Figure~\ref{fig:detection_rates}, we show the expected number of LISA detections based on our simulations considering variations in the physical assumptions.
+In Fig.~\ref{fig:detection_rates}, we show the expected number of LISA detections based on our simulations considering variations in the physical assumptions.
 We show the expected number of detections for BHBH, BHNS and NSNS systems in the top, middle and bottom panel respectively.
@@
 
-In Figure~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions.
+In Fig.~\ref{fig:lower_mass_gap_variation}, we show the component mass distribution for all LISA detectable DCOs (BHBHs, BHNSs and NSNSs) for two different remnant mass prescriptions.
 The grey distribution uses the Fryer \textit{delayed} remnant mass prescription \citep{Fryer+2012}, which is our fiducial assumption (model \modFid{}).
@@
 
-In Figure~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs.
+In Fig.~\ref{fig:ecc_low_kick_variation}, we investigate how decreasing the magnitude of natal kicks from core-collapse supernovae affects the eccentricity distribution of LISA detectable DCOs.
 For reference, we show the mean fiducial distributions (model \modFid{}) as dashed lines (see Fig.~\ref{fig:fiducial_pdf_distributions}d for full comparison).

### 2021-11-19 paper/tex/sections/conclusion.tex
add legwork citations

@@
 %
-To determine the detectability of sources with LISA we use the LEGWORK package (Wagg et al.\ in prep), that was specifically developed for this purpose and is publicly available. 
+To determine the detectability of sources with LISA we use the LEGWORK package \citep{Wagg+2021}, that was specifically developed for this purpose and is publicly available. 
 %

### 2021-11-19 paper/tex/sections/introduction.tex
add legwork citations

@@
 In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
-In a companion paper, Wagg et al.
-2021b (in preparation), we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+In a companion paper, \citet{Wagg+2021}, we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 

### 2021-11-19 paper/tex/sections/methods.tex
Change Figure->Fig.
add legwork citations

@@
 for $j = 1, 2, \dots, N_{\rm MW}$, where we set $N_{\rm MW} = 2 \times 10^{5}$, $\tau, R, Z$ and $z$ are defined and sampled using the distribution functions specified in Section~\ref{sec:mw_model}, $\theta$ is the azimuthal angle sampled uniformly on $[0, 2\pi)$ and $Z$ is the metallicity.
-Figure~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
+Fig.~\ref{fig:galaxy_schematic} shows an example of a random Milky Way instance created with these distributions.
 This shows how these distributions translate to positions and illustrates the gradient in metallicity over radius.
@@
 \subsection{Gravitational wave detection}\label{sec:gw_detection}
-We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to evolve binaries and calculate their LISA detectability.
-For a full derivation of the equations given below please see the LEGWORK release paper, Wagg et al.
-2021b (in preparation), or the documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
+We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{Wagg+2021} to evolve binaries and calculate their LISA detectability.
+For a full derivation of the equations given below see \citep[][Sec.~3]{Wagg+2021}, or the LEGWORK documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
 

### 2021-11-23 simulation/src/simulate_DCO_detections.py
first try at adding the new mask to simulation

@@ -25,16 +25,17 @@ def usage():
                                                                                 ansi_codes["reset"]))
     print()
     print("{}options:{}".format(ansi_codes["red"], ansi_codes["reset"]))
-    print("      Option names      :                       Description                        : Default value")
-    print("------------------------:----------------------------------------------------------:--------------")
-    print("  -h, --help            : print usage instructions                                 : -")
-    print("  -i, --input           : path to COMPAS h5 input file                             : 'COMPASOutput.h5'")
-    print("  -o, --output          : path to output h5 file                                   : 'COMPASOutput_testing.h5'")
-    print("  -n, --loops           : number of simulations to run                             : 10")
-    print("  -t, --binary-type     : which binary type to simulation ['BHBH', 'BHNS', 'NSNS'] : 'BHNS'")
-    print("  -f, --opt-flag        : whether to use the optimistic CE scenario                : -")
-    print("  -s, --simple-mw       : whether to use the simple MW model                       : -")
-    print("  -e, --extended-mission: whether to assume an extended (10 yr) LISA mission       : -")
+    print("      Option names      :                                     Description                                     :       Default value      ")
+    print("------------------------:-------------------------------------------------------------------------------------:--------------------------")
+    print("  -h, --help            : print usage instructions                                                            : -")
+    print("  -i, --input           : path to COMPAS h5 input file                                                        : 'COMPASOutput.h5'")
+    print("  -o, --output          : path to output h5 file                                                              : 'COMPASOutput_testing.h5'")
+    print("  -n, --loops           : number of simulations to run                                                        : 10")
+    print("  -t, --binary-type     : which binary type to simulation ['BHBH', 'BHNS', 'NSNS']                            : 'BHNS'")
+    print("  -f, --opt-flag        : whether to use the optimistic CE scenario                                           : -")
+    print("  -s, --simple-mw       : whether to use the simple MW model                                                  : -")
+    print("  -e, --extended-mission: whether to assume an extended (10 yr) LISA mission                                  : -")
+    print("  -b, --case-bb-survive : whether to allow case BB systems to survive CE whilst using pessimistic CE scenario : -")
     print()
 
 #####################################################################
[…]

### 2021-11-23 simulation/src/simulate_DCO_detections.py
fix conditions

@@ -90,9 +90,12 @@ def main():
         if option in ("-b", "--case-bb-survive"):
             allow_caseBB_survive = True
 
-    # switch to optimistic is letting case BB to survive so we can mask them away again
-    if allow_caseBB_survive and pessimistic:
-        pessimistic = False
+    if not pessimistic:
+        # no need to do case BB stuff if already optimistic
+        allow_caseBB_survive = False
+    else:
+        # force optimistic if letting case BB to survive so we can mask them away again
+        pessimistic = False if allow_caseBB_survive else True
 
     # open COMPAS file
     with h5.File(input_filepath, "r") as COMPAS_file:
@@ -125,7 +128,7 @@ def main():
                              [compas_Z_unique[-1]]))
 
     # allow case BB systems to survive the CE even when pessimistic
-    if allow_caseBB_survive and pessimistic:
+    if allow_caseBB_survive:
         ce_seeds, ce_Z, ce_st1, ce_st2 = get_COMPAS_vars(COMPAS_file,
                                                          "commonEnvelopes",
                                                          ["randomSeed", "Metallicity1",

### 2021-11-23 simulation/src/simulate_DCO_detections.py
second try at masking just HG!

@@ -45,14 +45,14 @@ def main():
     # get command line arguments and exit if error
     try:
         opts, _ = getopt.getopt(sys.argv[1:], "hi:o:n:t:fseb", ["help",
-                                                             "input=",
-                                                             "output=",
-                                                             "loops=",
-                                                             "binary-type=",
-                                                             "opt-flag",
-                                                             "simple-mw",
-                                                             "extended-mission",
-                                                             "case-bb-survive"])
+                                                                "input=",
+                                                                "output=",
+                                                                "loops=",
+                                                                "binary-type=",
+                                                                "opt-flag",
+                                                                "simple-mw",
+                                                                "extended-mission",
+                                                                "case-bb-survive"])
     except getopt.GetoptError as err:
         print(err)
         usage()
@@ -129,29 +129,37 @@ def main():
 
     # allow case BB systems to survive the CE even when pessimistic
     if allow_caseBB_survive:
-        ce_seeds, ce_Z, ce_st1, ce_st2 = get_COMPAS_vars(COMPAS_file,
-                                                         "commonEnvelopes",
-                                                         ["randomSeed", "Metallicity1",
-                                                          "stellarType1", "StellarType2"])
+
+        # start a mask of which binaries to throw away
+        exclude = np.repeat(False, compas_seeds.shape)
 
         # do it separately by metallicity to ensure seeds are unique
         for Z in compas_Z_unique:
-            ce_matching_Z = ce_Z == Z
-            dco_matching_Z = compas_Z == Z
+            # WARNING: I have hardcoded the use of the unstable case BB file here
+            # this will produce (possibly silent) errors if other models are use
+            ce_path = "/n/holystore01/LABS/berger_lab/Lab/fbroekgaarden/DATA/all_dco_legacy_CEbug_fix/"
+            ce_path += "unstableCaseBB/Z_{}/STROOPWAFELcombined/COMPASOutput.h5".format(Z)
+
+            # grab the CE file data for this metallicity bin
+            with h5.File(ce_path, "r") as ce_file:
[…]

### 2021-11-23 simulation/src/simulate_DCO_detections.py
error maybe because of metallicities?

@@ -120,12 +120,8 @@ def main():
         compas_a_DCO *= u.AU
         compas_t_evol *= u.Myr
 
-    # work out metallicity bins
+    # find unique metallicities
     compas_Z_unique = np.unique(compas_Z)
-    inner_bins = np.array([compas_Z_unique[i] + (compas_Z_unique[i+1] - compas_Z_unique[i]) / 2
-                           for i in range(len(compas_Z_unique) - 1)])
-    Z_bins = np.concatenate(([compas_Z_unique[0]], inner_bins,
-                             [compas_Z_unique[-1]]))
 
     # allow case BB systems to survive the CE even when pessimistic
     if allow_caseBB_survive:
@@ -160,6 +156,13 @@ def main():
             compas_t_evol, compas_weights, compas_seeds = compas_m_1[exclude], compas_m_2[exclude],\
             compas_Z[exclude], compas_a_DCO[exclude], compas_e_DCO[exclude], compas_t_evol[exclude],\
             compas_weights[exclude], compas_seeds[exclude]
+
+    # work out metallicity bins
+    compas_Z_unique = np.unique(compas_Z)
+    inner_bins = np.array([compas_Z_unique[i] + (compas_Z_unique[i+1] - compas_Z_unique[i]) / 2
+                           for i in range(len(compas_Z_unique) - 1)])
+    Z_bins = np.concatenate(([compas_Z_unique[0]], inner_bins,
+                             [compas_Z_unique[-1]]))
 
     # create a random number generator
     rng = np.random.default_rng()

### 2021-11-23 simulation/src/variations.py
revert variation labels

@@ -38,14 +38,14 @@ variations = np.array(
         {
             "file": "unstableCaseBB",
             "short": "E",
-            "med": "No Case BB",
-            "long": "Case BB mass transfer systems are removed",
+            "med": "Case BB\nunstable",
+            "long": "Case BB mass transfer is always unstable",
             "colour": plt.get_cmap("tab20")(3)
         },
         {
             "file": "unstableCaseBB_opt",
             "short": "F",
-            "med": "Case BB\nUnstable + K",
+            "med": "E + K",
             "long": "Case BB Unstable + Optimistic CE",
             "colour": plt.get_cmap("tab20")(2)
         },

### 2021-11-23 simulation/src/variations.py
make model E actually E prime

@@ -37,7 +37,7 @@ variations = np.array(
         },
         {
             "file": "unstableCaseBB",
-            "short": "E",
+            "short": "E'",
             "med": "Case BB\nunstable",
             "long": "Case BB mass transfer is always unstable",
             "colour": plt.get_cmap("tab20")(3)

### 2021-11-23 paper/tex/sections/results.tex
update all of the figure names

@@
     \centering
-    \includegraphics[width=\columnwidth]{fig6_snr_cumulative_all.pdf}
+    \includegraphics[width=\columnwidth]{fig5_snr_cumulative_all.pdf}
     \caption{Cumulative number of LISA detections with a given signal-to-noise ratio.
 Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig5_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:snr_dist}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig7_chirp_mass_uncertainty_all.pdf}
+    \includegraphics[width=\columnwidth]{fig6_chirp_mass_uncertainty_all.pdf}
     \caption{As Fig.~\ref{fig:snr_dist}, but for the chirp mass uncertainty.
 The shaded areas indicate regions with more than 10\% and 100\% uncertainty.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_chirp_mass_uncertainty_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:m_c_unc}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig8_angular_resolution_all.pdf}
+    \includegraphics[width=\columnwidth]{fig7_angular_resolution_all.pdf}
     \caption{As Fig.~\ref{fig:snr_dist}, but for the angular resolution.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig7_angular_resolution_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:ang_res}

### 2021-11-23 paper/tex/sections/variations.tex
update all of the figure names

@@
     \centering
-    \includegraphics[width=\textwidth]{fig9_dco_detections.pdf}
+    \includegraphics[width=\textwidth]{fig8_dco_detections.pdf}
     \caption{The number of expected detections in the LISA mission for different DCO types and model variations.
@@
 See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig8_dco_detections.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/detections.ipynb}{\faBook}.}
     \label{fig:detection_rates}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig10_lower_mass_gap_rapid_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig9_lower_mass_gap_rapid_variation.pdf}
     \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
 Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig9_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:lower_mass_gap_variation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig11_ecc_low_kick_variation.pdf}
+    \includegraphics[width=\columnwidth]{fig10_ecc_low_kick_variation.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}d, but for model \modSigLower{}.
 For comparison, we show the mean distribution for the fiducial model (model \modFid{}) as dashed lines.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_ecc_low_kick_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:ecc_low_kick_variation}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig12_wr_wind_mass_variations.pdf}
+    \includegraphics[width=\columnwidth]{fig11_wr_wind_mass_variations.pdf}
     \caption{As Fig.~\ref{fig:lower_mass_gap_variation}, but instead varying Wolf-Rayet wind efficiency (models \modWRLow{} and \modWRHigh{}).
 The curve for $f_{\rm WR} = 5$ has much higher uncertainties as there are many fewer DCO systems formed in this model (the inverse reasoning also explains the lower uncertainties for $f_{\rm WR} = 0.1$).
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig11_wr_wind_mass_variations.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
     \label{fig:wr_wind_mass_variations}

### 2021-11-23 paper/tex/paper.tex
Updates from Overleaf

@@
 
+\newcommand{\citefloorp}{(\citealt{Broekgaarden+2021}, Broekgaarden et al.\ (in prep.))}
+
 \newcommand{\confinv}[3]{$#1${\raisebox{0.5ex}{\tiny$_{-#2}^{+#3}$}}}
@@
 
-\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios, it is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
+\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios \citep{Wagg+2021}.
+It is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
 Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}.

### 2021-11-23 paper/tex/sections/discussion.tex
Updates from Overleaf

@@
 In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}).
+All statistics quoted in each subsection are for the fiducial (model \modFid{}) model.
+However, we find that the \textit{fraction} of systems for each statistic are robust over different model variations (though the total numbers for each statistic change over our model variations due to the different detection rates).
 
@@
 WDWDs formed in the disc are thought to be formed mainly through isolated binary formation and have little to no eccentricity (e.g.\ \citealt{Nelemans+2001}, see however \citealt{Dosopoulou+2016a, Dosopoulou+2016b, Gosnell+2019}).
-This is because WDWDs formed through isolated binary evolution all experience a phase of mass transfer or a common envelope, which circularises the binary \citep[e.g.][]{Marsh+2004}.
+This is because WDWDs formed through isolated binary evolution all experience a phase of mass transfer or a common envelope, which typically circularises the binary \citep[e.g.][]{Marsh+2004}.
 However, in contrast to the more massive DCOs that we study, WDWDs do not experience strong natal kicks which we find to be the main source of eccentricity.
@@
 
-However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}.
+However, we should also consider that eccentric WDWDs could be formed through dynamical formation in Milky Way globular clusters \citep[e.g.][]{Willems+2007, Kremer+2018}, or with third companions \citep[e.g.][]{Antonini+2017}.
 This means that we cannot assume that eccentric binaries are not WDWDs unless they are detected in the Galactic plane (though even then there is a chance they were formed dynamically).
@@
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
+Thus we will be able to confidently discuss approximately half of all detected sources from WDWDs.
+This increases to roughly 60\% for a 10-year mission.
 
-We highlight here that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by a greater factor since each of the more numerous sources are better measured.
+We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by a greater factor since each of the more numerous sources are better measured.
 This further underlines the benefits of extending the LISA mission to 10 years.
@@
 
-\textit{Population synthesis limitations:} As with any study involving a rapid population synthesis code, our results rely on uncertain stellar and binary physics and the use of approximate fitting formulae.
-COMPAS uses fitting formulae and approximate prescriptions based on (sometimes limited) grids of detailed models to describe the evolution of binary stars \citep{COMPAS:2021methodsPaper}.
-Much of the underlying physics is uncertain, such as the common-envelope evolution and mass transfer physics.
-We attempt to understand the importance of some these assumptions by varying over many different physics assumptions.
+Our predictions are subject to various uncertainties which can be broadly divided into different categories: (a) those arising from the progenitor models for the population of DCOs and (b) those arising from the choices we have made when placing these DCOs in our model for the Milky-Way.
+Furthermore, (c) there may be contributions from other formation channels that we have not considered here.
+Although we are unable, at present, to evaluate the impact of all these uncertainties, the reader should nevertheless keep in mind that they are likely very substantial.
+Most of these concerns are not unique to these study, but apply to most of the predictions available in present literature.
+We highlight a few main concerns.
 
-\textit{Large progenitor masses:} Many of the black holes that are formed in our sample come from progenitors with large initial masses.
-The primary stars in systems that form BHNSs and BHBHs have very large primary progenitor masses that peak around 50\Msun and 80\Msun, but these masses extend up to 150\Msun.
-The evolution of such massive progenitor stars is very poorly understood and observational constraints are very scarce in this mass range and practically non-existent for the later rapid evolutionary phases.
-For these reasons, the COMPAS code relies on heavily extrapolated fitting formulae to create evolutionary tracks for these higher mass progenitors.
-This leads to substantial uncertainties in our final predictions which are unfortunately still hard to quantify at present.
+\paragraph{Progenitor models (a)} Our binary-star progenitors models have been computed with a rapid population synthesis code (see Sec.~\ref{sec:COMPAS_explained}).
+This code relies on approximate parametric prescriptions for the stellar evolutionary tracks of single tracks and simple algorithms to mimic the effects of evolutionary and binary interaction  processes.
+Even though we explicitly consider the impact of some of the main physics uncertainties (see Sect.~\ref{sec:variation_assumptions}) the list of variations that we considered is far from exhaustive.
+Moreover, it is by no means guaranteed that the parametric prescriptions used in this code lead to realistic results, even when varying the values of the parameters to their extremes.
+We stress in particular the uncertainties affecting our most massive progenitor models.
+Observational constraints are scarce for high mass stars and practically non-existent for the rapid evolutionary phases \citep[e.g.\ ][]{Langer2012, Mapelli+2021}.
+This is even more true for the evolution of massive stars at low metallicity.
+In addition to our limited understanding of massive stars, we note that the rapid population synthesis code, such as the one employed to compute the models used in this study, rely on extrapolations of the original fitting formulae to approximate the evolutionary tracks for these higher mass progenitors \citep{Hurley+2000,Hurley+2002}.
 
-\textit{Underlying helium star models:} One source of weakness is that the \citet{Hurley+2000} fitting formulae (used by COMPAS) for the evolution of helium stars are based on a grid of models from $0.3 \unit{M_{\odot}}$ to $10 \unit{M_{\odot}}$, for a single metallicity ($Z= 0.02$) and thus the formulae have no metallicity dependence and are extrapolated for higher masses.
-A more comprehensive set of models in this regime could lead to large changes in the evolution of naked helium stars, a common progenitor of DCOs, and thus affect the detection rate of DCOs.
+\paragraph{Populating the Milky Way (b)} Our Milky Way model is semi-empirical and has been calibrated based on observations.
+Unfortunately, the early evolution of the (metallicity dependence of the) star formation history is poorly constrained.
+We do not expect this to be a major concern, as most of the double compact objects have relatively short delay times of less than 2\,Gyr (see Fig.~\ref{fig:fiducial_pdf_distributions}e), but this is a caveat that should be kept in mind.
+Furthermore, to estimate the rate of detectable systems, we rely on normalisation choices (e.g.\ how many detectable double compacts are formed per unit of star formation).
+This depends heavily on the initial mass function, as low mass stars account for most of the mass while high mass stars are the progenitors of double compact objects.
+Further choices, such as the binary fraction and the initial distributions of binary parameters also play a lesser but probably still significant role \citet[e.g.\ ][]{deMink+2015, Chruslinska+2017, Klencki+2018}.
 
-\textit{Limited metallicity range:} The stellar evolution fitting formulae that COMPAS uses is limited to a metallicity range of $10^{-4} \le Z \le 0.03$ \citep{Hurley+2000} and should not be extrapolated too far outside this range.
-However, in our simulated Milky Way (based on the metallicity relation in \citealt{Frankel+2018}), the metallicity distribution can extend as far as $10^{-5} \le Z \le 0.06$, with a significant fraction of star formation occurring past $Z = 0.03$.
+We also note that, for reasons of computational efficiency, we have not accounted for the spatial velocities resulting from the Blaauw-Boersma kick \citep{Blaauw+1961,Boersma1961}.
+In test simulations we find that accounting for this spreads out the population (increasing the typical height above the Galactic plane and Galactocentric radius), but we find that the impact on the rate is limited.
+In light of the other much larger uncertainties, we felt that this was justified (see however, e.g., \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
+We have further ignored a possible contribution coming from the Galactic halo, as  \citet{Lamberts+2018} estimates this not be significant.
+However, this may not be true for other formation channels other than those we have considered here.
 
-For metallicities below the range allowed by COMPAS, we assume that binaries evolve similar to our lowest metallicity models.
-DCO formation at metallicities above $Z = 0.03$ is significantly less efficient for increasing metallicity.
-And so, higher metallicities are unlikely to contribute significantly.
-Therefore, we place any sampled metallicity above the maximum of $Z = 0.03$ uniformly randomly in one of the top 5 highest metallicity bins that range across $0.01416 < Z < 0.03$ (since using a single metallicity for many binaries leads to unphysical artifacts).
-
-\textit{Normalisation choices}: The choice of the binary fraction has a strong effect on our results.
-For the normalisation of the detection rate we conservatively choose to set the binary fraction of all stars to 50\%.
-The binary fraction is uncertain and not well constrained, though we know it is higher for more massive stars \citep[e.g.][]{Sana+2012}.
-Increasing it to 70\% and 100\% would increase our expected detection rates for every physics variation by 30\% and 67\% respectively.
-Moreover, we assume that the mass ratio of secondary stars is uniformly distributed and this could also have strong effect on our results.
-We highlight this uncertainty in the normalisation to point out that the exact magnitude of the rates in each case could change as our understanding shifts.
-However, changes to this normalisation would affect every variation equally and so the trends across variations are more robust.
-
-\textit{Systemic kicks:} We do not include the effect of systemic kicks on the final location of the sources.
-This would require integrating the orbital evolution of the millions of binaries in our sample and thus was not computationally reasonable to include.
-We investigated the effect of kicks for a small grid of binaries and found that, though they would result in a more spread out distribution (with a smaller concentration in the Galactic centre) and larger heights above the plane, the overall distribution of positions would be relatively unchanged and very few sources have strong enough kicks to reach escape velocity for the Milky Way.
-
-\textit{Eccentricity measurement uncertainty:} The method that we use to determine the eccentricity uncertainty is pessimistic as it requires each harmonic to be individually detectable \citep[e.g.][]{Lau+2020}.
-In reality this may not be necessary depending on the efficacy of matched-filter analysis of LISA data.
-For an eccentric source to have been detected within the LISA data, several harmonics would already have to have been matched as originating from the same source.
-This could be done by looking in the same region of the sky for signals with similar chirp masses and distances to the most detectable harmonic in order to find other harmonics that are below the regular detection threshold.
-This would allow one to refine the measurement of the eccentricity uncertainty significantly by comparing the many different harmonics.
-Therefore, the eccentricity uncertainty that we calculate in this study is a pessimistic estimate.
-Smaller eccentricity uncertainties would have two main effects on our results.
-Firstly, the chirp mass error would decrease slightly in the cases where it is dominated by the eccentricity uncertainty.
-However, it is mainly dominated by the frequency derivative uncertainty since most sources are essentially stationary in frequency.
-Secondly, it would improve our ability to distinguish between WDWDs and higher mass DCOs.
-Until we know more about how LISA will search for eccentric sources, we rely upon our pessimistic estimates.
-
-\textit{Other formation channels, the Halo, globular clusters and young stellar clusters:} Our model for the Milky Way, though more extensive than many previous studies, does not consider the contributions from the Galactic halo, globular clusters or young massive and open stellar clusters.
-\citet{Lamberts+2018} found that the halo's contribution to the detection rate was minimal and, since the metallicity distribution of the halo is uncertain, we did not include it in our galaxy model.
-The impact of globular clusters would have required a more detailed look into dynamical formation that was beyond the scope of this paper but we highlight the work of \citet{Kremer+2018} that investigated these rates.
-Similarly, we did not consider DCO formation in young massive and open stellar clusters but \citet{Banerjee+2020} finds that the LISA detection rates could be even higher than contributions from isolated binary formation.
+\paragraph{Other formation channels (c)} In this work we considered the formation of double compact objects through the isolated binary formation channel.
+We have not included the possible contributions from other channels such as dynamical formation in dense star clusters, formation in young star clusters and triple systems in the field.
+We refer to \citet{Kremer+2018} and \citet{Banerjee+2020} for a studies of the contribution of dynamical formation in globular and young stellar clusters.

### 2021-11-23 paper/tex/sections/results.tex
Updates from Overleaf

--- 2021-11-19 paper/tex/sections/results.tex
@@
 \end{figure*}
-We show the expected LISA sensitivity curve \citep{Robson+2019} in Fig.~\ref{fig:dcos_on_sc} and overplot our predictions for the distribution of detectable sources.
+We show the expected LISA sensitivity curve \citep{Robson+2019} in Fig.~\ref{fig:dcos_on_sc}, which includes the confusion noise arising from the Galactic WDWD population, and overplot our predictions for the distribution of detectable sources.
 Eccentric systems emit gravitational waves in multiple harmonic frequencies ($n f_{\rm orb}$, with $n = 2, 3, \dots $).
-We choose to plot them at the $x$-coordinate that corresponds to the frequency of the harmonic that dominates the SNR.
+We choose to plot them at the $x$-coordinate that corresponds to the frequency of the harmonic that individually accumulates the largest SNR.
 For circular systems, the $x$-coordinate simply corresponds to $2 f_{\rm orb}$.
@@
 Each panel shows a kernel density estimator for a single property, coloured by DCO type.
-The shaded areas show the 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
+Each curve has been individually normalised.
+The shaded areas show the 1- and 2-$\sigma$ sampling uncertainties (obtained via bootstrapping).
 The dotted lines in panel b show the individual primary and secondary mass distributions.
@@
     \caption{Cumulative number of LISA detections with a given signal-to-noise ratio.
-Colours indicate LISA mission length and shading shows 1- and 2-$\sigma$ uncertainties (obtained via bootstrapping).
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+Colours indicate LISA mission length.
+The shading shows 1- and 2-$\sigma$ uncertainties on the model's expectation value for the number of detections (i.e., not including the Poisson noise arising from the distribution of a finite number of DCOs in the Galaxy) \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig6_snr_cumulative_all.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:snr_dist}

### 2021-11-23 paper/tex/sections/variations.tex
Updates from Overleaf

--- 2021-11-19 paper/tex/sections/variations.tex
@@
 Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope.
-There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations \citep[e.g.\ ][]{DeMarco+2011, Fragos+2019, Law-Smith+2020}, but no consistent picture has emerged.
+There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations \citep[e.g.\ ][]{DeMarco+2011, Law-Smith+2020, Lau+2021}, but no consistent picture has emerged.
 Therefore we consider large variations in this parameter.
@@
     \caption{Comparison of the component mass distribution of LISA detectable DCOs when using the Fryer delayed (model \modFid{}) and rapid (model \modRapid{}) remnant mass prescriptions.
-Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCOs types are shown in one curve and each type is weighted by its detection rate in the respective model.
+Distributions are plotted in the same way as Fig.~\ref{fig:fiducial_pdf_distributions}, except all DCO types are combined into one curve, with the contribution from each type weighted by the total detection rate of that DCO type in the respective model.
+Each model's curve is individually normalised.
 \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig10_lower_mass_gap_rapid_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/variations.ipynb}{\faBook}.}
@@
 This prescription produces compact objects in the lower mass gap ($2.5 \unit{M_{\odot}} \le m \le 5 \unit{M_{\odot}}$) and indeed we find that, of the LISA detectable DCOs, approximately \BHBHatLeastOneLowerMassGapPerc{}\% of BHBHs, \BHNSatLeastOneLowerMassGapPerc{}\% of BHNSs and \NSNSatLeastOneLowerMassGapPerc{}\% of NSNSs have at least one component in the lower mass gap.
-Overall, weighting by the relative detection rates, this gives that 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription.
-
+Overall, weighting by the relative detection rates, this gives that, in our fiducial model, 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription.
+This equates to approximately 68 systems being detected in the lower mass gap.
 Alternatively, the blue curve in Fig.~\ref{fig:lower_mass_gap_variation} shows the same distribution but for the \textit{rapid} remnant mass prescription \citep{Fryer+2012}, which we use in model \modRapid{}.
 In this case, no compact objects are formed (and therefore, detected) in the lower mass gap.
+
 From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.
-
+Indeed, we find that the percentage of detectable systems with at least one component in the lower mass gap varies between approximately 30-70\% (or, in terms of detections, from 15 to 156) for the different model variations.
 However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them.
-And thus, LISA could be a useful instrument for providing evidence for the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.
+And thus, LISA could be a useful instrument for providing constraints on the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.
 
@@
 
-Overall, we find that decreasing supernova natal kicks, though it strongly increases the number of detections (see Fig.~\ref{fig:detection_rates}), strongly \textit{decreases} the fraction of highly eccentric systems that are detected.
+Overall, compared to our fiducial model, we find that decreasing supernova natal kicks, though it strongly increases the number of detections (see Fig.~\ref{fig:detection_rates}), strongly \textit{decreases} the fraction of highly eccentric systems that are detected.
 

### 2021-11-23 paper/tex/sections/appendix.tex

@@
     \centering
-    \includegraphics[width=\columnwidth]{fig14_random_simple_galaxy.png}
+    \includegraphics[width=\columnwidth]{figD1_random_simple_galaxy.png}
     \caption{As Fig.~\ref{fig:galaxy_schematic} (right panel), but for the Milky Way model used in \citet{Breivik+2020}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig14_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figD1_random_simple_galaxy.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
     \label{fig:simple_mw}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig15_mBH_simple_mw_variation.pdf}
+    \includegraphics[width=\columnwidth]{figD2_mBH_simple_mw_variation.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}b, but for the Milky Way model used in \citet{Breivik+2020}.
 Dotted lines show the distribution from Fig.~\ref{fig:fiducial_pdf_distributions}b for comparison.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig15_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figD2_mBH_simple_mw_variation.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:bh_mass_simple_mw}
@@
     \centering
-    \includegraphics[height=0.85\textheight]{fig16_formation_channels.pdf}
+    \includegraphics[height=0.85\textheight]{figF1_formation_channels.pdf}
     \caption{Fraction of each DCO type that is formed through different formation channels for all physics variations.
@@
 The classic, single core CEE and double core CEE channels all require at least one common-envelope event whilst only ``only stable'' consists of only stable mass transfer and ``other'' contains the remaining binaries which are mainly formed from case A ``classic'' binaries as well as ``lucky'' supernova kicks that shrink the binary.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig16_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF1_formation_channels.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/formation_channels.ipynb}{\faBook}.}
     \label{fig:formation_channels}
@@
     \centering
-    \includegraphics[width=\textwidth]{fig17_dcos_on_sc_eccentric_colours.png}
+    \includegraphics[width=\textwidth]{figF2_dcos_on_sc_eccentric_colours.png}
     \caption{As the bottom panels of Fig.~\ref{fig:dcos_on_sc}, but without the density distributions and scatter points are coloured by their eccentricity.
 We show eccentric sources are located in an offshoot below the $30 \unit{kpc}$ around $2 \unit{mHz}$.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig17_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF2_dcos_on_sc_eccentric_colours.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/sensitivity_curve.ipynb}{\faBook}.}
     \label{fig:dcos_on_sc_ecc_col}
 
-    \includegraphics[width=0.8\textwidth]{fig18_dco_formation_distributions.pdf}
+    \includegraphics[width=0.8\textwidth]{figF3_dco_formation_distributions.pdf}
     \caption{As Fig.~\ref{fig:fiducial_pdf_distributions}, but for the properties of the detectable systems at DCO formation.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig18_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/figF3_dco_formation_distributions.pdf}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/fiducial.ipynb}{\faBook}.}
     \label{fig:dco_formation_properties}

### 2021-11-23 paper/tex/sections/comparisons.tex

@@
 Despite this, their study finds a much larger number of detections.
-They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for the differences.
+They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, assuming the optimistic CE scenario, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
+However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modOpt{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for the differences.
 It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
@@
 They assume that kicks for NSs formed through ECSN are slightly higher than our work ($50 \unit{km}{s^{-1}}$ instead of $30 \unit{km}{s^{-1}}$).
-This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold would offset this.
+This may account for their particularly low BHNS rate (as the binaries would be more likely to disrupt), which is a factor of 20 lower than ours, but we expect their assumption of the optimistic CE scenario, reduced Wolf-Rayet winds and lower SNR detection threshold could partially offset this.
 As we show in Appendix~\ref{app:mw_changes}, their use of a simpler Milky Way model, especially with only a single metallicity, would lead to an underestimate of the BHBH and BHNS rates, which may explain the discrepancy in our results.\\

### 2021-11-23 paper/tex/sections/conclusion.tex

@@
 %
-For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS.
+For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS \citefloorp{}.
 These simulations have been optimised with the adaptive sampling algorithm STROOPWAFEL to preferentially sample NS and BH binaries.
@@
     \item \textbf{Probing the black hole mass distribution and the lower mass gap:} We expect LISA to predominantly detect lower mass BHs (with 90\% of BHBH and BHNSs having BH masses lower than $11 \unit{M_\odot}$ in our fiducial simulations) in stark contrast to current ground-based detectors which are heavily biased towards high mass systems.
+For our fiducial simulation, we predict that approximately 69 systems with a component with a mass between $2.5$-$5 \unit{M_\odot}$ would be detected by a 4-year LISA.
 This implies that LISA can potentially make important contributions to the debate about the existence of a lower mass gap (see Fig.~\ref{fig:lower_mass_gap_variation}).
 
-    \item \textbf{Eccentricity distribution:} We find that for all DCO types a large fraction of detectable systems still have nonzero eccentricities ($e = 0.01$) when entering the LISA band, which can be used to distinguish them from the more numerous WDWD binaries, which are largely expected to be circular.
+    \item \textbf{Eccentricity distribution:} We find that for all DCO types a large fraction of detectable systems still have nonzero eccentricities ($e > 0.01$) when entering the LISA band, which can be used to distinguish them from the more numerous WDWD binaries, which are largely expected to be circular.
 In particular, for our fiducial model, we find that this is the case for around three quarters of detectable binaries.
@@
 
-    \item \textbf{Prospects for finding EM counterparts:} We expect about 13\% of detections with a sky localisation better than 1 degree.
+    \item \textbf{Prospects for finding EM counterparts:} We expect about 13\% of detections with a sky localisation better than 1 degree for our fiducial model (though the fraction remains roughly constant among model variations).
 This fraction remains the same for a 10-year LISA mission, meaning that the number increases proportionally.
@@
 
-   \item \textbf{Benefits of extending the LISA mission:} The number of detections scale approximately as $T_{\rm obs}^{0.5}$, where $T_{\rm obs}$ is the mission length.
-Therefore, extending the LISA mission from 4- to 10-years increases the number of detections by about 60\%.
+   \item \textbf{Benefits of extending the LISA mission:} The number of detections scale approximately as $\sqrt{T_{\rm obs}}$, where $T_{\rm obs}$ is the mission length.
+Therefore, extending the LISA mission from 4- to 10-years increases the number of detections by about 60\% for each model variation.
 A further important benefit is the improvement of the characterisation of the sources, since the relative error on the frequency derivative (which dominates the relative error in the chirp mass) scales as $T_{\rm obs}^{-2.5}$ for stationary sources (Eq.~\ref{eq:f_orb_dot_unc}).
-   We find that the number of systems with chirp masses that can be measured better than 10\% increases by a factor of 2.4.
+We find that the number of systems with chirp masses that can be measured better than 10\% increases by a factor of 2.4 for each model variation.
    In addition, the number of systems with a sky localisation better than one degree increases by a factor of 1.5.

### 2021-11-23 paper/tex/sections/introduction.tex

@@
 
-Earlier work on BHBHs, BHNSs and NSNSs in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.
+Earlier work on BHBHs, BHNSs and NSNSs in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020, Shao+2021}.
 We build upon previous efforts but with several important improvements.
-We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters.
+We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters \citefloorp{}.
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).

### 2021-11-23 paper/tex/sections/methods.tex

@@
 
-We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in preparation).
+We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in prep.).
 This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}.
@@
 \end{equation}
-for $i = 1, 2, \dots, N_{\rm binaries}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is immediately after the second supernova in the system) and gravitational-wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
+for $i = 1, 2, \dots, N_{\rm binaries}$, where $m_1$ and $m_2$ are the primary and secondary masses, $a_{\rm DCO}$ and $e_{\rm DCO}$ are the semi-major axis and eccentricity at the moment of double compact object (DCO) formation, $t_{\rm evolve}$ is the time between the binary's zero-age main sequence and DCO formation, $t_{\rm inspiral}$ is the time between DCO formation (that is, immediately after the second supernova in the system) and gravitational-wave merger and $w$ is the adaptive importance sampling weight assigned by STROOPWAFEL \cite[][Eq.~7]{Broekgaarden+2019}.
 We sample from these sets of parameters when creating synthetic galaxies.
@@
 We match each set of galaxy parameters $\mathbf{g}_{{j}}$, to a random set of binary parameters $\mathbf{b}_{{Z, i}}$, by drawing a binary from the closest metallicity bin to the metallicity in $\mathbf{g}_{{j}}$.
+If the metallicity in $\mathbf{g}_{{j}}$ is below the minimum COMPAS metallicity bin ($Z = 10^{-4}$), we use this minimum bin.
+If the metallicity in $\mathbf{g}_{{j}}$ is above the maximum COMPAS metallicity bin ($Z = 0.03$), we use a randomly selected bin from the five highest metallicity bins.
 
@@
 
-We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational-wave luminosity remains below 1\%.
+We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{Wagg+2021} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational-wave luminosity remains below 1\%.
 
@@
 We then determine the fraction of binaries that are detectable in each Milky Way instance by summing the adaptive importance sampling weights of the binaries that have an SNR greater than 7, and dividing by the total weights in the simulation.
-We multiply this fraction by the total number in the Milky Way to find a detection rate (which we write as a total number of detections per LISA mission)
+We multiply this fraction by $N_{\rm DCO}$ to find a detection rate (which we write as a total number of detections per LISA mission)
 \begin{equation}

### 2021-11-23 paper/tex/sections/appendix.tex
update table and other comments

@@
         \hline
-        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{9} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{14}{14} & \confinv{118}{11}{11} & \confinv{71}{8}{9} & \confinv{13}{4}{4}\\
-        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{8}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{13} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
-        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{10} & \confinv{76}{9}{9} & \confinv{14}{4}{3} & \confinv{6}{2}{3}\\
-        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{9} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
-        E & No Case BB mass transfer systems & \confinv{77}{9}{8} & \confinv{69}{8}{9} & \confinv{7}{2}{3} & \boldconfinv{0}{0}{1} & \confinv{121}{11}{11} & \confinv{109}{10}{11} & \confinv{12}{4}{3} & \boldconfinv{0}{0}{1} \\
-        F & Case BB Unstable + Optimistic CE & \boldconfinv{321}{18}{18} & \boldconfinv{154}{12}{13} & \boldconfinv{148}{12}{13} & \confinv{18}{4}{4} & \boldconfinv{484}{22}{22} & \boldconfinv{240}{16}{15} & \confinv{217}{15}{15} & \confinv{27}{5}{6}\\
-        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{7} & \confinv{28}{5}{5} & \boldconfinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{7} & \boldconfinv{3}{1}{2} & \confinv{17}{4}{4}\\
-        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{9}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{11}{12} & \confinv{92}{10}{9} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
-        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{11}{12} & \confinv{68}{9}{8} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{14}{15} & \confinv{110}{11}{10} & \confinv{63}{8}{8} & \confinv{46}{7}{7}\\
-        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{5}{5} & \confinv{16}{4}{4} & \boldconfinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \boldconfinv{57}{7}{8}\\
-        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{15} & \confinv{152}{13}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{341}{18}{19} & \confinv{230}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
-        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{12} & \confinv{50}{7}{7} & \confinv{70}{8}{9} & \confinv{7}{3}{2} & \confinv{205}{14}{14} & \confinv{77}{9}{8} & \confinv{117}{10}{11} & \confinv{11}{3}{3}\\
-        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{6} & \confinv{7}{2}{3} & \confinv{215}{14}{15} & \confinv{154}{13}{12} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
-        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{10}{11} & \confinv{58}{7}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{190}{14}{14} & \confinv{92}{10}{9} & \confinv{85}{9}{9} & \confinv{13}{3}{4}\\
-        O & No PISN and pulsational-PISN & \confinv{127}{12}{11} & \confinv{75}{8}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{206}{15}{14} & \confinv{121}{11}{10} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
-        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{185}{14}{13} & \confinv{83}{9}{9} & \confinv{87}{10}{9} & \confinv{15}{4}{4} & \confinv{301}{18}{17} & \confinv{130}{11}{12} & \confinv{145}{12}{12} & \confinv{26}{5}{5}\\
-        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{17} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{5} & \confinv{427}{21}{21} & \confinv{143}{12}{12} & \boldconfinv{229}{15}{15} & \confinv{55}{8}{7}\\
-        R & Black holes receive not natal kick & \confinv{230}{15}{15} & \confinv{91}{10}{9} & \confinv{132}{11}{12} & \confinv{7}{2}{3} & \confinv{373}{20}{19} & \confinv{142}{12}{12} & \confinv{219}{15}{14} & \confinv{12}{4}{3}\\
-        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{10}{11} & \confinv{76}{9}{8} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{13}{14} & \confinv{112}{10}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
-        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \boldconfinv{30}{6}{5} & \boldconfinv{6}{3}{2} & \confinv{16}{4}{3} & \confinv{8}{2}{3} & \boldconfinv{49}{7}{7} & \boldconfinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\
+        A & Fiducial & \confinv{124}{11}{11} & \confinv{74}{9}{8} & \confinv{42}{6}{7} & \confinv{8}{3}{3} & \confinv{202}{15}{14} & \confinv{117}{10}{11} & \confinv{71}{8}{8} & \confinv{13}{4}{4}\\
+        B & Fixed mass transfer efficiency of $\beta=0.25$ & \confinv{94}{10}{10} & \confinv{69}{9}{8} & \confinv{22}{4}{5} & \confinv{3}{2}{2} & \confinv{149}{12}{12} & \confinv{108}{11}{10} & \confinv{37}{6}{6} & \confinv{5}{2}{2}\\
+        C & Fixed mass transfer efficiency of $\beta=0.5$ & \confinv{59}{8}{8} & \confinv{47}{7}{7} & \confinv{8}{3}{3} & \confinv{4}{2}{2} & \confinv{96}{10}{9} & \confinv{76}{9}{8} & \confinv{14}{4}{3} & \confinv{7}{3}{2}\\
+        D & Fixed mass transfer efficiency of $\beta=0.75$ & \confinv{67}{8}{8} & \confinv{47}{7}{7} & \confinv{7}{2}{3} & \confinv{13}{4}{3} & \confinv{104}{10}{11} & \confinv{71}{8}{8} & \confinv{12}{3}{4} & \confinv{21}{4}{5}\\
+        E$^\prime$ & Case BB mass transfer is always unstable & \confinv{90}{10}{9} & \confinv{66}{8}{8} & \confinv{21}{5}{5} & \boldconfinv{3}{2}{1} & \confinv{133}{11}{12} & \confinv{101}{10}{10} & \confinv{29}{5}{5} & \boldconfinv{4}{2}{2}\\
+        F & Case BB Unstable + Optimistic CE & \boldconfinv{368}{19}{19} & \boldconfinv{154}{13}{12} & \boldconfinv{198}{14}{14} & \confinv{17}{4}{4} & \boldconfinv{553}{24}{23} & \boldconfinv{238}{15}{16} & \boldconfinv{289}{17}{17} & \confinv{25}{5}{5}\\
+        G & CE efficiency $\alpha = 0.1$ & \confinv{40}{6}{6} & \confinv{28}{5}{5} & \boldconfinv{2}{1}{2} & \confinv{10}{3}{3} & \confinv{64}{8}{8} & \confinv{44}{7}{6} & \boldconfinv{3}{1}{2} & \confinv{17}{4}{4}\\
+        H & CE efficiency $\alpha = 0.5$ & \confinv{86}{10}{9} & \confinv{58}{7}{8} & \confinv{22}{5}{4} & \confinv{6}{3}{2} & \confinv{136}{12}{11} & \confinv{91}{9}{10} & \confinv{35}{6}{6} & \confinv{10}{3}{3}\\
+        I & CE efficiency $\alpha = 2.0$ & \confinv{133}{12}{11} & \confinv{67}{8}{9} & \confinv{38}{6}{6} & \confinv{28}{6}{5} & \confinv{218}{15}{14} & \confinv{109}{10}{11} & \confinv{62}{7}{8} & \confinv{46}{7}{7}\\
+        J & CE efficiency $\alpha = 10.0$ & \confinv{78}{9}{9} & \confinv{27}{6}{5} & \confinv{16}{4}{4} & \boldconfinv{35}{6}{6} & \confinv{126}{11}{11} & \confinv{42}{6}{7} & \confinv{27}{6}{5} & \boldconfinv{57}{7}{8}\\
+        K & HG donor stars initiating a CE survive CE & \confinv{218}{15}{14} & \confinv{151}{12}{12} & \confinv{57}{8}{7} & \confinv{10}{3}{3} & \confinv{340}{18}{19} & \confinv{229}{15}{15} & \confinv{96}{10}{10} & \confinv{16}{4}{4}\\
+        L & Fryer rapid SN remnant mass prescription & \confinv{127}{11}{11} & \confinv{50}{7}{7} & \confinv{70}{8}{8} & \confinv{7}{3}{2} & \confinv{204}{14}{15} & \confinv{76}{8}{9} & \confinv{117}{11}{11} & \confinv{11}{3}{3}\\
+        M & Maximum NS mass = 2.0 ${\rm M_{\odot}}$ & \confinv{133}{11}{12} & \confinv{96}{10}{10} & \confinv{30}{5}{5} & \confinv{7}{2}{3} & \confinv{214}{14}{15} & \confinv{153}{12}{13} & \confinv{50}{7}{7} & \confinv{12}{4}{3}\\
+        N & Maximum NS mass = 3.0 ${\rm M_{\odot}}$ & \confinv{118}{11}{11} & \confinv{58}{8}{8} & \confinv{52}{7}{7} & \confinv{8}{3}{3} & \confinv{189}{13}{14} & \confinv{91}{9}{10} & \confinv{85}{10}{9} & \confinv{14}{4}{3}\\
+        O & No PISN and pulsational-PISN & \confinv{126}{11}{12} & \confinv{75}{9}{9} & \confinv{43}{6}{7} & \confinv{8}{3}{3} & \confinv{205}{14}{14} & \confinv{120}{11}{11} & \confinv{72}{8}{9} & \confinv{13}{4}{3}\\
+        P & $\sigma_{\rm RMS}^{\rm 1D} = 100 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{184}{14}{14} & \confinv{82}{9}{9} & \confinv{86}{9}{10} & \confinv{15}{4}{4} & \confinv{300}{17}{17} & \confinv{130}{12}{11} & \confinv{145}{12}{12} & \confinv{26}{6}{5}\\
+        Q & $\sigma_{\rm RMS}^{\rm 1D} = 30 \ {\rm km\ s^{-1}}$ for CCSN & \confinv{268}{16}{16} & \confinv{92}{10}{9} & \confinv{143}{12}{12} & \confinv{34}{6}{6} & \confinv{426}{20}{21} & \confinv{142}{11}{12} & \confinv{229}{16}{15} & \confinv{55}{7}{8}\\
+        R & Black holes receive not natal kick & \confinv{205}{14}{15} & \confinv{89}{9}{10} & \confinv{109}{11}{10} & \confinv{7}{2}{3} & \confinv{332}{18}{18} & \confinv{140}{12}{12} & \confinv{180}{13}{13} & \confinv{12}{4}{3}\\
+        S & Wolf-Rayet wind factor $f_{\rm WR} = 0.1$ & \confinv{118}{11}{11} & \confinv{75}{8}{9} & \confinv{34}{6}{6} & \confinv{9}{3}{3} & \confinv{182}{14}{13} & \confinv{112}{11}{11} & \confinv{56}{8}{7} & \confinv{14}{4}{4}\\
+        T & Wolf-Rayet wind factor $f_{\rm WR} = 5.0$ & \boldconfinv{30}{6}{5} & \boldconfinv{6}{3}{2} & \confinv{15}{3}{4} & \confinv{8}{2}{3} & \boldconfinv{49}{7}{7} & \boldconfinv{9}{3}{3} & \confinv{26}{5}{5} & \confinv{13}{3}{4}\\
         \hline 
-        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{0}{0}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{0}{0}{1} \\
-        - & Maximum rate & \confinv{321}{18}{18} & \confinv{154}{12}{13} & \confinv{148}{12}{13} & \confinv{35}{6}{6} & \confinv{484}{22}{22} & \confinv{240}{16}{15} & \confinv{229}{15}{15} & \confinv{57}{7}{8} \\
+        - & Minimum rate & \confinv{30}{6}{5} & \confinv{6}{3}{2} & \confinv{2}{1}{2} & \confinv{3}{2}{1} & \confinv{49}{7}{7} & \confinv{9}{3}{3} & \confinv{3}{1}{2} & \confinv{4}{2}{2} \\
+        - & Maximum rate & \confinv{368}{19}{19} & \confinv{154}{13}{12} & \confinv{198}{14}{14} & \confinv{35}{6}{6} & \confinv{553}{24}{23} & \confinv{238}{15}{16} & \confinv{289}{17}{17} & \confinv{57}{7}{8} \\
         \hline

### 2021-11-24 paper/tex/sections/abstract.tex
update model E discussion

@@
 We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
-We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the SKA.
+We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the Square Kilometre Array (SKA).

### 2021-11-24 paper/tex/sections/discussion.tex
update model E discussion

@@
 In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}).
-All statistics quoted in each subsection are for the fiducial (model \modFid{}) model.
-However, we find that the \textit{fraction} of systems for each statistic are robust over different model variations (though the total numbers for each statistic change over our model variations due to the different detection rates).
+All predictions quoted in each subsection are derived for the fiducial (model \modFid{}) model.
 
@@
 The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$.
-Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is calculated using Eq.~\ref{eq:chirp_mass_uncertainty}).
+Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is the error on the chirp mass, estimated using Eq.~\ref{eq:chirp_mass_uncertainty}).
 We find that for the detectable population of a 4(10)-year LISA mission, \BHBHAboveMaxWDWDFourPerc{}(\BHBHAboveMaxWDWDTenPerc{})\% of BHBHs, \BHNSAboveMaxWDWDFourPerc{}(\BHNSAboveMaxWDWDTenPerc{})\% of BHNSs and \NSNSAboveMaxWDWDFourPerc{}(\NSNSAboveMaxWDWDTenPerc{})\% of NSNSs satisfy this condition.
@@
 Therefore, if any system is detected with anything other than one detectable harmonic, this suggests that the system is unlikely to be a WDWD.
-We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics.
+We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics (see also Sec.~\ref{sec:fiducial_distributions}).
 Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.~\ref{sec:fiducial_distributions}).
@@
 This condition can be written as $\sigma_\theta < \arcsin(z_{\rm plane} / D_L)$ or $D_L < z_{\rm plane}$, where we set the height of the Galactic plane, $z_{\rm plane}=0.95 \unit{kpc}$, to the scale height of the high-$\alpha$ disc.
-We apply this condition to find that the fraction of sources that are eccentric \textit{and} localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs.
-Note that although the fractions are the same for the 10-year mission, the \textit{absolute} number of detections is still greater.
+We apply this condition to find that the fraction of sources that are eccentric and localised within the disc for a 4(10)-year LISA mission are \BHBHEccInDiscFourPerc{}(\BHBHEccInDiscTenPerc{})\% for BHBHs, \BHNSEccInDiscFourPerc{}(\BHNSEccInDiscTenPerc{})\% for BHNSs and \NSNSEccInDiscFourPerc{}(\NSNSEccInDiscTenPerc{})\% for NSNSs.
+Note that although the fractions are the same for the 10-year mission, the absolute number of detections is still greater.
 Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
@@
 
-We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of \textit{distinguishable} detections increases by a greater factor since each of the more numerous sources are better measured.
+We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of distinguishable detections increases by a greater factor since each of the more numerous sources are better measured.
 This further underlines the benefits of extending the LISA mission to 10 years.
@@
 
-\subsection{Matching LISA detections to pulsars with SKA}\label{sec:pulsar_matching}
+\subsection{Matching LISA detections to pulsars with the SKA}\label{sec:pulsar_matching}
 Since the vast majority of the LISA detectable population of DCOs will not merge for many years, the main type of electromagnetic counterpart for this population is pulsars.
 Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar.
-The joint detection of a binary pulsar with LISA and SKA would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
+The joint detection of a binary pulsar with LISA and the SKA \citep{Dewdney+2009} would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
 A pulsar(PSR)+BH can provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
@@
 
-We estimate that on average, given the number of detectable pulsars and SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
+We estimate that on average, given the number of detectable pulsars and the SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
 Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA.
@@
 Our predictions are subject to various uncertainties which can be broadly divided into different categories: (a) those arising from the progenitor models for the population of DCOs and (b) those arising from the choices we have made when placing these DCOs in our model for the Milky-Way.
-Furthermore, (c) there may be contributions from other formation channels that we have not considered here.
 Although we are unable, at present, to evaluate the impact of all these uncertainties, the reader should nevertheless keep in mind that they are likely very substantial.
@@
 
-\paragraph{Other formation channels (c)} In this work we considered the formation of double compact objects through the isolated binary formation channel.
-We have not included the possible contributions from other channels such as dynamical formation in dense star clusters, formation in young star clusters and triple systems in the field.
-We refer to \citet{Kremer+2018} and \citet{Banerjee+2020} for a studies of the contribution of dynamical formation in globular and young stellar clusters.
+\subsection{Other formation channels}
+
+In this paper we considered the formation of NS and BH binaries formed through isolated binary evolution through the classical CE channel, the stable mass transfer channel and variations on these (e.g.
+Fig.~\ref{fig:formation_channels}).
+We did not consider further possible contributions from other formation channels, which may play a role.
+
+We highlight the possible role of dynamical formation in globular clusters \citet[e.g.\ ][]{Kremer+2018}.
+For a nominal 4-year LISA mission, they estimate 21 sources in total of which 7 are binary black holes.
+
+\citet{Banerjee+2020} investigates formation in young star clusters and estimates xxx sources
+
+several 10s to 100s systems with SNR>5

### 2021-11-24 paper/tex/sections/introduction.tex
update model E discussion

@@
 A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
-These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and SKA, which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
+These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
 

### 2021-11-24 paper/tex/sections/results.tex
update model E discussion

@@
 \end{equation}
-The inspiral time depends most strongly on the separation at DCO formation ($a$) and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}).
+The inspiral time depends most strongly on the separation at DCO formation, $a$, and this is where the three types also differ most strongly (see Fig.~\ref{fig:dco_formation_properties}).
 The detectable NSNS systems have the tightest orbits at DCO formation.

### 2021-11-24 paper/tex/sections/variations.tex
update model E discussion

@@
 In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE.
-This effectively excludes any systems that evolve through case BB mass transfer since all common-envelopes initiated in this way have donors in the Hertzsprung gap and thus end as stellar mergers under the pessimistic CE assumption.
-Therefore, this kills nearly all NSNS systems.
-We also find a heavy reduction of the BHNS systems by a factor 6.
-The BHBH systems are not affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.
+Note that this is slightly different from model E from \citet{Broekgaarden+2019}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases).
+We make this change since, otherwise, the model would effectively exclude any systems that evolve through case BB mass transfer and kill nearly all NSNS systems.
+Therefore, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}).
+This model gives the lowest NSNS rate of all of our variations, which is a factor of 3 lower than our fiducial rate.
+We also find a reduction of the BHNS systems by a factor 2.
+The BHBH systems are not significantly affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.
 
 Finally, in model \modCaseBBOpt{}, we again enforce that case BB mass transfer is always unstable, but in combination with the optimistic treatment for CE (essentially combining models \modCaseBB{} and \modOpt{}).
-This allows the systems formed through case BB (as well as any other systems that have HG donors for common-envelopes) to survive the CE phase.
+This allows the systems  that have HG donors for common-envelopes (as well as those formed through case BB mass transfer) to survive the CE phase.
 We find that this model leads to the highest predictions for the detections among all variations that we have considered.

### 2021-11-24 paper/tex/sections/appendix.tex
update physics variations conclusion

@@
 Models \modRangeCE{} focus on altering the common-envelope physics.
-In model \modCaseBB{} Broekgaarden et al.\ (2021a, 2021b) investigate the consequence of assuming that case BB mass transfer onto a neutron star or black hole always leads to a stellar merger.
+In model \modCaseBB{} we modify model E from Broekgaarden et al.\ (2021a, 2021b) to investigate the consequence of assuming that case BB mass transfer is always unstable, whilst allowing Helium HG donors to survive CE events.
 They change the common-envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
@@
         \hline
-        \modCaseBB & Exclude Case BB mass transfer \\
+        \modCaseBB & Case BB mass transfer always unstable \\
         \modCaseBBOpt & Case BB always unstable + Optimistic CE \\

### 2021-11-24 paper/tex/sections/conclusion.tex
update physics variations conclusion

@@
 \begin{enumerate}
-    \item \textbf{Total detections:} We predict 30-300 detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
-This increases to about 50-500 for a 10-year LISA mission.
+    \item \textbf{Total detections:} We predict \rangeFourYear{} detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
+This increases to about \rangeTenYear{} for a 10-year LISA mission.
 Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered (see Table~\ref{tab:detection_rates}).
@@
 
-    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related the onset of the common-envelope phase and the efficiency of ejection have a strong impact on the rate predictions.
-This is also true for models where we reduce the natal kicks.
-Finally, our models where we have increased the strength of the Wolf-Rayet winds, drastically reduces the number of systems containing a BH (see Fig.~\ref{fig:detection_rates})
+    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope phase, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions.
+However, uncertainties related to the efficiency of mass transfer, the remnant mass prescription, the maximum neutron star mass and PISN have little effect on the detection rates (see Fig.~\ref{fig:detection_rates})
 

### 2021-11-24 paper/tex/sections/variations.tex
update physics variations conclusion

@@
 
-%We note that impact of physics variations cannot always be easily understood in simple terms as the evolutionary path of a progenitor of a detectable source involves multiple interactions stages.
-Providing full explanations is beyond our current scope, but we hope nevertheless that this section gives the reader an impression of the impact of the physics variations on the rates.
+\subsection{Detection rates}\label{sec:detection_rate_analysis}
+We predict approximately \rangeFourYear{} detections in a 4-year LISA mission, across all our simulations for varying physics assumptions.
+This increases to about \rangeTenYear{} for a 10-year LISA mission.
+Although the number of detections per type can vary by about 2 orders of magnitude, we find that the total detection rate is fairly robust, among the variations we have considered (see Table~\ref{tab:detection_rates}).
 
-\subsection{Detection rates}\label{sec:detection_rate_analysis}
 In Fig.~\ref{fig:detection_rates}, we show the expected number of LISA detections based on our simulations considering variations in the physical assumptions.

### 2021-11-24 paper/tex/sections/discussion.tex
ensure Overleaf is synced

@@
 
-In this paper we considered the formation of NS and BH binaries formed through isolated binary evolution through the classical CE channel, the stable mass transfer channel and variations on these (e.g.
-Fig.~\ref{fig:formation_channels}).
+In this paper we considered the formation of NS and BH binaries formed via isolated binary evolution, through the classical CE channel, the stable mass transfer channel and variations on these (see Fig.~\ref{fig:formation_channels}).
 We did not consider further possible contributions from other formation channels, which may play a role.
@@
 We highlight the possible role of dynamical formation in globular clusters \citet[e.g.\ ][]{Kremer+2018}.
-For a nominal 4-year LISA mission, they estimate 21 sources in total of which 7 are binary black holes.
+For a nominal 4-year LISA mission, they estimate 21 sources  in total will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}.
+In this case, we predict that the sources formed through isolated binary formation will be dominant in nearly every model variation.
 
-\citet{Banerjee+2020} investigates formation in young star clusters and estimates xxx sources
-
-several 10s to 100s systems with SNR>5
+In addition, \citet{Banerjee+2020} investigates formation in young massive and open stellar clusters.
+and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}.
+Note that this total uses a slightly longer mission length and a lower SNR threshold than those used in this paper.
+Nevertheless, this rate is on the same order as our predictions for LISA BHBHs.

### 2021-11-24 paper/tex/sections/introduction.tex
ensure Overleaf is synced

@@
 We do not, however, account for several alternative proposed formation channels, which could affect the rate and distribution of detectable NS and BH binaries in LISA.
-These channels include: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015}, young/open star clusters \citep[e.g.][]{Ziosi+2014, DiCarlo+2020, Rastello+2020, Rastello+2021} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated (hierarchical) triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017, Toonen+2020},  and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009,Mandel+2016,Marchant+2016,Marchant+2017,duBuisson+2020}.
+These channels include: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015}, young/open star clusters \citep[e.g.][]{Ziosi+2014, DiCarlo+2020, Banerjee+2020, Rastello+2020, Rastello+2021} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated (hierarchical) triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017, Toonen+2020},  and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009,Mandel+2016,Marchant+2016,Marchant+2017,duBuisson+2020}.
 
@@
 
-Earlier work on BHBHs, BHNSs and NSNSs in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020, Shao+2021}.
+Earlier work on BHBHs, BHNSs and NSNSs in LISA has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020, Shao+2021}.
 We build upon previous efforts but with several important improvements.

### 2021-11-24 paper/tex/sections/variations.tex
ensure Overleaf is synced

@@
 \paragraph{Case BB mass transfer} In models \modCaseBB{} and \modCaseBBOpt{} we consider uncertainties in case BB mass transfer.
-This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2003, Tauris+2015, Tauris+2017}.
+This is a phase of mass transfer where the donor star has already lost its hydrogen envelope in a prior interaction, but fills its Roche lobe again as it expands during helium shell burning phase \citep[e.g.][]{Dewi+2002, Tauris+2015, Tauris+2017}.
 This is of particular interest for the formation of NSs, as their lower mass progenitors are swelling the most during this phase \citep[e.g.][and references therein]{Laplace+2020}.

### 2021-11-24 paper/tex/paper.tex
update model E discussion
update physics variations conclusion

@@
 \newcommand{\modBetaHigh}{D}
-\newcommand{\modCaseBB}{E}
+\newcommand{\modCaseBB}{E$^{\prime}$}
 \newcommand{\modCaseBBOpt}{F}
@@
 \newcommand{\modRangeMT}{B-D}
-\newcommand{\modRangeCE}{E-K}
+\newcommand{\modRangeCE}{E$^{\prime}$-K}
 \newcommand{\modRangeSN}{L-R}
@@
 \newcommand{\nMinusOneModels}{19}
+
+\newcommand{\rangeFourYear}{30-370}
+\newcommand{\rangeTenYear}{50-550}
 
@@
 It is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
-Simulations in this paper made use of the COMPAS rapid binary population synthesis code, which is freely available at \url{http://github.com/TeamCOMPAS/COMPAS} \citep{Stevenson+2017, Vigna-Gomez+2018, Broekgaarden+2019}.
+Simulations in this paper made use of the COMPAS rapid binary population synthesis code \citep{COMPAS:2021methodsPaper}.
 The simulations performed in this work were simulated with a COMPAS version that predates the publicly available code.
-Our version of the code is most similar to version 02.13.01 of the publicly available COMPAS code.
+Our version is most similar to v02.13.01 of the publicly available COMPAS code.
 Requests for the original code can be made to Floor Broekgaarden.
 The authors used {\sc{STROOPWAFEL}} from \citep{Broekgaarden+2019}, publicly available at \url{https://github.com/FloorBroekgaarden/STROOPWAFEL}\footnote{For the latest pip installable version of STROOPWAFEL please contact Floor Broekgaarden.}.
-The authors also made use of Python from the Python Software Foundation.
-Python Language Reference, version 3.6.
-Available at \url{http://www.python.org}.
-In addition the following Python packages were used: matplotlib (\url{https://matplotlib.org/}), {NumPy} (\url{https://numpy.org/}), SciPy (\url{https://www.scipy.org/}), Jupyter Lab (\url{https://jupyter.org/}), seaborn (\url{https://seaborn.pydata.org/}), h5py (https://www.h5py.org/) and Astropy (\url{http://www.astropy.org}).
+The authors also made use of Python (v3.8), available at \url{http://www.python.org}.
+In addition the following Python packages were used: \texttt{matplotlib} \citep{Hunter+2007}, \texttt{NumPy} \citep{2020NumPy-Array}, \texttt{Astropy} \citep{AstropyCollaboration+2013,AstropyCollaboration+2018}, \texttt{Seaborn} \citep{Waskom+2021}, \texttt{SciPy} \citep{2020SciPy-NMeth}, \texttt{h5py} \citep{Collette+2021} and \texttt{Jupyter Lab} \citep{Kluyver+2016}.
 This research has made use of NASA’s Astrophysics Data System Bibliographic Services.
 We also made use of the computational facilities from the Harvard FAS Research Computing cluster.}
-
-\clearpage
 
@@
 \end{document}
+
+% Oh no, I certainly hope no one sees this comment. Wouldn't it be awful if astro-ph-leaks tweeted this and advertised our paper (:

### 2021-11-24 paper/tex/sections/comparisons.tex
update comparison table

@@
     \centering
-    \includegraphics[width=\textwidth]{fig13_1_compare_dco.png}
+    \includegraphics[width=\textwidth]{fig12_1_compare_dco.png}
 
@@
 
-    \includegraphics[width=\textwidth]{fig13_2_compare_dco.png}
+    \includegraphics[width=\textwidth]{fig12_2_compare_dco.png}
     \caption{A table comparing previous studies of a similar nature to this work.
@@
 The works listed in the table are \citet{Nelemans+2001}, \citet{Belczynski+2010}, \citet{Liu+2014}, \citet{Lamberts+2018}, \citet{Sesana+2020}, \citet{Lau+2020}, \citet{Breivik+2020} and \citet{Shao+2021}.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig13_2_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/previous_BH_NS_studies.xlsx}{\faFileExcel}.}
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_1_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig12_2_compare_dco.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/previous_BH_NS_studies.xlsx}{\faFileExcel}.}
     \label{fig:previous_studies}

### 2021-11-25 paper/tex/sections/appendix.tex
fix e.g. spacings

@@
 Moreover, the distribution of parameters within the population, particularly the mass distributions, are notably disparate.
-By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.\ ][]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
+By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.][]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
 For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.

### 2021-11-25 paper/tex/sections/discussion.tex
fix e.g. spacings

@@
 We stress in particular the uncertainties affecting our most massive progenitor models.
-Observational constraints are scarce for high mass stars and practically non-existent for the rapid evolutionary phases \citep[e.g.\ ][]{Langer2012, Mapelli+2021}.
+Observational constraints are scarce for high mass stars and practically non-existent for the rapid evolutionary phases \citep[e.g.][]{Langer2012, Mapelli+2021}.
 This is even more true for the evolution of massive stars at low metallicity.

### 2021-11-25 paper/tex/sections/introduction.tex
fix e.g. spacings

@@
 Moreover, this frequency regime is also of interest for the detection of \textit{local} stellar-mass double compact objects (DCOs) millions of years before their merger.
-This presents an opportunity for both multi-messenger detections to search for electromagnetic counterparts and multiband gravitational-wave detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
+This presents an opportunity for both multi-messenger detections to search for electromagnetic counterparts, as well as multiband gravitational-wave detections that can help to constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}.
 In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
@@
 The detection of NSNSs in LISA could improve our understanding of many phenomena.
-Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.
-\citealp{Hulse+1975, Antoniadis+2016}, see also refs.\ in \citealp{Tauris+2017}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational-wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
+Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.\ \citealp{Hulse+1975, Antoniadis+2016}, see also refs.\ in \citealp{Tauris+2017}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational-wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
 A LISA detectable NSNS with a pulsar component close to merger would be ideal for connecting these populations, as the binary could be observed from inspiral to merger.

### 2021-11-25 paper/tex/sections/variations.tex
fix e.g. spacings

@@
 
-The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche-lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.\ ][]{deMink+2007}.
+The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche-lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.][]{deMink+2007}.
 In our fiducial model A, we use a prescription in which the accretion rate onto stellar companions is regulated by their thermal timescale, i.e.\ the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
@@
 
-The common-envelope phase constitutes a highly uncertain phase in the evolution of interacting binary systems \citep[e.g.\ ][]{Ivanova+2013}.
+The common-envelope phase constitutes a highly uncertain phase in the evolution of interacting binary systems \citep[e.g.][]{Ivanova+2013}.
 The uncertainties concerns the conditions required for the onset of a common-envelope phase and, if a common-envelope phase occurs, what the outcome is.
@@
 Our fiducial model assumes a common-envelope efficiency parameter $\alpha_{\rm CE} = 1$ which can be interpreted as the case where all the energy liberated by shrinking the orbit is used in an optimal way to unbind the envelope.
-There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations \citep[e.g.\ ][]{DeMarco+2011, Law-Smith+2020, Lau+2021}, but no consistent picture has emerged.
+There have been many attempts to constrain this parameter using observations and more recently also using 3D simulations \citep[e.g.][]{DeMarco+2011, Law-Smith+2020, Lau+2021}, but no consistent picture has emerged.
 Therefore we consider large variations in this parameter.
@@
 In models \modAlphaLowest{}-\modAlphaHighest{} we alter the common-envelope efficiency parameter $\alpha_{\rm CE}$ to $0.1, 0.5, 2.0$ and $10.0$ respectively.
-Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta \citep[e.g.\ ][]{Ivanova+2013, Nandez+2016}.
+Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta \citep[e.g.][]{Ivanova+2013, Nandez+2016}.
 Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion \citep[e.g.\,][]{Schreier+2021}.

### 2021-11-25 paper/tex/sections/introduction.tex
introduction proofread

@@
 The detection of NSNSs in LISA could improve our understanding of many phenomena.
-Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.\ \citealp{Hulse+1975, Antoniadis+2016}, see also refs.\ in \citealp{Tauris+2017}) and more recently the mergers of NSNS binaries have been detected with ground-based gravitational-wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
+Galactic NSNSs have been observed with electromagnetic signals for several decades (e.g.\ \citealp{Hulse+1975, Antoniadis+2016}, see also refs.\ in \citealp{Tauris+2017}) and more recently the mergers of NSNSs have been detected with ground-based gravitational-wave detectors \citep[e.g.][]{Abbott+2017_NSNS}.
 A LISA detectable NSNS with a pulsar component close to merger would be ideal for connecting these populations, as the binary could be observed from inspiral to merger.
-NSNS (and possible BHNS) binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational-wave signals, such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Berger+2014}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
+NSNSs (and possibly BHNSs) are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational-wave signals, such as kilonovae \citep[e.g.][]{Li+1998, Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Berger+2014}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.
 
@@
 With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}.
-However, with only two detections (not including the low-confidence candidate GW190426 \citealt{Abbott+2020_GWTC2} or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1} ) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
+However, with only two detections (not including the low-confidence candidate GW190426, \citealt{Abbott+2020_GWTC2}, or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs, \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
 Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
@@
 
-In this paper, we present models for the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way.
+In this paper, we present models for the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBHs, BHNSs and NSNSs formed through isolated binary evolution in the Milky Way.
 We explore the effect of varying physical assumptions in our population synthesis model on our results as well as discuss the effect of extending the LISA mission length and the prospects for distinguishing DCO detections from the WDWD background.
@@
 We provide a detailed treatment of the eccentricity of detectable sources, both for the inspiral evolution as well as gravitational wave signal during the LISA mission.
-Moreover, our binary population synthesis simulation is the most extensive of its kind to date and makes use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.
-Overall we simulate over 2 billion massive binaries to produce the DCO populations used in this work.
+Moreover, the grid of binary population synthesis simulations that we use is the most extensive of its kind to date and makes use of the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019, Broekgaarden+2021}.
+Overall over 2 billion massive binaries were simulated to produce the DCO populations used in this work.
 We find that this large number of simulations is important to reduce the sampling noise even when using adaptive importance sampling.
@@
 Our paper is structured as follows.
-In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
+In Section~\ref{sec:method}, we describe the methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA.
 We present the main results for our fiducial model in Section~\ref{sec:results}, before exploring the variations in the detectable population when changing our physical assumptions in Section~\ref{sec:variations}.

### 2021-11-25 paper/tex/sections/abstract.tex
abstract updates

@@
 We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
+For our fiducial model, we predict that on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
 We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics.
-We predict that, on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all of our assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions).
+For these variations, in a 4(10)-year mission, the total detection rate across all three DCO types ranges between \rangeFourYear{}(\rangeTenYear{}).
+%We find that uncertainties related to the onset and the efficiency of ejection of the common-envelope, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions.
 We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged.

### 2021-11-25 paper/tex/sections/methods.tex
methods proofread

@@
-To produce predictions for the DCOs that are detectable with LISA, we synthesise a population of DCOs using the population synthesis methods described in Section~\ref{sec:COMPAS_explained}.
+To produce predictions for the DCOs that are detectable with LISA, we use a synthesised population of DCOs, simulated using the methods described in Section~\ref{sec:COMPAS_explained}.
 In Section~\ref{sec:galaxy_synthesis} we describe our model for the Milky Way and how we place DCOs in randomly sampled Milky Way instances.
 We evolve the orbit of each DCO in a Milky Way instance up to the LISA mission and calculate the detection rate for that instance using the methods presented in Section~\ref{sec:gw_detection}.
-
-\begin{figure*}[t]
-    \centering
-    \includegraphics[width=\textwidth]{fig1_galaxy_diagram.png}
-    \caption{A schematic illustrating how we model the Milky Way.
-The left panel illustrates the different model aspects: star formation history of three galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
-The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
-The top panel shows a side-on view and the bottom panel a face-on view.
-\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig1_galaxy_diagram.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
-    \label{fig:galaxy_schematic}
-\end{figure*}
 
@@
 
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=\textwidth]{fig1_galaxy_diagram.png}
+    \caption{A schematic illustrating how we model the Milky Way.
+The left panel illustrates the different model aspects: star formation history of three galactic components (individually shown in the dotted lines), radial distribution, metallicity-radius-time relation, and height distribution.
+The right panel shows an example instance of the Milky Way with $250000$ binaries shown as points coloured by metallicity.
+The top panel shows a side-on view and the bottom panel a face-on view.
+\href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figures/fig1_galaxy_diagram.png}{\faFileImage} \href{https://github.com/TomWagg/detecting-DCOs-in-LISA/blob/main/paper/figure_notebooks/galaxy_creation_station.ipynb}{\faBook}.}
+    \label{fig:galaxy_schematic}
+\end{figure*}
+
 Fig.~\ref{fig:galaxy_schematic} shows the distributions and relations outlined in this section and also displays an example random galaxy drawn using this model.
@@
 The two discs form stars in mutually exclusive time periods, such that the high-\achem~disc forms stars in the early history of the galaxy ($8$--$12 \unit{Gyr}$ ago) and the low-\achem~disc forms stars more recently ($0$--$8 \unit{Gyr}$ ago).
-We normalise both distributions so that an equal amount of mass is formed in each of the two components over their respective star forming periods.
+Both distributions are normalised so that an equal amount of mass is formed in each of the two components over their respective star forming periods.
 
@@
 $F_m = -1 \unit{dex}$ is the metallicity of the gas at the center of the disc at $\tau = \tau_m$, $\nabla [{\rm Fe} / {\rm H}] = -0.075 \unit{kpc^{-1}}$ is the metallicity gradient, $R^{\rm now}_{[{\rm Fe} / {\rm H}] = 0} = 8.7 \unit{kpc}$ is the radius at which the present day metallicity is solar and $\gamma_{[{\rm Fe} / {\rm H}]} = 0.3$ sets the time dependence of the chemical enrichment.
-We can convert this to the representation of metallicity that we use in this paper by applying \citep[e.g.][]{Bertelli+1994}
+We convert this to the representation of metallicity that we use in this paper by applying \citep[e.g.][]{Bertelli+1994}
 \begin{equation}\label{eq:galaxy_FeH_to_Z}
@@
 We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{Wagg+2021} to evolve binaries and calculate their LISA detectability.
-For a full derivation of the equations given below see \citep[][Sec.~3]{Wagg+2021}, or the LEGWORK documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
+For a full derivation of the equations given below see \citep[][Section~3]{Wagg+2021}, or the LEGWORK documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
 

### 2021-11-26 paper/tex/sections/results.tex
results I proofread

@@
 For reference, we show dotted lines to indicate where a hypothetical binary system would reside assuming a given distance from earth (diagonal lines) and a fixed remaining inspiral time (vertical lines).
-For each line we assume the binary is circular and has a chirp mass equal to the average of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel), unless indicated otherwise.
+For each line we assume the binary is circular and has a chirp mass equal to the average of the sample ($\avg{\mathcal{M}_c}$, annotated in each panel).
 We also overplot the LISA verification binaries (star symbols, \citealt{Kupfer+2018}).
@@
 A higher mass system can emit at lower frequency and still produce the minimum SNR needed for detection.
-We note that this effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically \citep[e.g.][]{Sesana+2020}.
+We note that this effect can be used to distinguish the heavier DCOs that we discuss in this work from WDWD systems, at least probabilistically (see Sec.~\ref{sec:WDWD_distinguish}).
 In the same way, this also explains the offset in frequency between the population of sources we predict and the LISA verification binaries.
@@
 Inspecting the dotted reference lines, we note that the peak of the density distribution of observable sources coincides with the location expected for circular systems at $8 \unit{kpc}$, which is the distance to the centre of the Milky Way.
-As can be seen best in the lower panels, the reference lines for $0.1$ and $30 \unit{kpc}$ enclose the majority of systems as expected given the dimensions of our Milky Way.
+As can be seen best in the lower panels, the reference lines for $0.1$ and $30 \unit{kpc}$ enclose the majority of systems, as expected given the dimensions of the Milky Way.
 
 There is a distinct subpopulation of binaries, most clearly visible in the lower panels as an offshoot that extends downwards to ASDs of $10^{-19} \unit{Hz}^{-1/2}$, especially around $2 \unit{mHz}$.
-This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col} in our appendix, which shows a similar figure but colouring individual systems by their eccentricity.
-This can also be seen, albeit indirectly, from the contours shown in the bottom panels of Fig.~\ref{fig:dcos_on_sc}, which encompass 90\% of the \textit{circular} sources in each population.
+This offshoot is almost uniquely composed of eccentric binaries, as can be seen in Fig.~\ref{fig:dcos_on_sc_ecc_col}, which shows a similar figure but colouring individual systems by their eccentricity.
+This can also be seen, albeit indirectly, from the contour lines shown in the bottom panels of Fig.~\ref{fig:dcos_on_sc}, which encompass 90\% of the \textit{circular} sources in each population.
 This contour does not include the offshoot.
@@
 \paragraph{Orbital Frequency} The orbital frequency distributions for BHBHs, BHNSs and NSNSs (Fig.~\ref{fig:fiducial_pdf_distributions}a) peak at progressively increasing frequencies.
-As already mentioned above, this is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
+As mentioned in Sec.~\ref{sec:dcos_on_sc}, this is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
 The distributions appear nearly symmetric, but closer inspections shows that the left hand side is more populated, which can be seen most clearly in the curve for the BHBHs.
@@
 We also note that our BH mass distribution extends down below $5\unit{M_{\odot}}$ to $2.5 \unit{M_{\odot}}$ which is our fiducial maximum neutron star mass.
-The BHs in this simulation fill the so-called ``lower mass gap'' marked as a grey band \citep{Ozel+2010,Farr+2011}, see also \citet{Shao+2021} who recently pointed this out.
-This prediction is sensitive to adopted model for fallback during the SN explosion as we discuss this further in Section~\ref{sec:lower_mass_gap}
+The BHs in this simulation fill the so-called ``lower mass gap'' marked as a grey band \citep{Ozel+2010,Farr+2011}, see also \citet{Shao+2021} who recently also pointed this out.
+This prediction is sensitive to adopted model for fallback during the SN explosion as we discuss this further in Section~\ref{sec:lower_mass_gap}.
 
@@
 Around two thirds of detectable BHNSs experience at least one common-envelope event, whilst the last third are formed through only stable mass transfer.
-The first peak at $q = 0.18$ is from systems that experience at least one common-envelope phase and occurs at the expected mass ratio, which approximately follows the mean BH mass ($\sim 6.5 \unit{M_\odot}$) and NS mass ($\sim 1.2 \unit{M_\odot}$).
+The first peak at $q = 0.18$ is from systems that experience at least one common-envelope phase and occurs at the expected mass ratio, which approximately follows the mean BH mass (${\sim}6.5 \unit{M_\odot}$) and NS mass (${\sim}1.2 \unit{M_\odot}$).
 Yet we also see a second peak at higher mass ratios around $q = 0.34$, which arises from the fraction of the population that underwent only stable mass transfer phases.
@@
 Such systems are more rare, but we find them to be significant among the BHBH population, where they account for \BHBHHighlyEccentric{} of systems.
-Detectable BHBHs in our simulation (and, in particular, those that are eccentric) are primarily systems formed through the stable mass transfer channel (see Section~\ref{fig:formation_channels}).
+Detectable BHBHs in our simulation (and, in particular, those that are eccentric) are primarily systems formed through the stable mass transfer channel (see Fig.~\ref{fig:formation_channels}).
 These systems are still relatively wide (compared to those formed through the CE channel) immediately prior to formation of the second BH, which makes them more easily affected by kicks.
@@
 \subsection{Distribution in the Milky Way}\label{sec:mw_detectable_distribution}
-For our Milky way model we consider three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar.
+For our Milky way model we consider three different components, a low-\achem~(``thin'') disc, an older high-\achem~(``thick'') disc and a bulge/bar (see Sec.~\ref{sec:galaxy_synthesis}).
 In Table~\ref{tab:component_fractions} we summarise the number of detections originating from each of these components.
@@
 
-The distribution for NSNS stands out by being flatter, making them more common nearby and, surprisingly, also at larger distances.
+The distribution for NSNS stands out by being flatter, making them more common nearby and, surprisingly, also at larger distances compared to the stellar density.
 This may seem counter intuitive as one might naively expect the less massive NSNS systems would not be observable out to larger distances than the more massive BHNS and NSNS systems.
@@
 
-The fraction of detectable DCOs that formed through different formation channels in other model variations are shown Fig.~\ref{fig:formation_channels}, where the first column corresponds to the fiducial model described above.
+The fraction of detectable DCOs that are formed through different formation channels in the other model variations are shown Fig.~\ref{fig:formation_channels}, where the first column in the plot corresponds to the fiducial model that we described above.
 

### 2021-11-26 simulation/src/variations.py
add a prime to label

@@ -45,7 +45,7 @@ variations = np.array(
         {
             "file": "unstableCaseBB_opt",
             "short": "F",
-            "med": "E + K",
+            "med": "E' + K",
             "long": "Case BB Unstable + Optimistic CE",
             "colour": plt.get_cmap("tab20")(2)
         },

### 2021-11-26 paper/tex/sections/variations.tex
variations proofread

@@
 In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE.
-Note that this is slightly different from model E from \citet{Broekgaarden+2019}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases).
+Note that this is slightly different from model E from \citet{Broekgaarden+2021}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases).
 We make this change since, otherwise, the model would effectively exclude any systems that evolve through case BB mass transfer and kill nearly all NSNS systems.
-Therefore, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}).
+As expected, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}).
 This model gives the lowest NSNS rate of all of our variations, which is a factor of 3 lower than our fiducial rate.
@@
 Overall, weighting by the relative detection rates, this gives that, in our fiducial model, 55\% of our predicted LISA DCO detections would have at least one component in the lower mass gap when using this remnant mass prescription.
-This equates to approximately 68 systems being detected in the lower mass gap.
+This equates to approximately 69 systems being detected in the lower mass gap.
 Alternatively, the blue curve in Fig.~\ref{fig:lower_mass_gap_variation} shows the same distribution but for the \textit{rapid} remnant mass prescription \citep{Fryer+2012}, which we use in model \modRapid{}.

### 2021-11-26 paper/tex/sections/discussion.tex
discussion proofread

@@
-In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}) and the main caveats for this study (Sec.~\ref{sec:caveats}).
-All predictions quoted in each subsection are derived for the fiducial (model \modFid{}) model.
+In this section we discuss the prospects of (and methods for) identifying LISA sources (Sec.~\ref{sec:identify_sources}), the possibility of matching LISA signals to SKA detections (Sec.~\ref{sec:pulsar_matching}), the main caveats for this study (Sec.~\ref{sec:caveats}) and the possible contribution from other formation channels (Sec.~\ref{sec:other_formation_channels}).
+All predictions quoted in each subsection are derived for the fiducial model (model \modFid{}).
 
@@
 The simplest way to check whether a source is a WDWD is to evaluate its chirp mass.
-The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be $\sim 1.2 \unit{M_{\odot}}$.
+The mass of a non-rotating white dwarf cannot be larger than the Chandrasekhar limit of $1.4 \unit{M_\odot}$ \citep{Chandrasekhar+1931, Hamada+1961}, so we can take the maximum chirp mass of a WDWD to be ${\sim}1.2 \unit{M_{\odot}}$.
 Therefore, any DCO with a chirp mass that satisfies $\mathcal{M}_c > 1.2 \unit{M_{\odot}} + \Delta \mathcal{M}_c$ must not be a WDWD (where $\Delta \mathcal{M}_c$ is the error on the chirp mass, estimated using Eq.~\ref{eq:chirp_mass_uncertainty}).
@@
 We find that for a 4(10)-year LISA mission, \BHBHMultipleHarmonicsFourPerc{}(\BHBHMultipleHarmonicsTenPerc{})\% of BHBHs, \BHNSMultipleHarmonicsFourPerc{}(\BHNSMultipleHarmonicsTenPerc{})\% of BHNSs and \NSNSMultipleHarmonicsFourPerc(\NSNSMultipleHarmonicsTenPerc{})\% of NSNSs are detected with multiple harmonics (see also Sec.~\ref{sec:fiducial_distributions}).
-Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions} and discussion in Sec.~\ref{sec:fiducial_distributions}).
+Both the absolute percentage and the relative improvement with an extended LISA mission is lower for the BHNSs with respect to other DCOs as we find that these BHNSs are less eccentric on average (see Fig.~\ref{fig:fiducial_pdf_distributions}d and discussion in Sec.~\ref{sec:fiducial_distributions}).
 
@@
 Note that although the fractions are the same for the 10-year mission, the absolute number of detections is still greater.
-Overall, combining these methods we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
-Thus we will be able to confidently discuss approximately half of all detected sources from WDWDs.
+
+Overall, combining these methods (chirp mass, eccentricity and sky localisation) we find that for a 4(10)-year mission, LISA will detect at least \BHBHNotWDWDFour{}(\BHBHNotWDWDTen{}) BHBHs, \BHNSNotWDWDFour{}(\BHNSNotWDWDTen{}) BHNSs and \NSNSNotWDWDFour{}(\NSNSNotWDWDTen{}) NSNSs that are distinguishable from the WDWD population.
+Thus we will be able to confidently distinguish approximately half of all detected sources from WDWDs.
 This increases to roughly 60\% for a 10-year mission.
-
 We highlight that, though the overall number of LISA detections in an extended mission only increases by a factor of $\sqrt{T_{\rm obs}}$, the number of distinguishable detections increases by a greater factor since each of the more numerous sources are better measured.
@@
 Therefore, for this section we focus only on BHNSs and NSNSs since no BHBH system will contain a pulsar.
-The joint detection of a binary pulsar with LISA and the SKA \citep{Dewdney+2009} would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
+The joint detection of a binary pulsar with LISA and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}) would not only help to constrain the parameters of the binary, but also enable investigation of other compact object physics.
 A pulsar(PSR)+BH can provide stringent tests of theories of gravity, in particular the ``No-hair theorem'' \citep{Keane+2015}.
@@
 
-We estimate that on average, given the number of detectable pulsars and the SKA sky area, each pulsar in SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
-Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in SKA.
+We estimate that on average, given the number of detectable pulsars and the SKA sky area, each pulsar in the SKA occupies a region with an angular resolution of $\sigma_{\theta} < 1.3^\circ$ or $0.7^\circ$ for SKA-1 and SKA-2 respectively (see Appendix~\ref{app:ska_area}).
+Therefore, any DCOs containing NSs localised by LISA with an angular resolution lower than these values can be unambiguously matched to the radio signal in the SKA.
 By considering Fig.~\ref{fig:ang_res}, approximately $11$ and $6$ (for SKA-1 and SKA-2) DCOs will satisfy this constraint.
 
-If there is more than one pulsar in the region given by the LISA sky localisation, one can compare the measured parameters of the system in LISA and SKA.
-Both SKA and LISA will measure the orbital frequency to high precision, as well as the time derivative of the frequency and chirp mass to a lesser precision, of each of these systems.
-Therefore, one could perform a targeted search with SKA that checks the sky location given by LISA, only looking for binary pulsars with orbital frequencies within the uncertainties.
+If there is more than one pulsar in the region given by the LISA sky localisation, one can compare the measured parameters of the system in LISA and the SKA.
+Both the SKA and LISA will measure the orbital frequency to high precision, as well as the time derivative of the frequency and chirp mass to a lesser precision, of each of these systems.
+Therefore, one could perform a targeted search with the SKA that checks the sky location given by LISA, only looking for binary pulsars with orbital frequencies within the uncertainties.
 If there was \textit{still} more than one possible pulsar one could also check against the chirp mass.
-In this way, we expect it will be possible to get a joint detection between SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
+In this way, we expect it will be possible to get a joint detection between the SKA and LISA even when the sky area implied by the LISA detection contains more than one pulsar.
 
@@
 However, the uncertainty in the orbital frequency of a binary on the detection threshold (${\rm SNR} = 7$) for a 4-year LISA mission is $2.5 \times 10^{-9} \unit{Hz}$ and $1.0 \times 10^{-9} \unit{Hz}$ for a 10-year mission (calculated using Eq.~\ref{eq:f_orb_unc}).
-Therefore, we expect that SKA could likely isolate the correct binary pulsar to match to a LISA detection even when several are present in the sky localisation region.
+Therefore, we expect that the SKA could likely isolate the correct binary pulsar to match to a LISA detection even when several are present in the sky localisation region.
 
@@
 
-Our predictions are subject to various uncertainties which can be broadly divided into different categories: (a) those arising from the progenitor models for the population of DCOs and (b) those arising from the choices we have made when placing these DCOs in our model for the Milky-Way.
+Our predictions are subject to various uncertainties which can be broadly divided into two different categories: those arising from the progenitor models for the population of DCOs and those arising from the choices we have made when placing these DCOs in our model for the Milky-Way.
 Although we are unable, at present, to evaluate the impact of all these uncertainties, the reader should nevertheless keep in mind that they are likely very substantial.
@@
 
-\paragraph{Progenitor models (a)} Our binary-star progenitors models have been computed with a rapid population synthesis code (see Sec.~\ref{sec:COMPAS_explained}).
+\paragraph{Progenitor models} Our binary-star progenitors models have been computed with a rapid population synthesis code (see Sec.~\ref{sec:COMPAS_explained}).
 This code relies on approximate parametric prescriptions for the stellar evolutionary tracks of single tracks and simple algorithms to mimic the effects of evolutionary and binary interaction  processes.
@@
 
-\paragraph{Populating the Milky Way (b)} Our Milky Way model is semi-empirical and has been calibrated based on observations.
+\paragraph{Populating the Milky Way} Our Milky Way model is semi-empirical and has been calibrated based on observations.
 Unfortunately, the early evolution of the (metallicity dependence of the) star formation history is poorly constrained.
-We do not expect this to be a major concern, as most of the double compact objects have relatively short delay times of less than 2\,Gyr (see Fig.~\ref{fig:fiducial_pdf_distributions}e), but this is a caveat that should be kept in mind.
+We do not expect this to be a major concern, as most of the double compact objects have relatively short delay times of less than $2 \unit{Gyr}$ (see Fig.~\ref{fig:fiducial_pdf_distributions}e), but this is a caveat that should be kept in mind.
 Furthermore, to estimate the rate of detectable systems, we rely on normalisation choices (e.g.\ how many detectable double compacts are formed per unit of star formation).
 This depends heavily on the initial mass function, as low mass stars account for most of the mass while high mass stars are the progenitors of double compact objects.
-Further choices, such as the binary fraction and the initial distributions of binary parameters also play a lesser but probably still significant role \citet[e.g.\ ][]{deMink+2015, Chruslinska+2017, Klencki+2018}.
+Further choices, such as the binary fraction and the initial distributions of binary parameters also play a lesser but probably still significant role \citet[e.g.][]{deMink+2015, Chruslinska+2017, Klencki+2018}.
 
@@
 
-\subsection{Other formation channels}
+\subsection{Other formation channels}\label{sec:other_formation_channels}
 
@@
 
-We highlight the possible role of dynamical formation in globular clusters \citet[e.g.\ ][]{Kremer+2018}.
+We highlight the possible role of dynamical formation in globular clusters, which was investigated by \citet{Kremer+2018}.
 For a nominal 4-year LISA mission, they estimate 21 sources in total will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}.
@@
 
-In addition, \citet{Banerjee+2020} investigates formation in young massive and open stellar clusters.
+In addition, \citet{Banerjee+2020} investigates formation of LISA detectable BHBHs in young massive and open stellar clusters.
 and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}.

### 2021-11-26 paper/tex/sections/variations.tex
discussion proofread

@@
 The efficiency of mass transfer, i.e.\ the fraction of mass lost by the donor through Roche-lobe overflow that is accreted by the companion, is poorly constrained and is considered as one of the main uncertainties in binary evolution \citep[e.g.][]{deMink+2007}.
-In our fiducial model A, we use a prescription in which the accretion rate onto stellar companions is regulated by their thermal timescale, i.e.\ the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.\ ][]{Schneider+2015}.
+In our fiducial model A, we use a prescription in which the accretion rate onto stellar companions is regulated by their thermal timescale, i.e.\ the timescale on which a star can react to changes and restore thermal equilibrium \citep[see e.g.][]{Schneider+2015}.
 
@@
 This is in part because  the changes in secondary mass and the orbital widening, affect the number of systems for which the reverse interaction successfully ejects the envelope and shrinks the orbit.
-Furthermore, the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS \citep[e.g.\,][]{Zapartas+2017}.
+Furthermore, the increased mass of the secondary stars allows stars that would have otherwise ended their life as a WD to instead become massive enough to form a NS \citep[e.g.][]{Zapartas+2017}.
 The same effect also allows some NS progenitors to become massive enough to become BH progenitors, which partially cancels the extra progenitors that would have originally been destined to become WDs.
@@
 Values smaller than 1 may represent cases where not all energy is used efficiently to unbind the envelope, for example when part of the energy escapes in the form of radiation or if part is used to impart additional kinetic energy in the ejecta \citep[e.g.][]{Ivanova+2013, Nandez+2016}.
-Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion \citep[e.g.\,][]{Schreier+2021}.
+Values larger than 1 may represent cases where additional energy sources can be tapped into, such as for example jets powered by accretion \citep[e.g.][]{Schreier+2021}.
 The variations can also be seen as a way to cover uncertainties in estimates for the binding energy itself.
@@
 This increases the overall number of DCOs.
-(2) The systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources \citep[e.g.\,][]{Klencki+2021}.
+(2) The systems that survive the CE phase are wider, possibly too wide to become detectable as gravitational wave sources \citep[e.g.][]{Klencki+2021}.
 So, while the first consequence favours the formation of DCOs, the second consequence disfavours the formation of DCOs that are tight enough to be detected.

### 2021-11-26 paper/tex/sections/comparisons.tex
comparisons proofread

@@
 We only include papers that are similar to our work, such that they use population synthesis and simulate sources in the Galactic plane.
-Moreover, Fig.~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for these DCOs.
+Moreover, Fig.~\ref{fig:previous_studies} does not include the numerous papers on the LISA WDWD population as we do not make predictions for WDWDs.
 
@@
 Unlike our work, \citet{Sesana+2020} assume that all binaries are circular for the purpose of detection in LISA, which could result in a lower number of detections by missing eccentric binaries that appear as weaker signals when assumed to be circular.
-This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Section~\ref{sec:fiducial_distributions}).
+This is especially relevant as we find that around $\BHBHNotCirc{}$ of LISA detectable BHBHs are not circular and around $\BHBHHighlyEccentric{}$ have significant eccentricity (see Fig.~\ref{fig:fiducial_pdf_distributions}d).
 We also improve upon this work by using a larger number of metallicity bins compared to \citet{Sesana+2020}, since a low number of metallicity bins can produce artificial features in the mass distribution of DCOs and possibly affect the detection rate \citep[see][ and also appendix~\ref{app:mw_changes} for further discussion]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
@@
 They make several different physical assumptions in their population synthesis, using the \citet{Fryer+2012} \textit{rapid} remnant mass prescription, assuming the optimistic CE scenario, limiting the maximum neutron star mass to $2 \unit{M_{\odot}}$ and not implementing PISN.
-However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modRapid{}, \modOpt{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for the differences.
-It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citet{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
+However, we note that none of these assumptions strongly affect the NSNS LISA detection rate (see bottom panel of Fig.~\ref{fig:detection_rates}, models \modOpt{}, \modRapid{}, \modNSLow{} and \modNoPISN{}) and so this is unlikely to entirely account for the differences.
+It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citealt{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
 %

### 2021-11-26 paper/tex/sections/conclusion.tex
conclusion proofread

@@
 
-     \item \textbf{Detections by type:} Specifically, our fiducial model predicts a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs.
+     \item \textbf{Detections by type:} For our fiducial model, we predict a total of $124 \pm 11$ detections and out of these we find about $\BHBHFourYear{}\pm 9$ BHBHs, $\BHNSFourYear{}\pm 6$ BHNSs and $\NSNSFourYear{}\pm 3$ NSNSs.
 The errors quoted here are the $1$-$\sigma$ Poisson uncertainties resulting from the random initialisation of the Milky Way (see Table~\ref{tab:detection_rates}).
 
-    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope phase, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions.
+    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions.
 However, uncertainties related to the efficiency of mass transfer, the remnant mass prescription, the maximum neutron star mass and PISN have little effect on the detection rates (see Fig.~\ref{fig:detection_rates})

### 2021-11-26 paper/combine_tex_files.py
write some quick scripts for prepping for arxiv

@@ -1,0 +1,8 @@
+with open("combined.tex", "w") as combined:
+    with open("tex/paper.tex", "r") as paper:
+        for line in paper:
+            if line.strip()[:7] == "\\input{":
+                with open("tex/" + line.strip()[7:].replace("}", "").replace("\n", ""), "r") as section:
+                    combined.writelines(section.readlines())
+            else:
+                combined.write(line.replace("../figures/", "./figures/"))

### 2021-11-26 paper/create_arxiv_tarball.sh

@@ -1,0 +1,11 @@
+rm -rf arxiv/
+mkdir arxiv
+mkdir arxiv/figures
+cp figures/fig*.pdf arxiv/figures
+cp figures/fig*.png arxiv/figures
+cp ./{tex/*.bst,tex/*.cls,tex/ORCID-ID.png,tex/*.bib} arxiv
+cp bbl.txt arxiv/paper.bbl
+python combine_tex_files.py
+mv combined.tex arxiv/paper.tex
+tar -czvf arxiv.tar.gz arxiv/
+rm -rf arxiv/

### 2021-11-26 paper/tex/paper.tex
update keywords
rename bib file for arxiv
Updates from Overleaf

@@
 
-\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA}}
+\title{{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA}}
 
@@
 \author[0000-0002-6411-8695]{N. Frankel}
-\affiliation{Max Planck Institute for Astronomy, Königstuhl 17, D-69117 Heidelberg, Germany}
+\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, ON M5S 3H8, Canada}
+\affiliation{Max Planck Institute for Astronomy, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
+\affiliation{David A. Dunlap Department for Astronomy and Astrophysics, University
+of Toronto, 50 St. George Street, Toronto, ON M5S 3H4, Canada}
 
@@
 
-\keywords{gravitational waves, LISA, black hole, neutron star, binary stars}
+\keywords{gravitational waves, gravitational wave detectors, compact objects, stellar mass black holes, neutron stars, binary stars, stellar evolution, pulsars}
 

### 2021-11-26 paper/tex/sections/discussion.tex
Updates from Overleaf

@@
 
-We highlight the possible role of dynamical formation in globular clusters, which was investigated by \citet{Kremer+2018}.
-For a nominal 4-year LISA mission, they estimate 21 sources in total will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}.
-In this case, we predict that the sources formed through isolated binary formation will be dominant in nearly every model variation.
+We highlight the possible role of dynamical formation in globular clusters.
+\citet{Kremer+2018} predict, for a nominal 4-year LISA mission, that 21 sources will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}.
+This is significantly lower than the rates we predict for nearly every model variation.
+If true, this would mean that formation through isolated binary formation will dominate the LISA detections.
 
-In addition, \citet{Banerjee+2020} investigates formation of LISA detectable BHBHs in young massive and open stellar clusters.
-and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}.
-Note that this total uses a slightly longer mission length and a lower SNR threshold than those used in this paper.
-Nevertheless, this rate is on the same order as our predictions for LISA BHBHs.
+\citet{Banerjee+2020} investigates formation of LISA detectable BHBHs in young massive and open stellar clusters and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}.
+Although this is similar to the number we predict for our fiducial model, we note these authors adopt a threshold SNR required for a detection that is lower and a mission length is slightly longer than what is typically assumed (i.e.
+SNR $>7$ and 4 years, as we have also adopted in our work).
+We expect that, after correcting for this and making a fair comparison, our fiducial model predicts about twice as many detections.
+
+The contribution of triples systems \citep[e.g.][]{Antonini+2017}, or even higher order multiple systems \citep[e.g.][]{Vynatheya+2021} will likely also be of interest, in particular for the formation of eccentric sources.
+We are, however, not aware of specific predictions for the detection rates that we can compare to directly.

### 2021-11-26 paper/tex/sections/variations.tex
Updates from Overleaf

@@
 In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE.
-Note that this is slightly different from model E from \citet{Broekgaarden+2021}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases).
-We make this change since, otherwise, the model would effectively exclude any systems that evolve through case BB mass transfer and kill nearly all NSNS systems.
+Note that this is slightly different from model E described in  \citet{Broekgaarden+2021}.
+In their work the pessimistic approach to CE evolution is implemented such that all HG stars are excluded including helium stars in the helium shell burning phase.
+This, in combination with the assumption that case BB mass transfer is always unstable, effectively leads to the exclusion of all systems that originate through this channel.
+We are interested in NSNS systems, which are frequently formed through this channel in our simulations.
+Therefore, we adapted this model to only exclude H-rich HG donors, but allow systems with donors that are helium stars in the helium shell burning phase to survive a CE phase.
+
 As expected, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}).

### 2021-11-26 paper/tex/sections/abstract.tex

--- 2021-11-16 paper/tex/sections/abstract.tex
@@
-We present models for the properties of the population of Galactic double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
-We use rapid population synthesis to produce an extensive sample of double compact objects (DCOs) and combine this with a new empirically-informed model to distribute them in a Milky Way-like galaxy based on their birth metallicity.
-We investigate the dependence of our results upon underlying physics assumptions by comparing the results of \nModels{} physics variations that vary assumptions relating to mass transfer, common-envelope, supernova and wind mass loss physics.
-We predict that, on average, for a 4(10)-year mission, LISA will detect about \BHBHFourYear{}(\BHBHTenYear{}) BHBHs, \BHNSFourYear{}(\BHNSTenYear{}) BHNSs, \NSNSFourYear{}(\NSNSTenYear{}) NSNSs.
-The predicted BHBH rate remains notably consistent under most physics assumptions, whilst in contrast the BHNS rate varies widely across all of our assumptions, changing by up to 3 orders of magnitude, and the NSNS rate shows equally strong variations (albeit for a smaller subset of the physics assumptions).
-We show that altering the underlying physics assumptions can lead to contrasting population parameter distributions, even when detection rates are unchanged.
-We discuss observable characteristics that could be used to distinguish the aforementioned DCOs from the more numerous double white dwarf population, as well as for disentangling the BHBH, BHNS and NSNS populations from each other.
-We additionally assess the possibility of multi-messenger observations of pulsar populations by combining the capabilities of LISA and the SKA.
+Future searches for gravitational waves from space will be sensitive to double compact objects (DCOs) in our Milky-Way.
+We present new simulations of the populations of double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
+%
+For our estimates, we use an empirically-informed model of the metallicity dependent star formation history of the Milky Way.
+We populate using an extensive suite of binary population-synthesis predictions for varying assumptions relating to mass transfer, common-envelope, supernova kicks, remnant masses and wind mass loss physics.
+
+For a 4(10)-year LISA mission, we predict between \rangeFourYear{}(\rangeTenYear{}) detections over these variations, out of which 6-154(9-238) are BHBHs, 2-198(3-289) are BHNSs and 3-35(4-57) are NSNSs.
+%
+We discuss how the variations in the physics assumptions alter the distribution of properties of the detectable systems, even when the detection rates are unchanged.
+In particular we discuss the observable characteristics such as the chirp mass, eccentricity and sky localisation and how the BHBH, BHNS and NSNS populations can be distinguished, both from each other and from the more numerous double white dwarf population.
+%
+We further discuss the possibility of multi-messenger observations of pulsar populations with the Square Kilometre Array (SKA) and assess the benefits of extending the LISA mission.

### 2021-11-26 paper/tex/sections/conclusion.tex

@@
 
-    \item \textbf{Physics variations:}  Among the model variations we consider, we find that uncertainties related to the onset and the efficiency of ejection of the common-envelope, the magnitude of natal kicks and the strength of Wolf-Rayet winds each have a strong impact on the rate predictions.
-However, uncertainties related to the efficiency of mass transfer, the remnant mass prescription, the maximum neutron star mass and PISN have little effect on the detection rates (see Fig.~\ref{fig:detection_rates})
+    \item \textbf{Physics variations:}   Among the model variations we consider, we find that our predictions for the rates for the different DCO types are robust within a factor of 2 of the fiducial rate, with the following exceptions.
+For BHBHs, is most sensitive to the treatment of common envelope phases or an increase of the WR wind mass loss.
+For BHNSs and NSNSs, the assumptions regarding the assumed common envelope ejection efficiency, treatment of case BB mass transfer and the kicks are most important.
+In addition, the assumed mass transfer efficiency impacts the BHNS (see Fig.~\ref{fig:detection_rates}).
 

### 2022-01-21 paper/tex/sections/abstract.tex

@@
-Future searches for gravitational waves from space will be sensitive to double compact objects (DCOs) in our Milky-Way.
+Future searches for gravitational waves from space will be sensitive to double compact objects (DCOs) in our Milky Way.
 We present new simulations of the populations of double black holes (BHBHs), black hole neutron stars (BHNSs) and double neutron stars (NSNSs) that will be detectable by the planned space-based gravitational wave detector LISA.
@@
 For our estimates, we use an empirically-informed model of the metallicity dependent star formation history of the Milky Way.
-We populate using an extensive suite of binary population-synthesis predictions for varying assumptions relating to mass transfer, common-envelope, supernova kicks, remnant masses and wind mass loss physics.
+We populate it using an extensive suite of binary population-synthesis predictions for varying assumptions relating to mass transfer, common-envelope, supernova kicks, remnant masses and wind mass loss physics.
 

### 2022-01-21 paper/tex/sections/appendix.tex
update floor citations

@@
 
-In this section we summarise the main assumptions and settings from the population synthesis simulation from Broekgaarden et al.\ (2021a, 2021b).
+In this section we summarise the main assumptions and settings from the population synthesis simulation from \citet{Broekgaarden+2021,Broekgaarden+2021b}.
 
@@
 
-Broekgaarden et al.\ (2021a, 2021b) simulate between 1 and 100 million massive binaries for each of 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
+\citet{Broekgaarden+2021,Broekgaarden+2021b} simulate between 1 and 100 million massive binaries for each of 50 metallicities equally spaced in log space between $Z \in [0.0001, 0.022]$, where $Z$ is the mass fraction of heavy elements.
 They simulate more binaries for higher metallicities so that large enough sample of DCOs at each metallicity (since DCOs are formed at a lower rate at higher metallicities).
@@
 The primary mass, that is the mass of the initially more massive star, is restricted to $m_1 \in [5, 150] \unit{M_{\odot}}$, which spans the range of interest for NS and BH formation in binary systems, and drawn from the \citet{Kroupa+2001} initial mass function (IMF), $p(m_1) \propto m_1^{-2.3}$.
-The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which Broekgaarden et al.\ (2021a, 2021b) assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[e.g.\ consistent with][]{Sana+2012}.
+The secondary mass, $m_2$, is drawn using the initial mass ratio of the binary, $q \equiv m_2 / m_1$, which \citet{Broekgaarden+2021,Broekgaarden+2021b} assume to be uniform on $[0, 1]$, therefore $p(q) = 1$ \citep[e.g.\ consistent with][]{Sana+2012}.
 They additionally restrict the secondary masses $m_2 \ge 0.1 \unit{M_{\odot}}$, which is approximately the minimum mass for a main sequence star.
@@
 
-Broekgaarden et al.\ (2021a, 2021b) apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of their sample.
+\citet{Broekgaarden+2021,Broekgaarden+2021b} apply the adaptive importance sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to improve the yield of their sample.
 This algorithm increases the prevalence of target DCOs (BHBHs, BHNSs and NSNSs in this case) in the sample and assigns each a weight, $w$, which represents the probability of drawing the DCO without STROOPWAFEL in effect.
@@
 
-\textit{Wind mass loss:} Broekgaarden et al.\ (2021a, 2021b) follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
+\textit{Wind mass loss:} \citet{Broekgaarden+2021,Broekgaarden+2021b} follow the wind prescription from \citet{Belczynski+2008}, which was based on results from Monte Carlo radiative transfer simulation of \citet{Vink+2000, Vink+2001}.
 They use the wind mass loss rates from \citet{Vink+2001} for stars above $12500 \unit{K}$ and the rates from \citet{Hurley+2000} for cooler stars.
@@
 
-\textit{Mass Transfer:} In determining the stability of mass transfer Broekgaarden et al.\ (2021a, 2021b) use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
+\textit{Mass Transfer:} In determining the stability of mass transfer \citet{Broekgaarden+2021,Broekgaarden+2021b} use the $\zeta$-prescription, which compares the radial response of the star with the response of the Roche lobe radius to the mass transfer \citep[e.g.][]{Hjellming+1987}.
 The mass transfer efficiency, $\beta \equiv \Delta M_{\rm acc} / \Delta M_{\rm don}$, is the fraction of the mass transferred by the donor that is actually accreted by the accretor.
@@
 
-\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and Broekgaarden et al.\ (2021a, 2021b) parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
+\textit{Common-Envelope:} A common-envelope phase follows dynamically unstable mass transfer and \citet{Broekgaarden+2021,Broekgaarden+2021b} parameterise this using the $\alpha$-$\lambda$ prescription from \citet{Webbink+1984} and \citet{deKool+1990}.
 They assume $\alpha = 1$, such that all of the gravitational binding energy is available for the ejection of the envelope.
@@
 
-\textit{Supernovae:} Broekgaarden et al.\ (2021a, 2021b) draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
+\textit{Supernovae:} \citet{Broekgaarden+2021,Broekgaarden+2021b} draw the remnant masses and natal kick magnitudes from different distributions depending on the type of supernova that occurs.
 For stars undergoing a general core-collapse supernova, they use the \textit{delayed} supernova remnant mass prescription from \citet{Fryer+2012}.
@@
 \subsection{Model variations} \label{sec:variation_assumptions}
-In addition to their fiducial model for the formation of DCOs, Broekgaarden et al.\ (2021a, 2021b) explore \nMinusOneModels{} other models in which they change various aspects of the mass transfer, common-envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
+In addition to their fiducial model for the formation of DCOs, \citet{Broekgaarden+2021,Broekgaarden+2021b} explore \nMinusOneModels{} other models in which they change various aspects of the mass transfer, common-envelope, supernova and wind mass loss physics assumptions in order to assess the effect of their uncertainties on the overall double compact object detection rates and distributions.
 Each of the models varies a single physics assumption (fiducial assumptions are outlined in Section~\ref{app:fiducial_physics}) and these models are outlined in Table~\ref{tab:physics_variations}.
@@
 Models \modRangeCE{} focus on altering the common-envelope physics.
-In model \modCaseBB{} we modify model E from Broekgaarden et al.\ (2021a, 2021b) to investigate the consequence of assuming that case BB mass transfer is always unstable, whilst allowing Helium HG donors to survive CE events.
+In model \modCaseBB{} we modify model E from \citet{Broekgaarden+2021,Broekgaarden+2021b} to investigate the consequence of assuming that case BB mass transfer is always unstable, whilst allowing Helium HG donors to survive CE events.
 They change the common-envelope efficiency parameter to $\alpha_{\rm CE} = 0.1, 0.5, 2.0, 10.0$ in models \modAlphaLowest{}, \modAlphaLow{}, \modAlphaHigh{} and \modAlphaHighest{} respectively.
@@
 
-Finally, in models \modRangeML{} Broekgaarden et al.\ (2021a, 2021b) investigate the effect of changing their assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
+Finally, in models \modRangeML{} \citet{Broekgaarden+2021,Broekgaarden+2021b} investigate the effect of changing their assumption about wind mass loss rates, specifically for Wolf-Rayet winds.
 They vary $f_{\rm WR}$ to $0.1$ and $5.0$ in models \modWRLow{} and \modWRHigh{} respectively.

### 2022-01-21 paper/tex/sections/conclusion.tex
update header
update floor citations

@@
 %
-For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS \citefloorp{}.
+For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS \citep{Broekgaarden+2021,Broekgaarden+2021b}.
 These simulations have been optimised with the adaptive sampling algorithm STROOPWAFEL to preferentially sample NS and BH binaries.
@@
     \item \textbf{Physics variations:} Among the model variations we consider, we find that our predictions for the rates for the different DCO types are robust within a factor of 2 of the fiducial rate, with the following exceptions.
-For BHBHs, is most sensitive to the treatment of common envelope phases or an increase of the WR wind mass loss.
+For BHBHs, the rate is most sensitive to the treatment of common envelope phases or an increase of the WR wind mass loss.
 For BHNSs and NSNSs, the assumptions regarding the assumed common envelope ejection efficiency, treatment of case BB mass transfer and the kicks are most important.

### 2022-01-21 paper/tex/sections/introduction.tex
update floor citations

@@
 We build upon previous efforts but with several important improvements.
-We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters \citefloorp{}.
+We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters \citep{Broekgaarden+2021,Broekgaarden+2021b}.
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).

### 2022-01-21 paper/tex/sections/variations.tex
update floor citations

@@
 In this section we explore the effect of varying the uncertain assumptions governing the evolution of binary system and the formation of compact objects.
-For this we use the population synthesis simulations and model variations presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ 2021b (in prep.).
+For this we use the population synthesis simulations and model variations presented in \citet{Broekgaarden+2021,Broekgaarden+2021b}.
 
@@
 In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE.
-Note that this is slightly different from model E described in  \citet{Broekgaarden+2021}.
+Note that this is slightly different from model E described in \citet{Broekgaarden+2021,Broekgaarden+2021b}.
 In their work the pessimistic approach to CE evolution is implemented such that all HG stars are excluded including helium stars in the helium shell burning phase.

### 2022-01-21 paper/create_arxiv_tarball.sh
minor code updates

@@ -4,6 +4,7 @@ mkdir arxiv/figures
 cp figures/fig*.pdf arxiv/figures
 cp figures/fig*.png arxiv/figures
 cp ./{tex/*.bst,tex/*.cls,tex/ORCID-ID.png,tex/*.bib} arxiv
+cp tex/paper.pdf arxiv/
 cp bbl.txt arxiv/paper.bbl
 python combine_tex_files.py
 mv combined.tex arxiv/paper.tex

### 2022-01-22 paper/tex/sections/introduction.tex
clarify where stellar-mass sources come from
remove sentence about BHNS counterparts

@@
 In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
-Unlike ground-based detectors, LISA only detects stellar-mass sources in local galaxies, with the majority residing in the Milky Way.
+Unlike ground-based detectors, \referee{the majority of stellar-mass sources detected in LISA will reside in local galaxies, with most situated in the Milky Way}.
 These sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.
@@
 Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
-Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts.
-A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
+A distinctly exciting possibility for BHNSs is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
 These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

### 2022-01-22 paper/tex/sections/methods.tex
update floor citations
clarify using 5 highest bins

@@
 
-We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021} and Broekgaarden et al.\ (in prep.).
+We use the grid of \nModels{} binary population synthesis simulations recently presented in \citet{Broekgaarden+2021,Broekgaarden+2021b}.
 This grid of simulations is synthesised using the rapid population synthesis code \href{https://compas.science}{COMPAS} \citep{Stevenson+2017,Vigna-Gomez+2018,Stevenson+2019,Broekgaarden+2019}.
@@
 If the metallicity in $\mathbf{g}_{{j}}$ is below the minimum COMPAS metallicity bin ($Z = 10^{-4}$), we use this minimum bin.
-If the metallicity in $\mathbf{g}_{{j}}$ is above the maximum COMPAS metallicity bin ($Z = 0.03$), we use a randomly selected bin from the five highest metallicity bins.
+If the metallicity in $\mathbf{g}_{{j}}$ is above the maximum COMPAS metallicity bin ($Z = 0.03$), we use a randomly selected bin from the five highest metallicity bins\footnote{\referee{We spread the binaries over the five highest bins, rather than just the highest bin, as we found that using a single bin led to unphysical artifacts in our results.
+These artifacts arose because the small population of binaries in the highest bin were oversampled.}}.
 

### 2022-01-22 paper/tex/sections/methods.tex
specify SNR within mission length

@@
 
-We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio (SNR) of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
+We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio (SNR) of greater than 7 \referee{by the end of the LISA mission} \citep[e.g.][]{Breivik+2020, Korol+2020}.
 The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following \citep[e.g.][]{Finn+2000}

### 2022-01-22 paper/tex/sections/results.tex
missing bracket

@@
 
-BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations.
+BHBHs with unequal masses typically come from progenitors that also had more extreme mass ratios at birth ($90$ and $30\unit{M_{\odot}}$ are typical for the progenitors of detectable BHBH systems in our simulations).
 The primary in such systems experiences strong mass loss by winds before filling its Roche lobe.

### 2022-01-22 paper/tex/sections/discussion.tex
nature may never be apparent, mass ratio not well measured

@@
 \subsection{Identification of GW sources}\label{sec:identify_sources}
-It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately apparent from the gravitational wave signal.
+It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately \referee{(or ever)} apparent from the gravitational wave signal.
 LISA can detect a variety of sources, from exoplanets \citep[e.g.][]{Tamanini+2019} to common-envelopes \citep[e.g.][]{Ginat+2020, Renzo+2021} that may cause confusion.
@@
 
-For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency, mass ratio and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}).
+For separating the BHBH and BHNS population one could do so probabilistically given the properties that are measured, particularly the orbital frequency and eccentricity, since these distributions are fairly different for the two DCO types (see Fig.~\ref{fig:fiducial_pdf_distributions}).
 This method would pose a challenge, however, as it would likely only indicate which type was more likely rather than discriminate between them with strong evidence.

### 2022-01-22 paper/tex/sections/comparisons.tex
split Lau paragraph
fix Breivik+20 numbers

@@
 It is also important to highlight that COMPAS has received several improvements and bug fixes since \citet{Vigna-Gomez+2018} (which contains the simulations used by \citealt{Lau+2020}) and these could possibly have affected the formation rate of NSNSs.
-%
+
 Yet it is most likely that the remaining difference between our results is due to way in which we simulate the Milky Way.
@@
 \paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
-They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
+They find that LISA will detect \referee{72 BHBHs, 19 BHNSs and 10 NSNSs} in the Milky Way over a 4 year mission.
 \citet{Breivik+2020} make many physical assumptions that differ from our fiducial model, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{app:mw_changes}).
@@
 This results in 97, 101 and 43 detections for BHBHs, BHNSs and NSNSs respectively.
-Therefore, though we are in very good agreement for BHBHs, we predict much higher rates for BHNSs and NSNSs.
+\referee{Therefore, though our BHBH rates agree reasonably well, we predict much higher rates for BHNSs and NSNSs}.
 These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS.

### 2022-01-22 paper/tex/sections/appendix.tex
missions are space-based

@@
 
-Here we describe how we estimate the uncertainty of the chirp mass . First, consider the chirp mass, which can be expressed as
+Here we describe how we estimate the uncertainty of the chirp mass. First, consider the chirp mass, which can be expressed as
 \begin{equation}
@@
 where $\rho$ is the signal-to-noise ratio and $T_{\rm obs}$ is the LISA mission length.
-We estimate the eccentricity certainty, $\Delta e$, following the methods of \citet{Lau+2020} and \citet{Korol+2021}, which use the relative SNRs of different harmonics to work out the eccentricity.
+We estimate the eccentricity uncertainty, $\Delta e$, following the methods of \citet{Lau+2020} and \citet{Korol+2021}, which use the relative SNRs of different harmonics to work out the eccentricity.
 We propagate this uncertainty such that
@@
 Next, we can find the total number of pulsars SKA will detect in a patch on the sky.
-The total sky area that the SKA mission covers is approximately $5700 \unit{deg^2}$, which is calculated by integrating over the sky for all Galactic longitudes and Galactic latitudes limited to $\abs{b} < 10^\circ$ and $\delta < 45^\circ$, which are the limits on SKA-mid \citep{Keane+2015}.
+The total sky area that the SKA covers is approximately $5700 \unit{deg^2}$, which is calculated by integrating over the sky for all Galactic longitudes and Galactic latitudes limited to $\abs{b} < 10^\circ$ and $\delta < 45^\circ$, which are the limits on SKA-mid \citep{Keane+2015}.
 If we assume that the pulsars are found uniformly across the sky, this means that roughly $0.2$ and $0.7$ binary pulsars are expected per square degree for SKA-1 and SKA-2 respectively.

### 2022-03-17 paper/tex/sections/abstract.tex
Updates from Overleaf

@@
 %
-We discuss how the variations in the physics assumptions alter the distribution of properties of the detectable systems, even when the detection rates are unchanged.
-In particular we discuss the observable characteristics such as the chirp mass, eccentricity and sky localisation and how the BHBH, BHNS and NSNS populations can be distinguished, both from each other and from the more numerous double white dwarf population.
+\edit1{We expect that about 50\%(60\%) can be  distinguished from WDWD sources, based on their mass or eccentricity and localisation.
+Specifically, for about 10\%(15\%) we expect to be able to determine chirp masses better than 10\%.
+For 13\%(13\%) we expect sky-localisations better than 1 degree.
 %
-We further discuss the possibility of multi-messenger observations of pulsar populations with the Square Kilometre Array (SKA) and assess the benefits of extending the LISA mission.
+We discuss the impact of physics variations and prospects for probing the NS-BH mass gap.}  We further discuss the possibility of multi-messenger observations of pulsar populations with the Square Kilometre Array (SKA) and assess the benefits of extending the LISA mission.

### 2022-03-17 paper/tex/sections/introduction.tex
add sentence about GR tests with PSR+BH
Updates from Overleaf

--- 2022-01-21 paper/tex/sections/introduction.tex
@@
 However, with only two detections (not including the low-confidence candidate GW190426, \citealt{Abbott+2020_GWTC2}, or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs, \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
-Current predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Mandel+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars.
 Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts.
@@
 We present the main results for our fiducial model in Section~\ref{sec:results}, before exploring the variations in the detectable population when changing our physical assumptions in Section~\ref{sec:variations}.
-In Section~\ref{sec:discussion} we discuss these results.
-In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.
+\edit1{In Section~\ref{sec:discussion} we discuss these how and whether these sources can be distinguished from the WDWD population and whether the subpopulations of NSNS, BHNS and BHBH can be distinguished from each other.
+We further discuss prospects for identifying EM counterparts, the role of different formation channels and overall caveats in the modelling approach.
+}In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2022-03-17 paper/tex/sections/methods.tex
Updates from Overleaf

--- 2021-11-25 paper/tex/sections/methods.tex
@@
 
-The star formation history of the Milky Way bulge (which we assume here to be dominated by the central bar) has many uncertainties due to the (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms that are still under debate.
-However, the central bar was shown to contain stars with an extended age range, with most observed stars between $6$ and $12 \unit{Gyr}$ with a younger tail of ages that could come from the subsequent secular growth of the Galactic bar \citep[e.g.,][]{Bovy+2019}.
-To model the bar's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+The star formation history of the bulge/bar of the Milky Way has many uncertainties due to the (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms that are still under debate.
+However, the central bar (which we assume here to dominate) was shown to contain stars with an extended age range, with most observed stars between $6$ and $12 \unit{Gyr}$ with a younger tail of ages that could come from the subsequent secular growth of the Galactic bar \citep[e.g.,][]{Bovy+2019}.
+To model the bar/bulge's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
 We show these distributions in the top left panel of Fig.~\ref{fig:galaxy_schematic}.
@@
 This scale length accounts for the inside-out growth of the low-\achem~disc and hence is age dependent.
-We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-\achem~disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bar component \citep{Bovy+2019}.
-We show the combination of these distributions in the second panel on the left in Fig.~\ref{fig:galaxy_schematic}.
+We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-\achem~disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bulge/bar component \citep{Bovy+2019}.
+\edit1{Note that in this way we approximate the bulge/bar component as being axi-symmetric, which is sufficient for our purposes.} We show the combination of these distributions in the second panel on the left in Fig.~\ref{fig:galaxy_schematic}.
 
@@
 We set $z_d = 0.3 \unit{kpc}$ for the low-\achem~disc \citep{McMillan+2011} and $z_d = 0.95 \unit{kpc}$ for the high-\achem~disc \citep{Bovy+2016}.
-For the bar, we set $z_d = 0.2 \unit{kpc}$ \citep{Wegg+15}.
+For the bulge/bar, we set $z_d = 0.2 \unit{kpc}$ \citep{Wegg+15}.
 We show the combination of these distributions in the bottom left panel of Fig.~\ref{fig:galaxy_schematic}.

### 2022-03-17 paper/tex/sections/discussion.tex

@@
 In light of the other much larger uncertainties, we felt that this was justified (see however, e.g., \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
-We have further ignored a possible contribution coming from the Galactic halo, as \citet{Lamberts+2018} estimates this not be significant.
+\referee{We have further ignored a possible contribution coming from the Galactic halo, as \citet{Sesana+2020} estimates this is not significant compared to the contributions from the Galactic bulge and discs}.
 However, this may not be true for other formation channels other than those we have considered here.

### 2022-03-17 paper/tex/sections/introduction.tex

@@
 However, with only two detections (not including the low-confidence candidate GW190426, \citealt{Abbott+2020_GWTC2}, or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs, \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain.
-Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts.
-A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
+A distinctly exciting possibility for BHNSs is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}.
 These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.
+\edit1{Moreover, the pulsar acts as an ultraprecise clock around a BH and thus a pulsar--BH system provides stringent tests of theories of gravity \citep{Keane+2015}.}
 

### 2022-03-17 paper/tex/sections/comparisons.tex
further updates after review

--- 2021-11-26 paper/tex/sections/comparisons.tex
@@
 \paragraph{\citet{Breivik+2020}} introduced the population synthesis code COSMIC and presented detections for many different DCO types in LISA using this code.
-They find that LISA will detect 93 BHBHs, 33 BHNSs and 8 NSNSs in the Milky Way over a 4 year mission.
+They find that LISA will detect \edit1{72 BHBHs, 19 BHNSs and 10 NSNSs} in the Milky Way over a 4 year mission.
 \citet{Breivik+2020} make many physical assumptions that differ from our fiducial model, the most notable being that they assume the optimistic CE scenario and that case BB mass transfer is always unstable, whilst also using a simpler model for the Milky Way (see Appendix~\ref{app:mw_changes}).
@@
 This results in 97, 101 and 43 detections for BHBHs, BHNSs and NSNSs respectively.
-Therefore, though we are in very good agreement for BHBHs, we predict much higher rates for BHNSs and NSNSs.
+\edit1{Therefore, though our BHBH rates agree reasonably well, we predict much higher rates for BHNSs and NSNSs}.
 These differences are likely due to using a different population synthesis code (COSMIC), which has different underlying physics assumptions from COMPAS.

### 2022-03-17 paper/tex/sections/discussion.tex
further updates after review

--- 2022-01-22 paper/tex/sections/discussion.tex
@@
 \subsection{Identification of GW sources}\label{sec:identify_sources}
-It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately \referee{(or ever)} apparent from the gravitational wave signal.
+It is important to note that, though we present predictions for the detection rates of specific DCO types, the nature of the source may not be immediately \edit1{(or ever)} apparent from the gravitational wave signal.
 LISA can detect a variety of sources, from exoplanets \citep[e.g.][]{Tamanini+2019} to common-envelopes \citep[e.g.][]{Ginat+2020, Renzo+2021} that may cause confusion.
@@
 In light of the other much larger uncertainties, we felt that this was justified (see however, e.g., \citealt{Brandt+1995, Abbott+2017_GW170817_progenitor}).
-We have further ignored a possible contribution coming from the Galactic halo, as \citet{Lamberts+2018} estimates this not be significant.
+\edit1{We have further ignored a possible contribution coming from the Galactic halo, as \citet{Sesana+2020} estimates this is not significant compared to the contributions from the Galactic bulge and discs}.
 However, this may not be true for other formation channels other than those we have considered here.

### 2022-03-17 paper/tex/sections/introduction.tex
further updates after review

@@
 In addition, LISA will be able to measure the eccentricities of DCOs, which may yield further constraints on binary evolution, differentiate between formation channels and distinguish between DCO types \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}.
-Unlike ground-based detectors, \referee{the majority of stellar-mass sources detected in LISA will reside in local galaxies, with most situated in the Milky Way}.
+Unlike ground-based detectors, \edit1{the majority of stellar-mass sources detected in LISA will reside in local galaxies, with most situated in the Milky Way}.
 These sources could be used as a probe for the structure of our galaxy \citep[e.g.][]{Korol+2019}.

### 2022-03-17 paper/tex/sections/methods.tex
further updates after review

--- 2022-03-17 paper/tex/sections/methods.tex
@@
 If the metallicity in $\mathbf{g}_{{j}}$ is below the minimum COMPAS metallicity bin ($Z = 10^{-4}$), we use this minimum bin.
-If the metallicity in $\mathbf{g}_{{j}}$ is above the maximum COMPAS metallicity bin ($Z = 0.03$), we use a randomly selected bin from the five highest metallicity bins.
+If the metallicity in $\mathbf{g}_{{j}}$ is above the maximum COMPAS metallicity bin ($Z = 0.03$), we use a randomly selected bin from the five highest metallicity bins\footnote{\edit1{We spread the binaries over the five highest bins, rather than just the highest bin, as we found that using a single bin led to unphysical artifacts in our results.
+These artifacts arose because the small population of binaries in the highest bin were oversampled.}}.
 
@@
 
-We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio (SNR) of greater than 7 \citep[e.g.][]{Breivik+2020, Korol+2020}.
+We define a binary as detectable if its gravitational wave signal has a signal-to-noise ratio (SNR) of greater than 7 \edit1{by the end of the LISA mission} \citep[e.g.][]{Breivik+2020, Korol+2020}.
 The sky-, polarisation- and orientation-averaged signal-to-noise ratio, $\rho$, of an inspiraling binary can be calculated with the following \citep[e.g.][]{Finn+2000}

### 2022-07-06 paper/tex/sections/abstract.tex
Updates from Overleaf

@@
 We populate it using an extensive suite of binary population-synthesis predictions for varying assumptions relating to mass transfer, common-envelope, supernova kicks, remnant masses and wind mass loss physics.
+\edit1{Each model in the grid has been recently shown to be consistent with current constraints on the inferred overall GW rates from ground-based detectors.}
 
@@
 Specifically, for about 10\%(15\%) we expect to be able to determine chirp masses better than 10\%.
-For 13\%(13\%) we expect sky-localisations better than 1 degree.
-%
-We discuss the impact of physics variations and prospects for probing the NS-BH mass gap.}  We further discuss the possibility of multi-messenger observations of pulsar populations with the Square Kilometre Array (SKA) and assess the benefits of extending the LISA mission.
+For 13\%(13\%) we expect sky-localisations better than 1 degree.} We discuss how the variations in the physics assumptions alter the distribution of properties of the detectable systems, even when the detection rates are unchanged.
+We further discuss the possibility of multi-messenger observations of pulsar populations with the Square Kilometre Array (SKA) and assess the benefits of extending the LISA mission.

### 2022-07-06 paper/tex/sections/introduction.tex
Updates from Overleaf

@@
 These detections have observed BHs with masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to contain at least one BH with a mass greater than $10 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}.
-These observations of X-ray binaries suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which there are no strong candidates for either black holes or neutron stars \citep{Ozel+2010,Farr+2011} but the gap's existence remains an open question \citep[e.g.][]{Kreidberg+2012, Mandel+2020}.
+These observations of X-ray binaries suggest the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which there are no strong candidates for either black holes or neutron stars \citep{Ozel+2010,Farr+2011} but the gap's existence remains an open question \edit1{\citep[e.g.][]{Kreidberg+2012, Mandel+2020, Jayasinghe+2021}}.
 Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019} which has subsequently been challenged (\citealp{El-Badry+2020, Abdul-Masih+2020, Shenar+2020,Eldridge+2020}, see also \citealp{Liu+2020}) and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}.
@@
 We build upon previous efforts but with several important improvements.
-We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models and comparing the effects on the detection rate and distributions of source parameters \citep{Broekgaarden+2021,Broekgaarden+2021b}.
+We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models\edit1{, which have each been shown to be consistent with constraints on the inferred overall GW rates from ground-based detectors,} and comparing the effects on the detection rate and distributions of source parameters \citep{Broekgaarden+2021,Broekgaarden+2021b}.
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
@@
 We present the main results for our fiducial model in Section~\ref{sec:results}, before exploring the variations in the detectable population when changing our physical assumptions in Section~\ref{sec:variations}.
-\edit1{In Section~\ref{sec:discussion} we discuss these how and whether these sources can be distinguished from the WDWD population and whether the subpopulations of NSNS, BHNS and BHBH can be distinguished from each other.
-We further discuss prospects for identifying EM counterparts, the role of different formation channels and overall caveats in the modelling approach.
-}In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.
+\edit1{In Section~\ref{sec:discussion} we discuss these how and whether these sources can be distinguished from the WDWD population and whether the subpopulations of NSNS, BHNS and BHBH can be distinguished from one other.
+We further discuss prospects for identifying EM counterparts, the role of different formation channels and overall caveats in the modelling approach.} In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2022-07-06 paper/tex/sections/methods.tex
Updates from Overleaf

@@
 The code is open source and documented in the papers listed above, the online documentation\footnote{\url{https://compas.science}} and in the methods paper \citep{COMPAS:2021methodsPaper}.
+\edit1{The model we refer to as our fiducial model allows for BHs with masses in the heavily debated mass gap, but we also consider \nModels{} physics variations.
+\citet{Broekgaarden+2021b} showed that all of these physics variations are still consistent with current constraints on the overall inferred GW rates, at least when considering large variations of the assumed metallicity specific cosmic star formation rate \citep{Abbott+2021_GWTC3}}.
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
@@
 Those authors developed this relation in order to measure the global efficiency of radial migration in the Milky Way and calibrated it using a sample of red clump stars measured with APOGEE \citep{Majewski+2017}.
+\edit1{We assess the impact of using this improved Milky Way model in Appendix~\ref{app:mw_changes} and the effect of Galactic models on LISA predictions has been investigated more generally in \citet{Storck+2022}}.
 
@@
 
-Our model for the Milky Way accounts for the low-\achem\footnote{Nomenclature used to describe the enhancement of $\alpha$ elements compared to iron in stellar atmospheres}~disc, high-\achem~disc and a central component approximating a bar/bulge.
+Our model for the Milky Way accounts for the low-\achem\footnote{Nomenclature used to describe the enhancement of $\alpha$ elements compared to iron in stellar atmospheres}~disc, high-\achem~disc and a central component approximating a bulge/bar.
 The low- and high-\achem~discs are often also referred to as the thin and thick discs because the stellar vertical distribution is better fit by a double exponential rather than a single one.
@@
 The star formation history of the bulge/bar of the Milky Way has many uncertainties due to the (1) sizeable age measurement uncertainties at large ages in observational studies, (2) complex selection processes affecting the observed age distributions, and (3) formation mechanisms that are still under debate.
-However, the central bar (which we assume here to dominate) was shown to contain stars with an extended age range, with most observed stars between $6$ and $12 \unit{Gyr}$ with a younger tail of ages that could come from the subsequent secular growth of the Galactic bar \citep[e.g.,][]{Bovy+2019}.
-To model the bar/bulge's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
+However, the central bar (which we assume to dominate here) was shown to contain stars with an extended age range, with most observed stars between $6$ and $12 \unit{Gyr}$ with a younger tail of ages that could come from the subsequent secular growth of the Galactic bar \citep[e.g.,][]{Bovy+2019}.
+To model the bulge/bar's age distribution more realistically than in previous studies (which assume an old bulge coming from a single starburst), we choose to adopt a more extended star formation history using a $\beta(2,3)$ distribution, shifted and scaled such that stars are only formed in the range $[6, 12] \unit{Gyr}$.
 We show these distributions in the top left panel of Fig.~\ref{fig:galaxy_schematic}.
@@
 We assume $R_d = (1 / 0.43) \unit{kpc}$ for the high-\achem~disc \citep[][Table~1]{Bovy+2016} and $R_d = 1.5 \unit{kpc}$ for the bulge/bar component \citep{Bovy+2019}.
-\edit1{Note that in this way we approximate the bulge/bar component as being axi-symmetric, which is sufficient for our purposes.} We show the combination of these distributions in the second panel on the left in Fig.~\ref{fig:galaxy_schematic}.
+\edit1{Note that in this way we have approximated the bulge/bar component as being axi-symmetric, which is sufficient for our purposes.} We show the combination of these distributions in the second panel on the left in Fig.~\ref{fig:galaxy_schematic}.
 

### 2022-07-06 paper/tex/sections/results.tex
Updates from Overleaf

@@
 As mentioned in Sec.~\ref{sec:dcos_on_sc}, this is because a higher mass DCO at the same distance and eccentricity requires a lower frequency to produce the same signal-to-noise ratio and thus be detected.
-The distributions appear nearly symmetric, but closer inspections shows that the left hand side is more populated, which can be seen most clearly in the curve for the BHBHs.
+The distributions appear nearly symmetric, \edit1{but the left tail of the distribution is more populated, especially} for the BHBHs.
 This is due to the contribution of highly eccentric binaries, which are most abundant in the BHBH population.
@@
 The shaded areas show the 1- and 2-$\sigma$ sampling uncertainties (obtained via bootstrapping).
-The dotted lines in panel b show the individual primary and secondary mass distributions.
 The dotted line in panel e shows the star formation history we have assumed in our Milky Way model.
@@
 \paragraph{Black Hole Mass}
-In Fig.~\ref{fig:fiducial_pdf_distributions}b, we show the distribution masses of individual black holes that are part of BHNS and BHBH systems. 
-The distribution for BHBH shows a bimodality.
-This results from the two contributions of the more and less massive BHs in BHBH systems, which peak at around $8 \unit{M_{\odot}}$ and $3.5 \unit{M_{\odot}}$ respectively as shown by the dotted lines (see also our discussion of the mass ratios below).
+In Fig.~\ref{fig:fiducial_pdf_distributions}b, we show the distribution of \edit1{primary} black hole masses for BHNS and BHBH systems.
+\edit1{The BHNS distribution shows a bimodality.
+This is due to the bimodal mass ratio distribution (see Fig.~\ref{fig:fiducial_pdf_distributions}c) since most NS components have approximately the same mass.}
 
 For both the BHBHs and BHNSs, we see that the black hole mass distribution favours low masses.
-About $90\%$ of BHs have masses below $11 \unit{M_{\odot}}$, in our fiducial simulations shown here.
-This is in stark contrast with observations from ground-based GW detectors, where heavy BHs with masses of about $30\unit{M_{\odot}}$ and higher have been common.
+About $90\%$ of BHs have masses below $12 \unit{M_{\odot}}$, in our fiducial simulations shown here.
+This is in contrast with observations from ground-based GW detectors, where heavy BHs with masses of about $30\unit{M_{\odot}}$ and higher have been common.
 There are two main reasons for this discrepancy.
@@
 Secondly, ground-based detectors are strongly biased towards high mass systems, since they can be detected out to larger distances and thus a greater volume is probed.
-In contrast, LISA has no such bias and is, in principle, sensitive to inspiraling BHBHs throughout the entire Milky Way regardless of their mass, as long as we catch them when they are emitting in the LISA band.
-For this reason, LISA is more likely to detect the more common lower mass BHBHs.
+In contrast, LISA has no such bias and is, in principle, sensitive to inspiraling DCOs throughout the entire Milky Way regardless of their mass, as long as we catch them when they are emitting in the LISA band.
+For this reason, LISA is more likely to detect the more common lower mass DCOs.
 
@@
 In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$.
-We find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this.
+We find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this\edit1{, though we still would not expect a significant number of detections at higher mass ratios since the intrinsic merging BHBH population tends to have less equal mass ratios \citep[e.g.][Fig.~8]{vanSon+2021}}.
 
@@
 By the time the primary fills its Roche lobe, it has become less massive and the mass ratio is closer to one.
-This favours stable mass transfer.
+This favours stable mass transfer\edit1{ and most detectable BHBHs form through stable mass transfer (see Section.~\ref{sec:progenitors_and_formation})}.
 The massive core of the primary star typically becomes the more massive BH.
@@
 This results in increase of the inspiral time by a factor of about 4000:80:1.
+
+\edit1{The distribution of separations at DCO formation is also the reason that the time since formation for NSNSs shows a bimodality.
+For NSNSs, the separation at DCO formation peaks around $2 \times 10^{-2} \unit{AU}$ but the distribution has a second population that extends to much lower separations relative to the the BHNS and BHBH distributions.
+It is this population of shorter separations that corresponds to the NSNSs that were formed more recently (within the last 100 Myr).}
+
 The total masses affect the inspiral time to the third power and this where the heavier BHBH systems are favoured.
@@
 \subsection{Formation channels}\label{sec:progenitors_and_formation}
-In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel, whilst the remaining third are primarily formed through the `classic' CE channel.
+In our fiducial model, approximately two thirds of detectable BHBHs are formed through the `only stable mass transfer' channel, whilst the remaining third are primarily formed through the `classic' CE channel \edit1{, in which the first phase of mass transfer is stable whilst the second is unstable and results in a common-envelope event}.
 Detectable BHNSs follow an inverse pattern, such that around two thirds are formed through the classic channel and the rest are mainly formed through only stable mass transfer.

### 2022-07-06 paper/tex/sections/variations.tex
Updates from Overleaf

@@
 
-Nearly all systems that can be detected form through channels where the very first interaction is stable mass transfer.
-Generally, higher mass transfer efficiencies lead to higher masses for the accreting stars, but also leads to wider orbits \citep{Soberman+1997, vanSon+2020}.
+Since nearly all systems that can be detected form through channels where the very first interaction is stable mass transfer, changing $\beta$ can affect the majority of systems.
+Generally, higher mass transfer efficiencies lead to higher masses for the accreting stars, but also lead to wider orbits \citep{Soberman+1997, vanSon+2020}.
 Changing $\beta$ thus already affects the masses and orbital separation after the first interaction phase, which in turn changes the starting conditions and outcome of all subsequent interactions phases.
@@
 The left axis and grid lines show the number of detections in a 4-year LISA mission and the right axis shows an approximation of the number of detections in a 10-year mission (we scale the axis by $\sqrt{T_{\rm obs}}$, see Table~\ref{tab:detection_rates} for exact rates).
-Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
+\edit1{The grey shaded regions indicate the 1- and 2-$\sigma$ region for the fiducial model.} Each model is described in further detail in Table~\ref{tab:physics_variations} and details of the fiducial assumptions are in Section~\ref{app:fiducial_physics}.
 See Sec.~\ref{sec:detection_rate_analysis} for a discussion.
@@
 
-\subsubsection{Using LISA to investigate the lower mass gap}\label{sec:lower_mass_gap}
+\subsubsection{Effect of remnant mass prescription on lower mass gap}\label{sec:lower_mass_gap}
 
@@
 From the stark difference between these models, it is clear that it is difficult at this point to say with any certainty what fraction of systems LISA will detect in the lower mass gap given the highly uncertain formation rate of systems in this mass range.
-Indeed, we find that the percentage of detectable systems with at least one component in the lower mass gap varies between approximately 30-70\% (or, in terms of detections, from 15 to 156) for the different model variations.
-However, it is important to highlight that \textit{if} DCOs are formed with components in the lower mass gap, LISA \textit{will} be able to detect them.
-And thus, LISA could be a useful instrument for providing constraints on the existence or non-existence of a lower mass gap based on the mass distribution of detected DCOs.
+
+We find that the percentage of detectable systems with at least one component in the lower mass gap varies between approximately 30-70\% (or, in terms of detections, from 15 to 156) for the different model variations that we consider, except for model \modRapid{}, for which it is 0\%.
+\edit1{We note however that the masses of detectable systems are not always well constrained (see Section~\ref{sec:measurement_uncertainties}).
+It may therefore be difficult to assess whether a detected system truly has components in the mass gap.}
+
+\edit1{Lastly, we highlight that recent investigations of the GW detections so far suggest a significant reduction of BHs in the lower mass gap \citep[e.g.
+][van Son et al.\ in prep.]{Farah+2021, Ye+2022}.
+All our models except model \modRapid{} allow for systems in the mass gap, which may be at tension with the observational constraints so far.}
 

### 2022-07-06 paper/tex/sections/conclusion.tex

@@
 %
-For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS \citep{Broekgaarden+2021,Broekgaarden+2021b}.
-These simulations have been optimised with the adaptive sampling algorithm STROOPWAFEL to preferentially sample NS and BH binaries.
-In total these comprise over two billion massive binaries that span 20 physics variations, which represent the most common uncertainties in binary physics.
+For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS\edit1{, which can reproduce the current constraints on the overall GW rates \citep{Broekgaarden+2021,Broekgaarden+2021b, Abbott+2021_GWTC3}}.
+Our suite of simulations consider 20 physics variations, which represent the most common uncertainties in binary physics.
 %
-To determine the detectability of sources with LISA we use the LEGWORK package \citep{Wagg+2021}, that was specifically developed for this purpose and is publicly available. 
+We investigate the detectability of sources in the planned space-based GW detector LISA using the LEGWORK package \citep{Wagg+2021}, that we specifically developed for this purpose and is publicly available.
 %
@@
 
-    \item \textbf{Probing the black hole mass distribution and the lower mass gap:} We expect LISA to predominantly detect lower mass BHs (with 90\% of BHBH and BHNSs having BH masses lower than $11 \unit{M_\odot}$ in our fiducial simulations) in stark contrast to current ground-based detectors which are heavily biased towards high mass systems.
-For our fiducial simulation, we predict that approximately 69 systems with a component with a mass between $2.5$-$5 \unit{M_\odot}$ would be detected by a 4-year LISA.
-This implies that LISA can potentially make important contributions to the debate about the existence of a lower mass gap (see Fig.~\ref{fig:lower_mass_gap_variation}).
+    \item \textbf{Probing the black hole mass distribution and the lower mass gap:} We expect LISA to predominantly detect lower mass BHs (with 90\% of BHBH and BHNSs having BH masses lower than $11 \unit{M_\odot}$ in our fiducial simulations).
+This is in stark contrast to current ground-based detectors which are heavily biased towards high mass systems, since they can be detected out to larger distances.
+We predict that between 15-156 systems with a component with a mass between $2.5$-$5 \unit{M_\odot}$ would be detected by a 4-year LISA, for our different physics variations.
+An exception is model using the Fryer Rapid remnant mass prescription, which produces none.
+However, it will likely be hard for LISA data to make a significant impact on this debate on the existence of the lower mass gap given the uncertainty of the individual masses (see Fig.~\ref{fig:lower_mass_gap_variation}).
 

### 2022-07-06 paper/tex/sections/discussion.tex

@@
 In addition to our limited understanding of massive stars, we note that the rapid population synthesis code, such as the one employed to compute the models used in this study, rely on extrapolations of the original fitting formulae to approximate the evolutionary tracks for these higher mass progenitors \citep{Hurley+2000,Hurley+2002}.
+\edit1{A further caveat is whether the population synthesis predictions used in our study realistically describe the population of compact objects.
+\citet{Broekgaarden+2021b} shows that none of the physics variations that we use can be excluded at present based on the overall constraints on the GW rates, but this does not mean that they are accurate.
+For example, at present it is unclear whether these models reproduce the features in the inferred mass distribution \citep[van Son et al.\ in prep.][]{Farah+2021,TheLIGOScientificCollaboration+2021,Li+2021,Veske+2021,Tiwari2022,Edelman+2022}.}
 

### 2022-07-06 paper/tex/sections/appendix.tex
forgot to change one figure

@@
 By using only two fixed metallicity populations, unphysical artifacts are introduced into distribution of DCO masses \citep[e.g.][]{Dominik+2015, Neijssel+2019, Kummer_thesis}.
-For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution produced by the simulation using the simple Milky Way model.
+For example, in Fig.~\ref{fig:bh_mass_simple_mw}, we show the black hole mass distribution \edit1{for BHNSs} produced by the simulation using the simple Milky Way model.
 Despite the fact that these KDEs use the same bandwidth as Fig.~\ref{fig:fiducial_pdf_distributions}, the distributions show many more sharp transitions, which is a result of pileups occurring at specific masses for specific metallicities.

### 2022-07-29 paper/tex/sections/introduction.tex
Updates from Overleaf

@@
 We build upon previous efforts but with several important improvements.
-We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models\edit1{, which have each been shown to be consistent with constraints on the inferred overall GW rates from ground-based detectors,} and comparing the effects on the detection rate and distributions of source parameters \citep{Broekgaarden+2021,Broekgaarden+2021b}.
+We explore the effects of varying binary physics assumptions by repeating our analysis for \nModels{} different models \citep{Broekgaarden+2021,Broekgaarden+2021b}
+%\edit1{, which were shown to be consistent with constraints on the inferred overall GW rates from ground-based detectors GWTC-2 that were available at the time when we started this work,} 
+and we compare the effects on the detection rate and distributions of source parameters.
 We use a model for the Milky Way that accounts for the chemical enrichment history and is calibrated on the APOGEE survey \citep{Majewski+2017,Frankel+2018}, whereas most others did not consider the effect of metallicity in detail (see however \citealp{Lamberts+2019, Sesana+2020}).
@@
 In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper.
-In a companion paper, \citet{Wagg+2021}, we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
+In a companion paper, \citet{LEGWORK_apjs}, we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, the \textbf{L}ISA \textbf{E}volution and \textbf{G}ravitational \textbf{W}ave \textbf{Or}bit \textbf{K}it, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.
 
@@
 We present the main results for our fiducial model in Section~\ref{sec:results}, before exploring the variations in the detectable population when changing our physical assumptions in Section~\ref{sec:variations}.
-\edit1{In Section~\ref{sec:discussion} we discuss these how and whether these sources can be distinguished from the WDWD population and whether the subpopulations of NSNS, BHNS and BHBH can be distinguished from one other.
+\edit1{In Section~\ref{sec:discussion} we discuss how and whether these sources can be distinguished from the WDWD population and whether the subpopulations of NSNS, BHNS and BHBH can be distinguished from one other.
 We further discuss prospects for identifying EM counterparts, the role of different formation channels and overall caveats in the modelling approach.} In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.

### 2022-07-29 paper/tex/sections/results.tex
Updates from Overleaf

@@
 
-In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$.
-We find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this\edit1{, though we still would not expect a significant number of detections at higher mass ratios since the intrinsic merging BHBH population tends to have less equal mass ratios \citep[e.g.][Fig.~8]{vanSon+2021}}.
+In contrast, only $\BHBHqAbovePointEight{}$ of detectable BHBHs are formed with $q > 0.8$ and the distribution peaks around $q = 0.4$\edit2{, we find that the strong stellar winds in our (typically high-metallicity) progenitors are the reason behind this, as we will discuss below.
+However, we note that the preference for unequal mass ratios is possibly at tension with the current inferred distribution from GWTC-3, which prefers equal masses \citep[][Fig.~10]{Abbott+2021_GWTC3}.
+The population detectable by ground-based detectors and the population to which LISA is sensitive may differ, for example because of difference in the underlying metallicity-specific star formation history or due to the lower masses of the LISA detectable systems, but it is unclear if this is sufficient to explain the discrepancy.}
 

### 2022-07-29 paper/tex/paper.tex
update floor citations
define referee command
clarify where stellar-mass sources come from
further updates after review

@@
-\documentclass[twocolumn, twocolappendix]{aastex63}
+\documentclass[twocolumn, twocolappendix, linenumbers]{aastex63}
 \received{\today}
@@
 
-\newcommand{\citefloorp}{(\citealt{Broekgaarden+2021}, Broekgaarden et al.\ (in prep.))}
-
 \newcommand{\confinv}[3]{$#1${\raisebox{0.5ex}{\tiny$_{-#2}^{+#3}$}}}
@@
 
-\acknowledgments{We thank Katie Brevik, Will Farr, Rob Farmer, Valeriya Korol, Floris Kummer, Eva Laplace, Mike Lau, Tyson Littenberg, Ilya Mandel, Mathieu Renzo, Alberto Sesana, Katie Sharpe, Simon Stevenson, the CCA GW group and COMPAS collaboration for insightful discussions.
+\acknowledgments{We thank the anonymous referee for critically reviewing our initial version and providing many helpful comments.
+We thank Katie Brevik, Will Farr, Rob Farmer, Valeriya Korol, Floris Kummer, Eva Laplace, Mike Lau, Tyson Littenberg, Ilya Mandel, Mathieu Renzo, Alberto Sesana, Katie Sharpe, Simon Stevenson, the CCA GW group and COMPAS collaboration for insightful discussions.
 TW also thanks Terence Lovatt for his advice and help on improving an earlier draft of this project.
@@
 
-\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios \citep{Wagg+2021}.
+\software{We used LEGWORK to evolve sources over time and calculate signal-to-noise ratios \citep{LEGWORK_joss}.
 It is freely available at \url{https://legwork.readthedocs.io/en/latest/}.
@@
 \bibliographystyle{aasjournal}
-\bibliography{references}
+\bibliography{paper}
 

### 2022-07-29 paper/tex/sections/conclusion.tex

@@
 %
-For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS\edit1{, which can reproduce the current constraints on the overall GW rates \citep{Broekgaarden+2021,Broekgaarden+2021b, Abbott+2021_GWTC3}}.
+For the binary population, we use the results of a large grid of simulations performed with the rapid population synthesis code COMPAS \citep{Broekgaarden+2021,Broekgaarden+2021b}.
 Our suite of simulations consider 20 physics variations, which represent the most common uncertainties in binary physics.
 %
-We investigate the detectability of sources in the planned space-based GW detector LISA using the LEGWORK package \citep{Wagg+2021}, that we specifically developed for this purpose and is publicly available.
+We investigate the detectability of sources in the planned space-based GW detector LISA using the LEGWORK package \citep{LEGWORK_apjs}, that we specifically developed for this purpose and is publicly available.
 %

### 2022-07-29 paper/tex/sections/discussion.tex

@@
 
+\edit2{\paragraph{Correspondence with ground-based detections} The models used in this paper were shown to be consistent with the inferred merger rates from the GWTC-3 catalogue available at the time of submission (for example the BHBH rate was quoted as $16-130 \unit{Gpc^{-3}}{yr^{-1}}$ in section IV.A of version 1 and 2 on the arXiv in Nov 2021 \citealt{GWTC-3-previous}).
+We note, however, that the upper limit on the rate has come down by a factor two since, after the completion and submission of our work.
+The inferred BHBH merger rate is now quoted as $16-61 \unit{Gpc^{-3}}{yr^{-1}}$ in the final version of the GWTC-3 paper that appeared in Feb 2022 \citep{Abbott+2021_GWTC3}.
+This means that some model variations may over predict the current rates.}
+
 \subsection{Other formation channels}\label{sec:other_formation_channels}

### 2022-07-29 paper/tex/sections/methods.tex

@@
 \edit1{The model we refer to as our fiducial model allows for BHs with masses in the heavily debated mass gap, but we also consider \nModels{} physics variations.
-\citet{Broekgaarden+2021b} showed that all of these physics variations are still consistent with current constraints on the overall inferred GW rates, at least when considering large variations of the assumed metallicity specific cosmic star formation rate \citep{Abbott+2021_GWTC3}}.
 We summarise the main assumptions and settings relevant for this work in Appendix~\ref{app:pop_synth}.
+\edit2{We used these models since \citet{Broekgaarden+2021b} showed that each physics variation led to a rate prediction that was consistent with the constraints available from ground-based detections in GWTC-3 that were released at that time \citep{GWTC-3-previous}.
+We note that the upper limit on the rates has come down by a factor of two since the original appearance of this catalogue on the arXiv \citep{Abbott+2021_GWTC3}.
+We discuss this in further detail in Section~\ref{sec:caveats}}.}
 
@@
 \subsection{Gravitational wave detection}\label{sec:gw_detection}
-We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{Wagg+2021} to evolve binaries and calculate their LISA detectability.
-For a full derivation of the equations given below see \citep[][Section~3]{Wagg+2021}, or the LEGWORK documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
+We use the Python package \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{LEGWORK_apjs} to evolve binaries and calculate their LISA detectability.
+For a full derivation of the equations given below see \citep[][Section~3]{LEGWORK_apjs}, or the LEGWORK documentation \href{https://legwork.readthedocs.io/en/latest/notebooks/Derivations.html}{\faBook}.
 
@@
 
-We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{Wagg+2021} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational-wave luminosity remains below 1\%.
+We use \href{https://legwork.readthedocs.io/en/latest/}{LEGWORK} \citep{LEGWORK_apjs} to calculate the signal-to-noise ratio for each binary and the package ensures that enough harmonics are computed for each binary such that the error on the gravitational-wave luminosity remains below 1\%.
 
